### 2022-01-15 content/box2.profiles.Rmd

---
output: md_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

<!--# 
This document is created from box2.profiles.Rmd, please made edits to code generating the table there.

Edit the table contents here:https://docs.google.com/spreadsheets/d/1R0_NGhAWJ3cxGKQVh06eHKxHGMCN6x5aNL3_qR3nAI0/edit?usp=sharing 
-->

```{r include=FALSE}
library(googlesheets4)
library(tidyverse)
library(knitr)
library(pander)
```

```{r include=FALSE}
df <- read_sheet("1R0_NGhAWJ3cxGKQVh06eHKxHGMCN6x5aNL3_qR3nAI0")
```

```{r results='asis'}
set.alignment("left")
df %>% 
  replace_na(replace = list(Role = "", Description = "")) %>%
  pander(split.table = 10000, caption = "Collaborator profiles and some example use cases for GitHub features.  This is a non-exhaustive list intended to showcase some creative uses of GitHub for collaborative academic projects, such as collaborative manuscript writing.")
```

### 2022-03-02 R/scatterblob.Rmd
beginning of the scatterblob

---
title: "scatterblob"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# Figure 2 scatterblob

### 2022-03-09 R/scatterblob.Rmd
the scatterblob is alive

@@
 ---
-title: "scatterblob"
+title: "Figure: the scatterblob"
 output: html_document
@@
 ```
-# Figure 2 scatterblob
+
+Data for this figure was generated on a collaborative [google spread sheet](https://docs.google.com/spreadsheets/d/1Ls0DofQWSZQsqtP4OLFj326sGfWsklrI2tA1GNUTR6g/edit#gid=0).
+Cognitive load [was measured in a different file](https://docs.google.com/spreadsheets/d/1OLBR3M0uV3PMSazWUYHgPeX28wllAgS4PIlJXaNu-2o/edit#gid=0).
+
+Reading the data csv file:
+
+```{r}
+library(readr)
+scatterblob_data <- readr::read_csv("scatterblob_data.csv")
+View(scatterblob_data)
+```
+
+Creating the `my_data` object from :
+
+```{r}
+names(scatterblob_data)
+scatterblob_data$x1 <- scatterblob_data$`Degree of immediate collaborativeness X1`
+scatterblob_data$x2 <- scatterblob_data$`Degree of immediate collaborativeness X2`
+scatterblob_data$y <- scatterblob_data$`Cognitive load absolute`
+
+scatterblob_data$`Cognitive load` <- c(2,3,4,4.3,4.6,5,5.2,5.4,5.6,5.8,6,6.5,9,9.5)
+
+my_data <- scatterblob_data[,c("Ways to use GitHub","y", "x1", "x2")]
+my_data
+```
+
+Plotting `my_data`
+
+```{r}
+my_colors <- viridis::turbo(n = nrow(scatterblob_data))
+
+svg(filename = "scatterblob_0.svg", width = 5, height = 8, bg = "white")
+plot(x = scatterblob_data$x2, 
+     y = scatterblob_data$`Cognitive load`, 
+     xlab = "Immediate collaborativeness",
+     ylab = "Cognitive load",
+     col = "white")
+
+for (i in seq(nrow(scatterblob_data))) {
+  X0 <- scatterblob_data$x1[i]
+  X1 <- scatterblob_data$x2[i]
+  Y <- scatterblob_data$`Cognitive load`[i]
+  if (X0 == X1) {
+    points(x = X0, 
+           y = Y,
+           col = my_colors[i],
+           pch = 19)
+  text(x = X0, 
+       y = Y, 
+       labels = scatterblob_data$`Ways to use GitHub`[i],
+       adj = 0)
+  } else {
+    segments(x0 = X0,
+             x1 = X1,
+             y0 = Y,
+             col = my_colors[i],
+             lwd = 15)
+  text(x = median(c(X0, X1)), 
+       y = Y, 
+       labels = scatterblob_data$`Ways to use GitHub`[i],
+       adj = 0.5)
+  }
+}
+dev.off()
+```
+![First try](scatterblob_0.svg)
+
+Distributing cognitive load evenly:
+
+```{r}
+my_colors <- viridis::turbo(n = nrow(scatterblob_data), alpha = 0.5)
+
+svg(filename = "scatterblob.svg", width = 7, height = 9, bg = "white")
+par(xpd = TRUE, mai = c(1.02, 0.82, 0.82, 2))
+plot(x = c(0.1,6), 
+     y = c(0.1,15), 
+     xlab = "Collaborativeness",
+     ylab = "Cognitive load - absolute",
+     col = "white")
+
+my_colors <- viridis::turbo(n = nrow(scatterblob_data))
+
+for (i in seq(nrow(scatterblob_data))) {
+  X0 <- my_data$x1[i]
+  X1 <- my_data$x2[i]
+  Y <- my_data$y[i]
+  if (X0 == X1) {
+    X0 <- X0 - 0.05
+    X1 <- X1 + 0.05
+    adj_text <- -0.1
+   } else {
+    adj_text <- 0.5
+   }
+  segments(x0 = X0,
+           x1 = X1,
+           y0 = Y,
+           col = my_colors[i],
+           lwd = 20)
+   text(x = median(c(X0, X1)), 
+       y = Y, 
+       labels = my_data$`Ways to use GitHub`[i],
+       adj = adj_text)
+}
+dev.off()
+```
+
+![Second try](scatterblob.svg)

### 2022-03-09 R/collaborative_use_table.R
draft of table

@@ -1,0 +1,45 @@
+library(tidyverse)
+library(here)
+df <- read_csv(here("R", "uses.csv"), na = "N/A")
+
+df
+
+# Table part --------------------------------------------------------------
+
+library(gt)
+library(glue)
+
+#function to replace difficulty with lightning bolts
+
+diff_to_lightning <- function(x) map_chr(x, ~rep("⚡️", .x) %>% glue_collapse())
+
+table <- 
+  df %>% 
+  gt() %>% 
+  text_transform(cells_body(difficulty), fn = diff_to_lightning) %>% 
+  # make NAs blanks
+  fmt_missing(example, missing_text = "") %>% 
+  #hide color column, for now
+  cols_hide(color) %>% 
+  cols_align("left") %>% 
+  #fix up column names
+  cols_label(
+    ways = "GitHub Use",
+    difficulty = "Technical Difficulty",
+    example = "Example"
+  ) %>% 
+  #add footer for difficulty legend
+  tab_footnote(
+    "⚡️ = Beginner ⚡️⚡️ = Intermediate ⚡️⚡️⚡️ = Advanced",
+    locations = cells_column_labels(
+      difficulty
+    )
+  ) %>% 
+  #try just using the color column
+  cols_unhide(color) %>% 
+  # text_transform(cells_body(color),grDevices::colors)
+  data_color(columns = color,
+             colors = color)
+  #would look better as a separate big arrow
+
+gtsave(table, here("content", "images", "collaborative_use.png"))

### 2022-03-09 R/collaborative_use_table.R
rename data file

@@ -1,8 +1,15 @@
 library(tidyverse)
 library(here)
-df <- read_csv(here("R", "uses.csv"), na = "N/A")
+df <- read_csv(here("R", "collaborative_uses.csv"), na = "N/A")
 
 df
+
+
+# big arrow ---------------------------------------------------------------
+
+#this will look better if I draw a big color gradient arrow from individual to
+#collaborative and stick that next to the table with `patchwork` or something.
+
 
 # Table part --------------------------------------------------------------
 
@@ -43,3 +50,8 @@ table <-
   #would look better as a separate big arrow
 
 gtsave(table, here("content", "images", "collaborative_use.png"))
+
+
+# Stick em together -------------------------------------------------------
+
+library(patchwork)

### 2022-03-09 R/collaborative_use_table.R
draw gradient

@@ -2,15 +2,6 @@ library(tidyverse)
 library(here)
 df <- read_csv(here("R", "collaborative_uses.csv"), na = "N/A")
 
-df
-
-
-# big arrow ---------------------------------------------------------------
-
-#this will look better if I draw a big color gradient arrow from individual to
-#collaborative and stick that next to the table with `patchwork` or something.
-
-
 # Table part --------------------------------------------------------------
 
 library(gt)
@@ -41,17 +32,45 @@ table <-
     locations = cells_column_labels(
       difficulty
     )
-  ) %>% 
-  #try just using the color column
-  cols_unhide(color) %>% 
-  # text_transform(cells_body(color),grDevices::colors)
-  data_color(columns = color,
-             colors = color)
-  #would look better as a separate big arrow
+  ) 
+
+#   #try just using the color column
+# table %>% 
+#   cols_unhide(color) %>% 
+#   data_color(columns = color,
+#              colors = color)
 
 gtsave(table, here("content", "images", "collaborative_use.png"))
 
 
-# Stick em together -------------------------------------------------------
 
-library(patchwork)
+# gradient ---------------------------------------------------------------
+
+#this will look better if I draw a big color gradient from individual to
+#collaborative and stick that next to the table with `patchwork` or something.
+
+gradient <- ggplot(tibble(x = 1, y = 1:1000)) +
+  geom_line(aes(x, y, color = y),
+            size = 15) +
+  scale_color_gradient(high = "#7fffbb", low = "#081d57") +
+  annotate("label", x = 1, y = 1,
+           fill = "#081d57",
+           color = "white",
+           label = "Highly Collaborative",
+           label.padding = unit(0.5, "lines")) +
+  annotate("label", x = 1, y = 1000,
+           fill = "#7fffbb",
+           color = "black",
+           label = "Individual",
+           label.padding = unit(0.5, "lines")) +
+  theme_void() +
+  theme(legend.position = "none")
+gradient
+
+# Stick 'em together -------------------------------------------------------
+
+# library(patchwork)
+
+# gradient + table
+# apparently this doesn't work yet: https://github.com/thomasp85/patchwork/issues/203
+

### 2022-03-10 R/scatterblob.Rmd
updating the scatterblob

--- 2022-03-02 R/scatterblob.Rmd
@@
 ```
-# Figure 2 scatterblob
+
+Goal: This is a summary figure, e.g., "here are all the ways and here are the entry points with low technical difficulty, and some  for beginner s and the more advanced ways to use it".
+There are ways to use github that allows different degrees of collaboration that do not require too many technical skills.
+
+Use even notation across text and figure
+
+space out middle blobs
+labels to x and y axis
+homogenizing titles of ways to use github
+
+## The data
+
+Data for this figure was generated on a collaborative [google spread sheet](https://docs.google.com/spreadsheets/d/1Ls0DofQWSZQsqtP4OLFj326sGfWsklrI2tA1GNUTR6g/edit#gid=0).
+Cognitive load [was measured in a different file](https://docs.google.com/spreadsheets/d/1OLBR3M0uV3PMSazWUYHgPeX28wllAgS4PIlJXaNu-2o/edit#gid=0).
+
+Reading the data csv file:
+
+```{r}
+library(readr)
+scatterblob_data <- readr::read_csv("scatterblob_data.csv")
+View(scatterblob_data)
+```
+
+Creating the `my_data` object from :
+
+```{r}
+names(scatterblob_data)
+scatterblob_data$x1 <- scatterblob_data$`Degree of immediate collaborativeness X1`
+scatterblob_data$x2 <- scatterblob_data$`Degree of immediate collaborativeness X2`
+scatterblob_data$y <- scatterblob_data$`Cognitive load absolute`
+
+scatterblob_data$`Cognitive load` <- c(2,3,4,4.3,4.6,5,5.2,5.4,5.6,5.8,6,6.5,9,9.5)
+
+my_data <- scatterblob_data[,c("Ways to use GitHub","y", "x1", "x2")]
+my_data
+```
+
+## Plotting the data
+
+### First try
+
+Using original cognitive values.
+
+```{r}
+my_colors <- viridis::turbo(n = nrow(scatterblob_data), alpha = 0.9)
+
+svg(filename = "scatterblob_0.svg", width = 7, height = 11, bg = "white")
+
+par(xpd = TRUE, mai = c(1.02, 0.82, 0.82, 1), bty="n")
+
+plot(x = c(0.1,8), 
+     y = c(1.1,10), 
+     xlab = "Collaborativeness",
+     ylab = "Technical difficulty",
+     col = "white")
+
+for (i in seq(nrow(scatterblob_data))) {
+  X0 <- scatterblob_data$x1[i]
+  X1 <- scatterblob_data$x2[i]
+  Y <- scatterblob_data$`Cognitive load`[i]
+  if (X0 == X1) {
+    X0 <- X0 - 0.01
+    X1 <- X1 + 0.01
+    adj_text <- -0.1
+   } else {
+    adj_text <- 0.5
+   }
+  segments(x0 = X0,
+           x1 = X1,
+           y0 = Y,
+           col = my_colors[i],
+           lwd = 20)
+   text(x = median(c(X0, X1)), 
+       y = Y, 
+       labels = my_data$`Ways to use GitHub`[i],
+       adj = adj_text)
+}
+dev.off()
+```
+![Fgure 1. Degree of collaboration VS technical difficulty](scatterblob_0.svg)
+
+### Second try
+
+Distributing cognitive load evenly:
+
+```{r}
+my_colors <- viridis::turbo(n = nrow(scatterblob_data), alpha = 0.9)
+
+svg(filename = "scatterblob.svg", width = 7, height = 9, bg = "white")
+par(xpd = TRUE, mai = c(1.02, 0.82, 0.82, 2), bty="n")
+plot(x = c(0.1,6), 
+     y = c(0.1,15), 
+     xlab = "Collaborativeness",
+     ylab = "Technical difficulty",
+     col = "white")
+
+for (i in seq(nrow(scatterblob_data))) {
+  X0 <- my_data$x1[i]
+  X1 <- my_data$x2[i]
+  Y <- my_data$y[i]
+  if (X0 == X1) {
+    X0 <- X0 - 0.01
+    X1 <- X1 + 0.01
+    adj_text <- -0.1
+   } else {
+    adj_text <- 0.5
+   }
+  segments(x0 = X0,
+           x1 = X1,
+           y0 = Y,
+           col = my_colors[i],
+           lwd = 40)
+   text(x = median(c(X0, X1)), 
+       y = Y, 
+       labels = my_data$`Ways to use GitHub`[i],
+       adj = adj_text)
+}
+dev.off()
+```
+
+![Figure 2. Degree of collaboration VS Even technical difficulty](scatterblob.svg)

### 2022-03-24 R/figures_tables.R
rename to table 2

@@ -13,12 +13,12 @@ library(flextable) #another possible table formatting package.  Can output to ht
 library(patchwork) #for multi-panel figures, if necessary
 
 
-# Box 2 - collaborator profiles table -------------------------------------------
+# table 2 - collaborator profiles table -------------------------------------------
 # edit text in .csv file
-box2 <- read_csv(here("R", "collaborator_roles.csv"))
+table2 <- read_csv(here("R", "collaborator_roles.csv"))
 
-box2_gt <-
-  box2 %>%
+table2_gt <-
+  table2 %>%
   tidyr::fill(Role, Description) %>% 
   flextable() %>% 
   merge_v(j = 1:2) %>% 
@@ -29,8 +29,8 @@ box2_gt <-
   fix_border_issues() %>% 
   autofit()
 #TODO: make prettier
-save_as_image(box2_gt, here("content", "images", "box2_hires.pdf"))  
-save_as_image(box2_gt, here("content", "images", "box2.png"))  
+save_as_image(table2_gt, here("content", "images", "table2_hires.pdf"))  
+save_as_image(table2_gt, here("content", "images", "table2.png"))  
 
 
 

### 2022-03-24 R/figures_tables.R
renamed to "roles"

@@ -15,10 +15,10 @@ library(patchwork) #for multi-panel figures, if necessary
 
 # table 2 - collaborator profiles table -------------------------------------------
 # edit text in .csv file
-table2 <- read_csv(here("R", "collaborator_roles.csv"))
+roles <- read_csv(here("R", "collaborator_roles.csv"))
 
-table2_gt <-
-  table2 %>%
+roles_gt <-
+  roles %>%
   tidyr::fill(Role, Description) %>% 
   flextable() %>% 
   merge_v(j = 1:2) %>% 
@@ -29,8 +29,8 @@ table2_gt <-
   fix_border_issues() %>% 
   autofit()
 #TODO: make prettier
-save_as_image(table2_gt, here("content", "images", "table2_hires.pdf"))  
-save_as_image(table2_gt, here("content", "images", "table2.png"))  
+save_as_image(roles_gt, here("content", "images", "roles_hires.pdf"))  
+save_as_image(roles_gt, here("content", "images", "roles.png"))  
 
 
 

### 2022-03-24 R/figures_tables.R
finish rough formatting

@@ -17,20 +17,27 @@ library(patchwork) #for multi-panel figures, if necessary
 # edit text in .csv file
 roles <- read_csv(here("R", "collaborator_roles.csv"))
 
-roles_gt <-
+roles_wide <-
   roles %>%
   tidyr::fill(Role, Description) %>% 
+  pivot_wider(names_from = `GitHub Feature`, values_from = `Use Case`) %>% 
+  select(Role, `GitHub repo`, README, Issue, Discussion, `Pull Request`, Fork, `GitHub Pages`)
+  
+  
+roles_table <-
+  roles_wide %>% 
   flextable() %>% 
-  merge_v(j = 1:2) %>% 
-  valign(j=1:3, valign = "top") %>% 
-  border_outer() %>% 
-  border_inner_h() %>% 
-  border_inner_v() %>% 
-  fix_border_issues() %>% 
+  valign(j=1:7, valign = "top") %>% 
+  add_header_row(values = c("", "GitHub Feature"),
+                 colwidths = c(1, ncol(roles_wide) -1)) %>%
+  theme_box() %>% 
   autofit()
+roles_table
+
 #TODO: make prettier
-save_as_image(roles_gt, here("content", "images", "roles_hires.pdf"))  
-save_as_image(roles_gt, here("content", "images", "roles.png"))  
+
+save_as_image(roles_table, here("content", "images", "roles_hires.pdf"))  
+save_as_image(roles_table, here("content", "images", "roles.png"))  
 
 
 

### 2022-03-25 R/figures_tables.Rmd
Try out Rmd for generating figure and tables md with citations.

---
knit: (function(input_file, encoding) {
  out_dir <- '../content';
  rmarkdown::render(input_file,
 encoding=encoding,
 output_file=file.path(dirname(input_file), out_dir, '09.figures-tables.md'))})
output: 
  md_document:
    variant: gfm #for debugging, forces table to be markdown, not html
    # variant: markdown
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
library(knitr)
library(tidyverse) #data wrangling and ggplot2
library(here) #for reproducible relative file paths
library(gt) #for HTML tables (which can be saved as .pdf)
library(flextable) #another possible table formatting package.  Can output to html, word, powerpoint, pdf.  Supports cell merging
library(patchwork) #for multi-panel figures, if necessary
options(knitr.table.format = 'pipe')
```

## Tables

```{r roles}
roles <- read_csv(here("R", "collaborator_roles.csv"))

roles_wide <-
  roles %>%
  tidyr::fill(Role, Description) %>% 
  pivot_wider(names_from = `GitHub Feature`, values_from = `Use Case`) %>% 
  select(Role, `GitHub repo`, README, Issue, Discussion, `Pull Request`, Fork, `GitHub Pages`) %>% 
  mutate(across(everything(), ~replace_na(.x, "")))

kable(roles_wide, caption = "Table: A non-exhaustive collection of ideas for how various GitHub features could be utilized for a research project. Here we have categorized contributors/collaborators into five roles. A Project Manager owns the GitHub repository for a project, and leads the academic project (e.g., lead author of a manuscript). A co-author contributes to writing and other aspects of research, but may have limited or no experience with programming, git, and/or GitHub. A code contributor writes or edits analysis code for the project. A code reviewer could be a project collaborator or a peer reviewer who reviews project code. They are familiar with coding, but not necessarily with git or GitHub (but they are willing to learn). Finally, community members could be other researchers or non-researchers interested in reproducing results, re-using code or data, or communicating with researchers involved in the project. These roles are not mutually exclusive—a co-author could also be e code contributor and code reviewer, for example. For definitions of the GitHub features, see Box 1. {#tbl:roles}")
```

Test citation of the above table @tbl:roles

## Figures

Alternate way:

![Caption for the example figure.](../content/images/figure-2.png){#fig:testfig}

test citation for figure @fig:testfig

### 2022-03-25 R/roles_table.Rmd
rename and edit so .Rmd generated table stands alone kindof

--- 2022-03-25 R/figures_tables.Rmd
@@
  encoding=encoding,
- output_file=file.path(dirname(input_file), out_dir, '09.figures-tables.md'))})
+ output_file=file.path(dirname(input_file), out_dir, '10.roles_table.md'))})
 output: 
@@
 
-## Tables
+<!--DO NOT EDIT. Generated from R/roles_table.Rmd, so edit that and render it to make changes.  This should get tacked on to the end of 09.figures-tables.md when compiled by Manubot -->
 
@@
 Test citation of the above table @tbl:roles
-
-## Figures
-
-Alternate way:
-
-![Caption for the example figure.](../content/images/figure-2.png){#fig:testfig}
-
-test citation for figure @fig:testfig

### 2022-03-31 R/scatterblob.Rmd
edits after small group discussion

@@
 
-svg(filename = "scatterblob_0.svg", width = 7, height = 11, bg = "white")
+svg(filename = "scatterblob_0.svg", width = 7, height = 15, bg = "white")
 
@@
    } else {
-    adj_text <- 0.5
+    # adj_text <- 0.5
+    adj_text <- 0
    }
@@
            col = my_colors[i],
-           lwd = 20)
-   text(x = median(c(X0, X1)), 
+           lwd = 25)
+   text(#x = median(c(X0, X1)),
+        x = X1,
        y = Y, 
@@
 ```
-![Fgure 1. Degree of collaboration VS technical difficulty](scatterblob_0.svg)
+![Figure 1. Degree of collaboration VS technical difficulty](scatterblob_0.svg)
 

### 2022-03-31 R/scatterblob.Rmd
workable figure versions of the scatter blob

--- 2022-03-10 R/scatterblob.Rmd
@@
 scatterblob_data <- readr::read_csv("scatterblob_data.csv")
+library(googlesheets4)
+scatterblob_data <- googlesheets4::read_sheet(ss = "https://docs.google.com/spreadsheets/d/1Ls0DofQWSZQsqtP4OLFj326sGfWsklrI2tA1GNUTR6g/edit?pli=1#gid=0")
+
 View(scatterblob_data)
+
 ```
@@
 scatterblob_data$y <- scatterblob_data$`Cognitive load absolute`
-
-scatterblob_data$`Cognitive load` <- c(2,3,4,4.3,4.6,5,5.2,5.4,5.6,5.8,6,6.5,9,9.5)
 
@@
 my_colors <- viridis::turbo(n = nrow(scatterblob_data), alpha = 0.9)
-
-svg(filename = "scatterblob_0.svg", width = 7, height = 11, bg = "white")
-
-par(xpd = TRUE, mai = c(1.02, 0.82, 0.82, 1), bty="n")
-
-plot(x = c(0.1,8), 
-     y = c(1.1,10), 
-     xlab = "Collaborativeness",
-     ylab = "Technical difficulty",
-     col = "white")
-
+###############################################################
+# start the pdf connection and set graphical parameters
+###############################################################
+pdf(file = "scatterblob_0.pdf", 
+    width = 8.25, 
+    height = 6, 
+    bg = "transparent")
+par(xpd = NA, 
+    mai = c(1.02, 1, 0.82, 4), 
+    bty="n")
+###############################################################
+# create the plot background
+###############################################################
+plot(x = c(0.5, 5.5), 
+     y = c(1.75, 9.75), 
+     xlab = "",
+     ylab = "",
+     col = "white",
+     # "hide" the tick labels so we can put some words instead of numbers:
+     col.axis = "white",
+     tck = 0.02) 
+title(ylab="Technical difficulty", line=4, cex.lab=1)
+title(xlab="Degree of collaborativeness", line= 3.5, cex.lab=1)
+###############################################################
+# add tick labels
+###############################################################
+text(x = 1:5,
+     y = c(1, rep(1.05, 4)), 
+     cex = 0.7,
+     labels = c("Personal", 
+                "Lab \nmembers", 
+                "Other \nlabs", 
+                "The \ncommunity", 
+                "The \npublic"))
+text(x = c(1, 3, 5),
+     y = 0.5, 
+     labels = c("Low", "Medium", "High"))
+# Technical difficulty levels from https://www.londonschool.com/level-scale/
+text(x = 0.2,
+     y = c(2, 4, 6, 8, 10), 
+     cex = 0.7,
+     adj = 1,
+     labels = c("Elementary", 
+                "Low \nintermediate", 
+                "Intermediate", 
+                "Pre- \nAdvanced", 
+                "Very \nAdvanced"))
+###############################################################
+# plot scatter blobs
+###############################################################
 for (i in seq(nrow(scatterblob_data))) {
@@
     X1 <- X1 + 0.01
-    adj_text <- -0.1
-   } else {
-    adj_text <- 0.5
    }
@@
            col = my_colors[i],
-           lwd = 20)
-   text(x = median(c(X0, X1)), 
-       y = Y, 
-       labels = my_data$`Ways to use GitHub`[i],
-       adj = adj_text)
+           lwd = 13)
 }
+###############################################################
+# add github uses text
+###############################################################
+text(x = 5.5,
+    y = scatterblob_data$`Cognitive load`, 
+    labels = my_data$`Ways to use GitHub`,
+    adj = 0,
+    col = my_colors)
 dev.off()
 ```
-![Fgure 1. Degree of collaboration VS technical difficulty](scatterblob_0.svg)
+![Figure 1. Degree of collaboration VS technical difficulty](scatterblob_0.pdf)
 
@@
 my_colors <- viridis::turbo(n = nrow(scatterblob_data), alpha = 0.9)
-
-svg(filename = "scatterblob.svg", width = 7, height = 9, bg = "white")
-par(xpd = TRUE, mai = c(1.02, 0.82, 0.82, 2), bty="n")
-plot(x = c(0.1,6), 
-     y = c(0.1,15), 
-     xlab = "Collaborativeness",
-     ylab = "Technical difficulty",
-     col = "white")
-
+###############################################################
+# start the pdf connection and set graphical parameters
+###############################################################
+pdf(file = "scatterblob_1.pdf", 
+    width = 8.25, 
+    height = 6, 
+    bg = "transparent")
+par(xpd = NA, 
+    mai = c(1.02, 1, 0.82, 4), 
+    bty="n")
+plot(x = c(0.5, 5.5), 
+     y = c(0.5, 14), 
+     xlab = "",
+     ylab = "",
+     col = "white",
+     # "hide" the tick labels so we can put some words instead of numbers:
+     col.axis = "white",
+     tck = 0.02) 
+title(ylab="Technical difficulty", line=4, cex.lab=1)
+title(xlab="Degree of collaborativeness", line= 3.5, cex.lab=1)
+###############################################################
+# add tick labels
+###############################################################
+text(x = 1:5,
+     y = c(-0.65, rep(-0.7, 4)), 
+     cex = 0.7,
+     labels = c("Personal", 
+                "Lab \nmembers", 
+                "Other \nlabs", 
+                "The \ncommunity", 
+                "The \npublic"))
+text(x = c(1, 3, 5),
+     y = -1.7, 
+     labels = c("Low", "Medium", "High"))
+# Technical difficulty levels from https://www.londonschool.com/level-scale/
+text(x = 0.2,
+     y = c(0, 2, 4, 6, 8, 10, 12, 14), 
+     cex = 0.7,
+     adj = 1,
+     labels = c("Beginner",
+                "Elementary", 
+                "Low\nintermediate",
+                "Pre-\nintermediate",
+                "Intermediate", 
+                "Upper\nintermediate",
+                "Pre-\nAdvanced", 
+                "Very\nAdvanced"))
+###############################################################
+# plot scatter blobs on sequential cognitive load
+###############################################################
 for (i in seq(nrow(scatterblob_data))) {
@@
            col = my_colors[i],
-           lwd = 40)
-   text(x = median(c(X0, X1)), 
-       y = Y, 
-       labels = my_data$`Ways to use GitHub`[i],
-       adj = adj_text)
+           lwd = 23)
 }
+###############################################################
+# add github uses text
+###############################################################
+text(x = 5.5,
+    y = my_data$y, 
+    labels = my_data$`Ways to use GitHub`,
+    adj = 0,
+    col = my_colors)
 dev.off()
@@
 
-![Figure 2. Degree of collaboration VS Even technical difficulty](scatterblob.svg)
+![Figure 2. Degree of collaboration VS Even technical difficulty](scatterblob_1.pdf)

### 2022-03-31 R/scatterblob.Rmd
some edits

@@
 ```{r}
-library(readr)
-scatterblob_data <- readr::read_csv("scatterblob_data.csv")
+# library(readr)
+# scatterblob_data <- readr::read_csv("scatterblob_data.csv")
 library(googlesheets4)
@@
 View(scatterblob_data)
-
 ```

### 2022-04-01 R/roles_table.Rmd
Got tables and table references working with manubot

@@
   md_document:
-    variant: gfm #for debugging, forces table to be markdown, not html
-    # variant: markdown
+    variant: gfm #forces table to be markdown, not html
 ---
@@
 
-Test citation of the above table @tbl:roles
+<!-- An example citation of this table (Table @tbl:roles). -->

### 2022-04-01 R/figures_tables.R

@@ -1,43 +1,0 @@
-##' Use this script for generating figures or tables.  Save outputs to
-##' ../content/images using the `here()` package with `here("content", "images",
-##' "<filename>")`.  Ideally save images as both a .png (for including into the
-##' manuscript) and a high res .tiff or vector format like .pdf, .eps, or .svg
-##' (for submission to journal).
-##' 
-# Load Packages -----------------------------------------------------------
-
-library(tidyverse) #data wrangling and ggplot2
-library(here) #for reproducible relative file paths
-library(gt) #for HTML tables (which can be saved as .pdf)
-library(flextable) #another possible table formatting package.  Can output to html, word, powerpoint, pdf.  Supports cell merging
-library(patchwork) #for multi-panel figures, if necessary
-
-
-# table 2 - collaborator profiles table -------------------------------------------
-# edit text in .csv file
-roles <- read_csv(here("R", "collaborator_roles.csv"))
-
-roles_wide <-
-  roles %>%
-  tidyr::fill(Role, Description) %>% 
-  pivot_wider(names_from = `GitHub Feature`, values_from = `Use Case`) %>% 
-  select(Role, `GitHub repo`, README, Issue, Discussion, `Pull Request`, Fork, `GitHub Pages`)
-  
-  
-roles_table <-
-  roles_wide %>% 
-  flextable() %>% 
-  valign(j=1:7, valign = "top") %>% 
-  add_header_row(values = c("", "GitHub Feature"),
-                 colwidths = c(1, ncol(roles_wide) -1)) %>%
-  theme_box() %>% 
-  autofit()
-roles_table
-
-#TODO: make prettier
-
-save_as_image(roles_table, here("content", "images", "roles_hires.pdf"))  
-save_as_image(roles_table, here("content", "images", "roles.png"))  
-
-
-

### 2022-04-11 R/scatterblob.Rmd
fixing some lost files
png and svg versions of both figures

--- 2022-03-31 R/scatterblob.Rmd
@@
 my_colors <- viridis::turbo(n = nrow(scatterblob_data), alpha = 0.9)
-
-svg(filename = "scatterblob_0.svg", width = 7, height = 15, bg = "white")
-
-par(xpd = TRUE, mai = c(1.02, 0.82, 0.82, 1), bty="n")
-
-plot(x = c(0.1,8), 
-     y = c(1.1,10), 
-     xlab = "Collaborativeness",
-     ylab = "Technical difficulty",
-     col = "white")
-
+###############################################################
+# start the pdf/png connection and set graphical parameters
+###############################################################
+# plot_format <- "pdf"
+plot_format <- "svg"
+# plot_format <- "png"
+if (plot_format == "pdf") {
+  pdf(file = "scatterblob_0.pdf",
+      width = 8.25,
+      height = 6,
+      bg = "transparent")  
+}
+if (plot_format == "svg") {
+  svg(filename = "scatterblob_0.svg",
+      width = 8.25,
+      height = 6,
+      bg = "transparent")  
+}
+if (plot_format == "png") {
+  png(file = "scatterblob_0.png",
+      width = 8.25,
+      height = 6,
+      units = "in",
+      res = 100,
+      bg = "transparent")  
+}
+par(xpd = NA,
+    mai = c(1.02, 1, 0.82, 4),
+    bty="n")
+###############################################################
+# create the plot background
+###############################################################
+plot(x = c(0.5, 5.5),
+     y = c(1.75, 9.75),
+     xlab = "",
+     ylab = "",
+     col = "white",
+     # "hide" the tick labels so we can put some words instead of numbers:
+     col.axis = "white",
+     tck = 0.02)
+title(ylab="Technical difficulty", line=4, cex.lab=1)
+title(xlab="Degree of collaborativeness", line= 3.5, cex.lab=1)
+###############################################################
+# add tick labels
+###############################################################
+text(x = 1:5,
+     y = c(1, rep(1.05, 4)),
+     cex = 0.7,
+     labels = c("Personal",
+                "Lab \nmembers",
+                "Other \nlabs",
+                "The \ncommunity",
+                "The \npublic"))
+text(x = c(1, 3, 5),
+     y = 0.5,
+     labels = c("Low", "Medium", "High"))
+# Technical difficulty levels from https://www.londonschool.com/level-scale/
+text(x = 0.2,
+     y = c(2, 4, 6, 8, 10),
+     cex = 0.7,
+     adj = 1,
+     labels = c("Elementary",
+                "Low \nintermediate",
+                "Intermediate",
+                "Pre- \nAdvanced",
+                "Very \nAdvanced"))
+###############################################################
+# plot scatter blobs
+###############################################################
 for (i in seq(nrow(scatterblob_data))) {
@@
     X1 <- X1 + 0.01
-    adj_text <- -0.1
-   } else {
-    # adj_text <- 0.5
-    adj_text <- 0
    }
@@
            col = my_colors[i],
-           lwd = 25)
-   text(#x = median(c(X0, X1)),
-        x = X1,
-       y = Y, 
-       labels = my_data$`Ways to use GitHub`[i],
-       adj = adj_text)
+           lwd = 13)
 }
+###############################################################
+# add github uses text
+###############################################################
+text(x = 5.5,
+    y = scatterblob_data$`Cognitive load`,
+    labels = my_data$`Ways to use GitHub`,
+    adj = 0,
+    col = my_colors)
 dev.off()
 ```
-![Figure 1. Degree of collaboration VS technical difficulty](scatterblob_0.svg)
+![Figure 1. Degree of collaboration VS technical difficulty](scatterblob_0.pdf)
 
@@
 my_colors <- viridis::turbo(n = nrow(scatterblob_data), alpha = 0.9)
-
-svg(filename = "scatterblob.svg", width = 7, height = 9, bg = "white")
-par(xpd = TRUE, mai = c(1.02, 0.82, 0.82, 2), bty="n")
-plot(x = c(0.1,6), 
-     y = c(0.1,15), 
-     xlab = "Collaborativeness",
-     ylab = "Technical difficulty",
-     col = "white")
-
+###############################################################
+# start the pdf/png/svg connection and set graphical parameters
+###############################################################
+# plot_format <- "pdf"
+# plot_format <- "svg"
+plot_format <- "png"
+if (plot_format == "pdf") {
+  pdf(file = "scatterblob_1.pdf",
+      width = 8.25,
+      height = 6,
+      bg = "transparent")  
+}
+if (plot_format == "svg") {
+  svg(filename = "scatterblob_1.svg",
+      width = 8.25,
+      height = 6,
+      bg = "transparent")  
+}
+if (plot_format == "png") {
+  png(file = "scatterblob_1.png",
+      width = 8.25,
+      height = 6,
+      units = "in",
+      res = 100,
+      bg = "transparent")  
+}
+par(xpd = NA,
+    mai = c(1.02, 1, 0.82, 4),
+    bty="n")
+###############################################################
+# create the plot background
+###############################################################
+plot(x = c(0.5, 5.5),
+     y = c(0.5, 14),
+     xlab = "",
+     ylab = "",
+     col = "white",
+     # "hide" the tick labels so we can put some words instead of numbers:
+     col.axis = "white",
+     tck = 0.02)
+title(ylab="Technical difficulty", line=4, cex.lab=1)
+title(xlab="Degree of collaborativeness", line= 3.5, cex.lab=1)
+###############################################################
+# add tick labels
+###############################################################
+text(x = 1:5,
+     y = c(-0.65, rep(-0.7, 4)), 
+     cex = 0.7,
+     labels = c("Personal", 
+                "Lab \nmembers", 
+                "Other \nlabs", 
+                "The \ncommunity", 
+                "The \npublic"))
+text(x = c(1, 3, 5),
+     y = -1.7, 
+     labels = c("Low", "Medium", "High"))
+# Technical difficulty levels from https://www.londonschool.com/level-scale/
+text(x = 0.2,
+     y = c(0, 2, 4, 6, 8, 10, 12, 14), 
+     cex = 0.7,
+     adj = 1,
+     labels = c("Beginner",
+                "Elementary", 
+                "Low\nintermediate",
+                "Pre-\nintermediate",
+                "Intermediate", 
+                "Upper\nintermediate",
+                "Pre-\nAdvanced", 
+                "Very\nAdvanced"))
+###############################################################
+# plot scatter blobs on sequential cognitive load
+###############################################################
 for (i in seq(nrow(scatterblob_data))) {
@@
            col = my_colors[i],
-           lwd = 40)
-   text(x = median(c(X0, X1)), 
-       y = Y, 
-       labels = my_data$`Ways to use GitHub`[i],
-       adj = adj_text)
+           lwd = 23)
 }
+###############################################################
+# add github uses text
+###############################################################
+text(x = 5.5,
+    y = my_data$y,
+    labels = my_data$`Ways to use GitHub`,
+    adj = 0,
+    col = my_colors)
 dev.off()

### 2022-04-11 R/roles_table.Rmd
output image of table

@@
 library(knitr)
-library(tidyverse) #data wrangling and ggplot2
+library(tidyverse) #data wrangling
 library(here) #for reproducible relative file paths
-library(gt) #for HTML tables (which can be saved as .pdf)
 library(flextable) #another possible table formatting package.  Can output to html, word, powerpoint, pdf.  Supports cell merging
-library(patchwork) #for multi-panel figures, if necessary
 options(knitr.table.format = 'pipe')
@@
 
-```{r roles}
+```{r wrangle, include=FALSE}
 roles <- read_csv(here("R", "collaborator_roles.csv"))
@@
   mutate(across(everything(), ~replace_na(.x, "")))
+```
 
+```{r save-img, include=FALSE}
+#produce a png version using flextable()
+roles_table <- flextable(roles_wide) %>% 
+  valign(j=1:8, valign = "top") %>% 
+  border_outer() %>% 
+  border_inner_h() %>% 
+  border_inner_v()
+# save_as_image(roles_table, here("content", "images", "roles_hires.pdf"))  
+save_as_image(roles_table, here("content", "images", "roles.png"))
+```
+
+```{r roles}
 kable(roles_wide, caption = "Table: A non-exhaustive collection of ideas for how various GitHub features could be utilized for a research project.

### 2022-04-12 R/scatterblob.Rmd
modifying difficulty (and collaborativeness) for citeable code

--- 2022-03-31 R/scatterblob.Rmd
@@
 
-Use even notation across text and figure
-
-space out middle blobs
-labels to x and y axis
+Use even notation across text and figure:
 homogenizing titles of ways to use github
@@
 ```{r}
-library(readr)
-scatterblob_data <- readr::read_csv("scatterblob_data.csv")
+#library(readr)
+#scatterblob_data <- readr::read_csv("scatterblob_data.csv")
 library(googlesheets4)
@@
 names(scatterblob_data)
-scatterblob_data$x1 <- scatterblob_data$`Degree of immediate collaborativeness X1`
-scatterblob_data$x2 <- scatterblob_data$`Degree of immediate collaborativeness X2`
-scatterblob_data$y <- scatterblob_data$`Cognitive load absolute`
+scatterblob_data$x1 <- scatterblob_data$`Min degree of collaborativeness X1`
+scatterblob_data$x2 <- scatterblob_data$`Max degree of collaborativeness X2`
+scatterblob_data$y_real <- scatterblob_data$`Cognitive load - real`
+scatterblob_data$y_seq <- scatterblob_data$`Cognitive load - sequential`
 
-my_data <- scatterblob_data[,c("Ways to use GitHub","y", "x1", "x2")]
+my_data <- scatterblob_data[,c("Ways to use GitHub","y_seq", "y_real", "x1", "x2")]
 my_data
@@
 ###############################################################
-# start the pdf connection and set graphical parameters
+# start the pdf/png connection and set graphical parameters
 ###############################################################
+# plot_format <- "pdf"
+# plot_format <- "svg"
+plot_format <- "png"
+if (plot_format == "pdf") {
   pdf(file = "scatterblob_0.pdf",
@@
       bg = "transparent")  
+}
+if (plot_format == "svg") {
+  svg(filename = "scatterblob_0.svg",
+      width = 8.25,
+      height = 6,
+      bg = "transparent")  
+}
+if (plot_format == "png") {
+  png(file = "scatterblob_0.png",
+      width = 8.25,
+      height = 6,
+      units = "in",
+      res = 100,
+      bg = "transparent")  
+}
 par(xpd = NA,
@@
 for (i in seq(nrow(scatterblob_data))) {
-  X0 <- scatterblob_data$x1[i]
-  X1 <- scatterblob_data$x2[i]
-  Y <- scatterblob_data$`Cognitive load`[i]
+  X0 <- my_data$x1[i]
+  X1 <- my_data$x2[i]
+  Y <- my_data$y_real[i]
   if (X0 == X1) {
@@
 text(x = 5.5,
-    y = scatterblob_data$`Cognitive load`, 
+    y = my_data$y_real,
     labels = my_data$`Ways to use GitHub`,
@@
 ###############################################################
-# start the pdf connection and set graphical parameters
+# start the pdf/png/svg connection and set graphical parameters
 ###############################################################
+ plot_format <- "pdf"
+# plot_format <- "svg"
+# plot_format <- "png"
+if (plot_format == "pdf") {
   pdf(file = "scatterblob_1.pdf",
@@
       bg = "transparent")  
+}
+if (plot_format == "svg") {
+  svg(filename = "scatterblob_1.svg",
+      width = 8.25,
+      height = 6,
+      bg = "transparent")  
+}
+if (plot_format == "png") {
+  png(file = "scatterblob_1.png",
+      width = 8.25,
+      height = 6,
+      units = "in",
+      res = 100,
+      bg = "transparent")  
+}
 par(xpd = NA,
@@
     bty="n")
+###############################################################
+# create the plot background
+###############################################################
 plot(x = c(0.5, 5.5),
-     y = c(0.5, 14), 
+     y = c(0.5, nrow(my_data)),
      xlab = "",
@@
 text(x = 0.2,
-     y = c(0, 2, 4, 6, 8, 10, 12, 14), 
+     y = c(0, 2, 4, 6, 8, 10, 12, 14, 15.5), 
      cex = 0.7,
@@
                 "Pre-\nAdvanced",
+                "Advanced",
                 "Very\nAdvanced"))
@@
   X1 <- my_data$x2[i]
-  Y <- my_data$y[i]
+  Y <- my_data$y_seq[i]
   if (X0 == X1) {
@@
 text(x = 5.5,
-    y = my_data$y, 
+    y = my_data$y_seq,
     labels = my_data$`Ways to use GitHub`,

### 2022-04-15 R/scatterblob.Rmd

@@
 knitr::opts_chunk$set(echo = TRUE)
+library(googlesheets4)
+library(here)
+library(readr)
 ```
@@
 ```{r}
-#library(readr)
-#scatterblob_data <- readr::read_csv("scatterblob_data.csv")
-library(googlesheets4)
-scatterblob_data <- googlesheets4::read_sheet(ss = "https://docs.google.com/spreadsheets/d/1Ls0DofQWSZQsqtP4OLFj326sGfWsklrI2tA1GNUTR6g/edit?pli=1#gid=0")
-
-View(scatterblob_data)
-
+scatterblob_data <- read_csv(here("data", "scatterblob_data_raw.csv"))
+# View(scatterblob_data)
 ```
@@
 ## Plotting the data
+```{r}
+outpath <- here("content", "images")
+```
 
@@
 ###############################################################
-# plot_format <- "pdf"
+plot_format <- "pdf"
 # plot_format <- "svg"
-plot_format <- "png"
+# plot_format <- "png"
+
 if (plot_format == "pdf") {
-  pdf(file = "scatterblob_0.pdf",
+  pdf(file = here(outpath, "scatterblob_0.pdf"),
       width = 8.25,
@@
 if (plot_format == "svg") {
-  svg(filename = "scatterblob_0.svg",
+  svg(filename = here(outpath, "scatterblob_0.svg"),
       width = 8.25,
@@
 if (plot_format == "png") {
-  png(file = "scatterblob_0.png",
+  png(file = here(outpath, "scatterblob_0.png"),
       width = 8.25,
@@
 plot_format <- "pdf"
+# plot_format <- "png"
 # plot_format <- "svg"
-# plot_format <- "png"
+
 if (plot_format == "pdf") {
-  pdf(file = "scatterblob_1.pdf",
+  pdf(file = here(outpath, "scatterblob_1.pdf"),
       width = 8.25,
@@
 if (plot_format == "svg") {
-  svg(filename = "scatterblob_1.svg",
+  svg(filename = here(outpath, "scatterblob_1.svg"),
       width = 8.25,
@@
 if (plot_format == "png") {
-  png(file = "scatterblob_1.png",
+  png(file = here(outpath, "scatterblob_1.png"),
       width = 8.25,

### 2022-04-19 R/comparison_table.Rmd

--- 2022-04-11 R/roles_table.Rmd
@@
  encoding=encoding,
- output_file=file.path(dirname(input_file), out_dir, '10.roles_table.md'))})
+ output_file=file.path(dirname(input_file), out_dir, '11.comparison_table.md'))})
 output: 
@@
 
-<!--DO NOT EDIT. Generated from R/roles_table.Rmd, so edit that and render it to make changes.  This should get tacked on to the end of 09.figures-tables.md when compiled by Manubot -->
+<!--DO NOT EDIT. Generated from R/comparison_table.Rmd, so edit that and render it to make changes.  This should get tacked on to the end of 09.figures-tables.md when compiled by Manubot -->
 
 ```{r wrangle, include=FALSE}
-roles <- read_csv(here("R", "collaborator_roles.csv"))
-
-roles_wide <-
-  roles %>%
-  tidyr::fill(Role, Description) %>% 
-  pivot_wider(names_from = `GitHub Feature`, values_from = `Use Case`) %>% 
-  select(Role, `GitHub repo`, README, Issue, Discussion, `Pull Request`, Fork, `GitHub Pages`) %>% 
-  mutate(across(everything(), ~replace_na(.x, "")))
+comp_tbl <- read_csv(here("data", "comparison_table_raw.csv"))
 ```
 
-```{r save-img, include=FALSE}
-#produce a png version using flextable()
-roles_table <- flextable(roles_wide) %>% 
-  valign(j=1:8, valign = "top") %>% 
-  border_outer() %>% 
-  border_inner_h() %>% 
-  border_inner_v()
-# save_as_image(roles_table, here("content", "images", "roles_hires.pdf"))  
-save_as_image(roles_table, here("content", "images", "roles.png"))
+```{r compare}
+kable(comp_tbl, caption = "Table: a comparison of technologies... {#tbl:compare}")
 ```
 
-```{r roles}
-kable(roles_wide, caption = "Table: A non-exhaustive collection of ideas for how various GitHub features could be utilized for a research project.
-Here we have categorized contributors/collaborators into five roles.
-A Project Manager owns the GitHub repository for a project, and leads the academic project (e.g., lead author of a manuscript).
-A co-author contributes to writing and other aspects of research, but may have limited or no experience with programming, git, and/or GitHub.
-A code contributor writes or edits analysis code for the project.
-A code reviewer could be a project collaborator or a peer reviewer who reviews project code.
-They are familiar with coding, but not necessarily with git or GitHub (but they are willing to learn).
-Finally, community members could be other researchers or non-researchers interested in reproducing results, re-using code or data, or communicating with researchers involved in the project.
-These roles are not mutually exclusive—a co-author could also be e code contributor and code reviewer, for example.
-For definitions of the GitHub features, see Box 1.
-{#tbl:roles}")
-```
-
-<!-- An example citation of this table (Table @tbl:roles). -->
+<!-- An example citation of this table (Table @tbl:compare). -->

### 2022-04-19 editorial-communication/cover-letter-submission.Rmd
Setting up a standard RMarkdown document for the cover letter

---
title: Habits
author: John Doe
date: March 22, 2005
output:
  html_document:
    theme: cosmo 
    highlight: tango
    self_contained: true
---
```{r include=FALSE}
knitr::opts_chunk$set(fig.retina = 2)
```

```{r ipsum_setup, message=FALSE, warning=FALSE, cache=FALSE, echo=FALSE}
library(hrbrthemes)
library(tidyverse)

update_geom_font_defaults(font_rc)
```
Captain John Sheridan: You know, I just had a thought. You've been back and forth to your world so many times since you got here. How do I know you're the same Vorlon? Inside that encounter suit you could be anyone. Kosh Naranek: I have *always* been here. Captain John Sheridan: Oh, yeah? You said that about me too. Kosh Naranek: Yes. [starts to walk away] Captain John Sheridan: I really *hate* it when you do that. Kosh Naranek: [turns around] Good! Delenn: I am Grey. I stand between the candle and the star. We are Grey. We stand between the darkness and the light.

Lt. Corwin: Do we trust no-one then? Cmdr. Susan Ivanova: No, trust Ivanova, trust yourself, anybody else, shoot'em. Ta'Lon: Congratulations citizen G'Kar. You are now a religious icon. Susan Ivanova: So the next time we find out where the Shadows plan to strike, we can mine the area, and as soon as they come out of hyperspace... Citizen G'Kar: Then, as you so concisely say, Boom!

## Section Title

G'Kar: It is said that the future is always born in pain. The history of war is the history of pain. If we are wise, what is born of that pain matures into the promise of a better world, because we learn that we can no longer afford the mistakes of the past. Dr. Stephen Franklin: Doesn't anyone listen to one damn word I say? Captain John Sheridan: No surrender, no retreat. [Opening narration, season 4] Lennier: It was the year of fire, Zack Allan: The year of destruction, Citizen G'Kar: The year we took back what was ours. Lyta Alexander: It was the year of rebirth, Ambassador Vir Cotto: The year of great sadness, Marcus Cole: The year of pain, Delenn: And a year of joy. Ambassador Londo Mollari: It was a new age. Dr. Stephen Franklin: It was the end of history. Susan Ivanova: It was the year everything changed. Michael Garibaldi: The year is 2261. Captain John Sheridan: The place, Babylon 5. Sinclair: They say God works in mysterious ways. Michael Garibaldi: Maybe so, but He's a con-man compared to the Vorlon.

## Figures

```{r, fig.show='hold'}
ggplot(mtcars, aes(wt, mpg)) +
  geom_point() +
  labs(title="mtcars again, it seems") +
  theme_ipsum_rc(grid="XY")

```

### Level 3

Commander Jeffrey David Sinclair: Everyone lies, Michael. The innocent lie because they don't want to be blamed for something they didn't do and the guilty lie because they don't have any other choice. Lt. Corwin: Do we trust no-one then? Cmdr. Susan Ivanova: No, trust Ivanova, trust yourself, anybody else, shoot'em. Susan Ivanova: If I live through this without completely losing my mind, it will be a miracle of Biblical proportions.

Lt. Corwin: [aside] Well, there goes my faith in the Almighty. [Opening narration, season 3] Susan Ivanova: The Babylon Project was our last, best hope for peace. It failed. But in the year of the Shadow War, it became something greater: our last, best hope for victory. The year is 2260. The place - Babylon 5. Alfred Bester: Being a telepath means you're special and rare and valuable.

#### Level 4

Delenn: We are star stuff. We are the universe made manifest trying to figure itself out.

Captain John Sheridan: If more of our so-called leaders would walk the same streets as the people who voted them in, live in the same buildings, eat the same food instead of hiding behind glass and steel and bodyguards, maybe we'd get better leadership and a little more concern for the future.

Captain John Sheridan: If more of our so-called leaders would walk the same streets as the people who voted them in, live in the same buildings, eat the same food instead of hiding behind glass and steel and bodyguards, maybe we'd get better leadership and a little more concern for the future. Kosh Naranek: Understanding is a three-edged sword. Alfred Bester: Much as it might offend their sense of perspective, not everything is about Babylon 5.

```{r bib, include=FALSE}
# KEEP THIS AT THE END OF THE DOCUMENT TO GENERATE A LOCAL bib FILE FOR PKGS USED
knitr::write_bib(sub("^package:", "", grep("package", search(), value=TRUE)), file='skeleton.bib')
```

### 2022-04-19 editorial-communication/cover-letter-submission.Rmd
Adding an action to render and deploy the editorial communication material
This commit includes a GitHub Action Workflow to render an RMarkdown file containing the letter to the editor and deploy it in the `gh-pages` branch

@@
 ---
-title: Habits
-author: John Doe
-date: March 22, 2005
+title: Letter to the Editor
+author: "Not just for programmers: A friendly guide on the benefits of GitHub for accelerating collaborative research in Ecology and Evolution"
+date: "Last compiled on `r format(Sys.time(), '%d %B, %Y')`"
 output:
@@
 ```
-Captain John Sheridan: You know, I just had a thought.
-You've been back and forth to your world so many times since you got here.
-How do I know you're the same Vorlon?
-Inside that encounter suit you could be anyone.
-Kosh Naranek: I have *always* been here.
-Captain John Sheridan: Oh, yeah?
-You said that about me too.
-Kosh Naranek: Yes.
-[starts to walk away] Captain John Sheridan: I really *hate* it when you do that.
-Kosh Naranek: [turns around] Good!
-Delenn: I am Grey.
-I stand between the candle and the star.
-We are Grey.
-We stand between the darkness and the light.
 
-Lt.
-Corwin: Do we trust no-one then?
-Cmdr.
-Susan Ivanova: No, trust Ivanova, trust yourself, anybody else, shoot'em.
-Ta'Lon: Congratulations citizen G'Kar.
-You are now a religious icon.
-Susan Ivanova: So the next time we find out where the Shadows plan to strike, we can mine the area, and as soon as they come out of hyperspace...
-Citizen G'Kar: Then, as you so concisely say, Boom!
+Dear Editor,
 
-## Section Title
+We would like to submit our manuscript entitled “Not just for programmers: A friendly guide on the versatility of GitHub for accelerating collaborative research in Ecology and Evolution” for consideration to be published in OUR_CHOICE_OF_JOURNAL.
+Our study provides researchers in ecology and evolution with a critical review on thirteen practical ways they can use Github -- an online, cloud-based service for cooperative and documented code development -- to make their research more collaborative, transparent, and reproducible.
 
-G'Kar: It is said that the future is always born in pain.
-The history of war is the history of pain.
-If we are wise, what is born of that pain matures into the promise of a better world, because we learn that we can no longer afford the mistakes of the past.
-Dr.
-Stephen Franklin: Doesn't anyone listen to one damn word I say?
-Captain John Sheridan: No surrender, no retreat.
-[Opening narration, season 4] Lennier: It was the year of fire, Zack Allan: The year of destruction, Citizen G'Kar: The year we took back what was ours.
-Lyta Alexander: It was the year of rebirth, Ambassador Vir Cotto: The year of great sadness, Marcus Cole: The year of pain, Delenn: And a year of joy.
-Ambassador Londo Mollari: It was a new age.
-Dr.
-Stephen Franklin: It was the end of history.
-Susan Ivanova: It was the year everything changed.
-Michael Garibaldi: The year is 2261.
-Captain John Sheridan: The place, Babylon 5.
-Sinclair: They say God works in mysterious ways.
-Michael Garibaldi: Maybe so, but He's a con-man compared to the Vorlon.
+Scientific advancement fundamentally requires researchers to adopt reproducible, collaborative and transparent practices.
 
-## Figures
+Most scientists, including ecologists and evolutionary biologists, have become critically dependent on computational tools in their research.
+This code-dependent workflow imposes steep requirements towards an efficient, well-documented process in the publication and collaboration of maintainable scientific code.
+Albeit, many researchers lack exposure to adequate software development practices and thus are required to dedicate valuable time and effort to self-teach the use of research-facilitating tools, and thus may find practical barriers when applying adequate standards to maintain their scientific code.
+In our study, we review and discuss one of the most used web-based platforms for computational version control and collaboration, GitHub, and provide researchers in ecology and evolutionary biology with practical workflows aimed at facilitating their scientific code and management process.
 
-```{r, fig.show='hold'}
-ggplot(mtcars, aes(wt, mpg)) +
-  geom_point() +
-  labs(title="mtcars again, it seems") +
-  theme_ipsum_rc(grid="XY")
+*Include another paragraph describing the implications of the study.*
 
-```
+The enclosed manuscript has not been previously published and is not under consideration for publication in another journal or book. 
+All authors have contributed and reviewed the current version of the manuscript and agreed to its submission to OUR_CHOICE_OF_JOURNAL.
 
-### Level 3
+We appreciate your time and consideration of our manuscript for publication in your journal.
 
-Commander Jeffrey David Sinclair: Everyone lies, Michael.
-The innocent lie because they don't want to be blamed for something they didn't do and the guilty lie because they don't have any other choice.
-Lt.
-Corwin: Do we trust no-one then?
-Cmdr.
-Susan Ivanova: No, trust Ivanova, trust yourself, anybody else, shoot'em.
-Susan Ivanova: If I live through this without completely losing my mind, it will be a miracle of Biblical proportions.
+Sincerely,
 
-Lt.
-Corwin: [aside] Well, there goes my faith in the Almighty.
-[Opening narration, season 3] Susan Ivanova: The Babylon Project was our last, best hope for peace.
-It failed.
-But in the year of the Shadow War, it became something greater: our last, best hope for victory.
-The year is 2260.
-The place - Babylon 5.
-Alfred Bester: Being a telepath means you're special and rare and valuable.
-
-#### Level 4
-
-Delenn: We are star stuff. We are the universe made manifest trying to figure itself out.
-
-Captain John Sheridan: If more of our so-called leaders would walk the same streets as the people who voted them in, live in the same buildings, eat the same food instead of hiding behind glass and steel and bodyguards, maybe we'd get better leadership and a little more concern for the future.
-
-Captain John Sheridan: If more of our so-called leaders would walk the same streets as the people who voted them in, live in the same buildings, eat the same food instead of hiding behind glass and steel and bodyguards, maybe we'd get better leadership and a little more concern for the future.
-Kosh Naranek: Understanding is a three-edged sword.
-Alfred Bester: Much as it might offend their sense of perspective, not everything is about Babylon 5.
-
-```{r bib, include=FALSE}
-# KEEP THIS AT THE END OF THE DOCUMENT TO GENERATE A LOCAL bib FILE FOR PKGS USED
-knitr::write_bib(sub("^package:", "", grep("package", search(), value=TRUE)), file='skeleton.bib')
-```
+OUR_CORRESPONDING AUTHOR, on behalf of all co-authors

### 2022-04-19 editorial-communication/cover-letter-submission.Rmd
Removing chunk to solve unmet dependencies

@@
 ```
-
-```{r ipsum_setup, message=FALSE, warning=FALSE, cache=FALSE, echo=FALSE}
-library(hrbrthemes)
-library(tidyverse)
-
-update_geom_font_defaults(font_rc)
-```
-
 Dear Editor,

### 2022-04-19 editorial-communication/cover-letter-submission.Rmd
Update cover-letter-submission.Rmd

@@
 
-We would like to submit our manuscript entitled “Not just for programmers: A friendly guide on the versatility of GitHub for accelerating collaborative research in Ecology and Evolution” for consideration to be published in OUR_CHOICE_OF_JOURNAL.
-Our study provides researchers in ecology and evolution with a critical review on thirteen practical ways they can use Github -- an online, cloud-based service for cooperative and documented code development -- to make their research more collaborative, transparent, and reproducible.
+We would like to submit our manuscript entitled “Not just for programmers: A friendly guide on the benefits of GitHub for accelerating collaborative research in Ecology and Evolution” for consideration to be published in *Nature Ecology & Evolution*.
+Our study provides researchers in ecology and evolution (E&E) with a critical review of thirteen practical ways they can use Github -- an online, cloud-based service for cooperative and documented code development -- to make their research more collaborative, transparent, and reproducible.
 
@@
 Albeit, many researchers lack exposure to adequate software development practices and thus are required to dedicate valuable time and effort to self-teach the use of research-facilitating tools, and thus may find practical barriers when applying adequate standards to maintain their scientific code.
+The adoption of GitHub in E&E workflows is not widespread in part because there have been only a few disparate attempts at creating domain-specific information and guidelines.
 In our study, we review and discuss one of the most used web-based platforms for computational version control and collaboration, GitHub, and provide researchers in ecology and evolutionary biology with practical workflows aimed at facilitating their scientific code and management process.
 
-*Include another paragraph describing the implications of the study.*
+Our manuscript is the most accessible and practical guide to using GitHub in E&E research to date. 
+This is because we represent a wide diversity of E&E domains, yet have all found GitHub essential to making our research more collaborative and transparent. 
+Our manuscript is important for the *Nature Ecology & Evolution* readership because EEB researchers will continue to migrate their workflows to GitHub and need resources to guide their journey toward more open and collaborative EEB science.
 
 The enclosed manuscript has not been previously published and is not under consideration for publication in another journal or book. 
-All authors have contributed and reviewed the current version of the manuscript and agreed to its submission to OUR_CHOICE_OF_JOURNAL.
+All authors have contributed and reviewed the current version of the manuscript and agreed to its submission to *Nature Ecology & Evolution*.
 
@@
 
-OUR_CORRESPONDING AUTHOR, on behalf of all co-authors
+Rob Crystal-Ornelas PhD, on behalf of all co-authors
+
+---
+We would like to suggest the following potential reviewers for our manuscript:
+- 
+-

### 2022-04-21 editorial-communication/cover-letter-submission.Rmd
Deploying to gh-pages from @ SORTEE-Github-Hackathon/manuscript@cf98dfc0a509af73955fdbcf6b1a324c394838cf 🚀

@@
 We would like to submit our manuscript entitled “Not just for programmers: A friendly guide on the benefits of GitHub for accelerating collaborative research in Ecology and Evolution” for consideration to be published in *Nature Ecology & Evolution*.
-Our study provides researchers in ecology and evolution (E&E) with a critical review of thirteen practical ways they can use Github -- an online, cloud-based service for cooperative and documented code development -- to make their research more collaborative, transparent, and reproducible.
+Our study provides ecology and evolutionary biology (EEB) researchers with a critical review of thirteen practical ways they can use Github -- an online, cloud-based service for cooperative and documented code development -- to make their research more collaborative, transparent, and reproducible.
 
-Scientific advancement fundamentally requires researchers to adopt reproducible, collaborative and transparent practices.
+Most scientists, including researchers in EEB, have become critically dependent on computational tools in their research.
+This code-dependent workflow imposes steep requirements towards an efficient, well-documented process in the publication and collaboration of maintainable scientific code.
+Albeit, many researchers lack exposure to adequate software development practices and thus are required to dedicate valuable time and effort to learning how to use research-facilitating tools. 
+Formal academic courses on these types of tools in EEB are often unavailable and researchers are left to learn through informal blogs, videos, and other online forums. 
+This may present a plethora of practical barriers to applying adequate standards to maintaining scientific code.
 
-Most scientists, including ecologists and evolutionary biologists, have become critically dependent on computational tools in their research.
-This code-dependent workflow imposes steep requirements towards an efficient, well-documented process in the publication and collaboration of maintainable scientific code.
-Albeit, many researchers lack exposure to adequate software development practices and thus are required to dedicate valuable time and effort to self-teach the use of research-facilitating tools, and thus may find practical barriers when applying adequate standards to maintain their scientific code.
-The adoption of GitHub in E&E workflows is not widespread in part because there have been only a few disparate attempts at creating domain-specific information and guidelines.
-In our study, we review and discuss one of the most used web-based platforms for computational version control and collaboration, GitHub, and provide researchers in ecology and evolutionary biology with practical workflows aimed at facilitating their scientific code and management process.
+The adoption of GitHub in EEB workflows is not widespread in part because there have been only a few disparate attempts at creating domain-specific information and guidelines.
+In our study, we review and discuss one of the most used web-based platforms for computational version control and collaboration, GitHub, and provide researchers in EEB with practical workflows aimed at facilitating their scientific code and management process.
 
-Our manuscript is the most accessible and practical guide to using GitHub in E&E research to date. 
-This is because we represent a wide diversity of E&E domains, yet have all found GitHub essential to making our research more collaborative and transparent. 
-Our manuscript is important for the *Nature Ecology & Evolution* readership because EEB researchers will continue to migrate their workflows to GitHub and need resources to guide their journey toward more open and collaborative EEB science.
+Our manuscript is the most accessible and practical guide to using GitHub in EEB research to date. 
+We build upon some existing resources, which are mainly targeted at other disciplines, and our own experiences (from across many EEB subdisciplines) in writing and sharing code openly, to highlight steps EEB researchers can take to improve their research practices in a reproducible, collaborative, and transparent way.
+Our manuscript is important for the *Nature Ecology & Evolution* readership because EEB researchers will continue to migrate their workflows to GitHub and need resources to guide their journey toward more open and collaborative science.
 
-The enclosed manuscript has not been previously published and is not under consideration for publication in another journal or book. 
+The enclosed manuscript is available as a preprint on the NAME OF SERVER AND CITATION, but is not published or in review elsewhere.
 All authors have contributed and reviewed the current version of the manuscript and agreed to its submission to *Nature Ecology & Evolution*.

### 2022-05-26 editorial-communication/cover-letter-submission.Rmd
Deploying to gh-pages from @ SORTEE-Github-Hackathon/manuscript@af9c0d0c919842e389aeaef2792d37ab167fccb1 🚀

@@
 The adoption of GitHub in EEB workflows is not widespread in part because there have been only a few disparate attempts at creating domain-specific information and guidelines.
-In our study, we review and discuss one of the most used web-based platforms for computational version control and collaboration, GitHub, and provide researchers in EEB with practical workflows aimed at facilitating their scientific code and management process.
+In our study, we review and discuss one of the most used web-based platforms for computational version control and collaboration, GitHub, and provide researchers in EEB with comprehensive and practical workflows aimed at facilitating their scientific code and management process.
+<!-- Added adjective 'comprehensive' because I think it adds to showing that this mauscript improves upon previous 'disparate' attempts at such resources -->
 
@@
 We build upon some existing resources, which are mainly targeted at other disciplines, and our own experiences (from across many EEB subdisciplines) in writing and sharing code openly, to highlight steps EEB researchers can take to improve their research practices in a reproducible, collaborative, and transparent way.
-Our manuscript is important for the *Nature Ecology & Evolution* readership because EEB researchers will continue to migrate their workflows to GitHub and need resources to guide their journey toward more open and collaborative science.
+Our manuscript is important for the *Nature Ecology & Evolution* readership because it will give EEB researchers key resources and workflows to guide them through migrating workflows to GitHub and supporting more open and collaborative science.
+<!-- Reworded for emphasis -->
 

### 2022-06-01 R/scatterblob.Rmd
updating github use titles and cognitive loads

@@
 
+Data was generated using Google docs, then manually saved as csv file "scatterblob_data_raw.csv" in the `data` folder.
+
 Data for this figure was generated on a collaborative [google spread sheet](https://docs.google.com/spreadsheets/d/1Ls0DofQWSZQsqtP4OLFj326sGfWsklrI2tA1GNUTR6g/edit#gid=0).
+
+[Data, version 2](https://docs.google.com/spreadsheets/d/1zCRgctjfjE2xZN9MkqfFh222K6bvVvA3gT0UdkL_CS8/edit#gid=0).
+
 Cognitive load [was measured in a different file](https://docs.google.com/spreadsheets/d/1OLBR3M0uV3PMSazWUYHgPeX28wllAgS4PIlJXaNu-2o/edit#gid=0).
+
+[Cognitive load, version 2](https://docs.google.com/spreadsheets/d/1YipCCdg5Z8w-IQO67rFfMBSTpLjO-_7HiW44gqzTXPM/edit#gid=0).
 
@@
 scatterblob_data$x2 <- scatterblob_data$`Max degree of collaborativeness X2`
-scatterblob_data$y_real <- scatterblob_data$`Cognitive load - real`
+scatterblob_data$y_real <- scatterblob_data$`Cognitive load - real - non-overlapping`
 scatterblob_data$y_seq <- scatterblob_data$`Cognitive load - sequential`
-
-my_data <- scatterblob_data[,c("Ways to use GitHub","y_seq", "y_real", "x1", "x2")]
+my_data <- scatterblob_data[1:12,c("Ways to use GitHub","y_seq", "y_real", "x1", "x2")]
  my_data
@@
 ```{r}
-my_colors <- viridis::turbo(n = nrow(scatterblob_data), alpha = 0.9)
+my_colors <- viridis::turbo(n = nrow(my_data), alpha = 0.9)
 ###############################################################
@@
       height = 6,
-      bg = "transparent")  
+      bg = "white")  
 }
@@
       res = 100,
-      bg = "transparent")  
+      bg = "white")  
 }
@@
 ###############################################################
-for (i in seq(nrow(scatterblob_data))) {
+for (i in seq(nrow(my_data))) {
   X0 <- my_data$x1[i]

### 2022-06-01 R/scatterblob.Rmd
playing with colors

@@
 my_colors <- viridis::turbo(n = nrow(my_data), alpha = 0.9)
+
+some_colors <- viridis::turbo(n = 30, alpha = 0.9)
+
+plot(1:30, 1:30, col = some_colors, pch = 8)
+```
+
+```{r}
+my_colors <- some_colors[c(3:4,
+                           8,10,12,
+                           20,21,22,23,24,
+                           28,30)]
 ###############################################################
@@
 ```{r}
-my_colors <- viridis::turbo(n = nrow(my_data), alpha = 0.9)
+some_colors <- viridis::turbo(n = 100, alpha = 0.9)
+
+plot(1:100, 1:100, col = some_colors, pch = 8)
+```
+
+```{r}
+my_colors <- some_colors[c(15,20,
+                           26,28,30,
+                           66,68,70,72,74,
+                           85,95)]
 ###############################################################
@@
 ###############################################################
-plot_format <- "pdf"
+#plot_format <- "pdf"
 # plot_format <- "png"
-# plot_format <- "svg"
+ plot_format <- "svg"
 
@@
 plot(x = c(0.5, 5.5),
-     y = c(0.5, nrow(my_data)),
+     y = c(0.4, 12.5),
      xlab = "",
@@
 text(x = 0.2,
-     y = c(0, 2, 4, 6, 8, 10, 12, 14, 15.5), 
+     y = c(0, 1.5, 3, 4.5, 6, 7.5, 9, 10.5, 12 ), 
      cex = 0.7,

### 2022-06-01 R/scatterblob.Rmd
fixing x and y axis labels

@@
                 "Intermediate",
-                "Pre- \nAdvanced",
+                "Pre \nAdvanced",
                 "Very \nAdvanced"))
@@
                 "Low\nintermediate",
-                "Pre-\nintermediate",
+                "Pre\nintermediate",
                 "Intermediate", 
                 "Upper\nintermediate",
-                "Pre-\nAdvanced",
+                "Pre\nAdvanced",
                 "Advanced",

### 2022-06-01 R/scatterblob.Rmd
pngs of color schemes

--- 2022-06-01 R/scatterblob.Rmd
@@
 my_colors <- viridis::turbo(n = nrow(my_data), alpha = 0.9)
+
+some_colors1 <- viridis::turbo(n = 30, alpha = 0.9)
+
+some_colors2 <- viridis::magma(n = 30, alpha = 0.9)
+
+plot(1:30, 1:30, col = some_colors2, pch = 8)
+```
+
+```{r}
+my_colors <- some_colors1[c(3:4,
+                           8,10,12,
+                           20,21,22,23,24,
+                           28,30)]
 ###############################################################
@@
 ###############################################################
-plot_format <- "pdf"
-# plot_format <- "svg"
-# plot_format <- "png"
+#plot_format <- "pdf"
+plot_format <- "svg"
+#plot_format <- "png"
 
@@
       units = "in",
-      res = 100,
+      res = 300,
       bg = "white")  
@@
                 "Other \nlabs",
-                "The \ncommunity",
-                "The \npublic"))
+                "EEB \ncommunity",
+                "All \nusers"))
 text(x = c(1, 3, 5),
@@
 ```{r}
-my_colors <- viridis::turbo(n = nrow(my_data), alpha = 0.9)
+some_colors3 <- viridis::turbo(n = 100, alpha = 0.9)
+some_colors4 <- wesanderson::wes_palette("Zissou1", 75, type = "continuous")
+some_colors5 <- wesanderson::wes_palette("Darjeeling1", 75, type = "continuous")
+some_colors6 <- wesanderson::wes_palette("Darjeeling2", 75, type = "continuous")
+some_colors7 <- wesanderson::wes_palette("Royal2", 75, type = "continuous")
+plot(1:75, 1:75, col = some_colors7, pch = 8)
+```
+
+```{r}
+my_colors <- some_colors3[c(5,15,
+                           26,28,30,
+                           68,72,76,80,84,
+                           94,100)]
+plot_name <- "scatterblob_1-viridis-turbo"
+#my_colors <- some_colors4[round(my_data$y_real*10)-20]
+#plot_name <- "scatterblob_1-zissou1"
+# my_colors <- some_colors5[round(my_data$y_real*10)-20]
+# plot_name <- "scatterblob_1-darjeeling1"
+# my_colors <- some_colors6[round(my_data$y_real*10)-20]
+# plot_name <- "scatterblob_1-darjeeling2"
+# my_colors <- some_colors7[round(my_data$y_real*10)-20]
+# plot_name <- "scatterblob_1-royal2"
 ###############################################################
@@
 if (plot_format == "pdf") {
-  pdf(file = here(outpath, "scatterblob_1.pdf"),
+  pdf(file = here(outpath, paste0(plot_name, ".pdf")),
       width = 8.25,
       height = 6,
-      bg = "transparent")  
+      bg = "white")  
 }
 if (plot_format == "svg") {
-  svg(filename = here(outpath, "scatterblob_1.svg"),
+  svg(filename = here(outpath, paste0(plot_name, ".svg")),
       width = 8.25,
       height = 6,
-      bg = "transparent")  
+      bg = "white")  
 }
 if (plot_format == "png") {
-  png(file = here(outpath, "scatterblob_1.png"),
+  png(file = here(outpath, paste0(plot_name, ".png")),
       width = 8.25,
@@
       units = "in",
-      res = 100,
-      bg = "transparent")  
+      res = 300,
+      bg = "white")  
 }
@@
                 "Other \nlabs", 
-                "The \ncommunity", 
-                "The \npublic"))
+                "EEB \ncommunity", 
+                "All \nusers"))
 text(x = c(1, 3, 5),

### 2022-06-01 editorial-communication/cover-letter-submission.Rmd
Deploying to gh-pages from @ SORTEE-Github-Hackathon/manuscript@7e78aea37b37b7249327e51fbb371a699f1ece2c 🚀

@@
 We would like to submit our manuscript entitled “Not just for programmers: A friendly guide on the benefits of GitHub for accelerating collaborative research in Ecology and Evolution” for consideration to be published in *Nature Ecology & Evolution*.
-Our study provides ecology and evolutionary biology (EEB) researchers with a critical review of thirteen practical ways they can use Github -- an online, cloud-based service for cooperative and documented code development -- to make their research more collaborative, transparent, and reproducible.
+Our study provides ecology and evolutionary biology (EEB) researchers with a critical review of twelve practical ways they can use Github -- an online, cloud-based service for cooperative and documented code development -- to make their research more collaborative, transparent, and reproducible.
 
@@
 In our study, we review and discuss one of the most used web-based platforms for computational version control and collaboration, GitHub, and provide researchers in EEB with comprehensive and practical workflows aimed at facilitating their scientific code and management process.
-<!-- Added adjective 'comprehensive' because I think it adds to showing that this mauscript improves upon previous 'disparate' attempts at such resources -->
 
@@
 Our manuscript is important for the *Nature Ecology & Evolution* readership because it will give EEB researchers key resources and workflows to guide them through migrating workflows to GitHub and supporting more open and collaborative science.
-<!-- Reworded for emphasis -->
 

### 2022-06-04 editorial-communication/cover-letter-submission.Rmd
Removing acronyms from the cover letter and making a few changes.

--- 2022-04-21 editorial-communication/cover-letter-submission.Rmd
@@
 ```
+
 Dear Editor,
@@
 We would like to submit our manuscript entitled “Not just for programmers: A friendly guide on the benefits of GitHub for accelerating collaborative research in Ecology and Evolution” for consideration to be published in *Nature Ecology & Evolution*.
-Our study provides ecology and evolutionary biology (EEB) researchers with a critical review of thirteen practical ways they can use Github -- an online, cloud-based service for cooperative and documented code development -- to make their research more collaborative, transparent, and reproducible.
+Our study provides researchers with a critical review of twelve practical ways they can use Github -- an online, cloud-based service for cooperative and documented code development -- to make their research more collaborative, transparent, and reproducible.
 
-Most scientists, including researchers in EEB, have become critically dependent on computational tools in their research.
+Most scientists, including researchers in ecology and evolutionary biology, have become critically dependent on computational tools in their research.
 This code-dependent workflow imposes steep requirements towards an efficient, well-documented process in the publication and collaboration of maintainable scientific code.
 Albeit, many researchers lack exposure to adequate software development practices and thus are required to dedicate valuable time and effort to learning how to use research-facilitating tools. 
-Formal academic courses on these types of tools in EEB are often unavailable and researchers are left to learn through informal blogs, videos, and other online forums. 
+Formal academic courses on these types of tools are often unavailable and researchers are left to learn through informal blogs, videos, and other online forums. 
 This may present a plethora of practical barriers to applying adequate standards to maintaining scientific code.
 
-The adoption of GitHub in EEB workflows is not widespread in part because there have been only a few disparate attempts at creating domain-specific information and guidelines.
-In our study, we review and discuss one of the most used web-based platforms for computational version control and collaboration, GitHub, and provide researchers in EEB with practical workflows aimed at facilitating their scientific code and management process.
+The adoption of GitHub in ecology and evolutionary biology workflows is not widespread in part because there have been only a few disparate attempts at creating domain-specific information and guidelines.
+In our study, we review and discuss one of the most used web-based platforms for computational version control and collaboration, GitHub, and provide researchers in ecology and evolution with comprehensive and practical workflows aimed at facilitating their scientific code and management process.
 
-Our manuscript is the most accessible and practical guide to using GitHub in EEB research to date. 
-We build upon some existing resources, which are mainly targeted at other disciplines, and our own experiences (from across many EEB subdisciplines) in writing and sharing code openly, to highlight steps EEB researchers can take to improve their research practices in a reproducible, collaborative, and transparent way.
-Our manuscript is important for the *Nature Ecology & Evolution* readership because EEB researchers will continue to migrate their workflows to GitHub and need resources to guide their journey toward more open and collaborative science.
+Our manuscript is the most accessible and practical guide to using GitHub in ecology and evolution research to date.
+We build upon our own experiences (as an international collaboration from authors across many ecology and evolution subdisciplines) and on existing resources mainly targeted at other disciplines, to highlight how researchers can use the readily available GitHub suite to make their research practices reproducible, collaborative, and transparent.
+Our manuscript is important for the *Nature Ecology & Evolution* readership because researchers in ecology and evolutionary biology can greatly benefit from our guide to migrate and incorporate GitHub workflows in their research and ultimately supporting a better open and collaborative science.
 
@@
 ---
+
 We would like to suggest the following potential reviewers for our manuscript:
@@
 - 
+-

### 2022-06-04 R/scatterblob.Rmd
Capitalize y-axis labels for consistency
e.g. `"Low\nintermediate"` -> `"Low\nIntermediate"`

@@
                 "Elementary", 
-                "Low\nintermediate",
-                "Pre\nintermediate",
+                "Low\nIntermediate",
+                "Pre\nIntermediate",
                 "Intermediate", 
-                "Upper\nintermediate",
+                "Upper\nIntermediate",
                 "Pre\nAdvanced",

### 2022-06-04 editorial-communication/cover-letter-submission.Rmd
Update cover-letter-submission.Rmd

@@
 We build upon our own experiences (as an international collaboration from authors across many ecology and evolution subdisciplines) and on existing resources mainly targeted at other disciplines, to highlight how researchers can use the readily available GitHub suite to make their research practices reproducible, collaborative, and transparent.
-Our manuscript is important for the *Nature Ecology & Evolution* readership because researchers in ecology and evolutionary biology can greatly benefit from our guide to migrate and incorporate GitHub workflows in their research and ultimately supporting a better open and collaborative science.
+Our manuscript is important for the *Nature Ecology & Evolution* readership because researchers in ecology and evolutionary biology can greatly benefit from our guide to migrate and incorporate GitHub workflows in their research practices ultimately towards an open and collaborative science.
 

### 2022-06-06 editorial-communication/cover-letter-submission.Rmd
Deploying to gh-pages from @ SORTEE-Github-Hackathon/manuscript@cbd4efaaa95b1488925ed715efcf0a82da9dbe82 🚀

@@
 title: Letter to the Editor
-author: "Not just for programmers: A friendly guide on the benefits of GitHub for accelerating collaborative research in Ecology and Evolution"
+author: "Not just for programmers: How GitHub can accelerate collaborative and reproducible research in ecology and evolution"
 date: "Last compiled on `r format(Sys.time(), '%d %B, %Y')`"
@@
 
-We would like to submit our manuscript entitled “Not just for programmers: A friendly guide on the benefits of GitHub for accelerating collaborative research in Ecology and Evolution” for consideration to be published in *Nature Ecology & Evolution*.
+We would like to submit our manuscript entitled “Not just for programmers: How GitHub can accelerate collaborative and reproducible research in ecology and evolution” for consideration to be published in *Nature Ecology & Evolution*.
 Our study provides researchers with a critical review of twelve practical ways they can use Github -- an online, cloud-based service for cooperative and documented code development -- to make their research more collaborative, transparent, and reproducible.

### 2022-06-06 R/roles_table.Rmd
move data
edit "repo" to "repository" in raw data

@@
 ```{r wrangle, include=FALSE}
-roles <- read_csv(here("R", "collaborator_roles.csv"))
+roles <- read_csv(here("data", "collaborator_roles.csv"))
 
@@
   pivot_wider(names_from = `GitHub Feature`, values_from = `Use Case`) %>% 
-  select(Role, `GitHub repo`, README, Issue, Discussion, `Pull Request`, Fork, `GitHub Pages`) %>% 
+  select(Role, `GitHub repository`, README, Issue, Discussion, `Pull Request`, Fork, `GitHub Pages`) %>% 
   mutate(across(everything(), ~replace_na(.x, "")))

### 2022-06-08 build/build.sh
Update build.sh

@@ -18,9 +18,9 @@ DOCKER_RUNNING="$(docker info &> /dev/null && echo "true" || (true && echo "fals
 # Set option defaults
 CI="${CI:-false}"
 BUILD_PDF="${BUILD_PDF:-true}"
-BUILD_DOCX="${BUILD_DOCX:-false}"
-BUILD_LATEX="${BUILD_LATEX:-false}"
-SPELLCHECK="${SPELLCHECK:-false}"
+BUILD_DOCX="${BUILD_DOCX:-true}"
+BUILD_LATEX="${BUILD_LATEX:-true}"
+SPELLCHECK="${SPELLCHECK:-true}"
 MANUBOT_USE_DOCKER="${MANUBOT_USE_DOCKER:-$DOCKER_RUNNING}"
 # Pandoc's configuration is specified via files of option defaults
 # located in the $PANDOC_DATA_DIR/defaults directory.

### 2022-06-08 manuscript.tex
Update build.sh [ci skip]
This build is based on
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/402617f9e4b0caf2a3e126b79bf17059d3cfef8c.

This commit was created by the following CI build and job:
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/402617f9e4b0caf2a3e126b79bf17059d3cfef8c/checks
https://github.com/SORTEE-Github-Hackathon/manuscript/actions/runs/2463442692

This manuscript
(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/402617f9e4b0caf2a3e126b79bf17059d3cfef8c/}{permalink})
was automatically generated
from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/402617f9e4b0caf2a3e126b79bf17059d3cfef8c}{SORTEE-Github-Hackathon/manuscript@402617f}
on June 8, 2022.

\hypertarget{authors}{%
\subsection{Authors}\label{authors}}

\begin{itemize}
\item
  \textbf{Robert Crystal-Ornelas}
  \includegraphics[width=0.16667in,height=0.16667in]{images/orcid.svg}
  \href{https://orcid.org/0000-0002-6339-1139}{0000-0002-6339-1139}
  · \includegraphics[width=0.16667in,height=0.16667in]{images/github.svg}
  \href{https://github.com/robcrystalornelas}{robcrystalornelas}
  · \includegraphics[width=0.16667in,height=0.16667in]{images/twitter.svg}
  \href{https://twitter.com/rob_c_ornelas}{rob\_c\_ornelas}
  Earth and Environmental Sciences Area, Lawrence Berkeley National Laboratory, Berkeley, CA 94720, USA
\item
  \textbf{Brandon P.M. Edwards}
  \includegraphics[width=0.16667in,height=0.16667in]{images/orcid.svg}
  \href{https://orcid.org/0000-0003-0865-3076}{0000-0003-0865-3076}
  · \includegraphics[width=0.16667in,height=0.16667in]{images/github.svg}
  \href{https://github.com/BrandonEdwards}{BrandonEdwards}
  Department of Biology, Carleton University, Ottawa, ON K1S 5B6, Canada
\item
  \textbf{Katherine Hébert}
  \includegraphics[width=0.16667in,height=0.16667in]{images/orcid.svg}
  \href{https://orcid.org/0000-0001-7866-6775}{0000-0001-7866-6775}
  · \includegraphics[width=0.16667in,height=0.16667in]{images/github.svg}
  \href{https://github.com/katherinehebert}{katherinehebert}
  · \includegraphics[width=0.16667in,height=0.16667in]{images/twitter.svg}
  \href{https://twitter.com/hebert_kat}{hebert\_kat}
  Département de biologie, Université de Sherbrooke, Québec, Canada
\item
  \textbf{Friederike Hillemann}
  \includegraphics[width=0.16667in,height=0.16667in]{images/orcid.svg}
  \href{https://orcid.org/0000-0002-8992-0676}{0000-0002-8992-0676}
  · \includegraphics[width=0.16667in,height=0.16667in]{images/github.svg}
  \href{https://github.com/fhillemann}{fhillemann}
  Department of Human Behavior, Ecology and Culture, Max Planck Institute for Evolutionary Anthropology, Leipzig, Germany
\item
  \textbf{Emma J. Hudgins}
  \includegraphics[width=0.16667in,height=0.16667in]{images/orcid.svg}
  \href{https://orcid.org/0000-0002-8402-5111}{0000-0002-8402-5111}
  · \includegraphics[width=0.16667in,height=0.16667in]{images/github.svg}
  \href{https://github.com/emmajhudgins}{emmajhudgins}
  Department of Biology, Carleton University, Ottawa, ON K1S 5B6, Canada
\item
  \textbf{Luna L. Sánchez Reyes}
  \includegraphics[width=0.16667in,height=0.16667in]{images/orcid.svg}
  \href{https://orcid.org/0000-0001-7668-2528}{0000-0001-7668-2528}
  · \includegraphics[width=0.16667in,height=0.16667in]{images/github.svg}
  \href{https://github.com/LunaSare}{LunaSare}
  · \includegraphics[width=0.16667in,height=0.16667in]{images/twitter.svg}
  \href{https://twitter.com/LunaSare}{LunaSare}
  School of Natural Sciences, University of California, Merced, USA
\item
  \textbf{Eric R. Scott}
  \includegraphics[width=0.16667in,height=0.16667in]{images/orcid.svg}
  \href{https://orcid.org/0000-0002-7430-7879}{0000-0002-7430-7879}
  · \includegraphics[width=0.16667in,height=0.16667in]{images/github.svg}
  \href{https://github.com/Aariq}{Aariq}
  Department of Wildlife Ecology and Conservation, University of Florida, Gainesville, FL, USA
\item
  \textbf{Matthew J. Grainger}
  \includegraphics[width=0.16667in,height=0.16667in]{images/orcid.svg}
  \href{https://orcid.org/0000-0001-8426-6495}{0000-0001-8426-6495}
  · \includegraphics[width=0.16667in,height=0.16667in]{images/github.svg}
  \href{https://github.com/DrMattG}{DrMattG}
  · \includegraphics[width=0.16667in,height=0.16667in]{images/twitter.svg}
  \href{https://twitter.com/Ed_pheasant}{Ed\_pheasant}
  Terrestrial Biodiversity, Norwegian Institute for Nature Research - NINA, Postbox 5685 Torgarden, 7485 Trondheim, Norway
\item
  \textbf{Vivienne Foroughirad}
  \includegraphics[width=0.16667in,height=0.16667in]{images/orcid.svg}
  \href{https://orcid.org/0000-0002-8656-7440}{0000-0002-8656-7440}
  · \includegraphics[width=0.16667in,height=0.16667in]{images/github.svg}
  \href{https://github.com/vjf2}{vjf2}
  · \includegraphics[width=0.16667in,height=0.16667in]{images/twitter.svg}
  \href{https://twitter.com/vforoughirad}{vforoughirad}
  Department of Biology, Georgetown University, Washington, DC, USA
\item
  \textbf{Allison D. Binley}
  \includegraphics[width=0.16667in,height=0.16667in]{images/orcid.svg}
  \href{https://orcid.org/0000-0001-8790-9935}{0000-0001-8790-9935}
  · \includegraphics[width=0.16667in,height=0.16667in]{images/github.svg}
  \href{https://github.com/adbinley}{adbinley}
  · \includegraphics[width=0.16667in,height=0.16667in]{images/twitter.svg}
  \href{https://twitter.com/AllisonBinley}{AllisonBinley}
  Department of Biology, Carleton University, Ottawa, ON K1S 5B6, Canada
\item
  \textbf{Cole B. Brookson}
  \includegraphics[width=0.16667in,height=0.16667in]{images/orcid.svg}
  \href{https://orcid.org/0000-0003-1237-4096}{0000-0003-1237-4096}
  · \includegraphics[width=0.16667in,height=0.16667in]{images/github.svg}
  \href{https://github.com/colebrookson}{colebrookson}
  Department of Biological Sciences, University of Alberta, Edmonton, AB, Canada
\item
  \textbf{Kaitlyn M. Gaynor}
  \includegraphics[width=0.16667in,height=0.16667in]{images/orcid.svg}
  \href{https://orcid.org/0000-0002-5747-0543}{0000-0002-5747-0543}
  · \includegraphics[width=0.16667in,height=0.16667in]{images/github.svg}
  \href{https://github.com/kaitlyngaynor}{kaitlyngaynor}
  · \includegraphics[width=0.16667in,height=0.16667in]{images/twitter.svg}
  \href{https://twitter.com/kaitlyngaynor}{kaitlyngaynor}
  Departments of Zoology and Botany, University of British Columbia, Vancouver, BC, Canada; National Center for Ecological Analysis and Synthesis, Santa Barbara, CA 93101, USA
\item
  \textbf{Saeed Shafiei Sabet}
  \includegraphics[width=0.16667in,height=0.16667in]{images/orcid.svg}
  \href{https://orcid.org/0000-0001-5919-2527}{0000-0001-5919-2527}
  · \includegraphics[width=0.16667in,height=0.16667in]{images/github.svg}
  \href{https://github.com/shafieisabets}{shafieisabets}
  · \includegraphics[width=0.16667in,height=0.16667in]{images/twitter.svg}
  \href{https://twitter.com/SaeedSHSABET}{SaeedSHSABET}
  Fisheries Department, Faculty of Natural Resources, University of Guilan, Sowmeh Sara, Iran
\item
  \textbf{Ali Güncan}
  \includegraphics[width=0.16667in,height=0.16667in]{images/orcid.svg}
  \href{https://orcid.org/0000-0003-1765-648X}{0000-0003-1765-648X}
  · \includegraphics[width=0.16667in,height=0.16667in]{images/github.svg}
  \href{https://github.com/Aguncan}{Aguncan}
  · \includegraphics[width=0.16667in,height=0.16667in]{images/twitter.svg}
  \href{https://twitter.com/aliguncan}{aliguncan}
  Department of Plant Protection, Faculty of Agriculture, Ordu University, 52200, Ordu, Turkey
\item
  \textbf{Friederike Hillemann}
  \includegraphics[width=0.16667in,height=0.16667in]{images/orcid.svg}
  \href{https://orcid.org/0000-0002-8992-0676}{0000-0002-8992-0676}
  · \includegraphics[width=0.16667in,height=0.16667in]{images/github.svg}
  \href{https://github.com/fhillemann}{fhillemann}
  Department of Human Behavior, Ecology and Culture, Max Planck Institute for Evolutionary Anthropology, Leipzig, Germany
\item
  \textbf{Helen Weierbach}
  \includegraphics[width=0.16667in,height=0.16667in]{images/orcid.svg}
  \href{https://orcid.org/0000-0001-6348-9120}{0000-0001-6348-9120}
  · \includegraphics[width=0.16667in,height=0.16667in]{images/github.svg}
  \href{https://github.com/helenweierbach}{helenweierbach}
  · \includegraphics[width=0.16667in,height=0.16667in]{images/twitter.svg}
  \href{https://twitter.com/HWeierbach}{HWeierbach}
  Earth and Environmental Sciences Area, Lawrence Berkeley National Laboratory, Berkeley, CA 94720, USA
\item
  \textbf{Dylan G. E. Gomes}
  \includegraphics[width=0.16667in,height=0.16667in]{images/orcid.svg}
  \href{https://orcid.org/0000-0002-2642-3728}{0000-0002-2642-3728}
  · \includegraphics[width=0.16667in,height=0.16667in]{images/github.svg}
  \href{https://github.com/dylangomes}{dylangomes}
  (Current) National Academy of Sciences NRC Research Associateship Program, Northwest Fisheries Science Center, National Marine Fisheries Service, National Oceanic and Atmospheric Administration, Seattle, WA, USA 98112; (Former) Cooperative Institute for Marine Resources Studies, Hatfield Marine Science Center, Oregon State University, Newport, OR, United States
\item
  \textbf{Pedro Henrique Pereira Braga}
  \includegraphics[width=0.16667in,height=0.16667in]{images/orcid.svg}
  \href{https://orcid.org/0000-0002-1308-1562}{0000-0002-1308-1562}
  · \includegraphics[width=0.16667in,height=0.16667in]{images/github.svg}
  \href{https://github.com/pedrohbraga}{pedrohbraga}
  · \includegraphics[width=0.16667in,height=0.16667in]{images/twitter.svg}
  \href{https://twitter.com/pedrohp_braga}{pedrohp\_braga}
  Department of Biology, Concordia University, 7141 Sherbrooke Street West, Montreal, QC H4B 1R6, Canada
\end{itemize}

\hypertarget{abstract}{%
\subsection{Abstract}\label{abstract}}

Researchers in ecology and evolutionary biology are increasingly dependent on computational code to conduct research.
With the growing role of data science in research, the use of efficient methods to share, reproduce, and collaborate on code has become fundamental.
GitHub is an online, cloud-based service that can help researchers to track, organize, discuss, share, and collaborate on software and code.
Despite these benefits, the use of GitHub by EEB researchers is not widespread due to the lack of domain-specific information and guidelines.
To help EEB researchers adopt useful features from GitHub in their own workflows, we review twelve practical ways to use the platform.
We outline features ranging from low to high technical difficulty: storing code, managing projects, coding collaboratively, conducting peer review, and writing a manuscript.
Given that members of a research team may have different technical skills and responsibilities, we describe how the optimal use of GitHub features may vary among members of a research collaboration.
As more ecologists and evolutionary biologists establish their workflows using GitHub, the field can continue to push the boundaries of collaborative, transparent, and open research.

\hypertarget{introduction}{%
\subsection{Introduction}\label{introduction}}

Most scientists, including ecologists and evolutionary biologists, are increasingly dependent on computational tools in their research {[}\protect\hyperlink{ref-fJWFe93e}{1}{]}.
Researchers write and use code as part of their scientific workflow to perform a wide-variety of tasks ranging from data management, data analysis, and study replication, to the application and the development of tools for hypothesis testing.
To maintain code for scientific collaboration requires an efficient and well-documented work-flow {[}\protect\hyperlink{ref-1Kqna6l2}{2}{]}.
To facilitate this process, scientists have been increasingly adopting tools from information and systems technology, such as cloud-based services for documentation and version control (\emph{e.g.}, from the Google Suite, with Docs, Sheets, and Drive; the Microsoft Suite, with Word, Excel, and OneDrive; and GitHub; {[}\protect\hyperlink{ref-10ghgV3S8}{3}{]}).
However, most researchers lack exposure to adequate software development practices and are required to dedicate valuable time and effort to self-teach the use of research-facilitating tools, and thus may be limited in their ability to adhere to adequate standards of scientific code quality and maintenance {[}\protect\hyperlink{ref-fJWFe93e}{1},\protect\hyperlink{ref-10SpoByIw}{4},\protect\hyperlink{ref-O6UbstGG}{5}{]}.
Here, we review and discuss one of the most used web-based platforms for computational version control and collaboration, GitHub, and provide researchers in ecology and evolutionary biology (EEB) with practical workflows aimed at facilitating their scientific code and management process.

With over 73 million registered users, as of 2022, GitHub is the most widely-used web platform for collaborating on computer code {[}\protect\hyperlink{ref-nwCtHDCn}{6}{]}.
GitHub provides a simplified but powerful web interface that allows users to participate in projects, contribute code, report and discuss software bugs, discover existing code and data, and publish new code.
Through version control, users have a detailed, chronological record of the files and directories stored in their repositories (see \protect\hyperlink{definitions}{Box 1}; {[}\protect\hyperlink{ref-RVetqmsg}{7}{]}).
This workflow provides a strong and clear advantage over receiving, processing and sending files back-and-forth (e.g.~via email), a process that can easily become challenging and time-consuming in projects extending in time and in the number of collaborators {[}\protect\hyperlink{ref-4ny1onB0}{8}{]}.
Through the combination of version control management and the network- and collaboration-based features, GitHub can broadly facilitate openly available source code alongside concomitant collaborative development {[}\protect\hyperlink{ref-kEX5dgzK}{9}{]}.

Git is the version control software system that enables all the collaborative tools available on GitHub.
Although the understanding of basic concepts of Git (such as commit, push, pull, checkout; see \protect\hyperlink{definitions}{Box 1}) is necessary, the GitHub web-based platform and its integrated development environments (such as the GitHub Desktop) allow users to perform most repository and data management operations without opening Git command-line sessions.
Still, GitHub users are encouraged to explore and improve their proficiency in Git when feeling comfortable, so they can feel confident in performing more flexible, complex operations (such as integrating changes from one branch into another branch with \texttt{git\ merge} and \texttt{git\ rebase}). Examples of extensive explanations on Git can be found in journal articles {[}\protect\hyperlink{ref-kEX5dgzK}{9},\protect\hyperlink{ref-PlcxShQU}{10}{]}, video tutorials {[}\protect\hyperlink{ref-NIS0JOW0}{11}{]}, and books {[}\protect\hyperlink{ref-13jOlVcpp}{12}{]}.

The expansive GitHub user-community and the numerous resources on how to use GitHub have boosted its growing popularity {[}\protect\hyperlink{ref-RVetqmsg}{7},\protect\hyperlink{ref-kEX5dgzK}{9},\protect\hyperlink{ref-13jOlVcpp}{12}/,\protect\hyperlink{ref-u5aEVE4B}{13}{]}.
Nevertheless, although multiple articles have encouraged researchers in EEB to adopt GitHub as part of their research process {[}\protect\hyperlink{ref-10ghgV3S8}{3},\protect\hyperlink{ref-3DKwn1sY}{14}{]}, its use is still not widespread.
First-time users without formal training in information technology may face steep learning curves because GitHub and its features have been centered on collaboration for software development in information systems {[}\protect\hyperlink{ref-139b0pSGc}{15}{]}.
Moreover, domain-specific perspectives and resources providing tractable examples and practical guidance for researchers in EEB on GitHub are scarce (but see https://ourcodingclub.github.io; https://www.openscapes.org).
A common adoption of GitHub for collaborating on a variety of research tasks can ultimately enable EEB researchers to spend less time on creating novel processes for collaboration and more time on their research {[}\protect\hyperlink{ref-ydrk01SR}{16}{]}.
More importantly, increasing the availability of data and code management standards -- of which GitHub is one increasingly important component -- make research more reproducible and collaborative {[}\protect\hyperlink{ref-13QX8XU3J}{17}{]}.

This paper is the result of an academic hackathon held during the 2021 conference for the Society for Open, Reliable, and Transparent Ecology and Evolutionary Biology (SORTEE, https://www.sortee.org).
We convened a group of around thirty researchers in EEB with varying levels of familiarity with using GitHub as part of their research projects to showcase and discuss how existing features can contribute to documentation and collaboration in EEB research.
During the hackathon, we identified the need for a formal discussion on how EEB researchers can benefit from GitHub and its features to make research more collaborative and transparent.
Here, we outline twelve practical ways that EEB researchers can use GitHub features for more collaborative, transparent, and reproducible science.
We also provide critical perspectives on features that could be improved and catered towards research development.

\hypertarget{definitions}{%
\subsubsection{Box 1}\label{definitions}}

\begin{tablenos:no-prefix-table-caption}

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\columnwidth - 0\tabcolsep) * \real{1.0000}}@{}}
\toprule
\begin{minipage}[b]{\linewidth}\raggedright
Glossary
\end{minipage} \\
\midrule
\endhead
\textbf{branch}: Development branches can be created at any point in time and work on each branch can continue independently.This is useful for testing out new ideas (both code and text) which may or may not eventually get integrated into the main branch of the project. Branches can also be used to isolate contributions of multiple contributors. Each person working on their own branch eliminates problems that arise when conflicting edits are \textbf{pushed} to the same remote branch. Changes in a development branch can be \textbf{merged} into the main branch via \textbf{pull requests}. Branches can only be made by those who are given access to the project \textbf{repository}. \\
\textbf{clone}: Cloning a \textbf{repository} is a way of making a local copy (i.e.~on your computer) of a GitHub \textbf{repository}. If you have access to \textbf{push} to a \textbf{repository}, this can be a first step to contributing to a project. \\
\textbf{commit}: Commits are snapshots of the development of a project. In Git, versions of files and directories are uniquely identified as ``commits'', allowing one to identify and track modifications line-by-line. Commits can include changes in multiple files and must include a brief commit message describing the changes made. A typical workflow is to make some related changes in files, make a commit (e.g.~``generate and include fig1 in results''), and after several commits \textbf{push} those commits to the remote (i.e., cloud-based) GitHub \textbf{repository}. \\
\textbf{fork}: A fork is a copy of a \textbf{repository} hosted on GitHub. If a repository is public, then anyone can make a fork. Even if they do not have access to \textbf{push} to the original repository, they can make a fork and edit it independently. Forks are linked to the original GitHub repository and ``upstream'' changes (those in the original repository) can be \textbf{merged} to keep the fork up to date with the original project. Changes made in the fork can be integrated into the original project via \textbf{pull requests}. \\
\textbf{merge}: Combining \textbf{commits} from two different branches together into one \textbf{branch} \\
\textbf{pull request}: A pull request is a request that the owner(s) of a GitHub repository integrate changes you've made on either a \textbf{branch} in the repository or in your own \textbf{fork}. When you initiate a pull request, you must provide a description of what changes are made. Some automated tests may be run and review may be required before integrating your changes into the main \textbf{branch}. \\
\textbf{push/pull}: When \textbf{commits} are made in a project locally, they must be synced with the remote GitHub repository by \textbf{pushing} them. Changes on a GitHub repository can then be \textbf{pulled} to keep your local version of the project up-to-date. \\
\textbf{repository}: Commonly shortened to ``repo'', a repository is a collection of files (\emph{e.g.}, a directory) tracked by Git. Repositories are managed by an owner and can be listed as ``public'' where the repository will be visible to all GitHub users or ``private'', where the repository is visible only to authorized users. \\
\textbf{release}: At any point a release can be made on GitHub to mark a significant milestone in the progression of a \textbf{repository}. While this GitHub feature is designed with releases of new versions of software in mind (\emph{e.g.}, v1.0.0), it can also be used to create a snapshot of a repository at significant stages like submission, revision, and acceptance of an associated manuscript. \\
\textbf{community}: A forum where GitHub users can ask for advice, offer solutions to questions, and share ideas (https://github.community/). \\
\bottomrule
\end{longtable}

\end{tablenos:no-prefix-table-caption}

\hypertarget{practical-ways-of-using-github-in-eeb}{%
\subsection{12 Practical ways of using GitHub in EEB}\label{practical-ways-of-using-github-in-eeb}}

\hypertarget{storing-a-research-compendium}{%
\subsubsection{Storing a research compendium}\label{storing-a-research-compendium}}

In EEB, a research compendium includes all computational materials related to research production, including data, code for analyses and protocols.
Having multiple copies of these files is important to ensure that research can continue should one copy of a file be accidentally modified or deleted.
Many researchers begin using GitHub as a means to backup their research compendium {[}\protect\hyperlink{ref-MwwMapRG}{18}{]} to a remote server (pull-commit-push, see \protect\hyperlink{definitions}{Box 1}).
The GitHub repository serves as a centralized backup and also allows users to synchronize files and work on any device with internet access.
Because GitHub is built on git, version control features are also available, allowing users to re-visit or even restore previous versions of the repository.
Storing a research compendium as a GitHub repository has additional benefits such as facilitating collaboration, integration with data and code archiving services, and contribution to open science, all discussed in sections below.

Unfortunately, GitHub repositories have file size limits, so they may not be appropriate for synchronizing large data files.
Commits (see \protect\hyperlink{definitions}{Box 1}{]}) greater than 50 MB receive a warning and commits larger than 100 MB are blocked ({[}\protect\hyperlink{ref-1Co6ZZjF1}{19}{]}).
Therefore, it is recommended that large datasets are stored only locally or using other cloud services.

\hypertarget{virtual-lab-notebook}{%
\subsubsection{Virtual lab notebook}\label{virtual-lab-notebook}}

Lab notebooks are the virtual or physical notebooks used to help researchers at any career stage keep track of their research methods or laboratory policies {[}\protect\hyperlink{ref-wwHxTOtm}{20}{]}.
Digital lab notebooks stored in the cloud provide clear benefits given the ease with which documents can be shared with new employees and updated as policy changes or experimental methods are modified {[}\protect\hyperlink{ref-10V7x4H4l}{21}{]}.
Increasingly, researchers are leveraging GitHub's underlying version control system to maintain and share digital lab notebooks {[}\protect\hyperlink{ref-10ghgV3S8}{3}{]}.
At least for aspects of a research project that involve writing code, a GitHub repository is a form of a lab notebook; when changes are made to files in a version controlled repository, the author of those changes makes a commit (\protect\hyperlink{definitions}{Box 1}) accompanied by a message describing the changes and the reason for them. Later, the entire history of commits and their messages are viewable and can be audited similar to a physical lab notebook {[}\protect\hyperlink{ref-4ny1onB0}{8}{]}.
GitHub issues (\protect\hyperlink{definitions}{Box 1}) can be used to prioritize lab objectives and goals, as well as track any status updates.
Some EEB labs have even turned their lab notebooks into shareable websites (\url{https://scheuerell-lab.github.io/lab-book}; \url{https://github.com/HuckleyLab/how_we_work}) as a centralized location for all lab resources.

\hypertarget{project-management}{%
\subsubsection{Project management}\label{project-management}}

Modern EEB research is highly collaborative, bringing together multidisciplinary teams from various institutions.
On GitHub, collaborators can share feedback, brainstorm ideas, and troubleshoot problems (Figure \ref{fig:github-diagram}).
GitHub has an ``Issues'' feature that allows for discrete tasks and sub-tasks to be identified, assigned to team members, and categorized with custom labels.
The new GitHub ``Discussion'' feature serves as a message board for conversation.
Scripts, commit messages, and pull requests can be linked directly to issues and discussions, providing a clear record of project workflow.
The use of GitHub for all project-related conversation and planning, rather than e-mail or messaging tools, makes it easier to keep track of progress throughout the lifespan of a project.
Unlike emails and messages which can get lost as more new tasks arise, GitHub issues are intentionally closed by repository administrators hiding the issue from view (closed issues remain accessible but not immediately visible).
Fortunately, it is not essential for all team members to have proficiency in git or programming, as users can interact with Issues and Discussions via web browser or e-mail (e-mail responses still get tracked as comments on the focal GitHub issue).
For larger projects with many team members and tens or hundreds of GitHub issues to sort through, project management software like ZenHub, can help prioritize issues and pull requests.
ZenHub's web interface includes a GitHub Issue visualizer where users can organize issues into high priority or backlogged tasks and link issues together when they are related to a shared project goal or milestone.
GitHub is currently beta testing a similar project management feature called GitHub Projects {[}\protect\hyperlink{ref-RhBKe0MG}{22}{]}. GitHub can also be integrated with other project management software such as Slack (https://slack.github.com/) so that teams are notified through a Slack group chat when updates are made to a repository.

\hypertarget{educational-materials}{%
\subsubsection{Educational materials}\label{educational-materials}}

GitHub supports a broad set of mechanisms for hosting educational materials.
The entire process of running a course, workshop, or lecture, can all be done openly on GitHub including material development, web hosting, and delivery, and even the submission and grading of assignments.
While there are other purpose-built platforms for this, GitHub provides a free, open-source alternative.

Making presentations can be done through most major high-level programming languages such as R, with \texttt{RMarkdown} {[}\protect\hyperlink{ref-QqMezOMg}{23}{]}, Python, with \texttt{python-ppt} (\url{https://python-pptx.readthedocs.io}), and Julia, with \texttt{Remark.jl} (\url{https://juliapackages.com/p/remark}).
Since all these programs work via code bases, they can be version-controlled through git and GitHub.
Once content is made, hosting a course website can be done through GitHub Pages, and there are lots of templates available (e.g., see \url{https://github.com/topics/course-website}).
This way, the course content can be available to enrolled students, as well as a global pool of learners and teachers interested in the course material.
Content can then be delivered via the course website, and/or a GitHub organization with, for example, template repositories for assignments.
Student submissions are perhaps the most challenging component, but the new GitHub Classroom tool (https://classroom.github.com) allows instructors to host private assignments submitted as code files (.R or .Rmd) or .pdf files, and even build custom autograding tests.

Instructors may only need to incorporate some of these tools given the time required to implement various GitHub features, however it is still valuable to do so and to encourage students to begin learning about version control through interacting with git/GitHub, however minimally, through the course.
Especially if a central tenet of a given course or educational unit is to introduce or give students experience with version control, reproducibility, and the tools that working professionals in EEB use, then adopting a few of these tools can be a great way to do so.

\hypertarget{creating-a-website}{%
\subsubsection{Creating a website}\label{creating-a-website}}

Personal or lab websites are one method of improving the dissemination of research findings and coordination of research efforts, but most EEB researchers have little experience in building or hosting webpages.
GitHub Pages (\url{https://pages.github.com}) is a feature that, when activated for a repository, renders content written in markdown (e.g., \url{https://github.com/SORTEE-Github-Hackathon/main-website}) as an HTML web page with a URL (e.g., \url{https://sortee-github-hackathon.github.io/main-website/}).
This can be useful for sharing reports (e.g.~written with RMarkdown and rendered to HTML) with collaborators, or for more complex projects like personal, project, or lab websites.
GitHub also offers website templates and it is possible to create a website by forking (\protect\hyperlink{definitions}{Box 1}) a repository hosting a GitHub Pages site as a starting point.
Aside from free hosting services, another benefit is that GitHub Pages are autogenerated, meaning that when content is modified in the associated GitHub repository, the website instantly updates {[}\protect\hyperlink{ref-RVetqmsg}{7}{]}.
Though the templates are useful for quickly starting up a new website, users are able to fully customize their Pages websites (for technical details of customizing GitHub Pages site see {[}\protect\hyperlink{ref-MXxgZJ45}{24}{]}).
We emphasize that despite the many benefits of using GitHub pages (free hosting, templates, customization), this avenue for creating a website will often be more time intensive than the out-of-the-box platforms. ``Static websites'' (i.e., websites where every user sees the same content) can be created using Jekyll (\url{https://jekyllrb.com}) and Hugo (\url{https://gohugo.io}), which also include template libraries for websites that can be hosted freely via GitHub pages.
Several R packages such as distill (\url{https://github.com/rstudio/distill}) and blogdown (\url{https://bookdown.org/yihui/blogdown}) have made the interface to these website generators more accessible.
In addition, Quarto (\url{https://quarto.org}) has options for creating websites (\url{https://quarto.org/docs/websites}) as well as the code-free website generator wowchemy (\url{https://wowchemy.com}) which uses Hugo.

\hypertarget{archiving-citable-code-and-data}{%
\subsubsection{Archiving citable code and data}\label{archiving-citable-code-and-data}}

GitHub makes it easy to store and share a variety of data files in the cloud.
If a repository is made ``public'' the URL to the repository can be shared freely with others.
However, for a variety of reasons (e.g., privately owned company, ability to make repositories private, accounts can be deleted at will) GitHub is not considered a long-term data or code repository like Zenodo and Figshare {[}\protect\hyperlink{ref-10ghgV3S8}{3},\protect\hyperlink{ref-kEX5dgzK}{9},\protect\hyperlink{ref-tbl:compare}{\textbf{tbl:compare?}}{]}.
Also, unlike long-term repositories, GitHub does not issue Digital Object Identifiers (DOIs) for content uploaded to their servers.
DOIs are persistent and unique alpha-numeric IDs assigned to research products like papers, code, and data.
DOIs allows tracking and citing research products.
For this reason, scientists who share code and data through GitHub are strongly encouraged to also submit GitHub repository content to a long-term data archive {[}\protect\hyperlink{ref-1Du6fzB8g}{25}{]}.
Fortunately, both long-term repositories mentioned above (Zenodo and Figshare) have integrations with GitHub.
After linking one's GitHub repository to Zenodo or Figshare, every time a release (\protect\hyperlink{definitions}{Box 1}) is made, a snapshot of the entire repository is archived with a versioned, citable DOI.
Linking one's GitHub repository with Zenodo, etc. to obtain a DOI helps work become findable, gives proper attribution, and can ensure long-term stability {[}\protect\hyperlink{ref-iIEKCTLU}{26}{]}.

Many researchers believe that their code is not useful because their analysis is context-specific and not explicitly designed for re-use like software.
However, there are many reasons to share data and code beyond re-use.
Even if code lacks detailed annotation, it shows the exact steps taken to conduct an analysis, and therefore provides the most detailed look into how to reproduce a given analysis {[}\protect\hyperlink{ref-uBJwnPbq}{27}{]}.
This is important in light of the reproducibility crisis {[}\protect\hyperlink{ref-1HZdsK5Kn}{28}{]} and will become increasingly important to the collective scientific enterprise as advances in computing power and accessibility unlock the ability to conduct `big data' meta research with data that has already been collected by others.
Failing to include data and code with publications leaves future scientists with fewer open resources from which to understand the world.

An important aspect of making code citable and reusable is adding an appropriate licence.
Code without a licence is (by default) actually provided more protection from reuse than code with an open licence.
The standard GitHub licensing options are best suited for software, so depending on how you want your code to be used you can choose one of the other license options.
For example, if your code is intended only for your specific analysis, consider a Creative Commons License.
If you wish to receive attribution for any reuse of your code, consider a CC BY 4.0 license.
If you have built an app, tool, package, or other product that you would like others to use and would like attribution for any reuse of your code, consider the GNU General Public License v3.
This license also prohibits the re-user from making their re-used version private.
To help navigate through the potential licenses available to you and their attributes the Choose a License (\url{https://choosealicense.com/non-software/}) website can offer further guidance.

\hypertarget{collaborative-code-editing-and-asynchronous-working}{%
\subsubsection{Collaborative (code) editing and asynchronous working}\label{collaborative-code-editing-and-asynchronous-working}}

GitHub facilitates collaborative coding and asynchronous working because researchers can seamlessly access and contribute to data and code regardless of disparities in schedules or location.
Project work can also be clearly split among team members, giving them the flexibility to contribute when it best fits their schedule.
We acknowledge that there are important differences between the average software developer and EEB researcher using GitHub, and that not all of GitHub's features are useful for research workflows (\protect\hyperlink{tbl:roles}{Table 1}).
However, git's core features such as forking and branching (\protect\hyperlink{definitions}{Box 1}) allow for simultaneous coding on different versions of the same research project, and alternative versions can be discussed and resolved with GitHub.
When EEB projects are contained on the GitHub platform, researchers can stay abreast of progress made by other collaborators without the need for meetings or emails.
Version control {[}\protect\hyperlink{ref-K7nbP1Ty}{29}{]} features also allow users to make progress and changes without worrying about irreparably writing over someone else's work.
By enabling more comprehensive remote collaboration, GitHub encourages the exchange of ideas among researchers at different institutions and in different countries, which can serve to improve the quality of the research itself by providing open access to data and code.
In academic settings, GitHub can also facilitate interactions between research advisors and advisees, providing a platform for students or other trainees to share in-progress code, and flag specific challenges or questions for their supervisors or mentors.
Periodic code review {[}\protect\hyperlink{ref-hm9PaCLD}{30}{]} can also help advisors identify errors early in the process, and inform further training and mentorship to fill gaps in skills.

\hypertarget{writing-a-manuscript}{%
\subsubsection{Writing a manuscript}\label{writing-a-manuscript}}

Beyond supporting collaboration at the level of code, GitHub can be used for collaboratively writing manuscripts.
Writing a manuscript in GitHub and storing it with associated data and code all in the same repository increases scientific reproducibility because files associated with a manuscript can be found in one place.
Co-authors can contribute new text to a manuscript or suggest revisions through GitHub's robust pull request feature (\protect\hyperlink{definitions}{Box 1}) which provides a line-by-line view of all proposed changes.
Further, authors can make use of the Discussions tab to suggest relevant papers to be cited, and can raise issues during the writing process that can be assigned to collaborators (\protect\hyperlink{tbl:roles}{Table 1}).

While GitHub is not considered as user-friendly for manuscript development as conventional text processors {[}\protect\hyperlink{ref-4ny1onB0}{8}{]}, it has been substantially improved with recent tools.
Manuscripts can be written on GitHub with Markdown.
Add-ons like HackMD (\url{https://hackmd.io}), can enable real-time collaboration for individual Markdown documents.
Many tools exist for extending Markdown and Pandoc to add formatting features necessary for scientific writing like in-text citations and figure and table cross references.

We wrote this manuscript using Manubot {[}\protect\hyperlink{ref-YuJbg3zO}{31}{]}, a collaborative manuscript platform that uses Markdown for writing and GitHub for storing and tracking changes to a manuscript over time.
Manubot uses a GitHub Actions-based typesetting system to compile individual Markdown files stored in a GitHub repository into a single LaTeX document, which can be displayed in Word, HTML, or PDF formats.
The resulting manuscript can also be compiled using a journal's .tex template to match their formatting requirements.
Since this tool reruns the entire manuscript compilation process with any change to the underlying repository, it can also accomodate continuous integration of code updates into figures and tables with additional GitHub Actions (e.g.~https://github.com/SORTEE-Github-Hackathon/manuscript/tree/main/.github/workflows).
Manubot also allows for straightforward citation management based on URLs or DOIs.
For more examples of Manubot being used for manuscripts, see {[}\protect\hyperlink{ref-YuJbg3zO}{31}{]}.

Since Manubot works on documents in a distributed format, it can be difficult to edit manuscripts for overall flow with only this tool.
We employed hypothes.is (\url{https://hypothes.is}) to write comments on the HTML manuscript document produced by Manubot, which we then addressed by committing changes to the underlying Markdown files via pull requests.
Other authors can reply to the comments to indicate agreement or disagreement, and to note when changes have been made.
Other tools can also be used for version control of scientific manuscripts including R Markdown via the bookdown package (\url{https://bookdown.org/}), jupyter notebooks {[}\protect\hyperlink{ref-i4FOZpjN}{32}{]} and a relatively new tool, Quarto (\url{https://quarto.org}).

\hypertarget{peer-review}{%
\subsubsection{Peer-Review}\label{peer-review}}

Peer review plays a critical role in the scientific evaluation of EEB research.
GitHub provides an open and transparent platform that can be used for either directly providing feedback on research products or building a to-do list from reviewer comments.
Peer review of research software by the open software development community rOpenSci (https://ropensci.org/software-review/) and of research software and associated manuscripts by the Journal of Open Source Software (https://joss.readthedocs.io/en/latest/submitting.html) requires that submitted work is hosted on GitHub and their review processes make use of GitHub issues.
rOpenSci's efforts have resulted in many well-used R packages for ecology research including rfishbase {[}\protect\hyperlink{ref-Xsdcv6q}{33}{]} and taxize {[}\protect\hyperlink{ref-FVBWKkZu}{34}{]}.

GitHub can also be used as a hub for reviewers and authors during the peer review process of an ordinary research manuscript.
If the code associated with a manuscript is made available at the time of submission (e.g.~via a link to a GitHub repository in a Data Availability Statement), peer-reviewers may be able to offer more helpful suggestions on written methods and may even make comments on the code itself, potentially catching bugs or errors before publication.
GitHub can also be used as a hub for reviewers and authors during the peer review process of an ordinary research manuscript.
GitHub issues can be used to organize and discuss reviewer suggestions and to assign them to co-authors (See example in \url{https://github.com/BrunaLab/HeliconiaDemography/issues?q=is\%3Aissue+label\%3A\%22reviewer+comment\%22+}).
When reviewer comments are posted as separate issues, authors can comment on the issues to discuss possible changes and assign themselves to indicate which comments they intend to handle.
Co-authors can then integrate their edits and responses to reviewers using pull requests.

Some specialized journals, such as the the Journal of Open Source Software (\url{https://joss.readthedocs.io/en/latest/submitting.html}), require that submitted work is hosted on GitHub and their review processes make use of GitHub issues.
Peer review of research software by rOpenSci (\url{https://ropensci.org/software-review/}) also makes use of many features of GitHub to streamline and automate parts of the review process.
rOpenSci's efforts have resulted in many well-used R packages for ecology research including rfishbase {[}\protect\hyperlink{ref-Xsdcv6q}{33}{]} and taxize {[}\protect\hyperlink{ref-FVBWKkZu}{34}{]}.
Although the use of GitHub in peer-review is currently restricted to these specialized cases, they may provide a model for peer-review in more traditional EEB journals for manuscripts that make use of code.

\hypertarget{open-science-discussion}{%
\subsubsection{Open science discussion}\label{open-science-discussion}}

Research papers are condensed outputs that hide the underlying intellectual and computational workflows, including the treatment of the raw data and analytical steps.
Granting readers access to code and other documentation of the analysis allows them to retrace and comprehend analytical decisions.
GitHub provides a platform to access all aspects of the project, and can be linked to platforms that create citable DOIs, rather than just the final manuscript.
While often thought of as storage for data and code, GitHub repositories can also be used to publish a time-stamped preregistration of research plans and hypotheses.

Conventional research practices typically rely on one or two people running and checking the data analyses, while most coauthors (and readers of the subsequent publication) see only the final results and a verbal description of the analytical steps.
In the developmental stages, collaborators can directly see the code for the analysis, manipulate and explore the data themselves, and check for errors.
Cynically, there is also more insurance against nefarious colleagues that may be tempted to distort results {[}\protect\hyperlink{ref-18PTmKJkq}{35}{]}.
Collaborators as well as pre-publication and post-publication reviewers are better positioned to discover questionable findings if they have full and transparent access to the project.

This transparency can similarly be extended beyond coauthors to the entire scientific community.
Publishing the data and reproducible workflows along with the manuscript allows any reader to review the analysis and reproduce the experiment {[}\protect\hyperlink{ref-NOgBWVAr}{36}{]}.
Supplying code for (novel) methods that are proposed or used also reduces barriers to knowledge and can greatly improve the ability of others to build on existing work, resulting in greater proliferation and accessibility for a broader audience.
GitHub even provides a useful Discussions Forum (\url{https://docs.github.com/en/discussions}) that aids the direct communication with repository owners, as well as the GitHub Community (\url{https://github.community/}) forum for more general questions and sharing of expertise (\protect\hyperlink{tbl:roles}{Table 1}.

\hypertarget{project-continuity}{%
\subsubsection{Project continuity}\label{project-continuity}}

The development of research software continues, and so does the need to consider project continuity, especially in EEB where graduate students, research assistants, and postdoctoral fellows often hold relatively short-term positions {[}\protect\hyperlink{ref-D4C4k4ak}{37}{]}.
Often with these types of short-term research projects, once the contract expires, the research software upkeep tends to fall off as the researchers move on to new projects.
Additionally, if the research software is kept on only the researcher's personal devices, it becomes increasingly difficult to access the software and code for future uses.
As projects or contracts end, there should be a handover period of this software in order for the next cohort of researchers to reuse what was already developed {[}\protect\hyperlink{ref-4ny1onB0}{8},\protect\hyperlink{ref-D4C4k4ak}{37}{]}.

GitHub facilitates project continuity among research software and research code by providing tools that make this handover period easier.
As we have already mentioned, using Git for code in Ecology and Evolution can allow for a ``paper trail'' of sorts to be created for the research software, thus allowing for future users of the code access to the entire history of the project {[}\protect\hyperlink{ref-3DKwn1sY}{14}{]}.
Additionally, GitHub allows for repositories and organizations to have designated Code Owners {[}\protect\hyperlink{ref-s91uGRZ2}{38}{]}; these code owners can change through time allowing for the transition of research software from one cohort of researchers to the next {[}\protect\hyperlink{ref-iIEKCTLU}{26}{]}.
There are also multiple means by which to archive software dependency information with GitHub.
Dependencies can be described in README files, added to environment.yml and/or an environment.txt file, or stored in a repository using tools such as renv (\url{https://rstudio.github.io/renv/articles/renv.html}).
This ensures that as packages continue to develop with new syntax, code will still run as it did when it was developed.

Within EEB projects, tasks are often divided among contributors taking various roles (see CRediT taxonomy, \url{https://casrai.org/credit/}).
The creation of project repositories is commonly the purview of those involved in the software, formal analysis, and/or visualization components of the project through their roles as code writers.
However, the structural components of a typical GitHub repository and the derived EEB-specific templates can provide functional ways for other collaborators not contributing to code to be engaged in aspects of repository design in a way that improves institutional memory and facilitates project continuity.
These other collaborators can offer many contributions to repository design and development, and their active involvement can both aid authors ability to act as guarantors of the project, and the clarity and reproducibility of the project for future users.
In (Figure \ref{fig:scatterblob}), we highlight several elements of good repository structure, and the various ways that contributors may interact with them.

\hypertarget{github-organizations}{%
\subsubsection{GitHub Organizations}\label{github-organizations}}

GitHub Organizations offer a shared virtual space that allows a team to work in different repositories, while remaining tied together under a larger figurehead, such as a laboratory, a department, an organization, or a large project involving several teams.
Organizations are well-suited to ensure larger projects with many steps or moving parts are constrained to one virtual space, where outputs and sub-projects can be easily accessed and located without relying on any one individual.
Because the repositories are grouped in one virtual space, members can reference and contribute to each other's work without necessarily being part of the same repository, broadening the accessibility and longevity of code and writing contributions.

Contributors can be assembled into teams within an organization, which allows administrators to assign roles and tasks to groups of people.
Whereas access to repositories is usually assigned to individual contributors, Organizations facilitate the management of access permissions by allowing each team to be granted access to certain repositories, and not to others.
This ensures that more sensitive repositories remain as restricted as needed, while repositories with greater general interest can be easily accessible to many members at once.

As an example, GitHub Organizations are particularly well-suited to house documents and projects within a laboratory, such as research compendia, codes of conduct, protocols, training documents, and other such documents that evolve collaboratively over time and are relevant to many colleagues.
In this way, teams can have full ownership of repositories within an organization, while ensuring that these materials stay accessible to the laboratory after people have moved on or lost their copies of project data.
This application extends to research centres, which may include several distinct projects that remain linked under a given institution, such as the German Centre for Integrative Biodiversity Research (iDiv, \url{https://github.com/idiv-biodiversity}).
Of course, the utility of this tool goes beyond laboratories - they are useful to structure the organization, presentation, and outcomes of working groups such as the hackathon which inspired this paper (SORTEE-Github-Hackathon, \url{https://github.com/SORTEE-Github-Hackathon}) by keeping track of all materials as ideas develop and take shape in one virtual space.
Organizations are also convenient for hosting a set of related learning materials such as a set of lectures or workshops, such as the Québec Centre for Biodiversity Science R Workshop Series (QCBSRworkshops, \url{https://github.com/QCBSRworkshops}) or the University of Edinburgh's Coding Club (Coding Club, \url{https://github.com/ourcodingclub}), which may be updated by an ever-evolving group of contributors over time.

Using GitHub organizations as a research group or even for a handful of individuals working on a group of projects can be incredibly useful for all involved.
GitHub organizations are relatively easy to set up, and especially easy to manage as membership to the organization changes through time.
Not only is it a useful way to store repositories of lab-related research products, but it is also incredibly helpful for storing ``living documents'' that may be edited frequently, and may be linked to a lab website (that could also be generated via a repository that lives within the organization).
The use of the ``Teams'' feature can allow certain groups to have varying levels of access to repositories in the organization with a select group having push access to some repositories but not others.
This can manifest in a group working on some common dataset(s) to have push access to the handful of repositories used for processing sequence data, while another group of students/researchers may have push access to an entirely different set of repositories.
The organization structure also allows for easy tracking of issues, projects, and discussions related to the research group, and provides group leads an easy birds-eye view of the progress going on across multiple projects.

\hypertarget{discussion}{%
\subsection{Discussion}\label{discussion}}

\hypertarget{the-promise-of-github-for-eeb-researchers}{%
\subsubsection{The promise of GitHub for EEB researchers}\label{the-promise-of-github-for-eeb-researchers}}

There have been many calls for researchers outside of the software development community to join the 73 million GitHub users for their collaborative research {[}\protect\hyperlink{ref-10ghgV3S8}{3},\protect\hyperlink{ref-1Du6fzB8g}{25},\protect\hyperlink{ref-UsTxAq4f}{39}{]}.
This call comes in light of both the continual shift toward open-science and increasing computational and data requirements in EEB.
Until now, resources and practical guidance specifically focused on using GitHub within the EEB community have been dispersed in blog posts and video tutorials (\protect\hyperlink{tips}{Box 2} Box {[}\protect\hyperlink{ref-box:tips}{\textbf{box:tips?}}{]}).
We felt these resources have been extremely useful for us to learn to use GitHub in our own work, and that a collation of the main ideas into one medium, while adding on our personal perspectives, would be of use to the EEB community.

In this paper, we described 12 tractable ways that EEB researchers can leverage GitHub to enable more transparent and collaborative research (Figure \ref{fig:scatterblob}).
Many of the examples are specifically meant for first-time GitHub users and can likely be adopted with just a little practice (storing data, creating virtual notebooks, making code citable).
For example, storing code and data and making it citable generally just involve creating a repository on GitHub, pushing code to the repository, and then going through the necessary steps (e.g., connecting a GitHub repository with Zenodo; see below) for creating a DOI for the repository.
These actions are often covered in any introductory tutorial on GitHub and take little effort to implement.
On the other hand, some other examples we described here, including material development, web hosting, and delivery, may require a greater time commitment, but have the potential to make EEB research more open, accessible, and collaborative than ever before.
Managing full research projects or research labs on GitHub will require careful thought as to how to delegate tasks such as reviewing pull requests or creating issues, as well as thought as to how modular to make the research project or research lab (i.e., which repository will be used for what, and how many repositories are needed).
For example, collaboratively writing a paper using GitHub, as we have done here, will involve a learning curve for co-authors less familiar with the intricacies of GitHub, and also require overhead to set up the repository using GitHub actions.
Despite the many potential applications of GitHub to EEB research, we acknowledge that there will still be many times when researchers might look to other platforms for research collaboration.

\hypertarget{other-platforms-for-collaboration}{%
\subsubsection{Other platforms for collaboration}\label{other-platforms-for-collaboration}}

Though we see GitHub as a useful tool for collaboration in EEB, we describe two use cases where, to our knowledge, GitHub's features still fall short of the type of highly collaborative work emblematic of EEB research.
First, real-time collaborative editing (e.g., as on a shared Google Doc or a Word document stored on Dropbox) is not possible on GitHub.
There are websites outside of the GitHub ecosystem that are built on top of the GitHub architecture that allow real-time collaborative editing (e.g., hackMD (\url{https://hackmd.io/}) or replit (\url{https://replit.com/})).
We used HackMD at two key points in writing our manuscript when real-time co-writing was essential: when taking meeting notes and writing the outline of our paper.
Second, we looked to other software when working on figures and tables.
Though creating tables and figures on GitHub using markdown or other scripting languages is possible, we found that it was not practical at the early brainstorming stages.
We needed to rapidly iterate on figure and table design, share feedback through comments, and merge/reorder ideas when necessary.
For these reasons, we used Google Slides for working on figures and Google Sheets for working on tables.
As our figures and tables moved towards more finalized forms, some co-authors chose to create the tables and figures using R and Markdown which could then be tracked using the same version control system as the rest of manuscript.

\hypertarget{why-arent-more-eeb-researchers-using-github}{%
\subsubsection{Why aren't more EEB researchers using GitHub?}\label{why-arent-more-eeb-researchers-using-github}}

Though GitHub has been available as a platform for more than a decade, its uptake among EEB researchers, especially as a tool for collaboration, has been slow.
Here we discuss four potential barriers to GitHub use in EEB.

First, there may be a hesitation to use GitHub due to the somewhat steep learning curve to using the platform combined with limited instruction available through traditional university courses.
When GitHub is taught within an EEB context, it is usually accompanying coursework in topics such as statistical programming, and some students may find it overwhelming to juggle learning git alongside scripting languages, statistical theory, and file system navigation, especially when many may also be new to using command-line interfaces in general.
Instructors likewise may confuse the expected digital literacy of younger students with computational fluency, even when modern technology increasingly abstracts many relevant concepts through search optimization and preponderant IDEs (Integrated Development Environments), or `point-and-click' user interfaces.

Second, while many EEB researchers take advantage of GitHub for individual use, collaborative use may lag due to how researchers traditionally divide labor within projects.
Despite broad utility, GitHub remains a tool predominantly used by computer scientists and software developers.
EEB researchers may take the view that GitHub is a platform that only needs to be used by individuals writing code, and may silo those aspects of projects to a single individual.
Those assumptions may obscure the utility of GitHub for tasks other than traditional data analysis and code development, or how GitHub can facilitate the integration of code with non-coding aspects of projects through the practice of repository design.
However, we emphasize that there are opportunities for collaboration using GitHub by researchers of all skill levels or time constraints (Table \ref{tbl:roles}); for example, project stakeholders can provide a list of use-cases or highlight important conceptual components of a project using the issues or discussions functionality of GitHub.

A third barrier may come from general reluctance to share data and code publicly, or technical and logistical issues.
The default public nature of GitHub usage can add additional pressure to students and scientists learning to use the platform.
We also note that large file storage is discouraged (and limited) on GitHub but add-ons do exist (e.g.~\url{https://git-lfs.github.com/}) that permit data storage, and increasing integration between platforms (e.g. {[}\protect\hyperlink{ref-lx49NGto}{40}{]}) allows data to be stored away from GitHub and linked dynamically.
We suspect a major additional barrier to EEB researchers is a distinct lack of GitHub help documents for non-English researchers in ecology and evolution, meaning that EEB researchers potentially miss the opportunity to fully understand the importance of version control, reproducibility, and other benefits of GitHub.

Lastly, GitHub has both free and paid plans.
When projects get highly collaborative they may have to pay for additional GitHub support.
The acquisition of GitHub by Microsoft has led to some concerns over the future of free plans and several biodiversity data managers have begun to switch to Open Source Git services (e.g.~Bitbucket and GitLab).
At this point however, there is little practical difference for EEB researchers between the paid and free GitHub plans.

\hypertarget{tips}{%
\subsubsection{Box 2}\label{tips}}

\begin{tablenos:no-prefix-table-caption}

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\columnwidth - 0\tabcolsep) * \real{1.0000}}@{}}
\toprule
\begin{minipage}[b]{\linewidth}\raggedright
10 Tips for getting started in GitHub
\end{minipage} \\
\midrule
\endhead
1. \textbf{Check for an existing solution to your problem} The GitHub Help webpage (\url{https://docs.github.com/en}) contains extensive and detailed documents with helpful screenshots. It is a good starting point for handling an issue, and has troubleshooting tips for specific problems. Alternatively, consider Tweeting your issue. There is a large community of GitHub users around the world who have likely faced analogous problems and may be able to provide quick solutions. Third, try to follow blogs (e.g., \url{https://github.blog}), Twitter accounts or YouTube channels that regularly post practical solutions about common GitHub issues. \\
2. \textbf{Consider taking free courses} such as those from Software Carpentries {[}\protect\hyperlink{ref-pjy75gHr}{41}{]} and sharing these courses with your lab members or colleagues. \\
3. \textbf{Take the advantage of GitHub as an asynchronous working tool for team-based projects} See the repository for this paper (\url{https://github.com/SORTEE-Github-Hackathon/manuscript}) as an example of a collaborative manuscript that includes discussions, issues, and a website via GitHub. \\
4. \textbf{The GitHub Learning Lab (\url{https://lab.github.com})} allows you to learn GitHub basics through short projects and tasks, and allows you to get feedback from their Learning Lab bot. \\
5. \textbf{Check out the following markdown cheatsheet (\url{http://markdownguide.org/basic-syntax})} so that you can write clear metadata README files for your repositories. \\
6. \textbf{The Jenny Bryan universe of GitHub material} provides a thorough and accessible introduction for a multitude of research-related uses for GitHub, and includes a book {[}\protect\hyperlink{ref-ZvrOcg9w}{42}{]}, statistics course {[}\protect\hyperlink{ref-6CMMeSeD}{43}{]} and academic article {[}\protect\hyperlink{ref-RVetqmsg}{7}{]}. \\
7. \textbf{Don't be afraid of trial and error} One of the best ways to learn GitHub is the trial and error method. Learning from your own mistakes can be the better way to master your GitHub abilities. In any case, GitHub has the advantage of making it easy to go back to any steps that you desire via version controlling if you make mistakes. \\
8. \textbf{If you are an educator, include lectures on reproducibility and tools for creating reproducible workflows in your curricula}. Some graduate programs now include coursework on course Rmarkdown and GitHub. Getting students started with these tools earlier will prevent the resistance that comes from working with a less reproducible workflow for a longer period of time. \\
9. \textbf{Try to begin committing with GUI (Graphical user interface) tools} like GitHub Desktop (\url{https://desktop.github.com}), git-gui (\url{https://git-scm.com/docs/git-gui}), RStudio (\url{https://www.rstudio.com}), Visual Studio Code (\url{https://code.visualstudio.com}), Atom (\url{https://atom.io}), GitKraken (\url{https://www.gitkraken.com}) tools instead of CLI (Command line interface) tools such as Terminal or Console for more advanced features. \\
10. \textbf{Get help deciphering GitHub Notifications.} Try using tools like Octobox (\url{https://octobox.io}) to disentangle and manage multiple notifications from distinct GitHub projects. \\
\bottomrule
\end{longtable}

\end{tablenos:no-prefix-table-caption}

\hypertarget{conclusion}{%
\subsection{Conclusion}\label{conclusion}}

We provide 12 practical ways that Ecologists and Evolutionary Biologists can incorporate GitHub into their research workflows, and include definitions (\protect\hyperlink{definitions}{Box 1}) and key user groups (Figure \ref{fig:github-diagram}) that can help researchers prioritize which GitHub skills to learn first.
Some GitHub uses are highly collaborative (e.g., open science discussion and collaborative code editing) while others are focused on individual actions (e.g., storing code/data, building a website).
Regardless of the degree of collaboration, GitHub use in ecology and evolution has the potential to make the field more open and transparent than ever before.
Our paper provides the most comprehensive review of how EEB researchers can use GitHub to date, and we encourage EEB researchers at any career stage studying any topic to try GitHub as a platform for sharing and collaboration.

\hypertarget{acknowledgements}{%
\subsection{Acknowledgements}\label{acknowledgements}}

This manuscript arose from a hackathon at the Society for Open, Reliable, and Transparent Ecology and Evolution (SORTEE) virtual meeting in July 2021.

RCO was funded by the U.S. Department of Energy, Office of Science, Office of Biological and Environmental Research, Earth and Environmental Sciences Division, Data Management program under contract number DE-AC02-05CH11231.

\hypertarget{code-and-data-availability}{%
\subsection{Code and data availability}\label{code-and-data-availability}}

The source code and data for this manuscript are available at https://github.com/SORTEE-Github-Hackathon/manuscript.

\hypertarget{figures}{%
\subsection{Figures}\label{figures}}

\begin{figure}
\hypertarget{fig:github-diagram}{%
\centering
\includegraphics{images/github_diagram.png}
\caption{An overview of the features of a GitHub repository. A) Multi-faceted components allow for code writing, small data storage, manuscript writing, and project management to all be done in one place. B) Issues, Pull Requests, Discussions, and Projects allow for team members to ask for feedback, suggest fixes, discuss related ideas, and keep track of all the moving parts of a project. C) All collaborators on a project can be a part of a single repository, with varying push privileges and responsibilities. D) CONTRIBUTING.md, LICENCE.md, \& README.md files can allow new team members or others wanting to use materials to understand the project components and learn how they can engage with the project and existing team members.}\label{fig:github-diagram}
}
\end{figure}

\begin{figure}
\hypertarget{fig:scatterblob}{%
\centering
\includegraphics{images/scatterblob_1.png}
\caption{A summary of ways GitHub can be used showing technical difficulty and degree of collaboration for each. Activities higher on the vertical axis require usage knowledge of more GitHub features than activities lower on the axis. On the horizontal axis, each activity spans a region representing who is potentially involved with or benefits from each activity. For example, storing data and code mainly benefits individual researchers or members of a lab group while making data and code citable and reproducible benefit other labs and the larger community as well. Independently of a users knowledge level of GitHub features, there are ways to use GitHub that allow tapping unto one of the most salient benefits of the platform: facilitating and enhancing collaboration.}\label{fig:scatterblob}
}
\end{figure}

\hypertarget{tables}{%
\subsection{Tables}\label{tables}}

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.0493}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.1425}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.1041}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.1562}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.1096}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.1479}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.1370}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.1534}}@{}}
\caption{A non-exhaustive collection of ideas for how various GitHub
features could be utilized for a research project. Here we have
categorized contributors/collaborators into five roles. A Project
Manager owns the GitHub repository for a project, and leads the academic
project (e.g., lead author of a manuscript). A co-author contributes to
writing and other aspects of research, but may have limited or no
experience with programming, git, and/or GitHub. A code contributor
writes or edits analysis code for the project. A code reviewer could be
a project collaborator or a peer reviewer who reviews project code. They
are familiar with coding, but not necessarily with git or GitHub (but
they are willing to learn). Finally, community members could be other
researchers or non-researchers interested in reproducing results,
re-using code or data, or communicating with researchers involved in the
project. These roles are not mutually exclusive---a co-author could also
be e code contributor and code reviewer, for example. For definitions of
the GitHub features, see Box 1. \label{tbl:roles}}\tabularnewline
\toprule
\begin{minipage}[b]{\linewidth}\raggedright
Role
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
GitHub repository
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
README
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Issue
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Discussion
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Pull Request
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Fork
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
GitHub Pages
\end{minipage} \\
\midrule
\endfirsthead
\toprule
\begin{minipage}[b]{\linewidth}\raggedright
Role
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
GitHub repository
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
README
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Issue
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Discussion
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Pull Request
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Fork
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
GitHub Pages
\end{minipage} \\
\midrule
\endhead
Project manager & Set contributor permissions, share code of conduct & Project descritption, citation, DOIs & Assign tasks to collaborators & Discuss project directions and goals & Approve and incorporate edits to code and/or writing & & Share up-to-date reports, figures, or draft manuscript \\
Co-author & Edit Markdown text or add files & & Propose changes involving code (e.g.~analyses, figures) & Discuss proposed changes to manuscript & & & \\
Code contributor & & & Suggest code changes & & Contribute changes to code, initiate code review & & Contribute to project website \\
Code reviewer & Find all code related to a project & & Highlight specific lines of code and make suggestions & & Review or recommended changes in code & & \\
Community & & & Suggest additional features and report bugs & Ask questions about data and code & & Create a linked, editable copy of the repository & View project website \\
\bottomrule
\end{longtable}

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.0628}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.0529}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.0281}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.0281}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.0380}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.0529}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.1851}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.1669}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.2562}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.1289}}@{}}
\caption{a comparison of technologies\ldots{} \label{tbl:compare}}\tabularnewline
\toprule
\begin{minipage}[b]{\linewidth}\raggedright
Guild
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Software
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Vesion control
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Backup (cloud)
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Passive collaboration
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Active real-time colalboration
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Free \$
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Permanent (DOI)
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Storage limits
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
GitHub Integration
\end{minipage} \\
\midrule
\endfirsthead
\toprule
\begin{minipage}[b]{\linewidth}\raggedright
Guild
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Software
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Vesion control
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Backup (cloud)
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Passive collaboration
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Active real-time colalboration
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Free \$
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Permanent (DOI)
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Storage limits
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
GitHub Integration
\end{minipage} \\
\midrule
\endhead
Multi-tool & GitHub & yes & yes & yes & NA & Broadly limited free version. Advanced features are provided for free to students and education professionals. & A DOI can only be obtained when integrating to other services that can mint DOI (e.g.~Zenodo, OSF). & 100MB per file, 500MB per private repository (2GB for paid accounts). 100GB for public repositories. Larger files (up to 2GB) can be attached to releases & NA \\
Multi-tool & OSF & yes & yes & yes & yes & yes & yes & 25GB for private projects, up to 5GB per file, plus partner add-ons, 50GB for public projects & yes \\
Long-term (public) data repositories & PANGAEA & yes & yes & yes & NA & yes & yes & 10 GB free & NA \\
Long-term (public) data repositories & Zenodo & after published & after published & NA & NA & yes & yes & 50 GB per dataset & yes \\
Long-term (public) data repositories & Dryad & after published & after published & NA & NA & some journals cover cost & yes & 300 GB per publication & Can link to individual files (not entire reopository); not really integrated \\
Long-term (public) data repositories & Figshare & yes & yes & yes & NA & yes & yes & 20 GB free, up to 5 TB & yes \\
Temporary (personal) drive storage & Google Drive & yes & yes & yes & yes & limited free version \& paid & NA & 15GB free, up to 100GB with Google One & yes \\
Temporary (personal) drive storage & Box & limited & yes & ? & ? & NA & NA & Unlimited total size for subscription & yes \\
Temporary (personal) drive storage & DropBox & limited & yes & yes & yes & limited free version \& paid & NA & 2GB free & yes \\
Temporary (personal) drive storage & OneDrive and the Office Suite & yes & yes & yes & yes & limited free version \& paid & NA & 5 GB free, up to 1TB paid & yes \\
Collaborative code/text editors & Overleaf (online latex editor) & yes & yes & yes & NA & NA & NA & 1MB for individual .tex, 50MB for individual files, unlimited project size & yes \\
Collaborative code/text editors & Jupyter Notebook & yes & ? & yes & with Colab & yes & NA & via Binder: no hard limit, but suggests no files \textgreater100MB, can also store on GitHub or Google Colab & yes \\
Collaborative code/text editors & HackMD & yes & yes & yes & yes & yes & NA & 3 documents free, private invitee limits & yes \\
\bottomrule
\end{longtable}

\hypertarget{references}{%
\subsection{References}\label{references}}

\hypertarget{refs}{}
\begin{CSLReferences}{0}{0}
\leavevmode\vadjust pre{\hypertarget{ref-fJWFe93e}{}}%
\CSLLeftMargin{1. }
\CSLRightInline{\textbf{How do scientists develop and use scientific software?}
\CSLBlock{Jo Erskine Hannay, Carolyn MacLeod, Janice Singer, Hans Petter Langtangen, Dietmar Pfahl, Greg Wilson} \emph{2009 ICSE Workshop on Software Engineering for Computational Science and Engineering} (2009-05) \url{https://doi.org/bw966x}
\CSLBlock{DOI: \href{https://doi.org/10.1109/secse.2009.5069155}{10.1109/secse.2009.5069155}}}

\leavevmode\vadjust pre{\hypertarget{ref-1Kqna6l2}{}}%
\CSLLeftMargin{2. }
\CSLRightInline{\textbf{Challenge to scientists: does your ten-year-old code still run?}
\CSLBlock{Jeffrey M Perkel} \emph{Nature} (2020-08-24) \url{https://doi.org/gg89cr}
\CSLBlock{DOI: \href{https://doi.org/10.1038/d41586-020-02462-7}{10.1038/d41586-020-02462-7} · PMID: \href{https://www.ncbi.nlm.nih.gov/pubmed/32839567}{32839567}}}

\leavevmode\vadjust pre{\hypertarget{ref-10ghgV3S8}{}}%
\CSLLeftMargin{3. }
\CSLRightInline{\textbf{Democratic databases: science on GitHub}
\CSLBlock{Jeffrey Perkel} \emph{Nature} (2016-10-03) \url{https://doi.org/gdz6dq}
\CSLBlock{DOI: \href{https://doi.org/10.1038/538127a}{10.1038/538127a} · PMID: \href{https://www.ncbi.nlm.nih.gov/pubmed/27708327}{27708327}}}

\leavevmode\vadjust pre{\hypertarget{ref-10SpoByIw}{}}%
\CSLLeftMargin{4. }
\CSLRightInline{\textbf{A survey of the practice of computational science}
\CSLBlock{Prakash Prabhu, Yun Zhang, Soumyadeep Ghosh, David I August, Jialu Huang, Stephen Beard, Hanjun Kim, Taewook Oh, Thomas B Jablin, Nick P Johnson, \ldots{} David Walker} \emph{State of the Practice Reports on - SC '11} (2011) \url{https://doi.org/bdpsrp}
\CSLBlock{DOI: \href{https://doi.org/10.1145/2063348.2063374}{10.1145/2063348.2063374}}}

\leavevmode\vadjust pre{\hypertarget{ref-O6UbstGG}{}}%
\CSLLeftMargin{5. }
\CSLRightInline{\textbf{Best Practices for Scientific Computing}
\CSLBlock{Greg Wilson, DA Aruliah, CTitus Brown, Neil P Chue Hong, Matt Davis, Richard T Guy, Steven HD Haddock, Kathryn D Huff, Ian M Mitchell, Mark D Plumbley, \ldots{} Paul Wilson} \emph{PLoS Biology} (2014-01-07) \url{https://doi.org/qtt}
\CSLBlock{DOI: \href{https://doi.org/10.1371/journal.pbio.1001745}{10.1371/journal.pbio.1001745} · PMID: \href{https://www.ncbi.nlm.nih.gov/pubmed/24415924}{24415924} · PMCID: \href{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC3886731}{PMC3886731}}}

\leavevmode\vadjust pre{\hypertarget{ref-nwCtHDCn}{}}%
\CSLLeftMargin{6. }
\CSLRightInline{\textbf{Build software better, together}
\CSLBlock{GitHub} \url{https://github.com}}

\leavevmode\vadjust pre{\hypertarget{ref-RVetqmsg}{}}%
\CSLLeftMargin{7. }
\CSLRightInline{\textbf{Excuse Me, Do You Have a Moment to Talk About Version Control?}
\CSLBlock{Jennifer Bryan} \emph{The American Statistician} (2018-01-02) \url{https://doi.org/gdhzdp}
\CSLBlock{DOI: \href{https://doi.org/10.1080/00031305.2017.1399928}{10.1080/00031305.2017.1399928}}}

\leavevmode\vadjust pre{\hypertarget{ref-4ny1onB0}{}}%
\CSLLeftMargin{8. }
\CSLRightInline{\textbf{Git can facilitate greater reproducibility and increased transparency in science}
\CSLBlock{Karthik Ram} \emph{Source Code for Biology and Medicine} (2013-02-28) \url{https://doi.org/krv}
\CSLBlock{DOI: \href{https://doi.org/10.1186/1751-0473-8-7}{10.1186/1751-0473-8-7} · PMID: \href{https://www.ncbi.nlm.nih.gov/pubmed/23448176}{23448176} · PMCID: \href{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC3639880}{PMC3639880}}}

\leavevmode\vadjust pre{\hypertarget{ref-kEX5dgzK}{}}%
\CSLLeftMargin{9. }
\CSLRightInline{\textbf{Ten Simple Rules for Taking Advantage of Git and GitHub}
\CSLBlock{Yasset Perez-Riverol, Laurent Gatto, Rui Wang, Timo Sachsenberg, Julian Uszkoreit, Felipe da Veiga Leprevost, Christian Fufezan, Tobias Ternent, Stephen J Eglen, Daniel S Katz, \ldots{} Juan Antonio Vizcaíno} \emph{PLOS Computational Biology} (2016-07-14) \url{https://doi.org/gbrb39}
\CSLBlock{DOI: \href{https://doi.org/10.1371/journal.pcbi.1004947}{10.1371/journal.pcbi.1004947} · PMID: \href{https://www.ncbi.nlm.nih.gov/pubmed/27415786}{27415786} · PMCID: \href{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC4945047}{PMC4945047}}}

\leavevmode\vadjust pre{\hypertarget{ref-PlcxShQU}{}}%
\CSLLeftMargin{10. }
\CSLRightInline{\textbf{A Quick Introduction to Version Control with Git and GitHub}
\CSLBlock{John D Blischak, Emily R Davenport, Greg Wilson} \emph{PLOS Computational Biology} (2016-01-19) \url{https://doi.org/gbqsnf}
\CSLBlock{DOI: \href{https://doi.org/10.1371/journal.pcbi.1004668}{10.1371/journal.pcbi.1004668} · PMID: \href{https://www.ncbi.nlm.nih.gov/pubmed/26785377}{26785377} · PMCID: \href{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC4718703}{PMC4718703}}}

\leavevmode\vadjust pre{\hypertarget{ref-NIS0JOW0}{}}%
\CSLLeftMargin{11. }
\CSLRightInline{\textbf{Learn Git In 15 Minutes} \url{https://www.youtube.com/watch?v=USjZcfj8yxE}}

\leavevmode\vadjust pre{\hypertarget{ref-13jOlVcpp}{}}%
\CSLLeftMargin{12. }
\CSLRightInline{\textbf{Let's Git started \textbar{} Happy Git and GitHub for the useR}
\CSLBlock{Jenny Bryan Hester the STAT 545 TAs, Jim} \url{https://happygitwithr.com/}}

\leavevmode\vadjust pre{\hypertarget{ref-u5aEVE4B}{}}%
\CSLLeftMargin{13. }
\CSLRightInline{\textbf{Coding Club: A Positive Peer-Learning Community} \url{https://ourcodingclub.github.io/}}

\leavevmode\vadjust pre{\hypertarget{ref-3DKwn1sY}{}}%
\CSLLeftMargin{14. }
\CSLRightInline{\textbf{Our path to better science in less time using open data science tools}
\CSLBlock{Julia SStewart Lowndes, Benjamin D Best, Courtney Scarborough, Jamie C Afflerbach, Melanie R Frazier, Casey C O'Hara, Ning Jiang, Benjamin S Halpern} \emph{Nature Ecology \&amp; Evolution} (2017-05-23) \url{https://doi.org/gc4jb3}
\CSLBlock{DOI: \href{https://doi.org/10.1038/s41559-017-0160}{10.1038/s41559-017-0160} · PMID: \href{https://www.ncbi.nlm.nih.gov/pubmed/28812630}{28812630}}}

\leavevmode\vadjust pre{\hypertarget{ref-139b0pSGc}{}}%
\CSLLeftMargin{15. }
\CSLRightInline{\textbf{Social network of software development at GitHub}
\CSLBlock{William Leibzon} \emph{2016 IEEE/ACM International Conference on Advances in Social Networks Analysis and Mining (ASONAM)} (2016-08) \url{https://doi.org/gph5qt}
\CSLBlock{DOI: \href{https://doi.org/10.1109/asonam.2016.7752419}{10.1109/asonam.2016.7752419}}}

\leavevmode\vadjust pre{\hypertarget{ref-ydrk01SR}{}}%
\CSLLeftMargin{16. }
\CSLRightInline{\textbf{Foundational Practices of Research Data Management}
\CSLBlock{Kristin Briney, Heather Coates, Abigail Goben} \emph{Research Ideas and Outcomes} (2020-07-27) \url{https://doi.org/ghssbk}
\CSLBlock{DOI: \href{https://doi.org/10.3897/rio.6.e56508}{10.3897/rio.6.e56508}}}

\leavevmode\vadjust pre{\hypertarget{ref-13QX8XU3J}{}}%
\CSLLeftMargin{17. }
\CSLRightInline{\textbf{A Beginner's Guide to Conducting Reproducible Research}
\CSLBlock{Jesse M Alston, Jessica A Rick} \emph{The Bulletin of the Ecological Society of America} (2021-01-15) \url{https://doi.org/gk5v4p}
\CSLBlock{DOI: \href{https://doi.org/10.1002/bes2.1801}{10.1002/bes2.1801}}}

\leavevmode\vadjust pre{\hypertarget{ref-MwwMapRG}{}}%
\CSLLeftMargin{18. }
\CSLRightInline{\textbf{Packaging Data Analytical Work Reproducibly Using R (and Friends)}
\CSLBlock{Ben Marwick, Carl Boettiger, Lincoln Mullen} \emph{The American Statistician} (2018-01-02) \url{https://doi.org/gdhvm8}
\CSLBlock{DOI: \href{https://doi.org/10.1080/00031305.2017.1375986}{10.1080/00031305.2017.1375986}}}

\leavevmode\vadjust pre{\hypertarget{ref-1Co6ZZjF1}{}}%
\CSLLeftMargin{19. }
\CSLRightInline{\textbf{About large files on GitHub}
\CSLBlock{GitHub Docs} \url{https://ghdocs-prod.azurewebsites.net/en/repositories/working-with-files/managing-large-files/about-large-files-on-github}}

\leavevmode\vadjust pre{\hypertarget{ref-wwHxTOtm}{}}%
\CSLLeftMargin{20. }
\CSLRightInline{\textbf{Electronic lab notebooks: can they replace paper?}
\CSLBlock{Samantha Kanza, Cerys Willoughby, Nicholas Gibbins, Richard Whitby, Jeremy Graham Frey, Jana Erjavec, Klemen Zupančič, Matjaž Hren, Katarina Kovač} \emph{Journal of Cheminformatics} (2017-05-24) \url{https://doi.org/gfz287}
\CSLBlock{DOI: \href{https://doi.org/10.1186/s13321-017-0221-3}{10.1186/s13321-017-0221-3} · PMID: \href{https://www.ncbi.nlm.nih.gov/pubmed/29086051}{29086051} · PMCID: \href{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC5443717}{PMC5443717}}}

\leavevmode\vadjust pre{\hypertarget{ref-10V7x4H4l}{}}%
\CSLLeftMargin{21. }
\CSLRightInline{\textbf{Ten Simple Rules for a Computational Biologist's Laboratory Notebook}
\CSLBlock{Santiago Schnell} \emph{PLOS Computational Biology} (2015-09-10) \url{https://doi.org/gf5fnr}
\CSLBlock{DOI: \href{https://doi.org/10.1371/journal.pcbi.1004385}{10.1371/journal.pcbi.1004385} · PMID: \href{https://www.ncbi.nlm.nih.gov/pubmed/26356732}{26356732} · PMCID: \href{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC4565690}{PMC4565690}}}

\leavevmode\vadjust pre{\hypertarget{ref-RhBKe0MG}{}}%
\CSLLeftMargin{22. }
\CSLRightInline{\textbf{About projects (beta)}
\CSLBlock{GitHub Docs} \url{https://ghdocs-prod.azurewebsites.net/en/issues/trying-out-the-new-projects-experience/about-projects}}

\leavevmode\vadjust pre{\hypertarget{ref-QqMezOMg}{}}%
\CSLLeftMargin{23. }
\CSLRightInline{\textbf{R Markdown: the definitive guide}
\CSLBlock{Yihui Xie, JJ Allaire, Garrett Grolemund} \emph{CRC Press, Taylor and Francis Group} (2019)
\CSLBlock{ISBN: 9780429782961}}

\leavevmode\vadjust pre{\hypertarget{ref-MXxgZJ45}{}}%
\CSLLeftMargin{24. }
\CSLRightInline{\textbf{Building tools with GitHub: customize your workflow}
\CSLBlock{Chris Dawson} \emph{O'Reilly} (2016)
\CSLBlock{ISBN: 9781491933503}}

\leavevmode\vadjust pre{\hypertarget{ref-1Du6fzB8g}{}}%
\CSLLeftMargin{25. }
\CSLRightInline{\textbf{A Guide to Using GitHub for Developing and Versioning Data Standards and Reporting Formats}
\CSLBlock{Robert Crystal‐Ornelas, Charuleka Varadharajan, Ben Bond‐Lamberty, Kristin Boye, Madison Burrus, Shreyas Cholia, Michael Crow, Joan Damerow, Ranjeet Devarakonda, Kim S Ely, \ldots{} Deborah A Agarwal} \emph{Earth and Space Science} (2021-08) \url{https://doi.org/gmbs9c}
\CSLBlock{DOI: \href{https://doi.org/10.1029/2021ea001797}{10.1029/2021ea001797}}}

\leavevmode\vadjust pre{\hypertarget{ref-iIEKCTLU}{}}%
\CSLLeftMargin{26. }
\CSLRightInline{\textbf{The Tao of open science for ecology}
\CSLBlock{Stephanie E Hampton, Sean S Anderson, Sarah C Bagby, Corinna Gries, Xueying Han, Edmund M Hart, Matthew B Jones, WChristopher Lenhardt, Andrew MacDonald, William K Michener, \ldots{} Naupaka Zimmerman} \emph{Ecosphere} (2015-07) \url{https://doi.org/gdj5w6}
\CSLBlock{DOI: \href{https://doi.org/10.1890/es14-00402.1}{10.1890/es14-00402.1}}}

\leavevmode\vadjust pre{\hypertarget{ref-uBJwnPbq}{}}%
\CSLLeftMargin{27. }
\CSLRightInline{\textbf{Elevating The Status of Code in Ecology}
\CSLBlock{KAS Mislan, Jeffrey M Heer, Ethan P White} \emph{Trends in Ecology \&amp; Evolution} (2016-01) \url{https://doi.org/gg43mk}
\CSLBlock{DOI: \href{https://doi.org/10.1016/j.tree.2015.11.006}{10.1016/j.tree.2015.11.006} · PMID: \href{https://www.ncbi.nlm.nih.gov/pubmed/26704455}{26704455}}}

\leavevmode\vadjust pre{\hypertarget{ref-1HZdsK5Kn}{}}%
\CSLLeftMargin{28. }
\CSLRightInline{\textbf{1,500 scientists lift the lid on reproducibility}
\CSLBlock{Monya Baker} \emph{Nature} (2016-05-25) \url{https://doi.org/gdgzjx}
\CSLBlock{DOI: \href{https://doi.org/10.1038/533452a}{10.1038/533452a} · PMID: \href{https://www.ncbi.nlm.nih.gov/pubmed/27225100}{27225100}}}

\leavevmode\vadjust pre{\hypertarget{ref-K7nbP1Ty}{}}%
\CSLLeftMargin{29. }
\CSLRightInline{\textbf{Not just for programmers: How GitHub can accelerate collaborative and reproducible research in ecology and evolution}
\CSLBlock{Robert Crystal-Ornelas, Brandon PM Edwards, Katherine Hébert, Friederike Hillemann, Emma J Hudgins, Luna LSánchez Reyes, Eric R Scott, Matthew J Grainger, Vivienne Foroughirad, Allison D Binley, \ldots{} Pedro Henrique Pereira Braga} \emph{Manubot} (2022-06-08) \url{https://SORTEE-Github-Hackathon.github.io/manuscript/}}

\leavevmode\vadjust pre{\hypertarget{ref-hm9PaCLD}{}}%
\CSLLeftMargin{30. }
\CSLRightInline{\textbf{Using Peer Code Review as an Educational Tool}
\CSLBlock{Xiangyu Song, Seth Copen Goldstein, Majd Sakr} \emph{Proceedings of the 2020 ACM Conference on Innovation and Technology in Computer Science Education} (2020-06-02) \url{https://doi.org/gp58rg}
\CSLBlock{DOI: \href{https://doi.org/10.1145/3341525.3387370}{10.1145/3341525.3387370}}}

\leavevmode\vadjust pre{\hypertarget{ref-YuJbg3zO}{}}%
\CSLLeftMargin{31. }
\CSLRightInline{\textbf{Open collaborative writing with Manubot}
\CSLBlock{Daniel S Himmelstein, Vincent Rubinetti, David R Slochower, Dongbo Hu, Venkat S Malladi, Casey S Greene, Anthony Gitter} \emph{PLOS Computational Biology} (2019-06-24) \url{https://doi.org/c7np}
\CSLBlock{DOI: \href{https://doi.org/10.1371/journal.pcbi.1007128}{10.1371/journal.pcbi.1007128} · PMID: \href{https://www.ncbi.nlm.nih.gov/pubmed/31233491}{31233491} · PMCID: \href{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC6611653}{PMC6611653}}}

\leavevmode\vadjust pre{\hypertarget{ref-i4FOZpjN}{}}%
\CSLLeftMargin{32. }
\CSLRightInline{\textbf{Creating an executable paper is a journey through Open Science}
\CSLBlock{Jana Lasser} \emph{Communications Physics} (2020-08-19) \url{https://doi.org/gg89zd}
\CSLBlock{DOI: \href{https://doi.org/10.1038/s42005-020-00403-4}{10.1038/s42005-020-00403-4}}}

\leavevmode\vadjust pre{\hypertarget{ref-Xsdcv6q}{}}%
\CSLLeftMargin{33. }
\CSLRightInline{\textbf{rfishbase: exploring, manipulating and visualizing FishBase data from R}
\CSLBlock{C Boettiger, DT Lang, PC Wainwright} \emph{Journal of Fish Biology} (2012-11) \url{https://doi.org/gh5x27}
\CSLBlock{DOI: \href{https://doi.org/10.1111/j.1095-8649.2012.03464.x}{10.1111/j.1095-8649.2012.03464.x} · PMID: \href{https://www.ncbi.nlm.nih.gov/pubmed/23130696}{23130696}}}

\leavevmode\vadjust pre{\hypertarget{ref-FVBWKkZu}{}}%
\CSLLeftMargin{34. }
\CSLRightInline{\textbf{taxize: taxonomic search and retrieval in R}
\CSLBlock{Scott A Chamberlain, Eduard Szöcs} \emph{F1000Research} (2013-10-28) \url{https://doi.org/ggdskx}
\CSLBlock{DOI: \href{https://doi.org/10.12688/f1000research.2-191.v2}{10.12688/f1000research.2-191.v2} · PMID: \href{https://www.ncbi.nlm.nih.gov/pubmed/24555091}{24555091} · PMCID: \href{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC3901538}{PMC3901538}}}

\leavevmode\vadjust pre{\hypertarget{ref-18PTmKJkq}{}}%
\CSLLeftMargin{35. }
\CSLRightInline{\textbf{\#PruittData and the Ethics of Data in Science}
\CSLBlock{Professor Lee BKass January 18, 2022 2:51 Pm} \emph{Ecology for the Masses} (2020-02-04) \url{https://ecologyforthemasses.com/2020/02/04/pruittdata-and-the-ethics-of-data-in-science/}}

\leavevmode\vadjust pre{\hypertarget{ref-NOgBWVAr}{}}%
\CSLLeftMargin{36. }
\CSLRightInline{\textbf{Low availability of code in ecology: A~call for urgent action}
\CSLBlock{Antica Culina, Ilona van den Berg, Simon Evans, Alfredo Sánchez-Tójar} \emph{PLOS Biology} (2020-07-28) \url{https://doi.org/gg6rgf}
\CSLBlock{DOI: \href{https://doi.org/10.1371/journal.pbio.3000763}{10.1371/journal.pbio.3000763} · PMID: \href{https://www.ncbi.nlm.nih.gov/pubmed/32722681}{32722681} · PMCID: \href{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC7386629}{PMC7386629}}}

\leavevmode\vadjust pre{\hypertarget{ref-D4C4k4ak}{}}%
\CSLLeftMargin{37. }
\CSLRightInline{\textbf{Sustainable Research Software Hand-Over}
\CSLBlock{J Fehr, C Himpe, S Rave, J Saak} \emph{Journal of Open Research Software} (2021-04-30) \url{https://doi.org/g4n4}
\CSLBlock{DOI: \href{https://doi.org/10.5334/jors.307}{10.5334/jors.307}}}

\leavevmode\vadjust pre{\hypertarget{ref-s91uGRZ2}{}}%
\CSLLeftMargin{38. }
\CSLRightInline{\textbf{About code owners}
\CSLBlock{GitHub Docs} \url{https://ghdocs-prod.azurewebsites.net/en/repositories/managing-your-repositorys-settings-and-features/customizing-your-repository/about-code-owners}}

\leavevmode\vadjust pre{\hypertarget{ref-UsTxAq4f}{}}%
\CSLLeftMargin{39. }
\CSLRightInline{\textbf{A collaborative GIS programming course using GitHub Classroom}
\CSLBlock{Berk Anbaroğlu} \emph{Transactions in GIS} (2021-07-21) \url{https://doi.org/gp44fx}
\CSLBlock{DOI: \href{https://doi.org/10.1111/tgis.12810}{10.1111/tgis.12810}}}

\leavevmode\vadjust pre{\hypertarget{ref-lx49NGto}{}}%
\CSLLeftMargin{40. }
\CSLRightInline{\textbf{Connect GitHub to a Project - OSF Support} \url{https://help.osf.io/article/211-connect-github-to-a-project}}

\leavevmode\vadjust pre{\hypertarget{ref-pjy75gHr}{}}%
\CSLLeftMargin{41. }
\CSLRightInline{\textbf{swcarpentry/git-novice: Software Carpentry: Version Control with Git, June 2019}
\CSLBlock{Madicken Munk, Katherine Koziar, Katrin Leinweber, Raniere Silva, François Michonneau, Rich McCue, Nima Hejazi, Simon Waldman, Rémi Emonet, Rayna Michelle Harris, \ldots{} Wolmar Nyberg Åkerström} \emph{Zenodo} (2019-07-01) \url{https://doi.org/gp44fz}
\CSLBlock{DOI: \href{https://doi.org/10.5281/zenodo.3264950}{10.5281/zenodo.3264950}}}

\leavevmode\vadjust pre{\hypertarget{ref-ZvrOcg9w}{}}%
\CSLLeftMargin{42. }
\CSLRightInline{\textbf{Let's Git started \textbar{} Happy Git and GitHub for the useR}
\CSLBlock{Jenny Bryan Hester the STAT 545 TAs, Jim} \url{https://happygitwithr.com/}}

\leavevmode\vadjust pre{\hypertarget{ref-6CMMeSeD}{}}%
\CSLLeftMargin{43. }
\CSLRightInline{\textbf{STAT 545}
\CSLBlock{Jenny Bryan, The STAT 545 TAs} \url{https://stat545.com/}}

\end{CSLReferences}

### 2022-06-08 manuscript.tex
Changing default CSL to Nature EcoEvol CSL [ci skip]
This build is based on
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/eafc396e1f32d378749c27716bfc058f4802928f.

This commit was created by the following CI build and job:
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/eafc396e1f32d378749c27716bfc058f4802928f/checks
https://github.com/SORTEE-Github-Hackathon/manuscript/actions/runs/2463521591

@@
 This manuscript
-(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/402617f9e4b0caf2a3e126b79bf17059d3cfef8c/}{permalink})
+(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/eafc396e1f32d378749c27716bfc058f4802928f/}{permalink})
 was automatically generated
-from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/402617f9e4b0caf2a3e126b79bf17059d3cfef8c}{SORTEE-Github-Hackathon/manuscript@402617f}
+from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/eafc396e1f32d378749c27716bfc058f4802928f}{SORTEE-Github-Hackathon/manuscript@eafc396}
 on June 8, 2022.
@@
 
-Most scientists, including ecologists and evolutionary biologists, are increasingly dependent on computational tools in their research {[}\protect\hyperlink{ref-fJWFe93e}{1}{]}.
+Most scientists, including ecologists and evolutionary biologists, are increasingly dependent on computational tools in their research\textsuperscript{\protect\hyperlink{ref-fJWFe93e}{1}}.
 Researchers write and use code as part of their scientific workflow to perform a wide-variety of tasks ranging from data management, data analysis, and study replication, to the application and the development of tools for hypothesis testing.
-To maintain code for scientific collaboration requires an efficient and well-documented work-flow {[}\protect\hyperlink{ref-1Kqna6l2}{2}{]}.
-To facilitate this process, scientists have been increasingly adopting tools from information and systems technology, such as cloud-based services for documentation and version control (\emph{e.g.}, from the Google Suite, with Docs, Sheets, and Drive; the Microsoft Suite, with Word, Excel, and OneDrive; and GitHub; {[}\protect\hyperlink{ref-10ghgV3S8}{3}{]}).
-However, most researchers lack exposure to adequate software development practices and are required to dedicate valuable time and effort to self-teach the use of research-facilitating tools, and thus may be limited in their ability to adhere to adequate standards of scientific code quality and maintenance {[}\protect\hyperlink{ref-fJWFe93e}{1},\protect\hyperlink{ref-10SpoByIw}{4},\protect\hyperlink{ref-O6UbstGG}{5}{]}.
+To maintain code for scientific collaboration requires an efficient and well-documented work-flow\textsuperscript{\protect\hyperlink{ref-1Kqna6l2}{2}}.
+To facilitate this process, scientists have been increasingly adopting tools from information and systems technology, such as cloud-based services for documentation and version control (\emph{e.g.}, from the Google Suite, with Docs, Sheets, and Drive; the Microsoft Suite, with Word, Excel, and OneDrive; and GitHub;\textsuperscript{\protect\hyperlink{ref-10ghgV3S8}{3}}).
+However, most researchers lack exposure to adequate software development practices and are required to dedicate valuable time and effort to self-teach the use of research-facilitating tools, and thus may be limited in their ability to adhere to adequate standards of scientific code quality and maintenance\textsuperscript{\protect\hyperlink{ref-fJWFe93e}{1},\protect\hyperlink{ref-10SpoByIw}{4},\protect\hyperlink{ref-O6UbstGG}{5}}.
 Here, we review and discuss one of the most used web-based platforms for computational version control and collaboration, GitHub, and provide researchers in ecology and evolutionary biology (EEB) with practical workflows aimed at facilitating their scientific code and management process.
 
-With over 73 million registered users, as of 2022, GitHub is the most widely-used web platform for collaborating on computer code {[}\protect\hyperlink{ref-nwCtHDCn}{6}{]}.
+With over 73 million registered users, as of 2022, GitHub is the most widely-used web platform for collaborating on computer code\textsuperscript{\protect\hyperlink{ref-nwCtHDCn}{6}}.
 GitHub provides a simplified but powerful web interface that allows users to participate in projects, contribute code, report and discuss software bugs, discover existing code and data, and publish new code.
-Through version control, users have a detailed, chronological record of the files and directories stored in their repositories (see \protect\hyperlink{definitions}{Box 1}; {[}\protect\hyperlink{ref-RVetqmsg}{7}{]}).
-This workflow provides a strong and clear advantage over receiving, processing and sending files back-and-forth (e.g.~via email), a process that can easily become challenging and time-consuming in projects extending in time and in the number of collaborators {[}\protect\hyperlink{ref-4ny1onB0}{8}{]}.
-Through the combination of version control management and the network- and collaboration-based features, GitHub can broadly facilitate openly available source code alongside concomitant collaborative development {[}\protect\hyperlink{ref-kEX5dgzK}{9}{]}.
+Through version control, users have a detailed, chronological record of the files and directories stored in their repositories (see \protect\hyperlink{definitions}{Box 1};\textsuperscript{\protect\hyperlink{ref-RVetqmsg}{7}}).
+This workflow provides a strong and clear advantage over receiving, processing and sending files back-and-forth (e.g.~via email), a process that can easily become challenging and time-consuming in projects extending in time and in the number of collaborators\textsuperscript{\protect\hyperlink{ref-4ny1onB0}{8}}.
+Through the combination of version control management and the network- and collaboration-based features, GitHub can broadly facilitate openly available source code alongside concomitant collaborative development\textsuperscript{\protect\hyperlink{ref-kEX5dgzK}{9}}.
 
@@
 Still, GitHub users are encouraged to explore and improve their proficiency in Git when feeling comfortable, so they can feel confident in performing more flexible, complex operations (such as integrating changes from one branch into another branch with \texttt{git\ merge} and \texttt{git\ rebase}).
-Examples of extensive explanations on Git can be found in journal articles {[}\protect\hyperlink{ref-kEX5dgzK}{9},\protect\hyperlink{ref-PlcxShQU}{10}{]}, video tutorials {[}\protect\hyperlink{ref-NIS0JOW0}{11}{]}, and books {[}\protect\hyperlink{ref-13jOlVcpp}{12}{]}.
-
-The expansive GitHub user-community and the numerous resources on how to use GitHub have boosted its growing popularity {[}\protect\hyperlink{ref-RVetqmsg}{7},\protect\hyperlink{ref-kEX5dgzK}{9},\protect\hyperlink{ref-13jOlVcpp}{12}/,\protect\hyperlink{ref-u5aEVE4B}{13}{]}.
-Nevertheless, although multiple articles have encouraged researchers in EEB to adopt GitHub as part of their research process {[}\protect\hyperlink{ref-10ghgV3S8}{3},\protect\hyperlink{ref-3DKwn1sY}{14}{]}, its use is still not widespread.
-First-time users without formal training in information technology may face steep learning curves because GitHub and its features have been centered on collaboration for software development in information systems {[}\protect\hyperlink{ref-139b0pSGc}{15}{]}.
+Examples of extensive explanations on Git can be found in journal articles\textsuperscript{\protect\hyperlink{ref-kEX5dgzK}{9},\protect\hyperlink{ref-PlcxShQU}{10}}, video tutorials\textsuperscript{\protect\hyperlink{ref-NIS0JOW0}{11}}, and books\textsuperscript{\protect\hyperlink{ref-13jOlVcpp}{12}}.
+
+The expansive GitHub user-community and the numerous resources on how to use GitHub have boosted its growing popularity\textsuperscript{\protect\hyperlink{ref-RVetqmsg}{7},\protect\hyperlink{ref-kEX5dgzK}{9},\protect\hyperlink{ref-13jOlVcpp}{12}/,\protect\hyperlink{ref-u5aEVE4B}{13}}.
+Nevertheless, although multiple articles have encouraged researchers in EEB to adopt GitHub as part of their research process\textsuperscript{\protect\hyperlink{ref-10ghgV3S8}{3},\protect\hyperlink{ref-3DKwn1sY}{14}}, its use is still not widespread.
+First-time users without formal training in information technology may face steep learning curves because GitHub and its features have been centered on collaboration for software development in information systems\textsuperscript{\protect\hyperlink{ref-139b0pSGc}{15}}.
 Moreover, domain-specific perspectives and resources providing tractable examples and practical guidance for researchers in EEB on GitHub are scarce (but see https://ourcodingclub.github.io; https://www.openscapes.org).
-A common adoption of GitHub for collaborating on a variety of research tasks can ultimately enable EEB researchers to spend less time on creating novel processes for collaboration and more time on their research {[}\protect\hyperlink{ref-ydrk01SR}{16}{]}.
-More importantly, increasing the availability of data and code management standards -- of which GitHub is one increasingly important component -- make research more reproducible and collaborative {[}\protect\hyperlink{ref-13QX8XU3J}{17}{]}.
+A common adoption of GitHub for collaborating on a variety of research tasks can ultimately enable EEB researchers to spend less time on creating novel processes for collaboration and more time on their research\textsuperscript{\protect\hyperlink{ref-ydrk01SR}{16}}.
+More importantly, increasing the availability of data and code management standards -- of which GitHub is one increasingly important component -- make research more reproducible and collaborative\textsuperscript{\protect\hyperlink{ref-13QX8XU3J}{17}}.
 
@@
 Having multiple copies of these files is important to ensure that research can continue should one copy of a file be accidentally modified or deleted.
-Many researchers begin using GitHub as a means to backup their research compendium {[}\protect\hyperlink{ref-MwwMapRG}{18}{]} to a remote server (pull-commit-push, see \protect\hyperlink{definitions}{Box 1}).
+Many researchers begin using GitHub as a means to backup their research compendium\textsuperscript{\protect\hyperlink{ref-MwwMapRG}{18}} to a remote server (pull-commit-push, see \protect\hyperlink{definitions}{Box 1}).
 The GitHub repository serves as a centralized backup and also allows users to synchronize files and work on any device with internet access.
@@
 Unfortunately, GitHub repositories have file size limits, so they may not be appropriate for synchronizing large data files.
-Commits (see \protect\hyperlink{definitions}{Box 1}{]}) greater than 50 MB receive a warning and commits larger than 100 MB are blocked ({[}\protect\hyperlink{ref-1Co6ZZjF1}{19}{]}).
+Commits (see \protect\hyperlink{definitions}{Box 1}{]}) greater than 50 MB receive a warning and commits larger than 100 MB are blocked (\textsuperscript{\protect\hyperlink{ref-1Co6ZZjF1}{19}}).
 Therefore, it is recommended that large datasets are stored only locally or using other cloud services.
@@
 
-Lab notebooks are the virtual or physical notebooks used to help researchers at any career stage keep track of their research methods or laboratory policies {[}\protect\hyperlink{ref-wwHxTOtm}{20}{]}.
-Digital lab notebooks stored in the cloud provide clear benefits given the ease with which documents can be shared with new employees and updated as policy changes or experimental methods are modified {[}\protect\hyperlink{ref-10V7x4H4l}{21}{]}.
-Increasingly, researchers are leveraging GitHub's underlying version control system to maintain and share digital lab notebooks {[}\protect\hyperlink{ref-10ghgV3S8}{3}{]}.
+Lab notebooks are the virtual or physical notebooks used to help researchers at any career stage keep track of their research methods or laboratory policies\textsuperscript{\protect\hyperlink{ref-wwHxTOtm}{20}}.
+Digital lab notebooks stored in the cloud provide clear benefits given the ease with which documents can be shared with new employees and updated as policy changes or experimental methods are modified\textsuperscript{\protect\hyperlink{ref-10V7x4H4l}{21}}.
+Increasingly, researchers are leveraging GitHub's underlying version control system to maintain and share digital lab notebooks\textsuperscript{\protect\hyperlink{ref-10ghgV3S8}{3}}.
 At least for aspects of a research project that involve writing code, a GitHub repository is a form of a lab notebook; when changes are made to files in a version controlled repository, the author of those changes makes a commit (\protect\hyperlink{definitions}{Box 1}) accompanied by a message describing the changes and the reason for them.
-Later, the entire history of commits and their messages are viewable and can be audited similar to a physical lab notebook {[}\protect\hyperlink{ref-4ny1onB0}{8}{]}.
+Later, the entire history of commits and their messages are viewable and can be audited similar to a physical lab notebook\textsuperscript{\protect\hyperlink{ref-4ny1onB0}{8}}.
 GitHub issues (\protect\hyperlink{definitions}{Box 1}) can be used to prioritize lab objectives and goals, as well as track any status updates.
@@
 ZenHub's web interface includes a GitHub Issue visualizer where users can organize issues into high priority or backlogged tasks and link issues together when they are related to a shared project goal or milestone.
-GitHub is currently beta testing a similar project management feature called GitHub Projects {[}\protect\hyperlink{ref-RhBKe0MG}{22}{]}.
+GitHub is currently beta testing a similar project management feature called GitHub Projects\textsuperscript{\protect\hyperlink{ref-RhBKe0MG}{22}}.
 GitHub can also be integrated with other project management software such as Slack (https://slack.github.com/) so that teams are notified through a Slack group chat when updates are made to a repository.
@@
 
-Making presentations can be done through most major high-level programming languages such as R, with \texttt{RMarkdown} {[}\protect\hyperlink{ref-QqMezOMg}{23}{]}, Python, with \texttt{python-ppt} (\url{https://python-pptx.readthedocs.io}), and Julia, with \texttt{Remark.jl} (\url{https://juliapackages.com/p/remark}).
+Making presentations can be done through most major high-level programming languages such as R, with \texttt{RMarkdown}\textsuperscript{\protect\hyperlink{ref-QqMezOMg}{23}}, Python, with \texttt{python-ppt} (\url{https://python-pptx.readthedocs.io}), and Julia, with \texttt{Remark.jl} (\url{https://juliapackages.com/p/remark}).
 Since all these programs work via code bases, they can be version-controlled through git and GitHub.
@@
 GitHub also offers website templates and it is possible to create a website by forking (\protect\hyperlink{definitions}{Box 1}) a repository hosting a GitHub Pages site as a starting point.
-Aside from free hosting services, another benefit is that GitHub Pages are autogenerated, meaning that when content is modified in the associated GitHub repository, the website instantly updates {[}\protect\hyperlink{ref-RVetqmsg}{7}{]}.
-Though the templates are useful for quickly starting up a new website, users are able to fully customize their Pages websites (for technical details of customizing GitHub Pages site see {[}\protect\hyperlink{ref-MXxgZJ45}{24}{]}).
+Aside from free hosting services, another benefit is that GitHub Pages are autogenerated, meaning that when content is modified in the associated GitHub repository, the website instantly updates\textsuperscript{\protect\hyperlink{ref-RVetqmsg}{7}}.
+Though the templates are useful for quickly starting up a new website, users are able to fully customize their Pages websites (for technical details of customizing GitHub Pages site see\textsuperscript{\protect\hyperlink{ref-MXxgZJ45}{24}}).
 We emphasize that despite the many benefits of using GitHub pages (free hosting, templates, customization), this avenue for creating a website will often be more time intensive than the out-of-the-box platforms.
@@
 If a repository is made ``public'' the URL to the repository can be shared freely with others.
-However, for a variety of reasons (e.g., privately owned company, ability to make repositories private, accounts can be deleted at will) GitHub is not considered a long-term data or code repository like Zenodo and Figshare {[}\protect\hyperlink{ref-10ghgV3S8}{3},\protect\hyperlink{ref-kEX5dgzK}{9},\protect\hyperlink{ref-tbl:compare}{\textbf{tbl:compare?}}{]}.
+However, for a variety of reasons (e.g., privately owned company, ability to make repositories private, accounts can be deleted at will) GitHub is not considered a long-term data or code repository like Zenodo and Figshare\textsuperscript{\protect\hyperlink{ref-10ghgV3S8}{3},\protect\hyperlink{ref-kEX5dgzK}{9},\protect\hyperlink{ref-tbl:compare}{\textbf{tbl:compare?}}}.
 Also, unlike long-term repositories, GitHub does not issue Digital Object Identifiers (DOIs) for content uploaded to their servers.
@@
 DOIs allows tracking and citing research products.
-For this reason, scientists who share code and data through GitHub are strongly encouraged to also submit GitHub repository content to a long-term data archive {[}\protect\hyperlink{ref-1Du6fzB8g}{25}{]}.
+For this reason, scientists who share code and data through GitHub are strongly encouraged to also submit GitHub repository content to a long-term data archive\textsuperscript{\protect\hyperlink{ref-1Du6fzB8g}{25}}.
 Fortunately, both long-term repositories mentioned above (Zenodo and Figshare) have integrations with GitHub.
 After linking one's GitHub repository to Zenodo or Figshare, every time a release (\protect\hyperlink{definitions}{Box 1}) is made, a snapshot of the entire repository is archived with a versioned, citable DOI.
-Linking one's GitHub repository with Zenodo, etc. to obtain a DOI helps work become findable, gives proper attribution, and can ensure long-term stability {[}\protect\hyperlink{ref-iIEKCTLU}{26}{]}.
+Linking one's GitHub repository with Zenodo, etc.
+to obtain a DOI helps work become findable, gives proper attribution, and can ensure long-term stability\textsuperscript{\protect\hyperlink{ref-iIEKCTLU}{26}}.
 
@@
 However, there are many reasons to share data and code beyond re-use.
-Even if code lacks detailed annotation, it shows the exact steps taken to conduct an analysis, and therefore provides the most detailed look into how to reproduce a given analysis {[}\protect\hyperlink{ref-uBJwnPbq}{27}{]}.
-This is important in light of the reproducibility crisis {[}\protect\hyperlink{ref-1HZdsK5Kn}{28}{]} and will become increasingly important to the collective scientific enterprise as advances in computing power and accessibility unlock the ability to conduct `big data' meta research with data that has already been collected by others.
+Even if code lacks detailed annotation, it shows the exact steps taken to conduct an analysis, and therefore provides the most detailed look into how to reproduce a given analysis\textsuperscript{\protect\hyperlink{ref-uBJwnPbq}{27}}.
+This is important in light of the reproducibility crisis\textsuperscript{\protect\hyperlink{ref-1HZdsK5Kn}{28}} and will become increasingly important to the collective scientific enterprise as advances in computing power and accessibility unlock the ability to conduct `big data' meta research with data that has already been collected by others.
 Failing to include data and code with publications leaves future scientists with fewer open resources from which to understand the world.
@@
 When EEB projects are contained on the GitHub platform, researchers can stay abreast of progress made by other collaborators without the need for meetings or emails.
-Version control {[}\protect\hyperlink{ref-K7nbP1Ty}{29}{]} features also allow users to make progress and changes without worrying about irreparably writing over someone else's work.
+Version control\textsuperscript{\protect\hyperlink{ref-K7nbP1Ty}{29}} features also allow users to make progress and changes without worrying about irreparably writing over someone else's work.
 By enabling more comprehensive remote collaboration, GitHub encourages the exchange of ideas among researchers at different institutions and in different countries, which can serve to improve the quality of the research itself by providing open access to data and code.
 In academic settings, GitHub can also facilitate interactions between research advisors and advisees, providing a platform for students or other trainees to share in-progress code, and flag specific challenges or questions for their supervisors or mentors.
-Periodic code review {[}\protect\hyperlink{ref-hm9PaCLD}{30}{]} can also help advisors identify errors early in the process, and inform further training and mentorship to fill gaps in skills.
+Periodic code review\textsuperscript{\protect\hyperlink{ref-hm9PaCLD}{30}} can also help advisors identify errors early in the process, and inform further training and mentorship to fill gaps in skills.
 
@@
 
-While GitHub is not considered as user-friendly for manuscript development as conventional text processors {[}\protect\hyperlink{ref-4ny1onB0}{8}{]}, it has been substantially improved with recent tools.
+While GitHub is not considered as user-friendly for manuscript development as conventional text processors\textsuperscript{\protect\hyperlink{ref-4ny1onB0}{8}}, it has been substantially improved with recent tools.
 Manuscripts can be written on GitHub with Markdown.
@@
 
-We wrote this manuscript using Manubot {[}\protect\hyperlink{ref-YuJbg3zO}{31}{]}, a collaborative manuscript platform that uses Markdown for writing and GitHub for storing and tracking changes to a manuscript over time.
+We wrote this manuscript using Manubot\textsuperscript{\protect\hyperlink{ref-YuJbg3zO}{31}}, a collaborative manuscript platform that uses Markdown for writing and GitHub for storing and tracking changes to a manuscript over time.
 Manubot uses a GitHub Actions-based typesetting system to compile individual Markdown files stored in a GitHub repository into a single LaTeX document, which can be displayed in Word, HTML, or PDF formats.
@@
 Manubot also allows for straightforward citation management based on URLs or DOIs.
-For more examples of Manubot being used for manuscripts, see {[}\protect\hyperlink{ref-YuJbg3zO}{31}{]}.
+For more examples of Manubot being used for manuscripts, see\textsuperscript{\protect\hyperlink{ref-YuJbg3zO}{31}}.
 
@@
 Other authors can reply to the comments to indicate agreement or disagreement, and to note when changes have been made.
-Other tools can also be used for version control of scientific manuscripts including R Markdown via the bookdown package (\url{https://bookdown.org/}), jupyter notebooks {[}\protect\hyperlink{ref-i4FOZpjN}{32}{]} and a relatively new tool, Quarto (\url{https://quarto.org}).
+Other tools can also be used for version control of scientific manuscripts including R Markdown via the bookdown package (\url{https://bookdown.org/}), jupyter notebooks\textsuperscript{\protect\hyperlink{ref-i4FOZpjN}{32}} and a relatively new tool, Quarto (\url{https://quarto.org}).
 
@@
 Peer review of research software by the open software development community rOpenSci (https://ropensci.org/software-review/) and of research software and associated manuscripts by the Journal of Open Source Software (https://joss.readthedocs.io/en/latest/submitting.html) requires that submitted work is hosted on GitHub and their review processes make use of GitHub issues.
-rOpenSci's efforts have resulted in many well-used R packages for ecology research including rfishbase {[}\protect\hyperlink{ref-Xsdcv6q}{33}{]} and taxize {[}\protect\hyperlink{ref-FVBWKkZu}{34}{]}.
+rOpenSci's efforts have resulted in many well-used R packages for ecology research including rfishbase\textsuperscript{\protect\hyperlink{ref-Xsdcv6q}{33}} and taxize\textsuperscript{\protect\hyperlink{ref-FVBWKkZu}{34}}.
 
@@
 Peer review of research software by rOpenSci (\url{https://ropensci.org/software-review/}) also makes use of many features of GitHub to streamline and automate parts of the review process.
-rOpenSci's efforts have resulted in many well-used R packages for ecology research including rfishbase {[}\protect\hyperlink{ref-Xsdcv6q}{33}{]} and taxize {[}\protect\hyperlink{ref-FVBWKkZu}{34}{]}.
+rOpenSci's efforts have resulted in many well-used R packages for ecology research including rfishbase\textsuperscript{\protect\hyperlink{ref-Xsdcv6q}{33}} and taxize\textsuperscript{\protect\hyperlink{ref-FVBWKkZu}{34}}.
 Although the use of GitHub in peer-review is currently restricted to these specialized cases, they may provide a model for peer-review in more traditional EEB journals for manuscripts that make use of code.
@@
 In the developmental stages, collaborators can directly see the code for the analysis, manipulate and explore the data themselves, and check for errors.
-Cynically, there is also more insurance against nefarious colleagues that may be tempted to distort results {[}\protect\hyperlink{ref-18PTmKJkq}{35}{]}.
+Cynically, there is also more insurance against nefarious colleagues that may be tempted to distort results\textsuperscript{\protect\hyperlink{ref-18PTmKJkq}{35}}.
 Collaborators as well as pre-publication and post-publication reviewers are better positioned to discover questionable findings if they have full and transparent access to the project.
@@
 This transparency can similarly be extended beyond coauthors to the entire scientific community.
-Publishing the data and reproducible workflows along with the manuscript allows any reader to review the analysis and reproduce the experiment {[}\protect\hyperlink{ref-NOgBWVAr}{36}{]}.
+Publishing the data and reproducible workflows along with the manuscript allows any reader to review the analysis and reproduce the experiment\textsuperscript{\protect\hyperlink{ref-NOgBWVAr}{36}}.
 Supplying code for (novel) methods that are proposed or used also reduces barriers to knowledge and can greatly improve the ability of others to build on existing work, resulting in greater proliferation and accessibility for a broader audience.
@@
 
-The development of research software continues, and so does the need to consider project continuity, especially in EEB where graduate students, research assistants, and postdoctoral fellows often hold relatively short-term positions {[}\protect\hyperlink{ref-D4C4k4ak}{37}{]}.
+The development of research software continues, and so does the need to consider project continuity, especially in EEB where graduate students, research assistants, and postdoctoral fellows often hold relatively short-term positions\textsuperscript{\protect\hyperlink{ref-D4C4k4ak}{37}}.
 Often with these types of short-term research projects, once the contract expires, the research software upkeep tends to fall off as the researchers move on to new projects.
 Additionally, if the research software is kept on only the researcher's personal devices, it becomes increasingly difficult to access the software and code for future uses.
-As projects or contracts end, there should be a handover period of this software in order for the next cohort of researchers to reuse what was already developed {[}\protect\hyperlink{ref-4ny1onB0}{8},\protect\hyperlink{ref-D4C4k4ak}{37}{]}.
+As projects or contracts end, there should be a handover period of this software in order for the next cohort of researchers to reuse what was already developed\textsuperscript{\protect\hyperlink{ref-4ny1onB0}{8},\protect\hyperlink{ref-D4C4k4ak}{37}}.
 
 GitHub facilitates project continuity among research software and research code by providing tools that make this handover period easier.
-As we have already mentioned, using Git for code in Ecology and Evolution can allow for a ``paper trail'' of sorts to be created for the research software, thus allowing for future users of the code access to the entire history of the project {[}\protect\hyperlink{ref-3DKwn1sY}{14}{]}.
-Additionally, GitHub allows for repositories and organizations to have designated Code Owners {[}\protect\hyperlink{ref-s91uGRZ2}{38}{]}; these code owners can change through time allowing for the transition of research software from one cohort of researchers to the next {[}\protect\hyperlink{ref-iIEKCTLU}{26}{]}.
+As we have already mentioned, using Git for code in Ecology and Evolution can allow for a ``paper trail'' of sorts to be created for the research software, thus allowing for future users of the code access to the entire history of the project\textsuperscript{\protect\hyperlink{ref-3DKwn1sY}{14}}.
+Additionally, GitHub allows for repositories and organizations to have designated Code Owners\textsuperscript{\protect\hyperlink{ref-s91uGRZ2}{38}}; these code owners can change through time allowing for the transition of research software from one cohort of researchers to the next\textsuperscript{\protect\hyperlink{ref-iIEKCTLU}{26}}.
 There are also multiple means by which to archive software dependency information with GitHub.
@@
 
-There have been many calls for researchers outside of the software development community to join the 73 million GitHub users for their collaborative research {[}\protect\hyperlink{ref-10ghgV3S8}{3},\protect\hyperlink{ref-1Du6fzB8g}{25},\protect\hyperlink{ref-UsTxAq4f}{39}{]}.
+There have been many calls for researchers outside of the software development community to join the 73 million GitHub users for their collaborative research\textsuperscript{\protect\hyperlink{ref-10ghgV3S8}{3},\protect\hyperlink{ref-1Du6fzB8g}{25},\protect\hyperlink{ref-UsTxAq4f}{39}}.
 This call comes in light of both the continual shift toward open-science and increasing computational and data requirements in EEB.
-Until now, resources and practical guidance specifically focused on using GitHub within the EEB community have been dispersed in blog posts and video tutorials (\protect\hyperlink{tips}{Box 2} Box {[}\protect\hyperlink{ref-box:tips}{\textbf{box:tips?}}{]}).
+Until now, resources and practical guidance specifically focused on using GitHub within the EEB community have been dispersed in blog posts and video tutorials (\protect\hyperlink{tips}{Box 2} Box\textsuperscript{\protect\hyperlink{ref-box:tips}{\textbf{box:tips?}}}).
 We felt these resources have been extremely useful for us to learn to use GitHub in our own work, and that a collation of the main ideas into one medium, while adding on our personal perspectives, would be of use to the EEB community.
@@
 The default public nature of GitHub usage can add additional pressure to students and scientists learning to use the platform.
-We also note that large file storage is discouraged (and limited) on GitHub but add-ons do exist (e.g.~\url{https://git-lfs.github.com/}) that permit data storage, and increasing integration between platforms (e.g.
-{[}\protect\hyperlink{ref-lx49NGto}{40}{]}) allows data to be stored away from GitHub and linked dynamically.
+We also note that large file storage is discouraged (and limited) on GitHub but add-ons do exist (e.g.~\url{https://git-lfs.github.com/}) that permit data storage, and increasing integration between platforms (e.g.\textsuperscript{\protect\hyperlink{ref-lx49NGto}{40}}) allows data to be stored away from GitHub and linked dynamically.
 We suspect a major additional barrier to EEB researchers is a distinct lack of GitHub help documents for non-English researchers in ecology and evolution, meaning that EEB researchers potentially miss the opportunity to fully understand the importance of version control, reproducibility, and other benefits of GitHub.
@@
 \\
-2. \textbf{Consider taking free courses} such as those from Software Carpentries {[}\protect\hyperlink{ref-pjy75gHr}{41}{]} and sharing these courses with your lab members or colleagues. \\
+2. \textbf{Consider taking free courses} such as those from Software Carpentries\textsuperscript{\protect\hyperlink{ref-pjy75gHr}{41}} and sharing these courses with your lab members or colleagues. \\
 3.
@@
 6.
-\textbf{The Jenny Bryan universe of GitHub material} provides a thorough and accessible introduction for a multitude of research-related uses for GitHub, and includes a book {[}\protect\hyperlink{ref-ZvrOcg9w}{42}{]}, statistics course {[}\protect\hyperlink{ref-6CMMeSeD}{43}{]} and academic article {[}\protect\hyperlink{ref-RVetqmsg}{7}{]}.
+\textbf{The Jenny Bryan universe of GitHub material} provides a thorough and accessible introduction for a multitude of research-related uses for GitHub, and includes a book\textsuperscript{\protect\hyperlink{ref-ZvrOcg9w}{42}}, statistics course\textsuperscript{\protect\hyperlink{ref-6CMMeSeD}{43}} and academic article\textsuperscript{\protect\hyperlink{ref-RVetqmsg}{7}}.
 \\
@@
 \CSLLeftMargin{1. }
-\CSLRightInline{\textbf{How do scientists develop and use scientific software?}
-\CSLBlock{Jo Erskine Hannay, Carolyn MacLeod, Janice Singer, Hans Petter Langtangen, Dietmar Pfahl, Greg Wilson} \emph{2009 ICSE Workshop on Software Engineering for Computational Science and Engineering} (2009-05) \url{https://doi.org/bw966x}
-\CSLBlock{DOI: \href{https://doi.org/10.1109/secse.2009.5069155}{10.1109/secse.2009.5069155}}}
+\CSLRightInline{Hannay, J.
+E.
+\emph{et al.} How do scientists develop and use scientific software?
+in \emph{2009 ICSE Workshop on Software Engineering for Computational Science and Engineering} (IEEE, 2009).
+doi:\href{https://doi.org/10.1109/secse.2009.5069155}{10.1109/secse.2009.5069155}.}
 
@@
 \CSLLeftMargin{2. }
-\CSLRightInline{\textbf{Challenge to scientists: does your ten-year-old code still run?}
-\CSLBlock{Jeffrey M Perkel} \emph{Nature} (2020-08-24) \url{https://doi.org/gg89cr}
-\CSLBlock{DOI: \href{https://doi.org/10.1038/d41586-020-02462-7}{10.1038/d41586-020-02462-7} · PMID: \href{https://www.ncbi.nlm.nih.gov/pubmed/32839567}{32839567}}}
+\CSLRightInline{Perkel, J. M. \href{https://doi.org/10.1038/d41586-020-02462-7}{Challenge to scientists: does your ten-year-old code still run?} \emph{Nature} \textbf{584}, 656--658 (2020).}
 
@@
 \CSLLeftMargin{3. }
-\CSLRightInline{\textbf{Democratic databases: science on GitHub}
-\CSLBlock{Jeffrey Perkel} \emph{Nature} (2016-10-03) \url{https://doi.org/gdz6dq}
-\CSLBlock{DOI: \href{https://doi.org/10.1038/538127a}{10.1038/538127a} · PMID: \href{https://www.ncbi.nlm.nih.gov/pubmed/27708327}{27708327}}}
+\CSLRightInline{Perkel, J. \href{https://doi.org/10.1038/538127a}{Democratic databases: science on GitHub}. \emph{Nature} \textbf{538}, 127--128 (2016).}
 
@@
 \CSLLeftMargin{4. }
-\CSLRightInline{\textbf{A survey of the practice of computational science}
-\CSLBlock{Prakash Prabhu, Yun Zhang, Soumyadeep Ghosh, David I August, Jialu Huang, Stephen Beard, Hanjun Kim, Taewook Oh, Thomas B Jablin, Nick P Johnson, \ldots{} David Walker} \emph{State of the Practice Reports on - SC '11} (2011) \url{https://doi.org/bdpsrp}
-\CSLBlock{DOI: \href{https://doi.org/10.1145/2063348.2063374}{10.1145/2063348.2063374}}}
+\CSLRightInline{Prabhu, P.
+\emph{et al.} A survey of the practice of computational science.
+in \emph{State of the Practice Reports on - SC '11} (ACM Press, 2011).
+doi:\href{https://doi.org/10.1145/2063348.2063374}{10.1145/2063348.2063374}.}
 
@@
 \CSLLeftMargin{5. }
-\CSLRightInline{\textbf{Best Practices for Scientific Computing}
-\CSLBlock{Greg Wilson, DA Aruliah, CTitus Brown, Neil P Chue Hong, Matt Davis, Richard T Guy, Steven HD Haddock, Kathryn D Huff, Ian M Mitchell, Mark D Plumbley, \ldots{} Paul Wilson} \emph{PLoS Biology} (2014-01-07) \url{https://doi.org/qtt}
-\CSLBlock{DOI: \href{https://doi.org/10.1371/journal.pbio.1001745}{10.1371/journal.pbio.1001745} · PMID: \href{https://www.ncbi.nlm.nih.gov/pubmed/24415924}{24415924} · PMCID: \href{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC3886731}{PMC3886731}}}
+\CSLRightInline{Wilson, G. \emph{et al.} \href{https://doi.org/10.1371/journal.pbio.1001745}{Best Practices for Scientific Computing}. \emph{PLoS Biol} \textbf{12}, e1001745 (2014).}
 
@@
 \CSLLeftMargin{6. }
-\CSLRightInline{\textbf{Build software better, together}
-\CSLBlock{GitHub} \url{https://github.com}}
+\CSLRightInline{Build software better, together. \emph{GitHub} \url{https://github.com}.}
 
@@
 \CSLLeftMargin{7. }
-\CSLRightInline{\textbf{Excuse Me, Do You Have a Moment to Talk About Version Control?}
-\CSLBlock{Jennifer Bryan} \emph{The American Statistician} (2018-01-02) \url{https://doi.org/gdhzdp}
-\CSLBlock{DOI: \href{https://doi.org/10.1080/00031305.2017.1399928}{10.1080/00031305.2017.1399928}}}
+\CSLRightInline{Bryan, J.
+\href{https://doi.org/10.1080/00031305.2017.1399928}{Excuse Me, Do You Have a Moment to Talk About Version Control?} \emph{The American Statistician} \textbf{72}, 20--27 (2018).}
 
@@
 \CSLLeftMargin{8. }
-\CSLRightInline{\textbf{Git can facilitate greater reproducibility and increased transparency in science}
-\CSLBlock{Karthik Ram} \emph{Source Code for Biology and Medicine} (2013-02-28) \url{https://doi.org/krv}
-\CSLBlock{DOI: \href{https://doi.org/10.1186/1751-0473-8-7}{10.1186/1751-0473-8-7} · PMID: \href{https://www.ncbi.nlm.nih.gov/pubmed/23448176}{23448176} · PMCID: \href{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC3639880}{PMC3639880}}}
+\CSLRightInline{Ram, K. \href{https://doi.org/10.1186/1751-0473-8-7}{Git can facilitate greater reproducibility and increased transparency in science}. \emph{Source Code Biol Med} \textbf{8}, (2013).}
 
@@
 \CSLLeftMargin{9. }
-\CSLRightInline{\textbf{Ten Simple Rules for Taking Advantage of Git and GitHub}
-\CSLBlock{Yasset Perez-Riverol, Laurent Gatto, Rui Wang, Timo Sachsenberg, Julian Uszkoreit, Felipe da Veiga Leprevost, Christian Fufezan, Tobias Ternent, Stephen J Eglen, Daniel S Katz, \ldots{} Juan Antonio Vizcaíno} \emph{PLOS Computational Biology} (2016-07-14) \url{https://doi.org/gbrb39}
-\CSLBlock{DOI: \href{https://doi.org/10.1371/journal.pcbi.1004947}{10.1371/journal.pcbi.1004947} · PMID: \href{https://www.ncbi.nlm.nih.gov/pubmed/27415786}{27415786} · PMCID: \href{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC4945047}{PMC4945047}}}
+\CSLRightInline{Perez-Riverol, Y.
+\emph{et al.} \href{https://doi.org/10.1371/journal.pcbi.1004947}{Ten Simple Rules for Taking Advantage of Git and GitHub}.
+\emph{PLoS Comput Biol} \textbf{12}, e1004947 (2016).}
 
@@
 \CSLLeftMargin{10. }
-\CSLRightInline{\textbf{A Quick Introduction to Version Control with Git and GitHub}
-\CSLBlock{John D Blischak, Emily R Davenport, Greg Wilson} \emph{PLOS Computational Biology} (2016-01-19) \url{https://doi.org/gbqsnf}
-\CSLBlock{DOI: \href{https://doi.org/10.1371/journal.pcbi.1004668}{10.1371/journal.pcbi.1004668} · PMID: \href{https://www.ncbi.nlm.nih.gov/pubmed/26785377}{26785377} · PMCID: \href{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC4718703}{PMC4718703}}}
+\CSLRightInline{Blischak, J.
+D., Davenport, E.
+R.
+\& Wilson, G.
+\href{https://doi.org/10.1371/journal.pcbi.1004668}{A Quick Introduction to Version Control with Git and GitHub}.
+\emph{PLoS Comput Biol} \textbf{12}, e1004668 (2016).}
 
@@
 \CSLLeftMargin{11. }
-\CSLRightInline{\textbf{Learn Git In 15 Minutes} \url{https://www.youtube.com/watch?v=USjZcfj8yxE}}
+\CSLRightInline{\emph{\href{https://www.youtube.com/watch?v=USjZcfj8yxE}{Learn Git In 15 Minutes}}.}
 
@@
 \CSLLeftMargin{12. }
-\CSLRightInline{\textbf{Let's Git started \textbar{} Happy Git and GitHub for the useR}
-\CSLBlock{Jenny Bryan Hester the STAT 545 TAs, Jim} \url{https://happygitwithr.com/}}
+\CSLRightInline{Hester, J. B., the STAT 545 TAs, Jim. \emph{\href{https://happygitwithr.com/}{Let's Git started \textbar{} Happy Git and GitHub for the useR}}.}
 
@@
 \CSLLeftMargin{13. }
-\CSLRightInline{\textbf{Coding Club: A Positive Peer-Learning Community} \url{https://ourcodingclub.github.io/}}
+\CSLRightInline{Coding Club: A Positive Peer-Learning Community. \url{https://ourcodingclub.github.io/}.}
 
@@
 \CSLLeftMargin{14. }
-\CSLRightInline{\textbf{Our path to better science in less time using open data science tools}
-\CSLBlock{Julia SStewart Lowndes, Benjamin D Best, Courtney Scarborough, Jamie C Afflerbach, Melanie R Frazier, Casey C O'Hara, Ning Jiang, Benjamin S Halpern} \emph{Nature Ecology \&amp; Evolution} (2017-05-23) \url{https://doi.org/gc4jb3}
-\CSLBlock{DOI: \href{https://doi.org/10.1038/s41559-017-0160}{10.1038/s41559-017-0160} · PMID: \href{https://www.ncbi.nlm.nih.gov/pubmed/28812630}{28812630}}}
+\CSLRightInline{Lowndes, J.
+S.
+S.
+\emph{et al.} \href{https://doi.org/10.1038/s41559-017-0160}{Our path to better science in less time using open data science tools}.
+\emph{Nat Ecol Evol} \textbf{1}, (2017).}
 
@@
 \CSLLeftMargin{15. }
-\CSLRightInline{\textbf{Social network of software development at GitHub}
-\CSLBlock{William Leibzon} \emph{2016 IEEE/ACM International Conference on Advances in Social Networks Analysis and Mining (ASONAM)} (2016-08) \url{https://doi.org/gph5qt}
-\CSLBlock{DOI: \href{https://doi.org/10.1109/asonam.2016.7752419}{10.1109/asonam.2016.7752419}}}
+\CSLRightInline{Leibzon, W.
+Social network of software development at GitHub.
+in \emph{2016 IEEE/ACM International Conference on Advances in Social Networks Analysis and Mining (ASONAM)} (IEEE, 2016).
+doi:\href{https://doi.org/10.1109/asonam.2016.7752419}{10.1109/asonam.2016.7752419}.}
 
@@
 \CSLLeftMargin{16. }
-\CSLRightInline{\textbf{Foundational Practices of Research Data Management}
-\CSLBlock{Kristin Briney, Heather Coates, Abigail Goben} \emph{Research Ideas and Outcomes} (2020-07-27) \url{https://doi.org/ghssbk}
-\CSLBlock{DOI: \href{https://doi.org/10.3897/rio.6.e56508}{10.3897/rio.6.e56508}}}
+\CSLRightInline{Briney, K., Coates, H. \& Goben, A. \href{https://doi.org/10.3897/rio.6.e56508}{Foundational Practices of Research Data Management}. \emph{RIO} \textbf{6}, (2020).}
 
@@
 \CSLLeftMargin{17. }
-\CSLRightInline{\textbf{A Beginner's Guide to Conducting Reproducible Research}
-\CSLBlock{Jesse M Alston, Jessica A Rick} \emph{The Bulletin of the Ecological Society of America} (2021-01-15) \url{https://doi.org/gk5v4p}
-\CSLBlock{DOI: \href{https://doi.org/10.1002/bes2.1801}{10.1002/bes2.1801}}}
+\CSLRightInline{Alston, J. M. \& Rick, J. A. \href{https://doi.org/10.1002/bes2.1801}{A Beginner's Guide to Conducting Reproducible Research}. \emph{Bull. Ecol. Soc. Am.} \textbf{102}, (2021).}
 
@@
 \CSLLeftMargin{18. }
-\CSLRightInline{\textbf{Packaging Data Analytical Work Reproducibly Using R (and Friends)}
-\CSLBlock{Ben Marwick, Carl Boettiger, Lincoln Mullen} \emph{The American Statistician} (2018-01-02) \url{https://doi.org/gdhvm8}
-\CSLBlock{DOI: \href{https://doi.org/10.1080/00031305.2017.1375986}{10.1080/00031305.2017.1375986}}}
+\CSLRightInline{Marwick, B., Boettiger, C.
+\& Mullen, L.
+\href{https://doi.org/10.1080/00031305.2017.1375986}{Packaging Data Analytical Work Reproducibly Using R (and Friends)}.
+\emph{The American Statistician} \textbf{72}, 80--88 (2018).}
 
@@
 \CSLLeftMargin{19. }
-\CSLRightInline{\textbf{About large files on GitHub}
-\CSLBlock{GitHub Docs} \url{https://ghdocs-prod.azurewebsites.net/en/repositories/working-with-files/managing-large-files/about-large-files-on-github}}
+\CSLRightInline{About large files on GitHub. \emph{GitHub Docs} \url{https://ghdocs-prod.azurewebsites.net/en/repositories/working-with-files/managing-large-files/about-large-files-on-github}.}
 
@@
 \CSLLeftMargin{20. }
-\CSLRightInline{\textbf{Electronic lab notebooks: can they replace paper?}
-\CSLBlock{Samantha Kanza, Cerys Willoughby, Nicholas Gibbins, Richard Whitby, Jeremy Graham Frey, Jana Erjavec, Klemen Zupančič, Matjaž Hren, Katarina Kovač} \emph{Journal of Cheminformatics} (2017-05-24) \url{https://doi.org/gfz287}
-\CSLBlock{DOI: \href{https://doi.org/10.1186/s13321-017-0221-3}{10.1186/s13321-017-0221-3} · PMID: \href{https://www.ncbi.nlm.nih.gov/pubmed/29086051}{29086051} · PMCID: \href{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC5443717}{PMC5443717}}}
+\CSLRightInline{Kanza, S. \emph{et al.} \href{https://doi.org/10.1186/s13321-017-0221-3}{Electronic lab notebooks: can they replace paper?} \emph{J Cheminform} \textbf{9}, (2017).}
 
@@
 \CSLLeftMargin{21. }
-\CSLRightInline{\textbf{Ten Simple Rules for a Computational Biologist's Laboratory Notebook}
-\CSLBlock{Santiago Schnell} \emph{PLOS Computational Biology} (2015-09-10) \url{https://doi.org/gf5fnr}
-\CSLBlock{DOI: \href{https://doi.org/10.1371/journal.pcbi.1004385}{10.1371/journal.pcbi.1004385} · PMID: \href{https://www.ncbi.nlm.nih.gov/pubmed/26356732}{26356732} · PMCID: \href{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC4565690}{PMC4565690}}}
+\CSLRightInline{Schnell, S.
+\href{https://doi.org/10.1371/journal.pcbi.1004385}{Ten Simple Rules for a Computational Biologist's Laboratory Notebook}.
+\emph{PLoS Comput Biol} \textbf{11}, e1004385 (2015).}
 
@@
 \CSLLeftMargin{22. }
-\CSLRightInline{\textbf{About projects (beta)}
-\CSLBlock{GitHub Docs} \url{https://ghdocs-prod.azurewebsites.net/en/issues/trying-out-the-new-projects-experience/about-projects}}
+\CSLRightInline{About projects (beta). \emph{GitHub Docs} \url{https://ghdocs-prod.azurewebsites.net/en/issues/trying-out-the-new-projects-experience/about-projects}.}
 
@@
 \CSLLeftMargin{23. }
-\CSLRightInline{\textbf{R Markdown: the definitive guide}
-\CSLBlock{Yihui Xie, JJ Allaire, Garrett Grolemund} \emph{CRC Press, Taylor and Francis Group} (2019)
-\CSLBlock{ISBN: 9780429782961}}
+\CSLRightInline{Xie, Y., Allaire, J. J. \& Grolemund, G. \emph{R Markdown: the definitive guide}. (CRC Press, Taylor and Francis Group, 2019).}
 
@@
 \CSLLeftMargin{24. }
-\CSLRightInline{\textbf{Building tools with GitHub: customize your workflow}
-\CSLBlock{Chris Dawson} \emph{O'Reilly} (2016)
-\CSLBlock{ISBN: 9781491933503}}
+\CSLRightInline{Dawson, C. \emph{Building tools with GitHub: customize your workflow}. (O'Reilly, 2016).}
 
@@
 \CSLLeftMargin{25. }
-\CSLRightInline{\textbf{A Guide to Using GitHub for Developing and Versioning Data Standards and Reporting Formats}
-\CSLBlock{Robert Crystal‐Ornelas, Charuleka Varadharajan, Ben Bond‐Lamberty, Kristin Boye, Madison Burrus, Shreyas Cholia, Michael Crow, Joan Damerow, Ranjeet Devarakonda, Kim S Ely, \ldots{} Deborah A Agarwal} \emph{Earth and Space Science} (2021-08) \url{https://doi.org/gmbs9c}
-\CSLBlock{DOI: \href{https://doi.org/10.1029/2021ea001797}{10.1029/2021ea001797}}}
+\CSLRightInline{Crystal‐Ornelas, R.
+\emph{et al.} \href{https://doi.org/10.1029/2021ea001797}{A Guide to Using GitHub for Developing and Versioning Data Standards and Reporting Formats}.
+\emph{Earth Space Sci} \textbf{8}, (2021).}
 
@@
 \CSLLeftMargin{26. }
-\CSLRightInline{\textbf{The Tao of open science for ecology}
-\CSLBlock{Stephanie E Hampton, Sean S Anderson, Sarah C Bagby, Corinna Gries, Xueying Han, Edmund M Hart, Matthew B Jones, WChristopher Lenhardt, Andrew MacDonald, William K Michener, \ldots{} Naupaka Zimmerman} \emph{Ecosphere} (2015-07) \url{https://doi.org/gdj5w6}
-\CSLBlock{DOI: \href{https://doi.org/10.1890/es14-00402.1}{10.1890/es14-00402.1}}}
+\CSLRightInline{Hampton, S. E. \emph{et al.} \href{https://doi.org/10.1890/es14-00402.1}{The Tao of open science for ecology}. \emph{Ecosphere} \textbf{6}, art120 (2015).}
 
@@
 \CSLLeftMargin{27. }
-\CSLRightInline{\textbf{Elevating The Status of Code in Ecology}
-\CSLBlock{KAS Mislan, Jeffrey M Heer, Ethan P White} \emph{Trends in Ecology \&amp; Evolution} (2016-01) \url{https://doi.org/gg43mk}
-\CSLBlock{DOI: \href{https://doi.org/10.1016/j.tree.2015.11.006}{10.1016/j.tree.2015.11.006} · PMID: \href{https://www.ncbi.nlm.nih.gov/pubmed/26704455}{26704455}}}
+\CSLRightInline{Mislan, K.
+A.
+S., Heer, J.
+M.
+\& White, E.
+P.
+\href{https://doi.org/10.1016/j.tree.2015.11.006}{Elevating The Status of Code in Ecology}.
+\emph{Trends in Ecology \&amp; Evolution} \textbf{31}, 4--7 (2016).}
 
@@
 \CSLLeftMargin{28. }
-\CSLRightInline{\textbf{1,500 scientists lift the lid on reproducibility}
-\CSLBlock{Monya Baker} \emph{Nature} (2016-05-25) \url{https://doi.org/gdgzjx}
-\CSLBlock{DOI: \href{https://doi.org/10.1038/533452a}{10.1038/533452a} · PMID: \href{https://www.ncbi.nlm.nih.gov/pubmed/27225100}{27225100}}}
+\CSLRightInline{Baker, M. \href{https://doi.org/10.1038/533452a}{1,500 scientists lift the lid on reproducibility}. \emph{Nature} \textbf{533}, 452--454 (2016).}
 
@@
 \CSLLeftMargin{29. }
-\CSLRightInline{\textbf{Not just for programmers: How GitHub can accelerate collaborative and reproducible research in ecology and evolution}
-\CSLBlock{Robert Crystal-Ornelas, Brandon PM Edwards, Katherine Hébert, Friederike Hillemann, Emma J Hudgins, Luna LSánchez Reyes, Eric R Scott, Matthew J Grainger, Vivienne Foroughirad, Allison D Binley, \ldots{} Pedro Henrique Pereira Braga} \emph{Manubot} (2022-06-08) \url{https://SORTEE-Github-Hackathon.github.io/manuscript/}}
+\CSLRightInline{Crystal-Ornelas, R.
+\emph{et al.} \emph{Not just for programmers: How GitHub can accelerate collaborative and reproducible research in ecology and evolution}.
+\url{https://SORTEE-Github-Hackathon.github.io/manuscript/} (2022).}
 
@@
 \CSLLeftMargin{30. }
-\CSLRightInline{\textbf{Using Peer Code Review as an Educational Tool}
-\CSLBlock{Xiangyu Song, Seth Copen Goldstein, Majd Sakr} \emph{Proceedings of the 2020 ACM Conference on Innovation and Technology in Computer Science Education} (2020-06-02) \url{https://doi.org/gp58rg}
-\CSLBlock{DOI: \href{https://doi.org/10.1145/3341525.3387370}{10.1145/3341525.3387370}}}
+\CSLRightInline{Song, X., Goldstein, S.
+C.
+\& Sakr, M.
+Using Peer Code Review as an Educational Tool.
+in \emph{Proceedings of the 2020 ACM Conference on Innovation and Technology in Computer Science Education} (ACM, 2020).
+doi:\href{https://doi.org/10.1145/3341525.3387370}{10.1145/3341525.3387370}.}
 
@@
 \CSLLeftMargin{31. }
-\CSLRightInline{\textbf{Open collaborative writing with Manubot}
-\CSLBlock{Daniel S Himmelstein, Vincent Rubinetti, David R Slochower, Dongbo Hu, Venkat S Malladi, Casey S Greene, Anthony Gitter} \emph{PLOS Computational Biology} (2019-06-24) \url{https://doi.org/c7np}
-\CSLBlock{DOI: \href{https://doi.org/10.1371/journal.pcbi.1007128}{10.1371/journal.pcbi.1007128} · PMID: \href{https://www.ncbi.nlm.nih.gov/pubmed/31233491}{31233491} · PMCID: \href{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC6611653}{PMC6611653}}}
+\CSLRightInline{Himmelstein, D. S. \emph{et al.} \href{https://doi.org/10.1371/journal.pcbi.1007128}{Open collaborative writing with Manubot}. \emph{PLoS Comput Biol} \textbf{15}, e1007128 (2019).}
 
@@
 \CSLLeftMargin{32. }
-\CSLRightInline{\textbf{Creating an executable paper is a journey through Open Science}
-\CSLBlock{Jana Lasser} \emph{Communications Physics} (2020-08-19) \url{https://doi.org/gg89zd}
-\CSLBlock{DOI: \href{https://doi.org/10.1038/s42005-020-00403-4}{10.1038/s42005-020-00403-4}}}
+\CSLRightInline{Lasser, J. \href{https://doi.org/10.1038/s42005-020-00403-4}{Creating an executable paper is a journey through Open Science}. \emph{Commun Phys} \textbf{3}, (2020).}
 
@@
 \CSLLeftMargin{33. }
-\CSLRightInline{\textbf{rfishbase: exploring, manipulating and visualizing FishBase data from R}
-\CSLBlock{C Boettiger, DT Lang, PC Wainwright} \emph{Journal of Fish Biology} (2012-11) \url{https://doi.org/gh5x27}
-\CSLBlock{DOI: \href{https://doi.org/10.1111/j.1095-8649.2012.03464.x}{10.1111/j.1095-8649.2012.03464.x} · PMID: \href{https://www.ncbi.nlm.nih.gov/pubmed/23130696}{23130696}}}
+\CSLRightInline{Boettiger, C., Lang, D.
+T.
+\& Wainwright, P.
+C.
+\href{https://doi.org/10.1111/j.1095-8649.2012.03464.x}{rfishbase: exploring, manipulating and visualizing FishBase data from R}.
+\emph{Journal of Fish Biology} \textbf{81}, 2030--2039 (2012).}
 
@@
 \CSLLeftMargin{34. }
-\CSLRightInline{\textbf{taxize: taxonomic search and retrieval in R}
-\CSLBlock{Scott A Chamberlain, Eduard Szöcs} \emph{F1000Research} (2013-10-28) \url{https://doi.org/ggdskx}
-\CSLBlock{DOI: \href{https://doi.org/10.12688/f1000research.2-191.v2}{10.12688/f1000research.2-191.v2} · PMID: \href{https://www.ncbi.nlm.nih.gov/pubmed/24555091}{24555091} · PMCID: \href{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC3901538}{PMC3901538}}}
+\CSLRightInline{Chamberlain, S. A. \& Szöcs, E. \href{https://doi.org/10.12688/f1000research.2-191.v2}{taxize: taxonomic search and retrieval in R}. \emph{F1000Res} \textbf{2}, 191 (2013).}
 
@@
 \CSLLeftMargin{35. }
-\CSLRightInline{\textbf{\#PruittData and the Ethics of Data in Science}
-\CSLBlock{Professor Lee BKass January 18, 2022 2:51 Pm} \emph{Ecology for the Masses} (2020-02-04) \url{https://ecologyforthemasses.com/2020/02/04/pruittdata-and-the-ethics-of-data-in-science/}}
+\CSLRightInline{January 18, P.
+L.
+B.
+K.
+\& Pm, 2022.
+2:51.
+\#PruittData and the Ethics of Data in Science.
+\emph{Ecology for the Masses} \url{https://ecologyforthemasses.com/2020/02/04/pruittdata-and-the-ethics-of-data-in-science/} (2020).}
 
@@
 \CSLLeftMargin{36. }
-\CSLRightInline{\textbf{Low availability of code in ecology: A~call for urgent action}
-\CSLBlock{Antica Culina, Ilona van den Berg, Simon Evans, Alfredo Sánchez-Tójar} \emph{PLOS Biology} (2020-07-28) \url{https://doi.org/gg6rgf}
-\CSLBlock{DOI: \href{https://doi.org/10.1371/journal.pbio.3000763}{10.1371/journal.pbio.3000763} · PMID: \href{https://www.ncbi.nlm.nih.gov/pubmed/32722681}{32722681} · PMCID: \href{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC7386629}{PMC7386629}}}
+\CSLRightInline{Culina, A., van den Berg, I., Evans, S.
+\& Sánchez-Tójar, A.
+\href{https://doi.org/10.1371/journal.pbio.3000763}{Low availability of code in ecology: A~call for urgent action}.
+\emph{PLoS Biol} \textbf{18}, e3000763 (2020).}
 
@@
 \CSLLeftMargin{37. }
-\CSLRightInline{\textbf{Sustainable Research Software Hand-Over}
-\CSLBlock{J Fehr, C Himpe, S Rave, J Saak} \emph{Journal of Open Research Software} (2021-04-30) \url{https://doi.org/g4n4}
-\CSLBlock{DOI: \href{https://doi.org/10.5334/jors.307}{10.5334/jors.307}}}
+\CSLRightInline{Fehr, J., Himpe, C., Rave, S. \& Saak, J. \href{https://doi.org/10.5334/jors.307}{Sustainable Research Software Hand-Over}. \emph{JORS} \textbf{9}, 5 (2021).}
 
@@
 \CSLLeftMargin{38. }
-\CSLRightInline{\textbf{About code owners}
-\CSLBlock{GitHub Docs} \url{https://ghdocs-prod.azurewebsites.net/en/repositories/managing-your-repositorys-settings-and-features/customizing-your-repository/about-code-owners}}
+\CSLRightInline{About code owners.
+\emph{GitHub Docs} \url{https://ghdocs-prod.azurewebsites.net/en/repositories/managing-your-repositorys-settings-and-features/customizing-your-repository/about-code-owners}.}
 
@@
 \CSLLeftMargin{39. }
-\CSLRightInline{\textbf{A collaborative GIS programming course using GitHub Classroom}
-\CSLBlock{Berk Anbaroğlu} \emph{Transactions in GIS} (2021-07-21) \url{https://doi.org/gp44fx}
-\CSLBlock{DOI: \href{https://doi.org/10.1111/tgis.12810}{10.1111/tgis.12810}}}
+\CSLRightInline{Anbaroğlu, B. \href{https://doi.org/10.1111/tgis.12810}{A collaborative GIS programming course using GitHub Classroom}. \emph{Transactions in GIS} \textbf{25}, 3132--3158 (2021).}
 
@@
 \CSLLeftMargin{40. }
-\CSLRightInline{\textbf{Connect GitHub to a Project - OSF Support} \url{https://help.osf.io/article/211-connect-github-to-a-project}}
+\CSLRightInline{Connect GitHub to a Project - OSF Support. \url{https://help.osf.io/article/211-connect-github-to-a-project}.}
 
@@
 \CSLLeftMargin{41. }
-\CSLRightInline{\textbf{swcarpentry/git-novice: Software Carpentry: Version Control with Git, June 2019}
-\CSLBlock{Madicken Munk, Katherine Koziar, Katrin Leinweber, Raniere Silva, François Michonneau, Rich McCue, Nima Hejazi, Simon Waldman, Rémi Emonet, Rayna Michelle Harris, \ldots{} Wolmar Nyberg Åkerström} \emph{Zenodo} (2019-07-01) \url{https://doi.org/gp44fz}
-\CSLBlock{DOI: \href{https://doi.org/10.5281/zenodo.3264950}{10.5281/zenodo.3264950}}}
+\CSLRightInline{Madicken Munk \emph{et al.} swcarpentry/git-novice: Software Carpentry: Version Control with Git, June 2019.
+(2019) doi:\href{https://doi.org/10.5281/zenodo.3264950}{10.5281/zenodo.3264950}.}
 
@@
 \CSLLeftMargin{42. }
-\CSLRightInline{\textbf{Let's Git started \textbar{} Happy Git and GitHub for the useR}
-\CSLBlock{Jenny Bryan Hester the STAT 545 TAs, Jim} \url{https://happygitwithr.com/}}
+\CSLRightInline{Hester, J. B., the STAT 545 TAs, Jim. \emph{\href{https://happygitwithr.com/}{Let's Git started \textbar{} Happy Git and GitHub for the useR}}.}
 
@@
 \CSLLeftMargin{43. }
-\CSLRightInline{\textbf{STAT 545}
-\CSLBlock{Jenny Bryan, The STAT 545 TAs} \url{https://stat545.com/}}
+\CSLRightInline{Bryan, J. \& TAs, T. S. 545. \emph{\href{https://stat545.com/}{STAT 545}}.}
 

### 2022-06-08 manuscript.tex
Merge pull request #221 from shafieisabets/main [ci skip]
This build is based on
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/c579f2e6dabd3334b02f563bb8ac53bfd042db72.

This commit was created by the following CI build and job:
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/c579f2e6dabd3334b02f563bb8ac53bfd042db72/checks
https://github.com/SORTEE-Github-Hackathon/manuscript/actions/runs/2463785278

@@
 This manuscript
-(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/eafc396e1f32d378749c27716bfc058f4802928f/}{permalink})
+(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/c579f2e6dabd3334b02f563bb8ac53bfd042db72/}{permalink})
 was automatically generated
-from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/eafc396e1f32d378749c27716bfc058f4802928f}{SORTEE-Github-Hackathon/manuscript@eafc396}
+from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/c579f2e6dabd3334b02f563bb8ac53bfd042db72}{SORTEE-Github-Hackathon/manuscript@c579f2e}
 on June 8, 2022.
@@
 \endhead
-\textbf{branch}: Development branches can be created at any point in time and work on each branch can continue independently.This is useful for testing out new ideas (both code and text) which may or may not eventually get integrated into the main branch of the project.
+\textbf{branch}: A git branch is an alternative line of development for a project (repository).
+Branches allow to add new features or modifications to the project without affecting the main part of the project.
+Development branches can be created at any point in time and work on each branch can continue independently.
+Branching is useful for testing out new ideas (both code and text) which may or may not eventually get integrated into the main branch of the project.
 Branches can also be used to isolate contributions of multiple contributors.
-Each person working on their own branch eliminates problems that arise when conflicting edits are \textbf{pushed} to the same remote branch.
+Each person working on their own branch eliminates problems that may arise if conflicting edits are \textbf{pushed} to the same remote branch.
 Changes in a development branch can be \textbf{merged} into the main branch via \textbf{pull requests}.
@@
 Commits can include changes in multiple files and must include a brief commit message describing the changes made.
-A typical workflow is to make some related changes in files, make a commit (e.g.~``generate and include fig1 in results''), and after several commits \textbf{push} those commits to the remote (i.e., cloud-based) GitHub \textbf{repository}.
+A typical workflow is to make some related changes in files, add a commit message (e.g.~``generate and include fig1 in results''), and after several commits \textbf{push} those commits to the remote (i.e., cloud-based) GitHub \textbf{repository}.
 \\
@@
 Even if they do not have access to \textbf{push} to the original repository, they can make a fork and edit it independently.
-Forks are linked to the original GitHub repository and ``upstream'' changes (those in the original repository) can be \textbf{merged} to keep the fork up to date with the original project.
+Forks are linked to the original GitHub repository and ``upstream'' changes (i.e.~those in the original repository) can be \textbf{merged} to keep the fork up to date with the original project.
 Changes made in the fork can be integrated into the original project via \textbf{pull requests}.
@@
 \textbf{pull request}: A pull request is a request that the owner(s) of a GitHub repository integrate changes you've made on either a \textbf{branch} in the repository or in your own \textbf{fork}.
-When you initiate a pull request, you must provide a description of what changes are made.
+When you initiate a pull request, you must provide a description of what changes were made.
 Some automated tests may be run and review may be required before integrating your changes into the main \textbf{branch}.
@@
 1.
-\textbf{Check for an existing solution to your problem} The GitHub Help webpage (\url{https://docs.github.com/en}) contains extensive and detailed documents with helpful screenshots.
+\textbf{Check for an existing solution to your problem.} The GitHub Help webpage (\url{https://docs.github.com/en}) contains extensive and detailed documents with helpful screenshots.
 It is a good starting point for handling an issue, and has troubleshooting tips for specific problems.
@@
 There is a large community of GitHub users around the world who have likely faced analogous problems and may be able to provide quick solutions.
-Third, try to follow blogs (e.g., \url{https://github.blog}), Twitter accounts or YouTube channels that regularly post practical solutions about common GitHub issues.
-\\
-2. \textbf{Consider taking free courses} such as those from Software Carpentries\textsuperscript{\protect\hyperlink{ref-pjy75gHr}{41}} and sharing these courses with your lab members or colleagues. \\
+Third, try to follow blogs (e.g., \url{https://github.blog}), Twitter accounts or YouTube channels that regularly post practical solutions about the most widely-used web platform for common GitHub issues.
+\\
+2. \textbf{Consider taking free courses.} such as those from Software Carpentry\textsuperscript{\protect\hyperlink{ref-pjy75gHr}{41}} and sharing these courses with your lab members or colleagues. \\
 3.
-\textbf{Take the advantage of GitHub as an asynchronous working tool for team-based projects} See the repository for this paper (\url{https://github.com/SORTEE-Github-Hackathon/manuscript}) as an example of a collaborative manuscript that includes discussions, issues, and a website via GitHub.
-\\
-4. \textbf{The GitHub Learning Lab (\url{https://lab.github.com})} allows you to learn GitHub basics through short projects and tasks, and allows you to get feedback from their Learning Lab bot. \\
-5. \textbf{Check out the following markdown cheatsheet (\url{http://markdownguide.org/basic-syntax})} so that you can write clear metadata README files for your repositories. \\
+\textbf{Take advantage of GitHub as an asynchronous working tool for team-based projects.} See the repository for this paper (\url{https://github.com/SORTEE-Github-Hackathon/manuscript}) as an example of a collaborative manuscript that includes discussions, issues, and a website via GitHub.
+\\
+4. \textbf{The GitHub Learning Lab (\url{https://lab.github.com}).} allows you to learn GitHub basics through short projects and tasks, and allows you to get feedback from their Learning Lab bot. \\
+5. \textbf{Check out the following markdown cheatsheet (\url{http://markdownguide.org/basic-syntax}).} so that you can write clear metadata README files for your repositories. \\
 6.
-\textbf{The Jenny Bryan universe of GitHub material} provides a thorough and accessible introduction for a multitude of research-related uses for GitHub, and includes a book\textsuperscript{\protect\hyperlink{ref-ZvrOcg9w}{42}}, statistics course\textsuperscript{\protect\hyperlink{ref-6CMMeSeD}{43}} and academic article\textsuperscript{\protect\hyperlink{ref-RVetqmsg}{7}}.
+\textbf{The Jenny Bryan universe of GitHub material.} provides a thorough and accessible introduction for a multitude of research-related uses for GitHub, and includes a book\textsuperscript{\protect\hyperlink{ref-ZvrOcg9w}{42}}, statistics course\textsuperscript{\protect\hyperlink{ref-6CMMeSeD}{43}} and academic article\textsuperscript{\protect\hyperlink{ref-RVetqmsg}{7}}.
 \\
 7.
-\textbf{Don't be afraid of trial and error} One of the best ways to learn GitHub is the trial and error method.
+\textbf{Don't be afraid of trial and error.} One of the best ways to learn GitHub is the trial and error method.
 Learning from your own mistakes can be the better way to master your GitHub abilities.
@@
 8.
-\textbf{If you are an educator, include lectures on reproducibility and tools for creating reproducible workflows in your curricula}.
+\textbf{If you are an educator, include lectures on reproducibility and tools for creating reproducible workflows in the curricula.}.
 Some graduate programs now include coursework on course Rmarkdown and GitHub.
@@
 9.
-\textbf{Try to begin committing with GUI (Graphical user interface) tools} like GitHub Desktop (\url{https://desktop.github.com}), git-gui (\url{https://git-scm.com/docs/git-gui}), RStudio (\url{https://www.rstudio.com}), Visual Studio Code (\url{https://code.visualstudio.com}), Atom (\url{https://atom.io}), GitKraken (\url{https://www.gitkraken.com}) tools instead of CLI (Command line interface) tools such as Terminal or Console for more advanced features.
+\textbf{Try to begin committing with GUI (Graphical user interface) tools.} like GitHub Desktop (\url{https://desktop.github.com}), git-gui (\url{https://git-scm.com/docs/git-gui}), RStudio (\url{https://www.rstudio.com}), Visual Studio Code (\url{https://code.visualstudio.com}), Atom (\url{https://atom.io}), GitKraken (\url{https://www.gitkraken.com}) tools instead of CLI (Command line interface) tools such as Terminal or Console for more advanced features.
 \\
@@
 \includegraphics{images/github_diagram.png}
-\caption{An overview of the features of a GitHub repository.
+\caption{An overview of git's core features.
 A) Multi-faceted components allow for code writing, small data storage, manuscript writing, and project management to all be done in one place.
@@
 & A DOI can only be obtained when integrating to other services that can mint DOI (e.g.~Zenodo, OSF).
-& 100MB per file, 500MB per private repository (2GB for paid accounts).
-100GB for public repositories.
-Larger files (up to 2GB) can be attached to releases & NA \\
-Multi-tool & OSF & yes & yes & yes & yes & yes & yes & 25GB for private projects, up to 5GB per file, plus partner add-ons, 50GB for public projects & yes \\
+& 100 MB per file, 500 MB per private repository (2 GB for paid accounts).
+100 GB for public repositories.
+Larger files (up to 2 GB) can be attached to releases & NA \\
+Multi-tool & OSF & yes & yes & yes & yes & yes & yes & 25 GB for private projects, up to 5GB per file, plus partner add-ons, 50GB for public projects & yes \\
 Long-term (public) data repositories & PANGAEA & yes & yes & yes & NA & yes & yes & 10 GB free & NA \\
@@
 Long-term (public) data repositories & Figshare & yes & yes & yes & NA & yes & yes & 20 GB free, up to 5 TB & yes \\
-Temporary (personal) drive storage & Google Drive & yes & yes & yes & yes & limited free version \& paid & NA & 15GB free, up to 100GB with Google One & yes \\
+Temporary (personal) drive storage & Google Drive & yes & yes & yes & yes & limited free version \& paid & NA & 15 GB free, up to 100 GB with Google One & yes \\
 Temporary (personal) drive storage & Box & limited & yes & ? & ? & NA & NA & Unlimited total size for subscription & yes \\
-Temporary (personal) drive storage & DropBox & limited & yes & yes & yes & limited free version \& paid & NA & 2GB free & yes \\
-Temporary (personal) drive storage & OneDrive and the Office Suite & yes & yes & yes & yes & limited free version \& paid & NA & 5 GB free, up to 1TB paid & yes \\
+Temporary (personal) drive storage & DropBox & limited & yes & yes & yes & limited free version \& paid & NA & 2 GB free & yes \\
+Temporary (personal) drive storage & One Drive and the Office Suite & yes & yes & yes & yes & limited free version \& paid & NA & 5 GB free, up to 1TB paid & yes \\
 Collaborative code/text editors & Overleaf (online latex editor) & yes & yes & yes & NA & NA & NA & 1MB for individual .tex, 50MB for individual files, unlimited project size & yes \\
 Collaborative code/text editors & Jupyter Notebook & yes & ?
-& yes & with Colab & yes & NA & via Binder: no hard limit, but suggests no files \textgreater100MB, can also store on GitHub or Google Colab & yes \\
+& yes & with Colab & yes & NA & via Binder: no hard limit, but suggests no files \textgreater100 MB, can also store on GitHub or Google Colab & yes \\
 Collaborative code/text editors & HackMD & yes & yes & yes & yes & yes & NA & 3 documents free, private invitee limits & yes \\

### 2022-06-09 R/scatterblob.Rmd
adjusting x and y axes labels, and rendering pdf for methods of the scatterblob

@@
 title: "Figure: the scatterblob"
-output: html_document
+# output: html_document
+output: pdf_document
 ---
@@
 [Data, version 2](https://docs.google.com/spreadsheets/d/1zCRgctjfjE2xZN9MkqfFh222K6bvVvA3gT0UdkL_CS8/edit#gid=0).
+
+### Measuring degree of technical difficulty
 
@@
 
-### First try
+### 1) Using raw cognitive values.
 
-Using original cognitive values.
+Define colors:
 
 ```{r}
-my_colors <- viridis::turbo(n = nrow(my_data), alpha = 0.9)
+some_colors <- viridis::turbo(n = nrow(my_data), alpha = 0.9)
 
@@
                            28,30)]
+```
+
+```{r}
 ###############################################################
@@
 #plot_format <- "pdf"
-plot_format <- "svg"
-#plot_format <- "png"
+# plot_format <- "svg"
+ plot_format <- "png"
 
@@
 title(ylab="Technical difficulty", line=4, cex.lab=1)
-title(xlab="Degree of collaborativeness", line= 3.5, cex.lab=1)
+title(xlab="Degree of collaboration", line= 3.5, cex.lab=1)
 ###############################################################
@@
      labels = c("Personal",
-                "Lab \nmembers",
-                "Other \nlabs",
-                "EEB \ncommunity",
-                "All \nusers"))
+                "Lab \nMembers",
+                "Other \nLabs",
+                "EEB \nCommunity",
+                "All \nUsers"))
 text(x = c(1, 3, 5),
@@
      labels = c("Elementary",
-                "Low \nintermediate",
+                "Low \nIntermediate",
                 "Intermediate",
@@
 ```
-![Figure 1. Degree of collaboration VS technical difficulty](scatterblob_0.pdf)
+![Degree of collaboration VS raw technical difficulty](../content/images/scatterblob_0.png)
 
-### Second try
+### 2) Distributing cognitive load evenly:
 
-Distributing cognitive load evenly:
+We tried different color palettes from two diffrent R packages: [viridis](https://cran.r-project.org/web/packages/viridis/vignettes/intro-to-viridis.html#the-color-scales) and [wesanderson](https://github.com/karthik/wesanderson#readme):
 
@@
 ```
+
+We agreed that viridis-turbo was the nicest palette for the purposes of our figure.
 
@@
 ###############################################################
-plot_format <- "pdf"
-# plot_format <- "png"
+# plot_format <- "pdf"
+plot_format <- "png"
 # plot_format <- "svg"
@@
      tck = 0.02)
-title(ylab="Technical difficulty", line=4, cex.lab=1)
-title(xlab="Degree of collaborativeness", line= 3.5, cex.lab=1)
+title(ylab="Technical Difficulty", line=4, cex.lab=1)
+title(xlab="Degree of Collaboration", line= 3.5, cex.lab=1)
 ###############################################################
@@
      labels = c("Personal", 
-                "Lab \nmembers", 
-                "Other \nlabs", 
-                "EEB \ncommunity", 
-                "All \nusers"))
+                "Lab \nMembers", 
+                "Other \nLabs", 
+                "EEB \nCommunity", 
+                "All \nUsers"))
 text(x = c(1, 3, 5),
@@
 text(x = 0.2,
-     y = c(0, 1.5, 3, 4.5, 6, 7.5, 9, 10.5, 12 ), 
+     y = c(0, 3, 6, 8.6, 12),
      cex = 0.7,
@@
      labels = c("Beginner",
-                "Elementary", 
                 "Low\nIntermediate",
-                "Pre\nIntermediate",
                 "Intermediate", 
-                "Upper\nIntermediate",
-                "Pre\nAdvanced",
-                "Advanced",
-                "Very\nAdvanced"))
+                "Pre \nAdvanced",
+                "Advanced"))
 ###############################################################
@@
 
-![Figure 2. Degree of collaboration VS Even technical difficulty](scatterblob_1.pdf)
+![Degree of collaboration VS Even technical difficulty](../content/images/scatterblob_1-viridis-turbo.png)

### 2022-06-09 R/scatterblob.Rmd
some more edits to scatterblob method pdf

@@
 ---
-title: "Figure: the scatterblob"
+title: "\\textbf{\\textsc{Supplementary Material} \\linebreak \\linebreak Not just for programmers: How GitHub can accelerate collaborative and reproducible research in ecology and evolution \\linebreak \\linebreak Methods to create \\textsl{the scatterblob} figure}"
 # output: html_document
@@
 library(readr)
+scatterblob_data <- read_csv(here("data", "scatterblob_data_raw.csv"))
+uses <- scatterblob_data$`Ways to use GitHub`
+column_names <- colnames(scatterblob_data[1:8])
 ```
 
-Goal: This is a summary figure, e.g., "here are all the ways and here are the entry points with low technical difficulty, and some  for beginner s and the more advanced ways to use it".
-There are ways to use github that allows different degrees of collaboration that do not require too many technical skills.
+**Goal**: This is a summary figure, e.g., here are all the ways and here are the entry points with low technical difficulty, some for beginners and some more advanced ways to use GitHub.
 
-Use even notation across text and figure:
-homogenizing titles of ways to use github
+**Highlight**: There are ways to use github that allow different degrees of collaboration that do not require too many technical skills.
 
@@
 
-Data was generated using Google docs, then manually saved as csv file "scatterblob_data_raw.csv" in the `data` folder.
+Data was assembled collaboratively using Google docs, then manually saved as a "csv" file called `scatterblob_data_raw.csv` in the `data` folder.
 
-Data for this figure was generated on a collaborative [google spread sheet](https://docs.google.com/spreadsheets/d/1Ls0DofQWSZQsqtP4OLFj326sGfWsklrI2tA1GNUTR6g/edit#gid=0).
+The collaborative [google spread sheet](https://docs.google.com/spreadsheets/d/1zCRgctjfjE2xZN9MkqfFh222K6bvVvA3gT0UdkL_CS8/edit#gid=0), features a first column listing the ways to use GitHub that were addressed in the manuscript (`r paste0(uses[1:12], collapse = "; " )`).
 
-[Data, version 2](https://docs.google.com/spreadsheets/d/1zCRgctjfjE2xZN9MkqfFh222K6bvVvA3gT0UdkL_CS8/edit#gid=0).
+The column _`r column_names[6]`_ corresponds to the degree of difficulty that was perceived by the authors.
+when assembling the data, based on personal experience.
+We quickly realized this varied greatly across authors, and that this variation seemed to depend on which github tools were previously known or mastered by the authors.
+
+The columns tagged as _Cognitive load -_ showcase a different way to assess technical difficulty of GitHub uses, measured as cognitive load (explained in the next section).
+
+The columns tagged as _degree of collaboration_ showcase the span of collaboration that can be achieved with each tool, as perceived by the authors.
 
@@
 
-Cognitive load [was measured in a different file](https://docs.google.com/spreadsheets/d/1OLBR3M0uV3PMSazWUYHgPeX28wllAgS4PIlJXaNu-2o/edit#gid=0).
+[Cognitive load](https://docs.google.com/spreadsheets/d/1YipCCdg5Z8w-IQO67rFfMBSTpLjO-_7HiW44gqzTXPM/edit#gid=0) was measured as follows:
 
-[Cognitive load, version 2](https://docs.google.com/spreadsheets/d/1YipCCdg5Z8w-IQO67rFfMBSTpLjO-_7HiW44gqzTXPM/edit#gid=0).
+1. We first created a list of skills that are needed to implement different GitHub uses. These occupied a column each.
+2. For each GitHub use listed on the first column, we went through each column, and marked a 1 if a skill was needed for that particular GitHub use, and 0 if the skill was not needed. 
+3.
+The sum of values across columns provides a measure of cognitive load required for a user that is a "GitHub beginner" to implement any GitHub use.
+The column _`r column_names[3]`_ reflects this number.
+4.
+As many GitHub uses tied with the same cognitive load value, we resourced to perceived difficulty to break ties and avoid overlap of uses in the figure, mainly to improve visualization of the data.
+The column _`r column_names[5]`_ shows this adjustment.
+5.
+Finally, we ordered the GitHub uses in increasing order following _`r column_names[5]`_, and assigned a sequential value of cognitive load, from 1 to _maximum number of GitHub uses_.
+This is column _`r column_names[4]`_
 
-Reading the data csv file:
+## Reading the data csv file:
 
@@
 scatterblob_data <- read_csv(here("data", "scatterblob_data_raw.csv"))
+head(scatterblob_data)
 #  View(scatterblob_data)
@@
 
-Creating the `my_data` object from :
+Cleaning the raw data and saving it as a `my_data` object:
 
@@
 names(scatterblob_data)
-scatterblob_data$x1 <- scatterblob_data$`Min degree of collaborativeness X1`
-scatterblob_data$x2 <- scatterblob_data$`Max degree of collaborativeness X2`
+scatterblob_data$x1 <- scatterblob_data$`Min degree of collaboration X1`
+scatterblob_data$x2 <- scatterblob_data$`Max degree of collaboration X2`
 scatterblob_data$y_real <- scatterblob_data$`Cognitive load - real - non-overlapping`
@@
 ```
-![Degree of collaboration VS raw technical difficulty](../content/images/scatterblob_0.png)
+![Degree of collaboration VS technical difficulty (real, non-overlapping)](../content/images/scatterblob_0.png)
 
@@
 
-![Degree of collaboration VS Even technical difficulty](../content/images/scatterblob_1-viridis-turbo.png)
+![Degree of collaboration VS technical difficulty (sequential)](../content/images/scatterblob_1-viridis-turbo.png)

### 2022-06-09 manuscript.tex
Merge pull request #224 from SORTEE-Github-Hackathon/RCO-author-name-fix [ci skip]
This build is based on
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/6f8258b509eed4946bfc21d796eab05bbae47d1d.

This commit was created by the following CI build and job:
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/6f8258b509eed4946bfc21d796eab05bbae47d1d/checks
https://github.com/SORTEE-Github-Hackathon/manuscript/actions/runs/2466367408

@@
 This manuscript
-(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/c579f2e6dabd3334b02f563bb8ac53bfd042db72/}{permalink})
+(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/6f8258b509eed4946bfc21d796eab05bbae47d1d/}{permalink})
 was automatically generated
-from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/c579f2e6dabd3334b02f563bb8ac53bfd042db72}{SORTEE-Github-Hackathon/manuscript@c579f2e}
-on June 8, 2022.
+from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/6f8258b509eed4946bfc21d796eab05bbae47d1d}{SORTEE-Github-Hackathon/manuscript@6f8258b}
+on June 9, 2022.
 
@@
   Département de biologie, Université de Sherbrooke, Québec, Canada
-\item
-  \textbf{Friederike Hillemann}
-  \includegraphics[width=0.16667in,height=0.16667in]{images/orcid.svg}
-  \href{https://orcid.org/0000-0002-8992-0676}{0000-0002-8992-0676}
-  · \includegraphics[width=0.16667in,height=0.16667in]{images/github.svg}
-  \href{https://github.com/fhillemann}{fhillemann}
-  Department of Human Behavior, Ecology and Culture, Max Planck Institute for Evolutionary Anthropology, Leipzig, Germany
 \item
@@
 \endhead
+\textbf{repository}: Commonly shortened to ``repo'', a repository is a collection of files (\emph{e.g.}, a directory) tracked by Git.
+Repositories are managed by an owner and can be listed as ``public'' where the repository will be visible to all GitHub users or ``private'', where the repository is visible only to authorized users.
+\\
+\textbf{fork}: A fork is a copy of a \textbf{repository} hosted on GitHub.
+If a repository is public, then anyone can make a fork.
+Even if they do not have access to \textbf{push} to the original repository, they can make a fork and edit it independently.
+Forks are linked to the original GitHub repository and ``upstream'' changes (i.e.~those in the original repository) can be \textbf{merged} to keep the fork up to date with the original project.
+Changes made in the fork can be integrated into the original project via \textbf{pull requests}.
+\\
+\textbf{clone}: Cloning a \textbf{repository} is a way of making a local copy (i.e.~on your computer) of a GitHub \textbf{repository}.
+If you have access to \textbf{push} to a \textbf{repository}, this can be a first step to contributing to a project.
+\\
 \textbf{branch}: A git branch is an alternative line of development for a project (repository).
@@
 \\
-\textbf{clone}: Cloning a \textbf{repository} is a way of making a local copy (i.e.~on your computer) of a GitHub \textbf{repository}.
-If you have access to \textbf{push} to a \textbf{repository}, this can be a first step to contributing to a project.
-\\
 \textbf{commit}: Commits are snapshots of the development of a project.
@@
 Commits can include changes in multiple files and must include a brief commit message describing the changes made.
-A typical workflow is to make some related changes in files, add a commit message (e.g.~``generate and include fig1 in results''), and after several commits \textbf{push} those commits to the remote (i.e., cloud-based) GitHub \textbf{repository}.
-\\
-\textbf{fork}: A fork is a copy of a \textbf{repository} hosted on GitHub.
-If a repository is public, then anyone can make a fork.
-Even if they do not have access to \textbf{push} to the original repository, they can make a fork and edit it independently.
-Forks are linked to the original GitHub repository and ``upstream'' changes (i.e.~those in the original repository) can be \textbf{merged} to keep the fork up to date with the original project.
-Changes made in the fork can be integrated into the original project via \textbf{pull requests}.
-\\
-\textbf{merge}: Combining \textbf{commits} from two different branches together into one \textbf{branch} \\
+A typical workflow is to make some related changes in files, add a commit message (e.g.~``generate and include fig1 in results''), and after several commits \textbf{push} those commits to the remote (\emph{i.e.}, cloud-based) GitHub \textbf{repository}.
+\\
+\textbf{push/pull}: When \textbf{commits} are made in a project locally, they must be synced with the remote GitHub repository by \textbf{pushing} them.
+Changes on a GitHub repository can then be \textbf{pulled} to keep your local version of the project up-to-date.
+\\
 \textbf{pull request}: A pull request is a request that the owner(s) of a GitHub repository integrate changes you've made on either a \textbf{branch} in the repository or in your own \textbf{fork}.
@@
 \\
-\textbf{push/pull}: When \textbf{commits} are made in a project locally, they must be synced with the remote GitHub repository by \textbf{pushing} them.
-Changes on a GitHub repository can then be \textbf{pulled} to keep your local version of the project up-to-date.
-\\
-\textbf{repository}: Commonly shortened to ``repo'', a repository is a collection of files (\emph{e.g.}, a directory) tracked by Git.
-Repositories are managed by an owner and can be listed as ``public'' where the repository will be visible to all GitHub users or ``private'', where the repository is visible only to authorized users.
-\\
+\textbf{merge}: Combining \textbf{commits} from two different branches together into one \textbf{branch} \\
 \textbf{release}: At any point a release can be made on GitHub to mark a significant milestone in the progression of a \textbf{repository}.
@@
 \\
-\textbf{community}: A forum where GitHub users can ask for advice, offer solutions to questions, and share ideas (https://github.community/). \\
+\textbf{community}: A forum where GitHub users can ask for advice, offer solutions to questions, and share ideas (\url{https://github.community/}). \\
 \bottomrule

### 2022-06-09 manuscript.tex
Merge pull request #226 from SORTEE-Github-Hackathon/RCO-reorder-box-1 [ci skip]
This build is based on
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/55dfe2ab70354dd7be425790d6bcbeb459fbb92e.

This commit was created by the following CI build and job:
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/55dfe2ab70354dd7be425790d6bcbeb459fbb92e/checks
https://github.com/SORTEE-Github-Hackathon/manuscript/actions/runs/2466364113

@@
 This manuscript
-(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/6f8258b509eed4946bfc21d796eab05bbae47d1d/}{permalink})
+(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/55dfe2ab70354dd7be425790d6bcbeb459fbb92e/}{permalink})
 was automatically generated
-from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/6f8258b509eed4946bfc21d796eab05bbae47d1d}{SORTEE-Github-Hackathon/manuscript@6f8258b}
+from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/55dfe2ab70354dd7be425790d6bcbeb459fbb92e}{SORTEE-Github-Hackathon/manuscript@55dfe2a}
 on June 9, 2022.
@@
   Département de biologie, Université de Sherbrooke, Québec, Canada
+\item
+  \textbf{Friederike Hillemann}
+  \includegraphics[width=0.16667in,height=0.16667in]{images/orcid.svg}
+  \href{https://orcid.org/0000-0002-8992-0676}{0000-0002-8992-0676}
+  · \includegraphics[width=0.16667in,height=0.16667in]{images/github.svg}
+  \href{https://github.com/fhillemann}{fhillemann}
+  Department of Human Behavior, Ecology and Culture, Max Planck Institute for Evolutionary Anthropology, Leipzig, Germany
 \item

### 2022-06-09 manuscript.tex
Merge pull request #225 from SORTEE-Github-Hackathon/RCO-software-to-code [ci skip]
This build is based on
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/f4614eb536313e122f922ad46d0e4f9f246b724a.

This commit was created by the following CI build and job:
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/f4614eb536313e122f922ad46d0e4f9f246b724a/checks
https://github.com/SORTEE-Github-Hackathon/manuscript/actions/runs/2466714947

@@
 This manuscript
-(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/55dfe2ab70354dd7be425790d6bcbeb459fbb92e/}{permalink})
+(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/f4614eb536313e122f922ad46d0e4f9f246b724a/}{permalink})
 was automatically generated
-from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/55dfe2ab70354dd7be425790d6bcbeb459fbb92e}{SORTEE-Github-Hackathon/manuscript@55dfe2a}
+from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/f4614eb536313e122f922ad46d0e4f9f246b724a}{SORTEE-Github-Hackathon/manuscript@f4614eb}
 on June 9, 2022.
@@
 Most scientists, including ecologists and evolutionary biologists, are increasingly dependent on computational tools in their research\textsuperscript{\protect\hyperlink{ref-fJWFe93e}{1}}.
-Researchers write and use code as part of their scientific workflow to perform a wide-variety of tasks ranging from data management, data analysis, and study replication, to the application and the development of tools for hypothesis testing.
+Researchers write and use software packages or data analysis code (hereafter, code) as part of their scientific workflow to perform a wide-variety of tasks ranging from data management, data analysis, and study replication, to the application and the development of tools for hypothesis testing.
 To maintain code for scientific collaboration requires an efficient and well-documented work-flow\textsuperscript{\protect\hyperlink{ref-1Kqna6l2}{2}}.
 To facilitate this process, scientists have been increasingly adopting tools from information and systems technology, such as cloud-based services for documentation and version control (\emph{e.g.}, from the Google Suite, with Docs, Sheets, and Drive; the Microsoft Suite, with Word, Excel, and OneDrive; and GitHub;\textsuperscript{\protect\hyperlink{ref-10ghgV3S8}{3}}).
-However, most researchers lack exposure to adequate software development practices and are required to dedicate valuable time and effort to self-teach the use of research-facilitating tools, and thus may be limited in their ability to adhere to adequate standards of scientific code quality and maintenance\textsuperscript{\protect\hyperlink{ref-fJWFe93e}{1},\protect\hyperlink{ref-10SpoByIw}{4},\protect\hyperlink{ref-O6UbstGG}{5}}.
+However, most researchers lack exposure to adequate code development practices and are required to dedicate valuable time and effort to self-teach the use of research-facilitating tools, and thus may be limited in their ability to adhere to adequate standards of scientific code quality and maintenance\textsuperscript{\protect\hyperlink{ref-fJWFe93e}{1},\protect\hyperlink{ref-10SpoByIw}{4},\protect\hyperlink{ref-O6UbstGG}{5}}.
 Here, we review and discuss one of the most used web-based platforms for computational version control and collaboration, GitHub, and provide researchers in ecology and evolutionary biology (EEB) with practical workflows aimed at facilitating their scientific code and management process.
@@
 With over 73 million registered users, as of 2022, GitHub is the most widely-used web platform for collaborating on computer code\textsuperscript{\protect\hyperlink{ref-nwCtHDCn}{6}}.
-GitHub provides a simplified but powerful web interface that allows users to participate in projects, contribute code, report and discuss software bugs, discover existing code and data, and publish new code.
+GitHub provides a simplified but powerful web interface that allows users to participate in projects, contribute code, report and discuss code bugs, discover existing code and data, and publish new code.
 Through version control, users have a detailed, chronological record of the files and directories stored in their repositories (see \protect\hyperlink{definitions}{Box 1};\textsuperscript{\protect\hyperlink{ref-RVetqmsg}{7}}).
@@
 
-Git is the version control software system that enables all the collaborative tools available on GitHub.
+Git is the version control system that enables all the collaborative tools available on GitHub.
 Although the understanding of basic concepts of Git (such as commit, push, pull, checkout; see \protect\hyperlink{definitions}{Box 1}) is necessary, the GitHub web-based platform and its integrated development environments (such as the GitHub Desktop) allow users to perform most repository and data management operations without opening Git command-line sessions.
@@
 Nevertheless, although multiple articles have encouraged researchers in EEB to adopt GitHub as part of their research process\textsuperscript{\protect\hyperlink{ref-10ghgV3S8}{3},\protect\hyperlink{ref-3DKwn1sY}{14}}, its use is still not widespread.
-First-time users without formal training in information technology may face steep learning curves because GitHub and its features have been centered on collaboration for software development in information systems\textsuperscript{\protect\hyperlink{ref-139b0pSGc}{15}}.
+First-time users without formal training in information technology may face steep learning curves because GitHub and its features have been centered on collaboration for code development in information systems\textsuperscript{\protect\hyperlink{ref-139b0pSGc}{15}}.
 Moreover, domain-specific perspectives and resources providing tractable examples and practical guidance for researchers in EEB on GitHub are scarce (but see https://ourcodingclub.github.io; https://www.openscapes.org).
@@
 \textbf{release}: At any point a release can be made on GitHub to mark a significant milestone in the progression of a \textbf{repository}.
-While this GitHub feature is designed with releases of new versions of software in mind (\emph{e.g.}, v1.0.0), it can also be used to create a snapshot of a repository at significant stages like submission, revision, and acceptance of an associated manuscript.
+While this GitHub feature is designed with releases of new versions of code in mind (\emph{e.g.}, v1.0.0), it can also be used to create a snapshot of a repository at significant stages like submission, revision, and acceptance of an associated manuscript.
 \\
@@
 GitHub provides an open and transparent platform that can be used for either directly providing feedback on research products or building a to-do list from reviewer comments.
-Peer review of research software by the open software development community rOpenSci (https://ropensci.org/software-review/) and of research software and associated manuscripts by the Journal of Open Source Software (https://joss.readthedocs.io/en/latest/submitting.html) requires that submitted work is hosted on GitHub and their review processes make use of GitHub issues.
+Peer review of research code by the open software development community rOpenSci (\url{https://ropensci.org/software-review/}) and of research software and associated manuscripts by the Journal of Open Source Software (\url{https://joss.readthedocs.io/en/latest/submitting.html}) requires that submitted work is hosted on GitHub and their review processes make use of GitHub issues.
 rOpenSci's efforts have resulted in many well-used R packages for ecology research including rfishbase\textsuperscript{\protect\hyperlink{ref-Xsdcv6q}{33}} and taxize\textsuperscript{\protect\hyperlink{ref-FVBWKkZu}{34}}.
@@
 
-Some specialized journals, such as the the Journal of Open Source Software (\url{https://joss.readthedocs.io/en/latest/submitting.html}), require that submitted work is hosted on GitHub and their review processes make use of GitHub issues.
-Peer review of research software by rOpenSci (\url{https://ropensci.org/software-review/}) also makes use of many features of GitHub to streamline and automate parts of the review process.
-rOpenSci's efforts have resulted in many well-used R packages for ecology research including rfishbase\textsuperscript{\protect\hyperlink{ref-Xsdcv6q}{33}} and taxize\textsuperscript{\protect\hyperlink{ref-FVBWKkZu}{34}}.
-Although the use of GitHub in peer-review is currently restricted to these specialized cases, they may provide a model for peer-review in more traditional EEB journals for manuscripts that make use of code.
-
 \hypertarget{open-science-discussion}{%
@@
 
-The development of research software continues, and so does the need to consider project continuity, especially in EEB where graduate students, research assistants, and postdoctoral fellows often hold relatively short-term positions\textsuperscript{\protect\hyperlink{ref-D4C4k4ak}{37}}.
-Often with these types of short-term research projects, once the contract expires, the research software upkeep tends to fall off as the researchers move on to new projects.
-Additionally, if the research software is kept on only the researcher's personal devices, it becomes increasingly difficult to access the software and code for future uses.
-As projects or contracts end, there should be a handover period of this software in order for the next cohort of researchers to reuse what was already developed\textsuperscript{\protect\hyperlink{ref-4ny1onB0}{8},\protect\hyperlink{ref-D4C4k4ak}{37}}.
-
-GitHub facilitates project continuity among research software and research code by providing tools that make this handover period easier.
-As we have already mentioned, using Git for code in Ecology and Evolution can allow for a ``paper trail'' of sorts to be created for the research software, thus allowing for future users of the code access to the entire history of the project\textsuperscript{\protect\hyperlink{ref-3DKwn1sY}{14}}.
-Additionally, GitHub allows for repositories and organizations to have designated Code Owners\textsuperscript{\protect\hyperlink{ref-s91uGRZ2}{38}}; these code owners can change through time allowing for the transition of research software from one cohort of researchers to the next\textsuperscript{\protect\hyperlink{ref-iIEKCTLU}{26}}.
-There are also multiple means by which to archive software dependency information with GitHub.
+The development of research code continues, and so does the need to consider project continuity, especially in EEB where graduate students, research assistants, and postdoctoral fellows often hold relatively short-term positions\textsuperscript{\protect\hyperlink{ref-D4C4k4ak}{37}}.
+Often with these types of short-term research projects, once the contract expires, the research code upkeep tends to fall off as the researchers move on to new projects.
+Additionally, if the code is kept on only the researcher's personal devices, it becomes increasingly difficult to access the code for future uses.
+As projects or contracts end, there should be a handover period of this code in order for the next cohort of researchers to reuse what was already developed\textsuperscript{\protect\hyperlink{ref-4ny1onB0}{8},\protect\hyperlink{ref-D4C4k4ak}{37}}.
+
+GitHub facilitates project continuity among research code by providing tools that make this handover period easier.
+As we have already mentioned, using Git for code in Ecology and Evolution can allow for a ``paper trail'' of sorts to be created for the code, thus allowing for future users of the code access to the entire history of the project\textsuperscript{\protect\hyperlink{ref-3DKwn1sY}{14}}.
+Additionally, GitHub allows for repositories and organizations to have designated Code Owners\textsuperscript{\protect\hyperlink{ref-s91uGRZ2}{38}}; these code owners can change through time allowing for the transition of code from one cohort of researchers to the next\textsuperscript{\protect\hyperlink{ref-iIEKCTLU}{26}}.
+There are also multiple means by which to archive code dependency information with GitHub.
 Dependencies can be described in README files, added to environment.yml and/or an environment.txt file, or stored in a repository using tools such as renv (\url{https://rstudio.github.io/renv/articles/renv.html}).
@@
 Within EEB projects, tasks are often divided among contributors taking various roles (see CRediT taxonomy, \url{https://casrai.org/credit/}).
-The creation of project repositories is commonly the purview of those involved in the software, formal analysis, and/or visualization components of the project through their roles as code writers.
+The creation of project repositories is commonly the purview of those involved in the code, formal analysis, and/or visualization components of the project through their roles as code writers.
 However, the structural components of a typical GitHub repository and the derived EEB-specific templates can provide functional ways for other collaborators not contributing to code to be engaged in aspects of repository design in a way that improves institutional memory and facilitates project continuity.

### 2022-06-09 manuscript.tex
Merge pull request #227 from shafieisabets/main [ci skip]
This build is based on
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/b1ebce0223ca94ed6e25905a066622e539a2724d.

This commit was created by the following CI build and job:
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/b1ebce0223ca94ed6e25905a066622e539a2724d/checks
https://github.com/SORTEE-Github-Hackathon/manuscript/actions/runs/2466723285

@@
 This manuscript
-(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/f4614eb536313e122f922ad46d0e4f9f246b724a/}{permalink})
+(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/b1ebce0223ca94ed6e25905a066622e539a2724d/}{permalink})
 was automatically generated
-from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/f4614eb536313e122f922ad46d0e4f9f246b724a}{SORTEE-Github-Hackathon/manuscript@f4614eb}
+from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/b1ebce0223ca94ed6e25905a066622e539a2724d}{SORTEE-Github-Hackathon/manuscript@b1ebce0}
 on June 9, 2022.
@@
 8.
-\textbf{If you are an educator, include lectures on reproducibility and tools for creating reproducible workflows in the curricula.}.
-Some graduate programs now include coursework on course Rmarkdown and GitHub.
+\textbf{If you are an educator, include lectures on reproducibility and tools for creating reproducible workflows in the curricula.} Some graduate programs include coursework on course Rmarkdown and GitHub.
 Getting students started with these tools earlier will prevent the resistance that comes from working with a less reproducible workflow for a longer period of time.
@@
 Temporary (personal) drive storage & One Drive and the Office Suite & yes & yes & yes & yes & limited free version \& paid & NA & 5 GB free, up to 1TB paid & yes \\
-Collaborative code/text editors & Overleaf (online latex editor) & yes & yes & yes & NA & NA & NA & 1MB for individual .tex, 50MB for individual files, unlimited project size & yes \\
+Collaborative code/text editors & Overleaf (online latex editor) & yes & yes & yes & NA & NA & NA & 1MB for individual .tex, 50 MB for individual files, unlimited project size & yes \\
 Collaborative code/text editors & Jupyter Notebook & yes & ?

### 2022-06-09 R/scatterblob.Rmd

@@
 
-The column _`r column_names[6]`_ corresponds to the degree of difficulty that was perceived by the authors.
-when assembling the data, based on personal experience.
+The column _`r column_names[6]`_ corresponds to the degree of difficulty that was perceived by the authors when assembling the data, based on personal experience.
 We quickly realized this varied greatly across authors, and that this variation seemed to depend on which github tools were previously known or mastered by the authors.

### 2022-06-09 manuscript.tex
Merge pull request #212 from SORTEE-Github-Hackathon/scatterblob-edits [ci skip]
This build is based on
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/995c4b12819cee4b095a8c81c7f5303afab9534e.

This commit was created by the following CI build and job:
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/995c4b12819cee4b095a8c81c7f5303afab9534e/checks
https://github.com/SORTEE-Github-Hackathon/manuscript/actions/runs/2470250121

@@
 This manuscript
-(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/b1ebce0223ca94ed6e25905a066622e539a2724d/}{permalink})
+(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/995c4b12819cee4b095a8c81c7f5303afab9534e/}{permalink})
 was automatically generated
-from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/b1ebce0223ca94ed6e25905a066622e539a2724d}{SORTEE-Github-Hackathon/manuscript@b1ebce0}
+from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/995c4b12819cee4b095a8c81c7f5303afab9534e}{SORTEE-Github-Hackathon/manuscript@995c4b1}
 on June 9, 2022.

### 2022-06-09 manuscript.tex
Merge pull request #233 from SORTEE-Github-Hackathon/RCO-box-2 [ci skip]
This build is based on
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/397be525b3f7dd06eb5e7e570a461d840fcb5a26.

This commit was created by the following CI build and job:
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/397be525b3f7dd06eb5e7e570a461d840fcb5a26/checks
https://github.com/SORTEE-Github-Hackathon/manuscript/actions/runs/2470691558

@@
 This manuscript
-(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/995c4b12819cee4b095a8c81c7f5303afab9534e/}{permalink})
+(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/397be525b3f7dd06eb5e7e570a461d840fcb5a26/}{permalink})
 was automatically generated
-from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/995c4b12819cee4b095a8c81c7f5303afab9534e}{SORTEE-Github-Hackathon/manuscript@995c4b1}
+from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/397be525b3f7dd06eb5e7e570a461d840fcb5a26}{SORTEE-Github-Hackathon/manuscript@397be52}
 on June 9, 2022.
@@
 Getting students started with these tools earlier will prevent the resistance that comes from working with a less reproducible workflow for a longer period of time.
-\\
+(see example \url{https://github.com/rmcelreath/stat_rethinking_2022}) \\
 9.

### 2022-06-09 manuscript.tex
Merge pull request #232 from SORTEE-Github-Hackathon/RCO-box-1 [ci skip]
This build is based on
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/024357f04df193fe87662943d6e0029321eca2a5.

This commit was created by the following CI build and job:
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/024357f04df193fe87662943d6e0029321eca2a5/checks
https://github.com/SORTEE-Github-Hackathon/manuscript/actions/runs/2470979213

@@
 This manuscript
-(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/397be525b3f7dd06eb5e7e570a461d840fcb5a26/}{permalink})
+(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/024357f04df193fe87662943d6e0029321eca2a5/}{permalink})
 was automatically generated
-from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/397be525b3f7dd06eb5e7e570a461d840fcb5a26}{SORTEE-Github-Hackathon/manuscript@397be52}
+from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/024357f04df193fe87662943d6e0029321eca2a5}{SORTEE-Github-Hackathon/manuscript@024357f}
 on June 9, 2022.
@@
 Repositories are managed by an owner and can be listed as ``public'' where the repository will be visible to all GitHub users or ``private'', where the repository is visible only to authorized users.
+Repositories can be either ``local'' and saved on an individual's computer or ``remote'' and stored on the cloud via GitHub's web platform.
 \\
@@
 \\
-\textbf{branch}: A git branch is an alternative line of development for a project (repository).
-Branches allow to add new features or modifications to the project without affecting the main part of the project.
+\textbf{branch}: Git workflow timelines or repositories are analogous to trees, with a main working project and diverging branches that are pointers to changes during the development process.
+A git branch is an alternative line of development for a project (repository).
+Branches allow users to add new features or modifications to the project without affecting the main part of the project.
 Development branches can be created at any point in time and work on each branch can continue independently.

### 2022-06-10 manuscript.tex
Merge pull request #228 from SORTEE-Github-Hackathon/phpb-filtering-section-a [ci skip]
This build is based on
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/ea3d52568405d25c555daffaef4bbf5a40954c92.

This commit was created by the following CI build and job:
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/ea3d52568405d25c555daffaef4bbf5a40954c92/checks
https://github.com/SORTEE-Github-Hackathon/manuscript/actions/runs/2477668636

@@
 This manuscript
-(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/024357f04df193fe87662943d6e0029321eca2a5/}{permalink})
+(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/ea3d52568405d25c555daffaef4bbf5a40954c92/}{permalink})
 was automatically generated
-from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/024357f04df193fe87662943d6e0029321eca2a5}{SORTEE-Github-Hackathon/manuscript@024357f}
-on June 9, 2022.
+from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/ea3d52568405d25c555daffaef4bbf5a40954c92}{SORTEE-Github-Hackathon/manuscript@ea3d525}
+on June 10, 2022.
 
@@
 
-\hypertarget{practical-ways-of-using-github-in-eeb}{%
-\subsection{12 Practical ways of using GitHub in EEB}\label{practical-ways-of-using-github-in-eeb}}
-
-\hypertarget{storing-a-research-compendium}{%
-\subsubsection{Storing a research compendium}\label{storing-a-research-compendium}}
-
-In EEB, a research compendium includes all computational materials related to research production, including data, code for analyses and protocols.
-Having multiple copies of these files is important to ensure that research can continue should one copy of a file be accidentally modified or deleted.
-Many researchers begin using GitHub as a means to backup their research compendium\textsuperscript{\protect\hyperlink{ref-MwwMapRG}{18}} to a remote server (pull-commit-push, see \protect\hyperlink{definitions}{Box 1}).
-The GitHub repository serves as a centralized backup and also allows users to synchronize files and work on any device with internet access.
-Because GitHub is built on git, version control features are also available, allowing users to re-visit or even restore previous versions of the repository.
-Storing a research compendium as a GitHub repository has additional benefits such as facilitating collaboration, integration with data and code archiving services, and contribution to open science, all discussed in sections below.
-
-Unfortunately, GitHub repositories have file size limits, so they may not be appropriate for synchronizing large data files.
-Commits (see \protect\hyperlink{definitions}{Box 1}{]}) greater than 50 MB receive a warning and commits larger than 100 MB are blocked (\textsuperscript{\protect\hyperlink{ref-1Co6ZZjF1}{19}}).
-Therefore, it is recommended that large datasets are stored only locally or using other cloud services.
-
-\hypertarget{virtual-lab-notebook}{%
-\subsubsection{Virtual lab notebook}\label{virtual-lab-notebook}}
-
-Lab notebooks are the virtual or physical notebooks used to help researchers at any career stage keep track of their research methods or laboratory policies\textsuperscript{\protect\hyperlink{ref-wwHxTOtm}{20}}.
-Digital lab notebooks stored in the cloud provide clear benefits given the ease with which documents can be shared with new employees and updated as policy changes or experimental methods are modified\textsuperscript{\protect\hyperlink{ref-10V7x4H4l}{21}}.
-Increasingly, researchers are leveraging GitHub's underlying version control system to maintain and share digital lab notebooks\textsuperscript{\protect\hyperlink{ref-10ghgV3S8}{3}}.
-At least for aspects of a research project that involve writing code, a GitHub repository is a form of a lab notebook; when changes are made to files in a version controlled repository, the author of those changes makes a commit (\protect\hyperlink{definitions}{Box 1}) accompanied by a message describing the changes and the reason for them.
-Later, the entire history of commits and their messages are viewable and can be audited similar to a physical lab notebook\textsuperscript{\protect\hyperlink{ref-4ny1onB0}{8}}.
-GitHub issues (\protect\hyperlink{definitions}{Box 1}) can be used to prioritize lab objectives and goals, as well as track any status updates.
-Some EEB labs have even turned their lab notebooks into shareable websites (\url{https://scheuerell-lab.github.io/lab-book}; \url{https://github.com/HuckleyLab/how_we_work}) as a centralized location for all lab resources.
+\hypertarget{twelve-practical-ways-github-can-accelerate-research-in-ecology-and-evolution}{%
+\subsection{Twelve practical ways GitHub can accelerate research in ecology and evolution}\label{twelve-practical-ways-github-can-accelerate-research-in-ecology-and-evolution}}
+
+\hypertarget{storing-and-sharing-research-compendia}{%
+\subsubsection{Storing and sharing research compendia}\label{storing-and-sharing-research-compendia}}
+
+An EEB research compendium includes all computational materials related to research production, including data, code for analyses and protocols.
+Having copies of these files safely stored is essential to protect against accidental modifications or deletions.
+Many researchers begin using GitHub as a means to store (or backup) their research compendium\textsuperscript{\protect\hyperlink{ref-MwwMapRG}{18}} to a centralized, readily-available remote server (see \protect\hyperlink{definitions}{Box 1}).
+A centralized research compendium stored in a version-controlled repository has the advantages of facilitating collaboration, integrating data and code archiving services, allowing file versions to be accessed and restored, and contributes to open science (see sections below).
+
+GitHub limits committed file sizes to 100 Mb (megabytes) (\textsuperscript{\protect\hyperlink{ref-1Co6ZZjF1}{19}}), which can make it challenging for centralizing research compedia containing larger file sizes.
+Users may still version large files using Git Large File Storage (LFS;\textsuperscript{\protect\hyperlink{ref-11GtZ7icJ}{20}}/) text pointers, but may have to rely on external file storage alternatives (such as local or cloud-hosting).
+
+\hypertarget{virtual-laboratory-notebooks}{%
+\subsubsection{Virtual laboratory notebooks}\label{virtual-laboratory-notebooks}}
+
+Laboratory notebooks help researchers track their research notes, methods, policies and protocols\textsuperscript{\protect\hyperlink{ref-wwHxTOtm}{21}}.
+Virtual laboratory notebooks can be stored in GitHub repositories and provide the benefits of simultaneous, centralized and selective access, and allows for the easy update of policies and experiment protocols\textsuperscript{\protect\hyperlink{ref-10V7x4H4l}{22}}.
+Researchers have been increasingly using GitHub to maintain versions and share digital laboratory notebooks\textsuperscript{\protect\hyperlink{ref-10ghgV3S8}{3}} (\emph{e.g.}, \url{https://scheuerell-lab.github.io/lab-book}; \url{https://github.com/HuckleyLab/how_we_work}).
+
+At least for aspects of a research project that involve writing code, a GitHub repository is a form of a laboratory notebook; when changes are made to files in a version controlled repository, the author of those changes makes a commit (\protect\hyperlink{definitions}{Box 1}) accompanied by a description of changes.
+Later, the entire history of commits and their commit messages are viewable and can be audited similar to a physical laboratory notebook\textsuperscript{\protect\hyperlink{ref-4ny1onB0}{8}}.
+GitHub issues (\protect\hyperlink{definitions}{Box 1}) can be used to prioritize laboratory objectives and goals, as well as track any status updates.
 
@@
 
-Modern EEB research is highly collaborative, bringing together multidisciplinary teams from various institutions.
+Modern research in ecology and evolution is highly collaborative, bringing together multidisciplinary teams from various institutions.
 On GitHub, collaborators can share feedback, brainstorm ideas, and troubleshoot problems (Figure \ref{fig:github-diagram}).
-GitHub has an ``Issues'' feature that allows for discrete tasks and sub-tasks to be identified, assigned to team members, and categorized with custom labels.
-The new GitHub ``Discussion'' feature serves as a message board for conversation.
-Scripts, commit messages, and pull requests can be linked directly to issues and discussions, providing a clear record of project workflow.
+Project management can happen via three GitHub repository features: ``Issues'', ``Discussion'' and ``Projects''.
+Github Issues allow for discrete tasks and sub-tasks to be identified, assigned to team members, and categorized with custom labels.
+Github Discussions serve as a message board for conversation.
+Finally, GitHub Projects integrate issues and pull requests on automated spreadsheets and project boards, providing users with real-time tracking of project priorities and status\textsuperscript{\protect\hyperlink{ref-RhBKe0MG}{23}}.
+Scripts, commit messages, and pull requests can be linked directly to issues, discussions, and projects providing a clear record of project workflow.
 The use of GitHub for all project-related conversation and planning, rather than e-mail or messaging tools, makes it easier to keep track of progress throughout the lifespan of a project.
 Unlike emails and messages which can get lost as more new tasks arise, GitHub issues are intentionally closed by repository administrators hiding the issue from view (closed issues remain accessible but not immediately visible).
-Fortunately, it is not essential for all team members to have proficiency in git or programming, as users can interact with Issues and Discussions via web browser or e-mail (e-mail responses still get tracked as comments on the focal GitHub issue).
-For larger projects with many team members and tens or hundreds of GitHub issues to sort through, project management software like ZenHub, can help prioritize issues and pull requests.
-ZenHub's web interface includes a GitHub Issue visualizer where users can organize issues into high priority or backlogged tasks and link issues together when they are related to a shared project goal or milestone.
-GitHub is currently beta testing a similar project management feature called GitHub Projects\textsuperscript{\protect\hyperlink{ref-RhBKe0MG}{22}}.
-GitHub can also be integrated with other project management software such as Slack (https://slack.github.com/) so that teams are notified through a Slack group chat when updates are made to a repository.
+Project management in GitHub can also be integrated with third-party applications, such as ZenHub (https://www.zenhub.com/) or Slack (https://slack.github.com/).
+ZenHub allows for the enhanced visualization and organization of repositories and their issues, while the GitHub for Slack integration allows notifications from GitHub events to be sent directly to users or group channels\textsuperscript{\protect\hyperlink{ref-1GRWGlDWy}{24}}.
 
@@
 GitHub supports a broad set of mechanisms for hosting educational materials.
-The entire process of running a course, workshop, or lecture, can all be done openly on GitHub including material development, web hosting, and delivery, and even the submission and grading of assignments.
+The entire process of running a course, workshop, or lecture, can all be done openly on GitHub including material development, web hosting, and delivery, and even submission and grading of assignments.
 While there are other purpose-built platforms for this, GitHub provides a free, open-source alternative.
 
-Making presentations can be done through most major high-level programming languages such as R, with \texttt{RMarkdown}\textsuperscript{\protect\hyperlink{ref-QqMezOMg}{23}}, Python, with \texttt{python-ppt} (\url{https://python-pptx.readthedocs.io}), and Julia, with \texttt{Remark.jl} (\url{https://juliapackages.com/p/remark}).
-Since all these programs work via code bases, they can be version-controlled through git and GitHub.
-Once content is made, hosting a course website can be done through GitHub Pages, and there are lots of templates available (e.g., see \url{https://github.com/topics/course-website}).
+Making presentations, syllabi and other course materials can be done through most major high-level programming languages such as R, with \texttt{RMarkdown}\textsuperscript{\protect\hyperlink{ref-QqMezOMg}{25}}, Python, with \texttt{python-ppt} (\url{https://python-pptx.readthedocs.io}), and Julia, with \texttt{Remark.jl} (\url{https://juliapackages.com/p/remark}), and be version-controlled and stored in GitHub.
+Once content is made, hosting a course website can be done through GitHub Pages\textsuperscript{\protect\hyperlink{ref-MDQfMwCW}{26}} (\emph{e.g.}, https://github.com/topics/course-website\textgreater).
 This way, the course content can be available to enrolled students, as well as a global pool of learners and teachers interested in the course material.
-Content can then be delivered via the course website, and/or a GitHub organization with, for example, template repositories for assignments.
-Student submissions are perhaps the most challenging component, but the new GitHub Classroom tool (https://classroom.github.com) allows instructors to host private assignments submitted as code files (.R or .Rmd) or .pdf files, and even build custom autograding tests.
-
-Instructors may only need to incorporate some of these tools given the time required to implement various GitHub features, however it is still valuable to do so and to encourage students to begin learning about version control through interacting with git/GitHub, however minimally, through the course.
-Especially if a central tenet of a given course or educational unit is to introduce or give students experience with version control, reproducibility, and the tools that working professionals in EEB use, then adopting a few of these tools can be a great way to do so.
+Content can then be delivered via the course website, and/or a GitHub Organization with, for example, template repositories for assignments.
+Student submissions are perhaps the most challenging component, but the new GitHub Classroom tool (\url{https://classroom.github.com}) allows instructors to host private assignments to be submitted collaboratively or individually as code or PDF files, and even build autograding tests.
+Although time-consuming to establish, using these features can integrate learning version control and GitHub with the learning course content, and thus boost students feelings of self-efficacy and confidence\textsuperscript{\protect\hyperlink{ref-dqrFjoSb}{27}}.
 
@@
 Aside from free hosting services, another benefit is that GitHub Pages are autogenerated, meaning that when content is modified in the associated GitHub repository, the website instantly updates\textsuperscript{\protect\hyperlink{ref-RVetqmsg}{7}}.
-Though the templates are useful for quickly starting up a new website, users are able to fully customize their Pages websites (for technical details of customizing GitHub Pages site see\textsuperscript{\protect\hyperlink{ref-MXxgZJ45}{24}}).
+Though the templates are useful for quickly starting up a new website, users are able to fully customize their Pages websites (for technical details of customizing GitHub Pages site see\textsuperscript{\protect\hyperlink{ref-MXxgZJ45}{28}}).
 We emphasize that despite the many benefits of using GitHub pages (free hosting, templates, customization), this avenue for creating a website will often be more time intensive than the out-of-the-box platforms.
@@
 DOIs allows tracking and citing research products.
-For this reason, scientists who share code and data through GitHub are strongly encouraged to also submit GitHub repository content to a long-term data archive\textsuperscript{\protect\hyperlink{ref-1Du6fzB8g}{25}}.
+For this reason, scientists who share code and data through GitHub are strongly encouraged to also submit GitHub repository content to a long-term data archive\textsuperscript{\protect\hyperlink{ref-1Du6fzB8g}{29}}.
 Fortunately, both long-term repositories mentioned above (Zenodo and Figshare) have integrations with GitHub.
@@
 Linking one's GitHub repository with Zenodo, etc.
-to obtain a DOI helps work become findable, gives proper attribution, and can ensure long-term stability\textsuperscript{\protect\hyperlink{ref-iIEKCTLU}{26}}.
+to obtain a DOI helps work become findable, gives proper attribution, and can ensure long-term stability\textsuperscript{\protect\hyperlink{ref-iIEKCTLU}{30}}.
 
@@
 However, there are many reasons to share data and code beyond re-use.
-Even if code lacks detailed annotation, it shows the exact steps taken to conduct an analysis, and therefore provides the most detailed look into how to reproduce a given analysis\textsuperscript{\protect\hyperlink{ref-uBJwnPbq}{27}}.
-This is important in light of the reproducibility crisis\textsuperscript{\protect\hyperlink{ref-1HZdsK5Kn}{28}} and will become increasingly important to the collective scientific enterprise as advances in computing power and accessibility unlock the ability to conduct `big data' meta research with data that has already been collected by others.
+Even if code lacks detailed annotation, it shows the exact steps taken to conduct an analysis, and therefore provides the most detailed look into how to reproduce a given analysis\textsuperscript{\protect\hyperlink{ref-uBJwnPbq}{31}}.
+This is important in light of the reproducibility crisis\textsuperscript{\protect\hyperlink{ref-1HZdsK5Kn}{32}} and will become increasingly important to the collective scientific enterprise as advances in computing power and accessibility unlock the ability to conduct `big data' meta research with data that has already been collected by others.
 Failing to include data and code with publications leaves future scientists with fewer open resources from which to understand the world.
@@
 When EEB projects are contained on the GitHub platform, researchers can stay abreast of progress made by other collaborators without the need for meetings or emails.
-Version control\textsuperscript{\protect\hyperlink{ref-K7nbP1Ty}{29}} features also allow users to make progress and changes without worrying about irreparably writing over someone else's work.
+Version control\textsuperscript{\protect\hyperlink{ref-K7nbP1Ty}{33}} features also allow users to make progress and changes without worrying about irreparably writing over someone else's work.
 By enabling more comprehensive remote collaboration, GitHub encourages the exchange of ideas among researchers at different institutions and in different countries, which can serve to improve the quality of the research itself by providing open access to data and code.
 In academic settings, GitHub can also facilitate interactions between research advisors and advisees, providing a platform for students or other trainees to share in-progress code, and flag specific challenges or questions for their supervisors or mentors.
-Periodic code review\textsuperscript{\protect\hyperlink{ref-hm9PaCLD}{30}} can also help advisors identify errors early in the process, and inform further training and mentorship to fill gaps in skills.
+Periodic code review\textsuperscript{\protect\hyperlink{ref-hm9PaCLD}{34}} can also help advisors identify errors early in the process, and inform further training and mentorship to fill gaps in skills.
 
@@
 
-We wrote this manuscript using Manubot\textsuperscript{\protect\hyperlink{ref-YuJbg3zO}{31}}, a collaborative manuscript platform that uses Markdown for writing and GitHub for storing and tracking changes to a manuscript over time.
+We wrote this manuscript using Manubot\textsuperscript{\protect\hyperlink{ref-YuJbg3zO}{35}}, a collaborative manuscript platform that uses Markdown for writing and GitHub for storing and tracking changes to a manuscript over time.
 Manubot uses a GitHub Actions-based typesetting system to compile individual Markdown files stored in a GitHub repository into a single LaTeX document, which can be displayed in Word, HTML, or PDF formats.
@@
 Manubot also allows for straightforward citation management based on URLs or DOIs.
-For more examples of Manubot being used for manuscripts, see\textsuperscript{\protect\hyperlink{ref-YuJbg3zO}{31}}.
+For more examples of Manubot being used for manuscripts, see\textsuperscript{\protect\hyperlink{ref-YuJbg3zO}{35}}.
 
@@
 Other authors can reply to the comments to indicate agreement or disagreement, and to note when changes have been made.
-Other tools can also be used for version control of scientific manuscripts including R Markdown via the bookdown package (\url{https://bookdown.org/}), jupyter notebooks\textsuperscript{\protect\hyperlink{ref-i4FOZpjN}{32}} and a relatively new tool, Quarto (\url{https://quarto.org}).
+Other tools can also be used for version control of scientific manuscripts including R Markdown via the bookdown package (\url{https://bookdown.org/}), jupyter notebooks\textsuperscript{\protect\hyperlink{ref-i4FOZpjN}{36}} and a relatively new tool, Quarto (\url{https://quarto.org}).
 
@@
 Peer review of research code by the open software development community rOpenSci (\url{https://ropensci.org/software-review/}) and of research software and associated manuscripts by the Journal of Open Source Software (\url{https://joss.readthedocs.io/en/latest/submitting.html}) requires that submitted work is hosted on GitHub and their review processes make use of GitHub issues.
-rOpenSci's efforts have resulted in many well-used R packages for ecology research including rfishbase\textsuperscript{\protect\hyperlink{ref-Xsdcv6q}{33}} and taxize\textsuperscript{\protect\hyperlink{ref-FVBWKkZu}{34}}.
+rOpenSci's efforts have resulted in many well-used R packages for ecology research including rfishbase\textsuperscript{\protect\hyperlink{ref-Xsdcv6q}{37}} and taxize\textsuperscript{\protect\hyperlink{ref-FVBWKkZu}{38}}.
 
@@
 In the developmental stages, collaborators can directly see the code for the analysis, manipulate and explore the data themselves, and check for errors.
-Cynically, there is also more insurance against nefarious colleagues that may be tempted to distort results\textsuperscript{\protect\hyperlink{ref-18PTmKJkq}{35}}.
+Cynically, there is also more insurance against nefarious colleagues that may be tempted to distort results\textsuperscript{\protect\hyperlink{ref-18PTmKJkq}{39}}.
 Collaborators as well as pre-publication and post-publication reviewers are better positioned to discover questionable findings if they have full and transparent access to the project.
@@
 This transparency can similarly be extended beyond coauthors to the entire scientific community.
-Publishing the data and reproducible workflows along with the manuscript allows any reader to review the analysis and reproduce the experiment\textsuperscript{\protect\hyperlink{ref-NOgBWVAr}{36}}.
+Publishing the data and reproducible workflows along with the manuscript allows any reader to review the analysis and reproduce the experiment\textsuperscript{\protect\hyperlink{ref-NOgBWVAr}{40}}.
 Supplying code for (novel) methods that are proposed or used also reduces barriers to knowledge and can greatly improve the ability of others to build on existing work, resulting in greater proliferation and accessibility for a broader audience.
@@
 
-The development of research code continues, and so does the need to consider project continuity, especially in EEB where graduate students, research assistants, and postdoctoral fellows often hold relatively short-term positions\textsuperscript{\protect\hyperlink{ref-D4C4k4ak}{37}}.
+The development of research code continues, and so does the need to consider project continuity, especially in EEB where graduate students, research assistants, and postdoctoral fellows often hold relatively short-term positions\textsuperscript{\protect\hyperlink{ref-D4C4k4ak}{41}}.
 Often with these types of short-term research projects, once the contract expires, the research code upkeep tends to fall off as the researchers move on to new projects.
 Additionally, if the code is kept on only the researcher's personal devices, it becomes increasingly difficult to access the code for future uses.
-As projects or contracts end, there should be a handover period of this code in order for the next cohort of researchers to reuse what was already developed\textsuperscript{\protect\hyperlink{ref-4ny1onB0}{8},\protect\hyperlink{ref-D4C4k4ak}{37}}.
+As projects or contracts end, there should be a handover period of this code in order for the next cohort of researchers to reuse what was already developed\textsuperscript{\protect\hyperlink{ref-4ny1onB0}{8},\protect\hyperlink{ref-D4C4k4ak}{41}}.
 
@@
 As we have already mentioned, using Git for code in Ecology and Evolution can allow for a ``paper trail'' of sorts to be created for the code, thus allowing for future users of the code access to the entire history of the project\textsuperscript{\protect\hyperlink{ref-3DKwn1sY}{14}}.
-Additionally, GitHub allows for repositories and organizations to have designated Code Owners\textsuperscript{\protect\hyperlink{ref-s91uGRZ2}{38}}; these code owners can change through time allowing for the transition of code from one cohort of researchers to the next\textsuperscript{\protect\hyperlink{ref-iIEKCTLU}{26}}.
+Additionally, GitHub allows for repositories and organizations to have designated Code Owners\textsuperscript{\protect\hyperlink{ref-s91uGRZ2}{42}}; these code owners can change through time allowing for the transition of code from one cohort of researchers to the next\textsuperscript{\protect\hyperlink{ref-iIEKCTLU}{30}}.
 There are also multiple means by which to archive code dependency information with GitHub.
@@
 
-There have been many calls for researchers outside of the software development community to join the 73 million GitHub users for their collaborative research\textsuperscript{\protect\hyperlink{ref-10ghgV3S8}{3},\protect\hyperlink{ref-1Du6fzB8g}{25},\protect\hyperlink{ref-UsTxAq4f}{39}}.
+There have been many calls for researchers outside of the software development community to join the 73 million GitHub users for their collaborative research\textsuperscript{\protect\hyperlink{ref-10ghgV3S8}{3},\protect\hyperlink{ref-1Du6fzB8g}{29},\protect\hyperlink{ref-UsTxAq4f}{43}}.
 This call comes in light of both the continual shift toward open-science and increasing computational and data requirements in EEB.
@@
 The default public nature of GitHub usage can add additional pressure to students and scientists learning to use the platform.
-We also note that large file storage is discouraged (and limited) on GitHub but add-ons do exist (e.g.~\url{https://git-lfs.github.com/}) that permit data storage, and increasing integration between platforms (e.g.\textsuperscript{\protect\hyperlink{ref-lx49NGto}{40}}) allows data to be stored away from GitHub and linked dynamically.
+We also note that large file storage is discouraged (and limited) on GitHub but add-ons do exist (e.g.~\url{https://git-lfs.github.com/}) that permit data storage, and increasing integration between platforms (e.g.\textsuperscript{\protect\hyperlink{ref-lx49NGto}{44}}) allows data to be stored away from GitHub and linked dynamically.
 We suspect a major additional barrier to EEB researchers is a distinct lack of GitHub help documents for non-English researchers in ecology and evolution, meaning that EEB researchers potentially miss the opportunity to fully understand the importance of version control, reproducibility, and other benefits of GitHub.
@@
 \\
-2. \textbf{Consider taking free courses.} such as those from Software Carpentry\textsuperscript{\protect\hyperlink{ref-pjy75gHr}{41}} and sharing these courses with your lab members or colleagues. \\
+2. \textbf{Consider taking free courses.} such as those from Software Carpentry\textsuperscript{\protect\hyperlink{ref-pjy75gHr}{45}} and sharing these courses with your lab members or colleagues. \\
 3.
@@
 6.
-\textbf{The Jenny Bryan universe of GitHub material.} provides a thorough and accessible introduction for a multitude of research-related uses for GitHub, and includes a book\textsuperscript{\protect\hyperlink{ref-ZvrOcg9w}{42}}, statistics course\textsuperscript{\protect\hyperlink{ref-6CMMeSeD}{43}} and academic article\textsuperscript{\protect\hyperlink{ref-RVetqmsg}{7}}.
+\textbf{The Jenny Bryan universe of GitHub material.} provides a thorough and accessible introduction for a multitude of research-related uses for GitHub, and includes a book\textsuperscript{\protect\hyperlink{ref-ZvrOcg9w}{46}}, statistics course\textsuperscript{\protect\hyperlink{ref-6CMMeSeD}{47}} and academic article\textsuperscript{\protect\hyperlink{ref-RVetqmsg}{7}}.
 \\
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-11GtZ7icJ}{}}%
+\CSLLeftMargin{20. }
+\CSLRightInline{Git Large File Storage. \emph{Git Large File Storage} \url{https://git-lfs.github.com/}.}
+
 \leavevmode\vadjust pre{\hypertarget{ref-wwHxTOtm}{}}%
-\CSLLeftMargin{20. }
+\CSLLeftMargin{21. }
 \CSLRightInline{Kanza, S. \emph{et al.} \href{https://doi.org/10.1186/s13321-017-0221-3}{Electronic lab notebooks: can they replace paper?} \emph{J Cheminform} \textbf{9}, (2017).}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-10V7x4H4l}{}}%
-\CSLLeftMargin{21. }
+\CSLLeftMargin{22. }
 \CSLRightInline{Schnell, S.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-RhBKe0MG}{}}%
-\CSLLeftMargin{22. }
+\CSLLeftMargin{23. }
 \CSLRightInline{About projects (beta). \emph{GitHub Docs} \url{https://ghdocs-prod.azurewebsites.net/en/issues/trying-out-the-new-projects-experience/about-projects}.}
 
+\leavevmode\vadjust pre{\hypertarget{ref-1GRWGlDWy}{}}%
+\CSLLeftMargin{24. }
+\CSLRightInline{Slack. GitHub for Slack. \emph{Slack Help Center} \url{https://slack.com/help/articles/232289568-GitHub-for-Slack}.}
+
 \leavevmode\vadjust pre{\hypertarget{ref-QqMezOMg}{}}%
-\CSLLeftMargin{23. }
+\CSLLeftMargin{25. }
 \CSLRightInline{Xie, Y., Allaire, J. J. \& Grolemund, G. \emph{R Markdown: the definitive guide}. (CRC Press, Taylor and Francis Group, 2019).}
 
+\leavevmode\vadjust pre{\hypertarget{ref-MDQfMwCW}{}}%
+\CSLLeftMargin{26. }
+\CSLRightInline{Quickstart for GitHub Pages. \emph{GitHub Docs} \url{https://ghdocs-prod.azurewebsites.net/en/pages/quickstart}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-dqrFjoSb}{}}%
+\CSLLeftMargin{27. }
+\CSLRightInline{Trujillo, G.
+\& Tanner, K.
+D.
+\href{https://doi.org/10.1187/cbe.13-12-0241}{Considering the Role of Affect in Learning: Monitoring Students' Self-Efficacy, Sense of Belonging, and Science Identity}.
+\emph{LSE} \textbf{13}, 6--15 (2014).}
+
 \leavevmode\vadjust pre{\hypertarget{ref-MXxgZJ45}{}}%
-\CSLLeftMargin{24. }
+\CSLLeftMargin{28. }
 \CSLRightInline{Dawson, C. \emph{Building tools with GitHub: customize your workflow}. (O'Reilly, 2016).}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-1Du6fzB8g}{}}%
-\CSLLeftMargin{25. }
+\CSLLeftMargin{29. }
 \CSLRightInline{Crystal‐Ornelas, R.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-iIEKCTLU}{}}%
-\CSLLeftMargin{26. }
+\CSLLeftMargin{30. }
 \CSLRightInline{Hampton, S. E. \emph{et al.} \href{https://doi.org/10.1890/es14-00402.1}{The Tao of open science for ecology}. \emph{Ecosphere} \textbf{6}, art120 (2015).}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-uBJwnPbq}{}}%
-\CSLLeftMargin{27. }
+\CSLLeftMargin{31. }
 \CSLRightInline{Mislan, K.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-1HZdsK5Kn}{}}%
-\CSLLeftMargin{28. }
+\CSLLeftMargin{32. }
 \CSLRightInline{Baker, M. \href{https://doi.org/10.1038/533452a}{1,500 scientists lift the lid on reproducibility}. \emph{Nature} \textbf{533}, 452--454 (2016).}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-K7nbP1Ty}{}}%
-\CSLLeftMargin{29. }
+\CSLLeftMargin{33. }
 \CSLRightInline{Crystal-Ornelas, R.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-hm9PaCLD}{}}%
-\CSLLeftMargin{30. }
+\CSLLeftMargin{34. }
 \CSLRightInline{Song, X., Goldstein, S.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-YuJbg3zO}{}}%
-\CSLLeftMargin{31. }
+\CSLLeftMargin{35. }
 \CSLRightInline{Himmelstein, D. S. \emph{et al.} \href{https://doi.org/10.1371/journal.pcbi.1007128}{Open collaborative writing with Manubot}. \emph{PLoS Comput Biol} \textbf{15}, e1007128 (2019).}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-i4FOZpjN}{}}%
-\CSLLeftMargin{32. }
+\CSLLeftMargin{36. }
 \CSLRightInline{Lasser, J. \href{https://doi.org/10.1038/s42005-020-00403-4}{Creating an executable paper is a journey through Open Science}. \emph{Commun Phys} \textbf{3}, (2020).}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Xsdcv6q}{}}%
-\CSLLeftMargin{33. }
+\CSLLeftMargin{37. }
 \CSLRightInline{Boettiger, C., Lang, D.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-FVBWKkZu}{}}%
-\CSLLeftMargin{34. }
+\CSLLeftMargin{38. }
 \CSLRightInline{Chamberlain, S. A. \& Szöcs, E. \href{https://doi.org/10.12688/f1000research.2-191.v2}{taxize: taxonomic search and retrieval in R}. \emph{F1000Res} \textbf{2}, 191 (2013).}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-18PTmKJkq}{}}%
-\CSLLeftMargin{35. }
+\CSLLeftMargin{39. }
 \CSLRightInline{January 18, P.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-NOgBWVAr}{}}%
-\CSLLeftMargin{36. }
+\CSLLeftMargin{40. }
 \CSLRightInline{Culina, A., van den Berg, I., Evans, S.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-D4C4k4ak}{}}%
-\CSLLeftMargin{37. }
+\CSLLeftMargin{41. }
 \CSLRightInline{Fehr, J., Himpe, C., Rave, S. \& Saak, J. \href{https://doi.org/10.5334/jors.307}{Sustainable Research Software Hand-Over}. \emph{JORS} \textbf{9}, 5 (2021).}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-s91uGRZ2}{}}%
-\CSLLeftMargin{38. }
+\CSLLeftMargin{42. }
 \CSLRightInline{About code owners.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-UsTxAq4f}{}}%
-\CSLLeftMargin{39. }
+\CSLLeftMargin{43. }
 \CSLRightInline{Anbaroğlu, B. \href{https://doi.org/10.1111/tgis.12810}{A collaborative GIS programming course using GitHub Classroom}. \emph{Transactions in GIS} \textbf{25}, 3132--3158 (2021).}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-lx49NGto}{}}%
-\CSLLeftMargin{40. }
+\CSLLeftMargin{44. }
 \CSLRightInline{Connect GitHub to a Project - OSF Support. \url{https://help.osf.io/article/211-connect-github-to-a-project}.}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-pjy75gHr}{}}%
-\CSLLeftMargin{41. }
+\CSLLeftMargin{45. }
 \CSLRightInline{Madicken Munk \emph{et al.} swcarpentry/git-novice: Software Carpentry: Version Control with Git, June 2019.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-ZvrOcg9w}{}}%
-\CSLLeftMargin{42. }
+\CSLLeftMargin{46. }
 \CSLRightInline{Hester, J. B., the STAT 545 TAs, Jim. \emph{\href{https://happygitwithr.com/}{Let's Git started \textbar{} Happy Git and GitHub for the useR}}.}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-6CMMeSeD}{}}%
-\CSLLeftMargin{43. }
+\CSLLeftMargin{47. }
 \CSLRightInline{Bryan, J. \& TAs, T. S. 545. \emph{\href{https://stat545.com/}{STAT 545}}.}

### 2022-06-13 manuscript.tex
Merge pull request #234 from colebrookson/main [ci skip]
This build is based on
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/1498796835167c3f7d1f4135eca274b5e7d6346c.

This commit was created by the following CI build and job:
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/1498796835167c3f7d1f4135eca274b5e7d6346c/checks
https://github.com/SORTEE-Github-Hackathon/manuscript/actions/runs/2489350199

@@
 This manuscript
-(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/ea3d52568405d25c555daffaef4bbf5a40954c92/}{permalink})
+(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/1498796835167c3f7d1f4135eca274b5e7d6346c/}{permalink})
 was automatically generated
-from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/ea3d52568405d25c555daffaef4bbf5a40954c92}{SORTEE-Github-Hackathon/manuscript@ea3d525}
-on June 10, 2022.
+from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/1498796835167c3f7d1f4135eca274b5e7d6346c}{SORTEE-Github-Hackathon/manuscript@1498796}
+on June 13, 2022.
 
@@
 \CSLLeftMargin{25. }
-\CSLRightInline{Xie, Y., Allaire, J. J. \& Grolemund, G. \emph{R Markdown: the definitive guide}. (CRC Press, Taylor and Francis Group, 2019).}
+\CSLRightInline{Xie, Y., Allaire, J. J. \& Grolemund, G. \emph{R Markdown: the definitive guide}. (CRC Press, Taylor \& Francis Group, 2019).}
 
@@
 \CSLLeftMargin{28. }
-\CSLRightInline{Dawson, C. \emph{Building tools with GitHub: customize your workflow}. (O'Reilly, 2016).}
+\CSLRightInline{Dawson, C. \& Straub, B. \emph{Building tools with GitHub: customize your workflow}. (O'Reilly, 2016).}
 

### 2022-06-13 manuscript.tex
Merge pull request #237 from SORTEE-Github-Hackathon/colebrookson-update-figure-caption [ci skip]
This build is based on
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/3b6215a8c54e5db5b4b561ab67693bb5c7fc5f73.

This commit was created by the following CI build and job:
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/3b6215a8c54e5db5b4b561ab67693bb5c7fc5f73/checks
https://github.com/SORTEE-Github-Hackathon/manuscript/actions/runs/2490456733

--- 2022-06-10 manuscript.tex
@@
 This manuscript
-(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/ea3d52568405d25c555daffaef4bbf5a40954c92/}{permalink})
+(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/3b6215a8c54e5db5b4b561ab67693bb5c7fc5f73/}{permalink})
 was automatically generated
-from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/ea3d52568405d25c555daffaef4bbf5a40954c92}{SORTEE-Github-Hackathon/manuscript@ea3d525}
-on June 10, 2022.
+from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/3b6215a8c54e5db5b4b561ab67693bb5c7fc5f73}{SORTEE-Github-Hackathon/manuscript@3b6215a}
+on June 13, 2022.
 
@@
 A) Multi-faceted components allow for code writing, small data storage, manuscript writing, and project management to all be done in one place.
+\texttt{CONTRIBUTING.md}, \texttt{LICENCE.md}, and \texttt{README.md} files allow new team members, or others wanting to use materials, to understand the project components and learn how they can engage with the project and existing team members.
 B) Issues, Pull Requests, Discussions, and Projects allow for team members to ask for feedback, suggest fixes, discuss related ideas, and keep track of all the moving parts of a project.
-C) All collaborators on a project can be a part of a single repository, with varying push privileges and responsibilities.
-D) CONTRIBUTING.md, LICENCE.md, \& README.md files can allow new team members or others wanting to use materials to understand the project components and learn how they can engage with the project and existing team members.}\label{fig:github-diagram}
+C) All collaborators on a project can be a part of a single repository, with varying push privileges and responsibilities}\label{fig:github-diagram}
 }

### 2022-06-13 manuscript.tex
Merge pull request #238 from SORTEE-Github-Hackathon/robcrystalornelas-fix-github-image [ci skip]
This build is based on
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/8c2aac108bf451c48272ca35f8bd93bfd6a499fd.

This commit was created by the following CI build and job:
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/8c2aac108bf451c48272ca35f8bd93bfd6a499fd/checks
https://github.com/SORTEE-Github-Hackathon/manuscript/actions/runs/2490483271

@@
 This manuscript
-(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/3b6215a8c54e5db5b4b561ab67693bb5c7fc5f73/}{permalink})
+(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/8c2aac108bf451c48272ca35f8bd93bfd6a499fd/}{permalink})
 was automatically generated
-from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/3b6215a8c54e5db5b4b561ab67693bb5c7fc5f73}{SORTEE-Github-Hackathon/manuscript@3b6215a}
+from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/8c2aac108bf451c48272ca35f8bd93bfd6a499fd}{SORTEE-Github-Hackathon/manuscript@8c2aac1}
 on June 13, 2022.

### 2022-06-15 manuscript.tex
Merge pull request #239 from SORTEE-Github-Hackathon/RCO-author-credit [ci skip]
This build is based on
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/4ac5f7eeaa29350c0b737ed7e3e45fa0be45da12.

This commit was created by the following CI build and job:
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/4ac5f7eeaa29350c0b737ed7e3e45fa0be45da12/checks
https://github.com/SORTEE-Github-Hackathon/manuscript/actions/runs/2505155697

@@
 This manuscript
-(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/8c2aac108bf451c48272ca35f8bd93bfd6a499fd/}{permalink})
+(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/4ac5f7eeaa29350c0b737ed7e3e45fa0be45da12/}{permalink})
 was automatically generated
-from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/8c2aac108bf451c48272ca35f8bd93bfd6a499fd}{SORTEE-Github-Hackathon/manuscript@8c2aac1}
-on June 13, 2022.
+from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/4ac5f7eeaa29350c0b737ed7e3e45fa0be45da12}{SORTEE-Github-Hackathon/manuscript@4ac5f7e}
+on June 15, 2022.
 
@@
 
+\hypertarget{author-contributions}{%
+\subsection{Author Contributions}\label{author-contributions}}
+
+We indicate author contributions using the \href{https://casrai.org/credit/}{CRediT Taxonomy}
+Conceptualization: RCO, BPME, KH, EJH, LLSR, PHPB
+Investigation: RCO, BPME, KH, EJH, LLSR, ERS, MJG, VF, ADB, CBB, KMG, SSHS, AG, FH, HW, DGEG, PHPB
+Methodology: RCO, BPME, KH, EJH, LLSR, PHPB
+Project administration: RCO
+
+Software: RCO, BPME, KH, EJH, LLSR, ERS, MJG, VF, ADB, CBB, KMG, SSHS, AG, FH, HW, DGEG, PHPB
+Visualization: RCO, BPME, KH, EJH, LLSR, ERS, MJG, VF, ADB, CBB, KMG, SSHS, AG, FH, HW, DGEG, PHPB
+Writing -- original draft: RCO, BPME, KH, EJH, LLSR, ERS, MJG, VF, ADB, CBB, KMG, SSHS, AG, FH, HW, DGEG, PHPB
+Writing -- review \& editing: RCO, BPME, KH, EJH, LLSR, ERS, MJG, VF, ADB, CBB, KMG, SSHS, AG, FH, HW, DGEG, PHPB
+
 \hypertarget{acknowledgements}{%
@@
 This manuscript arose from a hackathon at the Society for Open, Reliable, and Transparent Ecology and Evolution (SORTEE) virtual meeting in July 2021.
+We thank Ciera Martinez for being a co-organizer of the SORTEE hackathon that started our discussion on GitHub in EEB and for creating our hackathon website on GitHub.
 
@@
 The source code and data for this manuscript are available at https://github.com/SORTEE-Github-Hackathon/manuscript.
+The source code will be archived in the ESS-DIVE data repository prior to publication.
 

### 2022-06-20 editorial-communication/cover-letter-submission.Rmd
Cover letter a suggestion; We believe that our manuscript nicely complement a recently published paper in your journal with fundamental insights. Gallagher et al. 2020...

@@
 Our manuscript is important for the *Nature Ecology & Evolution* readership because researchers in ecology and evolutionary biology can greatly benefit from our guide to migrate and incorporate GitHub workflows in their research practices ultimately towards an open and collaborative science.
+We believe that our manuscript nicely complement a recently published paper in your journal with fundamental insights.
+Gallagher et al.
+2020 outlined how the adoption of key Open Science principles—open data, open source and open methods—is transforming trait science, increasing transparency, democratizing access and accelerating global synthesis.
+To implement and contribute collaborative software development via platforms like GitHub, an accessible, easy to use and practical guide to using GitHub is of interest for researchers in ecology and evolutionary biology.
 

### 2022-06-23 manuscript.tex
Merge pull request #241 from SORTEE-Github-Hackathon/phpb-conciseness-03.use-cases-b.md- [ci skip]
This build is based on
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/dc28d7dd993d0f5ca61b1bd7fc59d1cc22e39ce2.

This commit was created by the following CI build and job:
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/dc28d7dd993d0f5ca61b1bd7fc59d1cc22e39ce2/checks
https://github.com/SORTEE-Github-Hackathon/manuscript/actions/runs/2550899642

@@
 This manuscript
-(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/4ac5f7eeaa29350c0b737ed7e3e45fa0be45da12/}{permalink})
+(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/dc28d7dd993d0f5ca61b1bd7fc59d1cc22e39ce2/}{permalink})
 was automatically generated
-from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/4ac5f7eeaa29350c0b737ed7e3e45fa0be45da12}{SORTEE-Github-Hackathon/manuscript@4ac5f7e}
-on June 15, 2022.
+from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/dc28d7dd993d0f5ca61b1bd7fc59d1cc22e39ce2}{SORTEE-Github-Hackathon/manuscript@dc28d7d}
+on June 23, 2022.
 
@@
 
-\hypertarget{creating-a-website}{%
-\subsubsection{Creating a website}\label{creating-a-website}}
-
-Personal or lab websites are one method of improving the dissemination of research findings and coordination of research efforts, but most EEB researchers have little experience in building or hosting webpages.
-GitHub Pages (\url{https://pages.github.com}) is a feature that, when activated for a repository, renders content written in markdown (e.g., \url{https://github.com/SORTEE-Github-Hackathon/main-website}) as an HTML web page with a URL (e.g., \url{https://sortee-github-hackathon.github.io/main-website/}).
-This can be useful for sharing reports (e.g.~written with RMarkdown and rendered to HTML) with collaborators, or for more complex projects like personal, project, or lab websites.
-GitHub also offers website templates and it is possible to create a website by forking (\protect\hyperlink{definitions}{Box 1}) a repository hosting a GitHub Pages site as a starting point.
-Aside from free hosting services, another benefit is that GitHub Pages are autogenerated, meaning that when content is modified in the associated GitHub repository, the website instantly updates\textsuperscript{\protect\hyperlink{ref-RVetqmsg}{7}}.
-Though the templates are useful for quickly starting up a new website, users are able to fully customize their Pages websites (for technical details of customizing GitHub Pages site see\textsuperscript{\protect\hyperlink{ref-MXxgZJ45}{28}}).
-We emphasize that despite the many benefits of using GitHub pages (free hosting, templates, customization), this avenue for creating a website will often be more time intensive than the out-of-the-box platforms.
-``Static websites'' (i.e., websites where every user sees the same content) can be created using Jekyll (\url{https://jekyllrb.com}) and Hugo (\url{https://gohugo.io}), which also include template libraries for websites that can be hosted freely via GitHub pages.
-Several R packages such as distill (\url{https://github.com/rstudio/distill}) and blogdown (\url{https://bookdown.org/yihui/blogdown}) have made the interface to these website generators more accessible.
-In addition, Quarto (\url{https://quarto.org}) has options for creating websites (\url{https://quarto.org/docs/websites}) as well as the code-free website generator wowchemy (\url{https://wowchemy.com}) which uses Hugo.
+\hypertarget{hosting-a-website}{%
+\subsubsection{Hosting a website}\label{hosting-a-website}}
+
+Personal or laboratory websites can improve the sharing of research findings, build online presence, and increase coordination of research efforts\textsuperscript{\protect\hyperlink{ref-HiIPSSHV}{28}}.
+Despite many researchers in ecology and evolution having little experience in building or hosting webpages, many tools have been developed to help this process.
+Static websites can now be easily built using independent software and languages, such as Jekyll (\url{https://jekyllrb.com}), Hugo (\url{https://gohugo.io}), Quarto (\url{https://quarto.org}), and wowchemy (\url{https://wowchemy.com}), or with the help of dependencies in the programming languages scientists commonly use, such as the \texttt{distill} (\url{https://github.com/rstudio/distill}) and \texttt{blogdown} (\url{https://bookdown.org/yihui/blogdown}) R packages.
+The resulting files from static websites can then be hosted in repositories, from which one can activate GitHub's Pages (\url{https://pages.github.com}) feature, allowing for the direct live hosting of HyperText Markup Language (HTML), Cascading Style Sheets (CSS) and JavaScript files within a free github.io domain.
+Website templates are readily available on GitHub (https://github.com/topics/website-template) or in user-specific repositories, which can be forked (\protect\hyperlink{definitions}{Box 1}) and customized\textsuperscript{\protect\hyperlink{ref-MXxgZJ45}{29}}.
+Aside from free hosting services, GitHub Pages also allows websites to be autogenerated and instantly updated following content modifications\textsuperscript{\protect\hyperlink{ref-RVetqmsg}{7}}.
+Creating and hosting websites on GitHub pages can be often time-consuming, as this process usually requires more knowledge in web design than out-of-the-box platforms (\emph{e.g.}, Wix, Weebly, Google Sites).
+However, free hosting, widely available template customization, and versioning are strong advantages over the alternatives.
 
@@
 
-GitHub makes it easy to store and share a variety of data files in the cloud.
-If a repository is made ``public'' the URL to the repository can be shared freely with others.
-However, for a variety of reasons (e.g., privately owned company, ability to make repositories private, accounts can be deleted at will) GitHub is not considered a long-term data or code repository like Zenodo and Figshare\textsuperscript{\protect\hyperlink{ref-10ghgV3S8}{3},\protect\hyperlink{ref-kEX5dgzK}{9},\protect\hyperlink{ref-tbl:compare}{\textbf{tbl:compare?}}}.
-Also, unlike long-term repositories, GitHub does not issue Digital Object Identifiers (DOIs) for content uploaded to their servers.
-DOIs are persistent and unique alpha-numeric IDs assigned to research products like papers, code, and data.
-DOIs allows tracking and citing research products.
-For this reason, scientists who share code and data through GitHub are strongly encouraged to also submit GitHub repository content to a long-term data archive\textsuperscript{\protect\hyperlink{ref-1Du6fzB8g}{29}}.
-Fortunately, both long-term repositories mentioned above (Zenodo and Figshare) have integrations with GitHub.
-After linking one's GitHub repository to Zenodo or Figshare, every time a release (\protect\hyperlink{definitions}{Box 1}) is made, a snapshot of the entire repository is archived with a versioned, citable DOI.
-Linking one's GitHub repository with Zenodo, etc.
-to obtain a DOI helps work become findable, gives proper attribution, and can ensure long-term stability\textsuperscript{\protect\hyperlink{ref-iIEKCTLU}{30}}.
-
-Many researchers believe that their code is not useful because their analysis is context-specific and not explicitly designed for re-use like software.
-However, there are many reasons to share data and code beyond re-use.
-Even if code lacks detailed annotation, it shows the exact steps taken to conduct an analysis, and therefore provides the most detailed look into how to reproduce a given analysis\textsuperscript{\protect\hyperlink{ref-uBJwnPbq}{31}}.
-This is important in light of the reproducibility crisis\textsuperscript{\protect\hyperlink{ref-1HZdsK5Kn}{32}} and will become increasingly important to the collective scientific enterprise as advances in computing power and accessibility unlock the ability to conduct `big data' meta research with data that has already been collected by others.
-Failing to include data and code with publications leaves future scientists with fewer open resources from which to understand the world.
-
-An important aspect of making code citable and reusable is adding an appropriate licence.
-Code without a licence is (by default) actually provided more protection from reuse than code with an open licence.
-The standard GitHub licensing options are best suited for software, so depending on how you want your code to be used you can choose one of the other license options.
-For example, if your code is intended only for your specific analysis, consider a Creative Commons License.
-If you wish to receive attribution for any reuse of your code, consider a CC BY 4.0 license.
-If you have built an app, tool, package, or other product that you would like others to use and would like attribution for any reuse of your code, consider the GNU General Public License v3.
-This license also prohibits the re-user from making their re-used version private.
-To help navigate through the potential licenses available to you and their attributes the Choose a License (\url{https://choosealicense.com/non-software/}) website can offer further guidance.
-
-\hypertarget{collaborative-code-editing-and-asynchronous-working}{%
-\subsubsection{Collaborative (code) editing and asynchronous working}\label{collaborative-code-editing-and-asynchronous-working}}
-
-GitHub facilitates collaborative coding and asynchronous working because researchers can seamlessly access and contribute to data and code regardless of disparities in schedules or location.
-Project work can also be clearly split among team members, giving them the flexibility to contribute when it best fits their schedule.
-We acknowledge that there are important differences between the average software developer and EEB researcher using GitHub, and that not all of GitHub's features are useful for research workflows (\protect\hyperlink{tbl:roles}{Table 1}).
-However, git's core features such as forking and branching (\protect\hyperlink{definitions}{Box 1}) allow for simultaneous coding on different versions of the same research project, and alternative versions can be discussed and resolved with GitHub.
-When EEB projects are contained on the GitHub platform, researchers can stay abreast of progress made by other collaborators without the need for meetings or emails.
-Version control\textsuperscript{\protect\hyperlink{ref-K7nbP1Ty}{33}} features also allow users to make progress and changes without worrying about irreparably writing over someone else's work.
+Government, funding agencies, and publishers exercise rigorous open access data policies and mandates\textsuperscript{\protect\hyperlink{ref-PLmDFZrm}{30},\protect\hyperlink{ref-1Hcf13Q0k}{31}}.
+However, code and data sharing may be met by individual reluctance, temporary embargoes, or partially prevented by privacy and confidentiality reasons\textsuperscript{\protect\hyperlink{ref-1Ch6LSHef}{32}--\protect\hyperlink{ref-1CzUZwyU2}{34}}.
+Still, data deposition and ensuring its availability can amplify the outreach of published studies\textsuperscript{\protect\hyperlink{ref-666HppfO}{35}}, increase citation rates\textsuperscript{\protect\hyperlink{ref-1CcAUn3Lu}{36}}, and among many other reasons, enables the reproducibility and robustness of scientific advances\textsuperscript{\protect\hyperlink{ref-4LaijDIZ}{37}--\protect\hyperlink{ref-1HZdsK5Kn}{39}}.
+While public repositories on GitHub make it easy to store and share data files, they are not considered long-term repositories for research materials.
+This is because GitHub, a for-profit company, does not have long-term data availability guarantees, allowing users to delete or make repositories private after publication.
+Also, GitHub does not issue Digital Object Identifiers (DOI) for content uploaded to their servers.
+DOIs are persistent and citable unique alpha-numeric identifiers assigned to digitally stored research materials.
+Because of this, scientists sharing code and data through GitHub are strongly encouraged to independently submit their research materials to long-term data archives (\emph{e.g.}, Zenodo, Figshare, Dryad, OSF\textsuperscript{\protect\hyperlink{ref-10ghgV3S8}{3},\protect\hyperlink{ref-kEX5dgzK}{9},\protect\hyperlink{ref-1Du6fzB8g}{40},\protect\hyperlink{ref-tbl:compare}{\textbf{tbl:compare?}}}.
+Some of these options (Zenodo, Figshare and OSF) integrate with GitHub, allowing project, code, and data releases (\protect\hyperlink{definitions}{Box 1}) to be archived with versioned, citable DOIs.
+Linking GitHub repositories with a DOI helps research become findable, properly cited, and can ensure long-term stability\textsuperscript{\protect\hyperlink{ref-iIEKCTLU}{41}}.
+
+An important aspect of making code and data citable and reusable is to add an appropriate licence to protect intellectual property.
+Code published without a licence is under exclusive copyright (by default), protecting it from copy, distribution, and modifications.
+One may grant specific rights to their code for reuse by adding licensing files and specifications within GitHub repositories\textsuperscript{\protect\hyperlink{ref-TOsASkn5}{42}}.
+The Choose a License (\url{https://choosealicense.com/non-software/}) website offers further guidance on the licenses available for research and creative products.
+For example, Creative Commons (CC; \url{https://creativecommons.org/licenses/}) licenses can specify that shared code is intended for a specific analysis.
+A CC BY 4.0 license specifies that any code (or other creative products) must be appropriately credited to its original author when distributed, adapted or reused.
+A GNU General Public License v3 provides the same attributions above, but requires that all modified or adapted versions to be made public.
+
+\hypertarget{collaborative-and-asynchronous-code-editing}{%
+\subsubsection{Collaborative and asynchronous code editing}\label{collaborative-and-asynchronous-code-editing}}
+
+Researchers can asynchronously communicate and individually or collaboratively work in GitHub.
+By forking, branching, and cloning repositories (\protect\hyperlink{definitions}{Box 1}), researchers can simultaneously work on different issues of the same research project to then later merge changes to the main branch project with pull requests.
+Explicit project organization and increased communication in GitHub Issues, Discussions, or within pull requests can help with project development and with potential merge conflicts due to users simultaneously working on the same sections\textsuperscript{\protect\hyperlink{ref-1BJcvyTmV}{43}}.
+Moreover, version control\textsuperscript{\protect\hyperlink{ref-K7nbP1Ty}{44}} and commit reversal features allow researchers to track and progress without worrying about irreparably modifying someone else's work.
 By enabling more comprehensive remote collaboration, GitHub encourages the exchange of ideas among researchers at different institutions and in different countries, which can serve to improve the quality of the research itself by providing open access to data and code.
-In academic settings, GitHub can also facilitate interactions between research advisors and advisees, providing a platform for students or other trainees to share in-progress code, and flag specific challenges or questions for their supervisors or mentors.
-Periodic code review\textsuperscript{\protect\hyperlink{ref-hm9PaCLD}{34}} can also help advisors identify errors early in the process, and inform further training and mentorship to fill gaps in skills.
+In academic settings, GitHub can also facilitate interactions between research advisors and advisees, providing a platform for students or other trainees to share in-progress code, and flag specific challenges or questions for their supervisors or mentors (\protect\hyperlink{tbl:roles}{Table 1}).
+Periodic code review\textsuperscript{\protect\hyperlink{ref-hm9PaCLD}{45}} can also help advisors identify errors early in the process, and inform further training and mentorship to fill gaps in skills.
 
@@
 
-Beyond supporting collaboration at the level of code, GitHub can be used for collaboratively writing manuscripts.
-Writing a manuscript in GitHub and storing it with associated data and code all in the same repository increases scientific reproducibility because files associated with a manuscript can be found in one place.
-Co-authors can contribute new text to a manuscript or suggest revisions through GitHub's robust pull request feature (\protect\hyperlink{definitions}{Box 1}) which provides a line-by-line view of all proposed changes.
-Further, authors can make use of the Discussions tab to suggest relevant papers to be cited, and can raise issues during the writing process that can be assigned to collaborators (\protect\hyperlink{tbl:roles}{Table 1}).
-
-While GitHub is not considered as user-friendly for manuscript development as conventional text processors\textsuperscript{\protect\hyperlink{ref-4ny1onB0}{8}}, it has been substantially improved with recent tools.
-Manuscripts can be written on GitHub with Markdown.
-Add-ons like HackMD (\url{https://hackmd.io}), can enable real-time collaboration for individual Markdown documents.
-Many tools exist for extending Markdown and Pandoc to add formatting features necessary for scientific writing like in-text citations and figure and table cross references.
-
-We wrote this manuscript using Manubot\textsuperscript{\protect\hyperlink{ref-YuJbg3zO}{35}}, a collaborative manuscript platform that uses Markdown for writing and GitHub for storing and tracking changes to a manuscript over time.
-Manubot uses a GitHub Actions-based typesetting system to compile individual Markdown files stored in a GitHub repository into a single LaTeX document, which can be displayed in Word, HTML, or PDF formats.
-The resulting manuscript can also be compiled using a journal's .tex template to match their formatting requirements.
-Since this tool reruns the entire manuscript compilation process with any change to the underlying repository, it can also accomodate continuous integration of code updates into figures and tables with additional GitHub Actions (e.g.~https://github.com/SORTEE-Github-Hackathon/manuscript/tree/main/.github/workflows).
-Manubot also allows for straightforward citation management based on URLs or DOIs.
-For more examples of Manubot being used for manuscripts, see\textsuperscript{\protect\hyperlink{ref-YuJbg3zO}{35}}.
-
-Since Manubot works on documents in a distributed format, it can be difficult to edit manuscripts for overall flow with only this tool.
-We employed hypothes.is (\url{https://hypothes.is}) to write comments on the HTML manuscript document produced by Manubot, which we then addressed by committing changes to the underlying Markdown files via pull requests.
-Other authors can reply to the comments to indicate agreement or disagreement, and to note when changes have been made.
-Other tools can also be used for version control of scientific manuscripts including R Markdown via the bookdown package (\url{https://bookdown.org/}), jupyter notebooks\textsuperscript{\protect\hyperlink{ref-i4FOZpjN}{36}} and a relatively new tool, Quarto (\url{https://quarto.org}).
+Beyond supporting collaborative code development, GitHub can be used for writing manuscripts.
+Writing a manuscript and storing its associated data and code in GitHub increases scientific reproducibility because text, code, and data can be found in one place.
+Writing a manuscript on GitHub may take more time when compared to using conventional text processors\textsuperscript{\protect\hyperlink{ref-4ny1onB0}{8}}.
+Nevertheless, GitHub has many features that can allow for a powerful collaborative workflow when writing manuscripts.
+Text documents stored and versioned in GitHub can be instantly displayed when written in Markdown, a lightweight markup language increasingly popular among scientists.
+Co-authors can contribute changes or suggest revisions to a manuscript written in GitHub through pull requests (\protect\hyperlink{definitions}{Box 1}).
+Pull requests provide line-by-line views of proposed changes, which can be commented, modified, or approved by designated reviewers and collaborators (\protect\hyperlink{tbl:roles}{Table 1}).
+Relevant literature or issues can be made using the Discussions and Issues features.
+Moreover, real-time collaboration on text documents stored in GitHub repositories can be achieved with the help of other platforms (\emph{e.g.}, HackMD (\url{https://hackmd.io} for Markdown documents).
+
+We wrote this manuscript using Manubot\textsuperscript{\protect\hyperlink{ref-YuJbg3zO}{46}}, a workflow implemented in GitHub to automatically render manuscripts and automate bibliographical tasks.
+Manubot uses GitHub's automation workflow, GitHub Actions, to combine and convert individual Markdown files into a single LaTeX document, which can then be converted to a Word or PDF document, and displayed as a webpage.
+Citations and bibliographic references are automatically managed with citable persistent identifiers (\emph{e.g.}, DOIs, PubMed IDs, ISBNs, URLs).
+The resulting manuscript can be rendered with document templates and citation style language formatting to meet journal formatting requirements.
+Every change made to the manuscript triggers its rendering, so that updates are readily displayed and made publicly available.
+Additional GitHub Actions can be integrated with Manubot, such as ones creating figures or generating tables (\emph{e.g.}, https://github.com/SORTEE-Github-Hackathon/manuscript/tree/main/.github/workflows).
+For more examples of manuscripts built via Manubot, see\textsuperscript{\protect\hyperlink{ref-YuJbg3zO}{46}}.
 
 \hypertarget{peer-review}{%
-\subsubsection{Peer-Review}\label{peer-review}}
-
-Peer review plays a critical role in the scientific evaluation of EEB research.
-GitHub provides an open and transparent platform that can be used for either directly providing feedback on research products or building a to-do list from reviewer comments.
-Peer review of research code by the open software development community rOpenSci (\url{https://ropensci.org/software-review/}) and of research software and associated manuscripts by the Journal of Open Source Software (\url{https://joss.readthedocs.io/en/latest/submitting.html}) requires that submitted work is hosted on GitHub and their review processes make use of GitHub issues.
-rOpenSci's efforts have resulted in many well-used R packages for ecology research including rfishbase\textsuperscript{\protect\hyperlink{ref-Xsdcv6q}{37}} and taxize\textsuperscript{\protect\hyperlink{ref-FVBWKkZu}{38}}.
-
-GitHub can also be used as a hub for reviewers and authors during the peer review process of an ordinary research manuscript.
-If the code associated with a manuscript is made available at the time of submission (e.g.~via a link to a GitHub repository in a Data Availability Statement), peer-reviewers may be able to offer more helpful suggestions on written methods and may even make comments on the code itself, potentially catching bugs or errors before publication.
-GitHub can also be used as a hub for reviewers and authors during the peer review process of an ordinary research manuscript.
-GitHub issues can be used to organize and discuss reviewer suggestions and to assign them to co-authors (See example in \url{https://github.com/BrunaLab/HeliconiaDemography/issues?q=is\%3Aissue+label\%3A\%22reviewer+comment\%22+}).
+\subsubsection{Peer review}\label{peer-review}}
+
+Peer review is the standard process for assessing and judging whether research done in ecology and evolution should be published in a scientific journal.
+GitHub provides an open and transparent platform that can be used for either directly providing feedback on research products or addressing changes recommended by reviewers.
+GitHub Issues can be used to organize and discuss reviewer suggestions and to assign them to co-authors (\emph{e.g.}, \url{https://github.com/SORTEE-Github-Hackathon/manuscript/issues?q=label\%3A\%22Reviewer+Comment\%22+}).
 When reviewer comments are posted as separate issues, authors can comment on the issues to discuss possible changes and assign themselves to indicate which comments they intend to handle.
 Co-authors can then integrate their edits and responses to reviewers using pull requests.
+
+GitHub can also assist reviewers during the peer review process.
+If the code associated with a manuscript is made available at the time of submission (\emph{e.g.}, as a link to a GitHub repository within the Data Availability Statement), peer reviewers may be able to offer more comprehensive suggestions on the code and written materials, potentially recognizing errors before publication.
+Certain journals or software development communities require submitted work or research code to be hosted on GitHub and their review processes make use of GitHub Issues {[}\emph{e.g.}, rOpenSci (\url{https://ropensci.org/software-review/}); Journal of Open Source Software (\url{https://joss.readthedocs.io/en/latest/submitting.html}){]}.
+rOpenSci's efforts have resulted in many well-used R packages for ecology research including \texttt{rfishbase}\textsuperscript{\protect\hyperlink{ref-Xsdcv6q}{47}} and \texttt{taxize}\textsuperscript{\protect\hyperlink{ref-FVBWKkZu}{48}}.
 
@@
 In the developmental stages, collaborators can directly see the code for the analysis, manipulate and explore the data themselves, and check for errors.
-Cynically, there is also more insurance against nefarious colleagues that may be tempted to distort results\textsuperscript{\protect\hyperlink{ref-18PTmKJkq}{39}}.
+Cynically, there is also more insurance against nefarious colleagues that may be tempted to distort results\textsuperscript{\protect\hyperlink{ref-18PTmKJkq}{49}}.
 Collaborators as well as pre-publication and post-publication reviewers are better positioned to discover questionable findings if they have full and transparent access to the project.
@@
 This transparency can similarly be extended beyond coauthors to the entire scientific community.
-Publishing the data and reproducible workflows along with the manuscript allows any reader to review the analysis and reproduce the experiment\textsuperscript{\protect\hyperlink{ref-NOgBWVAr}{40}}.
+Publishing the data and reproducible workflows along with the manuscript allows any reader to review the analysis and reproduce the experiment\textsuperscript{\protect\hyperlink{ref-NOgBWVAr}{50}}.
 Supplying code for (novel) methods that are proposed or used also reduces barriers to knowledge and can greatly improve the ability of others to build on existing work, resulting in greater proliferation and accessibility for a broader audience.
@@
 
-The development of research code continues, and so does the need to consider project continuity, especially in EEB where graduate students, research assistants, and postdoctoral fellows often hold relatively short-term positions\textsuperscript{\protect\hyperlink{ref-D4C4k4ak}{41}}.
+The development of research code continues, and so does the need to consider project continuity, especially in EEB where graduate students, research assistants, and postdoctoral fellows often hold relatively short-term positions\textsuperscript{\protect\hyperlink{ref-D4C4k4ak}{51}}.
 Often with these types of short-term research projects, once the contract expires, the research code upkeep tends to fall off as the researchers move on to new projects.
 Additionally, if the code is kept on only the researcher's personal devices, it becomes increasingly difficult to access the code for future uses.
-As projects or contracts end, there should be a handover period of this code in order for the next cohort of researchers to reuse what was already developed\textsuperscript{\protect\hyperlink{ref-4ny1onB0}{8},\protect\hyperlink{ref-D4C4k4ak}{41}}.
+As projects or contracts end, there should be a handover period of this code in order for the next cohort of researchers to reuse what was already developed\textsuperscript{\protect\hyperlink{ref-4ny1onB0}{8},\protect\hyperlink{ref-D4C4k4ak}{51}}.
 
@@
 As we have already mentioned, using Git for code in Ecology and Evolution can allow for a ``paper trail'' of sorts to be created for the code, thus allowing for future users of the code access to the entire history of the project\textsuperscript{\protect\hyperlink{ref-3DKwn1sY}{14}}.
-Additionally, GitHub allows for repositories and organizations to have designated Code Owners\textsuperscript{\protect\hyperlink{ref-s91uGRZ2}{42}}; these code owners can change through time allowing for the transition of code from one cohort of researchers to the next\textsuperscript{\protect\hyperlink{ref-iIEKCTLU}{30}}.
+Additionally, GitHub allows for repositories and organizations to have designated Code Owners\textsuperscript{\protect\hyperlink{ref-s91uGRZ2}{52}}; these code owners can change through time allowing for the transition of code from one cohort of researchers to the next\textsuperscript{\protect\hyperlink{ref-iIEKCTLU}{41}}.
 There are also multiple means by which to archive code dependency information with GitHub.
@@
 
-There have been many calls for researchers outside of the software development community to join the 73 million GitHub users for their collaborative research\textsuperscript{\protect\hyperlink{ref-10ghgV3S8}{3},\protect\hyperlink{ref-1Du6fzB8g}{29},\protect\hyperlink{ref-UsTxAq4f}{43}}.
+There have been many calls for researchers outside of the software development community to join the 73 million GitHub users for their collaborative research\textsuperscript{\protect\hyperlink{ref-10ghgV3S8}{3},\protect\hyperlink{ref-1Du6fzB8g}{40},\protect\hyperlink{ref-UsTxAq4f}{53}}.
 This call comes in light of both the continual shift toward open-science and increasing computational and data requirements in EEB.
@@
 The default public nature of GitHub usage can add additional pressure to students and scientists learning to use the platform.
-We also note that large file storage is discouraged (and limited) on GitHub but add-ons do exist (e.g.~\url{https://git-lfs.github.com/}) that permit data storage, and increasing integration between platforms (e.g.\textsuperscript{\protect\hyperlink{ref-lx49NGto}{44}}) allows data to be stored away from GitHub and linked dynamically.
+We also note that large file storage is discouraged (and limited) on GitHub but add-ons do exist (e.g.~\url{https://git-lfs.github.com/}) that permit data storage, and increasing integration between platforms (e.g.\textsuperscript{\protect\hyperlink{ref-lx49NGto}{54}}) allows data to be stored away from GitHub and linked dynamically.
 We suspect a major additional barrier to EEB researchers is a distinct lack of GitHub help documents for non-English researchers in ecology and evolution, meaning that EEB researchers potentially miss the opportunity to fully understand the importance of version control, reproducibility, and other benefits of GitHub.
@@
 \\
-2. \textbf{Consider taking free courses.} such as those from Software Carpentry\textsuperscript{\protect\hyperlink{ref-pjy75gHr}{45}} and sharing these courses with your lab members or colleagues. \\
+2. \textbf{Consider taking free courses.} such as those from Software Carpentry\textsuperscript{\protect\hyperlink{ref-pjy75gHr}{55}} and sharing these courses with your lab members or colleagues. \\
 3.
@@
 6.
-\textbf{The Jenny Bryan universe of GitHub material.} provides a thorough and accessible introduction for a multitude of research-related uses for GitHub, and includes a book\textsuperscript{\protect\hyperlink{ref-ZvrOcg9w}{46}}, statistics course\textsuperscript{\protect\hyperlink{ref-6CMMeSeD}{47}} and academic article\textsuperscript{\protect\hyperlink{ref-RVetqmsg}{7}}.
+\textbf{The Jenny Bryan universe of GitHub material.} provides a thorough and accessible introduction for a multitude of research-related uses for GitHub, and includes a book\textsuperscript{\protect\hyperlink{ref-ZvrOcg9w}{56}}, statistics course\textsuperscript{\protect\hyperlink{ref-6CMMeSeD}{57}} and academic article\textsuperscript{\protect\hyperlink{ref-RVetqmsg}{7}}.
 \\
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-HiIPSSHV}{}}%
+\CSLLeftMargin{28. }
+\CSLRightInline{Smaglik, P.
+\href{https://doi.org/10.1038/nj7142-347a}{Creating better lab websites gives potential collaborators and recruiters a clearer window into your world.} \emph{Nature} \textbf{447}, 347--347 (2007).}
+
 \leavevmode\vadjust pre{\hypertarget{ref-MXxgZJ45}{}}%
-\CSLLeftMargin{28. }
+\CSLLeftMargin{29. }
 \CSLRightInline{Dawson, C. \emph{Building tools with GitHub: customize your workflow}. (O'Reilly, 2016).}
 
-\leavevmode\vadjust pre{\hypertarget{ref-1Du6fzB8g}{}}%
-\CSLLeftMargin{29. }
-\CSLRightInline{Crystal‐Ornelas, R.
-\emph{et al.} \href{https://doi.org/10.1029/2021ea001797}{A Guide to Using GitHub for Developing and Versioning Data Standards and Reporting Formats}.
-\emph{Earth Space Sci} \textbf{8}, (2021).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-iIEKCTLU}{}}%
+\leavevmode\vadjust pre{\hypertarget{ref-PLmDFZrm}{}}%
 \CSLLeftMargin{30. }
-\CSLRightInline{Hampton, S. E. \emph{et al.} \href{https://doi.org/10.1890/es14-00402.1}{The Tao of open science for ecology}. \emph{Ecosphere} \textbf{6}, art120 (2015).}
+\CSLRightInline{Tenopir, C.
+\emph{et al.} \href{https://doi.org/10.1371/journal.pone.0229003}{Data sharing, management, use, and reuse: Practices and perceptions of scientists worldwide}.
+\emph{PLoS ONE} \textbf{15}, e0229003 (2020).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-1Hcf13Q0k}{}}%
+\CSLLeftMargin{31. }
+\CSLRightInline{Nugroho, R.
+P., Zuiderwijk, A., Janssen, M.
+\& de Jong, M.
+\href{https://doi.org/10.1108/tg-03-2014-0008}{A comparison of national open data policies: lessons learned}.
+\emph{Transforming Government: People, Process and Policy} \textbf{9}, 286--308 (2015).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-1Ch6LSHef}{}}%
+\CSLLeftMargin{32. }
+\CSLRightInline{Wicherts, J.
+M., Bakker, M.
+\& Molenaar, D.
+\href{https://doi.org/10.1371/journal.pone.0026828}{Willingness to Share Research Data Is Related to the Strength of the Evidence and the Quality of Reporting of Statistical Results}.
+\emph{PLoS ONE} \textbf{6}, e26828 (2011).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-SLq38RVv}{}}%
+\CSLLeftMargin{33. }
+\CSLRightInline{Figueiredo, A. S. \href{https://doi.org/10.3389/fpubh.2017.00327}{Data Sharing: Convert Challenges into Opportunities}. \emph{Front. Public Health} \textbf{5}, (2017).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-1CzUZwyU2}{}}%
+\CSLLeftMargin{34. }
+\CSLRightInline{Tenopir, C.
+\emph{et al.} \href{https://doi.org/10.1371/journal.pone.0134826}{Changes in Data Sharing and Data Reuse Practices and Perceptions among Scientists Worldwide}.
+\emph{PLoS ONE} \textbf{10}, e0134826 (2015).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-666HppfO}{}}%
+\CSLLeftMargin{35. }
+\CSLRightInline{Pronk, T.
+E., Wiersma, P.
+H., van Weerden, A.
+\& Schieving, F.
+\href{https://doi.org/10.7717/peerj.1242}{A game theoretic analysis of research data sharing}.
+\emph{PeerJ} \textbf{3}, e1242 (2015).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-1CcAUn3Lu}{}}%
+\CSLLeftMargin{36. }
+\CSLRightInline{Piwowar, H.
+A., Day, R.
+S.
+\& Fridsma, D.
+B.
+\href{https://doi.org/10.1371/journal.pone.0000308}{Sharing Detailed Research Data Is Associated with Increased Citation Rate}.
+\emph{PLoS ONE} \textbf{2}, e308 (2007).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-4LaijDIZ}{}}%
+\CSLLeftMargin{37. }
+\CSLRightInline{\href{https://doi.org/10.1038/ncb3506}{On data availability, reproducibility and reuse}. \emph{Nat Cell Biol} \textbf{19}, 259--259 (2017).}
 
 \leavevmode\vadjust pre{\hypertarget{ref-uBJwnPbq}{}}%
-\CSLLeftMargin{31. }
+\CSLLeftMargin{38. }
 \CSLRightInline{Mislan, K.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-1HZdsK5Kn}{}}%
-\CSLLeftMargin{32. }
+\CSLLeftMargin{39. }
 \CSLRightInline{Baker, M. \href{https://doi.org/10.1038/533452a}{1,500 scientists lift the lid on reproducibility}. \emph{Nature} \textbf{533}, 452--454 (2016).}
 
+\leavevmode\vadjust pre{\hypertarget{ref-1Du6fzB8g}{}}%
+\CSLLeftMargin{40. }
+\CSLRightInline{Crystal‐Ornelas, R.
+\emph{et al.} \href{https://doi.org/10.1029/2021ea001797}{A Guide to Using GitHub for Developing and Versioning Data Standards and Reporting Formats}.
+\emph{Earth Space Sci} \textbf{8}, (2021).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-iIEKCTLU}{}}%
+\CSLLeftMargin{41. }
+\CSLRightInline{Hampton, S. E. \emph{et al.} \href{https://doi.org/10.1890/es14-00402.1}{The Tao of open science for ecology}. \emph{Ecosphere} \textbf{6}, art120 (2015).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-TOsASkn5}{}}%
+\CSLLeftMargin{42. }
+\CSLRightInline{Adding a license to a repository.
+\emph{GitHub Docs} \url{https://ghdocs-prod.azurewebsites.net/en/communities/setting-up-your-project-for-healthy-contributions/adding-a-license-to-a-repository}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-1BJcvyTmV}{}}%
+\CSLLeftMargin{43. }
+\CSLRightInline{Vale, G., Schmid, A., Santos, A.
+R., de Almeida, E.
+S.
+\& Apel, S.
+\href{https://doi.org/10.1007/s10664-019-09774-x}{On the relation between Github communication activity and merge conflicts}.
+\emph{Empir Software Eng} \textbf{25}, 402--433 (2019).}
+
 \leavevmode\vadjust pre{\hypertarget{ref-K7nbP1Ty}{}}%
-\CSLLeftMargin{33. }
+\CSLLeftMargin{44. }
 \CSLRightInline{Crystal-Ornelas, R.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-hm9PaCLD}{}}%
-\CSLLeftMargin{34. }
+\CSLLeftMargin{45. }
 \CSLRightInline{Song, X., Goldstein, S.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-YuJbg3zO}{}}%
-\CSLLeftMargin{35. }
+\CSLLeftMargin{46. }
 \CSLRightInline{Himmelstein, D. S. \emph{et al.} \href{https://doi.org/10.1371/journal.pcbi.1007128}{Open collaborative writing with Manubot}. \emph{PLoS Comput Biol} \textbf{15}, e1007128 (2019).}
 
-\leavevmode\vadjust pre{\hypertarget{ref-i4FOZpjN}{}}%
-\CSLLeftMargin{36. }
-\CSLRightInline{Lasser, J. \href{https://doi.org/10.1038/s42005-020-00403-4}{Creating an executable paper is a journey through Open Science}. \emph{Commun Phys} \textbf{3}, (2020).}
-
 \leavevmode\vadjust pre{\hypertarget{ref-Xsdcv6q}{}}%
-\CSLLeftMargin{37. }
+\CSLLeftMargin{47. }
 \CSLRightInline{Boettiger, C., Lang, D.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-FVBWKkZu}{}}%
-\CSLLeftMargin{38. }
+\CSLLeftMargin{48. }
 \CSLRightInline{Chamberlain, S. A. \& Szöcs, E. \href{https://doi.org/10.12688/f1000research.2-191.v2}{taxize: taxonomic search and retrieval in R}. \emph{F1000Res} \textbf{2}, 191 (2013).}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-18PTmKJkq}{}}%
-\CSLLeftMargin{39. }
+\CSLLeftMargin{49. }
 \CSLRightInline{January 18, P.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-NOgBWVAr}{}}%
-\CSLLeftMargin{40. }
+\CSLLeftMargin{50. }
 \CSLRightInline{Culina, A., van den Berg, I., Evans, S.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-D4C4k4ak}{}}%
-\CSLLeftMargin{41. }
+\CSLLeftMargin{51. }
 \CSLRightInline{Fehr, J., Himpe, C., Rave, S. \& Saak, J. \href{https://doi.org/10.5334/jors.307}{Sustainable Research Software Hand-Over}. \emph{JORS} \textbf{9}, 5 (2021).}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-s91uGRZ2}{}}%
-\CSLLeftMargin{42. }
+\CSLLeftMargin{52. }
 \CSLRightInline{About code owners.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-UsTxAq4f}{}}%
-\CSLLeftMargin{43. }
+\CSLLeftMargin{53. }
 \CSLRightInline{Anbaroğlu, B. \href{https://doi.org/10.1111/tgis.12810}{A collaborative GIS programming course using GitHub Classroom}. \emph{Transactions in GIS} \textbf{25}, 3132--3158 (2021).}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-lx49NGto}{}}%
-\CSLLeftMargin{44. }
+\CSLLeftMargin{54. }
 \CSLRightInline{Connect GitHub to a Project - OSF Support. \url{https://help.osf.io/article/211-connect-github-to-a-project}.}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-pjy75gHr}{}}%
-\CSLLeftMargin{45. }
+\CSLLeftMargin{55. }
 \CSLRightInline{Madicken Munk \emph{et al.} swcarpentry/git-novice: Software Carpentry: Version Control with Git, June 2019.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-ZvrOcg9w}{}}%
-\CSLLeftMargin{46. }
+\CSLLeftMargin{56. }
 \CSLRightInline{Hester, J. B., the STAT 545 TAs, Jim. \emph{\href{https://happygitwithr.com/}{Let's Git started \textbar{} Happy Git and GitHub for the useR}}.}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-6CMMeSeD}{}}%
-\CSLLeftMargin{47. }
+\CSLLeftMargin{57. }
 \CSLRightInline{Bryan, J. \& TAs, T. S. 545. \emph{\href{https://stat545.com/}{STAT 545}}.}

### 2022-06-23 editorial-communication/cover-letter-submission.Rmd

--- 2022-06-06 editorial-communication/cover-letter-submission.Rmd
@@
 Our manuscript is important for the *Nature Ecology & Evolution* readership because researchers in ecology and evolutionary biology can greatly benefit from our guide to migrate and incorporate GitHub workflows in their research practices ultimately towards an open and collaborative science.
+Also, we believe our manuscript complements a recently published manuscript in *Nature Ecology and Evolution*.
+In the manuscript, Gallagher et al.
+(2020) outline how the ongoing adoption of Open Science practices is transforming research in ecology and evolutionary biology.
+A key component of Open Science is the ability to collaboratively contribute to and share code and data--platforms like GitHub provide an free and accessible platform to do just that.
 

### 2022-06-23 manuscript.tex
Merge pull request #243 from SORTEE-Github-Hackathon/RCO-saeed-cover-letter [ci skip]
This build is based on
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/28647d1b51aa7df9b1214fa3fc7d0743b00d665e.

This commit was created by the following CI build and job:
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/28647d1b51aa7df9b1214fa3fc7d0743b00d665e/checks
https://github.com/SORTEE-Github-Hackathon/manuscript/actions/runs/2551271965

@@
 This manuscript
-(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/dc28d7dd993d0f5ca61b1bd7fc59d1cc22e39ce2/}{permalink})
+(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/28647d1b51aa7df9b1214fa3fc7d0743b00d665e/}{permalink})
 was automatically generated
-from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/dc28d7dd993d0f5ca61b1bd7fc59d1cc22e39ce2}{SORTEE-Github-Hackathon/manuscript@dc28d7d}
+from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/28647d1b51aa7df9b1214fa3fc7d0743b00d665e}{SORTEE-Github-Hackathon/manuscript@28647d1}
 on June 23, 2022.

### 2022-06-24 manuscript.tex
Merge pull request #244 from SORTEE-Github-Hackathon/emmajhudgins-patch-1 [ci skip]
This build is based on
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/b78a03a54df81c17eb98b9ca80e842dcb1883ab1.

This commit was created by the following CI build and job:
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/b78a03a54df81c17eb98b9ca80e842dcb1883ab1/checks
https://github.com/SORTEE-Github-Hackathon/manuscript/actions/runs/2552679395

@@
 This manuscript
-(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/28647d1b51aa7df9b1214fa3fc7d0743b00d665e/}{permalink})
+(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/b78a03a54df81c17eb98b9ca80e842dcb1883ab1/}{permalink})
 was automatically generated
-from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/28647d1b51aa7df9b1214fa3fc7d0743b00d665e}{SORTEE-Github-Hackathon/manuscript@28647d1}
-on June 23, 2022.
+from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/b78a03a54df81c17eb98b9ca80e842dcb1883ab1}{SORTEE-Github-Hackathon/manuscript@b78a03a}
+on June 24, 2022.
 
@@
 Most scientists, including ecologists and evolutionary biologists, are increasingly dependent on computational tools in their research\textsuperscript{\protect\hyperlink{ref-fJWFe93e}{1}}.
-Researchers write and use software packages or data analysis code (hereafter, code) as part of their scientific workflow to perform a wide-variety of tasks ranging from data management, data analysis, and study replication, to the application and the development of tools for hypothesis testing.
-To maintain code for scientific collaboration requires an efficient and well-documented work-flow\textsuperscript{\protect\hyperlink{ref-1Kqna6l2}{2}}.
-To facilitate this process, scientists have been increasingly adopting tools from information and systems technology, such as cloud-based services for documentation and version control (\emph{e.g.}, from the Google Suite, with Docs, Sheets, and Drive; the Microsoft Suite, with Word, Excel, and OneDrive; and GitHub;\textsuperscript{\protect\hyperlink{ref-10ghgV3S8}{3}}).
-However, most researchers lack exposure to adequate code development practices and are required to dedicate valuable time and effort to self-teach the use of research-facilitating tools, and thus may be limited in their ability to adhere to adequate standards of scientific code quality and maintenance\textsuperscript{\protect\hyperlink{ref-fJWFe93e}{1},\protect\hyperlink{ref-10SpoByIw}{4},\protect\hyperlink{ref-O6UbstGG}{5}}.
-Here, we review and discuss one of the most used web-based platforms for computational version control and collaboration, GitHub, and provide researchers in ecology and evolutionary biology (EEB) with practical workflows aimed at facilitating their scientific code and management process.
-
-With over 73 million registered users, as of 2022, GitHub is the most widely-used web platform for collaborating on computer code\textsuperscript{\protect\hyperlink{ref-nwCtHDCn}{6}}.
+Researchers write and use software packages or data analysis code (hereafter, code) to perform scientific tasks ranging from data management, data analysis, and study replication, to the application and the development of tools for hypothesis testing.
+Maintaining code for scientific collaboration requires an efficient and well-documented work-flow\textsuperscript{\protect\hyperlink{ref-1Kqna6l2}{2}}.
+To facilitate this process, scientists have been increasingly adopting tools from information and systems technology, such as cloud-based services for documentation and version control (\emph{e.g.}, from the Google Suite, the Microsoft Suite, and GitHub,\textsuperscript{\protect\hyperlink{ref-10ghgV3S8}{3}}).
+However, most researchers lack exposure to adequate code practices and thus dedicate valuable time and effort to self-teaching research-facilitating tools.
+Thus, researchers may not adhere to standards of code quality and maintenance\textsuperscript{\protect\hyperlink{ref-fJWFe93e}{1},\protect\hyperlink{ref-10SpoByIw}{4},\protect\hyperlink{ref-O6UbstGG}{5}}.
+Here, we review and discuss one of the most used web-based platforms for computational version control and collaboration, GitHub, and provide researchers in ecology and evolutionary biology (EEB) with practical workflows to facilitate and improve their code and its management.
+
+With over 73 million registered users as of 2022, GitHub is the most widely-used web platform for collaborating on computer code\textsuperscript{\protect\hyperlink{ref-nwCtHDCn}{6}}.
 GitHub provides a simplified but powerful web interface that allows users to participate in projects, contribute code, report and discuss code bugs, discover existing code and data, and publish new code.
 Through version control, users have a detailed, chronological record of the files and directories stored in their repositories (see \protect\hyperlink{definitions}{Box 1};\textsuperscript{\protect\hyperlink{ref-RVetqmsg}{7}}).
-This workflow provides a strong and clear advantage over receiving, processing and sending files back-and-forth (e.g.~via email), a process that can easily become challenging and time-consuming in projects extending in time and in the number of collaborators\textsuperscript{\protect\hyperlink{ref-4ny1onB0}{8}}.
-Through the combination of version control management and the network- and collaboration-based features, GitHub can broadly facilitate openly available source code alongside concomitant collaborative development\textsuperscript{\protect\hyperlink{ref-kEX5dgzK}{9}}.
+This workflow provides a strong and clear advantage over sending files back-and-forth (\emph{e.g.} via email), a process that can become challenging and time-consuming in more long-term and collaborative projects\textsuperscript{\protect\hyperlink{ref-4ny1onB0}{8}}.
+Through its combination of version control and and collaborative features, GitHub facilitates open source code alongside collaborative development\textsuperscript{\protect\hyperlink{ref-kEX5dgzK}{9}}.
 
@@
 Although the understanding of basic concepts of Git (such as commit, push, pull, checkout; see \protect\hyperlink{definitions}{Box 1}) is necessary, the GitHub web-based platform and its integrated development environments (such as the GitHub Desktop) allow users to perform most repository and data management operations without opening Git command-line sessions.
-Still, GitHub users are encouraged to explore and improve their proficiency in Git when feeling comfortable, so they can feel confident in performing more flexible, complex operations (such as integrating changes from one branch into another branch with \texttt{git\ merge} and \texttt{git\ rebase}).
-Examples of extensive explanations on Git can be found in journal articles\textsuperscript{\protect\hyperlink{ref-kEX5dgzK}{9},\protect\hyperlink{ref-PlcxShQU}{10}}, video tutorials\textsuperscript{\protect\hyperlink{ref-NIS0JOW0}{11}}, and books\textsuperscript{\protect\hyperlink{ref-13jOlVcpp}{12}}.
-
-The expansive GitHub user-community and the numerous resources on how to use GitHub have boosted its growing popularity\textsuperscript{\protect\hyperlink{ref-RVetqmsg}{7},\protect\hyperlink{ref-kEX5dgzK}{9},\protect\hyperlink{ref-13jOlVcpp}{12}/,\protect\hyperlink{ref-u5aEVE4B}{13}}.
-Nevertheless, although multiple articles have encouraged researchers in EEB to adopt GitHub as part of their research process\textsuperscript{\protect\hyperlink{ref-10ghgV3S8}{3},\protect\hyperlink{ref-3DKwn1sY}{14}}, its use is still not widespread.
-First-time users without formal training in information technology may face steep learning curves because GitHub and its features have been centered on collaboration for code development in information systems\textsuperscript{\protect\hyperlink{ref-139b0pSGc}{15}}.
-Moreover, domain-specific perspectives and resources providing tractable examples and practical guidance for researchers in EEB on GitHub are scarce (but see https://ourcodingclub.github.io; https://www.openscapes.org).
-A common adoption of GitHub for collaborating on a variety of research tasks can ultimately enable EEB researchers to spend less time on creating novel processes for collaboration and more time on their research\textsuperscript{\protect\hyperlink{ref-ydrk01SR}{16}}.
-More importantly, increasing the availability of data and code management standards -- of which GitHub is one increasingly important component -- make research more reproducible and collaborative\textsuperscript{\protect\hyperlink{ref-13QX8XU3J}{17}}.
-
-This paper is the result of an academic hackathon held during the 2021 conference for the Society for Open, Reliable, and Transparent Ecology and Evolutionary Biology (SORTEE, https://www.sortee.org).
+
+The expansive GitHub user-community and numerous GitHub resources have boosted its popularity\textsuperscript{\protect\hyperlink{ref-RVetqmsg}{7},\protect\hyperlink{ref-kEX5dgzK}{9},\protect\hyperlink{ref-13jOlVcpp}{10}/,\protect\hyperlink{ref-u5aEVE4B}{11}}.
+Nevertheless, although multiple articles have encouraged researchers in EEB to adopt GitHub as part of their research process\textsuperscript{\protect\hyperlink{ref-10ghgV3S8}{3},\protect\hyperlink{ref-3DKwn1sY}{12}}, its use is still not widespread.
+First-time users without formal training in information technology may face steep learning curves because GitHub and its features have been centered on collaboration for code development in information systems\textsuperscript{\protect\hyperlink{ref-139b0pSGc}{13}}.
+Moreover, domain-specific resources providing tractable examples and practical guidance for researchers in EEB on GitHub are scarce (but see \url{https://ourcodingclub.github.io}; \url{https://www.openscapes.org}).
+Widespread adoption of GitHub for collaborating on research tasks can ultimately enable EEB researchers to spend less time on creating novel processes for collaboration and more time on their research\textsuperscript{\protect\hyperlink{ref-ydrk01SR}{14}}.
+More importantly, increasing the availability of data and code management standards -- of which GitHub is one increasingly important component -- makes research more reproducible and collaborative\textsuperscript{\protect\hyperlink{ref-13QX8XU3J}{15}}.
+
+This paper is the result of an academic hackathon held during the 2021 conference for the Society for Open, Reliable, and Transparent Ecology and Evolutionary Biology (SORTEE, \url{https://www.sortee.org}).
 We convened a group of around thirty researchers in EEB with varying levels of familiarity with using GitHub as part of their research projects to showcase and discuss how existing features can contribute to documentation and collaboration in EEB research.
@@
 Even if they do not have access to \textbf{push} to the original repository, they can make a fork and edit it independently.
-Forks are linked to the original GitHub repository and ``upstream'' changes (i.e.~those in the original repository) can be \textbf{merged} to keep the fork up to date with the original project.
+Forks are linked to the original GitHub repository and ``upstream'' changes (\emph{i.e.} those in the original repository) can be \textbf{merged} to keep the fork up to date with the original project.
 Changes made in the fork can be integrated into the original project via \textbf{pull requests}.
 \\
-\textbf{clone}: Cloning a \textbf{repository} is a way of making a local copy (i.e.~on your computer) of a GitHub \textbf{repository}.
+\textbf{clone}: Cloning a \textbf{repository} is a way of making a local copy (\emph{i.e.} on your computer) of a GitHub \textbf{repository}.
 If you have access to \textbf{push} to a \textbf{repository}, this can be a first step to contributing to a project.
@@
 Commits can include changes in multiple files and must include a brief commit message describing the changes made.
-A typical workflow is to make some related changes in files, add a commit message (e.g.~``generate and include fig1 in results''), and after several commits \textbf{push} those commits to the remote (\emph{i.e.}, cloud-based) GitHub \textbf{repository}.
+A typical workflow is to make some related changes in files, add a commit message (\emph{e.g.} ``generate and include fig1 in results''), and after several commits \textbf{push} those commits to the remote (\emph{i.e.}, cloud-based) GitHub \textbf{repository}.
 \\
@@
 Having copies of these files safely stored is essential to protect against accidental modifications or deletions.
-Many researchers begin using GitHub as a means to store (or backup) their research compendium\textsuperscript{\protect\hyperlink{ref-MwwMapRG}{18}} to a centralized, readily-available remote server (see \protect\hyperlink{definitions}{Box 1}).
+Many researchers begin using GitHub as a means to store (or backup) their research compendium\textsuperscript{\protect\hyperlink{ref-MwwMapRG}{16}} to a centralized, readily-available remote server (see \protect\hyperlink{definitions}{Box 1}).
 A centralized research compendium stored in a version-controlled repository has the advantages of facilitating collaboration, integrating data and code archiving services, allowing file versions to be accessed and restored, and contributes to open science (see sections below).
 
-GitHub limits committed file sizes to 100 Mb (megabytes) (\textsuperscript{\protect\hyperlink{ref-1Co6ZZjF1}{19}}), which can make it challenging for centralizing research compedia containing larger file sizes.
-Users may still version large files using Git Large File Storage (LFS;\textsuperscript{\protect\hyperlink{ref-11GtZ7icJ}{20}}/) text pointers, but may have to rely on external file storage alternatives (such as local or cloud-hosting).
+GitHub limits committed file sizes to 100 Mb (megabytes) (\textsuperscript{\protect\hyperlink{ref-1Co6ZZjF1}{17}}), which can make it challenging for centralizing research compedia containing larger file sizes.
+Users may still version large files using Git Large File Storage (LFS;\textsuperscript{\protect\hyperlink{ref-11GtZ7icJ}{18}}/) text pointers, but may have to rely on external file storage alternatives (such as local or cloud-hosting).
 
@@
 
-Laboratory notebooks help researchers track their research notes, methods, policies and protocols\textsuperscript{\protect\hyperlink{ref-wwHxTOtm}{21}}.
-Virtual laboratory notebooks can be stored in GitHub repositories and provide the benefits of simultaneous, centralized and selective access, and allows for the easy update of policies and experiment protocols\textsuperscript{\protect\hyperlink{ref-10V7x4H4l}{22}}.
+Laboratory notebooks help researchers track their research notes, methods, policies and protocols\textsuperscript{\protect\hyperlink{ref-wwHxTOtm}{19}}.
+Virtual laboratory notebooks can be stored in GitHub repositories and provide the benefits of simultaneous, centralized and selective access, and allows for the easy update of policies and experiment protocols\textsuperscript{\protect\hyperlink{ref-10V7x4H4l}{20}}.
 Researchers have been increasingly using GitHub to maintain versions and share digital laboratory notebooks\textsuperscript{\protect\hyperlink{ref-10ghgV3S8}{3}} (\emph{e.g.}, \url{https://scheuerell-lab.github.io/lab-book}; \url{https://github.com/HuckleyLab/how_we_work}).
@@
 Github Discussions serve as a message board for conversation.
-Finally, GitHub Projects integrate issues and pull requests on automated spreadsheets and project boards, providing users with real-time tracking of project priorities and status\textsuperscript{\protect\hyperlink{ref-RhBKe0MG}{23}}.
+Finally, GitHub Projects integrate issues and pull requests on automated spreadsheets and project boards, providing users with real-time tracking of project priorities and status\textsuperscript{\protect\hyperlink{ref-RhBKe0MG}{21}}.
 Scripts, commit messages, and pull requests can be linked directly to issues, discussions, and projects providing a clear record of project workflow.
@@
 Project management in GitHub can also be integrated with third-party applications, such as ZenHub (https://www.zenhub.com/) or Slack (https://slack.github.com/).
-ZenHub allows for the enhanced visualization and organization of repositories and their issues, while the GitHub for Slack integration allows notifications from GitHub events to be sent directly to users or group channels\textsuperscript{\protect\hyperlink{ref-1GRWGlDWy}{24}}.
+ZenHub allows for the enhanced visualization and organization of repositories and their issues, while the GitHub for Slack integration allows notifications from GitHub events to be sent directly to users or group channels\textsuperscript{\protect\hyperlink{ref-1GRWGlDWy}{22}}.
 
@@
 
-Making presentations, syllabi and other course materials can be done through most major high-level programming languages such as R, with \texttt{RMarkdown}\textsuperscript{\protect\hyperlink{ref-QqMezOMg}{25}}, Python, with \texttt{python-ppt} (\url{https://python-pptx.readthedocs.io}), and Julia, with \texttt{Remark.jl} (\url{https://juliapackages.com/p/remark}), and be version-controlled and stored in GitHub.
-Once content is made, hosting a course website can be done through GitHub Pages\textsuperscript{\protect\hyperlink{ref-MDQfMwCW}{26}} (\emph{e.g.}, https://github.com/topics/course-website\textgreater).
+Making presentations, syllabi and other course materials can be done through most major high-level programming languages such as R, with \texttt{RMarkdown}\textsuperscript{\protect\hyperlink{ref-QqMezOMg}{23}}, Python, with \texttt{python-ppt} (\url{https://python-pptx.readthedocs.io}), and Julia, with \texttt{Remark.jl} (\url{https://juliapackages.com/p/remark}), and be version-controlled and stored in GitHub.
+Once content is made, hosting a course website can be done through GitHub Pages\textsuperscript{\protect\hyperlink{ref-MDQfMwCW}{24}} (\emph{e.g.}, https://github.com/topics/course-website\textgreater).
 This way, the course content can be available to enrolled students, as well as a global pool of learners and teachers interested in the course material.
@@
 Student submissions are perhaps the most challenging component, but the new GitHub Classroom tool (\url{https://classroom.github.com}) allows instructors to host private assignments to be submitted collaboratively or individually as code or PDF files, and even build autograding tests.
-Although time-consuming to establish, using these features can integrate learning version control and GitHub with the learning course content, and thus boost students feelings of self-efficacy and confidence\textsuperscript{\protect\hyperlink{ref-dqrFjoSb}{27}}.
+Although time-consuming to establish, using these features can integrate learning version control and GitHub with the learning course content, and thus boost students feelings of self-efficacy and confidence\textsuperscript{\protect\hyperlink{ref-dqrFjoSb}{25}}.
 
@@
 
-Personal or laboratory websites can improve the sharing of research findings, build online presence, and increase coordination of research efforts\textsuperscript{\protect\hyperlink{ref-HiIPSSHV}{28}}.
+Personal or laboratory websites can improve the sharing of research findings, build online presence, and increase coordination of research efforts\textsuperscript{\protect\hyperlink{ref-HiIPSSHV}{26}}.
 Despite many researchers in ecology and evolution having little experience in building or hosting webpages, many tools have been developed to help this process.
@@
 The resulting files from static websites can then be hosted in repositories, from which one can activate GitHub's Pages (\url{https://pages.github.com}) feature, allowing for the direct live hosting of HyperText Markup Language (HTML), Cascading Style Sheets (CSS) and JavaScript files within a free github.io domain.
-Website templates are readily available on GitHub (https://github.com/topics/website-template) or in user-specific repositories, which can be forked (\protect\hyperlink{definitions}{Box 1}) and customized\textsuperscript{\protect\hyperlink{ref-MXxgZJ45}{29}}.
+Website templates are readily available on GitHub (https://github.com/topics/website-template) or in user-specific repositories, which can be forked (\protect\hyperlink{definitions}{Box 1}) and customized\textsuperscript{\protect\hyperlink{ref-MXxgZJ45}{27}}.
 Aside from free hosting services, GitHub Pages also allows websites to be autogenerated and instantly updated following content modifications\textsuperscript{\protect\hyperlink{ref-RVetqmsg}{7}}.
@@
 
-Government, funding agencies, and publishers exercise rigorous open access data policies and mandates\textsuperscript{\protect\hyperlink{ref-PLmDFZrm}{30},\protect\hyperlink{ref-1Hcf13Q0k}{31}}.
-However, code and data sharing may be met by individual reluctance, temporary embargoes, or partially prevented by privacy and confidentiality reasons\textsuperscript{\protect\hyperlink{ref-1Ch6LSHef}{32}--\protect\hyperlink{ref-1CzUZwyU2}{34}}.
-Still, data deposition and ensuring its availability can amplify the outreach of published studies\textsuperscript{\protect\hyperlink{ref-666HppfO}{35}}, increase citation rates\textsuperscript{\protect\hyperlink{ref-1CcAUn3Lu}{36}}, and among many other reasons, enables the reproducibility and robustness of scientific advances\textsuperscript{\protect\hyperlink{ref-4LaijDIZ}{37}--\protect\hyperlink{ref-1HZdsK5Kn}{39}}.
+Government, funding agencies, and publishers exercise rigorous open access data policies and mandates\textsuperscript{\protect\hyperlink{ref-PLmDFZrm}{28},\protect\hyperlink{ref-1Hcf13Q0k}{29}}.
+However, code and data sharing may be met by individual reluctance, temporary embargoes, or partially prevented by privacy and confidentiality reasons\textsuperscript{\protect\hyperlink{ref-1Ch6LSHef}{30}--\protect\hyperlink{ref-1CzUZwyU2}{32}}.
+Still, data deposition and ensuring its availability can amplify the outreach of published studies\textsuperscript{\protect\hyperlink{ref-666HppfO}{33}}, increase citation rates\textsuperscript{\protect\hyperlink{ref-1CcAUn3Lu}{34}}, and among many other reasons, enables the reproducibility and robustness of scientific advances\textsuperscript{\protect\hyperlink{ref-4LaijDIZ}{35}--\protect\hyperlink{ref-1HZdsK5Kn}{37}}.
 While public repositories on GitHub make it easy to store and share data files, they are not considered long-term repositories for research materials.
@@
 DOIs are persistent and citable unique alpha-numeric identifiers assigned to digitally stored research materials.
-Because of this, scientists sharing code and data through GitHub are strongly encouraged to independently submit their research materials to long-term data archives (\emph{e.g.}, Zenodo, Figshare, Dryad, OSF\textsuperscript{\protect\hyperlink{ref-10ghgV3S8}{3},\protect\hyperlink{ref-kEX5dgzK}{9},\protect\hyperlink{ref-1Du6fzB8g}{40},\protect\hyperlink{ref-tbl:compare}{\textbf{tbl:compare?}}}.
+Because of this, scientists sharing code and data through GitHub are strongly encouraged to independently submit their research materials to long-term data archives (\emph{e.g.}, Zenodo, Figshare, Dryad, OSF\textsuperscript{\protect\hyperlink{ref-10ghgV3S8}{3},\protect\hyperlink{ref-kEX5dgzK}{9},\protect\hyperlink{ref-1Du6fzB8g}{38},\protect\hyperlink{ref-tbl:compare}{\textbf{tbl:compare?}}}.
 Some of these options (Zenodo, Figshare and OSF) integrate with GitHub, allowing project, code, and data releases (\protect\hyperlink{definitions}{Box 1}) to be archived with versioned, citable DOIs.
-Linking GitHub repositories with a DOI helps research become findable, properly cited, and can ensure long-term stability\textsuperscript{\protect\hyperlink{ref-iIEKCTLU}{41}}.
+Linking GitHub repositories with a DOI helps research become findable, properly cited, and can ensure long-term stability\textsuperscript{\protect\hyperlink{ref-iIEKCTLU}{39}}.
 
@@
 Code published without a licence is under exclusive copyright (by default), protecting it from copy, distribution, and modifications.
-One may grant specific rights to their code for reuse by adding licensing files and specifications within GitHub repositories\textsuperscript{\protect\hyperlink{ref-TOsASkn5}{42}}.
+One may grant specific rights to their code for reuse by adding licensing files and specifications within GitHub repositories\textsuperscript{\protect\hyperlink{ref-TOsASkn5}{40}}.
 The Choose a License (\url{https://choosealicense.com/non-software/}) website offers further guidance on the licenses available for research and creative products.
@@
 By forking, branching, and cloning repositories (\protect\hyperlink{definitions}{Box 1}), researchers can simultaneously work on different issues of the same research project to then later merge changes to the main branch project with pull requests.
-Explicit project organization and increased communication in GitHub Issues, Discussions, or within pull requests can help with project development and with potential merge conflicts due to users simultaneously working on the same sections\textsuperscript{\protect\hyperlink{ref-1BJcvyTmV}{43}}.
-Moreover, version control\textsuperscript{\protect\hyperlink{ref-K7nbP1Ty}{44}} and commit reversal features allow researchers to track and progress without worrying about irreparably modifying someone else's work.
+Explicit project organization and increased communication in GitHub Issues, Discussions, or within pull requests can help with project development and with potential merge conflicts due to users simultaneously working on the same sections\textsuperscript{\protect\hyperlink{ref-1BJcvyTmV}{41}}.
+Moreover, version control\textsuperscript{\protect\hyperlink{ref-K7nbP1Ty}{42}} and commit reversal features allow researchers to track and progress without worrying about irreparably modifying someone else's work.
 By enabling more comprehensive remote collaboration, GitHub encourages the exchange of ideas among researchers at different institutions and in different countries, which can serve to improve the quality of the research itself by providing open access to data and code.
 In academic settings, GitHub can also facilitate interactions between research advisors and advisees, providing a platform for students or other trainees to share in-progress code, and flag specific challenges or questions for their supervisors or mentors (\protect\hyperlink{tbl:roles}{Table 1}).
-Periodic code review\textsuperscript{\protect\hyperlink{ref-hm9PaCLD}{45}} can also help advisors identify errors early in the process, and inform further training and mentorship to fill gaps in skills.
+Periodic code review\textsuperscript{\protect\hyperlink{ref-hm9PaCLD}{43}} can also help advisors identify errors early in the process, and inform further training and mentorship to fill gaps in skills.
 
@@
 
-We wrote this manuscript using Manubot\textsuperscript{\protect\hyperlink{ref-YuJbg3zO}{46}}, a workflow implemented in GitHub to automatically render manuscripts and automate bibliographical tasks.
+We wrote this manuscript using Manubot\textsuperscript{\protect\hyperlink{ref-YuJbg3zO}{44}}, a workflow implemented in GitHub to automatically render manuscripts and automate bibliographical tasks.
 Manubot uses GitHub's automation workflow, GitHub Actions, to combine and convert individual Markdown files into a single LaTeX document, which can then be converted to a Word or PDF document, and displayed as a webpage.
@@
 Additional GitHub Actions can be integrated with Manubot, such as ones creating figures or generating tables (\emph{e.g.}, https://github.com/SORTEE-Github-Hackathon/manuscript/tree/main/.github/workflows).
-For more examples of manuscripts built via Manubot, see\textsuperscript{\protect\hyperlink{ref-YuJbg3zO}{46}}.
+For more examples of manuscripts built via Manubot, see\textsuperscript{\protect\hyperlink{ref-YuJbg3zO}{44}}.
 
@@
 Certain journals or software development communities require submitted work or research code to be hosted on GitHub and their review processes make use of GitHub Issues {[}\emph{e.g.}, rOpenSci (\url{https://ropensci.org/software-review/}); Journal of Open Source Software (\url{https://joss.readthedocs.io/en/latest/submitting.html}){]}.
-rOpenSci's efforts have resulted in many well-used R packages for ecology research including \texttt{rfishbase}\textsuperscript{\protect\hyperlink{ref-Xsdcv6q}{47}} and \texttt{taxize}\textsuperscript{\protect\hyperlink{ref-FVBWKkZu}{48}}.
+rOpenSci's efforts have resulted in many well-used R packages for ecology research including \texttt{rfishbase}\textsuperscript{\protect\hyperlink{ref-Xsdcv6q}{45}} and \texttt{taxize}\textsuperscript{\protect\hyperlink{ref-FVBWKkZu}{46}}.
 
@@
 In the developmental stages, collaborators can directly see the code for the analysis, manipulate and explore the data themselves, and check for errors.
-Cynically, there is also more insurance against nefarious colleagues that may be tempted to distort results\textsuperscript{\protect\hyperlink{ref-18PTmKJkq}{49}}.
+Cynically, there is also more insurance against nefarious colleagues that may be tempted to distort results\textsuperscript{\protect\hyperlink{ref-18PTmKJkq}{47}}.
 Collaborators as well as pre-publication and post-publication reviewers are better positioned to discover questionable findings if they have full and transparent access to the project.
@@
 This transparency can similarly be extended beyond coauthors to the entire scientific community.
-Publishing the data and reproducible workflows along with the manuscript allows any reader to review the analysis and reproduce the experiment\textsuperscript{\protect\hyperlink{ref-NOgBWVAr}{50}}.
+Publishing the data and reproducible workflows along with the manuscript allows any reader to review the analysis and reproduce the experiment\textsuperscript{\protect\hyperlink{ref-NOgBWVAr}{48}}.
 Supplying code for (novel) methods that are proposed or used also reduces barriers to knowledge and can greatly improve the ability of others to build on existing work, resulting in greater proliferation and accessibility for a broader audience.
@@
 
-The development of research code continues, and so does the need to consider project continuity, especially in EEB where graduate students, research assistants, and postdoctoral fellows often hold relatively short-term positions\textsuperscript{\protect\hyperlink{ref-D4C4k4ak}{51}}.
+The development of research code continues, and so does the need to consider project continuity, especially in EEB where graduate students, research assistants, and postdoctoral fellows often hold relatively short-term positions\textsuperscript{\protect\hyperlink{ref-D4C4k4ak}{49}}.
 Often with these types of short-term research projects, once the contract expires, the research code upkeep tends to fall off as the researchers move on to new projects.
 Additionally, if the code is kept on only the researcher's personal devices, it becomes increasingly difficult to access the code for future uses.
-As projects or contracts end, there should be a handover period of this code in order for the next cohort of researchers to reuse what was already developed\textsuperscript{\protect\hyperlink{ref-4ny1onB0}{8},\protect\hyperlink{ref-D4C4k4ak}{51}}.
+As projects or contracts end, there should be a handover period of this code in order for the next cohort of researchers to reuse what was already developed\textsuperscript{\protect\hyperlink{ref-4ny1onB0}{8},\protect\hyperlink{ref-D4C4k4ak}{49}}.
 
 GitHub facilitates project continuity among research code by providing tools that make this handover period easier.
-As we have already mentioned, using Git for code in Ecology and Evolution can allow for a ``paper trail'' of sorts to be created for the code, thus allowing for future users of the code access to the entire history of the project\textsuperscript{\protect\hyperlink{ref-3DKwn1sY}{14}}.
-Additionally, GitHub allows for repositories and organizations to have designated Code Owners\textsuperscript{\protect\hyperlink{ref-s91uGRZ2}{52}}; these code owners can change through time allowing for the transition of code from one cohort of researchers to the next\textsuperscript{\protect\hyperlink{ref-iIEKCTLU}{41}}.
+As we have already mentioned, using Git for code in Ecology and Evolution can allow for a ``paper trail'' of sorts to be created for the code, thus allowing for future users of the code access to the entire history of the project\textsuperscript{\protect\hyperlink{ref-3DKwn1sY}{12}}.
+Additionally, GitHub allows for repositories and organizations to have designated Code Owners\textsuperscript{\protect\hyperlink{ref-s91uGRZ2}{50}}; these code owners can change through time allowing for the transition of code from one cohort of researchers to the next\textsuperscript{\protect\hyperlink{ref-iIEKCTLU}{39}}.
 There are also multiple means by which to archive code dependency information with GitHub.
@@
 
-There have been many calls for researchers outside of the software development community to join the 73 million GitHub users for their collaborative research\textsuperscript{\protect\hyperlink{ref-10ghgV3S8}{3},\protect\hyperlink{ref-1Du6fzB8g}{40},\protect\hyperlink{ref-UsTxAq4f}{53}}.
+There have been many calls for researchers outside of the software development community to join the 73 million GitHub users for their collaborative research\textsuperscript{\protect\hyperlink{ref-10ghgV3S8}{3},\protect\hyperlink{ref-1Du6fzB8g}{38},\protect\hyperlink{ref-UsTxAq4f}{51}}.
 This call comes in light of both the continual shift toward open-science and increasing computational and data requirements in EEB.
@@
 The default public nature of GitHub usage can add additional pressure to students and scientists learning to use the platform.
-We also note that large file storage is discouraged (and limited) on GitHub but add-ons do exist (e.g.~\url{https://git-lfs.github.com/}) that permit data storage, and increasing integration between platforms (e.g.\textsuperscript{\protect\hyperlink{ref-lx49NGto}{54}}) allows data to be stored away from GitHub and linked dynamically.
+We also note that large file storage is discouraged (and limited) on GitHub but add-ons do exist (e.g.~\url{https://git-lfs.github.com/}) that permit data storage, and increasing integration between platforms (e.g.\textsuperscript{\protect\hyperlink{ref-lx49NGto}{52}}) allows data to be stored away from GitHub and linked dynamically.
 We suspect a major additional barrier to EEB researchers is a distinct lack of GitHub help documents for non-English researchers in ecology and evolution, meaning that EEB researchers potentially miss the opportunity to fully understand the importance of version control, reproducibility, and other benefits of GitHub.
@@
 \\
-2. \textbf{Consider taking free courses.} such as those from Software Carpentry\textsuperscript{\protect\hyperlink{ref-pjy75gHr}{55}} and sharing these courses with your lab members or colleagues. \\
+2. \textbf{Consider taking free courses.} such as those from Software Carpentry\textsuperscript{\protect\hyperlink{ref-pjy75gHr}{53}} and sharing these courses with your lab members or colleagues. \\
 3.
@@
 6.
-\textbf{The Jenny Bryan universe of GitHub material.} provides a thorough and accessible introduction for a multitude of research-related uses for GitHub, and includes a book\textsuperscript{\protect\hyperlink{ref-ZvrOcg9w}{56}}, statistics course\textsuperscript{\protect\hyperlink{ref-6CMMeSeD}{57}} and academic article\textsuperscript{\protect\hyperlink{ref-RVetqmsg}{7}}.
+\textbf{The Jenny Bryan universe of GitHub material.} provides a thorough and accessible introduction for a multitude of research-related uses for GitHub, and includes a book\textsuperscript{\protect\hyperlink{ref-ZvrOcg9w}{54}}, statistics course\textsuperscript{\protect\hyperlink{ref-6CMMeSeD}{55}} and academic article\textsuperscript{\protect\hyperlink{ref-RVetqmsg}{7}}.
 \\
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-PlcxShQU}{}}%
+\leavevmode\vadjust pre{\hypertarget{ref-13jOlVcpp}{}}%
 \CSLLeftMargin{10. }
-\CSLRightInline{Blischak, J.
-D., Davenport, E.
-R.
-\& Wilson, G.
-\href{https://doi.org/10.1371/journal.pcbi.1004668}{A Quick Introduction to Version Control with Git and GitHub}.
-\emph{PLoS Comput Biol} \textbf{12}, e1004668 (2016).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-NIS0JOW0}{}}%
+\CSLRightInline{Hester, J. B., the STAT 545 TAs, Jim. \emph{\href{https://happygitwithr.com/}{Let's Git started \textbar{} Happy Git and GitHub for the useR}}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-u5aEVE4B}{}}%
 \CSLLeftMargin{11. }
-\CSLRightInline{\emph{\href{https://www.youtube.com/watch?v=USjZcfj8yxE}{Learn Git In 15 Minutes}}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-13jOlVcpp}{}}%
+\CSLRightInline{Coding Club: A Positive Peer-Learning Community. \url{https://ourcodingclub.github.io/}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-3DKwn1sY}{}}%
 \CSLLeftMargin{12. }
-\CSLRightInline{Hester, J. B., the STAT 545 TAs, Jim. \emph{\href{https://happygitwithr.com/}{Let's Git started \textbar{} Happy Git and GitHub for the useR}}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-u5aEVE4B}{}}%
-\CSLLeftMargin{13. }
-\CSLRightInline{Coding Club: A Positive Peer-Learning Community. \url{https://ourcodingclub.github.io/}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-3DKwn1sY}{}}%
-\CSLLeftMargin{14. }
 \CSLRightInline{Lowndes, J.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-139b0pSGc}{}}%
-\CSLLeftMargin{15. }
+\CSLLeftMargin{13. }
 \CSLRightInline{Leibzon, W.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-ydrk01SR}{}}%
+\CSLLeftMargin{14. }
+\CSLRightInline{Briney, K., Coates, H. \& Goben, A. \href{https://doi.org/10.3897/rio.6.e56508}{Foundational Practices of Research Data Management}. \emph{RIO} \textbf{6}, (2020).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-13QX8XU3J}{}}%
+\CSLLeftMargin{15. }
+\CSLRightInline{Alston, J. M. \& Rick, J. A. \href{https://doi.org/10.1002/bes2.1801}{A Beginner's Guide to Conducting Reproducible Research}. \emph{Bull. Ecol. Soc. Am.} \textbf{102}, (2021).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-MwwMapRG}{}}%
 \CSLLeftMargin{16. }
-\CSLRightInline{Briney, K., Coates, H. \& Goben, A. \href{https://doi.org/10.3897/rio.6.e56508}{Foundational Practices of Research Data Management}. \emph{RIO} \textbf{6}, (2020).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-13QX8XU3J}{}}%
-\CSLLeftMargin{17. }
-\CSLRightInline{Alston, J. M. \& Rick, J. A. \href{https://doi.org/10.1002/bes2.1801}{A Beginner's Guide to Conducting Reproducible Research}. \emph{Bull. Ecol. Soc. Am.} \textbf{102}, (2021).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-MwwMapRG}{}}%
-\CSLLeftMargin{18. }
 \CSLRightInline{Marwick, B., Boettiger, C.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-1Co6ZZjF1}{}}%
+\CSLLeftMargin{17. }
+\CSLRightInline{About large files on GitHub. \emph{GitHub Docs} \url{https://ghdocs-prod.azurewebsites.net/en/repositories/working-with-files/managing-large-files/about-large-files-on-github}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-11GtZ7icJ}{}}%
+\CSLLeftMargin{18. }
+\CSLRightInline{Git Large File Storage. \emph{Git Large File Storage} \url{https://git-lfs.github.com/}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-wwHxTOtm}{}}%
 \CSLLeftMargin{19. }
-\CSLRightInline{About large files on GitHub. \emph{GitHub Docs} \url{https://ghdocs-prod.azurewebsites.net/en/repositories/working-with-files/managing-large-files/about-large-files-on-github}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-11GtZ7icJ}{}}%
+\CSLRightInline{Kanza, S. \emph{et al.} \href{https://doi.org/10.1186/s13321-017-0221-3}{Electronic lab notebooks: can they replace paper?} \emph{J Cheminform} \textbf{9}, (2017).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-10V7x4H4l}{}}%
 \CSLLeftMargin{20. }
-\CSLRightInline{Git Large File Storage. \emph{Git Large File Storage} \url{https://git-lfs.github.com/}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-wwHxTOtm}{}}%
-\CSLLeftMargin{21. }
-\CSLRightInline{Kanza, S. \emph{et al.} \href{https://doi.org/10.1186/s13321-017-0221-3}{Electronic lab notebooks: can they replace paper?} \emph{J Cheminform} \textbf{9}, (2017).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-10V7x4H4l}{}}%
-\CSLLeftMargin{22. }
 \CSLRightInline{Schnell, S.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-RhBKe0MG}{}}%
+\CSLLeftMargin{21. }
+\CSLRightInline{About projects (beta). \emph{GitHub Docs} \url{https://ghdocs-prod.azurewebsites.net/en/issues/trying-out-the-new-projects-experience/about-projects}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-1GRWGlDWy}{}}%
+\CSLLeftMargin{22. }
+\CSLRightInline{Slack. GitHub for Slack. \emph{Slack Help Center} \url{https://slack.com/help/articles/232289568-GitHub-for-Slack}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-QqMezOMg}{}}%
 \CSLLeftMargin{23. }
-\CSLRightInline{About projects (beta). \emph{GitHub Docs} \url{https://ghdocs-prod.azurewebsites.net/en/issues/trying-out-the-new-projects-experience/about-projects}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-1GRWGlDWy}{}}%
+\CSLRightInline{Xie, Y., Allaire, J. J. \& Grolemund, G. \emph{R Markdown: the definitive guide}. (CRC Press, Taylor and Francis Group, 2019).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-MDQfMwCW}{}}%
 \CSLLeftMargin{24. }
-\CSLRightInline{Slack. GitHub for Slack. \emph{Slack Help Center} \url{https://slack.com/help/articles/232289568-GitHub-for-Slack}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-QqMezOMg}{}}%
+\CSLRightInline{Quickstart for GitHub Pages. \emph{GitHub Docs} \url{https://ghdocs-prod.azurewebsites.net/en/pages/quickstart}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-dqrFjoSb}{}}%
 \CSLLeftMargin{25. }
-\CSLRightInline{Xie, Y., Allaire, J. J. \& Grolemund, G. \emph{R Markdown: the definitive guide}. (CRC Press, Taylor and Francis Group, 2019).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-MDQfMwCW}{}}%
-\CSLLeftMargin{26. }
-\CSLRightInline{Quickstart for GitHub Pages. \emph{GitHub Docs} \url{https://ghdocs-prod.azurewebsites.net/en/pages/quickstart}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-dqrFjoSb}{}}%
-\CSLLeftMargin{27. }
 \CSLRightInline{Trujillo, G.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-HiIPSSHV}{}}%
-\CSLLeftMargin{28. }
+\CSLLeftMargin{26. }
 \CSLRightInline{Smaglik, P.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-MXxgZJ45}{}}%
-\CSLLeftMargin{29. }
+\CSLLeftMargin{27. }
 \CSLRightInline{Dawson, C. \emph{Building tools with GitHub: customize your workflow}. (O'Reilly, 2016).}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-PLmDFZrm}{}}%
-\CSLLeftMargin{30. }
+\CSLLeftMargin{28. }
 \CSLRightInline{Tenopir, C.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-1Hcf13Q0k}{}}%
-\CSLLeftMargin{31. }
+\CSLLeftMargin{29. }
 \CSLRightInline{Nugroho, R.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-1Ch6LSHef}{}}%
-\CSLLeftMargin{32. }
+\CSLLeftMargin{30. }
 \CSLRightInline{Wicherts, J.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-SLq38RVv}{}}%
-\CSLLeftMargin{33. }
+\CSLLeftMargin{31. }
 \CSLRightInline{Figueiredo, A. S. \href{https://doi.org/10.3389/fpubh.2017.00327}{Data Sharing: Convert Challenges into Opportunities}. \emph{Front. Public Health} \textbf{5}, (2017).}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-1CzUZwyU2}{}}%
-\CSLLeftMargin{34. }
+\CSLLeftMargin{32. }
 \CSLRightInline{Tenopir, C.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-666HppfO}{}}%
-\CSLLeftMargin{35. }
+\CSLLeftMargin{33. }
 \CSLRightInline{Pronk, T.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-1CcAUn3Lu}{}}%
-\CSLLeftMargin{36. }
+\CSLLeftMargin{34. }
 \CSLRightInline{Piwowar, H.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-4LaijDIZ}{}}%
-\CSLLeftMargin{37. }
+\CSLLeftMargin{35. }
 \CSLRightInline{\href{https://doi.org/10.1038/ncb3506}{On data availability, reproducibility and reuse}. \emph{Nat Cell Biol} \textbf{19}, 259--259 (2017).}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-uBJwnPbq}{}}%
-\CSLLeftMargin{38. }
+\CSLLeftMargin{36. }
 \CSLRightInline{Mislan, K.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-1HZdsK5Kn}{}}%
-\CSLLeftMargin{39. }
+\CSLLeftMargin{37. }
 \CSLRightInline{Baker, M. \href{https://doi.org/10.1038/533452a}{1,500 scientists lift the lid on reproducibility}. \emph{Nature} \textbf{533}, 452--454 (2016).}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-1Du6fzB8g}{}}%
-\CSLLeftMargin{40. }
+\CSLLeftMargin{38. }
 \CSLRightInline{Crystal‐Ornelas, R.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-iIEKCTLU}{}}%
-\CSLLeftMargin{41. }
+\CSLLeftMargin{39. }
 \CSLRightInline{Hampton, S. E. \emph{et al.} \href{https://doi.org/10.1890/es14-00402.1}{The Tao of open science for ecology}. \emph{Ecosphere} \textbf{6}, art120 (2015).}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-TOsASkn5}{}}%
-\CSLLeftMargin{42. }
+\CSLLeftMargin{40. }
 \CSLRightInline{Adding a license to a repository.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-1BJcvyTmV}{}}%
-\CSLLeftMargin{43. }
+\CSLLeftMargin{41. }
 \CSLRightInline{Vale, G., Schmid, A., Santos, A.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-K7nbP1Ty}{}}%
-\CSLLeftMargin{44. }
+\CSLLeftMargin{42. }
 \CSLRightInline{Crystal-Ornelas, R.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-hm9PaCLD}{}}%
-\CSLLeftMargin{45. }
+\CSLLeftMargin{43. }
 \CSLRightInline{Song, X., Goldstein, S.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-YuJbg3zO}{}}%
-\CSLLeftMargin{46. }
+\CSLLeftMargin{44. }
 \CSLRightInline{Himmelstein, D. S. \emph{et al.} \href{https://doi.org/10.1371/journal.pcbi.1007128}{Open collaborative writing with Manubot}. \emph{PLoS Comput Biol} \textbf{15}, e1007128 (2019).}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Xsdcv6q}{}}%
-\CSLLeftMargin{47. }
+\CSLLeftMargin{45. }
 \CSLRightInline{Boettiger, C., Lang, D.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-FVBWKkZu}{}}%
-\CSLLeftMargin{48. }
+\CSLLeftMargin{46. }
 \CSLRightInline{Chamberlain, S. A. \& Szöcs, E. \href{https://doi.org/10.12688/f1000research.2-191.v2}{taxize: taxonomic search and retrieval in R}. \emph{F1000Res} \textbf{2}, 191 (2013).}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-18PTmKJkq}{}}%
-\CSLLeftMargin{49. }
+\CSLLeftMargin{47. }
 \CSLRightInline{January 18, P.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-NOgBWVAr}{}}%
-\CSLLeftMargin{50. }
+\CSLLeftMargin{48. }
 \CSLRightInline{Culina, A., van den Berg, I., Evans, S.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-D4C4k4ak}{}}%
-\CSLLeftMargin{51. }
+\CSLLeftMargin{49. }
 \CSLRightInline{Fehr, J., Himpe, C., Rave, S. \& Saak, J. \href{https://doi.org/10.5334/jors.307}{Sustainable Research Software Hand-Over}. \emph{JORS} \textbf{9}, 5 (2021).}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-s91uGRZ2}{}}%
-\CSLLeftMargin{52. }
+\CSLLeftMargin{50. }
 \CSLRightInline{About code owners.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-UsTxAq4f}{}}%
+\CSLLeftMargin{51. }
+\CSLRightInline{Anbaroğlu, B. \href{https://doi.org/10.1111/tgis.12810}{A collaborative GIS programming course using GitHub Classroom}. \emph{Transactions in GIS} \textbf{25}, 3132--3158 (2021).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-lx49NGto}{}}%
+\CSLLeftMargin{52. }
+\CSLRightInline{Connect GitHub to a Project - OSF Support. \url{https://help.osf.io/article/211-connect-github-to-a-project}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-pjy75gHr}{}}%
 \CSLLeftMargin{53. }
-\CSLRightInline{Anbaroğlu, B. \href{https://doi.org/10.1111/tgis.12810}{A collaborative GIS programming course using GitHub Classroom}. \emph{Transactions in GIS} \textbf{25}, 3132--3158 (2021).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-lx49NGto}{}}%
-\CSLLeftMargin{54. }
-\CSLRightInline{Connect GitHub to a Project - OSF Support. \url{https://help.osf.io/article/211-connect-github-to-a-project}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-pjy75gHr}{}}%
-\CSLLeftMargin{55. }
 \CSLRightInline{Madicken Munk \emph{et al.} swcarpentry/git-novice: Software Carpentry: Version Control with Git, June 2019.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-ZvrOcg9w}{}}%
-\CSLLeftMargin{56. }
+\CSLLeftMargin{54. }
 \CSLRightInline{Hester, J. B., the STAT 545 TAs, Jim. \emph{\href{https://happygitwithr.com/}{Let's Git started \textbar{} Happy Git and GitHub for the useR}}.}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-6CMMeSeD}{}}%
-\CSLLeftMargin{57. }
+\CSLLeftMargin{55. }
 \CSLRightInline{Bryan, J. \& TAs, T. S. 545. \emph{\href{https://stat545.com/}{STAT 545}}.}

### 2022-06-28 manuscript.tex
Merge pull request #245 from SORTEE-Github-Hackathon/phpb-consistency-use-cases-c [ci skip]
This build is based on
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/773da7b1a68108cf2ee8aa5b261b6f4ab75fb2ab.

This commit was created by the following CI build and job:
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/773da7b1a68108cf2ee8aa5b261b6f4ab75fb2ab/checks
https://github.com/SORTEE-Github-Hackathon/manuscript/actions/runs/2574365882

@@
 This manuscript
-(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/b78a03a54df81c17eb98b9ca80e842dcb1883ab1/}{permalink})
+(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/773da7b1a68108cf2ee8aa5b261b6f4ab75fb2ab/}{permalink})
 was automatically generated
-from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/b78a03a54df81c17eb98b9ca80e842dcb1883ab1}{SORTEE-Github-Hackathon/manuscript@b78a03a}
-on June 24, 2022.
+from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/773da7b1a68108cf2ee8aa5b261b6f4ab75fb2ab}{SORTEE-Github-Hackathon/manuscript@773da7b}
+on June 28, 2022.
 
@@
 
-Research papers are condensed outputs that hide the underlying intellectual and computational workflows, including the treatment of the raw data and analytical steps.
-Granting readers access to code and other documentation of the analysis allows them to retrace and comprehend analytical decisions.
-GitHub provides a platform to access all aspects of the project, and can be linked to platforms that create citable DOIs, rather than just the final manuscript.
-While often thought of as storage for data and code, GitHub repositories can also be used to publish a time-stamped preregistration of research plans and hypotheses.
-
-Conventional research practices typically rely on one or two people running and checking the data analyses, while most coauthors (and readers of the subsequent publication) see only the final results and a verbal description of the analytical steps.
-In the developmental stages, collaborators can directly see the code for the analysis, manipulate and explore the data themselves, and check for errors.
-Cynically, there is also more insurance against nefarious colleagues that may be tempted to distort results\textsuperscript{\protect\hyperlink{ref-18PTmKJkq}{47}}.
-Collaborators as well as pre-publication and post-publication reviewers are better positioned to discover questionable findings if they have full and transparent access to the project.
-
-This transparency can similarly be extended beyond coauthors to the entire scientific community.
-Publishing the data and reproducible workflows along with the manuscript allows any reader to review the analysis and reproduce the experiment\textsuperscript{\protect\hyperlink{ref-NOgBWVAr}{48}}.
-Supplying code for (novel) methods that are proposed or used also reduces barriers to knowledge and can greatly improve the ability of others to build on existing work, resulting in greater proliferation and accessibility for a broader audience.
-GitHub even provides a useful Discussions Forum (\url{https://docs.github.com/en/discussions}) that aids the direct communication with repository owners, as well as the GitHub Community (\url{https://github.community/}) forum for more general questions and sharing of expertise (\protect\hyperlink{tbl:roles}{Table 1}.
+Scientific publications often omit part of their intellectual and computational workflows, including the treatment of raw data and analytical steps (\emph{e.g.}, model assumption testing).
+Publishing data and reproducible workflows along with manuscripts can provide readers with all details about analytical steps and enable reproducing research experiments and results\textsuperscript{\protect\hyperlink{ref-NOgBWVAr}{47}}.
+In addition to storing data and code, GitHub repositories can provide a time-stamped (version controlled) preregistration of research plans and hypotheses.
+
+Conventional research practices typically separate tasks among collaborators (\emph{i.e.}, data entry, analysis, writing).
+It is common that coauthors discuss, but do not actively verify, edit, or execute research tasks that are not their main responsibility.
+GitHub can serve as a tool for open and tractable research development.
+Collaborators can directly interact with code and data, inspect for errors, and potentially identify scientific misconduct prior to manuscript submission (\emph{e.g.},\textsuperscript{\protect\hyperlink{ref-18PTmKJkq}{48}}).
+Collaborators and readers are better positioned to discover erroneous or questionable findings if they have complete and transparent access to projects.
+
+This transparency can be extended beyond coauthors to the entire scientific community and to the public.
+Supplying code for (novel) methods that are proposed or used reduces barriers to knowledge, improving the ability of others to build on existing work.
+This results in greater proliferation and accessibility for a broader audience.
+Projects can make use of GitHub Discussions (\url{https://docs.github.com/en/discussions}) to communicate among repository members (collaborators) and to engage with other scientists and the general public.
+Moreover, researches can also use the GitHub Community (\url{https://github.community/}) forum to share expertise or request help from other researchers in ecology and evolution on their analyses and ideas (\protect\hyperlink{tbl:roles}{Table 1}.
 
@@
 
-The development of research code continues, and so does the need to consider project continuity, especially in EEB where graduate students, research assistants, and postdoctoral fellows often hold relatively short-term positions\textsuperscript{\protect\hyperlink{ref-D4C4k4ak}{49}}.
-Often with these types of short-term research projects, once the contract expires, the research code upkeep tends to fall off as the researchers move on to new projects.
-Additionally, if the code is kept on only the researcher's personal devices, it becomes increasingly difficult to access the code for future uses.
-As projects or contracts end, there should be a handover period of this code in order for the next cohort of researchers to reuse what was already developed\textsuperscript{\protect\hyperlink{ref-4ny1onB0}{8},\protect\hyperlink{ref-D4C4k4ak}{49}}.
-
-GitHub facilitates project continuity among research code by providing tools that make this handover period easier.
-As we have already mentioned, using Git for code in Ecology and Evolution can allow for a ``paper trail'' of sorts to be created for the code, thus allowing for future users of the code access to the entire history of the project\textsuperscript{\protect\hyperlink{ref-3DKwn1sY}{12}}.
-Additionally, GitHub allows for repositories and organizations to have designated Code Owners\textsuperscript{\protect\hyperlink{ref-s91uGRZ2}{50}}; these code owners can change through time allowing for the transition of code from one cohort of researchers to the next\textsuperscript{\protect\hyperlink{ref-iIEKCTLU}{39}}.
-There are also multiple means by which to archive code dependency information with GitHub.
-Dependencies can be described in README files, added to environment.yml and/or an environment.txt file, or stored in a repository using tools such as renv (\url{https://rstudio.github.io/renv/articles/renv.html}).
-This ensures that as packages continue to develop with new syntax, code will still run as it did when it was developed.
-
-Within EEB projects, tasks are often divided among contributors taking various roles (see CRediT taxonomy, \url{https://casrai.org/credit/}).
-The creation of project repositories is commonly the purview of those involved in the code, formal analysis, and/or visualization components of the project through their roles as code writers.
-However, the structural components of a typical GitHub repository and the derived EEB-specific templates can provide functional ways for other collaborators not contributing to code to be engaged in aspects of repository design in a way that improves institutional memory and facilitates project continuity.
-These other collaborators can offer many contributions to repository design and development, and their active involvement can both aid authors ability to act as guarantors of the project, and the clarity and reproducibility of the project for future users.
-In (Figure \ref{fig:scatterblob}), we highlight several elements of good repository structure, and the various ways that contributors may interact with them.
+Projects in ecology and evolution often involve graduate students, research assistants, and post-doctoral fellows, who hold limited-term positions\textsuperscript{\protect\hyperlink{ref-D4C4k4ak}{49}}.
+Without clear plans on project continuity, the research code and data management upkeep tends to fall off as researchers move on to new projects or to other institutions.
+Additionally, code and data can be difficult to access when kept only on the personal devices of researchers\textsuperscript{\protect\hyperlink{ref-19kmNxiHc}{50}}.
+
+GitHub can facilitate project continuity among research code by making code handover easier\textsuperscript{\protect\hyperlink{ref-4ny1onB0}{8},see \protect\hyperlink{ref-D4C4k4ak}{49}}.
+Through version control, the history of code and data from projects in ecology and evolution can be tracked accessible to future laboratory members and collaborators\textsuperscript{\protect\hyperlink{ref-3DKwn1sY}{12}}.
+Repositories and organizations can have designated data and code owners (or more appropriate, stewards; see\textsuperscript{\protect\hyperlink{ref-iIEKCTLU}{39}},\textsuperscript{\protect\hyperlink{ref-s91uGRZ2}{51}}), who can also can change through time allowing for the transition of code from one cohort of researchers to the next.
+Other project collaborators can offer many contributions to repository design and development, and their active involvement can both aid authors ability to act as guarantors of the project, and the clarity and reproducibility of the project for future users.
+In (Figure \ref{fig:github-diagram}), we highlight several elements of good repository structure, and the various ways that contributors may interact with them.
+
+GitHub also allows users to describe and store information about software and code dependencies, ensuring that code can run using the same version of software as when it was initially developed.
+This can be achieved through the access of GitHub repositories containing the necessary releases of such software, or through the usage of actions with specific software versions in its automation tool, GitHub Actions.
 
@@
 
-GitHub Organizations offer a shared virtual space that allows a team to work in different repositories, while remaining tied together under a larger figurehead, such as a laboratory, a department, an organization, or a large project involving several teams.
+GitHub Organizations are shared virtual spaces that allow teams to work in different repositories, while remaining tied together under a larger group, such as a laboratory, department, or project involving several teams.
 Organizations are well-suited to ensure larger projects with many steps or moving parts are constrained to one virtual space, where outputs and sub-projects can be easily accessed and located without relying on any one individual.
-Because the repositories are grouped in one virtual space, members can reference and contribute to each other's work without necessarily being part of the same repository, broadening the accessibility and longevity of code and writing contributions.
-
-Contributors can be assembled into teams within an organization, which allows administrators to assign roles and tasks to groups of people.
-Whereas access to repositories is usually assigned to individual contributors, Organizations facilitate the management of access permissions by allowing each team to be granted access to certain repositories, and not to others.
-This ensures that more sensitive repositories remain as restricted as needed, while repositories with greater general interest can be easily accessible to many members at once.
+Because the repositories are grouped, members can reference and contribute to each other's work without necessarily being part of the same repository, broadening the accessibility and longevity of code and writing contributions.
+
+Contributors can be assembled into teams within an organization, which allows administrators to assign roles, tasks, and repository modification permissions to organization members.
+Whereas access to repositories is usually assigned to individual contributors, Organizations facilitate the management of access permissions by allowing teams to be granted access to specific repositories.
+This ensures repositories with sensitive information remain as restricted as needed, while repositories with general stay easily accessible to selected member groups.
+The organization structure also allows for easy issue tracking and discussions related to research content and progress.
 
@@
 In this way, teams can have full ownership of repositories within an organization, while ensuring that these materials stay accessible to the laboratory after people have moved on or lost their copies of project data.
-This application extends to research centres, which may include several distinct projects that remain linked under a given institution, such as the German Centre for Integrative Biodiversity Research (iDiv, \url{https://github.com/idiv-biodiversity}).
-Of course, the utility of this tool goes beyond laboratories - they are useful to structure the organization, presentation, and outcomes of working groups such as the hackathon which inspired this paper (SORTEE-Github-Hackathon, \url{https://github.com/SORTEE-Github-Hackathon}) by keeping track of all materials as ideas develop and take shape in one virtual space.
-Organizations are also convenient for hosting a set of related learning materials such as a set of lectures or workshops, such as the Québec Centre for Biodiversity Science R Workshop Series (QCBSRworkshops, \url{https://github.com/QCBSRworkshops}) or the University of Edinburgh's Coding Club (Coding Club, \url{https://github.com/ourcodingclub}), which may be updated by an ever-evolving group of contributors over time.
-
-Using GitHub organizations as a research group or even for a handful of individuals working on a group of projects can be incredibly useful for all involved.
-GitHub organizations are relatively easy to set up, and especially easy to manage as membership to the organization changes through time.
-Not only is it a useful way to store repositories of lab-related research products, but it is also incredibly helpful for storing ``living documents'' that may be edited frequently, and may be linked to a lab website (that could also be generated via a repository that lives within the organization).
-The use of the ``Teams'' feature can allow certain groups to have varying levels of access to repositories in the organization with a select group having push access to some repositories but not others.
-This can manifest in a group working on some common dataset(s) to have push access to the handful of repositories used for processing sequence data, while another group of students/researchers may have push access to an entirely different set of repositories.
-The organization structure also allows for easy tracking of issues, projects, and discussions related to the research group, and provides group leads an easy birds-eye view of the progress going on across multiple projects.
+This application extends to research centres, which may include several distinct projects that remain linked to institutions, such as the German Centre for Integrative Biodiversity Research (iDiv, \url{https://github.com/idiv-biodiversity}).
+The team organizing the hackathon which inspired this paper used a GitHub Organization (SORTEE-Github-Hackathon, \url{https://github.com/SORTEE-Github-Hackathon}) to keeping track of all materials as ideas developed and took shape in one virtual space.
+Organizations are also convenient for hosting learning materials, including lectures or workshops, such as the Québec Centre for Biodiversity Science R Workshop Series (QCBSRworkshops, \url{https://github.com/QCBSRworkshops}) or the University of Edinburgh's Coding Club (Coding Club, \url{https://github.com/ourcodingclub}), which may be updated by an ever-evolving group of contributors over time.
 
@@
 
-There have been many calls for researchers outside of the software development community to join the 73 million GitHub users for their collaborative research\textsuperscript{\protect\hyperlink{ref-10ghgV3S8}{3},\protect\hyperlink{ref-1Du6fzB8g}{38},\protect\hyperlink{ref-UsTxAq4f}{51}}.
+There have been many calls for researchers outside of the software development community to join the 73 million GitHub users for their collaborative research\textsuperscript{\protect\hyperlink{ref-10ghgV3S8}{3},\protect\hyperlink{ref-1Du6fzB8g}{38},\protect\hyperlink{ref-UsTxAq4f}{52}}.
 This call comes in light of both the continual shift toward open-science and increasing computational and data requirements in EEB.
@@
 The default public nature of GitHub usage can add additional pressure to students and scientists learning to use the platform.
-We also note that large file storage is discouraged (and limited) on GitHub but add-ons do exist (e.g.~\url{https://git-lfs.github.com/}) that permit data storage, and increasing integration between platforms (e.g.\textsuperscript{\protect\hyperlink{ref-lx49NGto}{52}}) allows data to be stored away from GitHub and linked dynamically.
+We also note that large file storage is discouraged (and limited) on GitHub but add-ons do exist (e.g.~\url{https://git-lfs.github.com/}) that permit data storage, and increasing integration between platforms (e.g.\textsuperscript{\protect\hyperlink{ref-lx49NGto}{53}}) allows data to be stored away from GitHub and linked dynamically.
 We suspect a major additional barrier to EEB researchers is a distinct lack of GitHub help documents for non-English researchers in ecology and evolution, meaning that EEB researchers potentially miss the opportunity to fully understand the importance of version control, reproducibility, and other benefits of GitHub.
@@
 \\
-2. \textbf{Consider taking free courses.} such as those from Software Carpentry\textsuperscript{\protect\hyperlink{ref-pjy75gHr}{53}} and sharing these courses with your lab members or colleagues. \\
+2. \textbf{Consider taking free courses.} such as those from Software Carpentry\textsuperscript{\protect\hyperlink{ref-pjy75gHr}{54}} and sharing these courses with your lab members or colleagues. \\
 3.
@@
 6.
-\textbf{The Jenny Bryan universe of GitHub material.} provides a thorough and accessible introduction for a multitude of research-related uses for GitHub, and includes a book\textsuperscript{\protect\hyperlink{ref-ZvrOcg9w}{54}}, statistics course\textsuperscript{\protect\hyperlink{ref-6CMMeSeD}{55}} and academic article\textsuperscript{\protect\hyperlink{ref-RVetqmsg}{7}}.
+\textbf{The Jenny Bryan universe of GitHub material.} provides a thorough and accessible introduction for a multitude of research-related uses for GitHub, and includes a book\textsuperscript{\protect\hyperlink{ref-ZvrOcg9w}{55}}, statistics course\textsuperscript{\protect\hyperlink{ref-6CMMeSeD}{56}} and academic article\textsuperscript{\protect\hyperlink{ref-RVetqmsg}{7}}.
 \\
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-NOgBWVAr}{}}%
+\CSLLeftMargin{47. }
+\CSLRightInline{Culina, A., van den Berg, I., Evans, S.
+\& Sánchez-Tójar, A.
+\href{https://doi.org/10.1371/journal.pbio.3000763}{Low availability of code in ecology: A~call for urgent action}.
+\emph{PLoS Biol} \textbf{18}, e3000763 (2020).}
+
 \leavevmode\vadjust pre{\hypertarget{ref-18PTmKJkq}{}}%
-\CSLLeftMargin{47. }
+\CSLLeftMargin{48. }
 \CSLRightInline{January 18, P.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-NOgBWVAr}{}}%
-\CSLLeftMargin{48. }
-\CSLRightInline{Culina, A., van den Berg, I., Evans, S.
-\& Sánchez-Tójar, A.
-\href{https://doi.org/10.1371/journal.pbio.3000763}{Low availability of code in ecology: A~call for urgent action}.
-\emph{PLoS Biol} \textbf{18}, e3000763 (2020).}
-
 \leavevmode\vadjust pre{\hypertarget{ref-D4C4k4ak}{}}%
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-19kmNxiHc}{}}%
+\CSLLeftMargin{50. }
+\CSLRightInline{Vines, Timothy~H.
+\emph{et al.} \href{https://doi.org/10.1016/j.cub.2013.11.014}{The Availability of Research Data Declines Rapidly with Article Age}.
+\emph{Current Biology} \textbf{24}, 94--97 (2014).}
+
 \leavevmode\vadjust pre{\hypertarget{ref-s91uGRZ2}{}}%
-\CSLLeftMargin{50. }
+\CSLLeftMargin{51. }
 \CSLRightInline{About code owners.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-UsTxAq4f}{}}%
-\CSLLeftMargin{51. }
+\CSLLeftMargin{52. }
 \CSLRightInline{Anbaroğlu, B. \href{https://doi.org/10.1111/tgis.12810}{A collaborative GIS programming course using GitHub Classroom}. \emph{Transactions in GIS} \textbf{25}, 3132--3158 (2021).}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-lx49NGto}{}}%
-\CSLLeftMargin{52. }
+\CSLLeftMargin{53. }
 \CSLRightInline{Connect GitHub to a Project - OSF Support. \url{https://help.osf.io/article/211-connect-github-to-a-project}.}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-pjy75gHr}{}}%
-\CSLLeftMargin{53. }
+\CSLLeftMargin{54. }
 \CSLRightInline{Madicken Munk \emph{et al.} swcarpentry/git-novice: Software Carpentry: Version Control with Git, June 2019.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-ZvrOcg9w}{}}%
-\CSLLeftMargin{54. }
+\CSLLeftMargin{55. }
 \CSLRightInline{Hester, J. B., the STAT 545 TAs, Jim. \emph{\href{https://happygitwithr.com/}{Let's Git started \textbar{} Happy Git and GitHub for the useR}}.}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-6CMMeSeD}{}}%
-\CSLLeftMargin{55. }
+\CSLLeftMargin{56. }
 \CSLRightInline{Bryan, J. \& TAs, T. S. 545. \emph{\href{https://stat545.com/}{STAT 545}}.}

### 2022-06-28 manuscript.tex
Merge pull request #246 from SORTEE-Github-Hackathon/RCO-discussion-conclusion [ci skip]
This build is based on
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/cc849099b23d210f6928264fd6a353fdcc54862d.

This commit was created by the following CI build and job:
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/cc849099b23d210f6928264fd6a353fdcc54862d/checks
https://github.com/SORTEE-Github-Hackathon/manuscript/actions/runs/2578285311

@@
 This manuscript
-(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/773da7b1a68108cf2ee8aa5b261b6f4ab75fb2ab/}{permalink})
+(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/cc849099b23d210f6928264fd6a353fdcc54862d/}{permalink})
 was automatically generated
-from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/773da7b1a68108cf2ee8aa5b261b6f4ab75fb2ab}{SORTEE-Github-Hackathon/manuscript@773da7b}
+from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/cc849099b23d210f6928264fd6a353fdcc54862d}{SORTEE-Github-Hackathon/manuscript@cc84909}
 on June 28, 2022.
@@
 This call comes in light of both the continual shift toward open-science and increasing computational and data requirements in EEB.
-Until now, resources and practical guidance specifically focused on using GitHub within the EEB community have been dispersed in blog posts and video tutorials (\protect\hyperlink{tips}{Box 2} Box\textsuperscript{\protect\hyperlink{ref-box:tips}{\textbf{box:tips?}}}).
-We felt these resources have been extremely useful for us to learn to use GitHub in our own work, and that a collation of the main ideas into one medium, while adding on our personal perspectives, would be of use to the EEB community.
+Until now, resources and practical guidance on using GitHub within the EEB community have been dispersed in blog posts and video tutorials (\protect\hyperlink{tips}{Box 2}).
+These resources have been extremely useful for learning to use GitHub in our own work.
+We also feel that a collation of the main uses of GitHub in EEB into one medium, while adding on our personal perspectives, will be useful to the EEB community.
 
@@
 Many of the examples are specifically meant for first-time GitHub users and can likely be adopted with just a little practice (storing data, creating virtual notebooks, making code citable).
-For example, storing code and data and making it citable generally just involve creating a repository on GitHub, pushing code to the repository, and then going through the necessary steps (e.g., connecting a GitHub repository with Zenodo; see below) for creating a DOI for the repository.
-These actions are often covered in any introductory tutorial on GitHub and take little effort to implement.
-On the other hand, some other examples we described here, including material development, web hosting, and delivery, may require a greater time commitment, but have the potential to make EEB research more open, accessible, and collaborative than ever before.
-Managing full research projects or research labs on GitHub will require careful thought as to how to delegate tasks such as reviewing pull requests or creating issues, as well as thought as to how modular to make the research project or research lab (i.e., which repository will be used for what, and how many repositories are needed).
-For example, collaboratively writing a paper using GitHub, as we have done here, will involve a learning curve for co-authors less familiar with the intricacies of GitHub, and also require overhead to set up the repository using GitHub actions.
+For example, storing code and data and making it citable involve creating a repository on GitHub, pushing code to the repository, and then going through the necessary steps (\emph{e.g.}, connecting a GitHub repository with Zenodo; see below) for creating a DOI.
+These actions are often covered in GitHub tutorials and take little effort to implement.
+On the other hand, some examples we described here, including course material development, web hosting, and delivery, may require a greater time commitment, but have the potential to make EEB research more open, accessible, and collaborative than ever before.
+Managing full research projects or research labs on GitHub will require careful thought as to how to delegate tasks such as reviewing pull requests or creating issues.
+For example, collaboratively writing a paper using GitHub, as we have done here, may involve a learning curve for co-authors less familiar with the intricacies of GitHub, and requires overhead to set up the repository using GitHub actions.
 Despite the many potential applications of GitHub to EEB research, we acknowledge that there will still be many times when researchers might look to other platforms for research collaboration.
@@
 
-Though we see GitHub as a useful tool for collaboration in EEB, we describe two use cases where, to our knowledge, GitHub's features still fall short of the type of highly collaborative work emblematic of EEB research.
-First, real-time collaborative editing (e.g., as on a shared Google Doc or a Word document stored on Dropbox) is not possible on GitHub.
-There are websites outside of the GitHub ecosystem that are built on top of the GitHub architecture that allow real-time collaborative editing (e.g., hackMD (\url{https://hackmd.io/}) or replit (\url{https://replit.com/})).
+Though we see GitHub as a useful tool for collaboration in EEB, we describe two use cases where, to our knowledge, GitHub's features still fall short of the highly collaborative work emblematic of EEB research.
+First, real-time collaborative editing (\emph{e.g.}, as on a shared Google Doc or a Word document stored on Dropbox) is not possible on GitHub.
+There are websites outside of the GitHub ecosystem, built on top of the GitHub architecture, that allow real-time collaborative editing (\emph{e.g.}, hackMD (\url{https://hackmd.io/})).
 We used HackMD at two key points in writing our manuscript when real-time co-writing was essential: when taking meeting notes and writing the outline of our paper.
@@
 Though creating tables and figures on GitHub using markdown or other scripting languages is possible, we found that it was not practical at the early brainstorming stages.
-We needed to rapidly iterate on figure and table design, share feedback through comments, and merge/reorder ideas when necessary.
-For these reasons, we used Google Slides for working on figures and Google Sheets for working on tables.
-As our figures and tables moved towards more finalized forms, some co-authors chose to create the tables and figures using R and Markdown which could then be tracked using the same version control system as the rest of manuscript.
+We used Google Slides for working on figures and Google Sheets for working on tables.
+As our figures and tables moved towards finalized forms, some co-authors chose to create the tables and figures using R and Markdown which were then tracked using the same version control system as the rest of manuscript.
 
@@
 When GitHub is taught within an EEB context, it is usually accompanying coursework in topics such as statistical programming, and some students may find it overwhelming to juggle learning git alongside scripting languages, statistical theory, and file system navigation, especially when many may also be new to using command-line interfaces in general.
-Instructors likewise may confuse the expected digital literacy of younger students with computational fluency, even when modern technology increasingly abstracts many relevant concepts through search optimization and preponderant IDEs (Integrated Development Environments), or `point-and-click' user interfaces.
+Instructors likewise may confuse the expected digital literacy of students with computational fluency, even when modern technology increasingly abstracts concepts through search optimization and preponderant IDEs (Integrated Development Environments), or `point-and-click' user interfaces.
 
@@
 EEB researchers may take the view that GitHub is a platform that only needs to be used by individuals writing code, and may silo those aspects of projects to a single individual.
-Those assumptions may obscure the utility of GitHub for tasks other than traditional data analysis and code development, or how GitHub can facilitate the integration of code with non-coding aspects of projects through the practice of repository design.
-However, we emphasize that there are opportunities for collaboration using GitHub by researchers of all skill levels or time constraints (Table \ref{tbl:roles}); for example, project stakeholders can provide a list of use-cases or highlight important conceptual components of a project using the issues or discussions functionality of GitHub.
-
-A third barrier may come from general reluctance to share data and code publicly, or technical and logistical issues.
-The default public nature of GitHub usage can add additional pressure to students and scientists learning to use the platform.
-We also note that large file storage is discouraged (and limited) on GitHub but add-ons do exist (e.g.~\url{https://git-lfs.github.com/}) that permit data storage, and increasing integration between platforms (e.g.\textsuperscript{\protect\hyperlink{ref-lx49NGto}{53}}) allows data to be stored away from GitHub and linked dynamically.
+Those assumptions may obscure the utility of GitHub for tasks other than traditional data analysis and code development.
+However, we emphasize that there are opportunities for collaboration using GitHub by researchers of all skill levels or time constraints (Table \ref{tbl:roles}); for example, project stakeholders can provide a list of use-cases or highlight important conceptual components of a project using GitHub's issues or discussions features.
+
+A third barrier may come from general reluctance to share data and code publicly, or technical and logistical issues\textsuperscript{\protect\hyperlink{ref-pq2Tv1BC}{53}}.
+GitHub is, by default, a public and open platform.
+This openness may add additional pressure to students and scientists learning to use the platform.
+We also note that large file storage is discouraged (and limited) on GitHub but add-ons do exist (e.g.~\url{https://git-lfs.github.com/}) that permit data storage, and increasing integration between platforms (e.g.\textsuperscript{\protect\hyperlink{ref-lx49NGto}{54}}) allows data to be stored away from GitHub and linked dynamically.
 We suspect a major additional barrier to EEB researchers is a distinct lack of GitHub help documents for non-English researchers in ecology and evolution, meaning that EEB researchers potentially miss the opportunity to fully understand the importance of version control, reproducibility, and other benefits of GitHub.
@@
 \\
-2. \textbf{Consider taking free courses.} such as those from Software Carpentry\textsuperscript{\protect\hyperlink{ref-pjy75gHr}{54}} and sharing these courses with your lab members or colleagues. \\
+2. \textbf{Consider taking free courses.} such as those from Software Carpentry\textsuperscript{\protect\hyperlink{ref-pjy75gHr}{55}} and sharing these courses with your lab members or colleagues. \\
 3.
@@
 6.
-\textbf{The Jenny Bryan universe of GitHub material.} provides a thorough and accessible introduction for a multitude of research-related uses for GitHub, and includes a book\textsuperscript{\protect\hyperlink{ref-ZvrOcg9w}{55}}, statistics course\textsuperscript{\protect\hyperlink{ref-6CMMeSeD}{56}} and academic article\textsuperscript{\protect\hyperlink{ref-RVetqmsg}{7}}.
+\textbf{The Jenny Bryan universe of GitHub material.} provides a thorough and accessible introduction for a multitude of research-related uses for GitHub, and includes a book\textsuperscript{\protect\hyperlink{ref-ZvrOcg9w}{56}}, statistics course\textsuperscript{\protect\hyperlink{ref-6CMMeSeD}{57}} and academic article\textsuperscript{\protect\hyperlink{ref-RVetqmsg}{7}}.
 \\
@@
 
-We provide 12 practical ways that Ecologists and Evolutionary Biologists can incorporate GitHub into their research workflows, and include definitions (\protect\hyperlink{definitions}{Box 1}) and key user groups (Figure \ref{fig:github-diagram}) that can help researchers prioritize which GitHub skills to learn first.
-Some GitHub uses are highly collaborative (e.g., open science discussion and collaborative code editing) while others are focused on individual actions (e.g., storing code/data, building a website).
-Regardless of the degree of collaboration, GitHub use in ecology and evolution has the potential to make the field more open and transparent than ever before.
-Our paper provides the most comprehensive review of how EEB researchers can use GitHub to date, and we encourage EEB researchers at any career stage studying any topic to try GitHub as a platform for sharing and collaboration.
+We provide 12 practical ways that ecologists and evolutionary biologists can incorporate GitHub into their research workflows, and include definitions (\protect\hyperlink{definitions}{Box 1}) and user groups (Figure \ref{fig:github-diagram}) to help researchers prioritize which GitHub skills to learn first.
+Some GitHub uses are highly collaborative (\emph{e.g.}, open science discussion and collaborative code editing) while others are focused on individual actions (\emph{e.g.}, storing code/data, building a website).
+Regardless of the degree of collaboration, GitHub use in EEB has the potential to make the field more open and transparent than ever before.
+Our paper provides the most comprehensive review of how EEB researchers can use GitHub to date, and we encourage researchers at any career stage studying any topic to try GitHub as a platform for sharing and collaboration.
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-pq2Tv1BC}{}}%
+\CSLLeftMargin{53. }
+\CSLRightInline{\url{https://doi.org/gqd9cc} doi:\href{https://doi.org/10.31222/osf.io/gaj43}{10.31222/osf.io/gaj43}.}
+
 \leavevmode\vadjust pre{\hypertarget{ref-lx49NGto}{}}%
-\CSLLeftMargin{53. }
+\CSLLeftMargin{54. }
 \CSLRightInline{Connect GitHub to a Project - OSF Support. \url{https://help.osf.io/article/211-connect-github-to-a-project}.}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-pjy75gHr}{}}%
-\CSLLeftMargin{54. }
+\CSLLeftMargin{55. }
 \CSLRightInline{Madicken Munk \emph{et al.} swcarpentry/git-novice: Software Carpentry: Version Control with Git, June 2019.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-ZvrOcg9w}{}}%
-\CSLLeftMargin{55. }
+\CSLLeftMargin{56. }
 \CSLRightInline{Hester, J. B., the STAT 545 TAs, Jim. \emph{\href{https://happygitwithr.com/}{Let's Git started \textbar{} Happy Git and GitHub for the useR}}.}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-6CMMeSeD}{}}%
-\CSLLeftMargin{56. }
+\CSLLeftMargin{57. }
 \CSLRightInline{Bryan, J. \& TAs, T. S. 545. \emph{\href{https://stat545.com/}{STAT 545}}.}

### 2022-06-29 manuscript.tex
Merge pull request #247 from SORTEE-Github-Hackathon/RCO-minor-edits-throughout [ci skip]
This build is based on
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/01e005e2f013f1fa621623483512d548119fb15d.

This commit was created by the following CI build and job:
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/01e005e2f013f1fa621623483512d548119fb15d/checks
https://github.com/SORTEE-Github-Hackathon/manuscript/actions/runs/2580515548

@@
 This manuscript
-(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/cc849099b23d210f6928264fd6a353fdcc54862d/}{permalink})
+(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/01e005e2f013f1fa621623483512d548119fb15d/}{permalink})
 was automatically generated
-from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/cc849099b23d210f6928264fd6a353fdcc54862d}{SORTEE-Github-Hackathon/manuscript@cc84909}
-on June 28, 2022.
+from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/01e005e2f013f1fa621623483512d548119fb15d}{SORTEE-Github-Hackathon/manuscript@01e005e}
+on June 29, 2022.
 
@@
 
-The expansive GitHub user-community and numerous GitHub resources have boosted its popularity\textsuperscript{\protect\hyperlink{ref-RVetqmsg}{7},\protect\hyperlink{ref-kEX5dgzK}{9},\protect\hyperlink{ref-13jOlVcpp}{10}/,\protect\hyperlink{ref-u5aEVE4B}{11}}.
+The expansive GitHub user-community and numerous GitHub resources have boosted its popularity\textsuperscript{\protect\hyperlink{ref-RVetqmsg}{7},\protect\hyperlink{ref-kEX5dgzK}{9}--\protect\hyperlink{ref-u5aEVE4B}{11}}.
 Nevertheless, although multiple articles have encouraged researchers in EEB to adopt GitHub as part of their research process\textsuperscript{\protect\hyperlink{ref-10ghgV3S8}{3},\protect\hyperlink{ref-3DKwn1sY}{12}}, its use is still not widespread.
@@
 
-GitHub limits committed file sizes to 100 Mb (megabytes) (\textsuperscript{\protect\hyperlink{ref-1Co6ZZjF1}{17}}), which can make it challenging for centralizing research compedia containing larger file sizes.
-Users may still version large files using Git Large File Storage (LFS;\textsuperscript{\protect\hyperlink{ref-11GtZ7icJ}{18}}/) text pointers, but may have to rely on external file storage alternatives (such as local or cloud-hosting).
+GitHub limits committed file sizes to 100 Mb (megabytes\textsuperscript{\protect\hyperlink{ref-1Co6ZZjF1}{17}}), which can make it challenging for centralizing research compendia containing larger file sizes.
+Users may still version large files using Git Large File Storage (LFS\textsuperscript{\protect\hyperlink{ref-11GtZ7icJ}{18}}) text pointers, but may have to rely on external file storage alternatives (such as local or cloud-hosting).
 
@@
 Unlike emails and messages which can get lost as more new tasks arise, GitHub issues are intentionally closed by repository administrators hiding the issue from view (closed issues remain accessible but not immediately visible).
-Project management in GitHub can also be integrated with third-party applications, such as ZenHub (https://www.zenhub.com/) or Slack (https://slack.github.com/).
+Project management in GitHub can also be integrated with third-party applications, such as ZenHub (\url{https://www.zenhub.com}) or Slack (\url{https://slack.github.com}).
 ZenHub allows for the enhanced visualization and organization of repositories and their issues, while the GitHub for Slack integration allows notifications from GitHub events to be sent directly to users or group channels\textsuperscript{\protect\hyperlink{ref-1GRWGlDWy}{22}}.
@@
 Making presentations, syllabi and other course materials can be done through most major high-level programming languages such as R, with \texttt{RMarkdown}\textsuperscript{\protect\hyperlink{ref-QqMezOMg}{23}}, Python, with \texttt{python-ppt} (\url{https://python-pptx.readthedocs.io}), and Julia, with \texttt{Remark.jl} (\url{https://juliapackages.com/p/remark}), and be version-controlled and stored in GitHub.
-Once content is made, hosting a course website can be done through GitHub Pages\textsuperscript{\protect\hyperlink{ref-MDQfMwCW}{24}} (\emph{e.g.}, https://github.com/topics/course-website\textgreater).
+Once content is made, hosting a course website can be done through GitHub Pages\textsuperscript{\protect\hyperlink{ref-MDQfMwCW}{24}} (\emph{e.g.}, \url{https://github.com/topics/course-website}).
 This way, the course content can be available to enrolled students, as well as a global pool of learners and teachers interested in the course material.
@@
 DOIs are persistent and citable unique alpha-numeric identifiers assigned to digitally stored research materials.
-Because of this, scientists sharing code and data through GitHub are strongly encouraged to independently submit their research materials to long-term data archives (\emph{e.g.}, Zenodo, Figshare, Dryad, OSF\textsuperscript{\protect\hyperlink{ref-10ghgV3S8}{3},\protect\hyperlink{ref-kEX5dgzK}{9},\protect\hyperlink{ref-1Du6fzB8g}{38},\protect\hyperlink{ref-tbl:compare}{\textbf{tbl:compare?}}}.
+Because of this, scientists sharing code and data through GitHub are strongly encouraged to independently submit their research materials to long-term data archives (\emph{e.g.}, Zenodo, Figshare, Dryad, OSF\textsuperscript{\protect\hyperlink{ref-10ghgV3S8}{3},\protect\hyperlink{ref-kEX5dgzK}{9},\protect\hyperlink{ref-1Du6fzB8g}{38}}; \protect\hyperlink{tbl:compare}{Table 2}).
+(\protect\hyperlink{tbl:roles}{Table 1})
 Some of these options (Zenodo, Figshare and OSF) integrate with GitHub, allowing project, code, and data releases (\protect\hyperlink{definitions}{Box 1}) to be archived with versioned, citable DOIs.
@@
 
-An important aspect of making code and data citable and reusable is to add an appropriate licence to protect intellectual property.
-Code published without a licence is under exclusive copyright (by default), protecting it from copy, distribution, and modifications.
+An important aspect of making code and data citable and reusable is to add an appropriate license to protect intellectual property.
+Code published without a license is under exclusive copyright (by default), protecting it from copy, distribution, and modifications.
 One may grant specific rights to their code for reuse by adding licensing files and specifications within GitHub repositories\textsuperscript{\protect\hyperlink{ref-TOsASkn5}{40}}.
@@
 Relevant literature or issues can be made using the Discussions and Issues features.
-Moreover, real-time collaboration on text documents stored in GitHub repositories can be achieved with the help of other platforms (\emph{e.g.}, HackMD (\url{https://hackmd.io} for Markdown documents).
+Moreover, real-time collaboration on text documents stored in GitHub repositories can be achieved with the help of other platforms (\emph{e.g.}, HackMD (\url{https://hackmd.io}) for Markdown documents).
 
@@
 Every change made to the manuscript triggers its rendering, so that updates are readily displayed and made publicly available.
-Additional GitHub Actions can be integrated with Manubot, such as ones creating figures or generating tables (\emph{e.g.}, https://github.com/SORTEE-Github-Hackathon/manuscript/tree/main/.github/workflows).
+Additional GitHub Actions can be integrated with Manubot, such as ones creating figures or generating tables (\emph{e.g.}, \url{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/main/.github/workflows}).
 For more examples of manuscripts built via Manubot, see\textsuperscript{\protect\hyperlink{ref-YuJbg3zO}{44}}.
@@
 If the code associated with a manuscript is made available at the time of submission (\emph{e.g.}, as a link to a GitHub repository within the Data Availability Statement), peer reviewers may be able to offer more comprehensive suggestions on the code and written materials, potentially recognizing errors before publication.
-Certain journals or software development communities require submitted work or research code to be hosted on GitHub and their review processes make use of GitHub Issues {[}\emph{e.g.}, rOpenSci (\url{https://ropensci.org/software-review/}); Journal of Open Source Software (\url{https://joss.readthedocs.io/en/latest/submitting.html}){]}.
+Certain journals or software development communities require submitted work or research code to be hosted on GitHub and their review processes make use of GitHub Issues (\emph{e.g.}, rOpenSci (\url{https://ropensci.org/software-review/}), Journal of Open Source Software (\url{https://joss.readthedocs.io/en/latest/submitting.html})).
 rOpenSci's efforts have resulted in many well-used R packages for ecology research including \texttt{rfishbase}\textsuperscript{\protect\hyperlink{ref-Xsdcv6q}{45}} and \texttt{taxize}\textsuperscript{\protect\hyperlink{ref-FVBWKkZu}{46}}.
@@
 Projects can make use of GitHub Discussions (\url{https://docs.github.com/en/discussions}) to communicate among repository members (collaborators) and to engage with other scientists and the general public.
-Moreover, researches can also use the GitHub Community (\url{https://github.community/}) forum to share expertise or request help from other researchers in ecology and evolution on their analyses and ideas (\protect\hyperlink{tbl:roles}{Table 1}.
+Moreover, researches can also use the GitHub Community (\url{https://github.community/}) forum to share expertise or request help from other researchers in ecology and evolution on their analyses and ideas (\protect\hyperlink{tbl:roles}{Table 1}).
 
@@
 
-GitHub can facilitate project continuity among research code by making code handover easier\textsuperscript{\protect\hyperlink{ref-4ny1onB0}{8},see \protect\hyperlink{ref-D4C4k4ak}{49}}.
+GitHub can facilitate project continuity among research code by making code handover easier\textsuperscript{\protect\hyperlink{ref-4ny1onB0}{8},\protect\hyperlink{ref-D4C4k4ak}{49}}.
 Through version control, the history of code and data from projects in ecology and evolution can be tracked accessible to future laboratory members and collaborators\textsuperscript{\protect\hyperlink{ref-3DKwn1sY}{12}}.
@@
 This openness may add additional pressure to students and scientists learning to use the platform.
-We also note that large file storage is discouraged (and limited) on GitHub but add-ons do exist (e.g.~\url{https://git-lfs.github.com/}) that permit data storage, and increasing integration between platforms (e.g.\textsuperscript{\protect\hyperlink{ref-lx49NGto}{54}}) allows data to be stored away from GitHub and linked dynamically.
+We also note that large file storage is discouraged (and limited) on GitHub but add-ons do exist (\emph{e.g.}, \url{https://git-lfs.github.com/}) that permit data storage, and increasing integration between platforms (\emph{e.g.},\textsuperscript{\protect\hyperlink{ref-lx49NGto}{54}}) allows data to be stored away from GitHub and linked dynamically.
 We suspect a major additional barrier to EEB researchers is a distinct lack of GitHub help documents for non-English researchers in ecology and evolution, meaning that EEB researchers potentially miss the opportunity to fully understand the importance of version control, reproducibility, and other benefits of GitHub.
@@
 When projects get highly collaborative they may have to pay for additional GitHub support.
-The acquisition of GitHub by Microsoft has led to some concerns over the future of free plans and several biodiversity data managers have begun to switch to Open Source Git services (e.g.~Bitbucket and GitLab).
+The acquisition of GitHub by Microsoft has led to some concerns over the future of free plans and several biodiversity data managers have begun to switch to Open Source Git services (\emph{e.g.}, Bitbucket and GitLab).
 At this point however, there is little practical difference for EEB researchers between the paid and free GitHub plans.
@@
 There is a large community of GitHub users around the world who have likely faced analogous problems and may be able to provide quick solutions.
-Third, try to follow blogs (e.g., \url{https://github.blog}), Twitter accounts or YouTube channels that regularly post practical solutions about the most widely-used web platform for common GitHub issues.
+Third, try to follow blogs (\emph{e.g.}, \url{https://github.blog}), Twitter accounts or YouTube channels that regularly post practical solutions about the most widely-used web platform for common GitHub issues.
 \\
@@
 
-The source code and data for this manuscript are available at https://github.com/SORTEE-Github-Hackathon/manuscript.
+The source code and data for this manuscript are available at \url{https://github.com/SORTEE-Github-Hackathon/manuscript}.
 The source code will be archived in the ESS-DIVE data repository prior to publication.
@@
 \endhead
-Project manager & Set contributor permissions, share code of conduct & Project descritption, citation, DOIs & Assign tasks to collaborators & Discuss project directions and goals & Approve and incorporate edits to code and/or writing & & Share up-to-date reports, figures, or draft manuscript \\
+Project manager & Set contributor permissions, share code of conduct & Project description, citation, DOIs & Assign tasks to collaborators & Discuss project directions and goals & Approve and incorporate edits to code and/or writing & & Share up-to-date reports, figures, or draft manuscript \\
 Co-author & Edit Markdown text or add files & & Propose changes involving code (e.g.~analyses, figures) & Discuss proposed changes to manuscript & & & \\
@@
   >{\raggedright\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.1289}}@{}}
-\caption{a comparison of technologies\ldots{} \label{tbl:compare}}\tabularnewline
+\caption{a comparison of technologies commonly used for collaborating on research in Ecology and Evolutionary Biology.
+In the first column, we group platforms for collaboration into broad guilds.
+The second column lists the platform for collaboration.
+The remaining columns indicate whether the platform for collaboration \label{tbl:compare}}\tabularnewline
 \toprule

### 2022-07-05 manuscript.tex
Merge pull request #248 from SORTEE-Github-Hackathon/overall-changes-phpb [ci skip]
This build is based on
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/366e2cb6517a7428a3aacf57613b727b67c17a03.

This commit was created by the following CI build and job:
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/366e2cb6517a7428a3aacf57613b727b67c17a03/checks
https://github.com/SORTEE-Github-Hackathon/manuscript/actions/runs/2618108587

@@
 This manuscript
-(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/01e005e2f013f1fa621623483512d548119fb15d/}{permalink})
+(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/366e2cb6517a7428a3aacf57613b727b67c17a03/}{permalink})
 was automatically generated
-from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/01e005e2f013f1fa621623483512d548119fb15d}{SORTEE-Github-Hackathon/manuscript@01e005e}
-on June 29, 2022.
+from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/366e2cb6517a7428a3aacf57613b727b67c17a03}{SORTEE-Github-Hackathon/manuscript@366e2cb}
+on July 5, 2022.
 
@@
 
-There have been many calls for researchers outside of the software development community to join the 73 million GitHub users for their collaborative research\textsuperscript{\protect\hyperlink{ref-10ghgV3S8}{3},\protect\hyperlink{ref-1Du6fzB8g}{38},\protect\hyperlink{ref-UsTxAq4f}{52}}.
-This call comes in light of both the continual shift toward open-science and increasing computational and data requirements in EEB.
+There have been many calls for researchers outside of the software development community to adopt GitHub to improve their collaborative research\textsuperscript{\protect\hyperlink{ref-10ghgV3S8}{3},\protect\hyperlink{ref-1Du6fzB8g}{38},\protect\hyperlink{ref-UsTxAq4f}{52}}.
+This call comes in light of both the continuous shift towards open-science and the increasing computational and data requirements in EEB.
 Until now, resources and practical guidance on using GitHub within the EEB community have been dispersed in blog posts and video tutorials (\protect\hyperlink{tips}{Box 2}).
@@
 
-In this paper, we described 12 tractable ways that EEB researchers can leverage GitHub to enable more transparent and collaborative research (Figure \ref{fig:scatterblob}).
+In this paper, we described twelve ways that EEB researchers can leverage GitHub to enable more transparent and collaborative research (Figure \ref{fig:scatterblob}).
 Many of the examples are specifically meant for first-time GitHub users and can likely be adopted with just a little practice (storing data, creating virtual notebooks, making code citable).
 For example, storing code and data and making it citable involve creating a repository on GitHub, pushing code to the repository, and then going through the necessary steps (\emph{e.g.}, connecting a GitHub repository with Zenodo; see below) for creating a DOI.
-These actions are often covered in GitHub tutorials and take little effort to implement.
-On the other hand, some examples we described here, including course material development, web hosting, and delivery, may require a greater time commitment, but have the potential to make EEB research more open, accessible, and collaborative than ever before.
-Managing full research projects or research labs on GitHub will require careful thought as to how to delegate tasks such as reviewing pull requests or creating issues.
-For example, collaboratively writing a paper using GitHub, as we have done here, may involve a learning curve for co-authors less familiar with the intricacies of GitHub, and requires overhead to set up the repository using GitHub actions.
+These actions are often covered in GitHub tutorials and require little effort to implement.
+On the other hand, some examples we described here, including course material development, web hosting, and delivery, may require a greater time commitment, but have the potential to make EEB research more open, accessible, and collaborative.
+Managing full research projects or laboratories on GitHub require careful thought as to how to delegate tasks such as reviewing pull requests or creating issues.
+For example, collaboratively writing a paper using GitHub, as we have done here, may involve a learning curve for co-authors less familiar with the intricacies of GitHub, and requires overhead to set up the repository using GitHub Actions.
 Despite the many potential applications of GitHub to EEB research, we acknowledge that there will still be many times when researchers might look to other platforms for research collaboration.
@@
 
-Though we see GitHub as a useful tool for collaboration in EEB, we describe two use cases where, to our knowledge, GitHub's features still fall short of the highly collaborative work emblematic of EEB research.
-First, real-time collaborative editing (\emph{e.g.}, as on a shared Google Doc or a Word document stored on Dropbox) is not possible on GitHub.
-There are websites outside of the GitHub ecosystem, built on top of the GitHub architecture, that allow real-time collaborative editing (\emph{e.g.}, hackMD (\url{https://hackmd.io/})).
-We used HackMD at two key points in writing our manuscript when real-time co-writing was essential: when taking meeting notes and writing the outline of our paper.
-Second, we looked to other software when working on figures and tables.
-Though creating tables and figures on GitHub using markdown or other scripting languages is possible, we found that it was not practical at the early brainstorming stages.
-We used Google Slides for working on figures and Google Sheets for working on tables.
-As our figures and tables moved towards finalized forms, some co-authors chose to create the tables and figures using R and Markdown which were then tracked using the same version control system as the rest of manuscript.
+Despite its strong collaborative potential, we describe two use cases where GitHub's features fall short of highly collaborative work emblematic of EEB research.
+
+First, real-time collaborative editing of files is not possible in GitHub.
+Users seeking to real-time edit documents might still need to rely on alternative features (\emph{e.g.}, cloud-stored documents from Microsoft Word, Google Docs, hackMD (\url{https://hackmd.io/})).
+Second, certain operations that are dependent on other software might not be easily achievable in GitHub, such as manipulating figures or tables.
+Although creating tables and figures can be achieve through code, users may be limited to other software to collaboratively brainstorm figures and tables (e.g.~Google Slides, Google Sheets).
+Albeit, files containing documents, figures and tables may still be versioned in GitHub.
 
@@
 
-Though GitHub has been available as a platform for more than a decade, its uptake among EEB researchers, especially as a tool for collaboration, has been slow.
-Here we discuss four potential barriers to GitHub use in EEB.
-
-First, there may be a hesitation to use GitHub due to the somewhat steep learning curve to using the platform combined with limited instruction available through traditional university courses.
-When GitHub is taught within an EEB context, it is usually accompanying coursework in topics such as statistical programming, and some students may find it overwhelming to juggle learning git alongside scripting languages, statistical theory, and file system navigation, especially when many may also be new to using command-line interfaces in general.
-Instructors likewise may confuse the expected digital literacy of students with computational fluency, even when modern technology increasingly abstracts concepts through search optimization and preponderant IDEs (Integrated Development Environments), or `point-and-click' user interfaces.
+Although GitHub has been available as a platform for more than a decade, its uptake among EEB researchers, especially as a tool for collaboration, has been slow.
+Here, we discuss four potential barriers to GitHub use in EEB.
+
+First, there may be hesitation to independently adopting and learning a new tool.
+Institutional encouragement and instructional resources focused in researchers in ecology and evolution may be limited.
+When GitHub is taught within an EEB context, it is usually accompanying coursework in topics such as statistical programming.
+It can be challenging to learn Git alongside scripting languages, statistical theory, and file system navigation, especially when many may be inexperimented with programming.
+Instructors likewise may confuse the expected digital literacy of students with computational fluency, even when modern technology increasingly abstracts concepts through search optimization and preponderant integrated development environments (IDE), or `point-and-click' user interfaces.
 
@@
 \begin{minipage}[b]{\linewidth}\raggedright
-10 Tips for getting started in GitHub
+Ten tips for getting started in GitHub
 \end{minipage} \\
@@
 
-We provide 12 practical ways that ecologists and evolutionary biologists can incorporate GitHub into their research workflows, and include definitions (\protect\hyperlink{definitions}{Box 1}) and user groups (Figure \ref{fig:github-diagram}) to help researchers prioritize which GitHub skills to learn first.
-Some GitHub uses are highly collaborative (\emph{e.g.}, open science discussion and collaborative code editing) while others are focused on individual actions (\emph{e.g.}, storing code/data, building a website).
-Regardless of the degree of collaboration, GitHub use in EEB has the potential to make the field more open and transparent than ever before.
-Our paper provides the most comprehensive review of how EEB researchers can use GitHub to date, and we encourage researchers at any career stage studying any topic to try GitHub as a platform for sharing and collaboration.
+We provide twelve practical ways that ecologists and evolutionary biologists can adopt GitHub to improve their research workflow.
+We provide definitions (\protect\hyperlink{definitions}{Box 1}) and types of users (Figure \ref{fig:github-diagram}) to help researchers identify and prioritize the skills and tools to learn first.
+We highlight tools providing high collaborative potential (\emph{e.g.}, open science discussion, collaborative code editing) to more individual focused (\emph{e.g.}, storing code and data, building a website).
+We argue that the tools readily available in GitHub have the potential to make ecology and evolution more open, reproducible and transparent.
+With this comprehensive review of how EEB researchers can use GitHub, we encourage researchers at any career stage to adopt GitHub as a platform for sharing and collaboration.
 
@@
 
-We indicate author contributions using the \href{https://casrai.org/credit/}{CRediT Taxonomy}
+We indicate author contributions using the \href{https://casrai.org/credit/}{CRediT Taxonomy}.
+
+\begin{itemize}
+\tightlist
+\item
   Conceptualization: RCO, BPME, KH, EJH, LLSR, PHPB
+\item
   Investigation: RCO, BPME, KH, EJH, LLSR, ERS, MJG, VF, ADB, CBB, KMG, SSHS, AG, FH, HW, DGEG, PHPB
+\item
   Methodology: RCO, BPME, KH, EJH, LLSR, PHPB
+\item
   Project administration: RCO
-
+\item
   Software: RCO, BPME, KH, EJH, LLSR, ERS, MJG, VF, ADB, CBB, KMG, SSHS, AG, FH, HW, DGEG, PHPB
+\item
   Visualization: RCO, BPME, KH, EJH, LLSR, ERS, MJG, VF, ADB, CBB, KMG, SSHS, AG, FH, HW, DGEG, PHPB
+\item
   Writing -- original draft: RCO, BPME, KH, EJH, LLSR, ERS, MJG, VF, ADB, CBB, KMG, SSHS, AG, FH, HW, DGEG, PHPB
-Writing -- review \& editing: RCO, BPME, KH, EJH, LLSR, ERS, MJG, VF, ADB, CBB, KMG, SSHS, AG, FH, HW, DGEG, PHPB
+\item
+  Writing -- review and editing: RCO, BPME, KH, EJH, LLSR, ERS, MJG, VF, ADB, CBB, KMG, SSHS, AG, FH, HW, DGEG, PHPB
+\item
+  Resources: PHPB
+\end{itemize}
 
@@
 \includegraphics{images/github_diagram.png}
-\caption{An overview of git's core features.
+\caption{An overview of Git's core features.
 A) Multi-faceted components allow for code writing, small data storage, manuscript writing, and project management to all be done in one place.
@@
 \CSLLeftMargin{53. }
-\CSLRightInline{\url{https://doi.org/gqd9cc} doi:\href{https://doi.org/10.31222/osf.io/gaj43}{10.31222/osf.io/gaj43}.}
+\CSLRightInline{Gomes, D.
+G.
+E.
+\emph{et al.} Why don't we share data and code?
+Perceived barriers and benefits to public archiving practices.
+(2022) doi:\href{https://doi.org/10.31222/osf.io/gaj43}{10.31222/osf.io/gaj43}.}
 
@@
 \CSLLeftMargin{55. }
-\CSLRightInline{Madicken Munk \emph{et al.} swcarpentry/git-novice: Software Carpentry: Version Control with Git, June 2019.
-(2019) doi:\href{https://doi.org/10.5281/zenodo.3264950}{10.5281/zenodo.3264950}.}
+\CSLRightInline{Madicken Munk \emph{et al.} swcarpentry/git-novice: Software Carpentry: Version Control with Git, June 2019. at \url{https://doi.org/10.5281/zenodo.3264950} (2019).}
 

### 2022-07-05 manuscript.tex
Merge pull request #249 from SORTEE-Github-Hackathon/hypothesis_EJH [ci skip]
This build is based on
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/fa53fc1f6968dfcec7f638e637a738b8da99085a.

This commit was created by the following CI build and job:
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/fa53fc1f6968dfcec7f638e637a738b8da99085a/checks
https://github.com/SORTEE-Github-Hackathon/manuscript/actions/runs/2618260413

@@
 This manuscript
-(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/366e2cb6517a7428a3aacf57613b727b67c17a03/}{permalink})
+(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/fa53fc1f6968dfcec7f638e637a738b8da99085a/}{permalink})
 was automatically generated
-from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/366e2cb6517a7428a3aacf57613b727b67c17a03}{SORTEE-Github-Hackathon/manuscript@366e2cb}
+from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/fa53fc1f6968dfcec7f638e637a738b8da99085a}{SORTEE-Github-Hackathon/manuscript@fa53fc1}
 on July 5, 2022.
@@
 On the other hand, some examples we described here, including course material development, web hosting, and delivery, may require a greater time commitment, but have the potential to make EEB research more open, accessible, and collaborative.
-Managing full research projects or laboratories on GitHub require careful thought as to how to delegate tasks such as reviewing pull requests or creating issues.
+Managing full research projects or laboratories on GitHub requires careful thought as to how to delegate tasks such as reviewing pull requests or creating issues.
 For example, collaboratively writing a paper using GitHub, as we have done here, may involve a learning curve for co-authors less familiar with the intricacies of GitHub, and requires overhead to set up the repository using GitHub Actions.
@@
 Second, certain operations that are dependent on other software might not be easily achievable in GitHub, such as manipulating figures or tables.
-Although creating tables and figures can be achieve through code, users may be limited to other software to collaboratively brainstorm figures and tables (e.g.~Google Slides, Google Sheets).
+Although creating tables and figures can be achieved through code, users may be limited to other software to collaboratively brainstorm figures and tables (e.g.~Google Slides, Google Sheets).
 Albeit, files containing documents, figures and tables may still be versioned in GitHub.
@@
 First, there may be hesitation to independently adopting and learning a new tool.
-Institutional encouragement and instructional resources focused in researchers in ecology and evolution may be limited.
+Institutional encouragement and instructional resources focused on researchers in ecology and evolution may be limited.
 When GitHub is taught within an EEB context, it is usually accompanying coursework in topics such as statistical programming.
-It can be challenging to learn Git alongside scripting languages, statistical theory, and file system navigation, especially when many may be inexperimented with programming.
+It can be challenging to learn Git alongside scripting languages, statistical theory, and file system navigation, especially when many may be inexperienced with programming.
 Instructors likewise may confuse the expected digital literacy of students with computational fluency, even when modern technology increasingly abstracts concepts through search optimization and preponderant integrated development environments (IDE), or `point-and-click' user interfaces.

### 2022-07-11 editorial-communication/cover-letter-submission.Rmd
updates before preprinting

@@
 Also, we believe our manuscript complements a recently published manuscript in *Nature Ecology and Evolution*. 
-In the manuscript, Gallagher et al.
-(2020) outline how the ongoing adoption of Open Science practices is transforming research in ecology and evolutionary biology.
+In their manuscript, Gallagher et al. (2020) outline how the ongoing adoption of Open Science practices is transforming research in ecology and evolutionary biology.
 A key component of Open Science is the ability to collaboratively contribute to and share code and data--platforms like GitHub provide an free and accessible platform to do just that.
 
-The enclosed manuscript is available as a preprint on the NAME OF SERVER AND CITATION, but is not published or in review elsewhere.
+The enclosed manuscript is available as a preprint on the MetaArXiv server (ADD CITATION), but is not published or in review elsewhere.
 All authors have contributed and reviewed the current version of the manuscript and agreed to its submission to *Nature Ecology & Evolution*.

### 2022-07-12 manuscript.tex
Merge pull request #251 from SORTEE-Github-Hackathon/RCO-final-before-preprint [ci skip]
This build is based on
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/63f18c11f35a239c2085d7d7dfdb935614f182cf.

This commit was created by the following CI build and job:
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/63f18c11f35a239c2085d7d7dfdb935614f182cf/checks
https://github.com/SORTEE-Github-Hackathon/manuscript/actions/runs/2654414681

@@
 This manuscript
-(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/fa53fc1f6968dfcec7f638e637a738b8da99085a/}{permalink})
+(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/63f18c11f35a239c2085d7d7dfdb935614f182cf/}{permalink})
 was automatically generated
-from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/fa53fc1f6968dfcec7f638e637a738b8da99085a}{SORTEE-Github-Hackathon/manuscript@fa53fc1}
-on July 5, 2022.
+from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/63f18c11f35a239c2085d7d7dfdb935614f182cf}{SORTEE-Github-Hackathon/manuscript@63f18c1}
+on July 12, 2022.
 
@@
 With the growing role of data science in research, the use of efficient methods to share, reproduce, and collaborate on code has become fundamental.
-GitHub is an online, cloud-based service that can help researchers to track, organize, discuss, share, and collaborate on software and code.
+GitHub is an online, cloud-based service that can help researchers track, organize, discuss, share, and collaborate on software and code.
 Despite these benefits, the use of GitHub by EEB researchers is not widespread due to the lack of domain-specific information and guidelines.
@@
 Maintaining code for scientific collaboration requires an efficient and well-documented work-flow\textsuperscript{\protect\hyperlink{ref-1Kqna6l2}{2}}.
-To facilitate this process, scientists have been increasingly adopting tools from information and systems technology, such as cloud-based services for documentation and version control (\emph{e.g.}, from the Google Suite, the Microsoft Suite, and GitHub,\textsuperscript{\protect\hyperlink{ref-10ghgV3S8}{3}}).
+To facilitate this process, scientists have been increasingly adopting tools from information and systems technology, such as cloud-based services for documentation and version control (\emph{e.g.}, from the Google Suite, the Microsoft Suite, and GitHub\textsuperscript{\protect\hyperlink{ref-10ghgV3S8}{3}}).
 However, most researchers lack exposure to adequate code practices and thus dedicate valuable time and effort to self-teaching research-facilitating tools.
@@
 With over 73 million registered users as of 2022, GitHub is the most widely-used web platform for collaborating on computer code\textsuperscript{\protect\hyperlink{ref-nwCtHDCn}{6}}.
-GitHub provides a simplified but powerful web interface that allows users to participate in projects, contribute code, report and discuss code bugs, discover existing code and data, and publish new code.
-Through version control, users have a detailed, chronological record of the files and directories stored in their repositories (see \protect\hyperlink{definitions}{Box 1};\textsuperscript{\protect\hyperlink{ref-RVetqmsg}{7}}).
-This workflow provides a strong and clear advantage over sending files back-and-forth (\emph{e.g.} via email), a process that can become challenging and time-consuming in more long-term and collaborative projects\textsuperscript{\protect\hyperlink{ref-4ny1onB0}{8}}.
+GitHub provides a simple but powerful web interface that allows users to participate in projects, contribute code, report and discuss code bugs, discover existing code and data, and publish new code.
+Through version control, users have a detailed, chronological record of the files and directories stored in their repositories\textsuperscript{\protect\hyperlink{ref-RVetqmsg}{7}} (see \protect\hyperlink{definitions}{Box 1}).
+This workflow provides a strong and clear advantage over sending files back-and-forth (\emph{e.g.} via email), a process that can become challenging and time-consuming in long-term and collaborative projects\textsuperscript{\protect\hyperlink{ref-4ny1onB0}{8}}.
 Through its combination of version control and and collaborative features, GitHub facilitates open source code alongside collaborative development\textsuperscript{\protect\hyperlink{ref-kEX5dgzK}{9}}.
@@
 Widespread adoption of GitHub for collaborating on research tasks can ultimately enable EEB researchers to spend less time on creating novel processes for collaboration and more time on their research\textsuperscript{\protect\hyperlink{ref-ydrk01SR}{14}}.
-More importantly, increasing the availability of data and code management standards -- of which GitHub is one increasingly important component -- makes research more reproducible and collaborative\textsuperscript{\protect\hyperlink{ref-13QX8XU3J}{15}}.
+More importantly, increasing the availability of data and code management standards -- of which GitHub is one increasingly important component -- makes research more reproducible and collaborative\textsuperscript{\protect\hyperlink{ref-13QX8XU3J}{15},\protect\hyperlink{ref-pq2Tv1BC}{16}}.
 
@@
 We convened a group of around thirty researchers in EEB with varying levels of familiarity with using GitHub as part of their research projects to showcase and discuss how existing features can contribute to documentation and collaboration in EEB research.
-During the hackathon, we identified the need for a formal discussion on how EEB researchers can benefit from GitHub and its features to make research more collaborative and transparent.
+During the hackathon, we identified the need for a formal discussion on how EEB researchers can benefit from GitHub and its features.
 Here, we outline twelve practical ways that EEB researchers can use GitHub features for more collaborative, transparent, and reproducible science.
@@
 \textbf{branch}: Git workflow timelines or repositories are analogous to trees, with a main working project and diverging branches that are pointers to changes during the development process.
-A git branch is an alternative line of development for a project (repository).
+A git branch is an alternative line of development for a project (\textbf{repository}).
 Branches allow users to add new features or modifications to the project without affecting the main part of the project.
@@
 Having copies of these files safely stored is essential to protect against accidental modifications or deletions.
-Many researchers begin using GitHub as a means to store (or backup) their research compendium\textsuperscript{\protect\hyperlink{ref-MwwMapRG}{16}} to a centralized, readily-available remote server (see \protect\hyperlink{definitions}{Box 1}).
+Many researchers begin using GitHub as a means to store (or backup) their research compendium\textsuperscript{\protect\hyperlink{ref-MwwMapRG}{17}} to a centralized, readily-available remote server (see \protect\hyperlink{definitions}{Box 1}).
 A centralized research compendium stored in a version-controlled repository has the advantages of facilitating collaboration, integrating data and code archiving services, allowing file versions to be accessed and restored, and contributes to open science (see sections below).
 
-GitHub limits committed file sizes to 100 Mb (megabytes\textsuperscript{\protect\hyperlink{ref-1Co6ZZjF1}{17}}), which can make it challenging for centralizing research compendia containing larger file sizes.
-Users may still version large files using Git Large File Storage (LFS\textsuperscript{\protect\hyperlink{ref-11GtZ7icJ}{18}}) text pointers, but may have to rely on external file storage alternatives (such as local or cloud-hosting).
+GitHub limits committed file sizes to 100 Mb (megabytes\textsuperscript{\protect\hyperlink{ref-1Co6ZZjF1}{18}}), which can make it challenging for centralizing research compendia containing larger file sizes.
+Users may still version large files using Git Large File Storage (LFS\textsuperscript{\protect\hyperlink{ref-11GtZ7icJ}{19}}) text pointers, but may have to rely on external file storage alternatives (such as local or cloud-hosting).
 
@@
 
-Laboratory notebooks help researchers track their research notes, methods, policies and protocols\textsuperscript{\protect\hyperlink{ref-wwHxTOtm}{19}}.
-Virtual laboratory notebooks can be stored in GitHub repositories and provide the benefits of simultaneous, centralized and selective access, and allows for the easy update of policies and experiment protocols\textsuperscript{\protect\hyperlink{ref-10V7x4H4l}{20}}.
+Laboratory notebooks help researchers track their research notes, methods, policies and protocols\textsuperscript{\protect\hyperlink{ref-wwHxTOtm}{20}}.
+Virtual laboratory notebooks can be stored in GitHub repositories and provide the benefits of simultaneous, centralized and selective access, and allows for the easy update of policies and experiment protocols\textsuperscript{\protect\hyperlink{ref-10V7x4H4l}{21}}.
 Researchers have been increasingly using GitHub to maintain versions and share digital laboratory notebooks\textsuperscript{\protect\hyperlink{ref-10ghgV3S8}{3}} (\emph{e.g.}, \url{https://scheuerell-lab.github.io/lab-book}; \url{https://github.com/HuckleyLab/how_we_work}).
@@
 Later, the entire history of commits and their commit messages are viewable and can be audited similar to a physical laboratory notebook\textsuperscript{\protect\hyperlink{ref-4ny1onB0}{8}}.
-GitHub issues (\protect\hyperlink{definitions}{Box 1}) can be used to prioritize laboratory objectives and goals, as well as track any status updates.
+GitHub issues (see project management section below) can be used to prioritize laboratory objectives and goals, as well as track any status updates.
 
@@
 Github Discussions serve as a message board for conversation.
-Finally, GitHub Projects integrate issues and pull requests on automated spreadsheets and project boards, providing users with real-time tracking of project priorities and status\textsuperscript{\protect\hyperlink{ref-RhBKe0MG}{21}}.
+Finally, GitHub Projects integrate issues and pull requests on automated spreadsheets and project boards, providing users with real-time tracking of project priorities and status\textsuperscript{\protect\hyperlink{ref-RhBKe0MG}{22}}.
 Scripts, commit messages, and pull requests can be linked directly to issues, discussions, and projects providing a clear record of project workflow.
-The use of GitHub for all project-related conversation and planning, rather than e-mail or messaging tools, makes it easier to keep track of progress throughout the lifespan of a project.
+
+Using GitHub for all project-related conversation and planning, rather than e-mail or messaging tools, makes it easier to keep track of progress throughout the lifespan of a project.
 Unlike emails and messages which can get lost as more new tasks arise, GitHub issues are intentionally closed by repository administrators hiding the issue from view (closed issues remain accessible but not immediately visible).
-Project management in GitHub can also be integrated with third-party applications, such as ZenHub (\url{https://www.zenhub.com}) or Slack (\url{https://slack.github.com}).
-ZenHub allows for the enhanced visualization and organization of repositories and their issues, while the GitHub for Slack integration allows notifications from GitHub events to be sent directly to users or group channels\textsuperscript{\protect\hyperlink{ref-1GRWGlDWy}{22}}.
+Project management in GitHub can also be integrated with third-party applications, such as Zenhub (\url{https://www.zenhub.com}) or Slack (\url{https://slack.github.com}).
+ZenHub allows for the enhanced visualization and organization of repositories and their issues, while the GitHub for Slack integration allows notifications from GitHub events to be sent directly to users or group channels\textsuperscript{\protect\hyperlink{ref-1GRWGlDWy}{23}}.
 
@@
 
-Making presentations, syllabi and other course materials can be done through most major high-level programming languages such as R, with \texttt{RMarkdown}\textsuperscript{\protect\hyperlink{ref-QqMezOMg}{23}}, Python, with \texttt{python-ppt} (\url{https://python-pptx.readthedocs.io}), and Julia, with \texttt{Remark.jl} (\url{https://juliapackages.com/p/remark}), and be version-controlled and stored in GitHub.
-Once content is made, hosting a course website can be done through GitHub Pages\textsuperscript{\protect\hyperlink{ref-MDQfMwCW}{24}} (\emph{e.g.}, \url{https://github.com/topics/course-website}).
-This way, the course content can be available to enrolled students, as well as a global pool of learners and teachers interested in the course material.
+Making presentations, syllabi and other course materials can be done through most major high-level programming languages such as R, with \texttt{RMarkdown}\textsuperscript{\protect\hyperlink{ref-QqMezOMg}{24}}, Python, with \texttt{python-ppt} (\url{https://python-pptx.readthedocs.io}), and Julia, with \texttt{Remark.jl} (\url{https://juliapackages.com/p/remark}), and be version-controlled and stored in GitHub.
+Once content is made, hosting a course website can be done through GitHub Pages\textsuperscript{\protect\hyperlink{ref-MDQfMwCW}{25}} (\emph{e.g.}, \url{https://github.com/topics/course-website}).
+This way, course content can be available to enrolled students, as well as a global pool of learners and teachers interested in the material.
 Content can then be delivered via the course website, and/or a GitHub Organization with, for example, template repositories for assignments.
 Student submissions are perhaps the most challenging component, but the new GitHub Classroom tool (\url{https://classroom.github.com}) allows instructors to host private assignments to be submitted collaboratively or individually as code or PDF files, and even build autograding tests.
-Although time-consuming to establish, using these features can integrate learning version control and GitHub with the learning course content, and thus boost students feelings of self-efficacy and confidence\textsuperscript{\protect\hyperlink{ref-dqrFjoSb}{25}}.
+Although time-consuming to establish, using these features can integrate learning version control and GitHub with the learning course content, and thus boost students feelings of self-efficacy and confidence\textsuperscript{\protect\hyperlink{ref-dqrFjoSb}{26}}.
 
@@
 
-Personal or laboratory websites can improve the sharing of research findings, build online presence, and increase coordination of research efforts\textsuperscript{\protect\hyperlink{ref-HiIPSSHV}{26}}.
+Personal or laboratory websites can improve the sharing of research findings, build online presence, and increase coordination of research efforts\textsuperscript{\protect\hyperlink{ref-HiIPSSHV}{27}}.
 Despite many researchers in ecology and evolution having little experience in building or hosting webpages, many tools have been developed to help this process.
@@
 The resulting files from static websites can then be hosted in repositories, from which one can activate GitHub's Pages (\url{https://pages.github.com}) feature, allowing for the direct live hosting of HyperText Markup Language (HTML), Cascading Style Sheets (CSS) and JavaScript files within a free github.io domain.
-Website templates are readily available on GitHub (https://github.com/topics/website-template) or in user-specific repositories, which can be forked (\protect\hyperlink{definitions}{Box 1}) and customized\textsuperscript{\protect\hyperlink{ref-MXxgZJ45}{27}}.
+
+Website templates are readily available on GitHub (\url{https://github.com/topics/website-template}) or in user-specific repositories, which can be forked (\protect\hyperlink{definitions}{Box 1}) and customized\textsuperscript{\protect\hyperlink{ref-MXxgZJ45}{28}}.
 Aside from free hosting services, GitHub Pages also allows websites to be autogenerated and instantly updated following content modifications\textsuperscript{\protect\hyperlink{ref-RVetqmsg}{7}}.
-Creating and hosting websites on GitHub pages can be often time-consuming, as this process usually requires more knowledge in web design than out-of-the-box platforms (\emph{e.g.}, Wix, Weebly, Google Sites).
+Creating and hosting websites on GitHub pages can be time-consuming, as this process usually requires more knowledge in web design than out-of-the-box platforms (\emph{e.g.}, Wix, Weebly, Google Sites).
 However, free hosting, widely available template customization, and versioning are strong advantages over the alternatives.
@@
 
-Government, funding agencies, and publishers exercise rigorous open access data policies and mandates\textsuperscript{\protect\hyperlink{ref-PLmDFZrm}{28},\protect\hyperlink{ref-1Hcf13Q0k}{29}}.
-However, code and data sharing may be met by individual reluctance, temporary embargoes, or partially prevented by privacy and confidentiality reasons\textsuperscript{\protect\hyperlink{ref-1Ch6LSHef}{30}--\protect\hyperlink{ref-1CzUZwyU2}{32}}.
-Still, data deposition and ensuring its availability can amplify the outreach of published studies\textsuperscript{\protect\hyperlink{ref-666HppfO}{33}}, increase citation rates\textsuperscript{\protect\hyperlink{ref-1CcAUn3Lu}{34}}, and among many other reasons, enables the reproducibility and robustness of scientific advances\textsuperscript{\protect\hyperlink{ref-4LaijDIZ}{35}--\protect\hyperlink{ref-1HZdsK5Kn}{37}}.
+Government, funding agencies, and publishers exercise rigorous open access data policies and mandates\textsuperscript{\protect\hyperlink{ref-PLmDFZrm}{29},\protect\hyperlink{ref-1Hcf13Q0k}{30}}.
+However, code and data sharing may be met by individual reluctance, temporary embargoes, or partially prevented by privacy and confidentiality reasons\textsuperscript{\protect\hyperlink{ref-1Ch6LSHef}{31}--\protect\hyperlink{ref-1CzUZwyU2}{33}}.
+Still, data deposition and ensuring its availability can amplify the outreach of published studies\textsuperscript{\protect\hyperlink{ref-666HppfO}{34}}, increase citation rates\textsuperscript{\protect\hyperlink{ref-1CcAUn3Lu}{35}}, and among many other reasons, enable the reproducibility and robustness of scientific advances\textsuperscript{\protect\hyperlink{ref-4LaijDIZ}{36}--\protect\hyperlink{ref-1HZdsK5Kn}{38}}.
 While public repositories on GitHub make it easy to store and share data files, they are not considered long-term repositories for research materials.
@@
 DOIs are persistent and citable unique alpha-numeric identifiers assigned to digitally stored research materials.
-Because of this, scientists sharing code and data through GitHub are strongly encouraged to independently submit their research materials to long-term data archives (\emph{e.g.}, Zenodo, Figshare, Dryad, OSF\textsuperscript{\protect\hyperlink{ref-10ghgV3S8}{3},\protect\hyperlink{ref-kEX5dgzK}{9},\protect\hyperlink{ref-1Du6fzB8g}{38}}; \protect\hyperlink{tbl:compare}{Table 2}).
-(\protect\hyperlink{tbl:roles}{Table 1})
+Because of this, scientists sharing code and data through GitHub are strongly encouraged to independently submit their research materials to long-term data archives (\emph{e.g.}, Zenodo, Figshare, Dryad, OSF\textsuperscript{\protect\hyperlink{ref-10ghgV3S8}{3},\protect\hyperlink{ref-kEX5dgzK}{9},\protect\hyperlink{ref-1Du6fzB8g}{39}}; \protect\hyperlink{tbl:compare}{Table 1}).
 Some of these options (Zenodo, Figshare and OSF) integrate with GitHub, allowing project, code, and data releases (\protect\hyperlink{definitions}{Box 1}) to be archived with versioned, citable DOIs.
-Linking GitHub repositories with a DOI helps research become findable, properly cited, and can ensure long-term stability\textsuperscript{\protect\hyperlink{ref-iIEKCTLU}{39}}.
+Linking GitHub repositories with a DOI helps research become findable, properly cited, and can ensure long-term stability\textsuperscript{\protect\hyperlink{ref-iIEKCTLU}{40}}.
 
@@
 Code published without a license is under exclusive copyright (by default), protecting it from copy, distribution, and modifications.
-One may grant specific rights to their code for reuse by adding licensing files and specifications within GitHub repositories\textsuperscript{\protect\hyperlink{ref-TOsASkn5}{40}}.
+One may grant specific rights to their code for reuse by adding licensing files and specifications within GitHub repositories\textsuperscript{\protect\hyperlink{ref-TOsASkn5}{41}}.
 The Choose a License (\url{https://choosealicense.com/non-software/}) website offers further guidance on the licenses available for research and creative products.
@@
 A CC BY 4.0 license specifies that any code (or other creative products) must be appropriately credited to its original author when distributed, adapted or reused.
-A GNU General Public License v3 provides the same attributions above, but requires that all modified or adapted versions to be made public.
 
@@
 By forking, branching, and cloning repositories (\protect\hyperlink{definitions}{Box 1}), researchers can simultaneously work on different issues of the same research project to then later merge changes to the main branch project with pull requests.
-Explicit project organization and increased communication in GitHub Issues, Discussions, or within pull requests can help with project development and with potential merge conflicts due to users simultaneously working on the same sections\textsuperscript{\protect\hyperlink{ref-1BJcvyTmV}{41}}.
-Moreover, version control\textsuperscript{\protect\hyperlink{ref-K7nbP1Ty}{42}} and commit reversal features allow researchers to track and progress without worrying about irreparably modifying someone else's work.
+Explicit project organization and increased communication in GitHub Issues, Discussions, or within pull requests can help with project development and with potential merge conflicts due to users simultaneously working on the same sections\textsuperscript{\protect\hyperlink{ref-1BJcvyTmV}{42}}.
+Moreover, version control\textsuperscript{\protect\hyperlink{ref-K7nbP1Ty}{43}} and commit reversal features allow researchers to track and progress without worrying about irreparably modifying someone else's work.
 By enabling more comprehensive remote collaboration, GitHub encourages the exchange of ideas among researchers at different institutions and in different countries, which can serve to improve the quality of the research itself by providing open access to data and code.
-In academic settings, GitHub can also facilitate interactions between research advisors and advisees, providing a platform for students or other trainees to share in-progress code, and flag specific challenges or questions for their supervisors or mentors (\protect\hyperlink{tbl:roles}{Table 1}).
-Periodic code review\textsuperscript{\protect\hyperlink{ref-hm9PaCLD}{43}} can also help advisors identify errors early in the process, and inform further training and mentorship to fill gaps in skills.
+In academic settings, GitHub can also facilitate interactions between research advisors and advisees, providing a platform for students or other trainees to share in-progress code, and flag specific challenges or questions for their supervisors or mentors (\protect\hyperlink{tbl:roles}{Table 2}).
+Periodic code review\textsuperscript{\protect\hyperlink{ref-hm9PaCLD}{44}} can also help advisors identify errors early in the process, and inform further training and mentorship to fill gaps in skills.
 
@@
 
-We wrote this manuscript using Manubot\textsuperscript{\protect\hyperlink{ref-YuJbg3zO}{44}}, a workflow implemented in GitHub to automatically render manuscripts and automate bibliographical tasks.
+We wrote this manuscript using Manubot\textsuperscript{\protect\hyperlink{ref-YuJbg3zO}{45}}, a workflow implemented in GitHub to automatically render manuscripts and automate bibliographical tasks.
 Manubot uses GitHub's automation workflow, GitHub Actions, to combine and convert individual Markdown files into a single LaTeX document, which can then be converted to a Word or PDF document, and displayed as a webpage.
@@
 Additional GitHub Actions can be integrated with Manubot, such as ones creating figures or generating tables (\emph{e.g.}, \url{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/main/.github/workflows}).
-For more examples of manuscripts built via Manubot, see\textsuperscript{\protect\hyperlink{ref-YuJbg3zO}{44}}.
+For more examples of manuscripts built via Manubot, see\textsuperscript{\protect\hyperlink{ref-YuJbg3zO}{45}}.
 
@@
 Certain journals or software development communities require submitted work or research code to be hosted on GitHub and their review processes make use of GitHub Issues (\emph{e.g.}, rOpenSci (\url{https://ropensci.org/software-review/}), Journal of Open Source Software (\url{https://joss.readthedocs.io/en/latest/submitting.html})).
-rOpenSci's efforts have resulted in many well-used R packages for ecology research including \texttt{rfishbase}\textsuperscript{\protect\hyperlink{ref-Xsdcv6q}{45}} and \texttt{taxize}\textsuperscript{\protect\hyperlink{ref-FVBWKkZu}{46}}.
+rOpenSci's efforts have resulted in many well-used R packages for ecology research including \texttt{rfishbase}\textsuperscript{\protect\hyperlink{ref-Xsdcv6q}{46}} and \texttt{taxize}\textsuperscript{\protect\hyperlink{ref-FVBWKkZu}{47}}.
 
@@
 Scientific publications often omit part of their intellectual and computational workflows, including the treatment of raw data and analytical steps (\emph{e.g.}, model assumption testing).
-Publishing data and reproducible workflows along with manuscripts can provide readers with all details about analytical steps and enable reproducing research experiments and results\textsuperscript{\protect\hyperlink{ref-NOgBWVAr}{47}}.
+Publishing data and reproducible workflows along with manuscripts can provide readers with all details about analytical steps and enable reproducing research experiments and results\textsuperscript{\protect\hyperlink{ref-NOgBWVAr}{48}}.
 In addition to storing data and code, GitHub repositories can provide a time-stamped (version controlled) preregistration of research plans and hypotheses.
@@
 GitHub can serve as a tool for open and tractable research development.
-Collaborators can directly interact with code and data, inspect for errors, and potentially identify scientific misconduct prior to manuscript submission (\emph{e.g.},\textsuperscript{\protect\hyperlink{ref-18PTmKJkq}{48}}).
+Collaborators can directly interact with code and data, inspect for errors, and potentially identify scientific misconduct prior to manuscript submission (\emph{e.g.},\textsuperscript{\protect\hyperlink{ref-18PTmKJkq}{49}}).
 Collaborators and readers are better positioned to discover erroneous or questionable findings if they have complete and transparent access to projects.
@@
 Projects can make use of GitHub Discussions (\url{https://docs.github.com/en/discussions}) to communicate among repository members (collaborators) and to engage with other scientists and the general public.
-Moreover, researches can also use the GitHub Community (\url{https://github.community/}) forum to share expertise or request help from other researchers in ecology and evolution on their analyses and ideas (\protect\hyperlink{tbl:roles}{Table 1}).
+Moreover, researchers can also use the GitHub Community (\url{https://github.community/}) forum to share expertise or request help from others on their analyses and ideas (\protect\hyperlink{tbl:roles}{Table 2}).
 
@@
 
-Projects in ecology and evolution often involve graduate students, research assistants, and post-doctoral fellows, who hold limited-term positions\textsuperscript{\protect\hyperlink{ref-D4C4k4ak}{49}}.
+Projects in ecology and evolution often involve graduate students, research assistants, and post-doctoral fellows, who hold limited-term positions\textsuperscript{\protect\hyperlink{ref-D4C4k4ak}{50}}.
 Without clear plans on project continuity, the research code and data management upkeep tends to fall off as researchers move on to new projects or to other institutions.
-Additionally, code and data can be difficult to access when kept only on the personal devices of researchers\textsuperscript{\protect\hyperlink{ref-19kmNxiHc}{50}}.
-
-GitHub can facilitate project continuity among research code by making code handover easier\textsuperscript{\protect\hyperlink{ref-4ny1onB0}{8},\protect\hyperlink{ref-D4C4k4ak}{49}}.
-Through version control, the history of code and data from projects in ecology and evolution can be tracked accessible to future laboratory members and collaborators\textsuperscript{\protect\hyperlink{ref-3DKwn1sY}{12}}.
-Repositories and organizations can have designated data and code owners (or more appropriate, stewards; see\textsuperscript{\protect\hyperlink{ref-iIEKCTLU}{39}},\textsuperscript{\protect\hyperlink{ref-s91uGRZ2}{51}}), who can also can change through time allowing for the transition of code from one cohort of researchers to the next.
+Additionally, code and data can be difficult to access when kept only on personal devices\textsuperscript{\protect\hyperlink{ref-19kmNxiHc}{51}}.
+
+GitHub can facilitate project continuity among research code by making code handover easier\textsuperscript{\protect\hyperlink{ref-4ny1onB0}{8},\protect\hyperlink{ref-D4C4k4ak}{50}}.
+Through version control, the history of code and data from projects in ecology and evolution can be tracked and accessible to future laboratory members and collaborators\textsuperscript{\protect\hyperlink{ref-3DKwn1sY}{12}}.
+Repositories and organizations can have designated data and code owners (or more appropriate, stewards; see\textsuperscript{\protect\hyperlink{ref-iIEKCTLU}{40}},\textsuperscript{\protect\hyperlink{ref-s91uGRZ2}{52}}), who can also can change through time allowing for the transition of code from one cohort of researchers to the next.
 Other project collaborators can offer many contributions to repository design and development, and their active involvement can both aid authors ability to act as guarantors of the project, and the clarity and reproducibility of the project for future users.
@@
 Whereas access to repositories is usually assigned to individual contributors, Organizations facilitate the management of access permissions by allowing teams to be granted access to specific repositories.
-This ensures repositories with sensitive information remain as restricted as needed, while repositories with general stay easily accessible to selected member groups.
+This ensures repositories with sensitive information remain as restricted as needed, while others stay open and accessible to selected member groups.
 The organization structure also allows for easy issue tracking and discussions related to research content and progress.
@@
 
-There have been many calls for researchers outside of the software development community to adopt GitHub to improve their collaborative research\textsuperscript{\protect\hyperlink{ref-10ghgV3S8}{3},\protect\hyperlink{ref-1Du6fzB8g}{38},\protect\hyperlink{ref-UsTxAq4f}{52}}.
+There have been many calls for researchers outside of the software development community to adopt GitHub to improve their collaborative research\textsuperscript{\protect\hyperlink{ref-10ghgV3S8}{3},\protect\hyperlink{ref-1Du6fzB8g}{39},\protect\hyperlink{ref-UsTxAq4f}{53}}.
 This call comes in light of both the continuous shift towards open-science and the increasing computational and data requirements in EEB.
@@
 
-First, real-time collaborative editing of files is not possible in GitHub.
-Users seeking to real-time edit documents might still need to rely on alternative features (\emph{e.g.}, cloud-stored documents from Microsoft Word, Google Docs, hackMD (\url{https://hackmd.io/})).
-Second, certain operations that are dependent on other software might not be easily achievable in GitHub, such as manipulating figures or tables.
-Although creating tables and figures can be achieved through code, users may be limited to other software to collaboratively brainstorm figures and tables (e.g.~Google Slides, Google Sheets).
-Albeit, files containing documents, figures and tables may still be versioned in GitHub.
+First, real-time document editing is still best performed on other platforms (\emph{e.g.}, cloud-stored documents from Microsoft Word, Google Docs, hackMD (\url{https://hackmd.io/})).
+Second, operations that are dependent on other software might not be easily accomplished in GitHub, such as manipulating figures or tables.
+Although creating tables and figures can be achieved through code, users may choose other software to collaboratively brainstorm figures and tables (\emph{e.g.} Google Slides, Google Sheets).
 
@@
 Institutional encouragement and instructional resources focused on researchers in ecology and evolution may be limited.
-When GitHub is taught within an EEB context, it is usually accompanying coursework in topics such as statistical programming.
+When GitHub is taught in an EEB context, it is usually accompanying coursework in topics such as statistical programming.
 It can be challenging to learn Git alongside scripting languages, statistical theory, and file system navigation, especially when many may be inexperienced with programming.
@@
 Those assumptions may obscure the utility of GitHub for tasks other than traditional data analysis and code development.
-However, we emphasize that there are opportunities for collaboration using GitHub by researchers of all skill levels or time constraints (Table \ref{tbl:roles}); for example, project stakeholders can provide a list of use-cases or highlight important conceptual components of a project using GitHub's issues or discussions features.
-
-A third barrier may come from general reluctance to share data and code publicly, or technical and logistical issues\textsuperscript{\protect\hyperlink{ref-pq2Tv1BC}{53}}.
+However, we emphasize that there are opportunities for collaboration using GitHub by researchers of all skill levels or time constraints \protect\hyperlink{tbl:roles}{Table 2}; for example, project stakeholders can provide a list of use-cases or highlight important conceptual components of a project using GitHub's issues or discussions features.
+
+A third barrier may come from general reluctance to share data and code publicly, or technical and logistical issues\textsuperscript{\protect\hyperlink{ref-pq2Tv1BC}{16}}.
 GitHub is, by default, a public and open platform.
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-pq2Tv1BC}{}}%
+\CSLLeftMargin{16. }
+\CSLRightInline{Gomes, D.
+G.
+E.
+\emph{et al.} Why don't we share data and code?
+Perceived barriers and benefits to public archiving practices.
+(2022) doi:\href{https://doi.org/10.31222/osf.io/gaj43}{10.31222/osf.io/gaj43}.}
+
 \leavevmode\vadjust pre{\hypertarget{ref-MwwMapRG}{}}%
-\CSLLeftMargin{16. }
+\CSLLeftMargin{17. }
 \CSLRightInline{Marwick, B., Boettiger, C.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-1Co6ZZjF1}{}}%
-\CSLLeftMargin{17. }
+\CSLLeftMargin{18. }
 \CSLRightInline{About large files on GitHub. \emph{GitHub Docs} \url{https://ghdocs-prod.azurewebsites.net/en/repositories/working-with-files/managing-large-files/about-large-files-on-github}.}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-11GtZ7icJ}{}}%
-\CSLLeftMargin{18. }
+\CSLLeftMargin{19. }
 \CSLRightInline{Git Large File Storage. \emph{Git Large File Storage} \url{https://git-lfs.github.com/}.}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-wwHxTOtm}{}}%
-\CSLLeftMargin{19. }
+\CSLLeftMargin{20. }
 \CSLRightInline{Kanza, S. \emph{et al.} \href{https://doi.org/10.1186/s13321-017-0221-3}{Electronic lab notebooks: can they replace paper?} \emph{J Cheminform} \textbf{9}, (2017).}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-10V7x4H4l}{}}%
-\CSLLeftMargin{20. }
+\CSLLeftMargin{21. }
 \CSLRightInline{Schnell, S.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-RhBKe0MG}{}}%
-\CSLLeftMargin{21. }
+\CSLLeftMargin{22. }
 \CSLRightInline{About projects (beta). \emph{GitHub Docs} \url{https://ghdocs-prod.azurewebsites.net/en/issues/trying-out-the-new-projects-experience/about-projects}.}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-1GRWGlDWy}{}}%
-\CSLLeftMargin{22. }
+\CSLLeftMargin{23. }
 \CSLRightInline{Slack. GitHub for Slack. \emph{Slack Help Center} \url{https://slack.com/help/articles/232289568-GitHub-for-Slack}.}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-QqMezOMg}{}}%
-\CSLLeftMargin{23. }
+\CSLLeftMargin{24. }
 \CSLRightInline{Xie, Y., Allaire, J. J. \& Grolemund, G. \emph{R Markdown: the definitive guide}. (CRC Press, Taylor and Francis Group, 2019).}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-MDQfMwCW}{}}%
-\CSLLeftMargin{24. }
+\CSLLeftMargin{25. }
 \CSLRightInline{Quickstart for GitHub Pages. \emph{GitHub Docs} \url{https://ghdocs-prod.azurewebsites.net/en/pages/quickstart}.}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-dqrFjoSb}{}}%
-\CSLLeftMargin{25. }
+\CSLLeftMargin{26. }
 \CSLRightInline{Trujillo, G.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-HiIPSSHV}{}}%
-\CSLLeftMargin{26. }
+\CSLLeftMargin{27. }
 \CSLRightInline{Smaglik, P.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-MXxgZJ45}{}}%
-\CSLLeftMargin{27. }
+\CSLLeftMargin{28. }
 \CSLRightInline{Dawson, C. \emph{Building tools with GitHub: customize your workflow}. (O'Reilly, 2016).}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-PLmDFZrm}{}}%
-\CSLLeftMargin{28. }
+\CSLLeftMargin{29. }
 \CSLRightInline{Tenopir, C.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-1Hcf13Q0k}{}}%
-\CSLLeftMargin{29. }
+\CSLLeftMargin{30. }
 \CSLRightInline{Nugroho, R.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-1Ch6LSHef}{}}%
-\CSLLeftMargin{30. }
+\CSLLeftMargin{31. }
 \CSLRightInline{Wicherts, J.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-SLq38RVv}{}}%
-\CSLLeftMargin{31. }
+\CSLLeftMargin{32. }
 \CSLRightInline{Figueiredo, A. S. \href{https://doi.org/10.3389/fpubh.2017.00327}{Data Sharing: Convert Challenges into Opportunities}. \emph{Front. Public Health} \textbf{5}, (2017).}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-1CzUZwyU2}{}}%
-\CSLLeftMargin{32. }
+\CSLLeftMargin{33. }
 \CSLRightInline{Tenopir, C.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-666HppfO}{}}%
-\CSLLeftMargin{33. }
+\CSLLeftMargin{34. }
 \CSLRightInline{Pronk, T.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-1CcAUn3Lu}{}}%
-\CSLLeftMargin{34. }
+\CSLLeftMargin{35. }
 \CSLRightInline{Piwowar, H.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-4LaijDIZ}{}}%
-\CSLLeftMargin{35. }
+\CSLLeftMargin{36. }
 \CSLRightInline{\href{https://doi.org/10.1038/ncb3506}{On data availability, reproducibility and reuse}. \emph{Nat Cell Biol} \textbf{19}, 259--259 (2017).}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-uBJwnPbq}{}}%
-\CSLLeftMargin{36. }
+\CSLLeftMargin{37. }
 \CSLRightInline{Mislan, K.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-1HZdsK5Kn}{}}%
-\CSLLeftMargin{37. }
+\CSLLeftMargin{38. }
 \CSLRightInline{Baker, M. \href{https://doi.org/10.1038/533452a}{1,500 scientists lift the lid on reproducibility}. \emph{Nature} \textbf{533}, 452--454 (2016).}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-1Du6fzB8g}{}}%
-\CSLLeftMargin{38. }
+\CSLLeftMargin{39. }
 \CSLRightInline{Crystal‐Ornelas, R.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-iIEKCTLU}{}}%
-\CSLLeftMargin{39. }
+\CSLLeftMargin{40. }
 \CSLRightInline{Hampton, S. E. \emph{et al.} \href{https://doi.org/10.1890/es14-00402.1}{The Tao of open science for ecology}. \emph{Ecosphere} \textbf{6}, art120 (2015).}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-TOsASkn5}{}}%
-\CSLLeftMargin{40. }
+\CSLLeftMargin{41. }
 \CSLRightInline{Adding a license to a repository.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-1BJcvyTmV}{}}%
-\CSLLeftMargin{41. }
+\CSLLeftMargin{42. }
 \CSLRightInline{Vale, G., Schmid, A., Santos, A.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-K7nbP1Ty}{}}%
-\CSLLeftMargin{42. }
+\CSLLeftMargin{43. }
 \CSLRightInline{Crystal-Ornelas, R.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-hm9PaCLD}{}}%
-\CSLLeftMargin{43. }
+\CSLLeftMargin{44. }
 \CSLRightInline{Song, X., Goldstein, S.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-YuJbg3zO}{}}%
-\CSLLeftMargin{44. }
+\CSLLeftMargin{45. }
 \CSLRightInline{Himmelstein, D. S. \emph{et al.} \href{https://doi.org/10.1371/journal.pcbi.1007128}{Open collaborative writing with Manubot}. \emph{PLoS Comput Biol} \textbf{15}, e1007128 (2019).}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Xsdcv6q}{}}%
-\CSLLeftMargin{45. }
+\CSLLeftMargin{46. }
 \CSLRightInline{Boettiger, C., Lang, D.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-FVBWKkZu}{}}%
-\CSLLeftMargin{46. }
+\CSLLeftMargin{47. }
 \CSLRightInline{Chamberlain, S. A. \& Szöcs, E. \href{https://doi.org/10.12688/f1000research.2-191.v2}{taxize: taxonomic search and retrieval in R}. \emph{F1000Res} \textbf{2}, 191 (2013).}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-NOgBWVAr}{}}%
-\CSLLeftMargin{47. }
+\CSLLeftMargin{48. }
 \CSLRightInline{Culina, A., van den Berg, I., Evans, S.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-18PTmKJkq}{}}%
-\CSLLeftMargin{48. }
+\CSLLeftMargin{49. }
 \CSLRightInline{January 18, P.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-D4C4k4ak}{}}%
-\CSLLeftMargin{49. }
+\CSLLeftMargin{50. }
 \CSLRightInline{Fehr, J., Himpe, C., Rave, S. \& Saak, J. \href{https://doi.org/10.5334/jors.307}{Sustainable Research Software Hand-Over}. \emph{JORS} \textbf{9}, 5 (2021).}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-19kmNxiHc}{}}%
-\CSLLeftMargin{50. }
+\CSLLeftMargin{51. }
 \CSLRightInline{Vines, Timothy~H.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-s91uGRZ2}{}}%
-\CSLLeftMargin{51. }
+\CSLLeftMargin{52. }
 \CSLRightInline{About code owners.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-UsTxAq4f}{}}%
-\CSLLeftMargin{52. }
+\CSLLeftMargin{53. }
 \CSLRightInline{Anbaroğlu, B. \href{https://doi.org/10.1111/tgis.12810}{A collaborative GIS programming course using GitHub Classroom}. \emph{Transactions in GIS} \textbf{25}, 3132--3158 (2021).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-pq2Tv1BC}{}}%
-\CSLLeftMargin{53. }
-\CSLRightInline{Gomes, D.
-G.
-E.
-\emph{et al.} Why don't we share data and code?
-Perceived barriers and benefits to public archiving practices.
-(2022) doi:\href{https://doi.org/10.31222/osf.io/gaj43}{10.31222/osf.io/gaj43}.}
 

### 2022-07-12 manuscript.tex
Merge pull request #254 from SORTEE-Github-Hackathon/DrMattG-Abstract_fhillemann [ci skip]
This build is based on
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/1aab55c67fc728559fe52f3f106965c1eef0e179.

This commit was created by the following CI build and job:
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/1aab55c67fc728559fe52f3f106965c1eef0e179/checks
https://github.com/SORTEE-Github-Hackathon/manuscript/actions/runs/2658244426

@@
 This manuscript
-(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/63f18c11f35a239c2085d7d7dfdb935614f182cf/}{permalink})
+(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/1aab55c67fc728559fe52f3f106965c1eef0e179/}{permalink})
 was automatically generated
-from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/63f18c11f35a239c2085d7d7dfdb935614f182cf}{SORTEE-Github-Hackathon/manuscript@63f18c1}
+from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/1aab55c67fc728559fe52f3f106965c1eef0e179}{SORTEE-Github-Hackathon/manuscript@1aab55c}
 on July 12, 2022.
@@
 
-Researchers in ecology and evolutionary biology are increasingly dependent on computational code to conduct research.
-With the growing role of data science in research, the use of efficient methods to share, reproduce, and collaborate on code has become fundamental.
-GitHub is an online, cloud-based service that can help researchers track, organize, discuss, share, and collaborate on software and code.
+Researchers in ecology and evolutionary biology are increasingly dependent on computational code to conduct research, and the use of efficient methods to share, reproduce, and collaborate on code as well as any research-related documentation has become fundamental.
+GitHub is an online, cloud-based service that can help researchers track, organize, discuss, share, and collaborate on software and other materials related to research production, including data, code for analyses, and protocols.
+
 Despite these benefits, the use of GitHub by EEB researchers is not widespread due to the lack of domain-specific information and guidelines.

### 2022-07-13 manuscript.tex
Merge pull request #255 from SORTEE-Github-Hackathon/RCO-moving-tables [ci skip]
This build is based on
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/3778b55f2950608f6cb50fc7f2a8a320ce757b6a.

This commit was created by the following CI build and job:
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/3778b55f2950608f6cb50fc7f2a8a320ce757b6a/checks
https://github.com/SORTEE-Github-Hackathon/manuscript/actions/runs/2664445561

@@
 This manuscript
-(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/1aab55c67fc728559fe52f3f106965c1eef0e179/}{permalink})
+(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/3778b55f2950608f6cb50fc7f2a8a320ce757b6a/}{permalink})
 was automatically generated
-from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/1aab55c67fc728559fe52f3f106965c1eef0e179}{SORTEE-Github-Hackathon/manuscript@1aab55c}
-on July 12, 2022.
+from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/3778b55f2950608f6cb50fc7f2a8a320ce757b6a}{SORTEE-Github-Hackathon/manuscript@3778b55}
+on July 13, 2022.
 
@@
 Co-authors can contribute changes or suggest revisions to a manuscript written in GitHub through pull requests (\protect\hyperlink{definitions}{Box 1}).
-Pull requests provide line-by-line views of proposed changes, which can be commented, modified, or approved by designated reviewers and collaborators (\protect\hyperlink{tbl:roles}{Table 1}).
+Pull requests provide line-by-line views of proposed changes, which can be commented, modified, or approved by designated reviewers and collaborators (\protect\hyperlink{tbl:roles}{Table 2}).
 Relevant literature or issues can be made using the Discussions and Issues features.
@@
 \subsection{Tables}\label{tables}}
+
+\begin{longtable}[]{@{}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.0628}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.0529}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.0281}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.0281}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.0380}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.0529}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.1851}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.1669}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.2562}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.1289}}@{}}
+\caption{a comparison of technologies commonly used for collaborating on research in Ecology and Evolutionary Biology.
+In the first column, we group platforms for collaboration into broad guilds.
+The second column lists the platform for collaboration.
+The remaining columns indicate whether the platform for collaboration \label{tbl:compare}}\tabularnewline
+\toprule
+\begin{minipage}[b]{\linewidth}\raggedright
+Guild
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+Software
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+Vesion control
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+Backup (cloud)
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+Passive collaboration
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+Active real-time colalboration
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+Free \$
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+Permanent (DOI)
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+Storage limits
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+GitHub Integration
+\end{minipage} \\
+\midrule
+\endfirsthead
+\toprule
+\begin{minipage}[b]{\linewidth}\raggedright
+Guild
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+Software
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+Vesion control
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+Backup (cloud)
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+Passive collaboration
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+Active real-time colalboration
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+Free \$
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+Permanent (DOI)
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+Storage limits
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+GitHub Integration
+\end{minipage} \\
+\midrule
+\endhead
+Multi-tool & GitHub & yes & yes & yes & NA & Broadly limited free version.
+Advanced features are provided for free to students and education professionals.
+& A DOI can only be obtained when integrating to other services that can mint DOI (e.g.~Zenodo, OSF).
+& 100 MB per file, 500 MB per private repository (2 GB for paid accounts).
+100 GB for public repositories.
+Larger files (up to 2 GB) can be attached to releases & NA \\
+Multi-tool & OSF & yes & yes & yes & yes & yes & yes & 25 GB for private projects, up to 5GB per file, plus partner add-ons, 50GB for public projects & yes \\
+Long-term (public) data repositories & PANGAEA & yes & yes & yes & NA & yes & yes & 10 GB free & NA \\
+Long-term (public) data repositories & Zenodo & after published & after published & NA & NA & yes & yes & 50 GB per dataset & yes \\
+Long-term (public) data repositories & Dryad & after published & after published & NA & NA & some journals cover cost & yes & 300 GB per publication & Can link to individual files (not entire reopository); not really integrated \\
+Long-term (public) data repositories & Figshare & yes & yes & yes & NA & yes & yes & 20 GB free, up to 5 TB & yes \\
+Temporary (personal) drive storage & Google Drive & yes & yes & yes & yes & limited free version \& paid & NA & 15 GB free, up to 100 GB with Google One & yes \\
+Temporary (personal) drive storage & Box & limited & yes & ? & ? & NA & NA & Unlimited total size for subscription & yes \\
+Temporary (personal) drive storage & DropBox & limited & yes & yes & yes & limited free version \& paid & NA & 2 GB free & yes \\
+Temporary (personal) drive storage & One Drive and the Office Suite & yes & yes & yes & yes & limited free version \& paid & NA & 5 GB free, up to 1TB paid & yes \\
+Collaborative code/text editors & Overleaf (online latex editor) & yes & yes & yes & NA & NA & NA & 1MB for individual .tex, 50 MB for individual files, unlimited project size & yes \\
+Collaborative code/text editors & Jupyter Notebook & yes & ?
+& yes & with Colab & yes & NA & via Binder: no hard limit, but suggests no files \textgreater100 MB, can also store on GitHub or Google Colab & yes \\
+Collaborative code/text editors & HackMD & yes & yes & yes & yes & yes & NA & 3 documents free, private invitee limits & yes \\
+\bottomrule
+\end{longtable}
 
@@
 
-\begin{longtable}[]{@{}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.0628}}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.0529}}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.0281}}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.0281}}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.0380}}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.0529}}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.1851}}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.1669}}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.2562}}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.1289}}@{}}
-\caption{a comparison of technologies commonly used for collaborating on research in Ecology and Evolutionary Biology.
-In the first column, we group platforms for collaboration into broad guilds.
-The second column lists the platform for collaboration.
-The remaining columns indicate whether the platform for collaboration \label{tbl:compare}}\tabularnewline
-\toprule
-\begin{minipage}[b]{\linewidth}\raggedright
-Guild
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
-Software
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
-Vesion control
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
-Backup (cloud)
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
-Passive collaboration
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
-Active real-time colalboration
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
-Free \$
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
-Permanent (DOI)
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
-Storage limits
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
-GitHub Integration
-\end{minipage} \\
-\midrule
-\endfirsthead
-\toprule
-\begin{minipage}[b]{\linewidth}\raggedright
-Guild
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
-Software
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
-Vesion control
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
-Backup (cloud)
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
-Passive collaboration
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
-Active real-time colalboration
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
-Free \$
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
-Permanent (DOI)
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
-Storage limits
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
-GitHub Integration
-\end{minipage} \\
-\midrule
-\endhead
-Multi-tool & GitHub & yes & yes & yes & NA & Broadly limited free version.
-Advanced features are provided for free to students and education professionals.
-& A DOI can only be obtained when integrating to other services that can mint DOI (e.g.~Zenodo, OSF).
-& 100 MB per file, 500 MB per private repository (2 GB for paid accounts).
-100 GB for public repositories.
-Larger files (up to 2 GB) can be attached to releases & NA \\
-Multi-tool & OSF & yes & yes & yes & yes & yes & yes & 25 GB for private projects, up to 5GB per file, plus partner add-ons, 50GB for public projects & yes \\
-Long-term (public) data repositories & PANGAEA & yes & yes & yes & NA & yes & yes & 10 GB free & NA \\
-Long-term (public) data repositories & Zenodo & after published & after published & NA & NA & yes & yes & 50 GB per dataset & yes \\
-Long-term (public) data repositories & Dryad & after published & after published & NA & NA & some journals cover cost & yes & 300 GB per publication & Can link to individual files (not entire reopository); not really integrated \\
-Long-term (public) data repositories & Figshare & yes & yes & yes & NA & yes & yes & 20 GB free, up to 5 TB & yes \\
-Temporary (personal) drive storage & Google Drive & yes & yes & yes & yes & limited free version \& paid & NA & 15 GB free, up to 100 GB with Google One & yes \\
-Temporary (personal) drive storage & Box & limited & yes & ? & ? & NA & NA & Unlimited total size for subscription & yes \\
-Temporary (personal) drive storage & DropBox & limited & yes & yes & yes & limited free version \& paid & NA & 2 GB free & yes \\
-Temporary (personal) drive storage & One Drive and the Office Suite & yes & yes & yes & yes & limited free version \& paid & NA & 5 GB free, up to 1TB paid & yes \\
-Collaborative code/text editors & Overleaf (online latex editor) & yes & yes & yes & NA & NA & NA & 1MB for individual .tex, 50 MB for individual files, unlimited project size & yes \\
-Collaborative code/text editors & Jupyter Notebook & yes & ?
-& yes & with Colab & yes & NA & via Binder: no hard limit, but suggests no files \textgreater100 MB, can also store on GitHub or Google Colab & yes \\
-Collaborative code/text editors & HackMD & yes & yes & yes & yes & yes & NA & 3 documents free, private invitee limits & yes \\
-\bottomrule
-\end{longtable}
-
 \hypertarget{references}{%

### 2022-07-14 manuscript.tex
Merge pull request #256 from robcrystalornelas/main [ci skip]
This build is based on
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/1871a551b58e817b71a630c86cdd3fb8268d2ada.

This commit was created by the following CI build and job:
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/1871a551b58e817b71a630c86cdd3fb8268d2ada/checks
https://github.com/SORTEE-Github-Hackathon/manuscript/actions/runs/2673284290

@@
 This manuscript
-(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/3778b55f2950608f6cb50fc7f2a8a320ce757b6a/}{permalink})
+(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/1871a551b58e817b71a630c86cdd3fb8268d2ada/}{permalink})
 was automatically generated
-from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/3778b55f2950608f6cb50fc7f2a8a320ce757b6a}{SORTEE-Github-Hackathon/manuscript@3778b55}
-on July 13, 2022.
+from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/1871a551b58e817b71a630c86cdd3fb8268d2ada}{SORTEE-Github-Hackathon/manuscript@1871a55}
+on July 14, 2022.
 
@@
 Maintaining code for scientific collaboration requires an efficient and well-documented work-flow\textsuperscript{\protect\hyperlink{ref-1Kqna6l2}{2}}.
-To facilitate this process, scientists have been increasingly adopting tools from information and systems technology, such as cloud-based services for documentation and version control (\emph{e.g.}, from the Google Suite, the Microsoft Suite, and GitHub\textsuperscript{\protect\hyperlink{ref-10ghgV3S8}{3}}).
+To facilitate this process, scientists have been adopting tools from information and systems technology, such as cloud-based services for documentation and version control (\emph{e.g.}, from the Google Suite, the Microsoft Suite, and GitHub\textsuperscript{\protect\hyperlink{ref-10ghgV3S8}{3}}).
 However, most researchers lack exposure to adequate code practices and thus dedicate valuable time and effort to self-teaching research-facilitating tools.
@@
 This workflow provides a strong and clear advantage over sending files back-and-forth (\emph{e.g.} via email), a process that can become challenging and time-consuming in long-term and collaborative projects\textsuperscript{\protect\hyperlink{ref-4ny1onB0}{8}}.
-Through its combination of version control and and collaborative features, GitHub facilitates open source code alongside collaborative development\textsuperscript{\protect\hyperlink{ref-kEX5dgzK}{9}}.
+Through its combination of version control and collaborative features, GitHub facilitates open source code alongside collaborative development\textsuperscript{\protect\hyperlink{ref-kEX5dgzK}{9}}.
 
@@
 Widespread adoption of GitHub for collaborating on research tasks can ultimately enable EEB researchers to spend less time on creating novel processes for collaboration and more time on their research\textsuperscript{\protect\hyperlink{ref-ydrk01SR}{14}}.
-More importantly, increasing the availability of data and code management standards -- of which GitHub is one increasingly important component -- makes research more reproducible and collaborative\textsuperscript{\protect\hyperlink{ref-13QX8XU3J}{15},\protect\hyperlink{ref-pq2Tv1BC}{16}}.
+More importantly, expanding the availability of data and code management standards -- of which GitHub is one increasingly important component -- makes research more reproducible and collaborative\textsuperscript{\protect\hyperlink{ref-13QX8XU3J}{15},\protect\hyperlink{ref-pq2Tv1BC}{16}}.
 
@@
 Even if they do not have access to \textbf{push} to the original repository, they can make a fork and edit it independently.
-Forks are linked to the original GitHub repository and ``upstream'' changes (\emph{i.e.} those in the original repository) can be \textbf{merged} to keep the fork up to date with the original project.
+Forks are linked to the original GitHub repository and ``upstream'' changes (\emph{i.e.}, those in the original repository) can be \textbf{merged} to keep the fork up to date with the original project.
 Changes made in the fork can be integrated into the original project via \textbf{pull requests}.
 \\
-\textbf{clone}: Cloning a \textbf{repository} is a way of making a local copy (\emph{i.e.} on your computer) of a GitHub \textbf{repository}.
+\textbf{clone}: Cloning a \textbf{repository} is a way of making a local copy (\emph{i.e.}, on your computer) of a GitHub \textbf{repository}.
 If you have access to \textbf{push} to a \textbf{repository}, this can be a first step to contributing to a project.
@@
 Commits can include changes in multiple files and must include a brief commit message describing the changes made.
-A typical workflow is to make some related changes in files, add a commit message (\emph{e.g.} ``generate and include fig1 in results''), and after several commits \textbf{push} those commits to the remote (\emph{i.e.}, cloud-based) GitHub \textbf{repository}.
+A typical workflow is to make some related changes in files, add a commit message (\emph{e.g.}, ``generate and include fig1 in results''), and after several commits \textbf{push} those commits to the remote (\emph{i.e.}, cloud-based) GitHub \textbf{repository}.
 \\
@@
 GitHub limits committed file sizes to 100 Mb (megabytes\textsuperscript{\protect\hyperlink{ref-1Co6ZZjF1}{18}}), which can make it challenging for centralizing research compendia containing larger file sizes.
-Users may still version large files using Git Large File Storage (LFS\textsuperscript{\protect\hyperlink{ref-11GtZ7icJ}{19}}) text pointers, but may have to rely on external file storage alternatives (such as local or cloud-hosting).
+Users may still version large files using Git Large File Storage\textsuperscript{\protect\hyperlink{ref-11GtZ7icJ}{19}} text pointers, but may have to rely on external file storage alternatives (such as local or cloud-hosting).
 
@@
 
-At least for aspects of a research project that involve writing code, a GitHub repository is a form of a laboratory notebook; when changes are made to files in a version controlled repository, the author of those changes makes a commit (\protect\hyperlink{definitions}{Box 1}) accompanied by a description of changes.
+At least for aspects of a research project that involve writing code, a GitHub repository is a form of a laboratory notebook; when changes are made to files in a version-controlled repository, the author of those changes makes a commit (\protect\hyperlink{definitions}{Box 1}) accompanied by a description of changes.
 Later, the entire history of commits and their commit messages are viewable and can be audited similar to a physical laboratory notebook\textsuperscript{\protect\hyperlink{ref-4ny1onB0}{8}}.
@@
 Student submissions are perhaps the most challenging component, but the new GitHub Classroom tool (\url{https://classroom.github.com}) allows instructors to host private assignments to be submitted collaboratively or individually as code or PDF files, and even build autograding tests.
-Although time-consuming to establish, using these features can integrate learning version control and GitHub with the learning course content, and thus boost students feelings of self-efficacy and confidence\textsuperscript{\protect\hyperlink{ref-dqrFjoSb}{26}}.
+Although time-consuming to establish, using these features can integrate learning version control and GitHub with the learning course content, and thus boost students' feelings of self-efficacy and confidence\textsuperscript{\protect\hyperlink{ref-dqrFjoSb}{26}}.
 
@@
 Those assumptions may obscure the utility of GitHub for tasks other than traditional data analysis and code development.
-However, we emphasize that there are opportunities for collaboration using GitHub by researchers of all skill levels or time constraints \protect\hyperlink{tbl:roles}{Table 2}; for example, project stakeholders can provide a list of use-cases or highlight important conceptual components of a project using GitHub's issues or discussions features.
+However, we emphasize that there are opportunities for collaboration using GitHub by researchers of all skill levels or time constraints (\protect\hyperlink{tbl:roles}{Table 2}); for example, project stakeholders can provide a list of use-cases or highlight important conceptual components of a project using GitHub's issues or discussions features.
 
@@
 Lastly, GitHub has both free and paid plans.
-When projects get highly collaborative they may have to pay for additional GitHub support.
-The acquisition of GitHub by Microsoft has led to some concerns over the future of free plans and several biodiversity data managers have begun to switch to Open Source Git services (\emph{e.g.}, Bitbucket and GitLab).
+When projects get highly collaborative, they may have to pay for additional GitHub support.
+The acquisition of GitHub by Microsoft has led to some concerns over the future of free plans and several biodiversity data managers have begun to switch to Open-Source Git services (\emph{e.g.}, Bitbucket and GitLab).
 At this point however, there is little practical difference for EEB researchers between the paid and free GitHub plans.
@@
 7.
-\textbf{Don't be afraid of trial and error.} One of the best ways to learn GitHub is the trial and error method.
+\textbf{Don't be afraid of trial-and-error.} One of the best ways to learn GitHub is the trial-and-error method.
 Learning from your own mistakes can be the better way to master your GitHub abilities.
@@
 The second column lists the platform for collaboration.
-The remaining columns indicate whether the platform for collaboration \label{tbl:compare}}\tabularnewline
+The remaining columns indicate whether the platform for collaboration includes certain features.
+\label{tbl:compare}}\tabularnewline
 \toprule

### 2022-07-14 manuscript.tex
Merge pull request #259 from SORTEE-Github-Hackathon/RCO-cover-letter-doi [ci skip]
This build is based on
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/956112ff108905503babe0eed04fa5ef9ddcd12b.

This commit was created by the following CI build and job:
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/956112ff108905503babe0eed04fa5ef9ddcd12b/checks
https://github.com/SORTEE-Github-Hackathon/manuscript/actions/runs/2673393113

@@
 This manuscript
-(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/1871a551b58e817b71a630c86cdd3fb8268d2ada/}{permalink})
+(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/956112ff108905503babe0eed04fa5ef9ddcd12b/}{permalink})
 was automatically generated
-from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/1871a551b58e817b71a630c86cdd3fb8268d2ada}{SORTEE-Github-Hackathon/manuscript@1871a55}
+from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/956112ff108905503babe0eed04fa5ef9ddcd12b}{SORTEE-Github-Hackathon/manuscript@956112f}
 on July 14, 2022.

### 2022-07-25 manuscript.tex
Merge pull request #264 from SORTEE-Github-Hackathon/phpb-post-preprint-modifications [ci skip]
This build is based on
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/56649aef2ef43f9ccca1da2bbf5f904c12f1699d.

This commit was created by the following CI build and job:
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/56649aef2ef43f9ccca1da2bbf5f904c12f1699d/checks
https://github.com/SORTEE-Github-Hackathon/manuscript/actions/runs/2735415467

@@
 This manuscript
-(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/956112ff108905503babe0eed04fa5ef9ddcd12b/}{permalink})
+(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/56649aef2ef43f9ccca1da2bbf5f904c12f1699d/}{permalink})
 was automatically generated
-from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/956112ff108905503babe0eed04fa5ef9ddcd12b}{SORTEE-Github-Hackathon/manuscript@956112f}
-on July 14, 2022.
+from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/56649aef2ef43f9ccca1da2bbf5f904c12f1699d}{SORTEE-Github-Hackathon/manuscript@56649ae}
+on July 25, 2022.
 
@@
 
-With over 73 million registered users as of 2022, GitHub is the most widely-used web platform for collaborating on computer code\textsuperscript{\protect\hyperlink{ref-nwCtHDCn}{6}}.
+With over 83 million registered users as of 2022, GitHub is the most widely-used web platform for collaborating on computer code\textsuperscript{\protect\hyperlink{ref-nwCtHDCn}{6}}.
 GitHub provides a simple but powerful web interface that allows users to participate in projects, contribute code, report and discuss code bugs, discover existing code and data, and publish new code.
@@
 This paper is the result of an academic hackathon held during the 2021 conference for the Society for Open, Reliable, and Transparent Ecology and Evolutionary Biology (SORTEE, \url{https://www.sortee.org}).
-We convened a group of around thirty researchers in EEB with varying levels of familiarity with using GitHub as part of their research projects to showcase and discuss how existing features can contribute to documentation and collaboration in EEB research.
+We convened around thirty researchers in EEB with varying levels of familiarity with the usage of GitHub in research projects to showcase and discuss how existing features can contribute to documentation and collaboration in EEB research.
 During the hackathon, we identified the need for a formal discussion on how EEB researchers can benefit from GitHub and its features.
@@
 
-\begin{longtable}[]{@{}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 0\tabcolsep) * \real{1.0000}}@{}}
+\begin{longtable}[]{@{}l@{}}
 \toprule
-\begin{minipage}[b]{\linewidth}\raggedright
-Glossary
-\end{minipage} \\
+Glossary \\
 \midrule
 \endhead
-\textbf{repository}: Commonly shortened to ``repo'', a repository is a collection of files (\emph{e.g.}, a directory) tracked by Git.
-Repositories are managed by an owner and can be listed as ``public'' where the repository will be visible to all GitHub users or ``private'', where the repository is visible only to authorized users.
-Repositories can be either ``local'' and saved on an individual's computer or ``remote'' and stored on the cloud via GitHub's web platform.
-\\
-\textbf{fork}: A fork is a copy of a \textbf{repository} hosted on GitHub.
+\bottomrule
+\end{longtable}
+
+\end{tablenos:no-prefix-table-caption}
+
+\textbar{}\textbf{repository}: A repository (commonly shortened to ``repo'') is a collection of files (\emph{e.g.}, a directory) tracked by Git.
+Repositories are managed by an owner and can be made either ``public'', to be visible to all GitHub users, or ``private'', to selected owner-specified users.
+Repositories can be either ``local'' and saved on an individual's computer or ``remote'' and stored on the cloud via GitHub's web platform.\textbar{}
+\textbar{}\textbf{fork}: A fork is a copy of a \textbf{repository} hosted on GitHub.
 If a repository is public, then anyone can make a fork.
 Even if they do not have access to \textbf{push} to the original repository, they can make a fork and edit it independently.
-Forks are linked to the original GitHub repository and ``upstream'' changes (\emph{i.e.}, those in the original repository) can be \textbf{merged} to keep the fork up to date with the original project.
-Changes made in the fork can be integrated into the original project via \textbf{pull requests}.
-\\
-\textbf{clone}: Cloning a \textbf{repository} is a way of making a local copy (\emph{i.e.}, on your computer) of a GitHub \textbf{repository}.
-If you have access to \textbf{push} to a \textbf{repository}, this can be a first step to contributing to a project.
-\\
-\textbf{branch}: Git workflow timelines or repositories are analogous to trees, with a main working project and diverging branches that are pointers to changes during the development process.
-A git branch is an alternative line of development for a project (\textbf{repository}).
+Forks are linked to the original GitHub repository and ``upstream'' changes (\emph{i.e.} those in the original repository) can be \textbf{merged} to keep the fork up to date with the original project.
+Changes made in the fork can be integrated into the original project via \textbf{pull requests}.\textbar{}
+\textbar{}\textbf{clone}: Cloning a \textbf{repository} is a way of making a local copy (\emph{i.e.}, on your computer) of a GitHub \textbf{repository}.
+If you have access to \textbf{push} to a \textbf{repository}, this can be a first step to contributing to a project.\textbar{}
+\textbar{}\textbf{branch}: Git workflow timelines or repositories are analogous to trees, with a main working project and diverging branches that are pointers to changes during the development process.
+A git branch is an alternative line of development for a project (repository).
 Branches allow users to add new features or modifications to the project without affecting the main part of the project.
@@
 Changes in a development branch can be \textbf{merged} into the main branch via \textbf{pull requests}.
-Branches can only be made by those who are given access to the project \textbf{repository}.
-\\
-\textbf{commit}: Commits are snapshots of the development of a project.
+Branches can only be made by those who are given access to the project \textbf{repository}.\textbar{}
+\textbar{}\textbf{commit}: Commits are snapshots of the development of a project.
 In Git, versions of files and directories are uniquely identified as ``commits'', allowing one to identify and track modifications line-by-line.
 Commits can include changes in multiple files and must include a brief commit message describing the changes made.
-A typical workflow is to make some related changes in files, add a commit message (\emph{e.g.}, ``generate and include fig1 in results''), and after several commits \textbf{push} those commits to the remote (\emph{i.e.}, cloud-based) GitHub \textbf{repository}.
-\\
-\textbf{push/pull}: When \textbf{commits} are made in a project locally, they must be synced with the remote GitHub repository by \textbf{pushing} them.
-Changes on a GitHub repository can then be \textbf{pulled} to keep your local version of the project up-to-date.
-\\
-\textbf{pull request}: A pull request is a request that the owner(s) of a GitHub repository integrate changes you've made on either a \textbf{branch} in the repository or in your own \textbf{fork}.
-When you initiate a pull request, you must provide a description of what changes were made.
-Some automated tests may be run and review may be required before integrating your changes into the main \textbf{branch}.
-\\
-\textbf{merge}: Combining \textbf{commits} from two different branches together into one \textbf{branch} \\
-\textbf{release}: At any point a release can be made on GitHub to mark a significant milestone in the progression of a \textbf{repository}.
-While this GitHub feature is designed with releases of new versions of code in mind (\emph{e.g.}, v1.0.0), it can also be used to create a snapshot of a repository at significant stages like submission, revision, and acceptance of an associated manuscript.
-\\
-\textbf{community}: A forum where GitHub users can ask for advice, offer solutions to questions, and share ideas (\url{https://github.community/}). \\
-\bottomrule
-\end{longtable}
-
-\end{tablenos:no-prefix-table-caption}
+A typical workflow is to make some related changes in files, add a commit message (\emph{e.g.} ``Generate and include results figure''), and after several commits \textbf{push} those commits to the remote (\emph{i.e.}, cloud-based) GitHub \textbf{repository}.\textbar{}
+\textbar{}\textbf{push and pull}: When \textbf{commits} are made in a project locally, they must be synced with the remote GitHub repository by \textbf{pushing} them.
+Changes on a GitHub repository can then be \textbf{pulled} to keep your local version of the project up-to-date with the remote.\textbar{}
+\textbar{}\textbf{pull request}: A pull request is a request for changes made on an individual's \textbf{branch} in the repository or in a user's \textbf{fork} to be merged to the repository.
+Pull requests contain a description of the changes made in a \textbf{branch} or \textbf{fork} alongside all code required for testing and reviewing by other users prior to merging into the repository.\textbar{}
+\textbar{}\textbf{merge}: Combining \textbf{commits} from two different branches together into one \textbf{branch}.\textbar{}
+\textbar{}\textbf{release}: At any point a release can be made on GitHub to mark a significant milestone in the progression of a \textbf{repository}.
+While this GitHub feature is designed with releases of new versions of code in mind (\emph{e.g.}, v1.0.0), it can also be used to create a snapshot of a repository at significant stages like pre-print, submission, revision, and acceptance of an associated manuscript.\textbar{}
+\textbar{}\textbf{community}: A forum where GitHub users can ask for advice, offer solutions to questions, and share ideas (\url{https://github.community/}).\textbar{}
 
@@
 Having copies of these files safely stored is essential to protect against accidental modifications or deletions.
-Many researchers begin using GitHub as a means to store (or backup) their research compendium\textsuperscript{\protect\hyperlink{ref-MwwMapRG}{17}} to a centralized, readily-available remote server (see \protect\hyperlink{definitions}{Box 1}).
+Many researchers begin using GitHub to store (or backup) their research compendium\textsuperscript{\protect\hyperlink{ref-MwwMapRG}{17}} to a centralized, readily-available remote server (see \protect\hyperlink{definitions}{Box 1}).
 A centralized research compendium stored in a version-controlled repository has the advantages of facilitating collaboration, integrating data and code archiving services, allowing file versions to be accessed and restored, and contributes to open science (see sections below).
@@
 Later, the entire history of commits and their commit messages are viewable and can be audited similar to a physical laboratory notebook\textsuperscript{\protect\hyperlink{ref-4ny1onB0}{8}}.
-GitHub issues (see project management section below) can be used to prioritize laboratory objectives and goals, as well as track any status updates.
+GitHub issues (see project management section below) can be used to prioritize laboratory objectives and goals, as well as track any progress updates.
 
@@
 Scripts, commit messages, and pull requests can be linked directly to issues, discussions, and projects providing a clear record of project workflow.
-
-Using GitHub for all project-related conversation and planning, rather than e-mail or messaging tools, makes it easier to keep track of progress throughout the lifespan of a project.
+Using GitHub for all project-related conversation and planning, rather than email or messaging tools, makes it easier to keep track of progress throughout the lifespan of a project.
 Unlike emails and messages which can get lost as more new tasks arise, GitHub issues are intentionally closed by repository administrators hiding the issue from view (closed issues remain accessible but not immediately visible).
@@
 
-We wrote this manuscript using Manubot\textsuperscript{\protect\hyperlink{ref-YuJbg3zO}{45}}, a workflow implemented in GitHub to automatically render manuscripts and automate bibliographical tasks.
+We wrote this manuscript using Manubot\textsuperscript{\protect\hyperlink{ref-Re6Eg2va}{45}}, a modifiable workflow implemented in GitHub to automatically render manuscripts and automate bibliographical tasks\textsuperscript{\protect\hyperlink{ref-YuJbg3zO}{46}}.
 Manubot uses GitHub's automation workflow, GitHub Actions, to combine and convert individual Markdown files into a single LaTeX document, which can then be converted to a Word or PDF document, and displayed as a webpage.
@@
 Additional GitHub Actions can be integrated with Manubot, such as ones creating figures or generating tables (\emph{e.g.}, \url{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/main/.github/workflows}).
-For more examples of manuscripts built via Manubot, see\textsuperscript{\protect\hyperlink{ref-YuJbg3zO}{45}}.
 
@@
 Certain journals or software development communities require submitted work or research code to be hosted on GitHub and their review processes make use of GitHub Issues (\emph{e.g.}, rOpenSci (\url{https://ropensci.org/software-review/}), Journal of Open Source Software (\url{https://joss.readthedocs.io/en/latest/submitting.html})).
-rOpenSci's efforts have resulted in many well-used R packages for ecology research including \texttt{rfishbase}\textsuperscript{\protect\hyperlink{ref-Xsdcv6q}{46}} and \texttt{taxize}\textsuperscript{\protect\hyperlink{ref-FVBWKkZu}{47}}.
+rOpenSci's efforts have resulted in many well-used R packages for ecology research including \texttt{rfishbase}\textsuperscript{\protect\hyperlink{ref-Xsdcv6q}{47}} and \texttt{taxize}\textsuperscript{\protect\hyperlink{ref-FVBWKkZu}{48}}.
 
@@
 Scientific publications often omit part of their intellectual and computational workflows, including the treatment of raw data and analytical steps (\emph{e.g.}, model assumption testing).
-Publishing data and reproducible workflows along with manuscripts can provide readers with all details about analytical steps and enable reproducing research experiments and results\textsuperscript{\protect\hyperlink{ref-NOgBWVAr}{48}}.
+Publishing data and reproducible workflows along with manuscripts can provide readers with all details about analytical steps and enable reproducing research experiments and results\textsuperscript{\protect\hyperlink{ref-NOgBWVAr}{49}}.
 In addition to storing data and code, GitHub repositories can provide a time-stamped (version controlled) preregistration of research plans and hypotheses.
@@
 GitHub can serve as a tool for open and tractable research development.
-Collaborators can directly interact with code and data, inspect for errors, and potentially identify scientific misconduct prior to manuscript submission (\emph{e.g.},\textsuperscript{\protect\hyperlink{ref-18PTmKJkq}{49}}).
+Collaborators can directly interact with code and data, inspect for errors, and potentially identify scientific misconduct prior to manuscript submission (\emph{e.g.},\textsuperscript{\protect\hyperlink{ref-18PTmKJkq}{50}}).
 Collaborators and readers are better positioned to discover erroneous or questionable findings if they have complete and transparent access to projects.
@@
 
-Projects in ecology and evolution often involve graduate students, research assistants, and post-doctoral fellows, who hold limited-term positions\textsuperscript{\protect\hyperlink{ref-D4C4k4ak}{50}}.
+Projects in ecology and evolution often involve graduate students, research assistants, and post-doctoral fellows, who hold limited-term positions\textsuperscript{\protect\hyperlink{ref-D4C4k4ak}{51}}.
 Without clear plans on project continuity, the research code and data management upkeep tends to fall off as researchers move on to new projects or to other institutions.
-Additionally, code and data can be difficult to access when kept only on personal devices\textsuperscript{\protect\hyperlink{ref-19kmNxiHc}{51}}.
-
-GitHub can facilitate project continuity among research code by making code handover easier\textsuperscript{\protect\hyperlink{ref-4ny1onB0}{8},\protect\hyperlink{ref-D4C4k4ak}{50}}.
-Through version control, the history of code and data from projects in ecology and evolution can be tracked and accessible to future laboratory members and collaborators\textsuperscript{\protect\hyperlink{ref-3DKwn1sY}{12}}.
-Repositories and organizations can have designated data and code owners (or more appropriate, stewards; see\textsuperscript{\protect\hyperlink{ref-iIEKCTLU}{40}},\textsuperscript{\protect\hyperlink{ref-s91uGRZ2}{52}}), who can also can change through time allowing for the transition of code from one cohort of researchers to the next.
-Other project collaborators can offer many contributions to repository design and development, and their active involvement can both aid authors ability to act as guarantors of the project, and the clarity and reproducibility of the project for future users.
+Additionally, code and data can be difficult to access when kept only on personal devices\textsuperscript{\protect\hyperlink{ref-19kmNxiHc}{52}}.
+
+GitHub can facilitate project continuity among research code by making code handover easier\textsuperscript{\protect\hyperlink{ref-4ny1onB0}{8},\protect\hyperlink{ref-D4C4k4ak}{51}}.
+Through version control, the history of code and data from projects in ecology and evolution can be tracked accessible to future laboratory members and collaborators\textsuperscript{\protect\hyperlink{ref-3DKwn1sY}{12}}.
+Repositories and organizations can have designated data and code owners (or more appropriate, stewards; see\textsuperscript{\protect\hyperlink{ref-iIEKCTLU}{40}},\textsuperscript{\protect\hyperlink{ref-s91uGRZ2}{53}}), who can also can change through time allowing for the transition of code between research cohorts.
+Other project collaborators can contribute to repository design and development, and their active involvement can both aid authors ability to act as guarantors of the project, and the clarity and reproducibility of the project for future users.
 In (Figure \ref{fig:github-diagram}), we highlight several elements of good repository structure, and the various ways that contributors may interact with them.
@@
 GitHub also allows users to describe and store information about software and code dependencies, ensuring that code can run using the same version of software as when it was initially developed.
-This can be achieved through the access of GitHub repositories containing the necessary releases of such software, or through the usage of actions with specific software versions in its automation tool, GitHub Actions.
+This can be achieved through the access of GitHub repositories containing the necessary releases of such software, or through the use of automated Github Actions with specific software versions.
 
@@
 This ensures repositories with sensitive information remain as restricted as needed, while others stay open and accessible to selected member groups.
-The organization structure also allows for easy issue tracking and discussions related to research content and progress.
-
-As an example, GitHub Organizations are particularly well-suited to house documents and projects within a laboratory, such as research compendia, codes of conduct, protocols, training documents, and other such documents that evolve collaboratively over time and are relevant to many colleagues.
-In this way, teams can have full ownership of repositories within an organization, while ensuring that these materials stay accessible to the laboratory after people have moved on or lost their copies of project data.
-This application extends to research centres, which may include several distinct projects that remain linked to institutions, such as the German Centre for Integrative Biodiversity Research (iDiv, \url{https://github.com/idiv-biodiversity}).
-The team organizing the hackathon which inspired this paper used a GitHub Organization (SORTEE-Github-Hackathon, \url{https://github.com/SORTEE-Github-Hackathon}) to keeping track of all materials as ideas developed and took shape in one virtual space.
-Organizations are also convenient for hosting learning materials, including lectures or workshops, such as the Québec Centre for Biodiversity Science R Workshop Series (QCBSRworkshops, \url{https://github.com/QCBSRworkshops}) or the University of Edinburgh's Coding Club (Coding Club, \url{https://github.com/ourcodingclub}), which may be updated by an ever-evolving group of contributors over time.
+The organization structure also allows for issue tracking and discussions related to research content and progress.
+
+As an example, GitHub Organizations are particularly well-suited to host documents and projects within a laboratory, such as research compendia, codes of conduct, protocols, training documents, and other relevant documents that evolve collaboratively over time.
+In this way, teams have full ownership of repositories within an organization, while ensuring that these materials stay accessible to the laboratory after people have moved on or when locally-stored data is lost.
+This application extends to research centres, which may include several distinct projects that remain linked to institutions {[}\emph{e.g.}, the German Centre for Integrative Biodiversity Research (iDiv, \url{https://github.com/idiv-biodiversity}){]}.
+The team organizing the hackathon which inspired this article used a GitHub Organization (SORTEE-Github-Hackathon, \url{https://github.com/SORTEE-Github-Hackathon}) to centralize the project development, from meeting notes to, ultimately, this manuscript.
+Organizations are also convenient for hosting learning materials, including lectures or workshops, such as the Québec Centre for Biodiversity Science R Workshop Series (QCBSRworkshops, \url{https://github.com/QCBSRworkshops}) or the University of Edinburgh's Coding Club (Coding Club, \url{https://github.com/ourcodingclub}), which may be continously updated by an ever-evolving group of contributors.
 
@@
 
-There have been many calls for researchers outside of the software development community to adopt GitHub to improve their collaborative research\textsuperscript{\protect\hyperlink{ref-10ghgV3S8}{3},\protect\hyperlink{ref-1Du6fzB8g}{39},\protect\hyperlink{ref-UsTxAq4f}{53}}.
-This call comes in light of both the continuous shift towards open-science and the increasing computational and data requirements in EEB.
+There have been many calls for researchers outside of the software development community to adopt GitHub to improve their collaborative research\textsuperscript{\protect\hyperlink{ref-10ghgV3S8}{3},\protect\hyperlink{ref-1Du6fzB8g}{39},\protect\hyperlink{ref-UsTxAq4f}{54}}.
+This call comes in light of the continuous shift towards open-science and the increasing computational and data requirements in EEB.
 Until now, resources and practical guidance on using GitHub within the EEB community have been dispersed in blog posts and video tutorials (\protect\hyperlink{tips}{Box 2}).
-These resources have been extremely useful for learning to use GitHub in our own work.
-We also feel that a collation of the main uses of GitHub in EEB into one medium, while adding on our personal perspectives, will be useful to the EEB community.
+These resources have been useful for learning to use GitHub in our own work.
+We expect that situating the main uses of GitHub in EEB into one medium, while adding on our personal perspectives, will be useful to the EEB community.
 
 In this paper, we described twelve ways that EEB researchers can leverage GitHub to enable more transparent and collaborative research (Figure \ref{fig:scatterblob}).
-Many of the examples are specifically meant for first-time GitHub users and can likely be adopted with just a little practice (storing data, creating virtual notebooks, making code citable).
-For example, storing code and data and making it citable involve creating a repository on GitHub, pushing code to the repository, and then going through the necessary steps (\emph{e.g.}, connecting a GitHub repository with Zenodo; see below) for creating a DOI.
-These actions are often covered in GitHub tutorials and require little effort to implement.
-On the other hand, some examples we described here, including course material development, web hosting, and delivery, may require a greater time commitment, but have the potential to make EEB research more open, accessible, and collaborative.
-Managing full research projects or laboratories on GitHub requires careful thought as to how to delegate tasks such as reviewing pull requests or creating issues.
-For example, collaboratively writing a paper using GitHub, as we have done here, may involve a learning curve for co-authors less familiar with the intricacies of GitHub, and requires overhead to set up the repository using GitHub Actions.
-Despite the many potential applications of GitHub to EEB research, we acknowledge that there will still be many times when researchers might look to other platforms for research collaboration.
+Most of these uses can be quickly integrated into the research practices of users (\emph{e.g.}, storing data, creating virtual notebooks, making code citable).
+Making stored data and code citable usually involves creating a repository on GitHub, pushing code and data, and then integrating a DOI minting service to the repository (\emph{e.g.}, with Zenodo; see below).
+On the other hand, some examples we described here, including course material development, web hosting, and delivery, require greater effort and time commitment, but have the potential to make EEB research more open, accessible, and collaborative.
+Managing full research projects or laboratories on GitHub require careful thought as to how to delegate tasks such as reviewing pull requests or creating issues.
+For example, collaboratively writing a paper using GitHub, as we have done here, involves a learning curve for co-authors less familiar with the intricacies of GitHub, requires overhead to set up the repository using GitHub Actions and the commitment from all co-authors to use GitHub when modifying and reviewing the text.
+Despite the many potential applications of GitHub to EEB research, we acknowledge that researchers might still look to other platforms for research collaboration.
 
@@
 First, real-time document editing is still best performed on other platforms (\emph{e.g.}, cloud-stored documents from Microsoft Word, Google Docs, hackMD (\url{https://hackmd.io/})).
-Second, operations that are dependent on other software might not be easily accomplished in GitHub, such as manipulating figures or tables.
-Although creating tables and figures can be achieved through code, users may choose other software to collaboratively brainstorm figures and tables (\emph{e.g.} Google Slides, Google Sheets).
+Second, operations that are dependent on other software might not be easily achievable in GitHub, such as manipulating figures or tables.
+Although creating tables and figures can be done through code, users may choose other software to collaboratively brainstorm figures and tables (\emph{e.g}.
+Google Slides, Google Sheets; but see GitHub Discussions).
 
@@
 Although GitHub has been available as a platform for more than a decade, its uptake among EEB researchers, especially as a tool for collaboration, has been slow.
+
 Here, we discuss four potential barriers to GitHub use in EEB.
@@
 First, there may be hesitation to independently adopting and learning a new tool.
-Institutional encouragement and instructional resources focused on researchers in ecology and evolution may be limited.
-When GitHub is taught in an EEB context, it is usually accompanying coursework in topics such as statistical programming.
+
+Institutional encouragement and instructional resources focused in researchers in ecology and evolution may be limited.
+When GitHub is taught within an EEB context, it usually accompanies coursework in topics such as statistical programming.
 It can be challenging to learn Git alongside scripting languages, statistical theory, and file system navigation, especially when many may be inexperienced with programming.
@@
 Those assumptions may obscure the utility of GitHub for tasks other than traditional data analysis and code development.
-However, we emphasize that there are opportunities for collaboration using GitHub by researchers of all skill levels or time constraints (\protect\hyperlink{tbl:roles}{Table 2}); for example, project stakeholders can provide a list of use-cases or highlight important conceptual components of a project using GitHub's issues or discussions features.
+However, we emphasize that there are opportunities for collaboration using GitHub by researchers of all skill levels or time constraints (\protect\hyperlink{tbl:roles}{Table 2}); for example, project stakeholders can provide a list of use-cases or highlight important conceptual components of a project using GitHub Issues or Discussions features.
 
@@
 This openness may add additional pressure to students and scientists learning to use the platform.
-We also note that large file storage is discouraged (and limited) on GitHub but add-ons do exist (\emph{e.g.}, \url{https://git-lfs.github.com/}) that permit data storage, and increasing integration between platforms (\emph{e.g.},\textsuperscript{\protect\hyperlink{ref-lx49NGto}{54}}) allows data to be stored away from GitHub and linked dynamically.
-We suspect a major additional barrier to EEB researchers is a distinct lack of GitHub help documents for non-English researchers in ecology and evolution, meaning that EEB researchers potentially miss the opportunity to fully understand the importance of version control, reproducibility, and other benefits of GitHub.
-
-Lastly, GitHub has both free and paid plans.
-When projects get highly collaborative, they may have to pay for additional GitHub support.
-The acquisition of GitHub by Microsoft has led to some concerns over the future of free plans and several biodiversity data managers have begun to switch to Open-Source Git services (\emph{e.g.}, Bitbucket and GitLab).
-At this point however, there is little practical difference for EEB researchers between the paid and free GitHub plans.
+File storage is size-limited on GitHub (but note that large files stored locally can still be versioned; see section ``Storing and sharing research compendia''), requiring the complementation of other tools to fully integration project files and GitHub repositories (\emph{e.g.},\textsuperscript{\protect\hyperlink{ref-lx49NGto}{55}}).
+A major additional barrier to EEB researchers is the lack language-specific resources for non-English speaking researchers working in ecology and evolution.
+Language is a well-known obstacle to international collaborative research progress and to widespread scientific knowledge\textsuperscript{see \protect\hyperlink{ref-cW7vGddM}{56}}.
+Non-English speaking EEB researchers can potentially miss opportunities to fully integrate version control, reproducibility, and other benefits of GitHub without language-inclusive contents.
+
+Lastly, fourth, GitHub may increase the distinctions between free and paid-for plans.
+When projects become highly collaborative, they may have to pay GitHub features, such for branch protections, multiple reviewers of pull requests and time in its automation tools.
+Currently, GitHub offers Education Packs (https://education.github.com/) to students and academics, which extends some paid features to the free plan.
+However, the acquisition of GitHub by Microsoft has raised concerns over the future of free plans, causing several biodiversity data managers to shift to alternative Open Source Git services (\emph{e.g.}, Bitbucket and GitLab).
 
@@
 \\
-2. \textbf{Consider taking free courses.} such as those from Software Carpentry\textsuperscript{\protect\hyperlink{ref-pjy75gHr}{55}} and sharing these courses with your lab members or colleagues. \\
+2. \textbf{Consider taking free courses.} such as those from Software Carpentry\textsuperscript{\protect\hyperlink{ref-pjy75gHr}{57}} and sharing these courses with your lab members or colleagues. \\
 3.
@@
 6.
-\textbf{The Jenny Bryan universe of GitHub material.} provides a thorough and accessible introduction for a multitude of research-related uses for GitHub, and includes a book\textsuperscript{\protect\hyperlink{ref-ZvrOcg9w}{56}}, statistics course\textsuperscript{\protect\hyperlink{ref-6CMMeSeD}{57}} and academic article\textsuperscript{\protect\hyperlink{ref-RVetqmsg}{7}}.
+\textbf{The Jenny Bryan universe of GitHub material.} provides a thorough and accessible introduction for a multitude of research-related uses for GitHub, and includes a book\textsuperscript{\protect\hyperlink{ref-ZvrOcg9w}{58}}, statistics course\textsuperscript{\protect\hyperlink{ref-6CMMeSeD}{59}} and academic article\textsuperscript{\protect\hyperlink{ref-RVetqmsg}{7}}.
 \\
@@
 
-We provide twelve practical ways that ecologists and evolutionary biologists can adopt GitHub to improve their research workflow.
-We provide definitions (\protect\hyperlink{definitions}{Box 1}) and types of users (Figure \ref{fig:github-diagram}) to help researchers identify and prioritize the skills and tools to learn first.
+We provide twelve practical ways that ecologists and evolutionary biologists can adopt GitHub to improve their research workflow and make it more open and reproducible.
+We provide definitions (\protect\hyperlink{definitions}{Box 1}) and types of users (Figure \ref{fig:github-diagram}) to help researchers identify and prioritize the skills and tools to learn and apply.
 We highlight tools providing high collaborative potential (\emph{e.g.}, open science discussion, collaborative code editing) to more individual focused (\emph{e.g.}, storing code and data, building a website).
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-Re6Eg2va}{}}%
+\CSLLeftMargin{45. }
+\CSLRightInline{Manubot - Manuscripts, open and automated. \url{https://manubot.org}.}
+
 \leavevmode\vadjust pre{\hypertarget{ref-YuJbg3zO}{}}%
-\CSLLeftMargin{45. }
+\CSLLeftMargin{46. }
 \CSLRightInline{Himmelstein, D. S. \emph{et al.} \href{https://doi.org/10.1371/journal.pcbi.1007128}{Open collaborative writing with Manubot}. \emph{PLoS Comput Biol} \textbf{15}, e1007128 (2019).}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Xsdcv6q}{}}%
-\CSLLeftMargin{46. }
+\CSLLeftMargin{47. }
 \CSLRightInline{Boettiger, C., Lang, D.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-FVBWKkZu}{}}%
-\CSLLeftMargin{47. }
+\CSLLeftMargin{48. }
 \CSLRightInline{Chamberlain, S. A. \& Szöcs, E. \href{https://doi.org/10.12688/f1000research.2-191.v2}{taxize: taxonomic search and retrieval in R}. \emph{F1000Res} \textbf{2}, 191 (2013).}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-NOgBWVAr}{}}%
-\CSLLeftMargin{48. }
+\CSLLeftMargin{49. }
 \CSLRightInline{Culina, A., van den Berg, I., Evans, S.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-18PTmKJkq}{}}%
-\CSLLeftMargin{49. }
+\CSLLeftMargin{50. }
 \CSLRightInline{January 18, P.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-D4C4k4ak}{}}%
-\CSLLeftMargin{50. }
+\CSLLeftMargin{51. }
 \CSLRightInline{Fehr, J., Himpe, C., Rave, S. \& Saak, J. \href{https://doi.org/10.5334/jors.307}{Sustainable Research Software Hand-Over}. \emph{JORS} \textbf{9}, 5 (2021).}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-19kmNxiHc}{}}%
-\CSLLeftMargin{51. }
+\CSLLeftMargin{52. }
 \CSLRightInline{Vines, Timothy~H.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-s91uGRZ2}{}}%
-\CSLLeftMargin{52. }
+\CSLLeftMargin{53. }
 \CSLRightInline{About code owners.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-UsTxAq4f}{}}%
-\CSLLeftMargin{53. }
+\CSLLeftMargin{54. }
 \CSLRightInline{Anbaroğlu, B. \href{https://doi.org/10.1111/tgis.12810}{A collaborative GIS programming course using GitHub Classroom}. \emph{Transactions in GIS} \textbf{25}, 3132--3158 (2021).}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-lx49NGto}{}}%
-\CSLLeftMargin{54. }
+\CSLLeftMargin{55. }
 \CSLRightInline{Connect GitHub to a Project - OSF Support. \url{https://help.osf.io/article/211-connect-github-to-a-project}.}
 
+\leavevmode\vadjust pre{\hypertarget{ref-cW7vGddM}{}}%
+\CSLLeftMargin{56. }
+\CSLRightInline{Khelifa, R., Amano, T.
+\& Nuñez, M.
+A.
+\href{https://doi.org/10.1016/j.tree.2021.11.003}{A solution for breaking the language barrier}.
+\emph{Trends in Ecology \&amp; Evolution} \textbf{37}, 109--112 (2022).}
+
 \leavevmode\vadjust pre{\hypertarget{ref-pjy75gHr}{}}%
-\CSLLeftMargin{55. }
+\CSLLeftMargin{57. }
 \CSLRightInline{Madicken Munk \emph{et al.} swcarpentry/git-novice: Software Carpentry: Version Control with Git, June 2019. at \url{https://doi.org/10.5281/zenodo.3264950} (2019).}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-ZvrOcg9w}{}}%
-\CSLLeftMargin{56. }
+\CSLLeftMargin{58. }
 \CSLRightInline{Hester, J. B., the STAT 545 TAs, Jim. \emph{\href{https://happygitwithr.com/}{Let's Git started \textbar{} Happy Git and GitHub for the useR}}.}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-6CMMeSeD}{}}%
-\CSLLeftMargin{57. }
+\CSLLeftMargin{59. }
 \CSLRightInline{Bryan, J. \& TAs, T. S. 545. \emph{\href{https://stat545.com/}{STAT 545}}.}

### 2022-07-26 R/scatterblob.Rmd
Adding Automation as use case to the figure

@@
 title: "\\textbf{\\textsc{Supplementary Material} \\linebreak \\linebreak Not just for programmers: How GitHub can accelerate collaborative and reproducible research in ecology and evolution \\linebreak \\linebreak Methods to create \\textsl{the scatterblob} figure}"
-# output: html_document
-output: pdf_document
+output: html_document
+# output: pdf_document
 ---
@@
 
-The column _`r column_names[6]`_ corresponds to the degree of difficulty that was perceived by the authors when assembling the data, based on personal experience.
+The column *`r column_names[6]`* corresponds to the degree of difficulty that was perceived by the authors when assembling the data, based on personal experience.
 We quickly realized this varied greatly across authors, and that this variation seemed to depend on which github tools were previously known or mastered by the authors.
 
-The columns tagged as _Cognitive load -_ showcase a different way to assess technical difficulty of GitHub uses, measured as cognitive load (explained in the next section).
+The columns tagged as *Cognitive load -* showcase a different way to assess technical difficulty of GitHub uses, measured as cognitive load (explained in the next section).
 
-The columns tagged as _degree of collaboration_ showcase the span of collaboration that can be achieved with each tool, as perceived by the authors.
+The columns tagged as *degree of collaboration* showcase the span of collaboration that can be achieved with each tool, as perceived by the authors.
 
@@
 The sum of values across columns provides a measure of cognitive load required for a user that is a "GitHub beginner" to implement any GitHub use.
-The column _`r column_names[3]`_ reflects this number.
+The column *`r column_names[3]`* reflects this number.
 4.
 As many GitHub uses tied with the same cognitive load value, we resourced to perceived difficulty to break ties and avoid overlap of uses in the figure, mainly to improve visualization of the data.
-The column _`r column_names[5]`_ shows this adjustment.
+The column *`r column_names[5]`* shows this adjustment.
 5.
-Finally, we ordered the GitHub uses in increasing order following _`r column_names[5]`_, and assigned a sequential value of cognitive load, from 1 to _maximum number of GitHub uses_.
-This is column _`r column_names[4]`_
+Finally, we ordered the GitHub uses in increasing order following *`r column_names[5]`*, and assigned a sequential value of cognitive load, from 1 to *maximum number of GitHub uses*.
+This is column *`r column_names[4]`*
 
-## Reading the data csv file:
+## Reading the data CSV file:
 
@@
 scatterblob_data$y_seq <- scatterblob_data$`Cognitive load - sequential`
-my_data <- scatterblob_data[1:12,c("Ways to use GitHub","y_seq", "y_real", "x1", "x2")]
+my_data <- scatterblob_data[1:13,c("Ways to use GitHub","y_seq", "y_real", "x1", "x2")]
 my_data
@@
 ## Plotting the data
+
 ```{r}
@@
 ```{r}
-my_colors <- some_colors1[c(3:4,
-                           8,10,12,
-                           20,21,22,23,24,
-                           28,30)]
+my_colors <- some_colors1[c(2:3, 5,
+                           8, 10, 12,
+                           20, 21, 22, 23, 24,
+                           28, 30)]
+
+plot(1:length(my_colors), 
+     1:length(my_colors), 
+     col = my_colors, pch = 8)
+
 ```
@@
 ###############################################################
-#plot_format <- "pdf"
+# plot_format <- "pdf"
 # plot_format <- "svg"
@@
 plot(x = c(0.5, 5.5),
-     y = c(1.75, 9.75),
+     y = c(1.75, 10.75),
      xlab = "",
@@
 ```
+
 ![Degree of collaboration VS technical difficulty (real, non-overlapping)](../content/images/scatterblob_0.png)
@@
 
-We tried different color palettes from two diffrent R packages: [viridis](https://cran.r-project.org/web/packages/viridis/vignettes/intro-to-viridis.html#the-color-scales) and [wesanderson](https://github.com/karthik/wesanderson#readme):
+We tried different color palettes from two different R packages: [viridis](https://cran.r-project.org/web/packages/viridis/vignettes/intro-to-viridis.html#the-color-scales) and [wesanderson](https://github.com/karthik/wesanderson#readme):
 
@@
 ```{r}
-my_colors <- some_colors3[c(5,15,
-                           26,28,30,
-                           68,72,76,80,84,
-                           94,100)]
+my_colors <- some_colors3[c(2, 5, 15,
+                           26, 28, 30,
+                           68, 72, 76, 80, 84,
+                           94, 100)]
 plot_name <- "scatterblob_1-viridis-turbo"
-#my_colors <- some_colors4[round(my_data$y_real*10)-20]
-#plot_name <- "scatterblob_1-zissou1"
+# my_colors <- some_colors4[round(my_data$y_real*10)-20]
+# plot_name <- "scatterblob_1-zissou1"
 # my_colors <- some_colors5[round(my_data$y_real*10)-20]
@@
 plot(x = c(0.5, 5.5),
-     y = c(0.4, 12.5),
+     y = c(0.4, 14),
      xlab = "",
@@
      tck = 0.02)
-title(ylab="Technical Difficulty", line=4, cex.lab=1)
-title(xlab="Degree of Collaboration", line= 3.5, cex.lab=1)
+
+title(ylab = "Technical Difficulty", 
+      line = 4, 
+      cex.lab = 1)
+
+title(xlab = "Degree of Collaboration", 
+      line = 3.5, 
+      cex.lab = 1)
 ###############################################################
@@
 text(x = 0.2,
-     y = c(0, 3, 6, 8.6, 12),
+     y = seq(1, 13, length.out = 5),
      cex = 0.7,

### 2022-07-26 R/scatterblob.Rmd
Lowercase "websites" in "Academic Websites"  and extends it to Personal

@@
 title: "\\textbf{\\textsc{Supplementary Material} \\linebreak \\linebreak Not just for programmers: How GitHub can accelerate collaborative and reproducible research in ecology and evolution \\linebreak \\linebreak Methods to create \\textsl{the scatterblob} figure}"
-output: html_document
-# output: pdf_document
+output: 
+  html_document
 ---

### 2022-07-26 manuscript.tex
Merge pull request #265 from SORTEE-Github-Hackathon/phpb-automation-use-cases [ci skip]
This build is based on
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/0aaaf3e6a685b4c96e2115ee2f709dab93a233f8.

This commit was created by the following CI build and job:
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/0aaaf3e6a685b4c96e2115ee2f709dab93a233f8/checks
https://github.com/SORTEE-Github-Hackathon/manuscript/actions/runs/2742885620

@@
 This manuscript
-(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/56649aef2ef43f9ccca1da2bbf5f904c12f1699d/}{permalink})
+(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/0aaaf3e6a685b4c96e2115ee2f709dab93a233f8/}{permalink})
 was automatically generated
-from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/56649aef2ef43f9ccca1da2bbf5f904c12f1699d}{SORTEE-Github-Hackathon/manuscript@56649ae}
-on July 25, 2022.
+from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/0aaaf3e6a685b4c96e2115ee2f709dab93a233f8}{SORTEE-Github-Hackathon/manuscript@0aaaf3e}
+on July 26, 2022.
 
@@
 
-Despite these benefits, the use of GitHub by EEB researchers is not widespread due to the lack of domain-specific information and guidelines.
-To help EEB researchers adopt useful features from GitHub in their own workflows, we review twelve practical ways to use the platform.
+Despite these benefits, the use of GitHub in ecology and evolution is not widespread.
+To help researchers in ecology and evolution adopt useful features from GitHub in their own workflows, we review thirteen practical ways to use the platform.
 We outline features ranging from low to high technical difficulty: storing code, managing projects, coding collaboratively, conducting peer review, and writing a manuscript.
@@
 With over 83 million registered users as of 2022, GitHub is the most widely-used web platform for collaborating on computer code\textsuperscript{\protect\hyperlink{ref-nwCtHDCn}{6}}.
-GitHub provides a simple but powerful web interface that allows users to participate in projects, contribute code, report and discuss code bugs, discover existing code and data, and publish new code.
+GitHub provides a simple but powerful web interface that allows users to participate in projects by contributing, modifying and discussing existing code, reporting bugs, discovering code and data, and publishing new code.
 Through version control, users have a detailed, chronological record of the files and directories stored in their repositories\textsuperscript{\protect\hyperlink{ref-RVetqmsg}{7}} (see \protect\hyperlink{definitions}{Box 1}).
-This workflow provides a strong and clear advantage over sending files back-and-forth (\emph{e.g.} via email), a process that can become challenging and time-consuming in long-term and collaborative projects\textsuperscript{\protect\hyperlink{ref-4ny1onB0}{8}}.
+This workflow provides a strong and clear advantage over sending files back-and-forth (\emph{e.g.}, via email), a process that can become challenging and time-consuming in long-term and collaborative projects\textsuperscript{\protect\hyperlink{ref-4ny1onB0}{8}}.
 Through its combination of version control and collaborative features, GitHub facilitates open source code alongside collaborative development\textsuperscript{\protect\hyperlink{ref-kEX5dgzK}{9}}.
@@
 We convened around thirty researchers in EEB with varying levels of familiarity with the usage of GitHub in research projects to showcase and discuss how existing features can contribute to documentation and collaboration in EEB research.
-During the hackathon, we identified the need for a formal discussion on how EEB researchers can benefit from GitHub and its features.
-Here, we outline twelve practical ways that EEB researchers can use GitHub features for more collaborative, transparent, and reproducible science.
+During the hackathon, we identified the need for formal discussions on how EEB researchers can benefit from GitHub and its features.
+Here, we outline thirteen practical ways that EEB researchers can use GitHub features for more collaborative, transparent, and reproducible science.
 We also provide critical perspectives on features that could be improved and catered towards research development.
@@
 
-\begin{longtable}[]{@{}l@{}}
+\begin{longtable}[]{@{}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 0\tabcolsep) * \real{1.0000}}@{}}
 \toprule
-Glossary \\
+\begin{minipage}[b]{\linewidth}\raggedright
+Glossary
+\end{minipage} \\
 \midrule
 \endhead
-\bottomrule
-\end{longtable}
-
-\end{tablenos:no-prefix-table-caption}
-
-\textbar{}\textbf{repository}: A repository (commonly shortened to ``repo'') is a collection of files (\emph{e.g.}, a directory) tracked by Git.
+\textbf{repository}: A repository (commonly shortened to ``repo'') is a collection of files (\emph{e.g.}, a directory) tracked by Git.
 Repositories are managed by an owner and can be made either ``public'', to be visible to all GitHub users, or ``private'', to selected owner-specified users.
-Repositories can be either ``local'' and saved on an individual's computer or ``remote'' and stored on the cloud via GitHub's web platform.\textbar{}
-\textbar{}\textbf{fork}: A fork is a copy of a \textbf{repository} hosted on GitHub.
+Repositories can be either ``local'' and saved on an individual's computer or ``remote'' and stored on the cloud via GitHub's web platform.
+\\
+\textbf{fork}: A fork is a copy of a \textbf{repository} hosted on GitHub.
 If a repository is public, then anyone can make a fork.
 Even if they do not have access to \textbf{push} to the original repository, they can make a fork and edit it independently.
-Forks are linked to the original GitHub repository and ``upstream'' changes (\emph{i.e.} those in the original repository) can be \textbf{merged} to keep the fork up to date with the original project.
-Changes made in the fork can be integrated into the original project via \textbf{pull requests}.\textbar{}
-\textbar{}\textbf{clone}: Cloning a \textbf{repository} is a way of making a local copy (\emph{i.e.}, on your computer) of a GitHub \textbf{repository}.
-If you have access to \textbf{push} to a \textbf{repository}, this can be a first step to contributing to a project.\textbar{}
-\textbar{}\textbf{branch}: Git workflow timelines or repositories are analogous to trees, with a main working project and diverging branches that are pointers to changes during the development process.
+Forks are linked to the original GitHub repository and ``upstream'' changes (\emph{i.e.}, those in the original repository) can be \textbf{merged} to keep the fork up-to-date with the original project.
+Changes made in the fork can be integrated into the original project via \textbf{pull requests}.
+\\
+\textbf{clone}: Cloning a \textbf{repository} is a way of making a local copy (\emph{i.e.}, on your computer) of a GitHub \textbf{repository}.
+If you have access to \textbf{push} to a \textbf{repository}, this can be a first step to contributing to a project.
+\\
+\textbf{branch}: Git workflow timelines or repositories are analogous to trees, with a main working project and diverging branches that are pointers to changes during the development process.
 A git branch is an alternative line of development for a project (repository).
@@
 Changes in a development branch can be \textbf{merged} into the main branch via \textbf{pull requests}.
-Branches can only be made by those who are given access to the project \textbf{repository}.\textbar{}
-\textbar{}\textbf{commit}: Commits are snapshots of the development of a project.
+Branches can only be made by those who are given access to the project \textbf{repository}.
+\\
+\textbf{commit}: Commits are snapshots of the development of a project.
 In Git, versions of files and directories are uniquely identified as ``commits'', allowing one to identify and track modifications line-by-line.
 Commits can include changes in multiple files and must include a brief commit message describing the changes made.
-A typical workflow is to make some related changes in files, add a commit message (\emph{e.g.} ``Generate and include results figure''), and after several commits \textbf{push} those commits to the remote (\emph{i.e.}, cloud-based) GitHub \textbf{repository}.\textbar{}
-\textbar{}\textbf{push and pull}: When \textbf{commits} are made in a project locally, they must be synced with the remote GitHub repository by \textbf{pushing} them.
-Changes on a GitHub repository can then be \textbf{pulled} to keep your local version of the project up-to-date with the remote.\textbar{}
-\textbar{}\textbf{pull request}: A pull request is a request for changes made on an individual's \textbf{branch} in the repository or in a user's \textbf{fork} to be merged to the repository.
-Pull requests contain a description of the changes made in a \textbf{branch} or \textbf{fork} alongside all code required for testing and reviewing by other users prior to merging into the repository.\textbar{}
-\textbar{}\textbf{merge}: Combining \textbf{commits} from two different branches together into one \textbf{branch}.\textbar{}
-\textbar{}\textbf{release}: At any point a release can be made on GitHub to mark a significant milestone in the progression of a \textbf{repository}.
-While this GitHub feature is designed with releases of new versions of code in mind (\emph{e.g.}, v1.0.0), it can also be used to create a snapshot of a repository at significant stages like pre-print, submission, revision, and acceptance of an associated manuscript.\textbar{}
-\textbar{}\textbf{community}: A forum where GitHub users can ask for advice, offer solutions to questions, and share ideas (\url{https://github.community/}).\textbar{}
-
-\hypertarget{twelve-practical-ways-github-can-accelerate-research-in-ecology-and-evolution}{%
-\subsection{Twelve practical ways GitHub can accelerate research in ecology and evolution}\label{twelve-practical-ways-github-can-accelerate-research-in-ecology-and-evolution}}
+A typical workflow is to make some related changes in files, add a commit message (\emph{e.g.} ``Generate and include results figure''), and after several commits \textbf{push} those commits to the remote (\emph{i.e.}, cloud-based) GitHub \textbf{repository}.
+\\
+\textbf{push and pull}: When \textbf{commits} are made in a project locally, they must be synced with the remote GitHub repository by \textbf{pushing} them.
+Changes on a GitHub repository can then be \textbf{pulled} to keep your local version of the project up-to-date with the remote.
+\\
+\textbf{pull request}: A pull request is a request for changes made on an individual's \textbf{branch} in the repository or in a user's \textbf{fork} to be merged to the repository.
+Pull requests contain a description of the changes alongside all code required for testing and review by other users prior to being merged into the repository.
+\\
+\textbf{merge}: Combining \textbf{commits} from two different branches together into one \textbf{branch}. \\
+\textbf{release}: At any point a release can be made on GitHub to mark a significant milestone in the progression of a \textbf{repository}.
+While this GitHub feature is designed with releases of new versions of code in mind (\emph{e.g.}, v1.0.0), it can also be used to create a snapshot of a repository at significant stages like pre-print, submission, revision, and acceptance of an associated manuscript.
+\\
+\textbf{community}: A forum where GitHub users can ask for advice, offer solutions to questions, and share ideas (\url{https://github.community/}). \\
+\bottomrule
+\end{longtable}
+
+\end{tablenos:no-prefix-table-caption}
+
+\hypertarget{thirteen-practical-ways-github-can-accelerate-research-in-ecology-and-evolution}{%
+\subsection{Thirteen practical ways GitHub can accelerate research in ecology and evolution}\label{thirteen-practical-ways-github-can-accelerate-research-in-ecology-and-evolution}}
 
@@
 
-This transparency can be extended beyond coauthors to the entire scientific community and to the public.
+This transparency can be extended beyond co-authors to the entire scientific community and to the public.
 Supplying code for (novel) methods that are proposed or used reduces barriers to knowledge, improving the ability of others to build on existing work.
@@
 
+\hypertarget{automation}{%
+\subsubsection{Automation}\label{automation}}
+
+Automation has a strong potential to expand the scale and pace of research in ecology and evolution\textsuperscript{\protect\hyperlink{ref-cfgXxgt1}{54}}.
+Automation frameworks can streamline many stages of the scientific process, including automated data collection and data validation\textsuperscript{\protect\hyperlink{ref-lXvpQxeN}{56}}, automated data analysis\textsuperscript{\emph{e.g.}, \protect\hyperlink{ref-Qh7xTLwz}{57}}, automated archiving and deployment of data, code and reports\textsuperscript{\emph{e.g.}, this manuscript, \protect\hyperlink{ref-SirQKFIz}{58}}.
+In this context, small modifications to code and data can be frequently committed and automatically tested, as in continuous integration and continuous deployment practices\textsuperscript{\protect\hyperlink{ref-1Ep9EJL6y}{59}}.
+This allows for early detection and correction of errors, potentially improving confidence in scientific development by minimizing software errors\textsuperscript{see \protect\hyperlink{ref-ufw0ZdnI}{60}}.
+In addition to increasing scientific rigor and confidence in ecological software\textsuperscript{\protect\hyperlink{ref-12103x16N}{61}}, automation can help advance more rapidly sharing ecological data and making sure the data are high quality\textsuperscript{\protect\hyperlink{ref-rTbinQMj}{62}}.
+Integrating automation workflows has been highly encouraged in areas of EEB, including predictive ecology\textsuperscript{\protect\hyperlink{ref-mmCOSRfr}{63}}, long-term ecological studies\textsuperscript{\protect\hyperlink{ref-1CJo8lo2v}{64},\protect\hyperlink{ref-RxK4CmfR}{65}}, and management of species at risk information\textsuperscript{\protect\hyperlink{ref-kZzfmBNu}{66}}.
+
+Automation can be integrated into GitHub repositories through the GitHub Actions feature\textsuperscript{\protect\hyperlink{ref-NUXbp429}{67}}, or through alternative automation systems (\emph{e.g.}, Circle CI\textsuperscript{\protect\hyperlink{ref-T03Api6e}{68}}, Travis CI\textsuperscript{\protect\hyperlink{ref-YeFSbfFV}{69}}).
+Users can set up workflows associated with their repositories that are triggered by events (\emph{e.g.}, push, pull request or at specified times) for remote servers to perform user-specified steps and actions.
+These actions are highly configurable and have numerous applications, such as automatically running analyses and creating figures when data or code are updated, incorporating changes to websites or applications, testing modifications to software (\emph{e.g.}, R or Python libraries).
+Action workflows can be found in GitHub's Marketplace (https://github.com/marketplace?type=actions) or, alternatively, in open user repositories.
+
 \hypertarget{github-organizations}{%
@@
 As an example, GitHub Organizations are particularly well-suited to host documents and projects within a laboratory, such as research compendia, codes of conduct, protocols, training documents, and other relevant documents that evolve collaboratively over time.
-In this way, teams have full ownership of repositories within an organization, while ensuring that these materials stay accessible to the laboratory after people have moved on or when locally-stored data is lost.
+In this way, teams have full ownership of repositories within an organization, while ensuring that these materials stay accessible to the laboratory after people have moved on or when locally-stored data are lost.
 This application extends to research centres, which may include several distinct projects that remain linked to institutions {[}\emph{e.g.}, the German Centre for Integrative Biodiversity Research (iDiv, \url{https://github.com/idiv-biodiversity}){]}.
@@
 
-There have been many calls for researchers outside of the software development community to adopt GitHub to improve their collaborative research\textsuperscript{\protect\hyperlink{ref-10ghgV3S8}{3},\protect\hyperlink{ref-1Du6fzB8g}{39},\protect\hyperlink{ref-UsTxAq4f}{54}}.
+There have been many calls for researchers outside of the software development community to adopt GitHub to improve their collaborative research\textsuperscript{\protect\hyperlink{ref-10ghgV3S8}{3},\protect\hyperlink{ref-1Du6fzB8g}{39},\protect\hyperlink{ref-UsTxAq4f}{70}}.
 This call comes in light of the continuous shift towards open-science and the increasing computational and data requirements in EEB.
@@
 
-In this paper, we described twelve ways that EEB researchers can leverage GitHub to enable more transparent and collaborative research (Figure \ref{fig:scatterblob}).
+The thirteen use cases we described here can leverage GitHub to enable more transparent and collaborative research in ecology and evolution (Figure \ref{fig:scatterblob}).
 Most of these uses can be quickly integrated into the research practices of users (\emph{e.g.}, storing data, creating virtual notebooks, making code citable).
 Making stored data and code citable usually involves creating a repository on GitHub, pushing code and data, and then integrating a DOI minting service to the repository (\emph{e.g.}, with Zenodo; see below).
-On the other hand, some examples we described here, including course material development, web hosting, and delivery, require greater effort and time commitment, but have the potential to make EEB research more open, accessible, and collaborative.
+On the other hand, some examples we described here, including course material development, web hosting, and automation, require greater effort and time commitment, but have the potential to make EEB research more open, accessible, and collaborative.
 Managing full research projects or laboratories on GitHub require careful thought as to how to delegate tasks such as reviewing pull requests or creating issues.
-For example, collaboratively writing a paper using GitHub, as we have done here, involves a learning curve for co-authors less familiar with the intricacies of GitHub, requires overhead to set up the repository using GitHub Actions and the commitment from all co-authors to use GitHub when modifying and reviewing the text.
-Despite the many potential applications of GitHub to EEB research, we acknowledge that researchers might still look to other platforms for research collaboration.
+For example, collaboratively authoring a paper using GitHub, as we have done here, involves a learning curve for co-authors less familiar with the intricacies of GitHub, requires overhead to set up the automation framework through GitHub Actions, and especially, the commitment from all co-authors to use GitHub when modifying and reviewing the text.
+Despite the potential applications of GitHub to EEB research, we acknowledge that researchers might still look to other platforms for research collaboration.
 
@@
 
-Institutional encouragement and instructional resources focused in researchers in ecology and evolution may be limited.
+Institutional encouragement and instructional resources focused on researchers in ecology and evolution may be limited.
 When GitHub is taught within an EEB context, it usually accompanies coursework in topics such as statistical programming.
@@
 
-Second, while many EEB researchers take advantage of GitHub for individual use, collaborative use may lag due to how researchers traditionally divide labor within projects.
+Second, while EEB researchers individually use GitHub, collaborative use may lag due to researchers traditionally dividing labor within projects.
 Despite broad utility, GitHub remains a tool predominantly used by computer scientists and software developers.
-EEB researchers may take the view that GitHub is a platform that only needs to be used by individuals writing code, and may silo those aspects of projects to a single individual.
+EEB researchers may take the view that GitHub is a platform that only needs to be used by individuals writing code and may silo those aspects of projects to a single individual.
 Those assumptions may obscure the utility of GitHub for tasks other than traditional data analysis and code development.
@@
 This openness may add additional pressure to students and scientists learning to use the platform.
-File storage is size-limited on GitHub (but note that large files stored locally can still be versioned; see section ``Storing and sharing research compendia''), requiring the complementation of other tools to fully integration project files and GitHub repositories (\emph{e.g.},\textsuperscript{\protect\hyperlink{ref-lx49NGto}{55}}).
+File storage is size-limited on GitHub (but note that large files stored locally can still be versioned; see section ``Storing and sharing research compendia''), requiring the complementation of other tools to fully integration project files and GitHub repositories (\emph{e.g.},\textsuperscript{\protect\hyperlink{ref-lx49NGto}{71}}).
 A major additional barrier to EEB researchers is the lack language-specific resources for non-English speaking researchers working in ecology and evolution.
-Language is a well-known obstacle to international collaborative research progress and to widespread scientific knowledge\textsuperscript{see \protect\hyperlink{ref-cW7vGddM}{56}}.
+Language is a well-known obstacle to international collaborative research progress and to widespread scientific knowledge\textsuperscript{see \protect\hyperlink{ref-cW7vGddM}{72}}.
 Non-English speaking EEB researchers can potentially miss opportunities to fully integrate version control, reproducibility, and other benefits of GitHub without language-inclusive contents.
@@
 \\
-2. \textbf{Consider taking free courses.} such as those from Software Carpentry\textsuperscript{\protect\hyperlink{ref-pjy75gHr}{57}} and sharing these courses with your lab members or colleagues. \\
+2. \textbf{Consider taking free courses}, such as those from Software Carpentry\textsuperscript{\protect\hyperlink{ref-pjy75gHr}{73}}, and sharing these courses with your lab members or colleagues. \\
 3.
-\textbf{Take advantage of GitHub as an asynchronous working tool for team-based projects.} See the repository for this paper (\url{https://github.com/SORTEE-Github-Hackathon/manuscript}) as an example of a collaborative manuscript that includes discussions, issues, and a website via GitHub.
+\textbf{Take advantage of GitHub as an asynchronous working tool for team-based projects.} See the repository for this paper (\url{https://github.com/SORTEE-Github-Hackathon/manuscript}) as an example of a collaboratively authored manuscript that used the GitHub Discussions, Issues, Pages, and Actions features.
 \\
-4. \textbf{The GitHub Learning Lab (\url{https://lab.github.com}).} allows you to learn GitHub basics through short projects and tasks, and allows you to get feedback from their Learning Lab bot. \\
-5. \textbf{Check out the following markdown cheatsheet (\url{http://markdownguide.org/basic-syntax}).} so that you can write clear metadata README files for your repositories. \\
+4. \textbf{The GitHub Learning Lab (\url{https://lab.github.com})} allows you to learn GitHub basics through short projects and tasks, and allows you to get feedback from their Learning Lab bot. \\
+5. \textbf{Learn markdown and use cheatsheets (\emph{e.g.}, \url{http://markdownguide.org/basic-syntax})} so you can write clear metadata README files for your repositories. \\
 6.
-\textbf{The Jenny Bryan universe of GitHub material.} provides a thorough and accessible introduction for a multitude of research-related uses for GitHub, and includes a book\textsuperscript{\protect\hyperlink{ref-ZvrOcg9w}{58}}, statistics course\textsuperscript{\protect\hyperlink{ref-6CMMeSeD}{59}} and academic article\textsuperscript{\protect\hyperlink{ref-RVetqmsg}{7}}.
+\textbf{Consult the Jenny Bryan Universe of GitHub material,} which provides a thorough and accessible introduction for a multitude of research-related uses for GitHub, and includes a book\textsuperscript{\protect\hyperlink{ref-ZvrOcg9w}{74}}, statistics course\textsuperscript{\protect\hyperlink{ref-6CMMeSeD}{75}} and academic article\textsuperscript{\protect\hyperlink{ref-RVetqmsg}{7}}.
 \\
 7.
-\textbf{Don't be afraid of trial-and-error.} One of the best ways to learn GitHub is the trial-and-error method.
-Learning from your own mistakes can be the better way to master your GitHub abilities.
-In any case, GitHub has the advantage of making it easy to go back to any steps that you desire via version controlling if you make mistakes.
+\textbf{Do not be afraid of trial-and-error.} One of the best ways to learn GitHub is the ``trial-and-error'' method.
+Learning from your own mistakes can be a valuable way to master your GitHub abilities.
+In any case, if you make mistakes, GitHub allows you to revert any steps that you desire via version controlling.
 \\
 8.
-\textbf{If you are an educator, include lectures on reproducibility and tools for creating reproducible workflows in the curricula.} Some graduate programs include coursework on course Rmarkdown and GitHub.
+\textbf{If you are an educator, include lectures on reproducibility and tools for creating reproducible workflows in the curricula.} Some graduate programs include coursework on course R Markdown and GitHub.
 Getting students started with these tools earlier will prevent the resistance that comes from working with a less reproducible workflow for a longer period of time.
@@
 9.
-\textbf{Try to begin committing with GUI (Graphical user interface) tools.} like GitHub Desktop (\url{https://desktop.github.com}), git-gui (\url{https://git-scm.com/docs/git-gui}), RStudio (\url{https://www.rstudio.com}), Visual Studio Code (\url{https://code.visualstudio.com}), Atom (\url{https://atom.io}), GitKraken (\url{https://www.gitkraken.com}) tools instead of CLI (Command line interface) tools such as Terminal or Console for more advanced features.
+\textbf{Try to begin committing with graphical user interfaces (GUI) instead of command line interfaces (CLI).} Examples of GUI are the GitHub Desktop (\url{https://desktop.github.com}), git-gui (\url{https://git-scm.com/docs/git-gui}), RStudio (\url{https://www.rstudio.com}), Visual Studio Code (\url{https://code.visualstudio.com}), Atom (\url{https://atom.io}), GitKraken (\url{https://www.gitkraken.com}).
 \\
@@
 
-We provide twelve practical ways that ecologists and evolutionary biologists can adopt GitHub to improve their research workflow and make it more open and reproducible.
+We provide thirteen practical ways that ecologists and evolutionary biologists can adopt GitHub to improve their research workflow and make it more open and reproducible.
 We provide definitions (\protect\hyperlink{definitions}{Box 1}) and types of users (Figure \ref{fig:github-diagram}) to help researchers identify and prioritize the skills and tools to learn and apply.
@@
   >{\raggedright\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.1289}}@{}}
-\caption{a comparison of technologies commonly used for collaborating on research in Ecology and Evolutionary Biology.
+\caption{a comparison of techNologies commonly used for collaborating on research in Ecology and Evolutionary Biology.
 In the first column, we group platforms for collaboration into broad guilds.
@@
 \endhead
-Multi-tool & GitHub & yes & yes & yes & NA & Broadly limited free version.
+Multi-tool & GitHub & Yes & Yes & Yes & NA & Broadly limited free version.
 Advanced features are provided for free to students and education professionals.
-& A DOI can only be obtained when integrating to other services that can mint DOI (e.g.~Zenodo, OSF).
+& A DOI can only be obtained when integrating to other services that can mint DOI (e.g.~ZeNodo, OSF).
 & 100 MB per file, 500 MB per private repository (2 GB for paid accounts).
 100 GB for public repositories.
-Larger files (up to 2 GB) can be attached to releases & NA \\
-Multi-tool & OSF & yes & yes & yes & yes & yes & yes & 25 GB for private projects, up to 5GB per file, plus partner add-ons, 50GB for public projects & yes \\
-Long-term (public) data repositories & PANGAEA & yes & yes & yes & NA & yes & yes & 10 GB free & NA \\
-Long-term (public) data repositories & Zenodo & after published & after published & NA & NA & yes & yes & 50 GB per dataset & yes \\
-Long-term (public) data repositories & Dryad & after published & after published & NA & NA & some journals cover cost & yes & 300 GB per publication & Can link to individual files (not entire reopository); not really integrated \\
-Long-term (public) data repositories & Figshare & yes & yes & yes & NA & yes & yes & 20 GB free, up to 5 TB & yes \\
-Temporary (personal) drive storage & Google Drive & yes & yes & yes & yes & limited free version \& paid & NA & 15 GB free, up to 100 GB with Google One & yes \\
-Temporary (personal) drive storage & Box & limited & yes & ? & ? & NA & NA & Unlimited total size for subscription & yes \\
-Temporary (personal) drive storage & DropBox & limited & yes & yes & yes & limited free version \& paid & NA & 2 GB free & yes \\
-Temporary (personal) drive storage & One Drive and the Office Suite & yes & yes & yes & yes & limited free version \& paid & NA & 5 GB free, up to 1TB paid & yes \\
-Collaborative code/text editors & Overleaf (online latex editor) & yes & yes & yes & NA & NA & NA & 1MB for individual .tex, 50 MB for individual files, unlimited project size & yes \\
+Larger files (up to 2 GB) can be attached to releases.
+& NA \\
+Multi-tool & OSF & Yes & Yes & Yes & Yes & Yes & Yes & 25 GB for private projects, up to 5GB per file, plus partner add-ons, 50GB for public projects & Yes \\
+Long-term (public) data repositories & PANGAEA & Yes & Yes & Yes & NA & Yes & Yes & 10 GB free & NA \\
+Long-term (public) data repositories & ZeNodo & after published & after published & NA & NA & Yes & Yes & 50 GB per dataset & Yes \\
+Long-term (public) data repositories & Dryad & after published & after published & NA & NA & Some journals cover cost & Yes & 300 GB per publication & Can link to individual files (Not entire reopository); Not really integrated \\
+Long-term (public) data repositories & Figshare & Yes & Yes & Yes & NA & Yes & Yes & 20 GB free, up to 5 TB & Yes \\
+Temporary (personal) drive storage & Google Drive & Yes & Yes & Yes & Yes & Limited free version \& paid & NA & 15 GB free, up to 100 GB with Google One & Yes \\
+Temporary (personal) drive storage & Box & limited & Yes & ? & ? & NA & NA & Unlimited total size for subscription & Yes \\
+Temporary (personal) drive storage & DropBox & limited & Yes & Yes & Yes & Limited free version \& paid & NA & 2 GB free & Yes \\
+Temporary (personal) drive storage & One Drive and the Office Suite & Yes & Yes & Yes & Yes & Limited free version \& paid & NA & 5 GB free, up to 1TB paid & Yes \\
+Collaborative code/text editors & Overleaf (online latex editor) & Yes & Yes & Yes & NA & NA & NA & 1MB for individual .tex, 50 MB for individual files, unlimited project size & Yes \\
+Collaborative code/text editors & Jupyter Notebook & Yes & ?
+& Yes & with Colab & Yes & NA & via Binder: No hard limit, but suggests No files \textgreater100 MB, can also store on GitHub or Google Colab & Yes \\
+Collaborative code/text editors & HackMD & Yes & Yes & Yes & Yes & Yes & NA & 3 documents free, private invitee limits & Yes \\
+\bottomrule
+\end{longtable}
+
+\begin{longtable}[]{@{}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.0627}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.0528}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.0281}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.0281}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.0380}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.0528}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.1799}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.1683}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.2558}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.1337}}@{}}
+\caption{a comparison of technologies\ldots{} \label{tbl:compare}}\tabularnewline
+\toprule
+\begin{minipage}[b]{\linewidth}\raggedright
+Guild
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+Software
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+Version control
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+Backup (cloud)
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+Passive collaboration
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+Active real-time collaboration
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+Free plan available
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+Permanent (DOI)
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+Storage limits
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+GitHub Integration
+\end{minipage} \\
+\midrule
+\endfirsthead
+\toprule
+\begin{minipage}[b]{\linewidth}\raggedright
+Guild
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+Software
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+Version control
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+Backup (cloud)
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+Passive collaboration
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+Active real-time collaboration
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+Free plan available
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+Permanent (DOI)
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+Storage limits
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+GitHub Integration
+\end{minipage} \\
+\midrule
+\endhead
+Multi-tool & GitHub & yes & yes & yes & no & Broadly used free version.
+Advanced features are provided for free to students and education professionals.
+& A DOI can only be obtained when integrating to other services that can mint DOI (e.g., Zenodo, OSF).
+& 100MB per file, 500MB per private repository (2GB for paid accounts).
+100GB for public repositories.
+Larger files (up to 2GB) can be attached to releases & N/A \\
+Multi-tool & Open Science Framework & yes & yes & yes & yes & yes & yes & 25GB for private projects, up to 5GB per file, plus partner add-ons, 50GB for public projects & yes \\
+Long-term (public) data repositories & PANGAEA & yes & yes & yes & no & yes & yes & 10 GB free & no \\
+Long-term (public) data repositories & Zenodo & after published & after published & yes & no & yes & yes & 50 GB per dataset & yes \\
+Long-term (public) data repositories & Dryad & after published & after published & yes & no & some journals cover cost & yes & 300 GB per publication & Can link to individual files (not entire repository), thus not fully integrated \\
+Long-term (public) data repositories & Figshare & yes & yes & yes & no & yes & yes & 20 GB free, up to 5 TB & yes \\
+Temporary (personal) drive storage & Google Drive & yes & yes & yes & yes & limited free version \& paid & no & 15GB free, up to 100GB with Google One & yes \\
+Temporary (personal) drive storage & Box & limited & yes & yes & yes & no & no & Unlimited total size for subscription & yes \\
+Temporary (personal) drive storage & DropBox & limited & yes & yes & yes & limited free version \& paid & no & 2GB free & yes \\
+Temporary (personal) drive storage & OneDrive and the Office Suite & yes & yes & yes & yes & limited free version \& paid & no & 5 GB free, up to 1TB paid & yes \\
+Collaborative code/text editors & Overleaf (online latex editor) & yes & yes & yes & yes & yes & no & 1MB for individual .tex, 50MB for individual files, unlimited project size & yes \\
 Collaborative code/text editors & Jupyter Notebook & yes & ?
-& yes & with Colab & yes & NA & via Binder: no hard limit, but suggests no files \textgreater100 MB, can also store on GitHub or Google Colab & yes \\
-Collaborative code/text editors & HackMD & yes & yes & yes & yes & yes & NA & 3 documents free, private invitee limits & yes \\
+& yes & with Colab & yes & no & via Binder: no hard limit, but suggests no files \textgreater100MB, can also store on GitHub or Google Colab & yes \\
+Collaborative code/text editors & HackMD & yes & yes & yes & yes & limited free version \& paid & no & 3 documents free, private invitee limits & yes \\
 \bottomrule
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-cfgXxgt1}{}}%
+\CSLLeftMargin{54. }
+\CSLRightInline{Keitt, T. H. \& Abelson, E. S. \href{https://doi.org/10.1126/science.abi4692}{Ecology in the age of automation}. \emph{Science} \textbf{373}, 858--859 (2021).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-bhDgD6lF}{}}%
+\CSLLeftMargin{55. }
+\CSLRightInline{Micheletti, T.
+\emph{et al.} \href{https://doi.org/10.3389/fevo.2021.679673}{Assessing Pathways of Climate Change Effects in SpaDES: An Application to Boreal Landbirds of Northwest Territories Canada}.
+\emph{Front.
+Ecol.
+Evol.} \textbf{9}, (2021).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-lXvpQxeN}{}}%
+\CSLLeftMargin{56. }
+\CSLRightInline{Yenni, G. M. \emph{et al.} Developing a modern data workflow for evolving data. (2018) doi:\href{https://doi.org/10.1101/344804}{10.1101/344804}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Qh7xTLwz}{}}%
+\CSLLeftMargin{57. }
+\CSLRightInline{Beaulieu-Jones, B.
+K.
+\& Greene, C.
+S.
+\href{https://doi.org/10.1038/nbt.3780}{Reproducibility of computational workflows is automated using continuous analysis}.
+\emph{Nat Biotechnol} \textbf{35}, 342--346 (2017).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-SirQKFIz}{}}%
+\CSLLeftMargin{58. }
+\CSLRightInline{White, E.
+P.
+\emph{et al.} \href{https://doi.org/10.1111/2041-210x.13104}{Developing an automated iterative near‐term forecasting system for an ecological study}.
+\emph{Methods Ecol Evol} \textbf{10}, 332--344 (2018).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-1Ep9EJL6y}{}}%
+\CSLLeftMargin{59. }
+\CSLRightInline{Meyer, M. \href{https://doi.org/10.1109/ms.2014.58}{Continuous Integration and Its Tools}. \emph{IEEE Softw.} \textbf{31}, 14--16 (2014).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-ufw0ZdnI}{}}%
+\CSLLeftMargin{60. }
+\CSLRightInline{Soergel, D. A. W. \href{https://doi.org/10.12688/f1000research.5930.2}{Rampant software errors may undermine scientific results}. \emph{F1000Res} \textbf{3}, 303 (2015).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-12103x16N}{}}%
+\CSLLeftMargin{61. }
+\CSLRightInline{Scheller, R.
+M., Sturtevant, B.
+R., Gustafson, E.
+J., Ward, B.
+C.
+\& Mladenoff, D.
+J.
+\href{https://doi.org/10.1890/080141}{Increasing the reliability of ecological models using modern software engineering techniques}.
+\emph{Frontiers in Ecology and the Environment} \textbf{8}, 253--260 (2010).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-rTbinQMj}{}}%
+\CSLLeftMargin{62. }
+\CSLRightInline{Dietze, M.
+C.
+\emph{et al.} \href{https://doi.org/10.1073/pnas.1710231115}{Iterative near-term ecological forecasting: Needs, opportunities, and challenges}.
+\emph{Proc.
+Natl.
+Acad.
+Sci.
+U.S.A.} \textbf{115}, 1424--1432 (2018).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-mmCOSRfr}{}}%
+\CSLLeftMargin{63. }
+\CSLRightInline{McIntire, E.
+J.
+B.
+\emph{et al.} \href{https://doi.org/10.1111/ele.13994}{PERFICT: A Re‐imagined foundation for predictive ecology}.
+\emph{Ecology Letters} \textbf{25}, 1345--1351 (2022).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-1CJo8lo2v}{}}%
+\CSLLeftMargin{64. }
+\CSLRightInline{Yenni, G.
+M.
+\emph{et al.} \href{https://doi.org/10.1371/journal.pbio.3000125}{Developing a modern data workflow for regularly updated data}.
+\emph{PLoS Biol} \textbf{17}, e3000125 (2019).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-RxK4CmfR}{}}%
+\CSLLeftMargin{65. }
+\CSLRightInline{Ernest, S. K. M. \emph{et al.} The Portal Project: a long-term study of a Chihuahuan desert ecosystem. (2018) doi:\href{https://doi.org/10.1101/332783}{10.1101/332783}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-kZzfmBNu}{}}%
+\CSLLeftMargin{66. }
+\CSLRightInline{Naujokaitis-Lewis, I., Endicott, S.
+\& Guezen, J.
+M.
+\href{https://doi.org/10.1038/s41597-022-01381-8}{CAN-SAR: A database of Canadian species at risk information}.
+\emph{Sci Data} \textbf{9}, (2022).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-NUXbp429}{}}%
+\CSLLeftMargin{67. }
+\CSLRightInline{Features • GitHub Actions. \emph{GitHub} \url{https://github.com/features/actions}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-T03Api6e}{}}%
+\CSLLeftMargin{68. }
+\CSLRightInline{Continuous Integration and Delivery. \emph{CircleCI} \url{https://circleci.com/}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-YeFSbfFV}{}}%
+\CSLLeftMargin{69. }
+\CSLRightInline{Homepage \textbar{} Travis CI -- Start building today! \emph{Travis CI} \url{https://www.travis-ci.com/}.}
+
 \leavevmode\vadjust pre{\hypertarget{ref-UsTxAq4f}{}}%
-\CSLLeftMargin{54. }
+\CSLLeftMargin{70. }
 \CSLRightInline{Anbaroğlu, B. \href{https://doi.org/10.1111/tgis.12810}{A collaborative GIS programming course using GitHub Classroom}. \emph{Transactions in GIS} \textbf{25}, 3132--3158 (2021).}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-lx49NGto}{}}%
-\CSLLeftMargin{55. }
+\CSLLeftMargin{71. }
 \CSLRightInline{Connect GitHub to a Project - OSF Support. \url{https://help.osf.io/article/211-connect-github-to-a-project}.}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-cW7vGddM}{}}%
-\CSLLeftMargin{56. }
+\CSLLeftMargin{72. }
 \CSLRightInline{Khelifa, R., Amano, T.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-pjy75gHr}{}}%
-\CSLLeftMargin{57. }
+\CSLLeftMargin{73. }
 \CSLRightInline{Madicken Munk \emph{et al.} swcarpentry/git-novice: Software Carpentry: Version Control with Git, June 2019. at \url{https://doi.org/10.5281/zenodo.3264950} (2019).}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-ZvrOcg9w}{}}%
-\CSLLeftMargin{58. }
+\CSLLeftMargin{74. }
 \CSLRightInline{Hester, J. B., the STAT 545 TAs, Jim. \emph{\href{https://happygitwithr.com/}{Let's Git started \textbar{} Happy Git and GitHub for the useR}}.}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-6CMMeSeD}{}}%
-\CSLLeftMargin{59. }
+\CSLLeftMargin{75. }
 \CSLRightInline{Bryan, J. \& TAs, T. S. 545. \emph{\href{https://stat545.com/}{STAT 545}}.}

### 2022-07-27 manuscript.tex
Merge pull request #266 from SORTEE-Github-Hackathon/RCO-iss263 [ci skip]
This build is based on
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/50a63631e17fef9d3b6a8798a25b2567c940fca3.

This commit was created by the following CI build and job:
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/50a63631e17fef9d3b6a8798a25b2567c940fca3/checks
https://github.com/SORTEE-Github-Hackathon/manuscript/actions/runs/2745745268

@@
 This manuscript
-(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/0aaaf3e6a685b4c96e2115ee2f709dab93a233f8/}{permalink})
+(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/50a63631e17fef9d3b6a8798a25b2567c940fca3/}{permalink})
 was automatically generated
-from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/0aaaf3e6a685b4c96e2115ee2f709dab93a233f8}{SORTEE-Github-Hackathon/manuscript@0aaaf3e}
-on July 26, 2022.
+from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/50a63631e17fef9d3b6a8798a25b2567c940fca3}{SORTEE-Github-Hackathon/manuscript@50a6363}
+on July 27, 2022.
 
@@
 \\
-4. \textbf{The GitHub Learning Lab (\url{https://lab.github.com})} allows you to learn GitHub basics through short projects and tasks, and allows you to get feedback from their Learning Lab bot. \\
+4. \textbf{The GitHub Skills page (\url{https://skills.github.com/})} allows you to learn GitHub basics through short projects and tasks with step-by-step guides. \\
 5. \textbf{Learn markdown and use cheatsheets (\emph{e.g.}, \url{http://markdownguide.org/basic-syntax})} so you can write clear metadata README files for your repositories. \\

### 2022-07-27 manuscript.tex
Merge pull request #267 from SORTEE-Github-Hackathon/phpb-organisations [ci skip]
This build is based on
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/def3bc7be9dc165100774b0e53208fbd9e00a9ba.

This commit was created by the following CI build and job:
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/def3bc7be9dc165100774b0e53208fbd9e00a9ba/checks
https://github.com/SORTEE-Github-Hackathon/manuscript/actions/runs/2748183697

@@
 This manuscript
-(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/50a63631e17fef9d3b6a8798a25b2567c940fca3/}{permalink})
+(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/def3bc7be9dc165100774b0e53208fbd9e00a9ba/}{permalink})
 was automatically generated
-from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/50a63631e17fef9d3b6a8798a25b2567c940fca3}{SORTEE-Github-Hackathon/manuscript@50a6363}
+from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/def3bc7be9dc165100774b0e53208fbd9e00a9ba}{SORTEE-Github-Hackathon/manuscript@def3bc7}
 on July 27, 2022.
@@
 
-\hypertarget{github-organizations}{%
-\subsubsection{GitHub Organizations}\label{github-organizations}}
+\hypertarget{organizing-and-managing-teams}{%
+\subsubsection{Organizing and managing teams}\label{organizing-and-managing-teams}}
 
 GitHub Organizations are shared virtual spaces that allow teams to work in different repositories, while remaining tied together under a larger group, such as a laboratory, department, or project involving several teams.
-Organizations are well-suited to ensure larger projects with many steps or moving parts are constrained to one virtual space, where outputs and sub-projects can be easily accessed and located without relying on any one individual.
-Because the repositories are grouped, members can reference and contribute to each other's work without necessarily being part of the same repository, broadening the accessibility and longevity of code and writing contributions.
+Organizations allow larger projects with many steps or moving parts to be constrained to one virtual space, where outputs and sub-projects can be easily accessed and located without relying on individuals.
+Because the repositories are grouped, members can reference and contribute to each others work without necessarily being part of the same repository, broadening the accessibility and longevity of code and writing contributions.
 
@@
 The team organizing the hackathon which inspired this article used a GitHub Organization (SORTEE-Github-Hackathon, \url{https://github.com/SORTEE-Github-Hackathon}) to centralize the project development, from meeting notes to, ultimately, this manuscript.
-Organizations are also convenient for hosting learning materials, including lectures or workshops, such as the Québec Centre for Biodiversity Science R Workshop Series (QCBSRworkshops, \url{https://github.com/QCBSRworkshops}) or the University of Edinburgh's Coding Club (Coding Club, \url{https://github.com/ourcodingclub}), which may be continously updated by an ever-evolving group of contributors.
+Organizations are also convenient for hosting learning materials, including lectures or workshops, such as the Québec Centre for Biodiversity Science R Workshop Series (QCBSRworkshops, \url{https://github.com/QCBSRworkshops}) or the University of Edinburgh's Coding Club (Coding Club, \url{https://github.com/ourcodingclub}), which may be continuously updated by an ever-evolving group of contributors.
 
@@
 \CSLLeftMargin{22. }
-\CSLRightInline{About projects (beta). \emph{GitHub Docs} \url{https://ghdocs-prod.azurewebsites.net/en/issues/trying-out-the-new-projects-experience/about-projects}.}
+\CSLRightInline{About Projects. \emph{GitHub Docs} \url{https://ghdocs-prod.azurewebsites.net/en/issues/planning-and-tracking-with-projects/learning-about-projects/about-projects}.}
 

### 2022-07-27 manuscript.tex
Merge pull request #268 from SORTEE-Github-Hackathon/phpb-minor-changes [ci skip]
This build is based on
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/9396d27adfc38e9204618775d08f1a56f0f98bb3.

This commit was created by the following CI build and job:
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/9396d27adfc38e9204618775d08f1a56f0f98bb3/checks
https://github.com/SORTEE-Github-Hackathon/manuscript/actions/runs/2749272649

@@
 This manuscript
-(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/def3bc7be9dc165100774b0e53208fbd9e00a9ba/}{permalink})
+(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/9396d27adfc38e9204618775d08f1a56f0f98bb3/}{permalink})
 was automatically generated
-from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/def3bc7be9dc165100774b0e53208fbd9e00a9ba}{SORTEE-Github-Hackathon/manuscript@def3bc7}
+from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/9396d27adfc38e9204618775d08f1a56f0f98bb3}{SORTEE-Github-Hackathon/manuscript@9396d27}
 on July 27, 2022.
@@
 First, there may be hesitation to independently adopting and learning a new tool.
-
 Institutional encouragement and instructional resources focused on researchers in ecology and evolution may be limited.
@@
 1.
-\textbf{Check for an existing solution to your problem.} The GitHub Help webpage (\url{https://docs.github.com/en}) contains extensive and detailed documents with helpful screenshots.
+\textbf{Check for existing solutions to your problem.} The GitHub Help webpage (\url{https://docs.github.com/en}) contains extensive and detailed documents with helpful screenshots.
 It is a good starting point for handling an issue, and has troubleshooting tips for specific problems.
@@
 \\
-4. \textbf{The GitHub Skills page (\url{https://skills.github.com/})} allows you to learn GitHub basics through short projects and tasks with step-by-step guides. \\
+4.
+\textbf{Use the interactive courses from the GitHub Skills page (\url{https://skills.github.com/})}, which allow you to learn GitHub basics through short projects and tasks with step-by-step guides.
+\\
 5. \textbf{Learn markdown and use cheatsheets (\emph{e.g.}, \url{http://markdownguide.org/basic-syntax})} so you can write clear metadata README files for your repositories. \\
 6.
-\textbf{Consult the Jenny Bryan Universe of GitHub material,} which provides a thorough and accessible introduction for a multitude of research-related uses for GitHub, and includes a book\textsuperscript{\protect\hyperlink{ref-ZvrOcg9w}{74}}, statistics course\textsuperscript{\protect\hyperlink{ref-6CMMeSeD}{75}} and academic article\textsuperscript{\protect\hyperlink{ref-RVetqmsg}{7}}.
+\textbf{Consult online resources.} The Jenny Bryan Universe of GitHub material, for example, provides a thorough and accessible introduction for a multitude of research-related uses for GitHub, and includes a book\textsuperscript{\protect\hyperlink{ref-ZvrOcg9w}{74}}, statistics course\textsuperscript{\protect\hyperlink{ref-6CMMeSeD}{75}} and academic article\textsuperscript{\protect\hyperlink{ref-RVetqmsg}{7}}.
 \\
@@
 \centering
-\includegraphics{images/scatterblob_1.png}
+\includegraphics{images/scatterblob_1-viridis-turbo.png}
 \caption{A summary of ways GitHub can be used showing technical difficulty and degree of collaboration for each.

### 2022-08-10 manuscript.tex
Merge pull request #269 from SORTEE-Github-Hackathon/removing-table [ci skip]
This build is based on
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/603d35edf8325ad77fc38594ae2a81ef11346da3.

This commit was created by the following CI build and job:
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/603d35edf8325ad77fc38594ae2a81ef11346da3/checks
https://github.com/SORTEE-Github-Hackathon/manuscript/actions/runs/2830986199

@@
 This manuscript
-(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/9396d27adfc38e9204618775d08f1a56f0f98bb3/}{permalink})
+(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/603d35edf8325ad77fc38594ae2a81ef11346da3/}{permalink})
 was automatically generated
-from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/9396d27adfc38e9204618775d08f1a56f0f98bb3}{SORTEE-Github-Hackathon/manuscript@9396d27}
-on July 27, 2022.
+from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/603d35edf8325ad77fc38594ae2a81ef11346da3}{SORTEE-Github-Hackathon/manuscript@603d35e}
+on August 10, 2022.
 
@@
 \begin{longtable}[]{@{}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.0628}}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.0529}}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.0281}}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.0281}}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.0380}}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.0529}}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.1851}}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.1669}}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.2562}}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.1289}}@{}}
-\caption{a comparison of techNologies commonly used for collaborating on research in Ecology and Evolutionary Biology.
-In the first column, we group platforms for collaboration into broad guilds.
-The second column lists the platform for collaboration.
-The remaining columns indicate whether the platform for collaboration includes certain features.
-\label{tbl:compare}}\tabularnewline
-\toprule
-\begin{minipage}[b]{\linewidth}\raggedright
-Guild
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
-Software
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
-Vesion control
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
-Backup (cloud)
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
-Passive collaboration
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
-Active real-time colalboration
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
-Free \$
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
-Permanent (DOI)
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
-Storage limits
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
-GitHub Integration
-\end{minipage} \\
-\midrule
-\endfirsthead
-\toprule
-\begin{minipage}[b]{\linewidth}\raggedright
-Guild
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
-Software
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
-Vesion control
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
-Backup (cloud)
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
-Passive collaboration
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
-Active real-time colalboration
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
-Free \$
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
-Permanent (DOI)
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
-Storage limits
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
-GitHub Integration
-\end{minipage} \\
-\midrule
-\endhead
-Multi-tool & GitHub & Yes & Yes & Yes & NA & Broadly limited free version.
-Advanced features are provided for free to students and education professionals.
-& A DOI can only be obtained when integrating to other services that can mint DOI (e.g.~ZeNodo, OSF).
-& 100 MB per file, 500 MB per private repository (2 GB for paid accounts).
-100 GB for public repositories.
-Larger files (up to 2 GB) can be attached to releases.
-& NA \\
-Multi-tool & OSF & Yes & Yes & Yes & Yes & Yes & Yes & 25 GB for private projects, up to 5GB per file, plus partner add-ons, 50GB for public projects & Yes \\
-Long-term (public) data repositories & PANGAEA & Yes & Yes & Yes & NA & Yes & Yes & 10 GB free & NA \\
-Long-term (public) data repositories & ZeNodo & after published & after published & NA & NA & Yes & Yes & 50 GB per dataset & Yes \\
-Long-term (public) data repositories & Dryad & after published & after published & NA & NA & Some journals cover cost & Yes & 300 GB per publication & Can link to individual files (Not entire reopository); Not really integrated \\
-Long-term (public) data repositories & Figshare & Yes & Yes & Yes & NA & Yes & Yes & 20 GB free, up to 5 TB & Yes \\
-Temporary (personal) drive storage & Google Drive & Yes & Yes & Yes & Yes & Limited free version \& paid & NA & 15 GB free, up to 100 GB with Google One & Yes \\
-Temporary (personal) drive storage & Box & limited & Yes & ? & ? & NA & NA & Unlimited total size for subscription & Yes \\
-Temporary (personal) drive storage & DropBox & limited & Yes & Yes & Yes & Limited free version \& paid & NA & 2 GB free & Yes \\
-Temporary (personal) drive storage & One Drive and the Office Suite & Yes & Yes & Yes & Yes & Limited free version \& paid & NA & 5 GB free, up to 1TB paid & Yes \\
-Collaborative code/text editors & Overleaf (online latex editor) & Yes & Yes & Yes & NA & NA & NA & 1MB for individual .tex, 50 MB for individual files, unlimited project size & Yes \\
-Collaborative code/text editors & Jupyter Notebook & Yes & ?
-& Yes & with Colab & Yes & NA & via Binder: No hard limit, but suggests No files \textgreater100 MB, can also store on GitHub or Google Colab & Yes \\
-Collaborative code/text editors & HackMD & Yes & Yes & Yes & Yes & Yes & NA & 3 documents free, private invitee limits & Yes \\
-\bottomrule
-\end{longtable}
-
-\begin{longtable}[]{@{}
   >{\raggedright\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.0627}}
@@
   >{\raggedright\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.1337}}@{}}
-\caption{a comparison of technologies\ldots{} \label{tbl:compare}}\tabularnewline
+\caption{A comparison of technologies commonly used for collaborating on research in Ecology and Evolutionary Biology.
+In the first column, we group platforms for collaboration into broad guilds.
+The second column lists the platform for collaboration.
+The remaining columns indicate whether the platform for collaboration includes certain features.
+\label{tbl:compare}}\tabularnewline
 \toprule

### 2022-08-10 manuscript.tex
Merge pull request #271 from SORTEE-Github-Hackathon/RCO-last-edits [ci skip]
This build is based on
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/b2d3efb7b1c0fed0477b041fbe9cb7dbc487d31c.

This commit was created by the following CI build and job:
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/b2d3efb7b1c0fed0477b041fbe9cb7dbc487d31c/checks
https://github.com/SORTEE-Github-Hackathon/manuscript/actions/runs/2834762391

@@
 This manuscript
-(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/603d35edf8325ad77fc38594ae2a81ef11346da3/}{permalink})
+(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/b2d3efb7b1c0fed0477b041fbe9cb7dbc487d31c/}{permalink})
 was automatically generated
-from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/603d35edf8325ad77fc38594ae2a81ef11346da3}{SORTEE-Github-Hackathon/manuscript@603d35e}
+from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/b2d3efb7b1c0fed0477b041fbe9cb7dbc487d31c}{SORTEE-Github-Hackathon/manuscript@b2d3efb}
 on August 10, 2022.
@@
 This workflow provides a strong and clear advantage over sending files back-and-forth (\emph{e.g.}, via email), a process that can become challenging and time-consuming in long-term and collaborative projects\textsuperscript{\protect\hyperlink{ref-4ny1onB0}{8}}.
-Through its combination of version control and collaborative features, GitHub facilitates open source code alongside collaborative development\textsuperscript{\protect\hyperlink{ref-kEX5dgzK}{9}}.
+Through its combination of version control and collaborative features, GitHub facilitates open-source code alongside collaborative development\textsuperscript{\protect\hyperlink{ref-kEX5dgzK}{9}}.
 
@@
 Commits can include changes in multiple files and must include a brief commit message describing the changes made.
-A typical workflow is to make some related changes in files, add a commit message (\emph{e.g.} ``Generate and include results figure''), and after several commits \textbf{push} those commits to the remote (\emph{i.e.}, cloud-based) GitHub \textbf{repository}.
+A typical workflow is to make some related changes in files, add a commit message (\emph{e.g.}, ``Generate and include results figure''), and after several commits \textbf{push} those commits to the remote (\emph{i.e.}, cloud-based) GitHub \textbf{repository}.
 \\
@@
 Automation has a strong potential to expand the scale and pace of research in ecology and evolution\textsuperscript{\protect\hyperlink{ref-cfgXxgt1}{54}}.
-Automation frameworks can streamline many stages of the scientific process, including automated data collection and data validation\textsuperscript{\protect\hyperlink{ref-lXvpQxeN}{56}}, automated data analysis\textsuperscript{\emph{e.g.}, \protect\hyperlink{ref-Qh7xTLwz}{57}}, automated archiving and deployment of data, code and reports\textsuperscript{\emph{e.g.}, this manuscript, \protect\hyperlink{ref-SirQKFIz}{58}}.
+Automation frameworks can streamline many stages of the scientific process, including automated data collection and data validation (\emph{e.g.},\textsuperscript{\protect\hyperlink{ref-bhDgD6lF}{55},\protect\hyperlink{ref-lXvpQxeN}{56}}), automated data analysis (\emph{e.g.},\textsuperscript{\protect\hyperlink{ref-Qh7xTLwz}{57}}), automated archiving and deployment of data, code and reports (\emph{e.g.}, this manuscript,\textsuperscript{\protect\hyperlink{ref-SirQKFIz}{58}}).
 In this context, small modifications to code and data can be frequently committed and automatically tested, as in continuous integration and continuous deployment practices\textsuperscript{\protect\hyperlink{ref-1Ep9EJL6y}{59}}.
-This allows for early detection and correction of errors, potentially improving confidence in scientific development by minimizing software errors\textsuperscript{see \protect\hyperlink{ref-ufw0ZdnI}{60}}.
+This allows for early detection and correction of errors, potentially improving confidence in scientific development by minimizing software errors (see\textsuperscript{\protect\hyperlink{ref-ufw0ZdnI}{60}}).
 In addition to increasing scientific rigor and confidence in ecological software\textsuperscript{\protect\hyperlink{ref-12103x16N}{61}}, automation can help advance more rapidly sharing ecological data and making sure the data are high quality\textsuperscript{\protect\hyperlink{ref-rTbinQMj}{62}}.
@@
 These actions are highly configurable and have numerous applications, such as automatically running analyses and creating figures when data or code are updated, incorporating changes to websites or applications, testing modifications to software (\emph{e.g.}, R or Python libraries).
-Action workflows can be found in GitHub's Marketplace (https://github.com/marketplace?type=actions) or, alternatively, in open user repositories.
+Action workflows can be found in GitHub's Marketplace (\url{https://github.com/marketplace?type=actions}) or, alternatively, in open user repositories.
 
@@
 In this way, teams have full ownership of repositories within an organization, while ensuring that these materials stay accessible to the laboratory after people have moved on or when locally-stored data are lost.
-This application extends to research centres, which may include several distinct projects that remain linked to institutions {[}\emph{e.g.}, the German Centre for Integrative Biodiversity Research (iDiv, \url{https://github.com/idiv-biodiversity}){]}.
+This application extends to research centres, which may include several distinct projects that remain linked to institutions (\emph{e.g.}, the German Centre for Integrative Biodiversity Research (iDiv, \url{https://github.com/idiv-biodiversity})).
 The team organizing the hackathon which inspired this article used a GitHub Organization (SORTEE-Github-Hackathon, \url{https://github.com/SORTEE-Github-Hackathon}) to centralize the project development, from meeting notes to, ultimately, this manuscript.
@@
 There have been many calls for researchers outside of the software development community to adopt GitHub to improve their collaborative research\textsuperscript{\protect\hyperlink{ref-10ghgV3S8}{3},\protect\hyperlink{ref-1Du6fzB8g}{39},\protect\hyperlink{ref-UsTxAq4f}{70}}.
-This call comes in light of the continuous shift towards open-science and the increasing computational and data requirements in EEB.
+These calls come in light of the continuous shift towards open-science and the increasing computational and data requirements in EEB.
 Until now, resources and practical guidance on using GitHub within the EEB community have been dispersed in blog posts and video tutorials (\protect\hyperlink{tips}{Box 2}).
@@
 Second, operations that are dependent on other software might not be easily achievable in GitHub, such as manipulating figures or tables.
-Although creating tables and figures can be done through code, users may choose other software to collaboratively brainstorm figures and tables (\emph{e.g}.
-Google Slides, Google Sheets; but see GitHub Discussions).
+Although creating tables and figures can be done through code, users may choose other software to collaboratively brainstorm figures and tables (\emph{e.g}., Google Slides, Google Sheets; but see GitHub Discussions).
 
@@
 
-Lastly, fourth, GitHub may increase the distinctions between free and paid-for plans.
-When projects become highly collaborative, they may have to pay GitHub features, such for branch protections, multiple reviewers of pull requests and time in its automation tools.
-Currently, GitHub offers Education Packs (https://education.github.com/) to students and academics, which extends some paid features to the free plan.
+Lastly, when projects become highly collaborative they may have to pay for GitHub features such as branch protections, multiple reviewers of pull requests, and time in its automation tools.
+Currently, GitHub offers Education Packs (\url{https://education.github.com/}) to students and academics, which extends some paid features to the free plan.
 However, the acquisition of GitHub by Microsoft has raised concerns over the future of free plans, causing several biodiversity data managers to shift to alternative Open Source Git services (\emph{e.g.}, Bitbucket and GitLab).
@@
 \textbf{If you are an educator, include lectures on reproducibility and tools for creating reproducible workflows in the curricula.} Some graduate programs include coursework on course R Markdown and GitHub.
-Getting students started with these tools earlier will prevent the resistance that comes from working with a less reproducible workflow for a longer period of time.
-(see example \url{https://github.com/rmcelreath/stat_rethinking_2022}) \\
+Getting students started with these tools earlier will prevent the resistance that comes from working with a less reproducible workflow for a longer period of time (see example \url{https://github.com/rmcelreath/stat_rethinking_2022}).
+\\
 9.
@@
 The source code will be archived in the ESS-DIVE data repository prior to publication.
+
+\hypertarget{ethics-declarations---competing-interests}{%
+\subsection{Ethics declarations - Competing interests}\label{ethics-declarations---competing-interests}}
+
+RCO was recently offered a position to work at GitHub (on July 15, 2022) and will start employment at GitHub on August 23, 2022.
+Initial discussion of publishing this manuscript began in July 2021 and all work on the manuscript took place while RCO was an employee at Lawrence Berkeley National Laboratory.
 

### 2022-09-22 manuscript.tex
Merge pull request #273 from SORTEE-Github-Hackathon/phpb-field-specific-examples [ci skip]
This build is based on
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/ec11faeb0bef6e3bab5ff066c8b7786218ca8fe5.

This commit was created by the following CI build and job:
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/ec11faeb0bef6e3bab5ff066c8b7786218ca8fe5/checks
https://github.com/SORTEE-Github-Hackathon/manuscript/actions/runs/3105140291

@@
 This manuscript
-(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/b2d3efb7b1c0fed0477b041fbe9cb7dbc487d31c/}{permalink})
+(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/ec11faeb0bef6e3bab5ff066c8b7786218ca8fe5/}{permalink})
 was automatically generated
-from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/b2d3efb7b1c0fed0477b041fbe9cb7dbc487d31c}{SORTEE-Github-Hackathon/manuscript@b2d3efb}
-on August 10, 2022.
+from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/ec11faeb0bef6e3bab5ff066c8b7786218ca8fe5}{SORTEE-Github-Hackathon/manuscript@ec11fae}
+on September 22, 2022.
 
@@
 Virtual laboratory notebooks can be stored in GitHub repositories and provide the benefits of simultaneous, centralized and selective access, and allows for the easy update of policies and experiment protocols\textsuperscript{\protect\hyperlink{ref-10V7x4H4l}{21}}.
-Researchers have been increasingly using GitHub to maintain versions and share digital laboratory notebooks\textsuperscript{\protect\hyperlink{ref-10ghgV3S8}{3}} (\emph{e.g.}, \url{https://scheuerell-lab.github.io/lab-book}; \url{https://github.com/HuckleyLab/how_we_work}).
+Researchers have been increasingly using GitHub to maintain versions and share digital laboratory notebooks across many fields\textsuperscript{\protect\hyperlink{ref-10ghgV3S8}{3}}, including applied ecology (\emph{e.g.}, \url{https://scheuerell-lab.github.io/lab-book}), biogeography and global change biology (\emph{e.g.}, \url{https://github.com/HuckleyLab/how_we_work}), and microbial ecology (\emph{e.g.}, \url{https://github.com/CarBBAS/uqam-guide}).
 
@@
 Later, the entire history of commits and their commit messages are viewable and can be audited similar to a physical laboratory notebook\textsuperscript{\protect\hyperlink{ref-4ny1onB0}{8}}.
-GitHub issues (see project management section below) can be used to prioritize laboratory objectives and goals, as well as track any progress updates.
+GitHub issues (see Project management section below) can be used to prioritize laboratory objectives and goals, as well as track any progress updates.
 
@@
 
-Modern research in ecology and evolution is highly collaborative, bringing together multidisciplinary teams from various institutions.
+Modern research in ecology and evolution is highly collaborative, bringing together multidisciplinary teams from various institutions\textsuperscript{\protect\hyperlink{ref-1HhzKAC1K}{22}}.
 On GitHub, collaborators can share feedback, brainstorm ideas, and troubleshoot problems (Figure \ref{fig:github-diagram}).
@@
 Github Discussions serve as a message board for conversation.
-Finally, GitHub Projects integrate issues and pull requests on automated spreadsheets and project boards, providing users with real-time tracking of project priorities and status\textsuperscript{\protect\hyperlink{ref-RhBKe0MG}{22}}.
+Finally, GitHub Projects integrate issues and pull requests on automated spreadsheets and project boards, providing users with real-time tracking of project priorities and status\textsuperscript{\protect\hyperlink{ref-RhBKe0MG}{23}}.
 Scripts, commit messages, and pull requests can be linked directly to issues, discussions, and projects providing a clear record of project workflow.
+For instance, one can create a discussion on a project repository to decide on which method to apply for analyzing biodiversity data, and then an issue can be created with the purpose of establishing the steps and responsibilities covering from data formatting, statistical analyses, until the figure generation and issue resolution {[}\emph{e.g.}, see issues and discussions in the sPlotOpen {[}doi:10.1111/geb.13346{]} manuscript repository (\url{https://github.com/fmsabatini/sPlotOpen_Manuscript/issues?q=is\%3Aissue+is\%3Aclosed}){]}.
 Using GitHub for all project-related conversation and planning, rather than email or messaging tools, makes it easier to keep track of progress throughout the lifespan of a project.
@@
 Project management in GitHub can also be integrated with third-party applications, such as Zenhub (\url{https://www.zenhub.com}) or Slack (\url{https://slack.github.com}).
-ZenHub allows for the enhanced visualization and organization of repositories and their issues, while the GitHub for Slack integration allows notifications from GitHub events to be sent directly to users or group channels\textsuperscript{\protect\hyperlink{ref-1GRWGlDWy}{23}}.
+ZenHub allows for the enhanced visualization and organization of repositories and their issues, while the GitHub for Slack integration allows notifications from GitHub events to be sent directly to users or group channels\textsuperscript{\protect\hyperlink{ref-1GRWGlDWy}{24}}.
 
@@
 
-Making presentations, syllabi and other course materials can be done through most major high-level programming languages such as R, with \texttt{RMarkdown}\textsuperscript{\protect\hyperlink{ref-QqMezOMg}{24}}, Python, with \texttt{python-ppt} (\url{https://python-pptx.readthedocs.io}), and Julia, with \texttt{Remark.jl} (\url{https://juliapackages.com/p/remark}), and be version-controlled and stored in GitHub.
-Once content is made, hosting a course website can be done through GitHub Pages\textsuperscript{\protect\hyperlink{ref-MDQfMwCW}{25}} (\emph{e.g.}, \url{https://github.com/topics/course-website}).
+Making presentations, syllabi and other course materials can be done through most major high-level programming languages such as R, with \texttt{RMarkdown}\textsuperscript{\protect\hyperlink{ref-QqMezOMg}{25}}, Python, with \texttt{python-ppt} (\url{https://python-pptx.readthedocs.io}), and Julia, with \texttt{Remark.jl} (\url{https://juliapackages.com/p/remark}), and be version-controlled and stored in GitHub.
+Once content is made, hosting a course website can be done through GitHub Pages\textsuperscript{\protect\hyperlink{ref-MDQfMwCW}{26}} (\emph{e.g.}, \url{https://github.com/topics/course-website}).
 This way, course content can be available to enrolled students, as well as a global pool of learners and teachers interested in the material.
@@
 Student submissions are perhaps the most challenging component, but the new GitHub Classroom tool (\url{https://classroom.github.com}) allows instructors to host private assignments to be submitted collaboratively or individually as code or PDF files, and even build autograding tests.
-Although time-consuming to establish, using these features can integrate learning version control and GitHub with the learning course content, and thus boost students' feelings of self-efficacy and confidence\textsuperscript{\protect\hyperlink{ref-dqrFjoSb}{26}}.
+Although time-consuming to establish, using these features can integrate learning version control and GitHub with the learning course content, and thus boost students' feelings of self-efficacy and confidence\textsuperscript{\protect\hyperlink{ref-dqrFjoSb}{27}}.
 
@@
 
-Personal or laboratory websites can improve the sharing of research findings, build online presence, and increase coordination of research efforts\textsuperscript{\protect\hyperlink{ref-HiIPSSHV}{27}}.
-Despite many researchers in ecology and evolution having little experience in building or hosting webpages, many tools have been developed to help this process.
+Personal or laboratory websites can improve the sharing of research findings, build online presence, and increase coordination of research efforts\textsuperscript{\protect\hyperlink{ref-HiIPSSHV}{28}}.
+Despite researchers in ecology and evolution generally lacking experience in building or hosting webpages, many tools have been developed to help this process.
 Static websites can now be easily built using independent software and languages, such as Jekyll (\url{https://jekyllrb.com}), Hugo (\url{https://gohugo.io}), Quarto (\url{https://quarto.org}), and wowchemy (\url{https://wowchemy.com}), or with the help of dependencies in the programming languages scientists commonly use, such as the \texttt{distill} (\url{https://github.com/rstudio/distill}) and \texttt{blogdown} (\url{https://bookdown.org/yihui/blogdown}) R packages.
@@
 
-Website templates are readily available on GitHub (\url{https://github.com/topics/website-template}) or in user-specific repositories, which can be forked (\protect\hyperlink{definitions}{Box 1}) and customized\textsuperscript{\protect\hyperlink{ref-MXxgZJ45}{28}}.
+Website templates are readily available on GitHub (\url{https://github.com/topics/website-template}) or in user-specific repositories, which can be forked (\protect\hyperlink{definitions}{Box 1}) and customized\textsuperscript{\protect\hyperlink{ref-MXxgZJ45}{29}}.
 Aside from free hosting services, GitHub Pages also allows websites to be autogenerated and instantly updated following content modifications\textsuperscript{\protect\hyperlink{ref-RVetqmsg}{7}}.
@@
 
-Government, funding agencies, and publishers exercise rigorous open access data policies and mandates\textsuperscript{\protect\hyperlink{ref-PLmDFZrm}{29},\protect\hyperlink{ref-1Hcf13Q0k}{30}}.
-However, code and data sharing may be met by individual reluctance, temporary embargoes, or partially prevented by privacy and confidentiality reasons\textsuperscript{\protect\hyperlink{ref-1Ch6LSHef}{31}--\protect\hyperlink{ref-1CzUZwyU2}{33}}.
-Still, data deposition and ensuring its availability can amplify the outreach of published studies\textsuperscript{\protect\hyperlink{ref-666HppfO}{34}}, increase citation rates\textsuperscript{\protect\hyperlink{ref-1CcAUn3Lu}{35}}, and among many other reasons, enable the reproducibility and robustness of scientific advances\textsuperscript{\protect\hyperlink{ref-4LaijDIZ}{36}--\protect\hyperlink{ref-1HZdsK5Kn}{38}}.
+Government, funding agencies, and publishers exercise rigorous open access data policies and mandates\textsuperscript{\protect\hyperlink{ref-PLmDFZrm}{30},\protect\hyperlink{ref-1Hcf13Q0k}{31}}.
+However, code and data sharing may be met by individual reluctance, temporary embargoes, or partially prevented by privacy and confidentiality reasons\textsuperscript{\protect\hyperlink{ref-1Ch6LSHef}{32}--\protect\hyperlink{ref-1CzUZwyU2}{34}}.
+Still, data deposition and ensuring its availability can amplify the outreach of published studies\textsuperscript{\protect\hyperlink{ref-666HppfO}{35}}, increase citation rates\textsuperscript{\protect\hyperlink{ref-1CcAUn3Lu}{36}}, and among many other reasons, enable the reproducibility and robustness of scientific advances\textsuperscript{\protect\hyperlink{ref-4LaijDIZ}{37}--\protect\hyperlink{ref-1HZdsK5Kn}{39}}.
 While public repositories on GitHub make it easy to store and share data files, they are not considered long-term repositories for research materials.
@@
 DOIs are persistent and citable unique alpha-numeric identifiers assigned to digitally stored research materials.
-Because of this, scientists sharing code and data through GitHub are strongly encouraged to independently submit their research materials to long-term data archives (\emph{e.g.}, Zenodo, Figshare, Dryad, OSF\textsuperscript{\protect\hyperlink{ref-10ghgV3S8}{3},\protect\hyperlink{ref-kEX5dgzK}{9},\protect\hyperlink{ref-1Du6fzB8g}{39}}; \protect\hyperlink{tbl:compare}{Table 1}).
+Because of this, scientists sharing code and data through GitHub are strongly encouraged to independently submit their research materials to long-term data archives (\emph{e.g.}, Zenodo, Figshare, Dryad, OSF\textsuperscript{\protect\hyperlink{ref-10ghgV3S8}{3},\protect\hyperlink{ref-kEX5dgzK}{9},\protect\hyperlink{ref-1Du6fzB8g}{40}}; \protect\hyperlink{tbl:compare}{Table 1}).
 Some of these options (Zenodo, Figshare and OSF) integrate with GitHub, allowing project, code, and data releases (\protect\hyperlink{definitions}{Box 1}) to be archived with versioned, citable DOIs.
-Linking GitHub repositories with a DOI helps research become findable, properly cited, and can ensure long-term stability\textsuperscript{\protect\hyperlink{ref-iIEKCTLU}{40}}.
+Linking GitHub repositories with a DOI helps research become findable, properly cited, and can ensure long-term stability\textsuperscript{\protect\hyperlink{ref-iIEKCTLU}{41}}.
+This strategy has been increasingly adopted in numerous studies in ecology and evolution (\emph{e.g.},\textsuperscript{\protect\hyperlink{ref-GQj3c17f}{42}};\textsuperscript{\protect\hyperlink{ref-bZNn2hbh}{43}};\textsuperscript{\protect\hyperlink{ref-ZI1OqZNr}{44}}).
 
@@
 Code published without a license is under exclusive copyright (by default), protecting it from copy, distribution, and modifications.
-One may grant specific rights to their code for reuse by adding licensing files and specifications within GitHub repositories\textsuperscript{\protect\hyperlink{ref-TOsASkn5}{41}}.
+One may grant specific rights to their code for reuse by adding licensing files and specifications within GitHub repositories\textsuperscript{\protect\hyperlink{ref-TOsASkn5}{45}}.
 The Choose a License (\url{https://choosealicense.com/non-software/}) website offers further guidance on the licenses available for research and creative products.
@@
 By forking, branching, and cloning repositories (\protect\hyperlink{definitions}{Box 1}), researchers can simultaneously work on different issues of the same research project to then later merge changes to the main branch project with pull requests.
-Explicit project organization and increased communication in GitHub Issues, Discussions, or within pull requests can help with project development and with potential merge conflicts due to users simultaneously working on the same sections\textsuperscript{\protect\hyperlink{ref-1BJcvyTmV}{42}}.
-Moreover, version control\textsuperscript{\protect\hyperlink{ref-K7nbP1Ty}{43}} and commit reversal features allow researchers to track and progress without worrying about irreparably modifying someone else's work.
+Explicit project organization and increased communication in GitHub Issues, Discussions, or within pull requests can help with project development and with potential merge conflicts due to users simultaneously working on the same sections\textsuperscript{\protect\hyperlink{ref-1BJcvyTmV}{46}}.
+Moreover, version control\textsuperscript{\protect\hyperlink{ref-K7nbP1Ty}{47}} and commit reversal features allow researchers to track and progress without worrying about irreparably modifying someone else's work.
 By enabling more comprehensive remote collaboration, GitHub encourages the exchange of ideas among researchers at different institutions and in different countries, which can serve to improve the quality of the research itself by providing open access to data and code.
 In academic settings, GitHub can also facilitate interactions between research advisors and advisees, providing a platform for students or other trainees to share in-progress code, and flag specific challenges or questions for their supervisors or mentors (\protect\hyperlink{tbl:roles}{Table 2}).
-Periodic code review\textsuperscript{\protect\hyperlink{ref-hm9PaCLD}{44}} can also help advisors identify errors early in the process, and inform further training and mentorship to fill gaps in skills.
+Periodic code review\textsuperscript{\protect\hyperlink{ref-hm9PaCLD}{48}} can also help advisors identify errors early in the process, and inform further training and mentorship to fill gaps in skills.
 
@@
 
-We wrote this manuscript using Manubot\textsuperscript{\protect\hyperlink{ref-Re6Eg2va}{45}}, a modifiable workflow implemented in GitHub to automatically render manuscripts and automate bibliographical tasks\textsuperscript{\protect\hyperlink{ref-YuJbg3zO}{46}}.
+We wrote this manuscript using Manubot\textsuperscript{\protect\hyperlink{ref-Re6Eg2va}{49}}, a modifiable workflow implemented in GitHub to automatically render manuscripts and automate bibliographical tasks\textsuperscript{\protect\hyperlink{ref-YuJbg3zO}{50}}.
 Manubot uses GitHub's automation workflow, GitHub Actions, to combine and convert individual Markdown files into a single LaTeX document, which can then be converted to a Word or PDF document, and displayed as a webpage.
@@
 Certain journals or software development communities require submitted work or research code to be hosted on GitHub and their review processes make use of GitHub Issues (\emph{e.g.}, rOpenSci (\url{https://ropensci.org/software-review/}), Journal of Open Source Software (\url{https://joss.readthedocs.io/en/latest/submitting.html})).
-rOpenSci's efforts have resulted in many well-used R packages for ecology research including \texttt{rfishbase}\textsuperscript{\protect\hyperlink{ref-Xsdcv6q}{47}} and \texttt{taxize}\textsuperscript{\protect\hyperlink{ref-FVBWKkZu}{48}}.
+rOpenSci's efforts have resulted in many well-used R packages for ecology research including \texttt{rfishbase}\textsuperscript{\protect\hyperlink{ref-Xsdcv6q}{51}} and \texttt{taxize}\textsuperscript{\protect\hyperlink{ref-FVBWKkZu}{52}}.
 
@@
 Scientific publications often omit part of their intellectual and computational workflows, including the treatment of raw data and analytical steps (\emph{e.g.}, model assumption testing).
-Publishing data and reproducible workflows along with manuscripts can provide readers with all details about analytical steps and enable reproducing research experiments and results\textsuperscript{\protect\hyperlink{ref-NOgBWVAr}{49}}.
+Publishing data and reproducible workflows along with manuscripts can provide readers with all details about analytical steps and enable reproducing research experiments and results\textsuperscript{\protect\hyperlink{ref-NOgBWVAr}{53}}.
 In addition to storing data and code, GitHub repositories can provide a time-stamped (version controlled) preregistration of research plans and hypotheses.
@@
 GitHub can serve as a tool for open and tractable research development.
-Collaborators can directly interact with code and data, inspect for errors, and potentially identify scientific misconduct prior to manuscript submission (\emph{e.g.},\textsuperscript{\protect\hyperlink{ref-18PTmKJkq}{50}}).
+Collaborators can directly interact with code and data, inspect for errors, and potentially identify scientific misconduct prior to manuscript submission (\emph{e.g.},\textsuperscript{\protect\hyperlink{ref-18PTmKJkq}{54}}).
 Collaborators and readers are better positioned to discover erroneous or questionable findings if they have complete and transparent access to projects.
@@
 
-Projects in ecology and evolution often involve graduate students, research assistants, and post-doctoral fellows, who hold limited-term positions\textsuperscript{\protect\hyperlink{ref-D4C4k4ak}{51}}.
+Projects in ecology and evolution often involve graduate students, research assistants, and post-doctoral fellows, who hold limited-term positions\textsuperscript{\protect\hyperlink{ref-D4C4k4ak}{55}}.
 Without clear plans on project continuity, the research code and data management upkeep tends to fall off as researchers move on to new projects or to other institutions.
-Additionally, code and data can be difficult to access when kept only on personal devices\textsuperscript{\protect\hyperlink{ref-19kmNxiHc}{52}}.
-
-GitHub can facilitate project continuity among research code by making code handover easier\textsuperscript{\protect\hyperlink{ref-4ny1onB0}{8},\protect\hyperlink{ref-D4C4k4ak}{51}}.
+Additionally, code and data can be difficult to access when kept only on personal devices\textsuperscript{\protect\hyperlink{ref-19kmNxiHc}{56}}.
+
+GitHub can facilitate project continuity among research code by making code handover easier\textsuperscript{\protect\hyperlink{ref-4ny1onB0}{8},\protect\hyperlink{ref-D4C4k4ak}{55}}.
 Through version control, the history of code and data from projects in ecology and evolution can be tracked accessible to future laboratory members and collaborators\textsuperscript{\protect\hyperlink{ref-3DKwn1sY}{12}}.
-Repositories and organizations can have designated data and code owners (or more appropriate, stewards; see\textsuperscript{\protect\hyperlink{ref-iIEKCTLU}{40}},\textsuperscript{\protect\hyperlink{ref-s91uGRZ2}{53}}), who can also can change through time allowing for the transition of code between research cohorts.
+Repositories and organizations can have designated data and code owners (or more appropriate, stewards; see\textsuperscript{\protect\hyperlink{ref-iIEKCTLU}{41}},\textsuperscript{\protect\hyperlink{ref-s91uGRZ2}{57}}), who can also can change through time allowing for the transition of code between research cohorts.
 Other project collaborators can contribute to repository design and development, and their active involvement can both aid authors ability to act as guarantors of the project, and the clarity and reproducibility of the project for future users.
@@
 
-Automation has a strong potential to expand the scale and pace of research in ecology and evolution\textsuperscript{\protect\hyperlink{ref-cfgXxgt1}{54}}.
-Automation frameworks can streamline many stages of the scientific process, including automated data collection and data validation (\emph{e.g.},\textsuperscript{\protect\hyperlink{ref-bhDgD6lF}{55},\protect\hyperlink{ref-lXvpQxeN}{56}}), automated data analysis (\emph{e.g.},\textsuperscript{\protect\hyperlink{ref-Qh7xTLwz}{57}}), automated archiving and deployment of data, code and reports (\emph{e.g.}, this manuscript,\textsuperscript{\protect\hyperlink{ref-SirQKFIz}{58}}).
-In this context, small modifications to code and data can be frequently committed and automatically tested, as in continuous integration and continuous deployment practices\textsuperscript{\protect\hyperlink{ref-1Ep9EJL6y}{59}}.
-This allows for early detection and correction of errors, potentially improving confidence in scientific development by minimizing software errors (see\textsuperscript{\protect\hyperlink{ref-ufw0ZdnI}{60}}).
-In addition to increasing scientific rigor and confidence in ecological software\textsuperscript{\protect\hyperlink{ref-12103x16N}{61}}, automation can help advance more rapidly sharing ecological data and making sure the data are high quality\textsuperscript{\protect\hyperlink{ref-rTbinQMj}{62}}.
-Integrating automation workflows has been highly encouraged in areas of EEB, including predictive ecology\textsuperscript{\protect\hyperlink{ref-mmCOSRfr}{63}}, long-term ecological studies\textsuperscript{\protect\hyperlink{ref-1CJo8lo2v}{64},\protect\hyperlink{ref-RxK4CmfR}{65}}, and management of species at risk information\textsuperscript{\protect\hyperlink{ref-kZzfmBNu}{66}}.
-
-Automation can be integrated into GitHub repositories through the GitHub Actions feature\textsuperscript{\protect\hyperlink{ref-NUXbp429}{67}}, or through alternative automation systems (\emph{e.g.}, Circle CI\textsuperscript{\protect\hyperlink{ref-T03Api6e}{68}}, Travis CI\textsuperscript{\protect\hyperlink{ref-YeFSbfFV}{69}}).
+Automation has a strong potential to expand the scale and pace of research in ecology and evolution\textsuperscript{\protect\hyperlink{ref-cfgXxgt1}{58}}.
+Automation frameworks can streamline many stages of the scientific process, including automated data collection and data validation (\emph{e.g.},\textsuperscript{\protect\hyperlink{ref-bhDgD6lF}{59},\protect\hyperlink{ref-lXvpQxeN}{60}}), automated data analysis (\emph{e.g.},\textsuperscript{\protect\hyperlink{ref-Qh7xTLwz}{61}}), automated archiving and deployment of data, code and reports (\emph{e.g.}, this manuscript,\textsuperscript{\protect\hyperlink{ref-SirQKFIz}{62}}).
+In this context, small modifications to code and data can be frequently committed and automatically tested, as in continuous integration and continuous deployment practices\textsuperscript{\protect\hyperlink{ref-1Ep9EJL6y}{63}}.
+This allows for early detection and correction of errors, potentially improving confidence in scientific development by minimizing software errors (see\textsuperscript{\protect\hyperlink{ref-ufw0ZdnI}{64}}).
+In addition to increasing scientific rigor and confidence in ecological software\textsuperscript{\protect\hyperlink{ref-12103x16N}{65}}, automation can help advance more rapidly sharing ecological data and making sure the data are high quality\textsuperscript{\protect\hyperlink{ref-rTbinQMj}{66}}.
+Integrating automation workflows has been highly encouraged in areas of EEB, including predictive ecology\textsuperscript{\protect\hyperlink{ref-mmCOSRfr}{67}}, long-term ecological studies\textsuperscript{\protect\hyperlink{ref-1CJo8lo2v}{68},\protect\hyperlink{ref-RxK4CmfR}{69}}, and management of species at risk information\textsuperscript{\protect\hyperlink{ref-kZzfmBNu}{70}}.
+
+Automation can be integrated into GitHub repositories through the GitHub Actions feature\textsuperscript{\protect\hyperlink{ref-NUXbp429}{71}}, or through alternative automation systems (\emph{e.g.}, Circle CI\textsuperscript{\protect\hyperlink{ref-T03Api6e}{72}}, Travis CI\textsuperscript{\protect\hyperlink{ref-YeFSbfFV}{73}}).
 Users can set up workflows associated with their repositories that are triggered by events (\emph{e.g.}, push, pull request or at specified times) for remote servers to perform user-specified steps and actions.
@@
 
-There have been many calls for researchers outside of the software development community to adopt GitHub to improve their collaborative research\textsuperscript{\protect\hyperlink{ref-10ghgV3S8}{3},\protect\hyperlink{ref-1Du6fzB8g}{39},\protect\hyperlink{ref-UsTxAq4f}{70}}.
+There have been many calls for researchers outside of the software development community to adopt GitHub to improve their collaborative research\textsuperscript{\protect\hyperlink{ref-10ghgV3S8}{3},\protect\hyperlink{ref-1Du6fzB8g}{40},\protect\hyperlink{ref-UsTxAq4f}{74}}.
 These calls come in light of the continuous shift towards open-science and the increasing computational and data requirements in EEB.
@@
 This openness may add additional pressure to students and scientists learning to use the platform.
-File storage is size-limited on GitHub (but note that large files stored locally can still be versioned; see section ``Storing and sharing research compendia''), requiring the complementation of other tools to fully integration project files and GitHub repositories (\emph{e.g.},\textsuperscript{\protect\hyperlink{ref-lx49NGto}{71}}).
+File storage is size-limited on GitHub (but note that large files stored locally can still be versioned; see section ``Storing and sharing research compendia''), requiring the complementation of other tools to fully integration project files and GitHub repositories (\emph{e.g.},\textsuperscript{\protect\hyperlink{ref-lx49NGto}{75}}).
 A major additional barrier to EEB researchers is the lack language-specific resources for non-English speaking researchers working in ecology and evolution.
-Language is a well-known obstacle to international collaborative research progress and to widespread scientific knowledge\textsuperscript{see \protect\hyperlink{ref-cW7vGddM}{72}}.
+Language is a well-known obstacle to international collaborative research progress and to widespread scientific knowledge\textsuperscript{see \protect\hyperlink{ref-cW7vGddM}{76}}.
 Non-English speaking EEB researchers can potentially miss opportunities to fully integrate version control, reproducibility, and other benefits of GitHub without language-inclusive contents.
@@
 \\
-2. \textbf{Consider taking free courses}, such as those from Software Carpentry\textsuperscript{\protect\hyperlink{ref-pjy75gHr}{73}}, and sharing these courses with your lab members or colleagues. \\
+2. \textbf{Consider taking free courses}, such as those from Software Carpentry\textsuperscript{\protect\hyperlink{ref-pjy75gHr}{77}}, and sharing these courses with your lab members or colleagues. \\
 3.
@@
 6.
-\textbf{Consult online resources.} The Jenny Bryan Universe of GitHub material, for example, provides a thorough and accessible introduction for a multitude of research-related uses for GitHub, and includes a book\textsuperscript{\protect\hyperlink{ref-ZvrOcg9w}{74}}, statistics course\textsuperscript{\protect\hyperlink{ref-6CMMeSeD}{75}} and academic article\textsuperscript{\protect\hyperlink{ref-RVetqmsg}{7}}.
+\textbf{Consult online resources.} The Jenny Bryan Universe of GitHub material, for example, provides a thorough and accessible introduction for a multitude of research-related uses for GitHub, and includes a book\textsuperscript{\protect\hyperlink{ref-ZvrOcg9w}{78}}, statistics course\textsuperscript{\protect\hyperlink{ref-6CMMeSeD}{79}} and academic article\textsuperscript{\protect\hyperlink{ref-RVetqmsg}{7}}.
 \\
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-1HhzKAC1K}{}}%
+\CSLLeftMargin{22. }
+\CSLRightInline{Goring, S.
+J.
+\emph{et al.} \href{https://doi.org/10.1890/120370}{Improving the culture of interdisciplinary collaboration in ecology by expanding measures of success}.
+\emph{Frontiers in Ecology and the Environment} \textbf{12}, 39--47 (2014).}
+
 \leavevmode\vadjust pre{\hypertarget{ref-RhBKe0MG}{}}%
-\CSLLeftMargin{22. }
+\CSLLeftMargin{23. }
 \CSLRightInline{About Projects. \emph{GitHub Docs} \url{https://ghdocs-prod.azurewebsites.net/en/issues/planning-and-tracking-with-projects/learning-about-projects/about-projects}.}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-1GRWGlDWy}{}}%
-\CSLLeftMargin{23. }
+\CSLLeftMargin{24. }
 \CSLRightInline{Slack. GitHub for Slack. \emph{Slack Help Center} \url{https://slack.com/help/articles/232289568-GitHub-for-Slack}.}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-QqMezOMg}{}}%
-\CSLLeftMargin{24. }
+\CSLLeftMargin{25. }
 \CSLRightInline{Xie, Y., Allaire, J. J. \& Grolemund, G. \emph{R Markdown: the definitive guide}. (CRC Press, Taylor and Francis Group, 2019).}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-MDQfMwCW}{}}%
-\CSLLeftMargin{25. }
+\CSLLeftMargin{26. }
 \CSLRightInline{Quickstart for GitHub Pages. \emph{GitHub Docs} \url{https://ghdocs-prod.azurewebsites.net/en/pages/quickstart}.}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-dqrFjoSb}{}}%
-\CSLLeftMargin{26. }
+\CSLLeftMargin{27. }
 \CSLRightInline{Trujillo, G.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-HiIPSSHV}{}}%
-\CSLLeftMargin{27. }
+\CSLLeftMargin{28. }
 \CSLRightInline{Smaglik, P.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-MXxgZJ45}{}}%
-\CSLLeftMargin{28. }
+\CSLLeftMargin{29. }
 \CSLRightInline{Dawson, C. \emph{Building tools with GitHub: customize your workflow}. (O'Reilly, 2016).}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-PLmDFZrm}{}}%
-\CSLLeftMargin{29. }
+\CSLLeftMargin{30. }
 \CSLRightInline{Tenopir, C.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-1Hcf13Q0k}{}}%
-\CSLLeftMargin{30. }
+\CSLLeftMargin{31. }
 \CSLRightInline{Nugroho, R.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-1Ch6LSHef}{}}%
-\CSLLeftMargin{31. }
+\CSLLeftMargin{32. }
 \CSLRightInline{Wicherts, J.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-SLq38RVv}{}}%
-\CSLLeftMargin{32. }
+\CSLLeftMargin{33. }
 \CSLRightInline{Figueiredo, A. S. \href{https://doi.org/10.3389/fpubh.2017.00327}{Data Sharing: Convert Challenges into Opportunities}. \emph{Front. Public Health} \textbf{5}, (2017).}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-1CzUZwyU2}{}}%
-\CSLLeftMargin{33. }
+\CSLLeftMargin{34. }
 \CSLRightInline{Tenopir, C.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-666HppfO}{}}%
-\CSLLeftMargin{34. }
+\CSLLeftMargin{35. }
 \CSLRightInline{Pronk, T.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-1CcAUn3Lu}{}}%
-\CSLLeftMargin{35. }
+\CSLLeftMargin{36. }
 \CSLRightInline{Piwowar, H.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-4LaijDIZ}{}}%
-\CSLLeftMargin{36. }
+\CSLLeftMargin{37. }
 \CSLRightInline{\href{https://doi.org/10.1038/ncb3506}{On data availability, reproducibility and reuse}. \emph{Nat Cell Biol} \textbf{19}, 259--259 (2017).}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-uBJwnPbq}{}}%
-\CSLLeftMargin{37. }
+\CSLLeftMargin{38. }
 \CSLRightInline{Mislan, K.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-1HZdsK5Kn}{}}%
-\CSLLeftMargin{38. }
+\CSLLeftMargin{39. }
 \CSLRightInline{Baker, M. \href{https://doi.org/10.1038/533452a}{1,500 scientists lift the lid on reproducibility}. \emph{Nature} \textbf{533}, 452--454 (2016).}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-1Du6fzB8g}{}}%
-\CSLLeftMargin{39. }
+\CSLLeftMargin{40. }
 \CSLRightInline{Crystal‐Ornelas, R.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-iIEKCTLU}{}}%
-\CSLLeftMargin{40. }
+\CSLLeftMargin{41. }
 \CSLRightInline{Hampton, S. E. \emph{et al.} \href{https://doi.org/10.1890/es14-00402.1}{The Tao of open science for ecology}. \emph{Ecosphere} \textbf{6}, art120 (2015).}
 
+\leavevmode\vadjust pre{\hypertarget{ref-GQj3c17f}{}}%
+\CSLLeftMargin{42. }
+\CSLRightInline{Hudgins, E. \emph{emmajhudgins/UStreedamage: publication release}. (Zenodo, 2022). doi:\href{https://doi.org/10.5281/zenodo.6097109}{10.5281/zenodo.6097109}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-bZNn2hbh}{}}%
+\CSLLeftMargin{43. }
+\CSLRightInline{EllenJCoombs. \emph{EllenJCoombs/Asymmetry-evolution-cetaceans-for-publication-v.1.0.0}. (Zenodo, 2020). doi:\href{https://doi.org/10.5281/zenodo.3893943}{10.5281/zenodo.3893943}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-ZI1OqZNr}{}}%
+\CSLLeftMargin{44. }
+\CSLRightInline{Lrharper1.
+Hulluni-Bioinformatics/Harper\_Et\_Al\_2018: Github Repository Deposited With Harper Et Al.
+(2018) In Ecology And Evolution.
+at \url{https://doi.org/10.5281/zenodo.1188710} (2018).}
+
 \leavevmode\vadjust pre{\hypertarget{ref-TOsASkn5}{}}%
-\CSLLeftMargin{41. }
+\CSLLeftMargin{45. }
 \CSLRightInline{Adding a license to a repository.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-1BJcvyTmV}{}}%
-\CSLLeftMargin{42. }
+\CSLLeftMargin{46. }
 \CSLRightInline{Vale, G., Schmid, A., Santos, A.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-K7nbP1Ty}{}}%
-\CSLLeftMargin{43. }
+\CSLLeftMargin{47. }
 \CSLRightInline{Crystal-Ornelas, R.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-hm9PaCLD}{}}%
-\CSLLeftMargin{44. }
+\CSLLeftMargin{48. }
 \CSLRightInline{Song, X., Goldstein, S.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Re6Eg2va}{}}%
-\CSLLeftMargin{45. }
+\CSLLeftMargin{49. }
 \CSLRightInline{Manubot - Manuscripts, open and automated. \url{https://manubot.org}.}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-YuJbg3zO}{}}%
-\CSLLeftMargin{46. }
+\CSLLeftMargin{50. }
 \CSLRightInline{Himmelstein, D. S. \emph{et al.} \href{https://doi.org/10.1371/journal.pcbi.1007128}{Open collaborative writing with Manubot}. \emph{PLoS Comput Biol} \textbf{15}, e1007128 (2019).}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Xsdcv6q}{}}%
-\CSLLeftMargin{47. }
+\CSLLeftMargin{51. }
 \CSLRightInline{Boettiger, C., Lang, D.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-FVBWKkZu}{}}%
-\CSLLeftMargin{48. }
+\CSLLeftMargin{52. }
 \CSLRightInline{Chamberlain, S. A. \& Szöcs, E. \href{https://doi.org/10.12688/f1000research.2-191.v2}{taxize: taxonomic search and retrieval in R}. \emph{F1000Res} \textbf{2}, 191 (2013).}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-NOgBWVAr}{}}%
-\CSLLeftMargin{49. }
+\CSLLeftMargin{53. }
 \CSLRightInline{Culina, A., van den Berg, I., Evans, S.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-18PTmKJkq}{}}%
-\CSLLeftMargin{50. }
+\CSLLeftMargin{54. }
 \CSLRightInline{January 18, P.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-D4C4k4ak}{}}%
-\CSLLeftMargin{51. }
+\CSLLeftMargin{55. }
 \CSLRightInline{Fehr, J., Himpe, C., Rave, S. \& Saak, J. \href{https://doi.org/10.5334/jors.307}{Sustainable Research Software Hand-Over}. \emph{JORS} \textbf{9}, 5 (2021).}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-19kmNxiHc}{}}%
-\CSLLeftMargin{52. }
+\CSLLeftMargin{56. }
 \CSLRightInline{Vines, Timothy~H.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-s91uGRZ2}{}}%
-\CSLLeftMargin{53. }
+\CSLLeftMargin{57. }
 \CSLRightInline{About code owners.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-cfgXxgt1}{}}%
-\CSLLeftMargin{54. }
+\CSLLeftMargin{58. }
 \CSLRightInline{Keitt, T. H. \& Abelson, E. S. \href{https://doi.org/10.1126/science.abi4692}{Ecology in the age of automation}. \emph{Science} \textbf{373}, 858--859 (2021).}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-bhDgD6lF}{}}%
-\CSLLeftMargin{55. }
+\CSLLeftMargin{59. }
 \CSLRightInline{Micheletti, T.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-lXvpQxeN}{}}%
-\CSLLeftMargin{56. }
+\CSLLeftMargin{60. }
 \CSLRightInline{Yenni, G. M. \emph{et al.} Developing a modern data workflow for evolving data. (2018) doi:\href{https://doi.org/10.1101/344804}{10.1101/344804}.}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Qh7xTLwz}{}}%
-\CSLLeftMargin{57. }
+\CSLLeftMargin{61. }
 \CSLRightInline{Beaulieu-Jones, B.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-SirQKFIz}{}}%
-\CSLLeftMargin{58. }
+\CSLLeftMargin{62. }
 \CSLRightInline{White, E.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-1Ep9EJL6y}{}}%
-\CSLLeftMargin{59. }
+\CSLLeftMargin{63. }
 \CSLRightInline{Meyer, M. \href{https://doi.org/10.1109/ms.2014.58}{Continuous Integration and Its Tools}. \emph{IEEE Softw.} \textbf{31}, 14--16 (2014).}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-ufw0ZdnI}{}}%
-\CSLLeftMargin{60. }
+\CSLLeftMargin{64. }
 \CSLRightInline{Soergel, D. A. W. \href{https://doi.org/10.12688/f1000research.5930.2}{Rampant software errors may undermine scientific results}. \emph{F1000Res} \textbf{3}, 303 (2015).}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-12103x16N}{}}%
-\CSLLeftMargin{61. }
+\CSLLeftMargin{65. }
 \CSLRightInline{Scheller, R.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-rTbinQMj}{}}%
-\CSLLeftMargin{62. }
+\CSLLeftMargin{66. }
 \CSLRightInline{Dietze, M.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-mmCOSRfr}{}}%
-\CSLLeftMargin{63. }
+\CSLLeftMargin{67. }
 \CSLRightInline{McIntire, E.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-1CJo8lo2v}{}}%
-\CSLLeftMargin{64. }
+\CSLLeftMargin{68. }
 \CSLRightInline{Yenni, G.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-RxK4CmfR}{}}%
-\CSLLeftMargin{65. }
+\CSLLeftMargin{69. }
 \CSLRightInline{Ernest, S. K. M. \emph{et al.} The Portal Project: a long-term study of a Chihuahuan desert ecosystem. (2018) doi:\href{https://doi.org/10.1101/332783}{10.1101/332783}.}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-kZzfmBNu}{}}%
-\CSLLeftMargin{66. }
+\CSLLeftMargin{70. }
 \CSLRightInline{Naujokaitis-Lewis, I., Endicott, S.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-NUXbp429}{}}%
-\CSLLeftMargin{67. }
+\CSLLeftMargin{71. }
 \CSLRightInline{Features • GitHub Actions. \emph{GitHub} \url{https://github.com/features/actions}.}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-T03Api6e}{}}%
-\CSLLeftMargin{68. }
+\CSLLeftMargin{72. }
 \CSLRightInline{Continuous Integration and Delivery. \emph{CircleCI} \url{https://circleci.com/}.}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-YeFSbfFV}{}}%
-\CSLLeftMargin{69. }
+\CSLLeftMargin{73. }
 \CSLRightInline{Homepage \textbar{} Travis CI -- Start building today! \emph{Travis CI} \url{https://www.travis-ci.com/}.}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-UsTxAq4f}{}}%
-\CSLLeftMargin{70. }
+\CSLLeftMargin{74. }
 \CSLRightInline{Anbaroğlu, B. \href{https://doi.org/10.1111/tgis.12810}{A collaborative GIS programming course using GitHub Classroom}. \emph{Transactions in GIS} \textbf{25}, 3132--3158 (2021).}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-lx49NGto}{}}%
-\CSLLeftMargin{71. }
+\CSLLeftMargin{75. }
 \CSLRightInline{Connect GitHub to a Project - OSF Support. \url{https://help.osf.io/article/211-connect-github-to-a-project}.}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-cW7vGddM}{}}%
-\CSLLeftMargin{72. }
+\CSLLeftMargin{76. }
 \CSLRightInline{Khelifa, R., Amano, T.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-pjy75gHr}{}}%
-\CSLLeftMargin{73. }
+\CSLLeftMargin{77. }
 \CSLRightInline{Madicken Munk \emph{et al.} swcarpentry/git-novice: Software Carpentry: Version Control with Git, June 2019. at \url{https://doi.org/10.5281/zenodo.3264950} (2019).}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-ZvrOcg9w}{}}%
-\CSLLeftMargin{74. }
+\CSLLeftMargin{78. }
 \CSLRightInline{Hester, J. B., the STAT 545 TAs, Jim. \emph{\href{https://happygitwithr.com/}{Let's Git started \textbar{} Happy Git and GitHub for the useR}}.}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-6CMMeSeD}{}}%
-\CSLLeftMargin{75. }
+\CSLLeftMargin{79. }
 \CSLRightInline{Bryan, J. \& TAs, T. S. 545. \emph{\href{https://stat545.com/}{STAT 545}}.}

### 2022-10-02 manuscript.tex
Merge pull request #274 from SORTEE-Github-Hackathon/RCO-edits-october [ci skip]
This build is based on
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/67184a6d4709f90ee2da7a7f13a18ae8b930330f.

This commit was created by the following CI build and job:
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/67184a6d4709f90ee2da7a7f13a18ae8b930330f/checks
https://github.com/SORTEE-Github-Hackathon/manuscript/actions/runs/3169645123

@@
 This manuscript
-(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/ec11faeb0bef6e3bab5ff066c8b7786218ca8fe5/}{permalink})
+(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/67184a6d4709f90ee2da7a7f13a18ae8b930330f/}{permalink})
 was automatically generated
-from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/ec11faeb0bef6e3bab5ff066c8b7786218ca8fe5}{SORTEE-Github-Hackathon/manuscript@ec11fae}
-on September 22, 2022.
+from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/67184a6d4709f90ee2da7a7f13a18ae8b930330f}{SORTEE-Github-Hackathon/manuscript@67184a6}
+on October 2, 2022.
 
@@
 First-time users without formal training in information technology may face steep learning curves because GitHub and its features have been centered on collaboration for code development in information systems\textsuperscript{\protect\hyperlink{ref-139b0pSGc}{13}}.
-Moreover, domain-specific resources providing tractable examples and practical guidance for researchers in EEB on GitHub are scarce (but see \url{https://ourcodingclub.github.io}; \url{https://www.openscapes.org}).
-Widespread adoption of GitHub for collaborating on research tasks can ultimately enable EEB researchers to spend less time on creating novel processes for collaboration and more time on their research\textsuperscript{\protect\hyperlink{ref-ydrk01SR}{14}}.
-More importantly, expanding the availability of data and code management standards -- of which GitHub is one increasingly important component -- makes research more reproducible and collaborative\textsuperscript{\protect\hyperlink{ref-13QX8XU3J}{15},\protect\hyperlink{ref-pq2Tv1BC}{16}}.
+Moreover, domain-specific resources providing tractable examples and practical guidance for researchers in EEB on GitHub are scarce (but see \url{https://ourcodingclub.github.io}; \url{https://www.openscapes.org},\textsuperscript{\protect\hyperlink{ref-lJAgyhYq}{14}}).
+Widespread adoption of GitHub for collaborating on research tasks can ultimately enable EEB researchers to spend less time on creating novel processes for collaboration and more time on their research\textsuperscript{\protect\hyperlink{ref-ydrk01SR}{15}}.
+More importantly, expanding the availability of data and code management standards -- of which GitHub is one increasingly important component -- makes research more reproducible and collaborative\textsuperscript{\protect\hyperlink{ref-13QX8XU3J}{16},\protect\hyperlink{ref-pq2Tv1BC}{17}}.
 
@@
 Having copies of these files safely stored is essential to protect against accidental modifications or deletions.
-Many researchers begin using GitHub to store (or backup) their research compendium\textsuperscript{\protect\hyperlink{ref-MwwMapRG}{17}} to a centralized, readily-available remote server (see \protect\hyperlink{definitions}{Box 1}).
+Many researchers begin using GitHub to store (or backup) their research compendium\textsuperscript{\protect\hyperlink{ref-MwwMapRG}{18}} to a centralized, readily-available remote server (see \protect\hyperlink{definitions}{Box 1}).
 A centralized research compendium stored in a version-controlled repository has the advantages of facilitating collaboration, integrating data and code archiving services, allowing file versions to be accessed and restored, and contributes to open science (see sections below).
 
-GitHub limits committed file sizes to 100 Mb (megabytes\textsuperscript{\protect\hyperlink{ref-1Co6ZZjF1}{18}}), which can make it challenging for centralizing research compendia containing larger file sizes.
-Users may still version large files using Git Large File Storage\textsuperscript{\protect\hyperlink{ref-11GtZ7icJ}{19}} text pointers, but may have to rely on external file storage alternatives (such as local or cloud-hosting).
+GitHub limits committed file sizes to 100 Mb (megabytes\textsuperscript{\protect\hyperlink{ref-1Co6ZZjF1}{19}}), which can make it challenging for centralizing research compendia containing larger file sizes.
+Users may still version large files using Git Large File Storage\textsuperscript{\protect\hyperlink{ref-11GtZ7icJ}{20}} text pointers, but may have to rely on external file storage alternatives (such as local or cloud-hosting).
 
@@
 
-Laboratory notebooks help researchers track their research notes, methods, policies and protocols\textsuperscript{\protect\hyperlink{ref-wwHxTOtm}{20}}.
-Virtual laboratory notebooks can be stored in GitHub repositories and provide the benefits of simultaneous, centralized and selective access, and allows for the easy update of policies and experiment protocols\textsuperscript{\protect\hyperlink{ref-10V7x4H4l}{21}}.
+Laboratory notebooks help researchers track their research notes, methods, policies and protocols\textsuperscript{\protect\hyperlink{ref-wwHxTOtm}{21}}.
+Virtual laboratory notebooks can be stored in GitHub repositories and provide the benefits of simultaneous, centralized and selective access, and allows for the easy update of policies and experiment protocols\textsuperscript{\protect\hyperlink{ref-10V7x4H4l}{22}}.
 Researchers have been increasingly using GitHub to maintain versions and share digital laboratory notebooks across many fields\textsuperscript{\protect\hyperlink{ref-10ghgV3S8}{3}}, including applied ecology (\emph{e.g.}, \url{https://scheuerell-lab.github.io/lab-book}), biogeography and global change biology (\emph{e.g.}, \url{https://github.com/HuckleyLab/how_we_work}), and microbial ecology (\emph{e.g.}, \url{https://github.com/CarBBAS/uqam-guide}).
@@
 
-Modern research in ecology and evolution is highly collaborative, bringing together multidisciplinary teams from various institutions\textsuperscript{\protect\hyperlink{ref-1HhzKAC1K}{22}}.
+Modern research in ecology and evolution is highly collaborative, bringing together multidisciplinary teams from various institutions\textsuperscript{\protect\hyperlink{ref-1HhzKAC1K}{23}}.
 On GitHub, collaborators can share feedback, brainstorm ideas, and troubleshoot problems (Figure \ref{fig:github-diagram}).
@@
 Github Discussions serve as a message board for conversation.
-Finally, GitHub Projects integrate issues and pull requests on automated spreadsheets and project boards, providing users with real-time tracking of project priorities and status\textsuperscript{\protect\hyperlink{ref-RhBKe0MG}{23}}.
+Finally, GitHub Projects integrate issues and pull requests on automated spreadsheets and project boards, providing users with real-time tracking of project priorities and status\textsuperscript{\protect\hyperlink{ref-RhBKe0MG}{24}}.
 Scripts, commit messages, and pull requests can be linked directly to issues, discussions, and projects providing a clear record of project workflow.
-For instance, one can create a discussion on a project repository to decide on which method to apply for analyzing biodiversity data, and then an issue can be created with the purpose of establishing the steps and responsibilities covering from data formatting, statistical analyses, until the figure generation and issue resolution {[}\emph{e.g.}, see issues and discussions in the sPlotOpen {[}doi:10.1111/geb.13346{]} manuscript repository (\url{https://github.com/fmsabatini/sPlotOpen_Manuscript/issues?q=is\%3Aissue+is\%3Aclosed}){]}.
+For instance, one can create a discussion on a project repository to decide which method to apply for biodiversity data analysis.
+Then, an issue can be created to establish steps and responsibilities including data formatting, statistical analyses, figure generation, and issue resolution {[}\emph{e.g.}, see issues and discussions in the sPlotOpen {[}doi:10.1111/geb.13346{]} manuscript repository (\url{https://github.com/fmsabatini/sPlotOpen_Manuscript/issues?q=is\%3Aissue+is\%3Aclosed}){]}.
 Using GitHub for all project-related conversation and planning, rather than email or messaging tools, makes it easier to keep track of progress throughout the lifespan of a project.
@@
 Project management in GitHub can also be integrated with third-party applications, such as Zenhub (\url{https://www.zenhub.com}) or Slack (\url{https://slack.github.com}).
-ZenHub allows for the enhanced visualization and organization of repositories and their issues, while the GitHub for Slack integration allows notifications from GitHub events to be sent directly to users or group channels\textsuperscript{\protect\hyperlink{ref-1GRWGlDWy}{24}}.
+Zenhub allows for the enhanced visualization and organization of repositories and their issues, while the GitHub for Slack integration allows notifications from GitHub events to be sent directly to users or group channels\textsuperscript{\protect\hyperlink{ref-1GRWGlDWy}{25}}.
 
@@
 
-Making presentations, syllabi and other course materials can be done through most major high-level programming languages such as R, with \texttt{RMarkdown}\textsuperscript{\protect\hyperlink{ref-QqMezOMg}{25}}, Python, with \texttt{python-ppt} (\url{https://python-pptx.readthedocs.io}), and Julia, with \texttt{Remark.jl} (\url{https://juliapackages.com/p/remark}), and be version-controlled and stored in GitHub.
-Once content is made, hosting a course website can be done through GitHub Pages\textsuperscript{\protect\hyperlink{ref-MDQfMwCW}{26}} (\emph{e.g.}, \url{https://github.com/topics/course-website}).
+Making presentations, syllabi and other course materials can be done through most major high-level programming languages such as R, with \texttt{RMarkdown}\textsuperscript{\protect\hyperlink{ref-QqMezOMg}{26}}, Python, with \texttt{python-ppt} (\url{https://python-pptx.readthedocs.io}), and Julia, with \texttt{Remark.jl} (\url{https://juliapackages.com/p/remark}), and be version-controlled and stored in GitHub.
+Once content is made, hosting a course website can be done through GitHub Pages\textsuperscript{\protect\hyperlink{ref-MDQfMwCW}{27}} (\emph{e.g.}, \url{https://github.com/topics/course-website}).
 This way, course content can be available to enrolled students, as well as a global pool of learners and teachers interested in the material.
@@
 Student submissions are perhaps the most challenging component, but the new GitHub Classroom tool (\url{https://classroom.github.com}) allows instructors to host private assignments to be submitted collaboratively or individually as code or PDF files, and even build autograding tests.
-Although time-consuming to establish, using these features can integrate learning version control and GitHub with the learning course content, and thus boost students' feelings of self-efficacy and confidence\textsuperscript{\protect\hyperlink{ref-dqrFjoSb}{27}}.
+Although time-consuming to establish, using these features can integrate learning version control and GitHub with the learning course content, and thus boost students' feelings of self-efficacy and confidence\textsuperscript{\protect\hyperlink{ref-dqrFjoSb}{28}}.
 
@@
 
-Personal or laboratory websites can improve the sharing of research findings, build online presence, and increase coordination of research efforts\textsuperscript{\protect\hyperlink{ref-HiIPSSHV}{28}}.
+Personal or laboratory websites can improve the sharing of research findings, build online presence, and increase coordination of research efforts\textsuperscript{\protect\hyperlink{ref-HiIPSSHV}{29}}.
 Despite researchers in ecology and evolution generally lacking experience in building or hosting webpages, many tools have been developed to help this process.
@@
 
-Website templates are readily available on GitHub (\url{https://github.com/topics/website-template}) or in user-specific repositories, which can be forked (\protect\hyperlink{definitions}{Box 1}) and customized\textsuperscript{\protect\hyperlink{ref-MXxgZJ45}{29}}.
+Website templates are readily available on GitHub (\url{https://github.com/topics/website-template}) or in user-specific repositories, which can be forked (\protect\hyperlink{definitions}{Box 1}) and customized\textsuperscript{\protect\hyperlink{ref-MXxgZJ45}{30}}.
 Aside from free hosting services, GitHub Pages also allows websites to be autogenerated and instantly updated following content modifications\textsuperscript{\protect\hyperlink{ref-RVetqmsg}{7}}.
@@
 
-Government, funding agencies, and publishers exercise rigorous open access data policies and mandates\textsuperscript{\protect\hyperlink{ref-PLmDFZrm}{30},\protect\hyperlink{ref-1Hcf13Q0k}{31}}.
-However, code and data sharing may be met by individual reluctance, temporary embargoes, or partially prevented by privacy and confidentiality reasons\textsuperscript{\protect\hyperlink{ref-1Ch6LSHef}{32}--\protect\hyperlink{ref-1CzUZwyU2}{34}}.
-Still, data deposition and ensuring its availability can amplify the outreach of published studies\textsuperscript{\protect\hyperlink{ref-666HppfO}{35}}, increase citation rates\textsuperscript{\protect\hyperlink{ref-1CcAUn3Lu}{36}}, and among many other reasons, enable the reproducibility and robustness of scientific advances\textsuperscript{\protect\hyperlink{ref-4LaijDIZ}{37}--\protect\hyperlink{ref-1HZdsK5Kn}{39}}.
+Government, funding agencies, and publishers exercise rigorous open access data policies and mandates\textsuperscript{\protect\hyperlink{ref-PLmDFZrm}{31},\protect\hyperlink{ref-1Hcf13Q0k}{32}}.
+However, code and data sharing may be met by individual reluctance, temporary embargoes, or partially prevented by privacy and confidentiality reasons\textsuperscript{\protect\hyperlink{ref-1Ch6LSHef}{33}--\protect\hyperlink{ref-1CzUZwyU2}{35}}.
+Still, data deposition and ensuring its availability can amplify the outreach of published studies\textsuperscript{\protect\hyperlink{ref-666HppfO}{36}}, increase citation rates\textsuperscript{\protect\hyperlink{ref-1CcAUn3Lu}{37}}, and among many other reasons, enable the reproducibility and robustness of scientific advances\textsuperscript{\protect\hyperlink{ref-4LaijDIZ}{38}--\protect\hyperlink{ref-1HZdsK5Kn}{40}}.
 While public repositories on GitHub make it easy to store and share data files, they are not considered long-term repositories for research materials.
@@
 DOIs are persistent and citable unique alpha-numeric identifiers assigned to digitally stored research materials.
-Because of this, scientists sharing code and data through GitHub are strongly encouraged to independently submit their research materials to long-term data archives (\emph{e.g.}, Zenodo, Figshare, Dryad, OSF\textsuperscript{\protect\hyperlink{ref-10ghgV3S8}{3},\protect\hyperlink{ref-kEX5dgzK}{9},\protect\hyperlink{ref-1Du6fzB8g}{40}}; \protect\hyperlink{tbl:compare}{Table 1}).
+Because of this, scientists sharing code and data through GitHub are strongly encouraged to independently submit their research materials to long-term data archives (\emph{e.g.}, Zenodo, Figshare, Dryad, OSF\textsuperscript{\protect\hyperlink{ref-10ghgV3S8}{3},\protect\hyperlink{ref-kEX5dgzK}{9},\protect\hyperlink{ref-1Du6fzB8g}{41}}; \protect\hyperlink{tbl:compare}{Table 1}).
 Some of these options (Zenodo, Figshare and OSF) integrate with GitHub, allowing project, code, and data releases (\protect\hyperlink{definitions}{Box 1}) to be archived with versioned, citable DOIs.
-Linking GitHub repositories with a DOI helps research become findable, properly cited, and can ensure long-term stability\textsuperscript{\protect\hyperlink{ref-iIEKCTLU}{41}}.
-This strategy has been increasingly adopted in numerous studies in ecology and evolution (\emph{e.g.},\textsuperscript{\protect\hyperlink{ref-GQj3c17f}{42}};\textsuperscript{\protect\hyperlink{ref-bZNn2hbh}{43}};\textsuperscript{\protect\hyperlink{ref-ZI1OqZNr}{44}}).
+Linking GitHub repositories with a DOI helps research become findable, properly cited, and can ensure long-term stability\textsuperscript{\protect\hyperlink{ref-iIEKCTLU}{42}}.
+This strategy has been increasingly adopted in numerous studies in ecology and evolution (\emph{e.g.},\textsuperscript{\protect\hyperlink{ref-GQj3c17f}{43}};\textsuperscript{\protect\hyperlink{ref-bZNn2hbh}{44}};\textsuperscript{\protect\hyperlink{ref-ZI1OqZNr}{45}}).
 
@@
 Code published without a license is under exclusive copyright (by default), protecting it from copy, distribution, and modifications.
-One may grant specific rights to their code for reuse by adding licensing files and specifications within GitHub repositories\textsuperscript{\protect\hyperlink{ref-TOsASkn5}{45}}.
+One may grant specific rights to their code for reuse by adding licensing files and specifications within GitHub repositories\textsuperscript{\protect\hyperlink{ref-TOsASkn5}{46}}.
 The Choose a License (\url{https://choosealicense.com/non-software/}) website offers further guidance on the licenses available for research and creative products.
@@
 By forking, branching, and cloning repositories (\protect\hyperlink{definitions}{Box 1}), researchers can simultaneously work on different issues of the same research project to then later merge changes to the main branch project with pull requests.
-Explicit project organization and increased communication in GitHub Issues, Discussions, or within pull requests can help with project development and with potential merge conflicts due to users simultaneously working on the same sections\textsuperscript{\protect\hyperlink{ref-1BJcvyTmV}{46}}.
-Moreover, version control\textsuperscript{\protect\hyperlink{ref-K7nbP1Ty}{47}} and commit reversal features allow researchers to track and progress without worrying about irreparably modifying someone else's work.
+Explicit project organization and increased communication in GitHub Issues, Discussions, or within pull requests can help with project development and with potential merge conflicts due to users simultaneously working on the same sections\textsuperscript{\protect\hyperlink{ref-1BJcvyTmV}{47}}.
+Moreover, version control\textsuperscript{\protect\hyperlink{ref-K7nbP1Ty}{48}} and commit reversal features allow researchers to track and progress without worrying about irreparably modifying someone else's work.
 By enabling more comprehensive remote collaboration, GitHub encourages the exchange of ideas among researchers at different institutions and in different countries, which can serve to improve the quality of the research itself by providing open access to data and code.
 In academic settings, GitHub can also facilitate interactions between research advisors and advisees, providing a platform for students or other trainees to share in-progress code, and flag specific challenges or questions for their supervisors or mentors (\protect\hyperlink{tbl:roles}{Table 2}).
-Periodic code review\textsuperscript{\protect\hyperlink{ref-hm9PaCLD}{48}} can also help advisors identify errors early in the process, and inform further training and mentorship to fill gaps in skills.
+Periodic code review\textsuperscript{\protect\hyperlink{ref-hm9PaCLD}{49}} can also help advisors identify errors early in the process, and inform further training and mentorship to fill gaps in skills.
 
@@
 
-We wrote this manuscript using Manubot\textsuperscript{\protect\hyperlink{ref-Re6Eg2va}{49}}, a modifiable workflow implemented in GitHub to automatically render manuscripts and automate bibliographical tasks\textsuperscript{\protect\hyperlink{ref-YuJbg3zO}{50}}.
+We wrote this manuscript using Manubot\textsuperscript{\protect\hyperlink{ref-Re6Eg2va}{50}}, a modifiable workflow implemented in GitHub to automatically render manuscripts and automate bibliographical tasks\textsuperscript{\protect\hyperlink{ref-YuJbg3zO}{51}}.
 Manubot uses GitHub's automation workflow, GitHub Actions, to combine and convert individual Markdown files into a single LaTeX document, which can then be converted to a Word or PDF document, and displayed as a webpage.
@@
 Certain journals or software development communities require submitted work or research code to be hosted on GitHub and their review processes make use of GitHub Issues (\emph{e.g.}, rOpenSci (\url{https://ropensci.org/software-review/}), Journal of Open Source Software (\url{https://joss.readthedocs.io/en/latest/submitting.html})).
-rOpenSci's efforts have resulted in many well-used R packages for ecology research including \texttt{rfishbase}\textsuperscript{\protect\hyperlink{ref-Xsdcv6q}{51}} and \texttt{taxize}\textsuperscript{\protect\hyperlink{ref-FVBWKkZu}{52}}.
+rOpenSci's efforts have resulted in many well-used R packages for ecology research including \texttt{rfishbase}\textsuperscript{\protect\hyperlink{ref-Xsdcv6q}{52}} and \texttt{taxize}\textsuperscript{\protect\hyperlink{ref-FVBWKkZu}{53}}.
 
@@
 Scientific publications often omit part of their intellectual and computational workflows, including the treatment of raw data and analytical steps (\emph{e.g.}, model assumption testing).
-Publishing data and reproducible workflows along with manuscripts can provide readers with all details about analytical steps and enable reproducing research experiments and results\textsuperscript{\protect\hyperlink{ref-NOgBWVAr}{53}}.
+Publishing data and reproducible workflows along with manuscripts can provide readers with all details about analytical steps and enable reproducing research experiments and results\textsuperscript{\protect\hyperlink{ref-NOgBWVAr}{54}}.
 In addition to storing data and code, GitHub repositories can provide a time-stamped (version controlled) preregistration of research plans and hypotheses.
@@
 GitHub can serve as a tool for open and tractable research development.
-Collaborators can directly interact with code and data, inspect for errors, and potentially identify scientific misconduct prior to manuscript submission (\emph{e.g.},\textsuperscript{\protect\hyperlink{ref-18PTmKJkq}{54}}).
+Collaborators can directly interact with code and data, inspect for errors, and potentially identify scientific misconduct prior to manuscript submission (\emph{e.g.},\textsuperscript{\protect\hyperlink{ref-18PTmKJkq}{55}}).
 Collaborators and readers are better positioned to discover erroneous or questionable findings if they have complete and transparent access to projects.
@@
 
-Projects in ecology and evolution often involve graduate students, research assistants, and post-doctoral fellows, who hold limited-term positions\textsuperscript{\protect\hyperlink{ref-D4C4k4ak}{55}}.
+Projects in ecology and evolution often involve graduate students, research assistants, and post-doctoral fellows, who hold limited-term positions\textsuperscript{\protect\hyperlink{ref-D4C4k4ak}{56}}.
 Without clear plans on project continuity, the research code and data management upkeep tends to fall off as researchers move on to new projects or to other institutions.
-Additionally, code and data can be difficult to access when kept only on personal devices\textsuperscript{\protect\hyperlink{ref-19kmNxiHc}{56}}.
-
-GitHub can facilitate project continuity among research code by making code handover easier\textsuperscript{\protect\hyperlink{ref-4ny1onB0}{8},\protect\hyperlink{ref-D4C4k4ak}{55}}.
+Additionally, code and data can be difficult to access when kept only on personal devices\textsuperscript{\protect\hyperlink{ref-19kmNxiHc}{57}}.
+
+GitHub can facilitate project continuity among research code by making code handover easier\textsuperscript{\protect\hyperlink{ref-4ny1onB0}{8},\protect\hyperlink{ref-D4C4k4ak}{56}}.
 Through version control, the history of code and data from projects in ecology and evolution can be tracked accessible to future laboratory members and collaborators\textsuperscript{\protect\hyperlink{ref-3DKwn1sY}{12}}.
-Repositories and organizations can have designated data and code owners (or more appropriate, stewards; see\textsuperscript{\protect\hyperlink{ref-iIEKCTLU}{41}},\textsuperscript{\protect\hyperlink{ref-s91uGRZ2}{57}}), who can also can change through time allowing for the transition of code between research cohorts.
+Repositories and organizations can have designated data and code owners (or more appropriate, stewards; see\textsuperscript{\protect\hyperlink{ref-iIEKCTLU}{42}},\textsuperscript{\protect\hyperlink{ref-s91uGRZ2}{58}}), who can also can change through time allowing for the transition of code between research cohorts.
 Other project collaborators can contribute to repository design and development, and their active involvement can both aid authors ability to act as guarantors of the project, and the clarity and reproducibility of the project for future users.
@@
 
-Automation has a strong potential to expand the scale and pace of research in ecology and evolution\textsuperscript{\protect\hyperlink{ref-cfgXxgt1}{58}}.
-Automation frameworks can streamline many stages of the scientific process, including automated data collection and data validation (\emph{e.g.},\textsuperscript{\protect\hyperlink{ref-bhDgD6lF}{59},\protect\hyperlink{ref-lXvpQxeN}{60}}), automated data analysis (\emph{e.g.},\textsuperscript{\protect\hyperlink{ref-Qh7xTLwz}{61}}), automated archiving and deployment of data, code and reports (\emph{e.g.}, this manuscript,\textsuperscript{\protect\hyperlink{ref-SirQKFIz}{62}}).
-In this context, small modifications to code and data can be frequently committed and automatically tested, as in continuous integration and continuous deployment practices\textsuperscript{\protect\hyperlink{ref-1Ep9EJL6y}{63}}.
-This allows for early detection and correction of errors, potentially improving confidence in scientific development by minimizing software errors (see\textsuperscript{\protect\hyperlink{ref-ufw0ZdnI}{64}}).
-In addition to increasing scientific rigor and confidence in ecological software\textsuperscript{\protect\hyperlink{ref-12103x16N}{65}}, automation can help advance more rapidly sharing ecological data and making sure the data are high quality\textsuperscript{\protect\hyperlink{ref-rTbinQMj}{66}}.
-Integrating automation workflows has been highly encouraged in areas of EEB, including predictive ecology\textsuperscript{\protect\hyperlink{ref-mmCOSRfr}{67}}, long-term ecological studies\textsuperscript{\protect\hyperlink{ref-1CJo8lo2v}{68},\protect\hyperlink{ref-RxK4CmfR}{69}}, and management of species at risk information\textsuperscript{\protect\hyperlink{ref-kZzfmBNu}{70}}.
-
-Automation can be integrated into GitHub repositories through the GitHub Actions feature\textsuperscript{\protect\hyperlink{ref-NUXbp429}{71}}, or through alternative automation systems (\emph{e.g.}, Circle CI\textsuperscript{\protect\hyperlink{ref-T03Api6e}{72}}, Travis CI\textsuperscript{\protect\hyperlink{ref-YeFSbfFV}{73}}).
+Automation has a strong potential to expand the scale and pace of research in ecology and evolution\textsuperscript{\protect\hyperlink{ref-cfgXxgt1}{59}}.
+Automation frameworks can streamline many stages of the scientific process, including automated data collection and data validation (\emph{e.g.},\textsuperscript{\protect\hyperlink{ref-bhDgD6lF}{60},\protect\hyperlink{ref-lXvpQxeN}{61}}), automated data analysis (\emph{e.g.},\textsuperscript{\protect\hyperlink{ref-Qh7xTLwz}{62}}), automated archiving and deployment of data, code and reports (\emph{e.g.}, this manuscript,\textsuperscript{\protect\hyperlink{ref-SirQKFIz}{63}}).
+In this context, small modifications to code and data can be frequently committed and automatically tested, as in continuous integration and continuous deployment practices\textsuperscript{\protect\hyperlink{ref-1Ep9EJL6y}{64}}.
+This allows for early detection and correction of errors, potentially improving confidence in scientific development by minimizing software errors (see\textsuperscript{\protect\hyperlink{ref-ufw0ZdnI}{65}}).
+In addition to increasing scientific rigor and confidence in ecological software\textsuperscript{\protect\hyperlink{ref-12103x16N}{66}}, automation can help advance more rapidly sharing ecological data and making sure the data are high quality\textsuperscript{\protect\hyperlink{ref-rTbinQMj}{67}}.
+Integrating automation workflows has been highly encouraged in areas of EEB, including predictive ecology\textsuperscript{\protect\hyperlink{ref-mmCOSRfr}{68}}, long-term ecological studies\textsuperscript{\protect\hyperlink{ref-1CJo8lo2v}{69},\protect\hyperlink{ref-RxK4CmfR}{70}}, and management of species at risk information\textsuperscript{\protect\hyperlink{ref-kZzfmBNu}{71}}.
+
+Automation can be integrated into GitHub repositories through the GitHub Actions feature\textsuperscript{\protect\hyperlink{ref-NUXbp429}{72}}, or through alternative automation systems (\emph{e.g.}, Circle CI\textsuperscript{\protect\hyperlink{ref-T03Api6e}{73}}, Travis CI\textsuperscript{\protect\hyperlink{ref-YeFSbfFV}{74}}).
 Users can set up workflows associated with their repositories that are triggered by events (\emph{e.g.}, push, pull request or at specified times) for remote servers to perform user-specified steps and actions.
@@
 
-There have been many calls for researchers outside of the software development community to adopt GitHub to improve their collaborative research\textsuperscript{\protect\hyperlink{ref-10ghgV3S8}{3},\protect\hyperlink{ref-1Du6fzB8g}{40},\protect\hyperlink{ref-UsTxAq4f}{74}}.
+There have been many calls for researchers outside of the software development community to adopt GitHub to improve their collaborative research\textsuperscript{\protect\hyperlink{ref-10ghgV3S8}{3},\protect\hyperlink{ref-1Du6fzB8g}{41},\protect\hyperlink{ref-UsTxAq4f}{75}}.
 These calls come in light of the continuous shift towards open-science and the increasing computational and data requirements in EEB.
@@
 
-A third barrier may come from general reluctance to share data and code publicly, or technical and logistical issues\textsuperscript{\protect\hyperlink{ref-pq2Tv1BC}{16}}.
+A third barrier may come from general reluctance to share data and code publicly, or technical and logistical issues\textsuperscript{\protect\hyperlink{ref-pq2Tv1BC}{17}}.
 GitHub is, by default, a public and open platform.
 This openness may add additional pressure to students and scientists learning to use the platform.
-File storage is size-limited on GitHub (but note that large files stored locally can still be versioned; see section ``Storing and sharing research compendia''), requiring the complementation of other tools to fully integration project files and GitHub repositories (\emph{e.g.},\textsuperscript{\protect\hyperlink{ref-lx49NGto}{75}}).
+File storage is size-limited on GitHub (but note that large files stored locally can still be versioned; see section ``Storing and sharing research compendia''), requiring the complementation of other tools to fully integration project files and GitHub repositories (\emph{e.g.},\textsuperscript{\protect\hyperlink{ref-lx49NGto}{76}}).
 A major additional barrier to EEB researchers is the lack language-specific resources for non-English speaking researchers working in ecology and evolution.
-Language is a well-known obstacle to international collaborative research progress and to widespread scientific knowledge\textsuperscript{see \protect\hyperlink{ref-cW7vGddM}{76}}.
+Language is a well-known obstacle to international collaborative research progress and to widespread scientific knowledge\textsuperscript{see \protect\hyperlink{ref-cW7vGddM}{77}}.
 Non-English speaking EEB researchers can potentially miss opportunities to fully integrate version control, reproducibility, and other benefits of GitHub without language-inclusive contents.
@@
 \\
-2. \textbf{Consider taking free courses}, such as those from Software Carpentry\textsuperscript{\protect\hyperlink{ref-pjy75gHr}{77}}, and sharing these courses with your lab members or colleagues. \\
+2. \textbf{Consider taking free courses}, such as those from Software Carpentry\textsuperscript{\protect\hyperlink{ref-pjy75gHr}{78}}, and sharing these courses with your lab members or colleagues. \\
 3.
@@
 6.
-\textbf{Consult online resources.} The Jenny Bryan Universe of GitHub material, for example, provides a thorough and accessible introduction for a multitude of research-related uses for GitHub, and includes a book\textsuperscript{\protect\hyperlink{ref-ZvrOcg9w}{78}}, statistics course\textsuperscript{\protect\hyperlink{ref-6CMMeSeD}{79}} and academic article\textsuperscript{\protect\hyperlink{ref-RVetqmsg}{7}}.
+\textbf{Consult online resources.} The Jenny Bryan Universe of GitHub material, for example, provides a thorough and accessible introduction for a multitude of research-related uses for GitHub, and includes a book\textsuperscript{\protect\hyperlink{ref-ZvrOcg9w}{79}}, statistics course\textsuperscript{\protect\hyperlink{ref-6CMMeSeD}{80}} and academic article\textsuperscript{\protect\hyperlink{ref-RVetqmsg}{7}}.
 \\
@@
 
-We provide thirteen practical ways that ecologists and evolutionary biologists can adopt GitHub to improve their research workflow and make it more open and reproducible.
+We describe thirteen practical ways that ecologists and evolutionary biologists can adopt GitHub to improve their research workflow and make it more open and reproducible.
 We provide definitions (\protect\hyperlink{definitions}{Box 1}) and types of users (Figure \ref{fig:github-diagram}) to help researchers identify and prioritize the skills and tools to learn and apply.
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-lJAgyhYq}{}}%
+\CSLLeftMargin{14. }
+\CSLRightInline{Kim, A.
+Y.
+\emph{et al.} Implementing GitHub Actions continuous integration to reduce error rates in ecological data collection.
+\emph{Methods Ecol Evol} (2022) doi:\href{https://doi.org/10.1111/2041-210x.13982}{10.1111/2041-210x.13982}.}
+
 \leavevmode\vadjust pre{\hypertarget{ref-ydrk01SR}{}}%
-\CSLLeftMargin{14. }
+\CSLLeftMargin{15. }
 \CSLRightInline{Briney, K., Coates, H. \& Goben, A. \href{https://doi.org/10.3897/rio.6.e56508}{Foundational Practices of Research Data Management}. \emph{RIO} \textbf{6}, (2020).}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-13QX8XU3J}{}}%
-\CSLLeftMargin{15. }
+\CSLLeftMargin{16. }
 \CSLRightInline{Alston, J. M. \& Rick, J. A. \href{https://doi.org/10.1002/bes2.1801}{A Beginner's Guide to Conducting Reproducible Research}. \emph{Bull. Ecol. Soc. Am.} \textbf{102}, (2021).}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-pq2Tv1BC}{}}%
-\CSLLeftMargin{16. }
+\CSLLeftMargin{17. }
 \CSLRightInline{Gomes, D.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-MwwMapRG}{}}%
-\CSLLeftMargin{17. }
+\CSLLeftMargin{18. }
 \CSLRightInline{Marwick, B., Boettiger, C.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-1Co6ZZjF1}{}}%
-\CSLLeftMargin{18. }
+\CSLLeftMargin{19. }
 \CSLRightInline{About large files on GitHub. \emph{GitHub Docs} \url{https://ghdocs-prod.azurewebsites.net/en/repositories/working-with-files/managing-large-files/about-large-files-on-github}.}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-11GtZ7icJ}{}}%
-\CSLLeftMargin{19. }
+\CSLLeftMargin{20. }
 \CSLRightInline{Git Large File Storage. \emph{Git Large File Storage} \url{https://git-lfs.github.com/}.}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-wwHxTOtm}{}}%
-\CSLLeftMargin{20. }
+\CSLLeftMargin{21. }
 \CSLRightInline{Kanza, S. \emph{et al.} \href{https://doi.org/10.1186/s13321-017-0221-3}{Electronic lab notebooks: can they replace paper?} \emph{J Cheminform} \textbf{9}, (2017).}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-1HhzKAC1K}{}}%
-\CSLLeftMargin{22. }
+\CSLLeftMargin{23. }
 \CSLRightInline{Goring, S.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-RhBKe0MG}{}}%
-\CSLLeftMargin{23. }
+\CSLLeftMargin{24. }
 \CSLRightInline{About Projects. \emph{GitHub Docs} \url{https://ghdocs-prod.azurewebsites.net/en/issues/planning-and-tracking-with-projects/learning-about-projects/about-projects}.}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-1GRWGlDWy}{}}%
-\CSLLeftMargin{24. }
+\CSLLeftMargin{25. }
 \CSLRightInline{Slack. GitHub for Slack. \emph{Slack Help Center} \url{https://slack.com/help/articles/232289568-GitHub-for-Slack}.}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-QqMezOMg}{}}%
-\CSLLeftMargin{25. }
+\CSLLeftMargin{26. }
 \CSLRightInline{Xie, Y., Allaire, J. J. \& Grolemund, G. \emph{R Markdown: the definitive guide}. (CRC Press, Taylor and Francis Group, 2019).}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-MDQfMwCW}{}}%
-\CSLLeftMargin{26. }
+\CSLLeftMargin{27. }
 \CSLRightInline{Quickstart for GitHub Pages. \emph{GitHub Docs} \url{https://ghdocs-prod.azurewebsites.net/en/pages/quickstart}.}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-dqrFjoSb}{}}%
-\CSLLeftMargin{27. }
+\CSLLeftMargin{28. }
 \CSLRightInline{Trujillo, G.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-HiIPSSHV}{}}%
-\CSLLeftMargin{28. }
+\CSLLeftMargin{29. }
 \CSLRightInline{Smaglik, P.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-MXxgZJ45}{}}%
-\CSLLeftMargin{29. }
+\CSLLeftMargin{30. }
 \CSLRightInline{Dawson, C. \emph{Building tools with GitHub: customize your workflow}. (O'Reilly, 2016).}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-PLmDFZrm}{}}%
-\CSLLeftMargin{30. }
+\CSLLeftMargin{31. }
 \CSLRightInline{Tenopir, C.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-1Hcf13Q0k}{}}%
-\CSLLeftMargin{31. }
+\CSLLeftMargin{32. }
 \CSLRightInline{Nugroho, R.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-1Ch6LSHef}{}}%
-\CSLLeftMargin{32. }
+\CSLLeftMargin{33. }
 \CSLRightInline{Wicherts, J.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-SLq38RVv}{}}%
-\CSLLeftMargin{33. }
+\CSLLeftMargin{34. }
 \CSLRightInline{Figueiredo, A. S. \href{https://doi.org/10.3389/fpubh.2017.00327}{Data Sharing: Convert Challenges into Opportunities}. \emph{Front. Public Health} \textbf{5}, (2017).}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-1CzUZwyU2}{}}%
-\CSLLeftMargin{34. }
+\CSLLeftMargin{35. }
 \CSLRightInline{Tenopir, C.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-666HppfO}{}}%
-\CSLLeftMargin{35. }
+\CSLLeftMargin{36. }
 \CSLRightInline{Pronk, T.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-1CcAUn3Lu}{}}%
-\CSLLeftMargin{36. }
+\CSLLeftMargin{37. }
 \CSLRightInline{Piwowar, H.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-4LaijDIZ}{}}%
-\CSLLeftMargin{37. }
+\CSLLeftMargin{38. }
 \CSLRightInline{\href{https://doi.org/10.1038/ncb3506}{On data availability, reproducibility and reuse}. \emph{Nat Cell Biol} \textbf{19}, 259--259 (2017).}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-uBJwnPbq}{}}%
-\CSLLeftMargin{38. }
+\CSLLeftMargin{39. }
 \CSLRightInline{Mislan, K.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-1HZdsK5Kn}{}}%
-\CSLLeftMargin{39. }
+\CSLLeftMargin{40. }
 \CSLRightInline{Baker, M. \href{https://doi.org/10.1038/533452a}{1,500 scientists lift the lid on reproducibility}. \emph{Nature} \textbf{533}, 452--454 (2016).}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-1Du6fzB8g}{}}%
-\CSLLeftMargin{40. }
+\CSLLeftMargin{41. }
 \CSLRightInline{Crystal‐Ornelas, R.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-iIEKCTLU}{}}%
-\CSLLeftMargin{41. }
+\CSLLeftMargin{42. }
 \CSLRightInline{Hampton, S. E. \emph{et al.} \href{https://doi.org/10.1890/es14-00402.1}{The Tao of open science for ecology}. \emph{Ecosphere} \textbf{6}, art120 (2015).}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-GQj3c17f}{}}%
-\CSLLeftMargin{42. }
+\CSLLeftMargin{43. }
 \CSLRightInline{Hudgins, E. \emph{emmajhudgins/UStreedamage: publication release}. (Zenodo, 2022). doi:\href{https://doi.org/10.5281/zenodo.6097109}{10.5281/zenodo.6097109}.}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-bZNn2hbh}{}}%
-\CSLLeftMargin{43. }
+\CSLLeftMargin{44. }
 \CSLRightInline{EllenJCoombs. \emph{EllenJCoombs/Asymmetry-evolution-cetaceans-for-publication-v.1.0.0}. (Zenodo, 2020). doi:\href{https://doi.org/10.5281/zenodo.3893943}{10.5281/zenodo.3893943}.}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-ZI1OqZNr}{}}%
-\CSLLeftMargin{44. }
+\CSLLeftMargin{45. }
 \CSLRightInline{Lrharper1.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-TOsASkn5}{}}%
-\CSLLeftMargin{45. }
+\CSLLeftMargin{46. }
 \CSLRightInline{Adding a license to a repository.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-1BJcvyTmV}{}}%
-\CSLLeftMargin{46. }
+\CSLLeftMargin{47. }
 \CSLRightInline{Vale, G., Schmid, A., Santos, A.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-K7nbP1Ty}{}}%
-\CSLLeftMargin{47. }
+\CSLLeftMargin{48. }
 \CSLRightInline{Crystal-Ornelas, R.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-hm9PaCLD}{}}%
-\CSLLeftMargin{48. }
+\CSLLeftMargin{49. }
 \CSLRightInline{Song, X., Goldstein, S.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Re6Eg2va}{}}%
-\CSLLeftMargin{49. }
+\CSLLeftMargin{50. }
 \CSLRightInline{Manubot - Manuscripts, open and automated. \url{https://manubot.org}.}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-YuJbg3zO}{}}%
-\CSLLeftMargin{50. }
+\CSLLeftMargin{51. }
 \CSLRightInline{Himmelstein, D. S. \emph{et al.} \href{https://doi.org/10.1371/journal.pcbi.1007128}{Open collaborative writing with Manubot}. \emph{PLoS Comput Biol} \textbf{15}, e1007128 (2019).}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Xsdcv6q}{}}%
-\CSLLeftMargin{51. }
+\CSLLeftMargin{52. }
 \CSLRightInline{Boettiger, C., Lang, D.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-FVBWKkZu}{}}%
-\CSLLeftMargin{52. }
+\CSLLeftMargin{53. }
 \CSLRightInline{Chamberlain, S. A. \& Szöcs, E. \href{https://doi.org/10.12688/f1000research.2-191.v2}{taxize: taxonomic search and retrieval in R}. \emph{F1000Res} \textbf{2}, 191 (2013).}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-NOgBWVAr}{}}%
-\CSLLeftMargin{53. }
+\CSLLeftMargin{54. }
 \CSLRightInline{Culina, A., van den Berg, I., Evans, S.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-18PTmKJkq}{}}%
-\CSLLeftMargin{54. }
+\CSLLeftMargin{55. }
 \CSLRightInline{January 18, P.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-D4C4k4ak}{}}%
-\CSLLeftMargin{55. }
+\CSLLeftMargin{56. }
 \CSLRightInline{Fehr, J., Himpe, C., Rave, S. \& Saak, J. \href{https://doi.org/10.5334/jors.307}{Sustainable Research Software Hand-Over}. \emph{JORS} \textbf{9}, 5 (2021).}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-19kmNxiHc}{}}%
-\CSLLeftMargin{56. }
+\CSLLeftMargin{57. }
 \CSLRightInline{Vines, Timothy~H.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-s91uGRZ2}{}}%
-\CSLLeftMargin{57. }
+\CSLLeftMargin{58. }
 \CSLRightInline{About code owners.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-cfgXxgt1}{}}%
-\CSLLeftMargin{58. }
+\CSLLeftMargin{59. }
 \CSLRightInline{Keitt, T. H. \& Abelson, E. S. \href{https://doi.org/10.1126/science.abi4692}{Ecology in the age of automation}. \emph{Science} \textbf{373}, 858--859 (2021).}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-bhDgD6lF}{}}%
-\CSLLeftMargin{59. }
+\CSLLeftMargin{60. }
 \CSLRightInline{Micheletti, T.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-lXvpQxeN}{}}%
-\CSLLeftMargin{60. }
+\CSLLeftMargin{61. }
 \CSLRightInline{Yenni, G. M. \emph{et al.} Developing a modern data workflow for evolving data. (2018) doi:\href{https://doi.org/10.1101/344804}{10.1101/344804}.}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Qh7xTLwz}{}}%
-\CSLLeftMargin{61. }
+\CSLLeftMargin{62. }
 \CSLRightInline{Beaulieu-Jones, B.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-SirQKFIz}{}}%
-\CSLLeftMargin{62. }
+\CSLLeftMargin{63. }
 \CSLRightInline{White, E.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-1Ep9EJL6y}{}}%
-\CSLLeftMargin{63. }
+\CSLLeftMargin{64. }
 \CSLRightInline{Meyer, M. \href{https://doi.org/10.1109/ms.2014.58}{Continuous Integration and Its Tools}. \emph{IEEE Softw.} \textbf{31}, 14--16 (2014).}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-ufw0ZdnI}{}}%
-\CSLLeftMargin{64. }
+\CSLLeftMargin{65. }
 \CSLRightInline{Soergel, D. A. W. \href{https://doi.org/10.12688/f1000research.5930.2}{Rampant software errors may undermine scientific results}. \emph{F1000Res} \textbf{3}, 303 (2015).}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-12103x16N}{}}%
-\CSLLeftMargin{65. }
+\CSLLeftMargin{66. }
 \CSLRightInline{Scheller, R.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-rTbinQMj}{}}%
-\CSLLeftMargin{66. }
+\CSLLeftMargin{67. }
 \CSLRightInline{Dietze, M.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-mmCOSRfr}{}}%
-\CSLLeftMargin{67. }
+\CSLLeftMargin{68. }
 \CSLRightInline{McIntire, E.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-1CJo8lo2v}{}}%
-\CSLLeftMargin{68. }
+\CSLLeftMargin{69. }
 \CSLRightInline{Yenni, G.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-RxK4CmfR}{}}%
-\CSLLeftMargin{69. }
+\CSLLeftMargin{70. }
 \CSLRightInline{Ernest, S. K. M. \emph{et al.} The Portal Project: a long-term study of a Chihuahuan desert ecosystem. (2018) doi:\href{https://doi.org/10.1101/332783}{10.1101/332783}.}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-kZzfmBNu}{}}%
-\CSLLeftMargin{70. }
+\CSLLeftMargin{71. }
 \CSLRightInline{Naujokaitis-Lewis, I., Endicott, S.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-NUXbp429}{}}%
-\CSLLeftMargin{71. }
+\CSLLeftMargin{72. }
 \CSLRightInline{Features • GitHub Actions. \emph{GitHub} \url{https://github.com/features/actions}.}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-T03Api6e}{}}%
-\CSLLeftMargin{72. }
+\CSLLeftMargin{73. }
 \CSLRightInline{Continuous Integration and Delivery. \emph{CircleCI} \url{https://circleci.com/}.}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-YeFSbfFV}{}}%
-\CSLLeftMargin{73. }
+\CSLLeftMargin{74. }
 \CSLRightInline{Homepage \textbar{} Travis CI -- Start building today! \emph{Travis CI} \url{https://www.travis-ci.com/}.}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-UsTxAq4f}{}}%
-\CSLLeftMargin{74. }
+\CSLLeftMargin{75. }
 \CSLRightInline{Anbaroğlu, B. \href{https://doi.org/10.1111/tgis.12810}{A collaborative GIS programming course using GitHub Classroom}. \emph{Transactions in GIS} \textbf{25}, 3132--3158 (2021).}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-lx49NGto}{}}%
-\CSLLeftMargin{75. }
+\CSLLeftMargin{76. }
 \CSLRightInline{Connect GitHub to a Project - OSF Support. \url{https://help.osf.io/article/211-connect-github-to-a-project}.}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-cW7vGddM}{}}%
-\CSLLeftMargin{76. }
+\CSLLeftMargin{77. }
 \CSLRightInline{Khelifa, R., Amano, T.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-pjy75gHr}{}}%
-\CSLLeftMargin{77. }
+\CSLLeftMargin{78. }
 \CSLRightInline{Madicken Munk \emph{et al.} swcarpentry/git-novice: Software Carpentry: Version Control with Git, June 2019. at \url{https://doi.org/10.5281/zenodo.3264950} (2019).}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-ZvrOcg9w}{}}%
-\CSLLeftMargin{78. }
+\CSLLeftMargin{79. }
 \CSLRightInline{Hester, J. B., the STAT 545 TAs, Jim. \emph{\href{https://happygitwithr.com/}{Let's Git started \textbar{} Happy Git and GitHub for the useR}}.}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-6CMMeSeD}{}}%
-\CSLLeftMargin{79. }
+\CSLLeftMargin{80. }
 \CSLRightInline{Bryan, J. \& TAs, T. S. 545. \emph{\href{https://stat545.com/}{STAT 545}}.}

### 2022-10-03 manuscript.tex
Merge pull request #275 from SORTEE-Github-Hackathon/phpb-citation-style-change [ci skip]
This build is based on
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/c5581246d860e031bbed754e4a7d18ff1ae072b2.

This commit was created by the following CI build and job:
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/c5581246d860e031bbed754e4a7d18ff1ae072b2/checks
https://github.com/SORTEE-Github-Hackathon/manuscript/actions/runs/3177054119

--- 2022-08-10 manuscript.tex
@@
 This manuscript
-(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/b2d3efb7b1c0fed0477b041fbe9cb7dbc487d31c/}{permalink})
+(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/c5581246d860e031bbed754e4a7d18ff1ae072b2/}{permalink})
 was automatically generated
-from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/b2d3efb7b1c0fed0477b041fbe9cb7dbc487d31c}{SORTEE-Github-Hackathon/manuscript@b2d3efb}
-on August 10, 2022.
+from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/c5581246d860e031bbed754e4a7d18ff1ae072b2}{SORTEE-Github-Hackathon/manuscript@c558124}
+on October 3, 2022.
 
@@
 
-Most scientists, including ecologists and evolutionary biologists, are increasingly dependent on computational tools in their research\textsuperscript{\protect\hyperlink{ref-fJWFe93e}{1}}.
+Most scientists, including ecologists and evolutionary biologists, are increasingly dependent on computational tools in their research (\protect\hyperlink{ref-fJWFe93e}{Hannay et al., 2009}).
 Researchers write and use software packages or data analysis code (hereafter, code) to perform scientific tasks ranging from data management, data analysis, and study replication, to the application and the development of tools for hypothesis testing.
-Maintaining code for scientific collaboration requires an efficient and well-documented work-flow\textsuperscript{\protect\hyperlink{ref-1Kqna6l2}{2}}.
-To facilitate this process, scientists have been adopting tools from information and systems technology, such as cloud-based services for documentation and version control (\emph{e.g.}, from the Google Suite, the Microsoft Suite, and GitHub\textsuperscript{\protect\hyperlink{ref-10ghgV3S8}{3}}).
+Maintaining code for scientific collaboration requires an efficient and well-documented work-flow (\protect\hyperlink{ref-1Kqna6l2}{J. M. Perkel, 2020}).
+To facilitate this process, scientists have been adopting tools from information and systems technology, such as cloud-based services for documentation and version control (\emph{e.g.}, from the Google Suite, the Microsoft Suite, and GitHub (\protect\hyperlink{ref-10ghgV3S8}{J.
+Perkel, 2016})).
 However, most researchers lack exposure to adequate code practices and thus dedicate valuable time and effort to self-teaching research-facilitating tools.
-Thus, researchers may not adhere to standards of code quality and maintenance\textsuperscript{\protect\hyperlink{ref-fJWFe93e}{1},\protect\hyperlink{ref-10SpoByIw}{4},\protect\hyperlink{ref-O6UbstGG}{5}}.
+Thus, researchers may not adhere to standards of code quality and maintenance (\protect\hyperlink{ref-fJWFe93e}{Hannay et al., 2009}; \protect\hyperlink{ref-10SpoByIw}{Prabhu et al., 2011}; \protect\hyperlink{ref-O6UbstGG}{Wilson et al., 2014}).
 Here, we review and discuss one of the most used web-based platforms for computational version control and collaboration, GitHub, and provide researchers in ecology and evolutionary biology (EEB) with practical workflows to facilitate and improve their code and its management.
 
-With over 83 million registered users as of 2022, GitHub is the most widely-used web platform for collaborating on computer code\textsuperscript{\protect\hyperlink{ref-nwCtHDCn}{6}}.
+With over 83 million registered users as of 2022, GitHub is the most widely-used web platform for collaborating on computer code (\protect\hyperlink{ref-nwCtHDCn}{\emph{Build Software Better, Together}, n.d.}).
 GitHub provides a simple but powerful web interface that allows users to participate in projects by contributing, modifying and discussing existing code, reporting bugs, discovering code and data, and publishing new code.
-Through version control, users have a detailed, chronological record of the files and directories stored in their repositories\textsuperscript{\protect\hyperlink{ref-RVetqmsg}{7}} (see \protect\hyperlink{definitions}{Box 1}).
-This workflow provides a strong and clear advantage over sending files back-and-forth (\emph{e.g.}, via email), a process that can become challenging and time-consuming in long-term and collaborative projects\textsuperscript{\protect\hyperlink{ref-4ny1onB0}{8}}.
-Through its combination of version control and collaborative features, GitHub facilitates open-source code alongside collaborative development\textsuperscript{\protect\hyperlink{ref-kEX5dgzK}{9}}.
+Through version control, users have a detailed, chronological record of the files and directories stored in their repositories (\protect\hyperlink{ref-RVetqmsg}{Bryan, 2018}) (see \protect\hyperlink{definitions}{Box 1}).
+This workflow provides a strong and clear advantage over sending files back-and-forth (\emph{e.g.}, via email), a process that can become challenging and time-consuming in long-term and collaborative projects (\protect\hyperlink{ref-4ny1onB0}{Ram, 2013}).
+Through its combination of version control and collaborative features, GitHub facilitates open-source code alongside collaborative development (\protect\hyperlink{ref-kEX5dgzK}{Perez-Riverol et al., 2016}).
 
@@
 
-The expansive GitHub user-community and numerous GitHub resources have boosted its popularity\textsuperscript{\protect\hyperlink{ref-RVetqmsg}{7},\protect\hyperlink{ref-kEX5dgzK}{9}--\protect\hyperlink{ref-u5aEVE4B}{11}}.
-Nevertheless, although multiple articles have encouraged researchers in EEB to adopt GitHub as part of their research process\textsuperscript{\protect\hyperlink{ref-10ghgV3S8}{3},\protect\hyperlink{ref-3DKwn1sY}{12}}, its use is still not widespread.
-First-time users without formal training in information technology may face steep learning curves because GitHub and its features have been centered on collaboration for code development in information systems\textsuperscript{\protect\hyperlink{ref-139b0pSGc}{13}}.
-Moreover, domain-specific resources providing tractable examples and practical guidance for researchers in EEB on GitHub are scarce (but see \url{https://ourcodingclub.github.io}; \url{https://www.openscapes.org}).
-Widespread adoption of GitHub for collaborating on research tasks can ultimately enable EEB researchers to spend less time on creating novel processes for collaboration and more time on their research\textsuperscript{\protect\hyperlink{ref-ydrk01SR}{14}}.
-More importantly, expanding the availability of data and code management standards -- of which GitHub is one increasingly important component -- makes research more reproducible and collaborative\textsuperscript{\protect\hyperlink{ref-13QX8XU3J}{15},\protect\hyperlink{ref-pq2Tv1BC}{16}}.
+The expansive GitHub user-community and numerous GitHub resources have boosted its popularity (\protect\hyperlink{ref-RVetqmsg}{Bryan, 2018}; \protect\hyperlink{ref-u5aEVE4B}{\emph{Coding Club: A Positive Peer-Learning Community}, n.d.}; \protect\hyperlink{ref-13jOlVcpp}{Hester, n.d.-a}; \protect\hyperlink{ref-kEX5dgzK}{Perez-Riverol et al., 2016}).
+Nevertheless, although multiple articles have encouraged researchers in EEB to adopt GitHub as part of their research process (\protect\hyperlink{ref-3DKwn1sY}{Lowndes et al., 2017}; \protect\hyperlink{ref-10ghgV3S8}{J.
+Perkel, 2016}), its use is still not widespread.
+First-time users without formal training in information technology may face steep learning curves because GitHub and its features have been centered on collaboration for code development in information systems (\protect\hyperlink{ref-139b0pSGc}{Leibzon, 2016}).
+Moreover, domain-specific resources providing tractable examples and practical guidance for researchers in EEB on GitHub are scarce (but see \url{https://ourcodingclub.github.io}; \url{https://www.openscapes.org}, (\protect\hyperlink{ref-lJAgyhYq}{Kim et al., 2022})).
+Widespread adoption of GitHub for collaborating on research tasks can ultimately enable EEB researchers to spend less time on creating novel processes for collaboration and more time on their research (\protect\hyperlink{ref-ydrk01SR}{Briney et al., 2020}).
+More importantly, expanding the availability of data and code management standards -- of which GitHub is one increasingly important component -- makes research more reproducible and collaborative (\protect\hyperlink{ref-13QX8XU3J}{Alston \& Rick, 2021}; \protect\hyperlink{ref-pq2Tv1BC}{Gomes et al., 2022}).
 
@@
 Having copies of these files safely stored is essential to protect against accidental modifications or deletions.
-Many researchers begin using GitHub to store (or backup) their research compendium\textsuperscript{\protect\hyperlink{ref-MwwMapRG}{17}} to a centralized, readily-available remote server (see \protect\hyperlink{definitions}{Box 1}).
+Many researchers begin using GitHub to store (or backup) their research compendium (\protect\hyperlink{ref-MwwMapRG}{Marwick et al., 2018}) to a centralized, readily-available remote server (see \protect\hyperlink{definitions}{Box 1}).
 A centralized research compendium stored in a version-controlled repository has the advantages of facilitating collaboration, integrating data and code archiving services, allowing file versions to be accessed and restored, and contributes to open science (see sections below).
 
-GitHub limits committed file sizes to 100 Mb (megabytes\textsuperscript{\protect\hyperlink{ref-1Co6ZZjF1}{18}}), which can make it challenging for centralizing research compendia containing larger file sizes.
-Users may still version large files using Git Large File Storage\textsuperscript{\protect\hyperlink{ref-11GtZ7icJ}{19}} text pointers, but may have to rely on external file storage alternatives (such as local or cloud-hosting).
+GitHub limits committed file sizes to 100 Mb (megabytes \emph{About Large Files on GitHub} (\protect\hyperlink{ref-1Co6ZZjF1}{n.d.})), which can make it challenging for centralizing research compendia containing larger file sizes.
+Users may still version large files using Git Large File Storage (\protect\hyperlink{ref-11GtZ7icJ}{\emph{Git Large File Storage}, n.d.}) text pointers, but may have to rely on external file storage alternatives (such as local or cloud-hosting).
 
@@
 
-Laboratory notebooks help researchers track their research notes, methods, policies and protocols\textsuperscript{\protect\hyperlink{ref-wwHxTOtm}{20}}.
-Virtual laboratory notebooks can be stored in GitHub repositories and provide the benefits of simultaneous, centralized and selective access, and allows for the easy update of policies and experiment protocols\textsuperscript{\protect\hyperlink{ref-10V7x4H4l}{21}}.
-Researchers have been increasingly using GitHub to maintain versions and share digital laboratory notebooks\textsuperscript{\protect\hyperlink{ref-10ghgV3S8}{3}} (\emph{e.g.}, \url{https://scheuerell-lab.github.io/lab-book}; \url{https://github.com/HuckleyLab/how_we_work}).
+Laboratory notebooks help researchers track their research notes, methods, policies and protocols (\protect\hyperlink{ref-wwHxTOtm}{Kanza et al., 2017}).
+Virtual laboratory notebooks can be stored in GitHub repositories and provide the benefits of simultaneous, centralized and selective access, and allows for the easy update of policies and experiment protocols (\protect\hyperlink{ref-10V7x4H4l}{Schnell, 2015}).
+Researchers have been increasingly using GitHub to maintain versions and share digital laboratory notebooks across many fields (\protect\hyperlink{ref-10ghgV3S8}{J.
+Perkel, 2016}), including applied ecology (\emph{e.g.}, \url{https://scheuerell-lab.github.io/lab-book}), biogeography and global change biology (\emph{e.g.}, \url{https://github.com/HuckleyLab/how_we_work}), and microbial ecology (\emph{e.g.}, \url{https://github.com/CarBBAS/uqam-guide}).
 
 At least for aspects of a research project that involve writing code, a GitHub repository is a form of a laboratory notebook; when changes are made to files in a version-controlled repository, the author of those changes makes a commit (\protect\hyperlink{definitions}{Box 1}) accompanied by a description of changes.
-Later, the entire history of commits and their commit messages are viewable and can be audited similar to a physical laboratory notebook\textsuperscript{\protect\hyperlink{ref-4ny1onB0}{8}}.
-GitHub issues (see project management section below) can be used to prioritize laboratory objectives and goals, as well as track any progress updates.
+Later, the entire history of commits and their commit messages are viewable and can be audited similar to a physical laboratory notebook (\protect\hyperlink{ref-4ny1onB0}{Ram, 2013}).
+GitHub issues (see Project management section below) can be used to prioritize laboratory objectives and goals, as well as track any progress updates.
 
@@
 
-Modern research in ecology and evolution is highly collaborative, bringing together multidisciplinary teams from various institutions.
+Modern research in ecology and evolution is highly collaborative, bringing together multidisciplinary teams from various institutions (\protect\hyperlink{ref-1HhzKAC1K}{Goring et al., 2014}).
 On GitHub, collaborators can share feedback, brainstorm ideas, and troubleshoot problems (Figure \ref{fig:github-diagram}).
@@
 Github Discussions serve as a message board for conversation.
-Finally, GitHub Projects integrate issues and pull requests on automated spreadsheets and project boards, providing users with real-time tracking of project priorities and status\textsuperscript{\protect\hyperlink{ref-RhBKe0MG}{22}}.
+Finally, GitHub Projects integrate issues and pull requests on automated spreadsheets and project boards, providing users with real-time tracking of project priorities and status (\protect\hyperlink{ref-RhBKe0MG}{\emph{About Projects}, n.d.}).
 Scripts, commit messages, and pull requests can be linked directly to issues, discussions, and projects providing a clear record of project workflow.
+For instance, one can create a discussion on a project repository to decide which method to apply for biodiversity data analysis.
+Then, an issue can be created to establish steps and responsibilities including data formatting, statistical analyses, figure generation, and issue resolution {[}\emph{e.g.}, see issues and discussions in the sPlotOpen {[}doi:10.1111/geb.13346{]} manuscript repository (\url{https://github.com/fmsabatini/sPlotOpen_Manuscript/issues?q=is\%3Aissue+is\%3Aclosed}){]}.
 Using GitHub for all project-related conversation and planning, rather than email or messaging tools, makes it easier to keep track of progress throughout the lifespan of a project.
@@
 Project management in GitHub can also be integrated with third-party applications, such as Zenhub (\url{https://www.zenhub.com}) or Slack (\url{https://slack.github.com}).
-ZenHub allows for the enhanced visualization and organization of repositories and their issues, while the GitHub for Slack integration allows notifications from GitHub events to be sent directly to users or group channels\textsuperscript{\protect\hyperlink{ref-1GRWGlDWy}{23}}.
+Zenhub allows for the enhanced visualization and organization of repositories and their issues, while the GitHub for Slack integration allows notifications from GitHub events to be sent directly to users or group channels (\protect\hyperlink{ref-1GRWGlDWy}{Slack, n.d.}).
 
@@
 
-Making presentations, syllabi and other course materials can be done through most major high-level programming languages such as R, with \texttt{RMarkdown}\textsuperscript{\protect\hyperlink{ref-QqMezOMg}{24}}, Python, with \texttt{python-ppt} (\url{https://python-pptx.readthedocs.io}), and Julia, with \texttt{Remark.jl} (\url{https://juliapackages.com/p/remark}), and be version-controlled and stored in GitHub.
-Once content is made, hosting a course website can be done through GitHub Pages\textsuperscript{\protect\hyperlink{ref-MDQfMwCW}{25}} (\emph{e.g.}, \url{https://github.com/topics/course-website}).
+Making presentations, syllabi and other course materials can be done through most major high-level programming languages such as R, with \texttt{RMarkdown} (\protect\hyperlink{ref-QqMezOMg}{Xie et al., 2019}), Python, with \texttt{python-ppt} (\url{https://python-pptx.readthedocs.io}), and Julia, with \texttt{Remark.jl} (\url{https://juliapackages.com/p/remark}), and be version-controlled and stored in GitHub.
+Once content is made, hosting a course website can be done through GitHub Pages (\protect\hyperlink{ref-MDQfMwCW}{\emph{Quickstart for GitHub Pages}, n.d.}) (\emph{e.g.}, \url{https://github.com/topics/course-website}).
 This way, course content can be available to enrolled students, as well as a global pool of learners and teachers interested in the material.
@@
 Student submissions are perhaps the most challenging component, but the new GitHub Classroom tool (\url{https://classroom.github.com}) allows instructors to host private assignments to be submitted collaboratively or individually as code or PDF files, and even build autograding tests.
-Although time-consuming to establish, using these features can integrate learning version control and GitHub with the learning course content, and thus boost students' feelings of self-efficacy and confidence\textsuperscript{\protect\hyperlink{ref-dqrFjoSb}{26}}.
+Although time-consuming to establish, using these features can integrate learning version control and GitHub with the learning course content, and thus boost students' feelings of self-efficacy and confidence (\protect\hyperlink{ref-dqrFjoSb}{Trujillo \& Tanner, 2014}).
 
@@
 
-Personal or laboratory websites can improve the sharing of research findings, build online presence, and increase coordination of research efforts\textsuperscript{\protect\hyperlink{ref-HiIPSSHV}{27}}.
-Despite many researchers in ecology and evolution having little experience in building or hosting webpages, many tools have been developed to help this process.
+Personal or laboratory websites can improve the sharing of research findings, build online presence, and increase coordination of research efforts (\protect\hyperlink{ref-HiIPSSHV}{Smaglik, 2007}).
+Despite researchers in ecology and evolution generally lacking experience in building or hosting webpages, many tools have been developed to help this process.
 Static websites can now be easily built using independent software and languages, such as Jekyll (\url{https://jekyllrb.com}), Hugo (\url{https://gohugo.io}), Quarto (\url{https://quarto.org}), and wowchemy (\url{https://wowchemy.com}), or with the help of dependencies in the programming languages scientists commonly use, such as the \texttt{distill} (\url{https://github.com/rstudio/distill}) and \texttt{blogdown} (\url{https://bookdown.org/yihui/blogdown}) R packages.
@@
 
-Website templates are readily available on GitHub (\url{https://github.com/topics/website-template}) or in user-specific repositories, which can be forked (\protect\hyperlink{definitions}{Box 1}) and customized\textsuperscript{\protect\hyperlink{ref-MXxgZJ45}{28}}.
-Aside from free hosting services, GitHub Pages also allows websites to be autogenerated and instantly updated following content modifications\textsuperscript{\protect\hyperlink{ref-RVetqmsg}{7}}.
+Website templates are readily available on GitHub (\url{https://github.com/topics/website-template}) or in user-specific repositories, which can be forked (\protect\hyperlink{definitions}{Box 1}) and customized (\protect\hyperlink{ref-MXxgZJ45}{Dawson, 2016}).
+Aside from free hosting services, GitHub Pages also allows websites to be autogenerated and instantly updated following content modifications (\protect\hyperlink{ref-RVetqmsg}{Bryan, 2018}).
 Creating and hosting websites on GitHub pages can be time-consuming, as this process usually requires more knowledge in web design than out-of-the-box platforms (\emph{e.g.}, Wix, Weebly, Google Sites).
@@
 
-Government, funding agencies, and publishers exercise rigorous open access data policies and mandates\textsuperscript{\protect\hyperlink{ref-PLmDFZrm}{29},\protect\hyperlink{ref-1Hcf13Q0k}{30}}.
-However, code and data sharing may be met by individual reluctance, temporary embargoes, or partially prevented by privacy and confidentiality reasons\textsuperscript{\protect\hyperlink{ref-1Ch6LSHef}{31}--\protect\hyperlink{ref-1CzUZwyU2}{33}}.
-Still, data deposition and ensuring its availability can amplify the outreach of published studies\textsuperscript{\protect\hyperlink{ref-666HppfO}{34}}, increase citation rates\textsuperscript{\protect\hyperlink{ref-1CcAUn3Lu}{35}}, and among many other reasons, enable the reproducibility and robustness of scientific advances\textsuperscript{\protect\hyperlink{ref-4LaijDIZ}{36}--\protect\hyperlink{ref-1HZdsK5Kn}{38}}.
+Government, funding agencies, and publishers exercise rigorous open access data policies and mandates (\protect\hyperlink{ref-1Hcf13Q0k}{Nugroho et al., 2015}; \protect\hyperlink{ref-PLmDFZrm}{Tenopir et al., 2020}).
+However, code and data sharing may be met by individual reluctance, temporary embargoes, or partially prevented by privacy and confidentiality reasons (\protect\hyperlink{ref-SLq38RVv}{Figueiredo, 2017}; \protect\hyperlink{ref-1CzUZwyU2}{Tenopir et al., 2015}; \protect\hyperlink{ref-1Ch6LSHef}{Wicherts et al., 2011}).
+Still, data deposition and ensuring its availability can amplify the outreach of published studies (\protect\hyperlink{ref-666HppfO}{Pronk et al., 2015}), increase citation rates (\protect\hyperlink{ref-1CcAUn3Lu}{Piwowar et al., 2007}), and among many other reasons, enable the reproducibility and robustness of scientific advances (\protect\hyperlink{ref-1HZdsK5Kn}{Baker, 2016}; \protect\hyperlink{ref-uBJwnPbq}{Mislan et al., 2016}; \protect\hyperlink{ref-4LaijDIZ}{{``On Data Availability, Reproducibility and Reuse,''} 2017}).
 While public repositories on GitHub make it easy to store and share data files, they are not considered long-term repositories for research materials.
@@
 DOIs are persistent and citable unique alpha-numeric identifiers assigned to digitally stored research materials.
-Because of this, scientists sharing code and data through GitHub are strongly encouraged to independently submit their research materials to long-term data archives (\emph{e.g.}, Zenodo, Figshare, Dryad, OSF\textsuperscript{\protect\hyperlink{ref-10ghgV3S8}{3},\protect\hyperlink{ref-kEX5dgzK}{9},\protect\hyperlink{ref-1Du6fzB8g}{39}}; \protect\hyperlink{tbl:compare}{Table 1}).
+Because of this, scientists sharing code and data through GitHub are strongly encouraged to independently submit their research materials to long-term data archives (\emph{e.g.}, Zenodo, Figshare, Dryad, OSF (\protect\hyperlink{ref-1Du6fzB8g}{Crystal‐Ornelas et al., 2021}; \protect\hyperlink{ref-kEX5dgzK}{Perez-Riverol et al., 2016}; \protect\hyperlink{ref-10ghgV3S8}{J.
+Perkel, 2016}); \protect\hyperlink{tbl:compare}{Table 1}).
 Some of these options (Zenodo, Figshare and OSF) integrate with GitHub, allowing project, code, and data releases (\protect\hyperlink{definitions}{Box 1}) to be archived with versioned, citable DOIs.
-Linking GitHub repositories with a DOI helps research become findable, properly cited, and can ensure long-term stability\textsuperscript{\protect\hyperlink{ref-iIEKCTLU}{40}}.
+Linking GitHub repositories with a DOI helps research become findable, properly cited, and can ensure long-term stability (\protect\hyperlink{ref-iIEKCTLU}{Hampton et al., 2015}).
+This strategy has been increasingly adopted in numerous studies in ecology and evolution (\emph{e.g.}, Hudgins (\protect\hyperlink{ref-GQj3c17f}{2022}); EllenJCoombs (\protect\hyperlink{ref-bZNn2hbh}{2020}); Lrharper1 (\protect\hyperlink{ref-ZI1OqZNr}{2018})).
 
@@
 Code published without a license is under exclusive copyright (by default), protecting it from copy, distribution, and modifications.
-One may grant specific rights to their code for reuse by adding licensing files and specifications within GitHub repositories\textsuperscript{\protect\hyperlink{ref-TOsASkn5}{41}}.
+One may grant specific rights to their code for reuse by adding licensing files and specifications within GitHub repositories (\protect\hyperlink{ref-TOsASkn5}{\emph{Adding a License to a Repository}, n.d.}).
 The Choose a License (\url{https://choosealicense.com/non-software/}) website offers further guidance on the licenses available for research and creative products.
@@
 By forking, branching, and cloning repositories (\protect\hyperlink{definitions}{Box 1}), researchers can simultaneously work on different issues of the same research project to then later merge changes to the main branch project with pull requests.
-Explicit project organization and increased communication in GitHub Issues, Discussions, or within pull requests can help with project development and with potential merge conflicts due to users simultaneously working on the same sections\textsuperscript{\protect\hyperlink{ref-1BJcvyTmV}{42}}.
-Moreover, version control\textsuperscript{\protect\hyperlink{ref-K7nbP1Ty}{43}} and commit reversal features allow researchers to track and progress without worrying about irreparably modifying someone else's work.
+Explicit project organization and increased communication in GitHub Issues, Discussions, or within pull requests can help with project development and with potential merge conflicts due to users simultaneously working on the same sections (\protect\hyperlink{ref-1BJcvyTmV}{Vale et al., 2019}).
+Moreover, version control (\protect\hyperlink{ref-K7nbP1Ty}{Crystal-Ornelas et al., 2022}) and commit reversal features allow researchers to track and progress without worrying about irreparably modifying someone else's work.
 By enabling more comprehensive remote collaboration, GitHub encourages the exchange of ideas among researchers at different institutions and in different countries, which can serve to improve the quality of the research itself by providing open access to data and code.
 In academic settings, GitHub can also facilitate interactions between research advisors and advisees, providing a platform for students or other trainees to share in-progress code, and flag specific challenges or questions for their supervisors or mentors (\protect\hyperlink{tbl:roles}{Table 2}).
-Periodic code review\textsuperscript{\protect\hyperlink{ref-hm9PaCLD}{44}} can also help advisors identify errors early in the process, and inform further training and mentorship to fill gaps in skills.
+Periodic code review (\protect\hyperlink{ref-hm9PaCLD}{Song et al., 2020}) can also help advisors identify errors early in the process, and inform further training and mentorship to fill gaps in skills.
 
@@
 Writing a manuscript and storing its associated data and code in GitHub increases scientific reproducibility because text, code, and data can be found in one place.
-Writing a manuscript on GitHub may take more time when compared to using conventional text processors\textsuperscript{\protect\hyperlink{ref-4ny1onB0}{8}}.
+Writing a manuscript on GitHub may take more time when compared to using conventional text processors (\protect\hyperlink{ref-4ny1onB0}{Ram, 2013}).
 Nevertheless, GitHub has many features that can allow for a powerful collaborative workflow when writing manuscripts.
@@
 
-We wrote this manuscript using Manubot\textsuperscript{\protect\hyperlink{ref-Re6Eg2va}{45}}, a modifiable workflow implemented in GitHub to automatically render manuscripts and automate bibliographical tasks\textsuperscript{\protect\hyperlink{ref-YuJbg3zO}{46}}.
+We wrote this manuscript using Manubot (\protect\hyperlink{ref-Re6Eg2va}{\emph{Manubot - Manuscripts, Open and Automated}, n.d.}), a modifiable workflow implemented in GitHub to automatically render manuscripts and automate bibliographical tasks (\protect\hyperlink{ref-YuJbg3zO}{Himmelstein et al., 2019}).
 Manubot uses GitHub's automation workflow, GitHub Actions, to combine and convert individual Markdown files into a single LaTeX document, which can then be converted to a Word or PDF document, and displayed as a webpage.
@@
 Certain journals or software development communities require submitted work or research code to be hosted on GitHub and their review processes make use of GitHub Issues (\emph{e.g.}, rOpenSci (\url{https://ropensci.org/software-review/}), Journal of Open Source Software (\url{https://joss.readthedocs.io/en/latest/submitting.html})).
-rOpenSci's efforts have resulted in many well-used R packages for ecology research including \texttt{rfishbase}\textsuperscript{\protect\hyperlink{ref-Xsdcv6q}{47}} and \texttt{taxize}\textsuperscript{\protect\hyperlink{ref-FVBWKkZu}{48}}.
+rOpenSci's efforts have resulted in many well-used R packages for ecology research including \texttt{rfishbase} (\protect\hyperlink{ref-Xsdcv6q}{Boettiger et al., 2012}) and \texttt{taxize} (\protect\hyperlink{ref-FVBWKkZu}{Chamberlain \& Szöcs, 2013}).
 
@@
 Scientific publications often omit part of their intellectual and computational workflows, including the treatment of raw data and analytical steps (\emph{e.g.}, model assumption testing).
-Publishing data and reproducible workflows along with manuscripts can provide readers with all details about analytical steps and enable reproducing research experiments and results\textsuperscript{\protect\hyperlink{ref-NOgBWVAr}{49}}.
+Publishing data and reproducible workflows along with manuscripts can provide readers with all details about analytical steps and enable reproducing research experiments and results (\protect\hyperlink{ref-NOgBWVAr}{Culina et al., 2020}).
 In addition to storing data and code, GitHub repositories can provide a time-stamped (version controlled) preregistration of research plans and hypotheses.
@@
 GitHub can serve as a tool for open and tractable research development.
-Collaborators can directly interact with code and data, inspect for errors, and potentially identify scientific misconduct prior to manuscript submission (\emph{e.g.},\textsuperscript{\protect\hyperlink{ref-18PTmKJkq}{50}}).
+Collaborators can directly interact with code and data, inspect for errors, and potentially identify scientific misconduct prior to manuscript submission (\emph{e.g.}, (\protect\hyperlink{ref-18PTmKJkq}{January 18 \& Pm, 2020})).
 Collaborators and readers are better positioned to discover erroneous or questionable findings if they have complete and transparent access to projects.
@@
 
-Projects in ecology and evolution often involve graduate students, research assistants, and post-doctoral fellows, who hold limited-term positions\textsuperscript{\protect\hyperlink{ref-D4C4k4ak}{51}}.
+Projects in ecology and evolution often involve graduate students, research assistants, and post-doctoral fellows, who hold limited-term positions (\protect\hyperlink{ref-D4C4k4ak}{Fehr et al., 2021}).
 Without clear plans on project continuity, the research code and data management upkeep tends to fall off as researchers move on to new projects or to other institutions.
-Additionally, code and data can be difficult to access when kept only on personal devices\textsuperscript{\protect\hyperlink{ref-19kmNxiHc}{52}}.
-
-GitHub can facilitate project continuity among research code by making code handover easier\textsuperscript{\protect\hyperlink{ref-4ny1onB0}{8},\protect\hyperlink{ref-D4C4k4ak}{51}}.
-Through version control, the history of code and data from projects in ecology and evolution can be tracked accessible to future laboratory members and collaborators\textsuperscript{\protect\hyperlink{ref-3DKwn1sY}{12}}.
-Repositories and organizations can have designated data and code owners (or more appropriate, stewards; see\textsuperscript{\protect\hyperlink{ref-iIEKCTLU}{40}},\textsuperscript{\protect\hyperlink{ref-s91uGRZ2}{53}}), who can also can change through time allowing for the transition of code between research cohorts.
+Additionally, code and data can be difficult to access when kept only on personal devices (\protect\hyperlink{ref-19kmNxiHc}{Vines et al., 2014}).
+
+GitHub can facilitate project continuity among research code by making code handover easier (\protect\hyperlink{ref-D4C4k4ak}{Fehr et al., 2021}; \protect\hyperlink{ref-4ny1onB0}{Ram, 2013}).
+Through version control, the history of code and data from projects in ecology and evolution can be tracked accessible to future laboratory members and collaborators (\protect\hyperlink{ref-3DKwn1sY}{Lowndes et al., 2017}).
+Repositories and organizations can have designated data and code owners (or more appropriate, stewards; see (\protect\hyperlink{ref-iIEKCTLU}{Hampton et al., 2015}), (\protect\hyperlink{ref-s91uGRZ2}{\emph{About Code Owners}, n.d.})), who can also can change through time allowing for the transition of code between research cohorts.
 Other project collaborators can contribute to repository design and development, and their active involvement can both aid authors ability to act as guarantors of the project, and the clarity and reproducibility of the project for future users.
@@
 
-Automation has a strong potential to expand the scale and pace of research in ecology and evolution\textsuperscript{\protect\hyperlink{ref-cfgXxgt1}{54}}.
-Automation frameworks can streamline many stages of the scientific process, including automated data collection and data validation (\emph{e.g.},\textsuperscript{\protect\hyperlink{ref-bhDgD6lF}{55},\protect\hyperlink{ref-lXvpQxeN}{56}}), automated data analysis (\emph{e.g.},\textsuperscript{\protect\hyperlink{ref-Qh7xTLwz}{57}}), automated archiving and deployment of data, code and reports (\emph{e.g.}, this manuscript,\textsuperscript{\protect\hyperlink{ref-SirQKFIz}{58}}).
-In this context, small modifications to code and data can be frequently committed and automatically tested, as in continuous integration and continuous deployment practices\textsuperscript{\protect\hyperlink{ref-1Ep9EJL6y}{59}}.
-This allows for early detection and correction of errors, potentially improving confidence in scientific development by minimizing software errors (see\textsuperscript{\protect\hyperlink{ref-ufw0ZdnI}{60}}).
-In addition to increasing scientific rigor and confidence in ecological software\textsuperscript{\protect\hyperlink{ref-12103x16N}{61}}, automation can help advance more rapidly sharing ecological data and making sure the data are high quality\textsuperscript{\protect\hyperlink{ref-rTbinQMj}{62}}.
-Integrating automation workflows has been highly encouraged in areas of EEB, including predictive ecology\textsuperscript{\protect\hyperlink{ref-mmCOSRfr}{63}}, long-term ecological studies\textsuperscript{\protect\hyperlink{ref-1CJo8lo2v}{64},\protect\hyperlink{ref-RxK4CmfR}{65}}, and management of species at risk information\textsuperscript{\protect\hyperlink{ref-kZzfmBNu}{66}}.
-
-Automation can be integrated into GitHub repositories through the GitHub Actions feature\textsuperscript{\protect\hyperlink{ref-NUXbp429}{67}}, or through alternative automation systems (\emph{e.g.}, Circle CI\textsuperscript{\protect\hyperlink{ref-T03Api6e}{68}}, Travis CI\textsuperscript{\protect\hyperlink{ref-YeFSbfFV}{69}}).
+Automation has a strong potential to expand the scale and pace of research in ecology and evolution (\protect\hyperlink{ref-cfgXxgt1}{Keitt \& Abelson, 2021}).
+Automation frameworks can streamline many stages of the scientific process, including automated data collection and data validation (\emph{e.g.}, (\protect\hyperlink{ref-bhDgD6lF}{Micheletti et al., 2021}; \protect\hyperlink{ref-lXvpQxeN}{Yenni et al., 2018})), automated data analysis (\emph{e.g.}, (\protect\hyperlink{ref-Qh7xTLwz}{Beaulieu-Jones \& Greene, 2017})), automated archiving and deployment of data, code and reports (\emph{e.g.}, this manuscript, (\protect\hyperlink{ref-SirQKFIz}{White et al., 2018})).
+In this context, small modifications to code and data can be frequently committed and automatically tested, as in continuous integration and continuous deployment practices (\protect\hyperlink{ref-1Ep9EJL6y}{Meyer, 2014}).
+This allows for early detection and correction of errors, potentially improving confidence in scientific development by minimizing software errors (see (\protect\hyperlink{ref-ufw0ZdnI}{Soergel, 2015})).
+In addition to increasing scientific rigor and confidence in ecological software (\protect\hyperlink{ref-12103x16N}{Scheller et al., 2010}), automation can help advance more rapidly sharing ecological data and making sure the data are high quality (\protect\hyperlink{ref-rTbinQMj}{Dietze et al., 2018}).
+Integrating automation workflows has been highly encouraged in areas of EEB, including predictive ecology (\protect\hyperlink{ref-mmCOSRfr}{McIntire et al., 2022}), long-term ecological studies (\protect\hyperlink{ref-RxK4CmfR}{Ernest et al., 2018}; \protect\hyperlink{ref-1CJo8lo2v}{Yenni et al., 2019}), and management of species at risk information (\protect\hyperlink{ref-kZzfmBNu}{Naujokaitis-Lewis et al., 2022}).
+
+Automation can be integrated into GitHub repositories through the GitHub Actions feature (\protect\hyperlink{ref-NUXbp429}{\emph{Features • GitHub Actions}, n.d.}), or through alternative automation systems (\emph{e.g.}, Circle CI(\protect\hyperlink{ref-T03Api6e}{\emph{Continuous Integration and Delivery}, n.d.}), Travis CI(\protect\hyperlink{ref-YeFSbfFV}{\emph{Homepage \textbar{} Travis CI -- Start Building Today!}, n.d.})).
 Users can set up workflows associated with their repositories that are triggered by events (\emph{e.g.}, push, pull request or at specified times) for remote servers to perform user-specified steps and actions.
@@
 
-There have been many calls for researchers outside of the software development community to adopt GitHub to improve their collaborative research\textsuperscript{\protect\hyperlink{ref-10ghgV3S8}{3},\protect\hyperlink{ref-1Du6fzB8g}{39},\protect\hyperlink{ref-UsTxAq4f}{70}}.
+There have been many calls for researchers outside of the software development community to adopt GitHub to improve their collaborative research (\protect\hyperlink{ref-UsTxAq4f}{Anbaroğlu, 2021}; \protect\hyperlink{ref-1Du6fzB8g}{Crystal‐Ornelas et al., 2021}; \protect\hyperlink{ref-10ghgV3S8}{J.
+Perkel, 2016}).
 These calls come in light of the continuous shift towards open-science and the increasing computational and data requirements in EEB.
@@
 
-A third barrier may come from general reluctance to share data and code publicly, or technical and logistical issues\textsuperscript{\protect\hyperlink{ref-pq2Tv1BC}{16}}.
+A third barrier may come from general reluctance to share data and code publicly, or technical and logistical issues (\protect\hyperlink{ref-pq2Tv1BC}{Gomes et al., 2022}).
 GitHub is, by default, a public and open platform.
 This openness may add additional pressure to students and scientists learning to use the platform.
-File storage is size-limited on GitHub (but note that large files stored locally can still be versioned; see section ``Storing and sharing research compendia''), requiring the complementation of other tools to fully integration project files and GitHub repositories (\emph{e.g.},\textsuperscript{\protect\hyperlink{ref-lx49NGto}{71}}).
+File storage is size-limited on GitHub (but note that large files stored locally can still be versioned; see section ``Storing and sharing research compendia''), requiring the complementation of other tools to fully integration project files and GitHub repositories (\emph{e.g.}, (\protect\hyperlink{ref-lx49NGto}{\emph{Connect GitHub to a Project - OSF Support}, n.d.})).
 A major additional barrier to EEB researchers is the lack language-specific resources for non-English speaking researchers working in ecology and evolution.
-Language is a well-known obstacle to international collaborative research progress and to widespread scientific knowledge\textsuperscript{see \protect\hyperlink{ref-cW7vGddM}{72}}.
+Language is a well-known obstacle to international collaborative research progress and to widespread scientific knowledge (see \protect\hyperlink{ref-cW7vGddM}{Khelifa et al., 2022}).
 Non-English speaking EEB researchers can potentially miss opportunities to fully integrate version control, reproducibility, and other benefits of GitHub without language-inclusive contents.
@@
 \\
-2. \textbf{Consider taking free courses}, such as those from Software Carpentry\textsuperscript{\protect\hyperlink{ref-pjy75gHr}{73}}, and sharing these courses with your lab members or colleagues. \\
+2.
+\textbf{Consider taking free courses}, such as those from Software Carpentry (\protect\hyperlink{ref-pjy75gHr}{Madicken Munk et al., 2019}), and sharing these courses with your lab members or colleagues.
+\\
 3.
@@
 6.
-\textbf{Consult online resources.} The Jenny Bryan Universe of GitHub material, for example, provides a thorough and accessible introduction for a multitude of research-related uses for GitHub, and includes a book\textsuperscript{\protect\hyperlink{ref-ZvrOcg9w}{74}}, statistics course\textsuperscript{\protect\hyperlink{ref-6CMMeSeD}{75}} and academic article\textsuperscript{\protect\hyperlink{ref-RVetqmsg}{7}}.
+\textbf{Consult online resources.} The Jenny Bryan Universe of GitHub material, for example, provides a thorough and accessible introduction for a multitude of research-related uses for GitHub, and includes a book (\protect\hyperlink{ref-ZvrOcg9w}{Hester, n.d.-b}), statistics course (\protect\hyperlink{ref-6CMMeSeD}{Bryan \& TAs, n.d.}) and academic article (\protect\hyperlink{ref-RVetqmsg}{Bryan, 2018}).
 \\
@@
 \hypertarget{refs}{}
-\begin{CSLReferences}{0}{0}
+\begin{CSLReferences}{1}{0}
+\leavevmode\vadjust pre{\hypertarget{ref-s91uGRZ2}{}}%
+\emph{About code owners}.
+(n.d.).
+GitHub Docs.
+Retrieved October 3, 2022, from \url{https://ghdocs-prod.azurewebsites.net/en/repositories/managing-your-repositorys-settings-and-features/customizing-your-repository/about-code-owners}
+
+\leavevmode\vadjust pre{\hypertarget{ref-1Co6ZZjF1}{}}%
+\emph{About large files on GitHub}.
+(n.d.).
+GitHub Docs.
+Retrieved October 3, 2022, from \url{https://ghdocs-prod.azurewebsites.net/en/repositories/working-with-files/managing-large-files/about-large-files-on-github}
+
+\leavevmode\vadjust pre{\hypertarget{ref-RhBKe0MG}{}}%
+\emph{About Projects}.
+(n.d.).
+GitHub Docs.
+Retrieved October 3, 2022, from \url{https://ghdocs-prod.azurewebsites.net/en/issues/planning-and-tracking-with-projects/learning-about-projects/about-projects}
+
+\leavevmode\vadjust pre{\hypertarget{ref-TOsASkn5}{}}%
+\emph{Adding a license to a repository}.
+(n.d.).
+GitHub Docs.
+Retrieved October 3, 2022, from \url{https://ghdocs-prod.azurewebsites.net/en/communities/setting-up-your-project-for-healthy-contributions/adding-a-license-to-a-repository}
+
+\leavevmode\vadjust pre{\hypertarget{ref-13QX8XU3J}{}}%
+Alston, J.
+M., \& Rick, J.
+A.
+(2021).
+A Beginner's Guide to Conducting Reproducible Research.
+\emph{The Bulletin of the Ecological Society of America}, \emph{102}(2).
+\url{https://doi.org/10.1002/bes2.1801}
+
+\leavevmode\vadjust pre{\hypertarget{ref-UsTxAq4f}{}}%
+Anbaroğlu, B. (2021). A collaborative GIS programming course using GitHub Classroom. \emph{Transactions in GIS}, \emph{25}(6), 3132--3158. \url{https://doi.org/10.1111/tgis.12810}
+
+\leavevmode\vadjust pre{\hypertarget{ref-1HZdsK5Kn}{}}%
+Baker, M. (2016). 1,500 scientists lift the lid on reproducibility. \emph{Nature}, \emph{533}(7604), 452--454. \url{https://doi.org/10.1038/533452a}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Qh7xTLwz}{}}%
+Beaulieu-Jones, B.
+K., \& Greene, C.
+S.
+(2017).
+Reproducibility of computational workflows is automated using continuous analysis.
+\emph{Nature Biotechnology}, \emph{35}(4), 342--346.
+\url{https://doi.org/10.1038/nbt.3780}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Xsdcv6q}{}}%
+Boettiger, C., Lang, D.
+T., \& Wainwright, P.
+C.
+(2012).
+rfishbase: exploring, manipulating and visualizing FishBase data from R.
+\emph{Journal of Fish Biology}, \emph{81}(6), 2030--2039.
+\url{https://doi.org/10.1111/j.1095-8649.2012.03464.x}
+
+\leavevmode\vadjust pre{\hypertarget{ref-ydrk01SR}{}}%
+Briney, K., Coates, H., \& Goben, A. (2020). Foundational Practices of Research Data Management. \emph{Research Ideas and Outcomes}, \emph{6}. \url{https://doi.org/10.3897/rio.6.e56508}
+
+\leavevmode\vadjust pre{\hypertarget{ref-RVetqmsg}{}}%
+Bryan, J. (2018). Excuse Me, Do You Have a Moment to Talk About Version Control? \emph{The American Statistician}, \emph{72}(1), 20--27. \url{https://doi.org/10.1080/00031305.2017.1399928}
+
+\leavevmode\vadjust pre{\hypertarget{ref-6CMMeSeD}{}}%
+Bryan, J., \& TAs, T. S. 545. (n.d.). \emph{STAT 545}. Retrieved October 3, 2022, from \url{https://stat545.com/}
+
+\leavevmode\vadjust pre{\hypertarget{ref-nwCtHDCn}{}}%
+\emph{Build software better, together}. (n.d.). GitHub. Retrieved October 3, 2022, from \url{https://github.com}
+
+\leavevmode\vadjust pre{\hypertarget{ref-FVBWKkZu}{}}%
+Chamberlain, S. A., \& Szöcs, E. (2013). taxize: taxonomic search and retrieval in R. \emph{F1000Research}, \emph{2}, 191. \url{https://doi.org/10.12688/f1000research.2-191.v2}
+
+\leavevmode\vadjust pre{\hypertarget{ref-u5aEVE4B}{}}%
+\emph{Coding Club: A Positive Peer-Learning Community}. (n.d.). Retrieved October 3, 2022, from \url{https://ourcodingclub.github.io/}
+
+\leavevmode\vadjust pre{\hypertarget{ref-lx49NGto}{}}%
+\emph{Connect GitHub to a Project - OSF Support}. (n.d.). Retrieved October 3, 2022, from \url{https://help.osf.io/article/211-connect-github-to-a-project}
+
+\leavevmode\vadjust pre{\hypertarget{ref-T03Api6e}{}}%
+\emph{Continuous Integration and Delivery}. (n.d.). CircleCI. Retrieved October 3, 2022, from \url{https://circleci.com/}
+
+\leavevmode\vadjust pre{\hypertarget{ref-K7nbP1Ty}{}}%
+Crystal-Ornelas, R., Edwards, B.
+P.
+M., Hébert, K., Hudgins, E.
+J., Reyes, L.
+L.
+S., Scott, E.
+R., Grainger, M.
+J., Foroughirad, V., Binley, A.
+D., Brookson, C.
+B., Gaynor, K.
+M., Sabet, S.
+S., Güncan, A., Hillemann, F., Weierbach, H., Gomes, D.
+G.
+E., \& Braga, P.
+H.
+P.
+(2022).
+\emph{Not just for programmers: How GitHub can accelerate collaborative and reproducible research in ecology and evolution}.
+Manubot.
+\url{https://SORTEE-Github-Hackathon.github.io/manuscript/}
+
+\leavevmode\vadjust pre{\hypertarget{ref-1Du6fzB8g}{}}%
+Crystal‐Ornelas, R., Varadharajan, C., Bond‐Lamberty, B., Boye, K., Burrus, M., Cholia, S., Crow, M., Damerow, J., Devarakonda, R., Ely, K.
+S., Goldman, A., Heinz, S., Hendrix, V., Kakalia, Z., Pennington, S.
+C., Robles, E., Rogers, A., Simmonds, M., Velliquette, T., \ldots{} Agarwal, D.
+A.
+(2021).
+A Guide to Using GitHub for Developing and Versioning Data Standards and Reporting Formats.
+\emph{Earth and Space Science}, \emph{8}(8).
+\url{https://doi.org/10.1029/2021ea001797}
+
+\leavevmode\vadjust pre{\hypertarget{ref-NOgBWVAr}{}}%
+Culina, A., van den Berg, I., Evans, S., \& Sánchez-Tójar, A.
+(2020).
+Low availability of code in ecology: A~call for urgent action.
+\emph{PLOS Biology}, \emph{18}(7), e3000763.
+\url{https://doi.org/10.1371/journal.pbio.3000763}
+
+\leavevmode\vadjust pre{\hypertarget{ref-MXxgZJ45}{}}%
+Dawson, C. (2016). \emph{Building tools with GitHub: customize your workflow} (First Edition). O'Reilly.
+
+\leavevmode\vadjust pre{\hypertarget{ref-rTbinQMj}{}}%
+Dietze, M.
+C., Fox, A., Beck-Johnson, L.
+M., Betancourt, J.
+L., Hooten, M.
+B., Jarnevich, C.
+S., Keitt, T.
+H., Kenney, M.
+A., Laney, C.
+M., Larsen, L.
+G., Loescher, H.
+W., Lunch, C.
+K., Pijanowski, B.
+C., Randerson, J.
+T., Read, E.
+K., Tredennick, A.
+T., Vargas, R., Weathers, K.
+C., \& White, E.
+P.
+(2018).
+Iterative near-term ecological forecasting: Needs, opportunities, and challenges.
+\emph{Proceedings of the National Academy of Sciences}, \emph{115}(7), 1424--1432.
+\url{https://doi.org/10.1073/pnas.1710231115}
+
+\leavevmode\vadjust pre{\hypertarget{ref-bZNn2hbh}{}}%
+EllenJCoombs. (2020). \emph{EllenJCoombs/Asymmetry-evolution-cetaceans-for-publication-v.1.0.0} (Version v.1.0.0) {[}Computer software{]}. Zenodo. \url{https://doi.org/10.5281/zenodo.3893943}
+
+\leavevmode\vadjust pre{\hypertarget{ref-RxK4CmfR}{}}%
+Ernest, S.
+K.
+M., Yenni, G.
+M., Allington, G., Bledsoe, E.
+K., Christensen, E.
+M., Diaz, R.
+M., Geluso, K., Goheen, J.
+R., Guo, Q., Heske, E., Kelt, D., Meiners, J.
+M., Munger, J., Restrepo, C., Samson, D.
+A., Schutzenhofer, M.
+R., Skupski, M., Supp, S.
+R., Thibault, K., \ldots{} Valone, T.
+J.
+(2018).
+\emph{The Portal Project: a long-term study of a Chihuahuan desert ecosystem}.
+Cold Spring Harbor Laboratory.
+\url{https://doi.org/10.1101/332783}
+
+\leavevmode\vadjust pre{\hypertarget{ref-NUXbp429}{}}%
+\emph{Features • GitHub Actions}. (n.d.). GitHub. Retrieved October 3, 2022, from \url{https://github.com/features/actions}
+
+\leavevmode\vadjust pre{\hypertarget{ref-D4C4k4ak}{}}%
+Fehr, J., Himpe, C., Rave, S., \& Saak, J. (2021). Sustainable Research Software Hand-Over. \emph{Journal of Open Research Software}, \emph{9}(1), 5. \url{https://doi.org/10.5334/jors.307}
+
+\leavevmode\vadjust pre{\hypertarget{ref-SLq38RVv}{}}%
+Figueiredo, A. S. (2017). Data Sharing: Convert Challenges into Opportunities. \emph{Frontiers in Public Health}, \emph{5}. \url{https://doi.org/10.3389/fpubh.2017.00327}
+
+\leavevmode\vadjust pre{\hypertarget{ref-11GtZ7icJ}{}}%
+\emph{Git Large File Storage}. (n.d.). Git Large File Storage. Retrieved October 3, 2022, from \url{https://git-lfs.github.com/}
+
+\leavevmode\vadjust pre{\hypertarget{ref-pq2Tv1BC}{}}%
+Gomes, D.
+G.
+E., Pottier, P., Crystal-Ornelas, R., Hudgins, E.
+J., Foroughirad, V., Sánchez-Reyes, L.
+L., Turba, R., Martinez, P.
+A., Moreau, D., Bertram, M., Smout, C., \& Gaynor, K.
+(2022).
+\emph{Why don't we share data and code?
+Perceived barriers and benefits to public archiving practices}.
+Center for Open Science.
+\url{https://doi.org/10.31222/osf.io/gaj43}
+
+\leavevmode\vadjust pre{\hypertarget{ref-1HhzKAC1K}{}}%
+Goring, S.
+J., Weathers, K.
+C., Dodds, W.
+K., Soranno, P.
+A., Sweet, L.
+C., Cheruvelil, K.
+S., Kominoski, J.
+S., Rüegg, J., Thorn, A.
+M., \& Utz, R.
+M.
+(2014).
+Improving the culture of interdisciplinary collaboration in ecology by expanding measures of success.
+\emph{Frontiers in Ecology and the Environment}, \emph{12}(1), 39--47.
+\url{https://doi.org/10.1890/120370}
+
+\leavevmode\vadjust pre{\hypertarget{ref-iIEKCTLU}{}}%
+Hampton, S.
+E., Anderson, S.
+S., Bagby, S.
+C., Gries, C., Han, X., Hart, E.
+M., Jones, M.
+B., Lenhardt, W.
+C., MacDonald, A., Michener, W.
+K., Mudge, J., Pourmokhtarian, A., Schildhauer, M.
+P., Woo, K.
+H., \& Zimmerman, N.
+(2015).
+The Tao of open science for ecology.
+\emph{Ecosphere}, \emph{6}(7), art120.
+\url{https://doi.org/10.1890/es14-00402.1}
+
 \leavevmode\vadjust pre{\hypertarget{ref-fJWFe93e}{}}%
-\CSLLeftMargin{1. }
-\CSLRightInline{Hannay, J.
+Hannay, J.
+E., MacLeod, C., Singer, J., Langtangen, H.
+P., Pfahl, D., \& Wilson, G.
+(2009, May).
+How do scientists develop and use scientific software?
+\emph{2009 ICSE Workshop on Software Engineering for Computational Science and Engineering}.
+2009 ICSE Workshop on Software Engineering for Computational Science and Engineering (SECSE).
+\url{https://doi.org/10.1109/secse.2009.5069155}
+
+\leavevmode\vadjust pre{\hypertarget{ref-ZvrOcg9w}{}}%
+Hester, J. B., the STAT 545 TAs, Jim. (n.d.-b). \emph{Let's Git started \textbar{} Happy Git and GitHub for the useR}. Retrieved October 3, 2022, from \url{https://happygitwithr.com/}
+
+\leavevmode\vadjust pre{\hypertarget{ref-13jOlVcpp}{}}%
+Hester, J. B., the STAT 545 TAs, Jim. (n.d.-a). \emph{Let's Git started \textbar{} Happy Git and GitHub for the useR}. Retrieved October 3, 2022, from \url{https://happygitwithr.com/}
+
+\leavevmode\vadjust pre{\hypertarget{ref-YuJbg3zO}{}}%
+Himmelstein, D.
+S., Rubinetti, V., Slochower, D.
+R., Hu, D., Malladi, V.
+S., Greene, C.
+S., \& Gitter, A.
+(2019).
+Open collaborative writing with Manubot.
+\emph{PLOS Computational Biology}, \emph{15}(6), e1007128.
+\url{https://doi.org/10.1371/journal.pcbi.1007128}
+
+\leavevmode\vadjust pre{\hypertarget{ref-YeFSbfFV}{}}%
+\emph{Homepage \textbar{} Travis CI -- Start building today!} (n.d.). Travis CI. Retrieved October 3, 2022, from \url{https://www.travis-ci.com/}
+
+\leavevmode\vadjust pre{\hypertarget{ref-GQj3c17f}{}}%
+Hudgins, E. (2022). \emph{emmajhudgins/UStreedamage: publication release} (accepted) {[}Computer software{]}. Zenodo. \url{https://doi.org/10.5281/zenodo.6097109}
+
+\leavevmode\vadjust pre{\hypertarget{ref-18PTmKJkq}{}}%
+January 18, P.
+L.
+B.
+K., \& Pm, 2022.
+2:51.
+(2020, February 4).
+\#PruittData and the Ethics of Data in Science.
+\emph{Ecology for the Masses}.
+\url{https://ecologyforthemasses.com/2020/02/04/pruittdata-and-the-ethics-of-data-in-science/}
+
+\leavevmode\vadjust pre{\hypertarget{ref-wwHxTOtm}{}}%
+Kanza, S., Willoughby, C., Gibbins, N., Whitby, R., Frey, J.
+G., Erjavec, J., Zupančič, K., Hren, M., \& Kovač, K.
+(2017).
+Electronic lab notebooks: can they replace paper?
+\emph{Journal of Cheminformatics}, \emph{9}(1).
+\url{https://doi.org/10.1186/s13321-017-0221-3}
+
+\leavevmode\vadjust pre{\hypertarget{ref-cfgXxgt1}{}}%
+Keitt, T. H., \& Abelson, E. S. (2021). Ecology in the age of automation. \emph{Science}, \emph{373}(6557), 858--859. \url{https://doi.org/10.1126/science.abi4692}
+
+\leavevmode\vadjust pre{\hypertarget{ref-cW7vGddM}{}}%
+Khelifa, R., Amano, T., \& Nuñez, M.
+A.
+(2022).
+A solution for breaking the language barrier.
+\emph{Trends in Ecology \&Amp; Evolution}, \emph{37}(2), 109--112.
+\url{https://doi.org/10.1016/j.tree.2021.11.003}
+
+\leavevmode\vadjust pre{\hypertarget{ref-lJAgyhYq}{}}%
+Kim, A.
+Y., Herrmann, V., Bareto, R., Calkins, B., Gonzalez‐Akre, E., Johnson, D.
+J., Jordan, J.
+A., Magee, L., McGregor, I.
+R., Montero, N., Novak, K., Rogers, T., Shue, J., \& Anderson‐Teixeira, K.
+J.
+(2022).
+Implementing GitHub Actions continuous integration to reduce error rates in ecological data collection.
+\emph{Methods in Ecology and Evolution}.
+\url{https://doi.org/10.1111/2041-210x.13982}
+
+\leavevmode\vadjust pre{\hypertarget{ref-139b0pSGc}{}}%
+Leibzon, W.
+(2016, August).
+Social network of software development at GitHub.
+\emph{2016 IEEE/ACM International Conference on Advances in Social Networks Analysis and Mining (ASONAM)}.
+2016 IEEE/ACM International Conference on Advances in Social Networks Analysis and Mining (ASONAM).
+\url{https://doi.org/10.1109/asonam.2016.7752419}
+
+\leavevmode\vadjust pre{\hypertarget{ref-3DKwn1sY}{}}%
+Lowndes, J.
+S.
+S., Best, B.
+D., Scarborough, C., Afflerbach, J.
+C., Frazier, M.
+R., O'Hara, C.
+C., Jiang, N., \& Halpern, B.
+S.
+(2017).
+Our path to better science in less time using open data science tools.
+\emph{Nature Ecology \&Amp; Evolution}, \emph{1}(6).
+\url{https://doi.org/10.1038/s41559-017-0160}
+
+\leavevmode\vadjust pre{\hypertarget{ref-ZI1OqZNr}{}}%
+Lrharper1.
+(2018).
+\emph{Hulluni-Bioinformatics/Harper\_Et\_Al\_2018: Github Repository Deposited With Harper Et Al.
+(2018) In Ecology And Evolution.} Zenodo.
+\url{https://doi.org/10.5281/zenodo.1188710}
+
+\leavevmode\vadjust pre{\hypertarget{ref-pjy75gHr}{}}%
+Madicken Munk, Koziar, K., Leinweber, K., Raniere Silva, Michonneau, F., McCue, R., Hejazi, N., Waldman, S., Emonet, R., Harris, R.
+M., Olex, A.
+L., Becker, E.
+A., Lever, J., Burle, M.-H., Moore, B., Umihiko Hoshijima, Maji, A., Topçuoğlu, B.
+D., Junghans, C., \ldots{} Wolmar Nyberg Åkerström.
+(2019).
+\emph{swcarpentry/git-novice: Software Carpentry: Version Control with Git, June 2019} (Version v2019.06.1).
+Zenodo.
+\url{https://doi.org/10.5281/zenodo.3264950}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Re6Eg2va}{}}%
+\emph{Manubot - Manuscripts, open and automated}. (n.d.). Retrieved October 3, 2022, from \url{https://manubot.org}
+
+\leavevmode\vadjust pre{\hypertarget{ref-MwwMapRG}{}}%
+Marwick, B., Boettiger, C., \& Mullen, L.
+(2018).
+Packaging Data Analytical Work Reproducibly Using R (and Friends).
+\emph{The American Statistician}, \emph{72}(1), 80--88.
+\url{https://doi.org/10.1080/00031305.2017.1375986}
+
+\leavevmode\vadjust pre{\hypertarget{ref-mmCOSRfr}{}}%
+McIntire, E.
+J.
+B., Chubaty, A.
+M., Cumming, S.
+G., Andison, D., Barros, C., Boisvenue, C., Haché, S., Luo, Y., Micheletti, T., \& Stewart, F.
 E.
-\emph{et al.} How do scientists develop and use scientific software?
-in \emph{2009 ICSE Workshop on Software Engineering for Computational Science and Engineering} (IEEE, 2009).
-doi:\href{https://doi.org/10.1109/secse.2009.5069155}{10.1109/secse.2009.5069155}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-1Kqna6l2}{}}%
-\CSLLeftMargin{2. }
-\CSLRightInline{Perkel, J. M. \href{https://doi.org/10.1038/d41586-020-02462-7}{Challenge to scientists: does your ten-year-old code still run?} \emph{Nature} \textbf{584}, 656--658 (2020).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-10ghgV3S8}{}}%
-\CSLLeftMargin{3. }
-\CSLRightInline{Perkel, J. \href{https://doi.org/10.1038/538127a}{Democratic databases: science on GitHub}. \emph{Nature} \textbf{538}, 127--128 (2016).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-10SpoByIw}{}}%
-\CSLLeftMargin{4. }
-\CSLRightInline{Prabhu, P.
-\emph{et al.} A survey of the practice of computational science.
-in \emph{State of the Practice Reports on - SC '11} (ACM Press, 2011).
-doi:\href{https://doi.org/10.1145/2063348.2063374}{10.1145/2063348.2063374}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-O6UbstGG}{}}%
-\CSLLeftMargin{5. }
-\CSLRightInline{Wilson, G. \emph{et al.} \href{https://doi.org/10.1371/journal.pbio.1001745}{Best Practices for Scientific Computing}. \emph{PLoS Biol} \textbf{12}, e1001745 (2014).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-nwCtHDCn}{}}%
-\CSLLeftMargin{6. }
-\CSLRightInline{Build software better, together. \emph{GitHub} \url{https://github.com}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-RVetqmsg}{}}%
-\CSLLeftMargin{7. }
-\CSLRightInline{Bryan, J.
-\href{https://doi.org/10.1080/00031305.2017.1399928}{Excuse Me, Do You Have a Moment to Talk About Version Control?} \emph{The American Statistician} \textbf{72}, 20--27 (2018).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-4ny1onB0}{}}%
-\CSLLeftMargin{8. }
-\CSLRightInline{Ram, K. \href{https://doi.org/10.1186/1751-0473-8-7}{Git can facilitate greater reproducibility and increased transparency in science}. \emph{Source Code Biol Med} \textbf{8}, (2013).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-kEX5dgzK}{}}%
-\CSLLeftMargin{9. }
-\CSLRightInline{Perez-Riverol, Y.
-\emph{et al.} \href{https://doi.org/10.1371/journal.pcbi.1004947}{Ten Simple Rules for Taking Advantage of Git and GitHub}.
-\emph{PLoS Comput Biol} \textbf{12}, e1004947 (2016).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-13jOlVcpp}{}}%
-\CSLLeftMargin{10. }
-\CSLRightInline{Hester, J. B., the STAT 545 TAs, Jim. \emph{\href{https://happygitwithr.com/}{Let's Git started \textbar{} Happy Git and GitHub for the useR}}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-u5aEVE4B}{}}%
-\CSLLeftMargin{11. }
-\CSLRightInline{Coding Club: A Positive Peer-Learning Community. \url{https://ourcodingclub.github.io/}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-3DKwn1sY}{}}%
-\CSLLeftMargin{12. }
-\CSLRightInline{Lowndes, J.
-S.
-S.
-\emph{et al.} \href{https://doi.org/10.1038/s41559-017-0160}{Our path to better science in less time using open data science tools}.
-\emph{Nat Ecol Evol} \textbf{1}, (2017).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-139b0pSGc}{}}%
-\CSLLeftMargin{13. }
-\CSLRightInline{Leibzon, W.
-Social network of software development at GitHub.
-in \emph{2016 IEEE/ACM International Conference on Advances in Social Networks Analysis and Mining (ASONAM)} (IEEE, 2016).
-doi:\href{https://doi.org/10.1109/asonam.2016.7752419}{10.1109/asonam.2016.7752419}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-ydrk01SR}{}}%
-\CSLLeftMargin{14. }
-\CSLRightInline{Briney, K., Coates, H. \& Goben, A. \href{https://doi.org/10.3897/rio.6.e56508}{Foundational Practices of Research Data Management}. \emph{RIO} \textbf{6}, (2020).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-13QX8XU3J}{}}%
-\CSLLeftMargin{15. }
-\CSLRightInline{Alston, J. M. \& Rick, J. A. \href{https://doi.org/10.1002/bes2.1801}{A Beginner's Guide to Conducting Reproducible Research}. \emph{Bull. Ecol. Soc. Am.} \textbf{102}, (2021).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-pq2Tv1BC}{}}%
-\CSLLeftMargin{16. }
-\CSLRightInline{Gomes, D.
-G.
+C.
+(2022).
+PERFICT: A Re‐imagined foundation for predictive ecology.
+\emph{Ecology Letters}, \emph{25}(6), 1345--1351.
+\url{https://doi.org/10.1111/ele.13994}
+
+\leavevmode\vadjust pre{\hypertarget{ref-1Ep9EJL6y}{}}%
+Meyer, M. (2014). Continuous Integration and Its Tools. \emph{IEEE Software}, \emph{31}(3), 14--16. \url{https://doi.org/10.1109/ms.2014.58}
+
+\leavevmode\vadjust pre{\hypertarget{ref-bhDgD6lF}{}}%
+Micheletti, T., Stewart, F.
 E.
-\emph{et al.} Why don't we share data and code?
-Perceived barriers and benefits to public archiving practices.
-(2022) doi:\href{https://doi.org/10.31222/osf.io/gaj43}{10.31222/osf.io/gaj43}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-MwwMapRG}{}}%
-\CSLLeftMargin{17. }
-\CSLRightInline{Marwick, B., Boettiger, C.
-\& Mullen, L.
-\href{https://doi.org/10.1080/00031305.2017.1375986}{Packaging Data Analytical Work Reproducibly Using R (and Friends)}.
-\emph{The American Statistician} \textbf{72}, 80--88 (2018).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-1Co6ZZjF1}{}}%
-\CSLLeftMargin{18. }
-\CSLRightInline{About large files on GitHub. \emph{GitHub Docs} \url{https://ghdocs-prod.azurewebsites.net/en/repositories/working-with-files/managing-large-files/about-large-files-on-github}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-11GtZ7icJ}{}}%
-\CSLLeftMargin{19. }
-\CSLRightInline{Git Large File Storage. \emph{Git Large File Storage} \url{https://git-lfs.github.com/}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-wwHxTOtm}{}}%
-\CSLLeftMargin{20. }
-\CSLRightInline{Kanza, S. \emph{et al.} \href{https://doi.org/10.1186/s13321-017-0221-3}{Electronic lab notebooks: can they replace paper?} \emph{J Cheminform} \textbf{9}, (2017).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-10V7x4H4l}{}}%
-\CSLLeftMargin{21. }
-\CSLRightInline{Schnell, S.
-\href{https://doi.org/10.1371/journal.pcbi.1004385}{Ten Simple Rules for a Computational Biologist's Laboratory Notebook}.
-\emph{PLoS Comput Biol} \textbf{11}, e1004385 (2015).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-RhBKe0MG}{}}%
-\CSLLeftMargin{22. }
-\CSLRightInline{About Projects. \emph{GitHub Docs} \url{https://ghdocs-prod.azurewebsites.net/en/issues/planning-and-tracking-with-projects/learning-about-projects/about-projects}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-1GRWGlDWy}{}}%
-\CSLLeftMargin{23. }
-\CSLRightInline{Slack. GitHub for Slack. \emph{Slack Help Center} \url{https://slack.com/help/articles/232289568-GitHub-for-Slack}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-QqMezOMg}{}}%
-\CSLLeftMargin{24. }
-\CSLRightInline{Xie, Y., Allaire, J. J. \& Grolemund, G. \emph{R Markdown: the definitive guide}. (CRC Press, Taylor and Francis Group, 2019).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-MDQfMwCW}{}}%
-\CSLLeftMargin{25. }
-\CSLRightInline{Quickstart for GitHub Pages. \emph{GitHub Docs} \url{https://ghdocs-prod.azurewebsites.net/en/pages/quickstart}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-dqrFjoSb}{}}%
-\CSLLeftMargin{26. }
-\CSLRightInline{Trujillo, G.
-\& Tanner, K.
-D.
-\href{https://doi.org/10.1187/cbe.13-12-0241}{Considering the Role of Affect in Learning: Monitoring Students' Self-Efficacy, Sense of Belonging, and Science Identity}.
-\emph{LSE} \textbf{13}, 6--15 (2014).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-HiIPSSHV}{}}%
-\CSLLeftMargin{27. }
-\CSLRightInline{Smaglik, P.
-\href{https://doi.org/10.1038/nj7142-347a}{Creating better lab websites gives potential collaborators and recruiters a clearer window into your world.} \emph{Nature} \textbf{447}, 347--347 (2007).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-MXxgZJ45}{}}%
-\CSLLeftMargin{28. }
-\CSLRightInline{Dawson, C. \emph{Building tools with GitHub: customize your workflow}. (O'Reilly, 2016).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-PLmDFZrm}{}}%
-\CSLLeftMargin{29. }
-\CSLRightInline{Tenopir, C.
-\emph{et al.} \href{https://doi.org/10.1371/journal.pone.0229003}{Data sharing, management, use, and reuse: Practices and perceptions of scientists worldwide}.
-\emph{PLoS ONE} \textbf{15}, e0229003 (2020).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-1Hcf13Q0k}{}}%
-\CSLLeftMargin{30. }
-\CSLRightInline{Nugroho, R.
-P., Zuiderwijk, A., Janssen, M.
-\& de Jong, M.
-\href{https://doi.org/10.1108/tg-03-2014-0008}{A comparison of national open data policies: lessons learned}.
-\emph{Transforming Government: People, Process and Policy} \textbf{9}, 286--308 (2015).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-1Ch6LSHef}{}}%
-\CSLLeftMargin{31. }
-\CSLRightInline{Wicherts, J.
-M., Bakker, M.
-\& Molenaar, D.
-\href{https://doi.org/10.1371/journal.pone.0026828}{Willingness to Share Research Data Is Related to the Strength of the Evidence and the Quality of Reporting of Statistical Results}.
-\emph{PLoS ONE} \textbf{6}, e26828 (2011).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-SLq38RVv}{}}%
-\CSLLeftMargin{32. }
-\CSLRightInline{Figueiredo, A. S. \href{https://doi.org/10.3389/fpubh.2017.00327}{Data Sharing: Convert Challenges into Opportunities}. \emph{Front. Public Health} \textbf{5}, (2017).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-1CzUZwyU2}{}}%
-\CSLLeftMargin{33. }
-\CSLRightInline{Tenopir, C.
-\emph{et al.} \href{https://doi.org/10.1371/journal.pone.0134826}{Changes in Data Sharing and Data Reuse Practices and Perceptions among Scientists Worldwide}.
-\emph{PLoS ONE} \textbf{10}, e0134826 (2015).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-666HppfO}{}}%
-\CSLLeftMargin{34. }
-\CSLRightInline{Pronk, T.
-E., Wiersma, P.
-H., van Weerden, A.
-\& Schieving, F.
-\href{https://doi.org/10.7717/peerj.1242}{A game theoretic analysis of research data sharing}.
-\emph{PeerJ} \textbf{3}, e1242 (2015).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-1CcAUn3Lu}{}}%
-\CSLLeftMargin{35. }
-\CSLRightInline{Piwowar, H.
-A., Day, R.
-S.
-\& Fridsma, D.
+C., Cumming, S.
+G., Haché, S., Stralberg, D., Tremblay, J.
+A., Barros, C., Eddy, I.
+M.
+S., Chubaty, A.
+M., Leblond, M., Pankratz, R.
+F., Mahon, C.
+L., Van Wilgenburg, S.
+L., Bayne, E.
+M., Schmiegelow, F., \& McIntire, E.
+J.
 B.
-\href{https://doi.org/10.1371/journal.pone.0000308}{Sharing Detailed Research Data Is Associated with Increased Citation Rate}.
-\emph{PLoS ONE} \textbf{2}, e308 (2007).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-4LaijDIZ}{}}%
-\CSLLeftMargin{36. }
-\CSLRightInline{\href{https://doi.org/10.1038/ncb3506}{On data availability, reproducibility and reuse}. \emph{Nat Cell Biol} \textbf{19}, 259--259 (2017).}
+(2021).
+Assessing Pathways of Climate Change Effects in SpaDES: An Application to Boreal Landbirds of Northwest Territories Canada.
+\emph{Frontiers in Ecology and Evolution}, \emph{9}.
+\url{https://doi.org/10.3389/fevo.2021.679673}
 
 \leavevmode\vadjust pre{\hypertarget{ref-uBJwnPbq}{}}%
-\CSLLeftMargin{37. }
-\CSLRightInline{Mislan, K.
+Mislan, K.
 A.
 S., Heer, J.
+M., \& White, E.
+P.
+(2016).
+Elevating The Status of Code in Ecology.
+\emph{Trends in Ecology \&Amp; Evolution}, \emph{31}(1), 4--7.
+\url{https://doi.org/10.1016/j.tree.2015.11.006}
+
+\leavevmode\vadjust pre{\hypertarget{ref-kZzfmBNu}{}}%
+Naujokaitis-Lewis, I., Endicott, S., \& Guezen, J.
 M.
-\& White, E.
-P.
-\href{https://doi.org/10.1016/j.tree.2015.11.006}{Elevating The Status of Code in Ecology}.
-\emph{Trends in Ecology \&amp; Evolution} \textbf{31}, 4--7 (2016).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-1HZdsK5Kn}{}}%
-\CSLLeftMargin{38. }
-\CSLRightInline{Baker, M. \href{https://doi.org/10.1038/533452a}{1,500 scientists lift the lid on reproducibility}. \emph{Nature} \textbf{533}, 452--454 (2016).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-1Du6fzB8g}{}}%
-\CSLLeftMargin{39. }
-\CSLRightInline{Crystal‐Ornelas, R.
-\emph{et al.} \href{https://doi.org/10.1029/2021ea001797}{A Guide to Using GitHub for Developing and Versioning Data Standards and Reporting Formats}.
-\emph{Earth Space Sci} \textbf{8}, (2021).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-iIEKCTLU}{}}%
-\CSLLeftMargin{40. }
-\CSLRightInline{Hampton, S. E. \emph{et al.} \href{https://doi.org/10.1890/es14-00402.1}{The Tao of open science for ecology}. \emph{Ecosphere} \textbf{6}, art120 (2015).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-TOsASkn5}{}}%
-\CSLLeftMargin{41. }
-\CSLRightInline{Adding a license to a repository.
-\emph{GitHub Docs} \url{https://ghdocs-prod.azurewebsites.net/en/communities/setting-up-your-project-for-healthy-contributions/adding-a-license-to-a-repository}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-1BJcvyTmV}{}}%
-\CSLLeftMargin{42. }
-\CSLRightInline{Vale, G., Schmid, A., Santos, A.
-R., de Almeida, E.
-S.
-\& Apel, S.
-\href{https://doi.org/10.1007/s10664-019-09774-x}{On the relation between Github communication activity and merge conflicts}.
-\emph{Empir Software Eng} \textbf{25}, 402--433 (2019).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-K7nbP1Ty}{}}%
-\CSLLeftMargin{43. }
-\CSLRightInline{Crystal-Ornelas, R.
-\emph{et al.} \emph{Not just for programmers: How GitHub can accelerate collaborative and reproducible research in ecology and evolution}.
-\url{https://SORTEE-Github-Hackathon.github.io/manuscript/} (2022).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-hm9PaCLD}{}}%
-\CSLLeftMargin{44. }
-\CSLRightInline{Song, X., Goldstein, S.
-C.
-\& Sakr, M.
-Using Peer Code Review as an Educational Tool.
-in \emph{Proceedings of the 2020 ACM Conference on Innovation and Technology in Computer Science Education} (ACM, 2020).
-doi:\href{https://doi.org/10.1145/3341525.3387370}{10.1145/3341525.3387370}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Re6Eg2va}{}}%
-\CSLLeftMargin{45. }
-\CSLRightInline{Manubot - Manuscripts, open and automated. \url{https://manubot.org}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-YuJbg3zO}{}}%
-\CSLLeftMargin{46. }
-\CSLRightInline{Himmelstein, D. S. \emph{et al.} \href{https://doi.org/10.1371/journal.pcbi.1007128}{Open collaborative writing with Manubot}. \emph{PLoS Comput Biol} \textbf{15}, e1007128 (2019).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Xsdcv6q}{}}%
-\CSLLeftMargin{47. }
-\CSLRightInline{Boettiger, C., Lang, D.
-T.
-\& Wainwright, P.
-C.
-\href{https://doi.org/10.1111/j.1095-8649.2012.03464.x}{rfishbase: exploring, manipulating and visualizing FishBase data from R}.
-\emph{Journal of Fish Biology} \textbf{81}, 2030--2039 (2012).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-FVBWKkZu}{}}%
-\CSLLeftMargin{48. }
-\CSLRightInline{Chamberlain, S. A. \& Szöcs, E. \href{https://doi.org/10.12688/f1000research.2-191.v2}{taxize: taxonomic search and retrieval in R}. \emph{F1000Res} \textbf{2}, 191 (2013).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-NOgBWVAr}{}}%
-\CSLLeftMargin{49. }
-\CSLRightInline{Culina, A., van den Berg, I., Evans, S.
-\& Sánchez-Tójar, A.
-\href{https://doi.org/10.1371/journal.pbio.3000763}{Low availability of code in ecology: A~call for urgent action}.
-\emph{PLoS Biol} \textbf{18}, e3000763 (2020).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-18PTmKJkq}{}}%
-\CSLLeftMargin{50. }
-\CSLRightInline{January 18, P.
-L.
+(2022).
+CAN-SAR: A database of Canadian species at risk information.
+\emph{Scientific Data}, \emph{9}(1).
+\url{https://doi.org/10.1038/s41597-022-01381-8}
+
+\leavevmode\vadjust pre{\hypertarget{ref-1Hcf13Q0k}{}}%
+Nugroho, R.
+P., Zuiderwijk, A., Janssen, M., \& de Jong, M.
+(2015).
+A comparison of national open data policies: lessons learned.
+\emph{Transforming Government: People, Process and Policy}, \emph{9}(3), 286--308.
+\url{https://doi.org/10.1108/tg-03-2014-0008}
+
+\leavevmode\vadjust pre{\hypertarget{ref-4LaijDIZ}{}}%
+On data availability, reproducibility and reuse. (2017). \emph{Nature Cell Biology}, \emph{19}(4), 259--259. \url{https://doi.org/10.1038/ncb3506}
+
+\leavevmode\vadjust pre{\hypertarget{ref-kEX5dgzK}{}}%
+Perez-Riverol, Y., Gatto, L., Wang, R., Sachsenberg, T., Uszkoreit, J., Leprevost, F.
+da V., Fufezan, C., Ternent, T., Eglen, S.
+J., Katz, D.
+S., Pollard, T.
+J., Konovalov, A., Flight, R.
+M., Blin, K., \& Vizcaíno, J.
+A.
+(2016).
+Ten Simple Rules for Taking Advantage of Git and GitHub.
+\emph{PLOS Computational Biology}, \emph{12}(7), e1004947.
+\url{https://doi.org/10.1371/journal.pcbi.1004947}
+
+\leavevmode\vadjust pre{\hypertarget{ref-10ghgV3S8}{}}%
+Perkel, J. (2016). Democratic databases: science on GitHub. \emph{Nature}, \emph{538}(7623), 127--128. \url{https://doi.org/10.1038/538127a}
+
+\leavevmode\vadjust pre{\hypertarget{ref-1Kqna6l2}{}}%
+Perkel, J. M. (2020). Challenge to scientists: does your ten-year-old code still run? \emph{Nature}, \emph{584}(7822), 656--658. \url{https://doi.org/10.1038/d41586-020-02462-7}
+
+\leavevmode\vadjust pre{\hypertarget{ref-1CcAUn3Lu}{}}%
+Piwowar, H.
+A., Day, R.
+S., \& Fridsma, D.
 B.
-K.
-\& Pm, 2022.
-2:51.
-\#PruittData and the Ethics of Data in Science.
-\emph{Ecology for the Masses} \url{https://ecologyforthemasses.com/2020/02/04/pruittdata-and-the-ethics-of-data-in-science/} (2020).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-D4C4k4ak}{}}%
-\CSLLeftMargin{51. }
-\CSLRightInline{Fehr, J., Himpe, C., Rave, S. \& Saak, J. \href{https://doi.org/10.5334/jors.307}{Sustainable Research Software Hand-Over}. \emph{JORS} \textbf{9}, 5 (2021).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-19kmNxiHc}{}}%
-\CSLLeftMargin{52. }
-\CSLRightInline{Vines, Timothy~H.
-\emph{et al.} \href{https://doi.org/10.1016/j.cub.2013.11.014}{The Availability of Research Data Declines Rapidly with Article Age}.
-\emph{Current Biology} \textbf{24}, 94--97 (2014).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-s91uGRZ2}{}}%
-\CSLLeftMargin{53. }
-\CSLRightInline{About code owners.
-\emph{GitHub Docs} \url{https://ghdocs-prod.azurewebsites.net/en/repositories/managing-your-repositorys-settings-and-features/customizing-your-repository/about-code-owners}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-cfgXxgt1}{}}%
-\CSLLeftMargin{54. }
-\CSLRightInline{Keitt, T. H. \& Abelson, E. S. \href{https://doi.org/10.1126/science.abi4692}{Ecology in the age of automation}. \emph{Science} \textbf{373}, 858--859 (2021).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-bhDgD6lF}{}}%
-\CSLLeftMargin{55. }
-\CSLRightInline{Micheletti, T.
-\emph{et al.} \href{https://doi.org/10.3389/fevo.2021.679673}{Assessing Pathways of Climate Change Effects in SpaDES: An Application to Boreal Landbirds of Northwest Territories Canada}.
-\emph{Front.
-Ecol.
-Evol.} \textbf{9}, (2021).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-lXvpQxeN}{}}%
-\CSLLeftMargin{56. }
-\CSLRightInline{Yenni, G. M. \emph{et al.} Developing a modern data workflow for evolving data. (2018) doi:\href{https://doi.org/10.1101/344804}{10.1101/344804}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Qh7xTLwz}{}}%
-\CSLLeftMargin{57. }
-\CSLRightInline{Beaulieu-Jones, B.
-K.
-\& Greene, C.
-S.
-\href{https://doi.org/10.1038/nbt.3780}{Reproducibility of computational workflows is automated using continuous analysis}.
-\emph{Nat Biotechnol} \textbf{35}, 342--346 (2017).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-SirQKFIz}{}}%
-\CSLLeftMargin{58. }
-\CSLRightInline{White, E.
-P.
-\emph{et al.} \href{https://doi.org/10.1111/2041-210x.13104}{Developing an automated iterative near‐term forecasting system for an ecological study}.
-\emph{Methods Ecol Evol} \textbf{10}, 332--344 (2018).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-1Ep9EJL6y}{}}%
-\CSLLeftMargin{59. }
-\CSLRightInline{Meyer, M. \href{https://doi.org/10.1109/ms.2014.58}{Continuous Integration and Its Tools}. \emph{IEEE Softw.} \textbf{31}, 14--16 (2014).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-ufw0ZdnI}{}}%
-\CSLLeftMargin{60. }
-\CSLRightInline{Soergel, D. A. W. \href{https://doi.org/10.12688/f1000research.5930.2}{Rampant software errors may undermine scientific results}. \emph{F1000Res} \textbf{3}, 303 (2015).}
+(2007).
+Sharing Detailed Research Data Is Associated with Increased Citation Rate.
+\emph{PLoS ONE}, \emph{2}(3), e308.
+\url{https://doi.org/10.1371/journal.pone.0000308}
+
+\leavevmode\vadjust pre{\hypertarget{ref-10SpoByIw}{}}%
+Prabhu, P., Zhang, Y., Ghosh, S., August, D.
+I., Huang, J., Beard, S., Kim, H., Oh, T., Jablin, T.
+B., Johnson, N.
+P., Zoufaly, M., Raman, A., Liu, F., \& Walker, D.
+(2011).
+A survey of the practice of computational science.
+\emph{State of the Practice Reports on - SC '11}.
+State of the Practice Reports.
+\url{https://doi.org/10.1145/2063348.2063374}
+
+\leavevmode\vadjust pre{\hypertarget{ref-666HppfO}{}}%
+Pronk, T. E., Wiersma, P. H., van Weerden, A., \& Schieving, F. (2015). A game theoretic analysis of research data sharing. \emph{PeerJ}, \emph{3}, e1242. \url{https://doi.org/10.7717/peerj.1242}
+
+\leavevmode\vadjust pre{\hypertarget{ref-MDQfMwCW}{}}%
+\emph{Quickstart for GitHub Pages}. (n.d.). GitHub Docs. Retrieved October 3, 2022, from \url{https://ghdocs-prod.azurewebsites.net/en/pages/quickstart}
+
+\leavevmode\vadjust pre{\hypertarget{ref-4ny1onB0}{}}%
+Ram, K. (2013). Git can facilitate greater reproducibility and increased transparency in science. \emph{Source Code for Biology and Medicine}, \emph{8}(1). \url{https://doi.org/10.1186/1751-0473-8-7}
 
 \leavevmode\vadjust pre{\hypertarget{ref-12103x16N}{}}%
-\CSLLeftMargin{61. }
-\CSLRightInline{Scheller, R.
+Scheller, R.
 M., Sturtevant, B.
@@
 J., Ward, B.
-C.
-\& Mladenoff, D.
+C., \& Mladenoff, D.
 J.
-\href{https://doi.org/10.1890/080141}{Increasing the reliability of ecological models using modern software engineering techniques}.
-\emph{Frontiers in Ecology and the Environment} \textbf{8}, 253--260 (2010).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-rTbinQMj}{}}%
-\CSLLeftMargin{62. }
-\CSLRightInline{Dietze, M.
-C.
-\emph{et al.} \href{https://doi.org/10.1073/pnas.1710231115}{Iterative near-term ecological forecasting: Needs, opportunities, and challenges}.
-\emph{Proc.
-Natl.
-Acad.
-Sci.
-U.S.A.} \textbf{115}, 1424--1432 (2018).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-mmCOSRfr}{}}%
-\CSLLeftMargin{63. }
-\CSLRightInline{McIntire, E.
+(2010).
+Increasing the reliability of ecological models using modern software engineering techniques.
+\emph{Frontiers in Ecology and the Environment}, \emph{8}(5), 253--260.
+\url{https://doi.org/10.1890/080141}
+
+\leavevmode\vadjust pre{\hypertarget{ref-10V7x4H4l}{}}%
+Schnell, S. (2015). Ten Simple Rules for a Computational Biologist's Laboratory Notebook. \emph{PLOS Computational Biology}, \emph{11}(9), e1004385. \url{https://doi.org/10.1371/journal.pcbi.1004385}
+
+\leavevmode\vadjust pre{\hypertarget{ref-1GRWGlDWy}{}}%
+Slack. (n.d.). \emph{GitHub for Slack}. Slack Help Center. Retrieved October 3, 2022, from \url{https://slack.com/help/articles/232289568-GitHub-for-Slack}
+
+\leavevmode\vadjust pre{\hypertarget{ref-HiIPSSHV}{}}%
+Smaglik, P.
+(2007).
+Creating better lab websites gives potential collaborators and recruiters a clearer window into your world.
+\emph{Nature}, \emph{447}(7142), 347--347.
+\url{https://doi.org/10.1038/nj7142-347a}
+
+\leavevmode\vadjust pre{\hypertarget{ref-ufw0ZdnI}{}}%
+Soergel, D. A. W. (2015). Rampant software errors may undermine scientific results. \emph{F1000Research}, \emph{3}, 303. \url{https://doi.org/10.12688/f1000research.5930.2}
+
+\leavevmode\vadjust pre{\hypertarget{ref-hm9PaCLD}{}}%
+Song, X., Goldstein, S.
+C., \& Sakr, M.
+(2020, June 2).
+Using Peer Code Review as an Educational Tool.
+\emph{Proceedings of the 2020 ACM Conference on Innovation and Technology in Computer Science Education}.
+ITiCSE '20: Innovation and Technology in Computer Science Education.
+\url{https://doi.org/10.1145/3341525.3387370}
+
+\leavevmode\vadjust pre{\hypertarget{ref-1CzUZwyU2}{}}%
+Tenopir, C., Dalton, E.
+D., Allard, S., Frame, M., Pjesivac, I., Birch, B., Pollock, D., \& Dorsett, K.
+(2015).
+Changes in Data Sharing and Data Reuse Practices and Perceptions among Scientists Worldwide.
+\emph{PLOS ONE}, \emph{10}(8), e0134826.
+\url{https://doi.org/10.1371/journal.pone.0134826}
+
+\leavevmode\vadjust pre{\hypertarget{ref-PLmDFZrm}{}}%
+Tenopir, C., Rice, N.
+M., Allard, S., Baird, L., Borycz, J., Christian, L., Grant, B., Olendorf, R., \& Sandusky, R.
 J.
-B.
-\emph{et al.} \href{https://doi.org/10.1111/ele.13994}{PERFICT: A Re‐imagined foundation for predictive ecology}.
-\emph{Ecology Letters} \textbf{25}, 1345--1351 (2022).}
+(2020).
+Data sharing, management, use, and reuse: Practices and perceptions of scientists worldwide.
+\emph{PLOS ONE}, \emph{15}(3), e0229003.
+\url{https://doi.org/10.1371/journal.pone.0229003}
+
+\leavevmode\vadjust pre{\hypertarget{ref-dqrFjoSb}{}}%
+Trujillo, G., \& Tanner, K.
+D.
+(2014).
+Considering the Role of Affect in Learning: Monitoring Students' Self-Efficacy, Sense of Belonging, and Science Identity.
+\emph{CBE---Life Sciences Education}, \emph{13}(1), 6--15.
+\url{https://doi.org/10.1187/cbe.13-12-0241}
+
+\leavevmode\vadjust pre{\hypertarget{ref-1BJcvyTmV}{}}%
+Vale, G., Schmid, A., Santos, A.
+R., de Almeida, E.
+S., \& Apel, S.
+(2019).
+On the relation between Github communication activity and merge conflicts.
+\emph{Empirical Software Engineering}, \emph{25}(1), 402--433.
+\url{https://doi.org/10.1007/s10664-019-09774-x}
+
+\leavevmode\vadjust pre{\hypertarget{ref-19kmNxiHc}{}}%
+Vines, Timothy~H., Albert, Arianne~Y.
+K., Andrew, Rose~L., Débarre, F., Bock, Dan~G., Franklin, Michelle~T., Gilbert, Kimberly~J., Moore, J.-S., Renaut, S., \& Rennison, Diana~J.
+(2014).
+The Availability of Research Data Declines Rapidly with Article Age.
+\emph{Current Biology}, \emph{24}(1), 94--97.
+\url{https://doi.org/10.1016/j.cub.2013.11.014}
+
+\leavevmode\vadjust pre{\hypertarget{ref-SirQKFIz}{}}%
+White, E.
+P., Yenni, G.
+M., Taylor, S.
+D., Christensen, E.
+M., Bledsoe, E.
+K., Simonis, J.
+L., \& Ernest, S.
+K.
+M.
+(2018).
+Developing an automated iterative near‐term forecasting system for an ecological study.
+\emph{Methods in Ecology and Evolution}, \emph{10}(3), 332--344.
+\url{https://doi.org/10.1111/2041-210x.13104}
+
+\leavevmode\vadjust pre{\hypertarget{ref-1Ch6LSHef}{}}%
+Wicherts, J.
+M., Bakker, M., \& Molenaar, D.
+(2011).
+Willingness to Share Research Data Is Related to the Strength of the Evidence and the Quality of Reporting of Statistical Results.
+\emph{PLoS ONE}, \emph{6}(11), e26828.
+\url{https://doi.org/10.1371/journal.pone.0026828}
+
+\leavevmode\vadjust pre{\hypertarget{ref-O6UbstGG}{}}%
+Wilson, G., Aruliah, D.
+A., Brown, C.
+T., Chue Hong, N.
+P., Davis, M., Guy, R.
+T., Haddock, S.
+H.
+D., Huff, K.
+D., Mitchell, I.
+M., Plumbley, M.
+D., Waugh, B., White, E.
+P., \& Wilson, P.
+(2014).
+Best Practices for Scientific Computing.
+\emph{PLoS Biology}, \emph{12}(1), e1001745.
+\url{https://doi.org/10.1371/journal.pbio.1001745}
+
+\leavevmode\vadjust pre{\hypertarget{ref-QqMezOMg}{}}%
+Xie, Y., Allaire, J. J., \& Grolemund, G. (2019). \emph{R Markdown: the definitive guide}. CRC Press, Taylor and Francis Group.
 
 \leavevmode\vadjust pre{\hypertarget{ref-1CJo8lo2v}{}}%
-\CSLLeftMargin{64. }
-\CSLRightInline{Yenni, G.
+Yenni, G.
+M., Christensen, E.
+M., Bledsoe, E.
+K., Supp, S.
+R., Diaz, R.
+M., White, E.
+P., \& Ernest, S.
+K.
 M.
-\emph{et al.} \href{https://doi.org/10.1371/journal.pbio.3000125}{Developing a modern data workflow for regularly updated data}.
-\emph{PLoS Biol} \textbf{17}, e3000125 (2019).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-RxK4CmfR}{}}%
-\CSLLeftMargin{65. }
-\CSLRightInline{Ernest, S. K. M. \emph{et al.} The Portal Project: a long-term study of a Chihuahuan desert ecosystem. (2018) doi:\href{https://doi.org/10.1101/332783}{10.1101/332783}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-kZzfmBNu}{}}%
-\CSLLeftMargin{66. }
-\CSLRightInline{Naujokaitis-Lewis, I., Endicott, S.
-\& Guezen, J.
+(2019).
+Developing a modern data workflow for regularly updated data.
+\emph{PLOS Biology}, \emph{17}(1), e3000125.
+\url{https://doi.org/10.1371/journal.pbio.3000125}
+
+\leavevmode\vadjust pre{\hypertarget{ref-lXvpQxeN}{}}%
+Yenni, G.
+M., Christensen, E.
+M., Bledsoe, E.
+K., Supp, S.
+R., Diaz, R.
+M., White, E.
+P., \& Ernest, S.
+K.
 M.
-\href{https://doi.org/10.1038/s41597-022-01381-8}{CAN-SAR: A database of Canadian species at risk information}.
-\emph{Sci Data} \textbf{9}, (2022).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-NUXbp429}{}}%
-\CSLLeftMargin{67. }
-\CSLRightInline{Features • GitHub Actions. \emph{GitHub} \url{https://github.com/features/actions}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-T03Api6e}{}}%
-\CSLLeftMargin{68. }
-\CSLRightInline{Continuous Integration and Delivery. \emph{CircleCI} \url{https://circleci.com/}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-YeFSbfFV}{}}%
-\CSLLeftMargin{69. }
-\CSLRightInline{Homepage \textbar{} Travis CI -- Start building today! \emph{Travis CI} \url{https://www.travis-ci.com/}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-UsTxAq4f}{}}%
-\CSLLeftMargin{70. }
-\CSLRightInline{Anbaroğlu, B. \href{https://doi.org/10.1111/tgis.12810}{A collaborative GIS programming course using GitHub Classroom}. \emph{Transactions in GIS} \textbf{25}, 3132--3158 (2021).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-lx49NGto}{}}%
-\CSLLeftMargin{71. }
-\CSLRightInline{Connect GitHub to a Project - OSF Support. \url{https://help.osf.io/article/211-connect-github-to-a-project}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-cW7vGddM}{}}%
-\CSLLeftMargin{72. }
-\CSLRightInline{Khelifa, R., Amano, T.
-\& Nuñez, M.
-A.
-\href{https://doi.org/10.1016/j.tree.2021.11.003}{A solution for breaking the language barrier}.
-\emph{Trends in Ecology \&amp; Evolution} \textbf{37}, 109--112 (2022).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-pjy75gHr}{}}%
-\CSLLeftMargin{73. }
-\CSLRightInline{Madicken Munk \emph{et al.} swcarpentry/git-novice: Software Carpentry: Version Control with Git, June 2019. at \url{https://doi.org/10.5281/zenodo.3264950} (2019).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-ZvrOcg9w}{}}%
-\CSLLeftMargin{74. }
-\CSLRightInline{Hester, J. B., the STAT 545 TAs, Jim. \emph{\href{https://happygitwithr.com/}{Let's Git started \textbar{} Happy Git and GitHub for the useR}}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-6CMMeSeD}{}}%
-\CSLLeftMargin{75. }
-\CSLRightInline{Bryan, J. \& TAs, T. S. 545. \emph{\href{https://stat545.com/}{STAT 545}}.}
+(2018).
+\emph{Developing a modern data workflow for evolving data}.
+Cold Spring Harbor Laboratory.
+\url{https://doi.org/10.1101/344804}
 

### 2022-10-26 manuscript.tex
Fixing hyperlinks [ci skip]
This build is based on
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/63bb253cf3ea3c8d75c1d2600670c1f130fe5f92.

This commit was created by the following CI build and job:
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/63bb253cf3ea3c8d75c1d2600670c1f130fe5f92/checks
https://github.com/SORTEE-Github-Hackathon/manuscript/actions/runs/3332123823

@@
 This manuscript
-(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/c5581246d860e031bbed754e4a7d18ff1ae072b2/}{permalink})
+(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/63bb253cf3ea3c8d75c1d2600670c1f130fe5f92/}{permalink})
 was automatically generated
-from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/c5581246d860e031bbed754e4a7d18ff1ae072b2}{SORTEE-Github-Hackathon/manuscript@c558124}
-on October 3, 2022.
+from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/63bb253cf3ea3c8d75c1d2600670c1f130fe5f92}{SORTEE-Github-Hackathon/manuscript@63bb253}
+on October 26, 2022.
 
@@
 
-With over 83 million registered users as of 2022, GitHub is the most widely-used web platform for collaborating on computer code (\protect\hyperlink{ref-nwCtHDCn}{\emph{Build Software Better, Together}, n.d.}).
+With over 83 million registered users as of 2022, GitHub \url{https://github.com} is the most widely-used web platform for collaborating on computer code (\protect\hyperlink{ref-nwCtHDCn}{\emph{Build Software Better, Together}, n.d.}).
 GitHub provides a simple but powerful web interface that allows users to participate in projects by contributing, modifying and discussing existing code, reporting bugs, discovering code and data, and publishing new code.
@@
 
-The expansive GitHub user-community and numerous GitHub resources have boosted its popularity (\protect\hyperlink{ref-RVetqmsg}{Bryan, 2018}; \protect\hyperlink{ref-u5aEVE4B}{\emph{Coding Club: A Positive Peer-Learning Community}, n.d.}; \protect\hyperlink{ref-13jOlVcpp}{Hester, n.d.-a}; \protect\hyperlink{ref-kEX5dgzK}{Perez-Riverol et al., 2016}).
+The expansive GitHub user-community and numerous GitHub resources have boosted its popularity {[}Perez-Riverol et al.
+(\protect\hyperlink{ref-kEX5dgzK}{2016}); Bryan (\protect\hyperlink{ref-RVetqmsg}{2018}); \url{https://happygitwithr.com}; \url{https://ourcodingclub.github.io}{]}.
 Nevertheless, although multiple articles have encouraged researchers in EEB to adopt GitHub as part of their research process (\protect\hyperlink{ref-3DKwn1sY}{Lowndes et al., 2017}; \protect\hyperlink{ref-10ghgV3S8}{J.
@@
 First-time users without formal training in information technology may face steep learning curves because GitHub and its features have been centered on collaboration for code development in information systems (\protect\hyperlink{ref-139b0pSGc}{Leibzon, 2016}).
-Moreover, domain-specific resources providing tractable examples and practical guidance for researchers in EEB on GitHub are scarce (but see \url{https://ourcodingclub.github.io}; \url{https://www.openscapes.org}, (\protect\hyperlink{ref-lJAgyhYq}{Kim et al., 2022})).
+Moreover, domain-specific resources providing tractable examples and practical guidance for researchers in EEB on GitHub are scarce {[}but see Kim et al.
+(\protect\hyperlink{ref-lJAgyhYq}{2022}); \url{https://ourcodingclub.github.io}; \url{https://www.openscapes.org}{]}.
 Widespread adoption of GitHub for collaborating on research tasks can ultimately enable EEB researchers to spend less time on creating novel processes for collaboration and more time on their research (\protect\hyperlink{ref-ydrk01SR}{Briney et al., 2020}).
@@
 6.
-\textbf{Consult online resources.} The Jenny Bryan Universe of GitHub material, for example, provides a thorough and accessible introduction for a multitude of research-related uses for GitHub, and includes a book (\protect\hyperlink{ref-ZvrOcg9w}{Hester, n.d.-b}), statistics course (\protect\hyperlink{ref-6CMMeSeD}{Bryan \& TAs, n.d.}) and academic article (\protect\hyperlink{ref-RVetqmsg}{Bryan, 2018}).
+\textbf{Consult online resources.} The Jenny Bryan Universe of GitHub material, for example, provides a thorough and accessible introduction for a multitude of research-related uses for GitHub, and includes a book (\protect\hyperlink{ref-ZvrOcg9w}{Hester, n.d.}), statistics course (\protect\hyperlink{ref-6CMMeSeD}{Bryan \& TAs, n.d.}) and academic article (\protect\hyperlink{ref-RVetqmsg}{Bryan, 2018}).
 \\
@@
 GitHub Docs.
-Retrieved October 3, 2022, from \url{https://ghdocs-prod.azurewebsites.net/en/repositories/managing-your-repositorys-settings-and-features/customizing-your-repository/about-code-owners}
+Retrieved October 26, 2022, from \url{https://ghdocs-prod.azurewebsites.net/en/repositories/managing-your-repositorys-settings-and-features/customizing-your-repository/about-code-owners}
 
@@
 GitHub Docs.
-Retrieved October 3, 2022, from \url{https://ghdocs-prod.azurewebsites.net/en/repositories/working-with-files/managing-large-files/about-large-files-on-github}
+Retrieved October 26, 2022, from \url{https://ghdocs-prod.azurewebsites.net/en/repositories/working-with-files/managing-large-files/about-large-files-on-github}
 
@@
 GitHub Docs.
-Retrieved October 3, 2022, from \url{https://ghdocs-prod.azurewebsites.net/en/issues/planning-and-tracking-with-projects/learning-about-projects/about-projects}
+Retrieved October 26, 2022, from \url{https://ghdocs-prod.azurewebsites.net/en/issues/planning-and-tracking-with-projects/learning-about-projects/about-projects}
 
@@
 GitHub Docs.
-Retrieved October 3, 2022, from \url{https://ghdocs-prod.azurewebsites.net/en/communities/setting-up-your-project-for-healthy-contributions/adding-a-license-to-a-repository}
+Retrieved October 26, 2022, from \url{https://ghdocs-prod.azurewebsites.net/en/communities/setting-up-your-project-for-healthy-contributions/adding-a-license-to-a-repository}
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-6CMMeSeD}{}}%
-Bryan, J., \& TAs, T. S. 545. (n.d.). \emph{STAT 545}. Retrieved October 3, 2022, from \url{https://stat545.com/}
+Bryan, J., \& TAs, T. S. 545. (n.d.). \emph{STAT 545}. Retrieved October 26, 2022, from \url{https://stat545.com/}
 
 \leavevmode\vadjust pre{\hypertarget{ref-nwCtHDCn}{}}%
-\emph{Build software better, together}. (n.d.). GitHub. Retrieved October 3, 2022, from \url{https://github.com}
+\emph{Build software better, together}. (n.d.). GitHub. Retrieved October 26, 2022, from \url{https://github.com}
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-u5aEVE4B}{}}%
-\emph{Coding Club: A Positive Peer-Learning Community}. (n.d.). Retrieved October 3, 2022, from \url{https://ourcodingclub.github.io/}
-
 \leavevmode\vadjust pre{\hypertarget{ref-lx49NGto}{}}%
-\emph{Connect GitHub to a Project - OSF Support}. (n.d.). Retrieved October 3, 2022, from \url{https://help.osf.io/article/211-connect-github-to-a-project}
+\emph{Connect GitHub to a Project - OSF Support}. (n.d.). Retrieved October 26, 2022, from \url{https://help.osf.io/article/211-connect-github-to-a-project}
 
 \leavevmode\vadjust pre{\hypertarget{ref-T03Api6e}{}}%
-\emph{Continuous Integration and Delivery}. (n.d.). CircleCI. Retrieved October 3, 2022, from \url{https://circleci.com/}
+\emph{Continuous Integration and Delivery}. (n.d.). CircleCI. Retrieved October 26, 2022, from \url{https://circleci.com/}
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-NUXbp429}{}}%
-\emph{Features • GitHub Actions}. (n.d.). GitHub. Retrieved October 3, 2022, from \url{https://github.com/features/actions}
+\emph{Features • GitHub Actions}. (n.d.). GitHub. Retrieved October 26, 2022, from \url{https://github.com/features/actions}
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-11GtZ7icJ}{}}%
-\emph{Git Large File Storage}. (n.d.). Git Large File Storage. Retrieved October 3, 2022, from \url{https://git-lfs.github.com/}
+\emph{Git Large File Storage}. (n.d.). Git Large File Storage. Retrieved October 26, 2022, from \url{https://git-lfs.github.com/}
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-ZvrOcg9w}{}}%
-Hester, J. B., the STAT 545 TAs, Jim. (n.d.-b). \emph{Let's Git started \textbar{} Happy Git and GitHub for the useR}. Retrieved October 3, 2022, from \url{https://happygitwithr.com/}
-
-\leavevmode\vadjust pre{\hypertarget{ref-13jOlVcpp}{}}%
-Hester, J. B., the STAT 545 TAs, Jim. (n.d.-a). \emph{Let's Git started \textbar{} Happy Git and GitHub for the useR}. Retrieved October 3, 2022, from \url{https://happygitwithr.com/}
+Hester, J. B., the STAT 545 TAs, Jim. (n.d.). \emph{Let's Git started \textbar{} Happy Git and GitHub for the useR}. Retrieved October 26, 2022, from \url{https://happygitwithr.com/}
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-YeFSbfFV}{}}%
-\emph{Homepage \textbar{} Travis CI -- Start building today!} (n.d.). Travis CI. Retrieved October 3, 2022, from \url{https://www.travis-ci.com/}
+\emph{Homepage \textbar{} Travis CI -- Start building today!} (n.d.). Travis CI. Retrieved October 26, 2022, from \url{https://www.travis-ci.com/}
 
@@
 Kim, A.
-Y., Herrmann, V., Bareto, R., Calkins, B., Gonzalez‐Akre, E., Johnson, D.
+Y., Herrmann, V., Barreto, R., Calkins, B., Gonzalez‐Akre, E., Johnson, D.
 J., Jordan, J.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Re6Eg2va}{}}%
-\emph{Manubot - Manuscripts, open and automated}. (n.d.). Retrieved October 3, 2022, from \url{https://manubot.org}
+\emph{Manubot - Manuscripts, open and automated}. (n.d.). Retrieved October 26, 2022, from \url{https://manubot.org}
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-MDQfMwCW}{}}%
-\emph{Quickstart for GitHub Pages}. (n.d.). GitHub Docs. Retrieved October 3, 2022, from \url{https://ghdocs-prod.azurewebsites.net/en/pages/quickstart}
+\emph{Quickstart for GitHub Pages}. (n.d.). GitHub Docs. Retrieved October 26, 2022, from \url{https://ghdocs-prod.azurewebsites.net/en/pages/quickstart}
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-1GRWGlDWy}{}}%
-Slack. (n.d.). \emph{GitHub for Slack}. Slack Help Center. Retrieved October 3, 2022, from \url{https://slack.com/help/articles/232289568-GitHub-for-Slack}
+Slack. (n.d.). \emph{GitHub for Slack}. Slack Help Center. Retrieved October 26, 2022, from \url{https://slack.com/help/articles/232289568-GitHub-for-Slack}
 

### 2022-10-26 manuscript.tex
Fixing citations [ci skip]
This build is based on
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/3096a8deace92d7df98c206c233bcf3f62c7e805.

This commit was created by the following CI build and job:
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/3096a8deace92d7df98c206c233bcf3f62c7e805/checks
https://github.com/SORTEE-Github-Hackathon/manuscript/actions/runs/3332157790

@@
 This manuscript
-(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/63bb253cf3ea3c8d75c1d2600670c1f130fe5f92/}{permalink})
+(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/3096a8deace92d7df98c206c233bcf3f62c7e805/}{permalink})
 was automatically generated
-from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/63bb253cf3ea3c8d75c1d2600670c1f130fe5f92}{SORTEE-Github-Hackathon/manuscript@63bb253}
+from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/3096a8deace92d7df98c206c233bcf3f62c7e805}{SORTEE-Github-Hackathon/manuscript@3096a8d}
 on October 26, 2022.
@@
 
-GitHub limits committed file sizes to 100 Mb (megabytes \emph{About Large Files on GitHub} (\protect\hyperlink{ref-1Co6ZZjF1}{n.d.})), which can make it challenging for centralizing research compendia containing larger file sizes.
-Users may still version large files using Git Large File Storage (\protect\hyperlink{ref-11GtZ7icJ}{\emph{Git Large File Storage}, n.d.}) text pointers, but may have to rely on external file storage alternatives (such as local or cloud-hosting).
+GitHub limits committed file sizes to 100 Mb (megabytes) (\protect\hyperlink{ref-1Co6ZZjF1}{\emph{About Large Files on GitHub}, n.d.}), which can make it challenging for centralizing research compendia containing larger file sizes.
+Users may still version large files using Git Large File Storage (\url{https://git-lfs.github.com}) text pointers, but may have to rely on external file storage alternatives (such as local or cloud-hosting).
 
@@
 For instance, one can create a discussion on a project repository to decide which method to apply for biodiversity data analysis.
-Then, an issue can be created to establish steps and responsibilities including data formatting, statistical analyses, figure generation, and issue resolution {[}\emph{e.g.}, see issues and discussions in the sPlotOpen {[}doi:10.1111/geb.13346{]} manuscript repository (\url{https://github.com/fmsabatini/sPlotOpen_Manuscript/issues?q=is\%3Aissue+is\%3Aclosed}){]}.
+Then, an issue can be created to establish steps and responsibilities including data formatting, statistical analyses, figure generation, and issue resolution (\emph{e.g.}, see issues and discussions in the sPlotOpen manuscript repository \protect\hyperlink{ref-doi:10.1111ux2fgeb.13346}{\textbf{doi:10.1111/geb.13346?}}); \emph{Issues · Fmsabatini/sPlotOpen\_Manuscript} (\protect\hyperlink{ref-3UAritXO}{n.d.})=is\%3Aissue+is\%3Aclosed{]}.
 Using GitHub for all project-related conversation and planning, rather than email or messaging tools, makes it easier to keep track of progress throughout the lifespan of a project.
@@
 Project management in GitHub can also be integrated with third-party applications, such as Zenhub (\url{https://www.zenhub.com}) or Slack (\url{https://slack.github.com}).
-Zenhub allows for the enhanced visualization and organization of repositories and their issues, while the GitHub for Slack integration allows notifications from GitHub events to be sent directly to users or group channels (\protect\hyperlink{ref-1GRWGlDWy}{Slack, n.d.}).
+Zenhub allows for the enhanced visualization and organization of repositories and their issues, while the GitHub for Slack integration allows notifications from GitHub events to be sent directly to users or group channels (see \protect\hyperlink{ref-1GRWGlDWy}{Slack, n.d.}).
 
@@
 Making presentations, syllabi and other course materials can be done through most major high-level programming languages such as R, with \texttt{RMarkdown} (\protect\hyperlink{ref-QqMezOMg}{Xie et al., 2019}), Python, with \texttt{python-ppt} (\url{https://python-pptx.readthedocs.io}), and Julia, with \texttt{Remark.jl} (\url{https://juliapackages.com/p/remark}), and be version-controlled and stored in GitHub.
-Once content is made, hosting a course website can be done through GitHub Pages (\protect\hyperlink{ref-MDQfMwCW}{\emph{Quickstart for GitHub Pages}, n.d.}) (\emph{e.g.}, \url{https://github.com/topics/course-website}).
+Once content is made, hosting a course website can be done through GitHub Pages (\url{https://pages.github.com}; \emph{e.g.}, \url{https://github.com/topics/course-website}).
 This way, course content can be available to enrolled students, as well as a global pool of learners and teachers interested in the material.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-11GtZ7icJ}{}}%
-\emph{Git Large File Storage}. (n.d.). Git Large File Storage. Retrieved October 26, 2022, from \url{https://git-lfs.github.com/}
-
 \leavevmode\vadjust pre{\hypertarget{ref-pq2Tv1BC}{}}%
@@
 Hudgins, E. (2022). \emph{emmajhudgins/UStreedamage: publication release} (accepted) {[}Computer software{]}. Zenodo. \url{https://doi.org/10.5281/zenodo.6097109}
+
+\leavevmode\vadjust pre{\hypertarget{ref-3UAritXO}{}}%
+\emph{Issues · fmsabatini/sPlotOpen\_Manuscript}. (n.d.). GitHub. Retrieved October 26, 2022, from \url{https://github.com/fmsabatini/sPlotOpen_Manuscript}
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-MDQfMwCW}{}}%
-\emph{Quickstart for GitHub Pages}. (n.d.). GitHub Docs. Retrieved October 26, 2022, from \url{https://ghdocs-prod.azurewebsites.net/en/pages/quickstart}
-
 \leavevmode\vadjust pre{\hypertarget{ref-4ny1onB0}{}}%

### 2022-10-26 manuscript.tex
Update 04.use-cases-b.md [ci skip]
This build is based on
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/e15161667619fdac1d5235514e3585de24f91b37.

This commit was created by the following CI build and job:
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/e15161667619fdac1d5235514e3585de24f91b37/checks
https://github.com/SORTEE-Github-Hackathon/manuscript/actions/runs/3332196213

@@
 This manuscript
-(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/3096a8deace92d7df98c206c233bcf3f62c7e805/}{permalink})
+(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/e15161667619fdac1d5235514e3585de24f91b37/}{permalink})
 was automatically generated
-from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/3096a8deace92d7df98c206c233bcf3f62c7e805}{SORTEE-Github-Hackathon/manuscript@3096a8d}
+from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/e15161667619fdac1d5235514e3585de24f91b37}{SORTEE-Github-Hackathon/manuscript@e151616}
 on October 26, 2022.
@@
 Linking GitHub repositories with a DOI helps research become findable, properly cited, and can ensure long-term stability (\protect\hyperlink{ref-iIEKCTLU}{Hampton et al., 2015}).
-This strategy has been increasingly adopted in numerous studies in ecology and evolution (\emph{e.g.}, Hudgins (\protect\hyperlink{ref-GQj3c17f}{2022}); EllenJCoombs (\protect\hyperlink{ref-bZNn2hbh}{2020}); Lrharper1 (\protect\hyperlink{ref-ZI1OqZNr}{2018})).
+This strategy has been increasingly adopted in numerous studies in ecology and evolution (\emph{e.g.}, the Zenodo repositores for Hudgins (\protect\hyperlink{ref-GQj3c17f}{2022}), EllenJCoombs (\protect\hyperlink{ref-bZNn2hbh}{2020}), and Lrharper1 (\protect\hyperlink{ref-ZI1OqZNr}{2018})).
 
@@
 Relevant literature or issues can be made using the Discussions and Issues features.
-Moreover, real-time collaboration on text documents stored in GitHub repositories can be achieved with the help of other platforms (\emph{e.g.}, HackMD (\url{https://hackmd.io}) for Markdown documents).
+Moreover, real-time collaboration on text documents stored in GitHub repositories can be achieved with the help of other platforms {[}\emph{e.g.}, HackMD (\url{https://hackmd.io}) for Markdown documents{]}.
 

### 2022-10-26 manuscript.tex
Updating citations [ci skip]
This build is based on
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/891e1faad1b05462ff855da04e5af9c7a676855d.

This commit was created by the following CI build and job:
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/891e1faad1b05462ff855da04e5af9c7a676855d/checks
https://github.com/SORTEE-Github-Hackathon/manuscript/actions/runs/3332227852

@@
 This manuscript
-(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/e15161667619fdac1d5235514e3585de24f91b37/}{permalink})
+(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/891e1faad1b05462ff855da04e5af9c7a676855d/}{permalink})
 was automatically generated
-from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/e15161667619fdac1d5235514e3585de24f91b37}{SORTEE-Github-Hackathon/manuscript@e151616}
+from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/891e1faad1b05462ff855da04e5af9c7a676855d}{SORTEE-Github-Hackathon/manuscript@891e1fa}
 on October 26, 2022.
@@
 GitHub can serve as a tool for open and tractable research development.
-Collaborators can directly interact with code and data, inspect for errors, and potentially identify scientific misconduct prior to manuscript submission (\emph{e.g.}, (\protect\hyperlink{ref-18PTmKJkq}{January 18 \& Pm, 2020})).
+Collaborators can directly interact with code and data, inspect for errors, and potentially identify scientific misconduct prior to manuscript submission (\emph{e.g.}, \url{https://ecologyforthemasses.com/2020/02/04/pruittdata-and-the-ethics-of-data-in-science}).
 Collaborators and readers are better positioned to discover erroneous or questionable findings if they have complete and transparent access to projects.
@@
 Through version control, the history of code and data from projects in ecology and evolution can be tracked accessible to future laboratory members and collaborators (\protect\hyperlink{ref-3DKwn1sY}{Lowndes et al., 2017}).
-Repositories and organizations can have designated data and code owners (or more appropriate, stewards; see (\protect\hyperlink{ref-iIEKCTLU}{Hampton et al., 2015}), (\protect\hyperlink{ref-s91uGRZ2}{\emph{About Code Owners}, n.d.})), who can also can change through time allowing for the transition of code between research cohorts.
+Repositories and organizations can have designated data and code owners {[}or more appropriate, stewards; see Hampton et al.
+(\protect\hyperlink{ref-iIEKCTLU}{2015}), \emph{About Code Owners} (\protect\hyperlink{ref-s91uGRZ2}{n.d.}){]}, who can also can change through time allowing for the transition of code between research cohorts.
 Other project collaborators can contribute to repository design and development, and their active involvement can both aid authors ability to act as guarantors of the project, and the clarity and reproducibility of the project for future users.
@@
 Automation has a strong potential to expand the scale and pace of research in ecology and evolution (\protect\hyperlink{ref-cfgXxgt1}{Keitt \& Abelson, 2021}).
-Automation frameworks can streamline many stages of the scientific process, including automated data collection and data validation (\emph{e.g.}, (\protect\hyperlink{ref-bhDgD6lF}{Micheletti et al., 2021}; \protect\hyperlink{ref-lXvpQxeN}{Yenni et al., 2018})), automated data analysis (\emph{e.g.}, (\protect\hyperlink{ref-Qh7xTLwz}{Beaulieu-Jones \& Greene, 2017})), automated archiving and deployment of data, code and reports (\emph{e.g.}, this manuscript, (\protect\hyperlink{ref-SirQKFIz}{White et al., 2018})).
+Automation frameworks can streamline many stages of the scientific process, including automated data collection and data validation (\emph{e.g.}, \protect\hyperlink{ref-bhDgD6lF}{Micheletti et al., 2021}; \protect\hyperlink{ref-lXvpQxeN}{Yenni et al., 2018}), automated data analysis (\emph{e.g.}, \protect\hyperlink{ref-Qh7xTLwz}{Beaulieu-Jones \& Greene, 2017}), automated archiving and deployment of data, code and reports (\emph{e.g.}, this manuscript, \protect\hyperlink{ref-SirQKFIz}{White et al., 2018}).
 In this context, small modifications to code and data can be frequently committed and automatically tested, as in continuous integration and continuous deployment practices (\protect\hyperlink{ref-1Ep9EJL6y}{Meyer, 2014}).
-This allows for early detection and correction of errors, potentially improving confidence in scientific development by minimizing software errors (see (\protect\hyperlink{ref-ufw0ZdnI}{Soergel, 2015})).
+This allows for early detection and correction of errors, potentially improving confidence in scientific development by minimizing software errors (see \protect\hyperlink{ref-ufw0ZdnI}{Soergel, 2015}).
 In addition to increasing scientific rigor and confidence in ecological software (\protect\hyperlink{ref-12103x16N}{Scheller et al., 2010}), automation can help advance more rapidly sharing ecological data and making sure the data are high quality (\protect\hyperlink{ref-rTbinQMj}{Dietze et al., 2018}).
@@
 
-Automation can be integrated into GitHub repositories through the GitHub Actions feature (\protect\hyperlink{ref-NUXbp429}{\emph{Features • GitHub Actions}, n.d.}), or through alternative automation systems (\emph{e.g.}, Circle CI(\protect\hyperlink{ref-T03Api6e}{\emph{Continuous Integration and Delivery}, n.d.}), Travis CI(\protect\hyperlink{ref-YeFSbfFV}{\emph{Homepage \textbar{} Travis CI -- Start Building Today!}, n.d.})).
+Automation can be integrated into GitHub repositories through the GitHub Actions feature (\protect\hyperlink{ref-NUXbp429}{\emph{Features • GitHub Actions}, n.d.}), or through alternative automation systems (\emph{e.g.}, Circle CI, \protect\hyperlink{ref-T03Api6e}{\emph{Continuous Integration and Delivery}, n.d.}); Travis CI, \emph{Homepage \textbar{} Travis CI -- Start Building Today!} (\protect\hyperlink{ref-YeFSbfFV}{n.d.}){]}.
 Users can set up workflows associated with their repositories that are triggered by events (\emph{e.g.}, push, pull request or at specified times) for remote servers to perform user-specified steps and actions.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-18PTmKJkq}{}}%
-January 18, P.
-L.
-B.
-K., \& Pm, 2022.
-2:51.
-(2020, February 4).
-\#PruittData and the Ethics of Data in Science.
-\emph{Ecology for the Masses}.
-\url{https://ecologyforthemasses.com/2020/02/04/pruittdata-and-the-ethics-of-data-in-science/}
-
 \leavevmode\vadjust pre{\hypertarget{ref-wwHxTOtm}{}}%

### 2022-10-26 manuscript.tex
Adding parenthesis to a link [ci skip]
This build is based on
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/3f5fcbe49678055053a9a9df3dabe7aed164fdd3.

This commit was created by the following CI build and job:
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/3f5fcbe49678055053a9a9df3dabe7aed164fdd3/checks
https://github.com/SORTEE-Github-Hackathon/manuscript/actions/runs/3332243977

@@
 This manuscript
-(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/891e1faad1b05462ff855da04e5af9c7a676855d/}{permalink})
+(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/3f5fcbe49678055053a9a9df3dabe7aed164fdd3/}{permalink})
 was automatically generated
-from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/891e1faad1b05462ff855da04e5af9c7a676855d}{SORTEE-Github-Hackathon/manuscript@891e1fa}
+from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/3f5fcbe49678055053a9a9df3dabe7aed164fdd3}{SORTEE-Github-Hackathon/manuscript@3f5fcbe}
 on October 26, 2022.
@@
 
-With over 83 million registered users as of 2022, GitHub \url{https://github.com} is the most widely-used web platform for collaborating on computer code (\protect\hyperlink{ref-nwCtHDCn}{\emph{Build Software Better, Together}, n.d.}).
+With over 83 million registered users as of 2022, GitHub (\url{https://github.com}) is the most widely-used web platform for collaborating on computer code (\protect\hyperlink{ref-nwCtHDCn}{\emph{Build Software Better, Together}, n.d.}).
 GitHub provides a simple but powerful web interface that allows users to participate in projects by contributing, modifying and discussing existing code, reporting bugs, discovering code and data, and publishing new code.

### 2022-10-26 manuscript.tex
Update 05.use-cases-c.md [ci skip]
This build is based on
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/d9023c5954b959cbeee18d64728f6cc4f4caff03.

This commit was created by the following CI build and job:
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/d9023c5954b959cbeee18d64728f6cc4f4caff03/checks
https://github.com/SORTEE-Github-Hackathon/manuscript/actions/runs/3332253874

@@
 This manuscript
-(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/3f5fcbe49678055053a9a9df3dabe7aed164fdd3/}{permalink})
+(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/d9023c5954b959cbeee18d64728f6cc4f4caff03/}{permalink})
 was automatically generated
-from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/3f5fcbe49678055053a9a9df3dabe7aed164fdd3}{SORTEE-Github-Hackathon/manuscript@3f5fcbe}
+from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/d9023c5954b959cbeee18d64728f6cc4f4caff03}{SORTEE-Github-Hackathon/manuscript@d9023c5}
 on October 26, 2022.
@@
 In this way, teams have full ownership of repositories within an organization, while ensuring that these materials stay accessible to the laboratory after people have moved on or when locally-stored data are lost.
-This application extends to research centres, which may include several distinct projects that remain linked to institutions (\emph{e.g.}, the German Centre for Integrative Biodiversity Research (iDiv, \url{https://github.com/idiv-biodiversity})).
+This application extends to research centres, which may include several distinct projects that remain linked to institutions {[}\emph{e.g.}, the German Centre for Integrative Biodiversity Research (iDiv, \url{https://github.com/idiv-biodiversity}){]}.
 The team organizing the hackathon which inspired this article used a GitHub Organization (SORTEE-Github-Hackathon, \url{https://github.com/SORTEE-Github-Hackathon}) to centralize the project development, from meeting notes to, ultimately, this manuscript.

### 2022-10-26 manuscript.tex
Update cover-letter-submission.Rmd [ci skip]
This build is based on
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/82d8f8423ae39d95f7eb1d44a90ac5b2055f6267.

This commit was created by the following CI build and job:
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/82d8f8423ae39d95f7eb1d44a90ac5b2055f6267/checks
https://github.com/SORTEE-Github-Hackathon/manuscript/actions/runs/3332319562

@@
 This manuscript
-(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/d9023c5954b959cbeee18d64728f6cc4f4caff03/}{permalink})
+(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/82d8f8423ae39d95f7eb1d44a90ac5b2055f6267/}{permalink})
 was automatically generated
-from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/d9023c5954b959cbeee18d64728f6cc4f4caff03}{SORTEE-Github-Hackathon/manuscript@d9023c5}
+from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/82d8f8423ae39d95f7eb1d44a90ac5b2055f6267}{SORTEE-Github-Hackathon/manuscript@82d8f84}
 on October 26, 2022.

### 2022-10-26 manuscript.tex
Update 03.use-cases-a.md [ci skip]
This build is based on
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/9d912d5cc44030361976bccfd3cc8c304075ed06.

This commit was created by the following CI build and job:
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/9d912d5cc44030361976bccfd3cc8c304075ed06/checks
https://github.com/SORTEE-Github-Hackathon/manuscript/actions/runs/3332378207

@@
 This manuscript
-(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/82d8f8423ae39d95f7eb1d44a90ac5b2055f6267/}{permalink})
+(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/9d912d5cc44030361976bccfd3cc8c304075ed06/}{permalink})
 was automatically generated
-from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/82d8f8423ae39d95f7eb1d44a90ac5b2055f6267}{SORTEE-Github-Hackathon/manuscript@82d8f84}
+from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/9d912d5cc44030361976bccfd3cc8c304075ed06}{SORTEE-Github-Hackathon/manuscript@9d912d5}
 on October 26, 2022.
@@
 For instance, one can create a discussion on a project repository to decide which method to apply for biodiversity data analysis.
-Then, an issue can be created to establish steps and responsibilities including data formatting, statistical analyses, figure generation, and issue resolution (\emph{e.g.}, see issues and discussions in the sPlotOpen manuscript repository \protect\hyperlink{ref-doi:10.1111ux2fgeb.13346}{\textbf{doi:10.1111/geb.13346?}}); \emph{Issues · Fmsabatini/sPlotOpen\_Manuscript} (\protect\hyperlink{ref-3UAritXO}{n.d.})=is\%3Aissue+is\%3Aclosed{]}.
+Then, an issue can be created to establish steps and responsibilities including data formatting, statistical analyses, figure generation, and issue resolution (\emph{e.g.}, see issues and discussions in the sPlotOpen manuscript repository, \protect\hyperlink{ref-doi:10.1111ux2fgeb.13346}{\textbf{doi:10.1111/geb.13346?}}); \emph{Issues · Fmsabatini/sPlotOpen\_Manuscript} (\protect\hyperlink{ref-3UAritXO}{n.d.})=is\%3Aissue+is\%3Aclosed{]}.
 Using GitHub for all project-related conversation and planning, rather than email or messaging tools, makes it easier to keep track of progress throughout the lifespan of a project.

### 2022-10-27 manuscript.tex
Merge pull request #276 from SORTEE-Github-Hackathon/dylangomes-patch-1 [ci skip]
This build is based on
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/52a70b5c9cc16becb6a12e911a4d0a5793bdea18.

This commit was created by the following CI build and job:
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/52a70b5c9cc16becb6a12e911a4d0a5793bdea18/checks
https://github.com/SORTEE-Github-Hackathon/manuscript/actions/runs/3336631558

@@
 This manuscript
-(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/9d912d5cc44030361976bccfd3cc8c304075ed06/}{permalink})
+(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/52a70b5c9cc16becb6a12e911a4d0a5793bdea18/}{permalink})
 was automatically generated
-from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/9d912d5cc44030361976bccfd3cc8c304075ed06}{SORTEE-Github-Hackathon/manuscript@9d912d5}
-on October 26, 2022.
+from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/52a70b5c9cc16becb6a12e911a4d0a5793bdea18}{SORTEE-Github-Hackathon/manuscript@52a70b5}
+on October 27, 2022.
 
@@
   \href{https://github.com/dylangomes}{dylangomes}
-  (Current) National Academy of Sciences NRC Research Associateship Program, Northwest Fisheries Science Center, National Marine Fisheries Service, National Oceanic and Atmospheric Administration, Seattle, WA, USA 98112; (Former) Cooperative Institute for Marine Resources Studies, Hatfield Marine Science Center, Oregon State University, Newport, OR, United States
+  (Current) National Academy of Sciences NRC Research Associateship Program, Northwest Fisheries Science Center, National Marine Fisheries Service, National Oceanic and Atmospheric Administration, Seattle, WA, USA 98112; (Former) Cooperative Institute for Marine Resources Studies, Hatfield Marine Science Center, Oregon State University, Newport, OR, USA 97365
 \item
@@
 GitHub Docs.
-Retrieved October 26, 2022, from \url{https://ghdocs-prod.azurewebsites.net/en/repositories/managing-your-repositorys-settings-and-features/customizing-your-repository/about-code-owners}
+Retrieved October 27, 2022, from \url{https://ghdocs-prod.azurewebsites.net/en/repositories/managing-your-repositorys-settings-and-features/customizing-your-repository/about-code-owners}
 
@@
 GitHub Docs.
-Retrieved October 26, 2022, from \url{https://ghdocs-prod.azurewebsites.net/en/repositories/working-with-files/managing-large-files/about-large-files-on-github}
+Retrieved October 27, 2022, from \url{https://ghdocs-prod.azurewebsites.net/en/repositories/working-with-files/managing-large-files/about-large-files-on-github}
 
@@
 GitHub Docs.
-Retrieved October 26, 2022, from \url{https://ghdocs-prod.azurewebsites.net/en/issues/planning-and-tracking-with-projects/learning-about-projects/about-projects}
+Retrieved October 27, 2022, from \url{https://ghdocs-prod.azurewebsites.net/en/issues/planning-and-tracking-with-projects/learning-about-projects/about-projects}
 
@@
 GitHub Docs.
-Retrieved October 26, 2022, from \url{https://ghdocs-prod.azurewebsites.net/en/communities/setting-up-your-project-for-healthy-contributions/adding-a-license-to-a-repository}
+Retrieved October 27, 2022, from \url{https://ghdocs-prod.azurewebsites.net/en/communities/setting-up-your-project-for-healthy-contributions/adding-a-license-to-a-repository}
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-6CMMeSeD}{}}%
-Bryan, J., \& TAs, T. S. 545. (n.d.). \emph{STAT 545}. Retrieved October 26, 2022, from \url{https://stat545.com/}
+Bryan, J., \& TAs, T. S. 545. (n.d.). \emph{STAT 545}. Retrieved October 27, 2022, from \url{https://stat545.com/}
 
 \leavevmode\vadjust pre{\hypertarget{ref-nwCtHDCn}{}}%
-\emph{Build software better, together}. (n.d.). GitHub. Retrieved October 26, 2022, from \url{https://github.com}
+\emph{Build software better, together}. (n.d.). GitHub. Retrieved October 27, 2022, from \url{https://github.com}
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-lx49NGto}{}}%
-\emph{Connect GitHub to a Project - OSF Support}. (n.d.). Retrieved October 26, 2022, from \url{https://help.osf.io/article/211-connect-github-to-a-project}
+\emph{Connect GitHub to a Project - OSF Support}. (n.d.). Retrieved October 27, 2022, from \url{https://help.osf.io/article/211-connect-github-to-a-project}
 
 \leavevmode\vadjust pre{\hypertarget{ref-T03Api6e}{}}%
-\emph{Continuous Integration and Delivery}. (n.d.). CircleCI. Retrieved October 26, 2022, from \url{https://circleci.com/}
+\emph{Continuous Integration and Delivery}. (n.d.). CircleCI. Retrieved October 27, 2022, from \url{https://circleci.com/}
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-NUXbp429}{}}%
-\emph{Features • GitHub Actions}. (n.d.). GitHub. Retrieved October 26, 2022, from \url{https://github.com/features/actions}
+\emph{Features • GitHub Actions}. (n.d.). GitHub. Retrieved October 27, 2022, from \url{https://github.com/features/actions}
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-ZvrOcg9w}{}}%
-Hester, J. B., the STAT 545 TAs, Jim. (n.d.). \emph{Let's Git started \textbar{} Happy Git and GitHub for the useR}. Retrieved October 26, 2022, from \url{https://happygitwithr.com/}
+Hester, J. B., the STAT 545 TAs, Jim. (n.d.). \emph{Let's Git started \textbar{} Happy Git and GitHub for the useR}. Retrieved October 27, 2022, from \url{https://happygitwithr.com/}
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-YeFSbfFV}{}}%
-\emph{Homepage \textbar{} Travis CI -- Start building today!} (n.d.). Travis CI. Retrieved October 26, 2022, from \url{https://www.travis-ci.com/}
+\emph{Homepage \textbar{} Travis CI -- Start building today!} (n.d.). Travis CI. Retrieved October 27, 2022, from \url{https://www.travis-ci.com/}
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-3UAritXO}{}}%
-\emph{Issues · fmsabatini/sPlotOpen\_Manuscript}. (n.d.). GitHub. Retrieved October 26, 2022, from \url{https://github.com/fmsabatini/sPlotOpen_Manuscript}
+\emph{Issues · fmsabatini/sPlotOpen\_Manuscript}. (n.d.). GitHub. Retrieved October 27, 2022, from \url{https://github.com/fmsabatini/sPlotOpen_Manuscript}
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Re6Eg2va}{}}%
-\emph{Manubot - Manuscripts, open and automated}. (n.d.). Retrieved October 26, 2022, from \url{https://manubot.org}
+\emph{Manubot - Manuscripts, open and automated}. (n.d.). Retrieved October 27, 2022, from \url{https://manubot.org}
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-1GRWGlDWy}{}}%
-Slack. (n.d.). \emph{GitHub for Slack}. Slack Help Center. Retrieved October 26, 2022, from \url{https://slack.com/help/articles/232289568-GitHub-for-Slack}
+Slack. (n.d.). \emph{GitHub for Slack}. Slack Help Center. Retrieved October 27, 2022, from \url{https://slack.com/help/articles/232289568-GitHub-for-Slack}
 

### 2022-10-27 editorial-communication/cover-letter-submission.Rmd
updates with preprint link
Deploying to gh-pages from @ SORTEE-Github-Hackathon/manuscript@52a70b5c9cc16becb6a12e911a4d0a5793bdea18 🚀

--- 2022-06-23 editorial-communication/cover-letter-submission.Rmd
@@
 
-We would like to submit our manuscript entitled “Not just for programmers: How GitHub can accelerate collaborative and reproducible research in ecology and evolution” for consideration to be published in *Nature Ecology & Evolution*.
-Our study provides researchers with a critical review of twelve practical ways they can use Github -- an online, cloud-based service for cooperative and documented code development -- to make their research more collaborative, transparent, and reproducible.
+We would like to submit our manuscript entitled “Not just for programmers: How GitHub can accelerate collaborative and reproducible research in ecology and evolution” for consideration to be published in *Methods in Ecology and Evolution*.
+Our study provides researchers with a critical review of thirteen practical ways they can use GitHub – an online, cloud-based service for cooperative and documented code development – to make their research more collaborative, transparent, and reproducible.
 
@@
 We build upon our own experiences (as an international collaboration from authors across many ecology and evolution subdisciplines) and on existing resources mainly targeted at other disciplines, to highlight how researchers can use the readily available GitHub suite to make their research practices reproducible, collaborative, and transparent.
-Our manuscript is important for the *Nature Ecology & Evolution* readership because researchers in ecology and evolutionary biology can greatly benefit from our guide to migrate and incorporate GitHub workflows in their research practices ultimately towards an open and collaborative science.
-Also, we believe our manuscript complements a recently published manuscript in *Nature Ecology and Evolution*.
-In the manuscript, Gallagher et al.
-(2020) outline how the ongoing adoption of Open Science practices is transforming research in ecology and evolutionary biology.
-A key component of Open Science is the ability to collaboratively contribute to and share code and data--platforms like GitHub provide an free and accessible platform to do just that.
+Our manuscript is important for the *Methods in Ecology and Evolution* readership because researchers in ecology and evolutionary biology can greatly benefit from our perspectives to migrate and incorporate GitHub workflows in their research practices ultimately towards an open and collaborative science.
+Our manuscript also complements recently published literature outlining how the ongoing adoption of Open Science practices is transforming research in ecology and evolutionary biology.
 
-The enclosed manuscript is available as a preprint on the NAME OF SERVER AND CITATION, but is not published or in review elsewhere.
-All authors have contributed and reviewed the current version of the manuscript and agreed to its submission to *Nature Ecology & Evolution*.
+The enclosed manuscript is available as a preprint on the MetaArXiv server (https://www.doi.org/10.31222/osf.io/x3p2q), with over 440 downloads and 2,400 views in four months. 
+We declare that our study is not published or under consideration for publication elsewhere.
+
+All authors have contributed and reviewed the current version of the manuscript and agreed to its submission to Methods in Ecology and Evolution.
 
@@
 
-Rob Crystal-Ornelas PhD, on behalf of all co-authors
+Pedro Henrique Pereira Braga, on behalf of all co-authors
 

### 2022-11-17 editorial-communication/response-to-the-reviewers.Rmd
Create response-to-the-reviewers.Rmd

---
title: "Response to the reviewers"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Dear Mr Pedro Henrique Braga,

Thank you for submitting your manuscript to Methods in Ecology and Evolution. I have now received the reviewers' reports, copies of which are included below. This manuscript has the potential to make a valuable contribution to the area, but there are a number of significant concerns that need to be addressed. I have considered your paper in light of the comments received and I would like to invite you to prepare a major revision.

In addition to addressing the comments from the reviewers, I note the following.

As a long-term but sporadic GitHub user myself, I agree with most of the points and cases presented in the paper.

**E1.1.** I agree with Reviewer 1 that these could be streamlined somewhat into a smaller number of more generalizable cases. They also are a bit heavily weighted towards more experienced users. "Simple" operations like push, pull, and commit are rarely understandable to new users, who routinely forget to commit their actions. The GitHub Desktop app makes many of the operations and use of GitHub somewhat easier, and is a good entree into GitHub and Git for novices. More could be made of the desktop app.

**E1.2.** In my own experience, the "public" nature of repos is a major barrier to the use of GitHub for exactly the reason you suggest - EEB practioners remain very uncomfortable with sharing data pre-publication (and often even post-publication). Some additional emphasis on the ability to make repos "private" should be included beyond the Boxes.

**E1.3.** Another reason that many EEBers don't use GitHub appears to be related to how we develop code for projects. Unless we are developing packages that others are likely to use, we tend to develop one-off scripts or functions that, once they work and are run, are never returned to. Version control is not used widely, or even needed in these cases (and my own work in software engineering provenance software has similarly had little uptake for the same reasons). I recognize that this makes it difficult to document the processes involved, but if the goal is simply to analyze the data at hand and push out another paper, why deal with the overhead of version control? At root, this is a sociological phenomenon, not a scientific one. Within your ms., consider saying something about how even one-off scripts may need to be documented, archived, and assigned a DOI to conform to evolving archiving requirements of journals.

**E1.4.** I am surprised you didn't include integration between GitHub and Overleaf. Overleaf is also a good collaborative latex-based text processor, and provides syncing with GitHub (and Dropbox) in a way that will be more familiar to beginning users. (Actually, I eventually found it buried in Table 1)

**E1.5.** Finally, DropBox, SharePoint, and OneDrive are file-sharing systems that include version control, are widely supported, especially in colleges and universities, and are much easier to use for those who might be uncomfortable learning a system such as GitHub. Other than the ability to clone and fork, why should one choose GitHub over, for example, DropBox or SharePoint? More should be made of this in text, as opposed to burying it in Table 1, which is referenced only once in text (line 232) and only in the context of other longterm archives (line 231). Indeed, I suggest a somewhat expanded section of the ms. dedicated to a detailed exploration of the comparisons made in this Table. Otherwise, the ms. comes across as more proselytizing and less analytical/convincing.

Reviewer(s)' Comments to Author: Reviewer: 1

Comments to the Corresponding Author

This paper clearly communicates the enthusiasm of the authors for integrating GitHub in the EEB research process. Advantages in areas of collaboration, transparent and reproducible science are clear and nicely discussed. This is a well written paper.

**R1.1.** I would, however, recommend some restructuring and shortening. As it stands, this paper is too long and some of the use cases are too nerdy to spark enthusiasm in somebody who is not already using GitHub. Breaking it into 13 use cases leads to some repetition and those use cases may be combined more effectively for convincing a new user.

**R1.2.** The title and abstract gave me the impression that the goal is to convince EEB researcher to start using GitHub. If that's the case, it might be better to tailor the use cases to that entry level and use less GitHub specific lingo. Advanced usage may be mentioned but not detailed as much as it is currently done. E.g. collaboratively writing a paper in GitHub is probably out of the question for most. Most GitHub options for communication, discussion, issue tracking are still somewhat esoteric for most non-programmers.

**R1.3.** Although the abstract states 'We outline features ranging from low to high technical difficulty' the paper reads a bit like a laundry list of what GitHub can do (in fact, the word 'can' is used about 140 times, which makes for tedious read). Figure 2 helps sort through this laundry list and defines the technical difficulty. It might be better to clearly lay out where anybody can start using GitHub effectively in the text. And the emphasis is on 'effectively'. Most people are not likely to learn a new piece of software if it does not promise to reduce effort and time. So, defining tasks where GitHub shines in terms of return on investment maybe the better approach to convincing new users and then only mention the advance use cases with some pointers to further reading, but not going into too much detail.

**R1.4.** In my experience, the project continuity is actually very high on the importance list for researchers, i.e., knowing that the code and data will be findable by the next student. This includes the discussion of organizing and managing teams, keeping lab information in one place etc. Followed by code versioning and the ability to go back to older versions. Interest in website development is picking up because it really is simple to do in GitHub, and the information can be maintained by several people (i.e., a lab group).

Detailed comments:

**R1.5.** Line 346 delete second 'can': who can also can change through time

**R1.6.** Line 389 it should be 'each other's work': contribute to each other work without necessarily

**R1.7.** Line 457 missing 'collaborator'? especially when many may be

**R1.8.** Line 477: not sure what this sentence is saying: 'requiring the complementation of other tools to fully integration project files and GitHub repositories'

Reviewer: 2

Comments to the Corresponding Author

The manuscript presents how ecologists and evolutionary biologists (EEB) can use collaborative software development project management tools. The authors present a high-level view of Github and the Git version control system that is at its core. As the authors detail, the tools that Github provides has broad potential to be leveraged within the EEB community. The paper is well written and helps to make Github tools and related concepts legible to EEB audiences. On the whole, I see this as potentially being an impactful paper for improving EEB research. I have the following Major and Minor comments for the authors:

Major Comments

**R2.1.** Figure 1 was more confusing to me than helpful. It presents a view of a Github interface in order to detail generalized features; however, it is edited/abstracted so much that it doesn't map easily to the interface as it would be viewed by a reader of the paper. To improve this I would reduce the level of abstraction of the web interface.

**R2.2.** Figure 2 was useful, especially as it summarized across multiple areas that a reader make in-roads into using Github. Please clarify how the "Technical Difficulty" was assessed. Was this based on the impression of the working group? Was it quantified using different types of required knowledge (e.g., programming, software design, working in the Terminal, etc.)?

**R2.3.** I would find it helpful to give a brief (1-2 sentence) history of Git (L85-89). Namely, that it was developed as an aid for software development within distributed groups of software engineers and was developed within an open-source framework so that it could be improved by the community. This provides more context as to why Github (as it extends Git) is a useful tool for collaboration "by design".

**R2.4.** I suggest adding a discussion on dependency testing within or following the paragraph on Automation (Lines 373-382). This is a project "ecosystem" phenomenon that comes from collaboration, where you build your project on the work of someone else. As projects change over time, they can alter other projects. Software engineers have been working on this challenge for a long time in distributed teams where different parts of software are being built by different programmers. Checks can be done automatically within the software engineering framework (see Pasquier et al. 2017 <https://www.nature.com/articles/sdata2017114>). Beyond detection, any major changes can be detected and presented without additional work from the user via features like badges (<https://shields.io/>) within the project page (e.g., README).

**R2.5.** Related to Major Comments 1 and 4, given that the focus of the paper is toward integration into EEB scientific research workflows, I suggest adding another figure (or replacing Figure 1) that details a generalized scientific research workflow (e.g., Munafò et al. 2017 <https://www.nature.com/articles/s41562-016-0021>) and how Github supports/augments that workflow. This could relate to or build on Table 2, which a useful summarization of important features as they relate to different research participants.

Minor Comments

**R2.6.** The sentence from Line 66-67 is missing a close parenthesis.

**R2.7.** There appears to be a "fourth" barrier at Line 478. I suggest splitting the paragraph from Line 472 to 483 into two paragraphs and expanding on both "reluctance to share data" and "language-specific resources" as barriers to adoption.

**R2.8.** Line 570 "could also be e" should be "could also be a".

### 2022-11-17 manuscript.tex
Adding render response to the reviewers to action [ci skip]
This build is based on
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/e1d16866f2990cbb44fa4baf16633ca0e6a67556.

This commit was created by the following CI build and job:
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/e1d16866f2990cbb44fa4baf16633ca0e6a67556/checks
https://github.com/SORTEE-Github-Hackathon/manuscript/actions/runs/3490510374

@@
 This manuscript
-(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/52a70b5c9cc16becb6a12e911a4d0a5793bdea18/}{permalink})
+(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/e1d16866f2990cbb44fa4baf16633ca0e6a67556/}{permalink})
 was automatically generated
-from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/52a70b5c9cc16becb6a12e911a4d0a5793bdea18}{SORTEE-Github-Hackathon/manuscript@52a70b5}
-on October 27, 2022.
+from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/e1d16866f2990cbb44fa4baf16633ca0e6a67556}{SORTEE-Github-Hackathon/manuscript@e1d1686}
+on November 17, 2022.
 
@@
 GitHub Docs.
-Retrieved October 27, 2022, from \url{https://ghdocs-prod.azurewebsites.net/en/repositories/managing-your-repositorys-settings-and-features/customizing-your-repository/about-code-owners}
+Retrieved November 17, 2022, from \url{https://ghdocs-prod.azurewebsites.net/en/repositories/managing-your-repositorys-settings-and-features/customizing-your-repository/about-code-owners}
 
@@
 GitHub Docs.
-Retrieved October 27, 2022, from \url{https://ghdocs-prod.azurewebsites.net/en/repositories/working-with-files/managing-large-files/about-large-files-on-github}
+Retrieved November 17, 2022, from \url{https://ghdocs-prod.azurewebsites.net/en/repositories/working-with-files/managing-large-files/about-large-files-on-github}
 
@@
 GitHub Docs.
-Retrieved October 27, 2022, from \url{https://ghdocs-prod.azurewebsites.net/en/issues/planning-and-tracking-with-projects/learning-about-projects/about-projects}
+Retrieved November 17, 2022, from \url{https://ghdocs-prod.azurewebsites.net/en/issues/planning-and-tracking-with-projects/learning-about-projects/about-projects}
 
@@
 GitHub Docs.
-Retrieved October 27, 2022, from \url{https://ghdocs-prod.azurewebsites.net/en/communities/setting-up-your-project-for-healthy-contributions/adding-a-license-to-a-repository}
+Retrieved November 17, 2022, from \url{https://ghdocs-prod.azurewebsites.net/en/communities/setting-up-your-project-for-healthy-contributions/adding-a-license-to-a-repository}
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-6CMMeSeD}{}}%
-Bryan, J., \& TAs, T. S. 545. (n.d.). \emph{STAT 545}. Retrieved October 27, 2022, from \url{https://stat545.com/}
+Bryan, J., \& TAs, T. S. 545. (n.d.). \emph{STAT 545}. Retrieved November 17, 2022, from \url{https://stat545.com/}
 
 \leavevmode\vadjust pre{\hypertarget{ref-nwCtHDCn}{}}%
-\emph{Build software better, together}. (n.d.). GitHub. Retrieved October 27, 2022, from \url{https://github.com}
+\emph{Build software better, together}. (n.d.). GitHub. Retrieved November 17, 2022, from \url{https://github.com}
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-lx49NGto}{}}%
-\emph{Connect GitHub to a Project - OSF Support}. (n.d.). Retrieved October 27, 2022, from \url{https://help.osf.io/article/211-connect-github-to-a-project}
+\emph{Connect GitHub to a Project - OSF Support}. (n.d.). Retrieved November 17, 2022, from \url{https://help.osf.io/article/211-connect-github-to-a-project}
 
 \leavevmode\vadjust pre{\hypertarget{ref-T03Api6e}{}}%
-\emph{Continuous Integration and Delivery}. (n.d.). CircleCI. Retrieved October 27, 2022, from \url{https://circleci.com/}
+\emph{Continuous Integration and Delivery}. (n.d.). CircleCI. Retrieved November 17, 2022, from \url{https://circleci.com/}
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-NUXbp429}{}}%
-\emph{Features • GitHub Actions}. (n.d.). GitHub. Retrieved October 27, 2022, from \url{https://github.com/features/actions}
+\emph{Features • GitHub Actions}. (n.d.). GitHub. Retrieved November 17, 2022, from \url{https://github.com/features/actions}
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-ZvrOcg9w}{}}%
-Hester, J. B., the STAT 545 TAs, Jim. (n.d.). \emph{Let's Git started \textbar{} Happy Git and GitHub for the useR}. Retrieved October 27, 2022, from \url{https://happygitwithr.com/}
+Hester, J. B., the STAT 545 TAs, Jim. (n.d.). \emph{Let's Git started \textbar{} Happy Git and GitHub for the useR}. Retrieved November 17, 2022, from \url{https://happygitwithr.com/}
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-YeFSbfFV}{}}%
-\emph{Homepage \textbar{} Travis CI -- Start building today!} (n.d.). Travis CI. Retrieved October 27, 2022, from \url{https://www.travis-ci.com/}
+\emph{Homepage \textbar{} Travis CI -- Start building today!} (n.d.). Travis CI. Retrieved November 17, 2022, from \url{https://www.travis-ci.com/}
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-3UAritXO}{}}%
-\emph{Issues · fmsabatini/sPlotOpen\_Manuscript}. (n.d.). GitHub. Retrieved October 27, 2022, from \url{https://github.com/fmsabatini/sPlotOpen_Manuscript}
+\emph{Issues · fmsabatini/sPlotOpen\_Manuscript}. (n.d.). GitHub. Retrieved November 17, 2022, from \url{https://github.com/fmsabatini/sPlotOpen_Manuscript}
 
@@
 Implementing GitHub Actions continuous integration to reduce error rates in ecological data collection.
-\emph{Methods in Ecology and Evolution}.
+\emph{Methods in Ecology and Evolution}, \emph{13}(11), 2572--2585.
 \url{https://doi.org/10.1111/2041-210x.13982}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Re6Eg2va}{}}%
-\emph{Manubot - Manuscripts, open and automated}. (n.d.). Retrieved October 27, 2022, from \url{https://manubot.org}
+\emph{Manubot - Manuscripts, open and automated}. (n.d.). Retrieved November 17, 2022, from \url{https://manubot.org}
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-1GRWGlDWy}{}}%
-Slack. (n.d.). \emph{GitHub for Slack}. Slack Help Center. Retrieved October 27, 2022, from \url{https://slack.com/help/articles/232289568-GitHub-for-Slack}
+Slack. (n.d.). \emph{GitHub for Slack}. Slack Help Center. Retrieved November 17, 2022, from \url{https://slack.com/help/articles/232289568-GitHub-for-Slack}
 

### 2022-11-17 manuscript.tex
Adding output settings to trigger the rendering action [ci skip]
This build is based on
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/8d4190ca13a7f11fb128da7e17ec7e4c73eefe31.

This commit was created by the following CI build and job:
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/8d4190ca13a7f11fb128da7e17ec7e4c73eefe31/checks
https://github.com/SORTEE-Github-Hackathon/manuscript/actions/runs/3490551921

@@
 This manuscript
-(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/e1d16866f2990cbb44fa4baf16633ca0e6a67556/}{permalink})
+(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/8d4190ca13a7f11fb128da7e17ec7e4c73eefe31/}{permalink})
 was automatically generated
-from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/e1d16866f2990cbb44fa4baf16633ca0e6a67556}{SORTEE-Github-Hackathon/manuscript@e1d1686}
+from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/8d4190ca13a7f11fb128da7e17ec7e4c73eefe31}{SORTEE-Github-Hackathon/manuscript@8d4190c}
 on November 17, 2022.

### 2022-11-17 manuscript.tex
Update response-to-the-reviewers.Rmd [ci skip]
This build is based on
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/366399c3a3d8d06832f71ea5ec300bf690d17bdd.

This commit was created by the following CI build and job:
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/366399c3a3d8d06832f71ea5ec300bf690d17bdd/checks
https://github.com/SORTEE-Github-Hackathon/manuscript/actions/runs/3490578909

@@
 This manuscript
-(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/8d4190ca13a7f11fb128da7e17ec7e4c73eefe31/}{permalink})
+(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/366399c3a3d8d06832f71ea5ec300bf690d17bdd/}{permalink})
 was automatically generated
-from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/8d4190ca13a7f11fb128da7e17ec7e4c73eefe31}{SORTEE-Github-Hackathon/manuscript@8d4190c}
+from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/366399c3a3d8d06832f71ea5ec300bf690d17bdd}{SORTEE-Github-Hackathon/manuscript@366399c}
 on November 17, 2022.

### 2022-11-22 editorial-communication/response-to-the-reviewers.Rmd
Adding output settings to trigger the rendering action
Update response-to-the-reviewers.Rmd
Discussing Overleaf & other integrations to address issue #290

@@
 title: "Response to the reviewers"
-date: "`r Sys.Date()`"
-output: html_document
+date: "Last compiled on `r format(Sys.time(), '%d %B, %Y')`"
+output:
+  html_document:
+    theme: cosmo 
+    highlight: tango
+    self_contained: true
 ---
@@
 
-Dear Mr Pedro Henrique Braga,
+Dear authors,
 
@@
 (Actually, I eventually found it buried in Table 1)
+
+We now discuss the possibility of integrating GitHub into existing workflows on Overleaf, Google Drive, and DropBox among others to collaboratively write scientific manuscripts, in the section "Writing a manuscript".
+We refer to Table 1 for further details on these integrations.
 

### 2022-12-07 manuscript.tex
Merge pull request #293 from SORTEE-Github-Hackathon/kh-revision-edits [ci skip]
This build is based on
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/eedb895f5a0d3ccba43cee5d4d3cd457b3a838f9.

This commit was created by the following CI build and job:
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/eedb895f5a0d3ccba43cee5d4d3cd457b3a838f9/checks
https://github.com/SORTEE-Github-Hackathon/manuscript/actions/runs/3635460690

@@
 This manuscript
-(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/366399c3a3d8d06832f71ea5ec300bf690d17bdd/}{permalink})
+(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/eedb895f5a0d3ccba43cee5d4d3cd457b3a838f9/}{permalink})
 was automatically generated
-from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/366399c3a3d8d06832f71ea5ec300bf690d17bdd}{SORTEE-Github-Hackathon/manuscript@366399c}
-on November 17, 2022.
+from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/eedb895f5a0d3ccba43cee5d4d3cd457b3a838f9}{SORTEE-Github-Hackathon/manuscript@eedb895}
+on December 7, 2022.
 
@@
 A centralized research compendium stored in a version-controlled repository has the advantages of facilitating collaboration, integrating data and code archiving services, allowing file versions to be accessed and restored, and contributes to open science (see sections below).
+The ability to make a GitHub repository private is particularly advantageous for storing materials without necessarily sacrificing privacy, which may be preferred or even essential for certain compendia.
+Researchers can then grant specific collaborators read and/or write access to private repositories to pursue pre-publication analyses or writing in privacy, or even to collaborate on research that will permanently remain private.
 
@@
 Text documents stored and versioned in GitHub can be instantly displayed when written in Markdown, a lightweight markup language increasingly popular among scientists.
-Co-authors can contribute changes or suggest revisions to a manuscript written in GitHub through pull requests (\protect\hyperlink{definitions}{Box 1}).
+Co-authors can contribute changes or suggest revisions to a manuscript written on GitHub through pull requests (\protect\hyperlink{definitions}{Box 1}).
 Pull requests provide line-by-line views of proposed changes, which can be commented, modified, or approved by designated reviewers and collaborators (\protect\hyperlink{tbl:roles}{Table 2}).
@@
 Moreover, real-time collaboration on text documents stored in GitHub repositories can be achieved with the help of other platforms {[}\emph{e.g.}, HackMD (\url{https://hackmd.io}) for Markdown documents{]}.
+
+Incorporating GitHub into the process of writing a manuscript does not necessarily mean pivoting to an entirely new workflow.
+For instance, authors who prefer writing in LaTeX can link their new or existing Overleaf projects to GitHub via the Git-Bridge and GitHub Synchronization features (\protect\hyperlink{tbl:compare}{Table 1}), which are available through premium subscriptions to Overleaf or through many institutions worldwide via the Overleaf Commons service (\url{https://www.overleaf.com/for/universities}) (\protect\hyperlink{ref-oGbKxHzj}{\emph{Using Git and GitHub}, n.d.}).
+Similar GitHub integrations are available for projects stored in DropBox, Google Drive, among other popular tools that are likely to be familiar to many scientists and their collaborators (\protect\hyperlink{tbl:compare}{Table 1}).
 
@@
 
+The desire or need for privacy during the developmental stages of a manuscript or of a larger research project is common in EEB, and this is often perceived as a major barrier to doing science openly through GitHub.
+Because GitHub repositories can be made private or public at any time, there is no need to choose privacy over open science, or vice-versa.
+As such, repositories can simply be kept private until their contents are ready to be shared publicly, as might occur when a research article is published or when an embargo is lifted.
+
 \hypertarget{project-continuity}{%
@@
 
-Automation can be integrated into GitHub repositories through the GitHub Actions feature (\protect\hyperlink{ref-NUXbp429}{\emph{Features • GitHub Actions}, n.d.}), or through alternative automation systems (\emph{e.g.}, Circle CI, \protect\hyperlink{ref-T03Api6e}{\emph{Continuous Integration and Delivery}, n.d.}); Travis CI, \emph{Homepage \textbar{} Travis CI -- Start Building Today!} (\protect\hyperlink{ref-YeFSbfFV}{n.d.}){]}.
+Automation can be integrated into GitHub repositories through the GitHub Actions feature (\protect\hyperlink{ref-NUXbp429}{\emph{Features • GitHub Actions}, n.d.}), or through alternative automation systems (\emph{e.g.}, Circle CI, \protect\hyperlink{ref-T03Api6e}{\emph{Continuous Integration and Delivery}, n.d.}); Travis CI, \emph{Home -- Travis-CI} (\protect\hyperlink{ref-YeFSbfFV}{2022}){]}.
 Users can set up workflows associated with their repositories that are triggered by events (\emph{e.g.}, push, pull request or at specified times) for remote servers to perform user-specified steps and actions.
@@
 GitHub Docs.
-Retrieved November 17, 2022, from \url{https://ghdocs-prod.azurewebsites.net/en/repositories/managing-your-repositorys-settings-and-features/customizing-your-repository/about-code-owners}
+Retrieved December 6, 2022, from \url{https://ghdocs-prod.azurewebsites.net/en/repositories/managing-your-repositorys-settings-and-features/customizing-your-repository/about-code-owners}
 
@@
 GitHub Docs.
-Retrieved November 17, 2022, from \url{https://ghdocs-prod.azurewebsites.net/en/repositories/working-with-files/managing-large-files/about-large-files-on-github}
+Retrieved December 6, 2022, from \url{https://ghdocs-prod.azurewebsites.net/en/repositories/working-with-files/managing-large-files/about-large-files-on-github}
 
@@
 GitHub Docs.
-Retrieved November 17, 2022, from \url{https://ghdocs-prod.azurewebsites.net/en/issues/planning-and-tracking-with-projects/learning-about-projects/about-projects}
+Retrieved December 6, 2022, from \url{https://ghdocs-prod.azurewebsites.net/en/issues/planning-and-tracking-with-projects/learning-about-projects/about-projects}
 
@@
 GitHub Docs.
-Retrieved November 17, 2022, from \url{https://ghdocs-prod.azurewebsites.net/en/communities/setting-up-your-project-for-healthy-contributions/adding-a-license-to-a-repository}
+Retrieved December 6, 2022, from \url{https://ghdocs-prod.azurewebsites.net/en/communities/setting-up-your-project-for-healthy-contributions/adding-a-license-to-a-repository}
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-6CMMeSeD}{}}%
-Bryan, J., \& TAs, T. S. 545. (n.d.). \emph{STAT 545}. Retrieved November 17, 2022, from \url{https://stat545.com/}
+Bryan, J., \& TAs, T. S. 545. (n.d.). \emph{STAT 545}. Retrieved December 6, 2022, from \url{https://stat545.com/}
 
 \leavevmode\vadjust pre{\hypertarget{ref-nwCtHDCn}{}}%
-\emph{Build software better, together}. (n.d.). GitHub. Retrieved November 17, 2022, from \url{https://github.com}
+\emph{Build software better, together}. (n.d.). GitHub. Retrieved December 6, 2022, from \url{https://github.com}
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-lx49NGto}{}}%
-\emph{Connect GitHub to a Project - OSF Support}. (n.d.). Retrieved November 17, 2022, from \url{https://help.osf.io/article/211-connect-github-to-a-project}
+\emph{Connect GitHub to a Project - OSF Support}. (n.d.). Retrieved December 6, 2022, from \url{https://help.osf.io/article/211-connect-github-to-a-project}
 
 \leavevmode\vadjust pre{\hypertarget{ref-T03Api6e}{}}%
-\emph{Continuous Integration and Delivery}. (n.d.). CircleCI. Retrieved November 17, 2022, from \url{https://circleci.com/}
+\emph{Continuous Integration and Delivery}. (n.d.). CircleCI. Retrieved December 6, 2022, from \url{https://circleci.com/}
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-NUXbp429}{}}%
-\emph{Features • GitHub Actions}. (n.d.). GitHub. Retrieved November 17, 2022, from \url{https://github.com/features/actions}
+\emph{Features • GitHub Actions}. (n.d.). GitHub. Retrieved December 6, 2022, from \url{https://github.com/features/actions}
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-ZvrOcg9w}{}}%
-Hester, J. B., the STAT 545 TAs, Jim. (n.d.). \emph{Let's Git started \textbar{} Happy Git and GitHub for the useR}. Retrieved November 17, 2022, from \url{https://happygitwithr.com/}
+Hester, J. B., the STAT 545 TAs, Jim. (n.d.). \emph{Let's Git started \textbar{} Happy Git and GitHub for the useR}. Retrieved December 6, 2022, from \url{https://happygitwithr.com/}
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-YeFSbfFV}{}}%
-\emph{Homepage \textbar{} Travis CI -- Start building today!} (n.d.). Travis CI. Retrieved November 17, 2022, from \url{https://www.travis-ci.com/}
+\emph{Home -- Travis-CI}. (2022, October 6). \url{https://www.travis-ci.com/}
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-3UAritXO}{}}%
-\emph{Issues · fmsabatini/sPlotOpen\_Manuscript}. (n.d.). GitHub. Retrieved November 17, 2022, from \url{https://github.com/fmsabatini/sPlotOpen_Manuscript}
+\emph{Issues · fmsabatini/sPlotOpen\_Manuscript}. (n.d.). GitHub. Retrieved December 6, 2022, from \url{https://github.com/fmsabatini/sPlotOpen_Manuscript}
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Re6Eg2va}{}}%
-\emph{Manubot - Manuscripts, open and automated}. (n.d.). Retrieved November 17, 2022, from \url{https://manubot.org}
+\emph{Manubot - Manuscripts, open and automated}. (n.d.). Retrieved December 6, 2022, from \url{https://manubot.org}
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-1GRWGlDWy}{}}%
-Slack. (n.d.). \emph{GitHub for Slack}. Slack Help Center. Retrieved November 17, 2022, from \url{https://slack.com/help/articles/232289568-GitHub-for-Slack}
+Slack. (n.d.). \emph{GitHub for Slack}. Slack Help Center. Retrieved December 6, 2022, from \url{https://slack.com/help/articles/232289568-GitHub-for-Slack}
 
@@
 \url{https://doi.org/10.1187/cbe.13-12-0241}
+
+\leavevmode\vadjust pre{\hypertarget{ref-oGbKxHzj}{}}%
+\emph{Using Git and GitHub}. (n.d.). Retrieved December 6, 2022, from \url{https://www.overleaf.com/learn/how-to/Using_Git_and_GitHub}
 

### 2022-12-07 editorial-communication/response-to-the-reviewers.Rmd
Address issue #288
- Added a short paragraph in the "Storing and sharing research compendia" section to mention that materials can be kept private
- Added a short paragraph in the "Open science discussion" to mention that private repos help to avoid a trade-off between privacy restrictions and open science practices
- Documented these changes in the response to reviewers
- Added my name to these two sections

(thanks to @kaitlyngaynor for these suggestions!)
Addressing changes in the response to reviewers

@@
 
+| We now directly discuss the possibility of keeping repositories private in the section "Storing and sharing research compendia" and in the "Open science discussion" to emphasize that there is not necessarily a trade-off between privacy, collaboration, and open science practices.
+
 **E1.3.** Another reason that many EEBers don't use GitHub appears to be related to how we develop code for projects.
@@
 
-We now discuss the possibility of integrating GitHub into existing workflows on Overleaf, Google Drive, and DropBox among others to collaboratively write scientific manuscripts, in the section "Writing a manuscript".
+| We now discuss the possibility of integrating GitHub into existing workflows on Overleaf, Google Drive, and DropBox among others to collaboratively write scientific manuscripts, in the section "Writing a manuscript".
 We refer to Table 1 for further details on these integrations.
@@
 
+| Corrected! Thank you for catching this!
+
 **R1.6.** Line 389 it should be 'each other's work': contribute to each other work without necessarily
+
+| Corrected! Thank you once again!
 
@@
 
+| We have added "prospective users" to this sentence.
+It now is "*It can be challenging to learn Git alongside scripting languages, statistical theory, and file system navigation, especially when many prospective users may be inexperienced with programming."*
+
 **R1.8.** Line 477: not sure what this sentence is saying: 'requiring the complementation of other tools to fully integration project files and GitHub repositories'
+
+| We agree that this sentence needed clarification.
+We have simplified it and it reads now as: "*Moreover, additional tools may be required to fully integrate project files and GitHub repositories [...]*".
+Thank you once again!
 
@@
 
+| Thank you for catching this. We closed the brackets.
+
 **R2.7.** There appears to be a "fourth" barrier at Line 478.
@@
 
+| Indeed! We have numbered all five barriers to using GitHub to clarify this section.
+
 **R2.8.** Line 570 "could also be e" should be "could also be a".
+
+| You are right! We have corrected this issue. Thank you once again!

### 2022-12-07 manuscript.tex
Merge pull request #295 from SORTEE-Github-Hackathon/phpb-addressing-minor-issue-281 [ci skip]
This build is based on
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/8f400dd0f6c28e752d4f7127284c1a33f564d2a1.

This commit was created by the following CI build and job:
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/8f400dd0f6c28e752d4f7127284c1a33f564d2a1/checks
https://github.com/SORTEE-Github-Hackathon/manuscript/actions/runs/3637845023

@@
 This manuscript
-(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/eedb895f5a0d3ccba43cee5d4d3cd457b3a838f9/}{permalink})
+(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/8f400dd0f6c28e752d4f7127284c1a33f564d2a1/}{permalink})
 was automatically generated
-from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/eedb895f5a0d3ccba43cee5d4d3cd457b3a838f9}{SORTEE-Github-Hackathon/manuscript@eedb895}
+from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/8f400dd0f6c28e752d4f7127284c1a33f564d2a1}{SORTEE-Github-Hackathon/manuscript@8f400dd}
 on December 7, 2022.
@@
 Maintaining code for scientific collaboration requires an efficient and well-documented work-flow (\protect\hyperlink{ref-1Kqna6l2}{J. M. Perkel, 2020}).
-To facilitate this process, scientists have been adopting tools from information and systems technology, such as cloud-based services for documentation and version control (\emph{e.g.}, from the Google Suite, the Microsoft Suite, and GitHub (\protect\hyperlink{ref-10ghgV3S8}{J.
-Perkel, 2016})).
+To facilitate this process, scientists have been adopting tools from information and systems technology, such as cloud-based services for documentation and version control {[}\emph{e.g.}, from the Google Suite, the Microsoft Suite, and GitHub (\protect\hyperlink{ref-10ghgV3S8}{J.
+Perkel, 2016}){]}.
 However, most researchers lack exposure to adequate code practices and thus dedicate valuable time and effort to self-teaching research-facilitating tools.
@@
 Repositories and organizations can have designated data and code owners {[}or more appropriate, stewards; see Hampton et al.
-(\protect\hyperlink{ref-iIEKCTLU}{2015}), \emph{About Code Owners} (\protect\hyperlink{ref-s91uGRZ2}{n.d.}){]}, who can also can change through time allowing for the transition of code between research cohorts.
+(\protect\hyperlink{ref-iIEKCTLU}{2015}), \emph{About Code Owners} (\protect\hyperlink{ref-s91uGRZ2}{n.d.}){]}, who can also change through time allowing for the transition of code between research cohorts.
 Other project collaborators can contribute to repository design and development, and their active involvement can both aid authors ability to act as guarantors of the project, and the clarity and reproducibility of the project for future users.
@@
 Organizations allow larger projects with many steps or moving parts to be constrained to one virtual space, where outputs and sub-projects can be easily accessed and located without relying on individuals.
-Because the repositories are grouped, members can reference and contribute to each others work without necessarily being part of the same repository, broadening the accessibility and longevity of code and writing contributions.
+Because the repositories are grouped, members can reference and contribute to each other's work without necessarily being part of the same repository, broadening the accessibility and longevity of code and writing contributions.
 
@@
 Although GitHub has been available as a platform for more than a decade, its uptake among EEB researchers, especially as a tool for collaboration, has been slow.
-
-Here, we discuss four potential barriers to GitHub use in EEB.
+Here, we discuss five potential barriers to GitHub use in EEB:
 
@@
 When GitHub is taught within an EEB context, it usually accompanies coursework in topics such as statistical programming.
-It can be challenging to learn Git alongside scripting languages, statistical theory, and file system navigation, especially when many may be inexperienced with programming.
+It can be challenging to learn Git alongside scripting languages, statistical theory, and file system navigation, especially when many prospective users may be inexperienced with programming.
 Instructors likewise may confuse the expected digital literacy of students with computational fluency, even when modern technology increasingly abstracts concepts through search optimization and preponderant integrated development environments (IDE), or `point-and-click' user interfaces.
@@
 This openness may add additional pressure to students and scientists learning to use the platform.
-File storage is size-limited on GitHub (but note that large files stored locally can still be versioned; see section ``Storing and sharing research compendia''), requiring the complementation of other tools to fully integration project files and GitHub repositories (\emph{e.g.}, (\protect\hyperlink{ref-lx49NGto}{\emph{Connect GitHub to a Project - OSF Support}, n.d.})).
-A major additional barrier to EEB researchers is the lack language-specific resources for non-English speaking researchers working in ecology and evolution.
+Moreover, additional tools may be required to fully integrate project files and GitHub repositories (\emph{e.g.}, (\protect\hyperlink{ref-lx49NGto}{\emph{Connect GitHub to a Project - OSF Support}, n.d.})).
+
+A fourth additional barrier to EEB researchers is the lack language-specific resources for non-English speaking researchers working in ecology and evolution.
 Language is a well-known obstacle to international collaborative research progress and to widespread scientific knowledge (see \protect\hyperlink{ref-cW7vGddM}{Khelifa et al., 2022}).
@@
 
-Lastly, when projects become highly collaborative they may have to pay for GitHub features such as branch protections, multiple reviewers of pull requests, and time in its automation tools.
-Currently, GitHub offers Education Packs (\url{https://education.github.com/}) to students and academics, which extends some paid features to the free plan.
+Fifth and lastly, when projects become highly collaborative, they may have to pay for GitHub features such as branch protections, multiple reviewers of pull requests, and time in its automation tools.
+Currently, GitHub offers Education Packs (\url{https://education.github.com/}) to students and academics, which extend some paid features to the free plan.
 However, the acquisition of GitHub by Microsoft has raised concerns over the future of free plans, causing several biodiversity data managers to shift to alternative Open Source Git services (\emph{e.g.}, Bitbucket and GitLab).
@@
 project. These roles are not mutually exclusive---a co-author could also
-be e code contributor and code reviewer, for example. For definitions of
+be a code contributor and code reviewer, for example. For definitions of
 the GitHub features, see Box 1. \label{tbl:roles}}\tabularnewline
@@
 GitHub Docs.
-Retrieved December 6, 2022, from \url{https://ghdocs-prod.azurewebsites.net/en/repositories/managing-your-repositorys-settings-and-features/customizing-your-repository/about-code-owners}
+Retrieved December 7, 2022, from \url{https://ghdocs-prod.azurewebsites.net/en/repositories/managing-your-repositorys-settings-and-features/customizing-your-repository/about-code-owners}
 
@@
 GitHub Docs.
-Retrieved December 6, 2022, from \url{https://ghdocs-prod.azurewebsites.net/en/repositories/working-with-files/managing-large-files/about-large-files-on-github}
+Retrieved December 7, 2022, from \url{https://ghdocs-prod.azurewebsites.net/en/repositories/working-with-files/managing-large-files/about-large-files-on-github}
 
@@
 GitHub Docs.
-Retrieved December 6, 2022, from \url{https://ghdocs-prod.azurewebsites.net/en/issues/planning-and-tracking-with-projects/learning-about-projects/about-projects}
+Retrieved December 7, 2022, from \url{https://ghdocs-prod.azurewebsites.net/en/issues/planning-and-tracking-with-projects/learning-about-projects/about-projects}
 
@@
 GitHub Docs.
-Retrieved December 6, 2022, from \url{https://ghdocs-prod.azurewebsites.net/en/communities/setting-up-your-project-for-healthy-contributions/adding-a-license-to-a-repository}
+Retrieved December 7, 2022, from \url{https://ghdocs-prod.azurewebsites.net/en/communities/setting-up-your-project-for-healthy-contributions/adding-a-license-to-a-repository}
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-6CMMeSeD}{}}%
-Bryan, J., \& TAs, T. S. 545. (n.d.). \emph{STAT 545}. Retrieved December 6, 2022, from \url{https://stat545.com/}
+Bryan, J., \& TAs, T. S. 545. (n.d.). \emph{STAT 545}. Retrieved December 7, 2022, from \url{https://stat545.com/}
 
 \leavevmode\vadjust pre{\hypertarget{ref-nwCtHDCn}{}}%
-\emph{Build software better, together}. (n.d.). GitHub. Retrieved December 6, 2022, from \url{https://github.com}
+\emph{Build software better, together}. (n.d.). GitHub. Retrieved December 7, 2022, from \url{https://github.com}
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-lx49NGto}{}}%
-\emph{Connect GitHub to a Project - OSF Support}. (n.d.). Retrieved December 6, 2022, from \url{https://help.osf.io/article/211-connect-github-to-a-project}
+\emph{Connect GitHub to a Project - OSF Support}. (n.d.). Retrieved December 7, 2022, from \url{https://help.osf.io/article/211-connect-github-to-a-project}
 
 \leavevmode\vadjust pre{\hypertarget{ref-T03Api6e}{}}%
-\emph{Continuous Integration and Delivery}. (n.d.). CircleCI. Retrieved December 6, 2022, from \url{https://circleci.com/}
+\emph{Continuous Integration and Delivery}. (n.d.). CircleCI. Retrieved December 7, 2022, from \url{https://circleci.com/}
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-NUXbp429}{}}%
-\emph{Features • GitHub Actions}. (n.d.). GitHub. Retrieved December 6, 2022, from \url{https://github.com/features/actions}
+\emph{Features • GitHub Actions}. (n.d.). GitHub. Retrieved December 7, 2022, from \url{https://github.com/features/actions}
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-ZvrOcg9w}{}}%
-Hester, J. B., the STAT 545 TAs, Jim. (n.d.). \emph{Let's Git started \textbar{} Happy Git and GitHub for the useR}. Retrieved December 6, 2022, from \url{https://happygitwithr.com/}
+Hester, J. B., the STAT 545 TAs, Jim. (n.d.). \emph{Let's Git started \textbar{} Happy Git and GitHub for the useR}. Retrieved December 7, 2022, from \url{https://happygitwithr.com/}
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-3UAritXO}{}}%
-\emph{Issues · fmsabatini/sPlotOpen\_Manuscript}. (n.d.). GitHub. Retrieved December 6, 2022, from \url{https://github.com/fmsabatini/sPlotOpen_Manuscript}
+\emph{Issues · fmsabatini/sPlotOpen\_Manuscript}. (n.d.). GitHub. Retrieved December 7, 2022, from \url{https://github.com/fmsabatini/sPlotOpen_Manuscript}
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Re6Eg2va}{}}%
-\emph{Manubot - Manuscripts, open and automated}. (n.d.). Retrieved December 6, 2022, from \url{https://manubot.org}
+\emph{Manubot - Manuscripts, open and automated}. (n.d.). Retrieved December 7, 2022, from \url{https://manubot.org}
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-1GRWGlDWy}{}}%
-Slack. (n.d.). \emph{GitHub for Slack}. Slack Help Center. Retrieved December 6, 2022, from \url{https://slack.com/help/articles/232289568-GitHub-for-Slack}
+Slack. (n.d.). \emph{GitHub for Slack}. Slack Help Center. Retrieved December 7, 2022, from \url{https://slack.com/help/articles/232289568-GitHub-for-Slack}
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-oGbKxHzj}{}}%
-\emph{Using Git and GitHub}. (n.d.). Retrieved December 6, 2022, from \url{https://www.overleaf.com/learn/how-to/Using_Git_and_GitHub}
+\emph{Using Git and GitHub}. (n.d.). Retrieved December 7, 2022, from \url{https://www.overleaf.com/learn/how-to/Using_Git_and_GitHub}
 

### 2022-12-07 editorial-communication/response-to-the-reviewers.Rmd
Additional information to address issue #284
- Added a sentence and reference to address issue #284, and edited the next sentence to follow the new information we added.
- Added a response to the reviewer comment (brief - we will need to add line numbers when edits are complete)

--- 2022-11-22 editorial-communication/response-to-the-reviewers.Rmd
@@
 Some additional emphasis on the ability to make repos "private" should be included beyond the Boxes.
+
+We now directly discuss the possibility of keeping repositories private in the section "Storing and sharing research compendia" and in the "Open science discussion" to emphasize that there is not necessarily a trade-off between privacy, collaboration, and open science practices.
 
@@
 
+We now briefly discuss the origin of Git and its expansion to applications beyond software development to help manage collaborations and community contributions, in the introduction.
+
 **R2.4.** I suggest adding a discussion on dependency testing within or following the paragraph on Automation (Lines 373-382).

### 2022-12-07 manuscript.tex
Merge pull request #296 from SORTEE-Github-Hackathon/phpb-addressing-git-issue-284 [ci skip]
This build is based on
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/58a2b25be4b30ef82f1ebbb07581893859ebcd27.

This commit was created by the following CI build and job:
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/58a2b25be4b30ef82f1ebbb07581893859ebcd27/checks
https://github.com/SORTEE-Github-Hackathon/manuscript/actions/runs/3640990890

@@
 This manuscript
-(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/8f400dd0f6c28e752d4f7127284c1a33f564d2a1/}{permalink})
+(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/58a2b25be4b30ef82f1ebbb07581893859ebcd27/}{permalink})
 was automatically generated
-from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/8f400dd0f6c28e752d4f7127284c1a33f564d2a1}{SORTEE-Github-Hackathon/manuscript@8f400dd}
+from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/58a2b25be4b30ef82f1ebbb07581893859ebcd27}{SORTEE-Github-Hackathon/manuscript@58a2b25}
 on December 7, 2022.
@@
 Git is the version control system that enables all the collaborative tools available on GitHub.
-Although the understanding of basic concepts of Git (such as commit, push, pull, checkout; see \protect\hyperlink{definitions}{Box 1}) is necessary, the GitHub web-based platform and its integrated development environments (such as the GitHub Desktop) allow users to perform most repository and data management operations without opening Git command-line sessions.
+Git was originally developed as a fast, lightweight and open-source system that would allow software engineers to efficiently develop and collaborate in projects (\protect\hyperlink{ref-1CM2EcdVk}{\emph{Git - A Short History of Git}, n.d.}\#:\textasciitilde:text=A\%20Short\%20History\%20of\%20Git\%20As\%20with\%20many,were\%20passed\%20around\%20as\%20patches\%20and\%20archived\%20files.).
+Since its launch in 2005, Git has become the leading version control system in software development and in other disciplines that similarly require collaboration and community contributions, such as scientific research (\protect\hyperlink{ref-7q3wZN6d}{Spinellis, 2012}).
+Although the understanding of basic concepts of Git (such as commit, push, pull, checkout; see \protect\hyperlink{definitions}{Box 1}) is necessary, the GitHub web-based platform and its integrated development environments (such as GitHub Desktop) allow users to perform most repository and data management operations without opening Git command-line sessions, making these functionalities available to users who are less familiar with software development.
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-1CM2EcdVk}{}}%
+\emph{Git - A Short History of Git}. (n.d.). Retrieved December 7, 2022, from \url{https://git-scm.com/book/en/v2/Getting-Started-A-Short-History-of-Git}
+
 \leavevmode\vadjust pre{\hypertarget{ref-pq2Tv1BC}{}}%
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-7q3wZN6d}{}}%
+Spinellis, D. (2012). Git. \emph{IEEE Software}, \emph{29}(3), 100--101. \url{https://doi.org/10.1109/ms.2012.61}
+
 \leavevmode\vadjust pre{\hypertarget{ref-1CzUZwyU2}{}}%

### 2022-12-14 R/Supp_Info_1.Rmd
Renames `scatterblob.Rmd` to `Supp_Info_1.Rmd`

--- 2022-07-26 R/scatterblob.Rmd
@@
 
-The collaborative [google spread sheet](https://docs.google.com/spreadsheets/d/1zCRgctjfjE2xZN9MkqfFh222K6bvVvA3gT0UdkL_CS8/edit#gid=0), features a first column listing the ways to use GitHub that were addressed in the manuscript (`r paste0(uses[1:12], collapse = "; " )`).
+The collaborative [google spread sheet](https://docs.google.com/spreadsheets/d/1zCRgctjfjE2xZN9MkqfFh222K6bvVvA3gT0UdkL_CS8/edit#gid=0), features a first column listing the ways to use GitHub that were addressed in the manuscript (`r paste0(uses[1:13], collapse = "; " )`).
 
@@
 plot(x = c(0.5, 5.5),
-     y = c(1.75, 10.75),
+     y = c(1.75, 11.5),
      xlab = "",
@@
      tck = 0.02)
-title(ylab="Technical difficulty", line=4, cex.lab=1)
-title(xlab="Degree of collaboration", line= 3.5, cex.lab=1)
+title(ylab="Technical difficulty", line = 4, cex.lab = 1)
+title(xlab="Degree of collaboration", line = 3.5, cex.lab = 1)
 ###############################################################
@@
 plot(x = c(0.5, 5.5),
-     y = c(0.4, 14),
+     y = c(0.5, 13.5),
      xlab = "",
@@
 
-![Degree of collaboration VS technical difficulty (sequential)](../content/images/scatterblob_1-viridis-turbo.png)
+![Degree of collaboration _versus_ technical difficulty (sequential)](../content/images/scatterblob_1-viridis-turbo.png)

### 2022-12-14 R/Supp_Info_1.Rmd
Building a skeleton for the supplementary material

@@
 ---
-title: "\\textbf{\\textsc{Supplementary Material} \\linebreak \\linebreak Not just for programmers: How GitHub can accelerate collaborative and reproducible research in ecology and evolution \\linebreak \\linebreak Methods to create \\textsl{the scatterblob} figure}"
 output:
-  html_document
+  bookdown::pdf_document2:
+      latex_engine: xelatex
+      number_sections: false
+      toc: false
+mainfont: "Times New Roman"
+geometry: margin = 1in
+spacing: double
+fontsize: 11pt
+editor_options:
+  markdown:
+    wrap: sentence
+csl: https://raw.githubusercontent.com/marlonecobos/kuenm/master/ecography.csl
+link-citations: yes
+header-includes:
+   - \usepackage{lineno}
+   - \linenumbers
+   - \usepackage{setspace}\doublespacing
+   - \usepackage{parskip}
+   - \setlength{\parindent}{4em}
+   - \setlength{\parskip}{0em}
+   - \usepackage{caption}
+   - \usepackage{pdflscape}
+   - \newcommand{\blandscape}{\begin{landscape}}
+   - \newcommand{\elandscape}{\end{landscape}}
 ---
@@
 ```
+
+## Study
+
+### Not just for programmers: How GitHub can accelerate collaborative and reproducible research in ecology and evolution
+
+### Supplementary Information 1
+
+### Representing technical difficulty and degree of collaboration in use cases for Github in ecology and evolution
+
+**Appendix S1.1. Computing indices of technical difficulty and degree of collaboration**
+
+We aimed at distributing the use cases discussed in our study across gradients of technical difficulty and collaboration.
+For this, we [...].
+
+We then [\...].
+
+We used Google Docs and Google Sheets to manipulate data, and plotted results using `R` version 4.02.
+
+\noindent
+
+**Appendix S1.2. Annotated code and prose allowing the representation of indices of technical difficulty and degree of collaboration**
 
@@
 
-![Degree of collaboration _versus_ technical difficulty (sequential)](../content/images/scatterblob_1-viridis-turbo.png)
+![Degree of collaboration *versus* technical difficulty (sequential)](../content/images/scatterblob_1-viridis-turbo.png)

### 2022-12-28 manuscript.tex
Merge pull request #300 from SORTEE-Github-Hackathon/RCO-E1.3-edits [ci skip]
This build is based on
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/1f11b09ef362e4c495e1cada9082ac6278c9ffd1.

This commit was created by the following CI build and job:
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/1f11b09ef362e4c495e1cada9082ac6278c9ffd1/checks
https://github.com/SORTEE-Github-Hackathon/manuscript/actions/runs/3796162565

@@
 This manuscript
-(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/58a2b25be4b30ef82f1ebbb07581893859ebcd27/}{permalink})
+(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/1f11b09ef362e4c495e1cada9082ac6278c9ffd1/}{permalink})
 was automatically generated
-from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/58a2b25be4b30ef82f1ebbb07581893859ebcd27}{SORTEE-Github-Hackathon/manuscript@58a2b25}
-on December 7, 2022.
+from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/1f11b09ef362e4c495e1cada9082ac6278c9ffd1}{SORTEE-Github-Hackathon/manuscript@1f11b09}
+on December 28, 2022.
 
@@
 Widespread adoption of GitHub for collaborating on research tasks can ultimately enable EEB researchers to spend less time on creating novel processes for collaboration and more time on their research (\protect\hyperlink{ref-ydrk01SR}{Briney et al., 2020}).
-More importantly, expanding the availability of data and code management standards -- of which GitHub is one increasingly important component -- makes research more reproducible and collaborative (\protect\hyperlink{ref-13QX8XU3J}{Alston \& Rick, 2021}; \protect\hyperlink{ref-pq2Tv1BC}{Gomes et al., 2022}).
+More importantly, expanding the availability of data and code management standards -- of which GitHub is one increasingly important component -- makes research more reproducible and collaborative (\protect\hyperlink{ref-13QX8XU3J}{Alston \& Rick, 2021}; \protect\hyperlink{ref-pq2Tv1BC}{Gomes et al., 2022b}).
 
@@
 Second, operations that are dependent on other software might not be easily achievable in GitHub, such as manipulating figures or tables.
-Although creating tables and figures can be done through code, users may choose other software to collaboratively brainstorm figures and tables (\emph{e.g}., Google Slides, Google Sheets; but see GitHub Discussions).
+While creating tables and figures can be done through code, users may choose other software to collaboratively brainstorm figures and tables (\emph{e.g}., Google Slides, Google Sheets; but see GitHub Discussions).
 
@@
 
-A third barrier may come from general reluctance to share data and code publicly, or technical and logistical issues (\protect\hyperlink{ref-pq2Tv1BC}{Gomes et al., 2022}).
+A third barrier may come from general reluctance to share data and code publicly, or technical and logistical issues (\protect\hyperlink{ref-pq2Tv1BC}{Gomes et al., 2022b}).
 GitHub is, by default, a public and open platform.
@@
 Moreover, additional tools may be required to fully integrate project files and GitHub repositories (\emph{e.g.}, (\protect\hyperlink{ref-lx49NGto}{\emph{Connect GitHub to a Project - OSF Support}, n.d.})).
+Other scientists may simply lack the time or incentives to document and version control their code if the code is unlikely to be reused beyond their analysis.
+However we (and others, \emph{e.g.,} (\protect\hyperlink{ref-VDJput1V}{Gomes et al., 2022a})) argue that the endeavour of open science and collaboration requires code owners to document and version control code despite uncertainty around future use.
 
@@
 GitHub Docs.
-Retrieved December 7, 2022, from \url{https://ghdocs-prod.azurewebsites.net/en/repositories/managing-your-repositorys-settings-and-features/customizing-your-repository/about-code-owners}
+Retrieved December 28, 2022, from \url{https://ghdocs-prod.azurewebsites.net/en/repositories/managing-your-repositorys-settings-and-features/customizing-your-repository/about-code-owners}
 
@@
 GitHub Docs.
-Retrieved December 7, 2022, from \url{https://ghdocs-prod.azurewebsites.net/en/repositories/working-with-files/managing-large-files/about-large-files-on-github}
+Retrieved December 28, 2022, from \url{https://ghdocs-prod.azurewebsites.net/en/repositories/working-with-files/managing-large-files/about-large-files-on-github}
 
@@
 GitHub Docs.
-Retrieved December 7, 2022, from \url{https://ghdocs-prod.azurewebsites.net/en/issues/planning-and-tracking-with-projects/learning-about-projects/about-projects}
+Retrieved December 28, 2022, from \url{https://ghdocs-prod.azurewebsites.net/en/issues/planning-and-tracking-with-projects/learning-about-projects/about-projects}
 
@@
 GitHub Docs.
-Retrieved December 7, 2022, from \url{https://ghdocs-prod.azurewebsites.net/en/communities/setting-up-your-project-for-healthy-contributions/adding-a-license-to-a-repository}
+Retrieved December 28, 2022, from \url{https://ghdocs-prod.azurewebsites.net/en/communities/setting-up-your-project-for-healthy-contributions/adding-a-license-to-a-repository}
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-6CMMeSeD}{}}%
-Bryan, J., \& TAs, T. S. 545. (n.d.). \emph{STAT 545}. Retrieved December 7, 2022, from \url{https://stat545.com/}
+Bryan, J., \& TAs, T. S. 545. (n.d.). \emph{STAT 545}. Retrieved December 28, 2022, from \url{https://stat545.com/}
 
 \leavevmode\vadjust pre{\hypertarget{ref-nwCtHDCn}{}}%
-\emph{Build software better, together}. (n.d.). GitHub. Retrieved December 7, 2022, from \url{https://github.com}
+\emph{Build software better, together}. (n.d.). GitHub. Retrieved December 28, 2022, from \url{https://github.com}
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-lx49NGto}{}}%
-\emph{Connect GitHub to a Project - OSF Support}. (n.d.). Retrieved December 7, 2022, from \url{https://help.osf.io/article/211-connect-github-to-a-project}
+\emph{Connect GitHub to a Project - OSF Support}. (n.d.). Retrieved December 28, 2022, from \url{https://help.osf.io/article/211-connect-github-to-a-project}
 
 \leavevmode\vadjust pre{\hypertarget{ref-T03Api6e}{}}%
-\emph{Continuous Integration and Delivery}. (n.d.). CircleCI. Retrieved December 7, 2022, from \url{https://circleci.com/}
+\emph{Continuous Integration and Delivery}. (n.d.). CircleCI. Retrieved December 28, 2022, from \url{https://circleci.com/}
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-NUXbp429}{}}%
-\emph{Features • GitHub Actions}. (n.d.). GitHub. Retrieved December 7, 2022, from \url{https://github.com/features/actions}
+\emph{Features • GitHub Actions}. (n.d.). GitHub. Retrieved December 28, 2022, from \url{https://github.com/features/actions}
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-1CM2EcdVk}{}}%
-\emph{Git - A Short History of Git}. (n.d.). Retrieved December 7, 2022, from \url{https://git-scm.com/book/en/v2/Getting-Started-A-Short-History-of-Git}
+\emph{Git - A Short History of Git}. (n.d.). Retrieved December 28, 2022, from \url{https://git-scm.com/book/en/v2/Getting-Started-A-Short-History-of-Git}
+
+\leavevmode\vadjust pre{\hypertarget{ref-VDJput1V}{}}%
+Gomes, D.
+G.
+E., Pottier, P., Crystal-Ornelas, R., Hudgins, E.
+J., Foroughirad, V., Sánchez-Reyes, L.
+L., Turba, R., Martinez, P.
+A., Moreau, D., Bertram, M.
+G., Smout, C.
+A., \& Gaynor, K.
+M.
+(2022a).
+Why don't we share data and code?
+Perceived barriers and benefits to public archiving practices.
+\emph{Proceedings of the Royal Society B: Biological Sciences}, \emph{289}(1987).
+\url{https://doi.org/10.1098/rspb.2022.1113}
 
@@
 A., Moreau, D., Bertram, M., Smout, C., \& Gaynor, K.
-(2022).
+(2022b).
 \emph{Why don't we share data and code?
@@
 \leavevmode\vadjust pre{\hypertarget{ref-ZvrOcg9w}{}}%
-Hester, J. B., the STAT 545 TAs, Jim. (n.d.). \emph{Let's Git started \textbar{} Happy Git and GitHub for the useR}. Retrieved December 7, 2022, from \url{https://happygitwithr.com/}
+Hester, J. B., the STAT 545 TAs, Jim. (n.d.). \emph{Let's Git started \textbar{} Happy Git and GitHub for the useR}. Retrieved December 28, 2022, from \url{https://happygitwithr.com/}
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-3UAritXO}{}}%
-\emph{Issues · fmsabatini/sPlotOpen\_Manuscript}. (n.d.). GitHub. Retrieved December 7, 2022, from \url{https://github.com/fmsabatini/sPlotOpen_Manuscript}
+\emph{Issues · fmsabatini/sPlotOpen\_Manuscript}. (n.d.). GitHub. Retrieved December 28, 2022, from \url{https://github.com/fmsabatini/sPlotOpen_Manuscript}
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Re6Eg2va}{}}%
-\emph{Manubot - Manuscripts, open and automated}. (n.d.). Retrieved December 7, 2022, from \url{https://manubot.org}
+\emph{Manubot - Manuscripts, open and automated}. (n.d.). Retrieved December 28, 2022, from \url{https://manubot.org}
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-1GRWGlDWy}{}}%
-Slack. (n.d.). \emph{GitHub for Slack}. Slack Help Center. Retrieved December 7, 2022, from \url{https://slack.com/help/articles/232289568-GitHub-for-Slack}
+Slack. (n.d.). \emph{Where work happens}. Slack Help Center. Retrieved December 28, 2022, from \url{https://slack.com/help/articles/232289568-GitHub-for-Slack}
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-oGbKxHzj}{}}%
-\emph{Using Git and GitHub}. (n.d.). Retrieved December 7, 2022, from \url{https://www.overleaf.com/learn/how-to/Using_Git_and_GitHub}
+\emph{Using Git and GitHub}. (n.d.). Retrieved December 28, 2022, from \url{https://www.overleaf.com/learn/how-to/Using_Git_and_GitHub}
 

### 2022-12-29 manuscript.tex
Merge pull request #301 from SORTEE-Github-Hackathon/RCO-E1.5 [ci skip]
This build is based on
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/73fa0d8679265b37682a8d4b8159c51616f5dc98.

This commit was created by the following CI build and job:
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/73fa0d8679265b37682a8d4b8159c51616f5dc98/checks
https://github.com/SORTEE-Github-Hackathon/manuscript/actions/runs/3799015277

@@
 This manuscript
-(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/1f11b09ef362e4c495e1cada9082ac6278c9ffd1/}{permalink})
+(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/73fa0d8679265b37682a8d4b8159c51616f5dc98/}{permalink})
 was automatically generated
-from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/1f11b09ef362e4c495e1cada9082ac6278c9ffd1}{SORTEE-Github-Hackathon/manuscript@1f11b09}
-on December 28, 2022.
+from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/73fa0d8679265b37682a8d4b8159c51616f5dc98}{SORTEE-Github-Hackathon/manuscript@73fa0d8}
+on December 29, 2022.
 
@@
 Maintaining code for scientific collaboration requires an efficient and well-documented work-flow (\protect\hyperlink{ref-1Kqna6l2}{J. M. Perkel, 2020}).
-To facilitate this process, scientists have been adopting tools from information and systems technology, such as cloud-based services for documentation and version control {[}\emph{e.g.}, from the Google Suite, the Microsoft Suite, and GitHub (\protect\hyperlink{ref-10ghgV3S8}{J.
+To facilitate this process, scientists have been adopting tools from information and systems technology, such as cloud-based services for documentation and version control {[}\emph{e.g.}, the Google Suite, the Microsoft Suite, DropBox, and GitHub (\protect\hyperlink{ref-10ghgV3S8}{J.
 Perkel, 2016}){]}.
+Of all the tools mentioned above, GitHub is uniquely positioned (\protect\hyperlink{tbl:compare}{Table 1}) to benefit scientists because the platform is designed to enable collaboration on computer code--a fundamental component of modern research.
 However, most researchers lack exposure to adequate code practices and thus dedicate valuable time and effort to self-teaching research-facilitating tools.
-Thus, researchers may not adhere to standards of code quality and maintenance (\protect\hyperlink{ref-fJWFe93e}{Hannay et al., 2009}; \protect\hyperlink{ref-10SpoByIw}{Prabhu et al., 2011}; \protect\hyperlink{ref-O6UbstGG}{Wilson et al., 2014}).
-Here, we review and discuss one of the most used web-based platforms for computational version control and collaboration, GitHub, and provide researchers in ecology and evolutionary biology (EEB) with practical workflows to facilitate and improve their code and its management.
+GitHub is one of the most used web-based platforms for computational version control and collaboration, and in this paper we provide researchers in ecology and evolutionary biology (EEB) with practical workflows to use GitHub to facilitate and improve their code and its management.
 
@@
 Through version control, users have a detailed, chronological record of the files and directories stored in their repositories (\protect\hyperlink{ref-RVetqmsg}{Bryan, 2018}) (see \protect\hyperlink{definitions}{Box 1}).
+Additionally, unlike sharing documents and code via DropBox or Google Drive links, GitHub defaults to public sharing of code and documents and has features like Issues and Discussions (see \protect\hyperlink{definitions}{Box 1}) that can immediately and directly contribute to more open science and knowledge sharing.
 This workflow provides a strong and clear advantage over sending files back-and-forth (\emph{e.g.}, via email), a process that can become challenging and time-consuming in long-term and collaborative projects (\protect\hyperlink{ref-4ny1onB0}{Ram, 2013}).
@@
 Perkel, 2016}), its use is still not widespread.
-First-time users without formal training in information technology may face steep learning curves because GitHub and its features have been centered on collaboration for code development in information systems (\protect\hyperlink{ref-139b0pSGc}{Leibzon, 2016}).
+First-time users without formal training in information technology may face steep learning curves because GitHub and its features have been centered on software development (\protect\hyperlink{ref-139b0pSGc}{Leibzon, 2016}).
 Moreover, domain-specific resources providing tractable examples and practical guidance for researchers in EEB on GitHub are scarce {[}but see Kim et al.
@@
 A centralized research compendium stored in a version-controlled repository has the advantages of facilitating collaboration, integrating data and code archiving services, allowing file versions to be accessed and restored, and contributes to open science (see sections below).
+While some EEB researchers may prefer to store their code in Google Drive or DropBox, the process of sharing code through these services becomes cumbersome when collaborators have to download and re-upload edited code.
+On GitHub, code is by default public, and the process of forking and submitting pull requests (see \protect\hyperlink{definitions}{Box 1}) ensures a code owner has full control over code and documents in a repository.
 The ability to make a GitHub repository private is particularly advantageous for storing materials without necessarily sacrificing privacy, which may be preferred or even essential for certain compendia.
@@
 
-There have been many calls for researchers outside of the software development community to adopt GitHub to improve their collaborative research (\protect\hyperlink{ref-UsTxAq4f}{Anbaroğlu, 2021}; \protect\hyperlink{ref-1Du6fzB8g}{Crystal‐Ornelas et al., 2021}; \protect\hyperlink{ref-10ghgV3S8}{J.
+There have been many calls for researchers outside of the software development community to adopt GitHub for their collaborative research (\protect\hyperlink{ref-UsTxAq4f}{Anbaroğlu, 2021}; \protect\hyperlink{ref-1Du6fzB8g}{Crystal‐Ornelas et al., 2021}; \protect\hyperlink{ref-10ghgV3S8}{J.
 Perkel, 2016}).
 These calls come in light of the continuous shift towards open-science and the increasing computational and data requirements in EEB.
+While tools like the Google Suite and DropBox enable rapid sharing and collaboration of some research documents, GitHub brings together features that directly address open science such as tools for soliciting public discussions on code and findings, tracking multiple rounds of edits to files in a sensible way for easy review, and managing complex research projects with many collaborators and goals.
 Until now, resources and practical guidance on using GitHub within the EEB community have been dispersed in blog posts and video tutorials (\protect\hyperlink{tips}{Box 2}).
@@
 
-Despite its strong collaborative potential, we describe two use cases where GitHub's features fall short of highly collaborative work emblematic of EEB research.
+Despite its strong collaborative potential, we describe two use cases where GitHub's features fall short of highly collaborative work.
 
@@
 
-Although GitHub has been available as a platform for more than a decade, its uptake among EEB researchers, especially as a tool for collaboration, has been slow.
+GitHub has been available as a platform for more than a decade, its uptake among EEB researchers, especially as a tool for collaboration, has been slow.
 Here, we discuss five potential barriers to GitHub use in EEB:
@@
 Institutional encouragement and instructional resources focused on researchers in ecology and evolution may be limited.
+And with institutional availability of software licenses for tools like the Google Suite or Microsoft Office, researchers may be hesitant to spend valuable time learning another tool.
 When GitHub is taught within an EEB context, it usually accompanies coursework in topics such as statistical programming.
@@
 GitHub Docs.
-Retrieved December 28, 2022, from \url{https://ghdocs-prod.azurewebsites.net/en/repositories/managing-your-repositorys-settings-and-features/customizing-your-repository/about-code-owners}
+Retrieved December 29, 2022, from \url{https://ghdocs-prod.azurewebsites.net/en/repositories/managing-your-repositorys-settings-and-features/customizing-your-repository/about-code-owners}
 
@@
 GitHub Docs.
-Retrieved December 28, 2022, from \url{https://ghdocs-prod.azurewebsites.net/en/repositories/working-with-files/managing-large-files/about-large-files-on-github}
+Retrieved December 29, 2022, from \url{https://ghdocs-prod.azurewebsites.net/en/repositories/working-with-files/managing-large-files/about-large-files-on-github}
 
@@
 GitHub Docs.
-Retrieved December 28, 2022, from \url{https://ghdocs-prod.azurewebsites.net/en/issues/planning-and-tracking-with-projects/learning-about-projects/about-projects}
+Retrieved December 29, 2022, from \url{https://ghdocs-prod.azurewebsites.net/en/issues/planning-and-tracking-with-projects/learning-about-projects/about-projects}
 
@@
 GitHub Docs.
-Retrieved December 28, 2022, from \url{https://ghdocs-prod.azurewebsites.net/en/communities/setting-up-your-project-for-healthy-contributions/adding-a-license-to-a-repository}
+Retrieved December 29, 2022, from \url{https://ghdocs-prod.azurewebsites.net/en/communities/setting-up-your-project-for-healthy-contributions/adding-a-license-to-a-repository}
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-6CMMeSeD}{}}%
-Bryan, J., \& TAs, T. S. 545. (n.d.). \emph{STAT 545}. Retrieved December 28, 2022, from \url{https://stat545.com/}
+Bryan, J., \& TAs, T. S. 545. (n.d.). \emph{STAT 545}. Retrieved December 29, 2022, from \url{https://stat545.com/}
 
 \leavevmode\vadjust pre{\hypertarget{ref-nwCtHDCn}{}}%
-\emph{Build software better, together}. (n.d.). GitHub. Retrieved December 28, 2022, from \url{https://github.com}
+\emph{Build software better, together}. (n.d.). GitHub. Retrieved December 29, 2022, from \url{https://github.com}
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-lx49NGto}{}}%
-\emph{Connect GitHub to a Project - OSF Support}. (n.d.). Retrieved December 28, 2022, from \url{https://help.osf.io/article/211-connect-github-to-a-project}
+\emph{Connect GitHub to a Project - OSF Support}. (n.d.). Retrieved December 29, 2022, from \url{https://help.osf.io/article/211-connect-github-to-a-project}
 
 \leavevmode\vadjust pre{\hypertarget{ref-T03Api6e}{}}%
-\emph{Continuous Integration and Delivery}. (n.d.). CircleCI. Retrieved December 28, 2022, from \url{https://circleci.com/}
+\emph{Continuous Integration and Delivery}. (n.d.). CircleCI. Retrieved December 29, 2022, from \url{https://circleci.com/}
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-NUXbp429}{}}%
-\emph{Features • GitHub Actions}. (n.d.). GitHub. Retrieved December 28, 2022, from \url{https://github.com/features/actions}
+\emph{Features • GitHub Actions}. (n.d.). GitHub. Retrieved December 29, 2022, from \url{https://github.com/features/actions}
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-1CM2EcdVk}{}}%
-\emph{Git - A Short History of Git}. (n.d.). Retrieved December 28, 2022, from \url{https://git-scm.com/book/en/v2/Getting-Started-A-Short-History-of-Git}
+\emph{Git - A Short History of Git}. (n.d.). Retrieved December 29, 2022, from \url{https://git-scm.com/book/en/v2/Getting-Started-A-Short-History-of-Git}
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-ZvrOcg9w}{}}%
-Hester, J. B., the STAT 545 TAs, Jim. (n.d.). \emph{Let's Git started \textbar{} Happy Git and GitHub for the useR}. Retrieved December 28, 2022, from \url{https://happygitwithr.com/}
+Hester, J. B., the STAT 545 TAs, Jim. (n.d.). \emph{Let's Git started \textbar{} Happy Git and GitHub for the useR}. Retrieved December 29, 2022, from \url{https://happygitwithr.com/}
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-3UAritXO}{}}%
-\emph{Issues · fmsabatini/sPlotOpen\_Manuscript}. (n.d.). GitHub. Retrieved December 28, 2022, from \url{https://github.com/fmsabatini/sPlotOpen_Manuscript}
+\emph{Issues · fmsabatini/sPlotOpen\_Manuscript}. (n.d.). GitHub. Retrieved December 29, 2022, from \url{https://github.com/fmsabatini/sPlotOpen_Manuscript}
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Re6Eg2va}{}}%
-\emph{Manubot - Manuscripts, open and automated}. (n.d.). Retrieved December 28, 2022, from \url{https://manubot.org}
+\emph{Manubot - Manuscripts, open and automated}. (n.d.). Retrieved December 29, 2022, from \url{https://manubot.org}
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-10SpoByIw}{}}%
-Prabhu, P., Zhang, Y., Ghosh, S., August, D.
-I., Huang, J., Beard, S., Kim, H., Oh, T., Jablin, T.
-B., Johnson, N.
-P., Zoufaly, M., Raman, A., Liu, F., \& Walker, D.
-(2011).
-A survey of the practice of computational science.
-\emph{State of the Practice Reports on - SC '11}.
-State of the Practice Reports.
-\url{https://doi.org/10.1145/2063348.2063374}
-
 \leavevmode\vadjust pre{\hypertarget{ref-666HppfO}{}}%
@@
 \leavevmode\vadjust pre{\hypertarget{ref-1GRWGlDWy}{}}%
-Slack. (n.d.). \emph{Where work happens}. Slack Help Center. Retrieved December 28, 2022, from \url{https://slack.com/help/articles/232289568-GitHub-for-Slack}
+Slack. (n.d.). \emph{Where work happens}. Slack Help Center. Retrieved December 29, 2022, from \url{https://slack.com/help/articles/232289568-GitHub-for-Slack}
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-oGbKxHzj}{}}%
-\emph{Using Git and GitHub}. (n.d.). Retrieved December 28, 2022, from \url{https://www.overleaf.com/learn/how-to/Using_Git_and_GitHub}
+\emph{Using Git and GitHub}. (n.d.). Retrieved December 29, 2022, from \url{https://www.overleaf.com/learn/how-to/Using_Git_and_GitHub}
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-O6UbstGG}{}}%
-Wilson, G., Aruliah, D.
-A., Brown, C.
-T., Chue Hong, N.
-P., Davis, M., Guy, R.
-T., Haddock, S.
-H.
-D., Huff, K.
-D., Mitchell, I.
-M., Plumbley, M.
-D., Waugh, B., White, E.
-P., \& Wilson, P.
-(2014).
-Best Practices for Scientific Computing.
-\emph{PLoS Biology}, \emph{12}(1), e1001745.
-\url{https://doi.org/10.1371/journal.pbio.1001745}
-
 \leavevmode\vadjust pre{\hypertarget{ref-QqMezOMg}{}}%

### 2023-01-02 manuscript.tex
Merge pull request #297 from SORTEE-Github-Hackathon/R1 [ci skip]
This build is based on
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/077be9d884d5bc703a0a7db131e90f2d35254fbc.

This commit was created by the following CI build and job:
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/077be9d884d5bc703a0a7db131e90f2d35254fbc/checks
https://github.com/SORTEE-Github-Hackathon/manuscript/actions/runs/3823725295

@@
 This manuscript
-(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/73fa0d8679265b37682a8d4b8159c51616f5dc98/}{permalink})
+(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/077be9d884d5bc703a0a7db131e90f2d35254fbc/}{permalink})
 was automatically generated
-from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/73fa0d8679265b37682a8d4b8159c51616f5dc98}{SORTEE-Github-Hackathon/manuscript@73fa0d8}
-on December 29, 2022.
+from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/077be9d884d5bc703a0a7db131e90f2d35254fbc}{SORTEE-Github-Hackathon/manuscript@077be9d}
+on January 2, 2023.
 
@@
 
-Most scientists, including ecologists and evolutionary biologists, are increasingly dependent on computational tools in their research (\protect\hyperlink{ref-fJWFe93e}{Hannay et al., 2009}).
-Researchers write and use software packages or data analysis code (hereafter, code) to perform scientific tasks ranging from data management, data analysis, and study replication, to the application and the development of tools for hypothesis testing.
+Most scientists, including ecologists and evolutionary biologists, depend on computational tools for their research (\protect\hyperlink{ref-fJWFe93e}{Hannay et al., 2009}).
+Researchers write and use software packages or write code (hereafter, code) to perform scientific tasks ranging from data management, data analysis, and study replication, to the application and the development of tools for hypothesis testing.
 Maintaining code for scientific collaboration requires an efficient and well-documented work-flow (\protect\hyperlink{ref-1Kqna6l2}{J. M. Perkel, 2020}).
@@
 
-With over 83 million registered users as of 2022, GitHub (\url{https://github.com}) is the most widely-used web platform for collaborating on computer code (\protect\hyperlink{ref-nwCtHDCn}{\emph{Build Software Better, Together}, n.d.}).
-GitHub provides a simple but powerful web interface that allows users to participate in projects by contributing, modifying and discussing existing code, reporting bugs, discovering code and data, and publishing new code.
+GitHub (\url{https://github.com}) provides a simple but powerful web interface that allows users to participate in projects by contributing, modifying and discussing existing code, reporting bugs, discovering code and data, and publishing new code.
 Through version control, users have a detailed, chronological record of the files and directories stored in their repositories (\protect\hyperlink{ref-RVetqmsg}{Bryan, 2018}) (see \protect\hyperlink{definitions}{Box 1}).
@@
 Git is the version control system that enables all the collaborative tools available on GitHub.
-Git was originally developed as a fast, lightweight and open-source system that would allow software engineers to efficiently develop and collaborate in projects (\protect\hyperlink{ref-1CM2EcdVk}{\emph{Git - A Short History of Git}, n.d.}\#:\textasciitilde:text=A\%20Short\%20History\%20of\%20Git\%20As\%20with\%20many,were\%20passed\%20around\%20as\%20patches\%20and\%20archived\%20files.).
+Git was originally developed as a fast, lightweight and open-source system that would allow software engineers to efficiently develop and collaborate in projects (\protect\hyperlink{ref-1CM2EcdVk}{\emph{Git - A Short History of Git}, n.d.}).
 Since its launch in 2005, Git has become the leading version control system in software development and in other disciplines that similarly require collaboration and community contributions, such as scientific research (\protect\hyperlink{ref-7q3wZN6d}{Spinellis, 2012}).
 Although the understanding of basic concepts of Git (such as commit, push, pull, checkout; see \protect\hyperlink{definitions}{Box 1}) is necessary, the GitHub web-based platform and its integrated development environments (such as GitHub Desktop) allow users to perform most repository and data management operations without opening Git command-line sessions, making these functionalities available to users who are less familiar with software development.
+
+Version control involves tracking the state of the files in a folder, called a ``repository'' (see \protect\hyperlink{definitions}{Box 1}), through the evolution of a project.
+A basic workflow using git and GitHub is to 1) make changes to files in a repository on your computer, 2) record related changes in files as a ``commit'' (see \protect\hyperlink{definitions}{Box 1}) along with a message describing the changes, 3) synchronize commits with GitHub (see ``push'' in \protect\hyperlink{definitions}{Box 1}) so that the repository on the web is up to date.
+Collaborators can then view your changes online and synchronize them to their own computers (see ``pull'' in \protect\hyperlink{definitions}{Box 1}).
+Commits act like snapshots and one can view or even revert the state of the project to any previous commit.
+If the modified files are plain text (\emph{e.g.} computer code or .txt files), only the differences from the previous commit are recorded, allowing you to frequently commit changes without causing the size of the project to grow excessively.
+This provides a safe and less cluttered alternative to frequently making full copies of documents at different points in their evolution (\emph{e.g.} analysis.R, analasys\_v2.R, analysis\_FINAL.R).
+More technical details about the use of Git and GitHub are beyond the scope of this paper (but see Perez-Riverol et al.
+(\protect\hyperlink{ref-kEX5dgzK}{2016}), Blischak et al.
+(\protect\hyperlink{ref-PlcxShQU}{2016}), and Kalliamvakou et al.
+(\protect\hyperlink{ref-ndfO9H}{2015})).
 
@@
 Widespread adoption of GitHub for collaborating on research tasks can ultimately enable EEB researchers to spend less time on creating novel processes for collaboration and more time on their research (\protect\hyperlink{ref-ydrk01SR}{Briney et al., 2020}).
-More importantly, expanding the availability of data and code management standards -- of which GitHub is one increasingly important component -- makes research more reproducible and collaborative (\protect\hyperlink{ref-13QX8XU3J}{Alston \& Rick, 2021}; \protect\hyperlink{ref-pq2Tv1BC}{Gomes et al., 2022b}).
+More importantly, expanding the availability of data and code management standards---of which GitHub is one increasingly important component---makes research more reproducible and collaborative (\protect\hyperlink{ref-13QX8XU3J}{Alston \& Rick, 2021}; \protect\hyperlink{ref-pq2Tv1BC}{Gomes et al., 2022b}).
 
@@
 
-GitHub limits committed file sizes to 100 Mb (megabytes) (\protect\hyperlink{ref-1Co6ZZjF1}{\emph{About Large Files on GitHub}, n.d.}), which can make it challenging for centralizing research compendia containing larger file sizes.
-Users may still version large files using Git Large File Storage (\url{https://git-lfs.github.com}) text pointers, but may have to rely on external file storage alternatives (such as local or cloud-hosting).
+GitHub limits committed file sizes to 100 Mb (megabytes) (\protect\hyperlink{ref-1Co6ZZjF1}{\emph{About Large Files on GitHub}, n.d.}), which can may require external file storage alternatives (such as local or cloud-hosting) for some parts of research compendia.
+However, with some additional setup, users can still track versions of these external files in their repositories using Git Large File Storage (\url{https://git-lfs.github.com}).
 
@@
 Laboratory notebooks help researchers track their research notes, methods, policies and protocols (\protect\hyperlink{ref-wwHxTOtm}{Kanza et al., 2017}).
-Virtual laboratory notebooks can be stored in GitHub repositories and provide the benefits of simultaneous, centralized and selective access, and allows for the easy update of policies and experiment protocols (\protect\hyperlink{ref-10V7x4H4l}{Schnell, 2015}).
+Virtual laboratory notebooks can be stored on GitHub and provide the benefits of simultaneous, centralized and selective access, and allows for the easy update of policies and experiment protocols (\protect\hyperlink{ref-10V7x4H4l}{Schnell, 2015}).
 Researchers have been increasingly using GitHub to maintain versions and share digital laboratory notebooks across many fields (\protect\hyperlink{ref-10ghgV3S8}{J.
@@
 On GitHub, collaborators can share feedback, brainstorm ideas, and troubleshoot problems (Figure \ref{fig:github-diagram}).
-Project management can happen via three GitHub repository features: ``Issues'', ``Discussion'' and ``Projects''.
+Project management can happen via three GitHub repository features: ``Issues'', ``Discussion'' and ``Projects'' (\protect\hyperlink{definitions}{Box 1}).
 Github Issues allow for discrete tasks and sub-tasks to be identified, assigned to team members, and categorized with custom labels.
 Github Discussions serve as a message board for conversation.
-Finally, GitHub Projects integrate issues and pull requests on automated spreadsheets and project boards, providing users with real-time tracking of project priorities and status (\protect\hyperlink{ref-RhBKe0MG}{\emph{About Projects}, n.d.}).
-Scripts, commit messages, and pull requests can be linked directly to issues, discussions, and projects providing a clear record of project workflow.
+Finally, GitHub Projects provides users with real-time tracking of project priorities and status (\protect\hyperlink{ref-RhBKe0MG}{\emph{About Projects}, n.d.}).
 For instance, one can create a discussion on a project repository to decide which method to apply for biodiversity data analysis.
@@
 Using GitHub for all project-related conversation and planning, rather than email or messaging tools, makes it easier to keep track of progress throughout the lifespan of a project.
+However, one can opt to receive new issues, discussions, and responses as emails and can post replies by email as well.\\
+This allows for centralized communication for a team even when some members prefer to use email for communication.
 Unlike emails and messages which can get lost as more new tasks arise, GitHub issues are intentionally closed by repository administrators hiding the issue from view (closed issues remain accessible but not immediately visible).
-Project management in GitHub can also be integrated with third-party applications, such as Zenhub (\url{https://www.zenhub.com}) or Slack (\url{https://slack.github.com}).
-Zenhub allows for the enhanced visualization and organization of repositories and their issues, while the GitHub for Slack integration allows notifications from GitHub events to be sent directly to users or group channels (see \protect\hyperlink{ref-1GRWGlDWy}{Slack, n.d.}).
 
@@
 
-Making presentations, syllabi and other course materials can be done through most major high-level programming languages such as R, with \texttt{RMarkdown} (\protect\hyperlink{ref-QqMezOMg}{Xie et al., 2019}), Python, with \texttt{python-ppt} (\url{https://python-pptx.readthedocs.io}), and Julia, with \texttt{Remark.jl} (\url{https://juliapackages.com/p/remark}), and be version-controlled and stored in GitHub.
-Once content is made, hosting a course website can be done through GitHub Pages (\url{https://pages.github.com}; \emph{e.g.}, \url{https://github.com/topics/course-website}).
-This way, course content can be available to enrolled students, as well as a global pool of learners and teachers interested in the material.
-Content can then be delivered via the course website, and/or a GitHub Organization with, for example, template repositories for assignments.
-Student submissions are perhaps the most challenging component, but the new GitHub Classroom tool (\url{https://classroom.github.com}) allows instructors to host private assignments to be submitted collaboratively or individually as code or PDF files, and even build autograding tests.
-Although time-consuming to establish, using these features can integrate learning version control and GitHub with the learning course content, and thus boost students' feelings of self-efficacy and confidence (\protect\hyperlink{ref-dqrFjoSb}{Trujillo \& Tanner, 2014}).
+Syllabi, presentations, and other course materials can be version-controlled and stored in GitHub.
+Although plain text formats such as markdown or HTML work best with GitHub and help to keep the total size of the repository within limits, any file type can be stored on and downloaded from GitHub including PowerPoint and Word documents.
+Content can then be delivered by sharing a link to the GitHub repository or creating a template repository with assignments that students can use.
+Using GitHub to host a course website is also an option for making course content more widely and easily accessible (see \protect\hyperlink{hosting-a-website}{Hosting a Website}).
+
+Using GitHub to collect student submissions is more advanced, but the new GitHub Classroom tool (\url{https://classroom.github.com}) allows instructors to host private assignments to be submitted collaboratively or individually as code or PDF files, and even build auto-grading tests.
+Using GitHub for course management may take an additional time investment compared to traditional tools, but integrating version control and GitHub into course content can boost students' feelings of self-efficacy and confidence (\protect\hyperlink{ref-dqrFjoSb}{Trujillo \& Tanner, 2014}).
 
@@
 Despite researchers in ecology and evolution generally lacking experience in building or hosting webpages, many tools have been developed to help this process.
-Static websites can now be easily built using independent software and languages, such as Jekyll (\url{https://jekyllrb.com}), Hugo (\url{https://gohugo.io}), Quarto (\url{https://quarto.org}), and wowchemy (\url{https://wowchemy.com}), or with the help of dependencies in the programming languages scientists commonly use, such as the \texttt{distill} (\url{https://github.com/rstudio/distill}) and \texttt{blogdown} (\url{https://bookdown.org/yihui/blogdown}) R packages.
-The resulting files from static websites can then be hosted in repositories, from which one can activate GitHub's Pages (\url{https://pages.github.com}) feature, allowing for the direct live hosting of HyperText Markup Language (HTML), Cascading Style Sheets (CSS) and JavaScript files within a free github.io domain.
-
-Website templates are readily available on GitHub (\url{https://github.com/topics/website-template}) or in user-specific repositories, which can be forked (\protect\hyperlink{definitions}{Box 1}) and customized (\protect\hyperlink{ref-MXxgZJ45}{Dawson, 2016}).
-Aside from free hosting services, GitHub Pages also allows websites to be autogenerated and instantly updated following content modifications (\protect\hyperlink{ref-RVetqmsg}{Bryan, 2018}).
-Creating and hosting websites on GitHub pages can be time-consuming, as this process usually requires more knowledge in web design than out-of-the-box platforms (\emph{e.g.}, Wix, Weebly, Google Sites).
-However, free hosting, widely available template customization, and versioning are strong advantages over the alternatives.
+Simple websites can consist of a single HTML or markdown document that will be rendered as a website by activating GitHub's Pages (\url{https://pages.github.com}) feature.
+More complex websites can now be easily built from templates that can be found on GitHub (\url{https://github.com/topics/website-template}) or generated using literate programming tools like Quarto (\url{https://quarto.org}) and RMarkdown (e.g.~with the \texttt{blogdown} package).
+These can be customized by editing text files and GitHub Pages will automatically generate and publish the resulting website.
+These methods of creating and hosting websites on GitHub pages lack a graphical user interface; however, free hosting, widely available template customization, and versioning are strong advantages over alternatives (\emph{e.g.}, Wix, Weebly, Google Sites).
 
@@
 
-\hypertarget{collaborative-and-asynchronous-code-editing}{%
-\subsubsection{Collaborative and asynchronous code editing}\label{collaborative-and-asynchronous-code-editing}}
-
-Researchers can asynchronously communicate and individually or collaboratively work in GitHub.
-By forking, branching, and cloning repositories (\protect\hyperlink{definitions}{Box 1}), researchers can simultaneously work on different issues of the same research project to then later merge changes to the main branch project with pull requests.
-Explicit project organization and increased communication in GitHub Issues, Discussions, or within pull requests can help with project development and with potential merge conflicts due to users simultaneously working on the same sections (\protect\hyperlink{ref-1BJcvyTmV}{Vale et al., 2019}).
-Moreover, version control (\protect\hyperlink{ref-K7nbP1Ty}{Crystal-Ornelas et al., 2022}) and commit reversal features allow researchers to track and progress without worrying about irreparably modifying someone else's work.
+\hypertarget{code-editing}{%
+\subsubsection{Collaborative and asynchronous code editing}\label{code-editing}}
+
+In academic settings, GitHub can serve as a platform for everyone (advisors, advisees, collaborators) to share in-progress work, and flag specific challenges or questions for each other (\protect\hyperlink{tbl:roles}{Table 2}).
+Periodic code review (\protect\hyperlink{ref-hm9PaCLD}{Song et al., 2020}) is useful for identifying errors early in the scientific process, and informing further training and mentorship to fill gaps in skills.
+This is facilitated by a group of core features of git and GitHub that allow contributors to work simultaneously on the same project without interfering with each other's work.
+``Branching'' and ``forking'' (see \protect\hyperlink{definitions}{Box 1}) allow users to work independently on a linked copy of a repository and then later merge their changes into the main project.
+When a set of related changes contributing some new feature or milestone are ready to be evaluated and merged, one makes a ``pull request'' (see \protect\hyperlink{definitions}{Box 1}).
+Pull requests are a formalized way of integrating changes to avoid conflicts that arise when users make simultaneous edits to the same parts of files (\protect\hyperlink{ref-1BJcvyTmV}{Vale et al., 2019}).
+The GitHub interface for a pull request allows collaborators to comment on specific lines of code/text being changed and even to provide suggestions that the pull request author can implement with the click of a button, greatly facilitating peer review.
+Moreover, version control (\protect\hyperlink{ref-K7nbP1Ty}{Crystal-Ornelas et al., 2022}) allows researchers to make changes in code or documents without worrying about irreparably modifying someone else's work.
 By enabling more comprehensive remote collaboration, GitHub encourages the exchange of ideas among researchers at different institutions and in different countries, which can serve to improve the quality of the research itself by providing open access to data and code.
-In academic settings, GitHub can also facilitate interactions between research advisors and advisees, providing a platform for students or other trainees to share in-progress code, and flag specific challenges or questions for their supervisors or mentors (\protect\hyperlink{tbl:roles}{Table 2}).
-Periodic code review (\protect\hyperlink{ref-hm9PaCLD}{Song et al., 2020}) can also help advisors identify errors early in the process, and inform further training and mentorship to fill gaps in skills.
 
@@
 Text documents stored and versioned in GitHub can be instantly displayed when written in Markdown, a lightweight markup language increasingly popular among scientists.
-Co-authors can contribute changes or suggest revisions to a manuscript written on GitHub through pull requests (\protect\hyperlink{definitions}{Box 1}).
-Pull requests provide line-by-line views of proposed changes, which can be commented, modified, or approved by designated reviewers and collaborators (\protect\hyperlink{tbl:roles}{Table 2}).
-Relevant literature or issues can be made using the Discussions and Issues features.
-Moreover, real-time collaboration on text documents stored in GitHub repositories can be achieved with the help of other platforms {[}\emph{e.g.}, HackMD (\url{https://hackmd.io}) for Markdown documents{]}.
+When manuscripts are written in Markdown on GitHub, co-authors can contribute changes or suggest revisions to a manuscript in the same ways they would contribute changes or suggest revisions to code (see \protect\hyperlink{code-editing}{Collaborative and asynchronous code editing}).
+Relevant literature or issues can be suggested using the Discussions and Issues features.
 
@@
 GitHub Docs.
-Retrieved December 29, 2022, from \url{https://ghdocs-prod.azurewebsites.net/en/repositories/managing-your-repositorys-settings-and-features/customizing-your-repository/about-code-owners}
+Retrieved January 2, 2023, from \url{https://ghdocs-prod.azurewebsites.net/en/repositories/managing-your-repositorys-settings-and-features/customizing-your-repository/about-code-owners}
 
@@
 GitHub Docs.
-Retrieved December 29, 2022, from \url{https://ghdocs-prod.azurewebsites.net/en/repositories/working-with-files/managing-large-files/about-large-files-on-github}
+Retrieved January 2, 2023, from \url{https://ghdocs-prod.azurewebsites.net/en/repositories/working-with-files/managing-large-files/about-large-files-on-github}
 
@@
 GitHub Docs.
-Retrieved December 29, 2022, from \url{https://ghdocs-prod.azurewebsites.net/en/issues/planning-and-tracking-with-projects/learning-about-projects/about-projects}
+Retrieved January 2, 2023, from \url{https://ghdocs-prod.azurewebsites.net/en/issues/planning-and-tracking-with-projects/learning-about-projects/about-projects}
 
@@
 GitHub Docs.
-Retrieved December 29, 2022, from \url{https://ghdocs-prod.azurewebsites.net/en/communities/setting-up-your-project-for-healthy-contributions/adding-a-license-to-a-repository}
+Retrieved January 2, 2023, from \url{https://ghdocs-prod.azurewebsites.net/en/communities/setting-up-your-project-for-healthy-contributions/adding-a-license-to-a-repository}
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-PlcxShQU}{}}%
+Blischak, J.
+D., Davenport, E.
+R., \& Wilson, G.
+(2016).
+A Quick Introduction to Version Control with Git and GitHub.
+\emph{PLOS Computational Biology}, \emph{12}(1), e1004668.
+\url{https://doi.org/10.1371/journal.pcbi.1004668}
+
 \leavevmode\vadjust pre{\hypertarget{ref-Xsdcv6q}{}}%
@@
 \leavevmode\vadjust pre{\hypertarget{ref-6CMMeSeD}{}}%
-Bryan, J., \& TAs, T. S. 545. (n.d.). \emph{STAT 545}. Retrieved December 29, 2022, from \url{https://stat545.com/}
-
-\leavevmode\vadjust pre{\hypertarget{ref-nwCtHDCn}{}}%
-\emph{Build software better, together}. (n.d.). GitHub. Retrieved December 29, 2022, from \url{https://github.com}
+Bryan, J., \& TAs, T. S. 545. (n.d.). \emph{STAT 545}. Retrieved January 2, 2023, from \url{https://stat545.com/}
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-lx49NGto}{}}%
-\emph{Connect GitHub to a Project - OSF Support}. (n.d.). Retrieved December 29, 2022, from \url{https://help.osf.io/article/211-connect-github-to-a-project}
+\emph{Connect GitHub to a Project - OSF Support}. (n.d.). Retrieved January 2, 2023, from \url{https://help.osf.io/article/211-connect-github-to-a-project}
 
 \leavevmode\vadjust pre{\hypertarget{ref-T03Api6e}{}}%
-\emph{Continuous Integration and Delivery}. (n.d.). CircleCI. Retrieved December 29, 2022, from \url{https://circleci.com/}
+\emph{Continuous Integration and Delivery}. (n.d.). CircleCI. Retrieved January 2, 2023, from \url{https://circleci.com/}
 
@@
 \url{https://doi.org/10.1371/journal.pbio.3000763}
-
-\leavevmode\vadjust pre{\hypertarget{ref-MXxgZJ45}{}}%
-Dawson, C. (2016). \emph{Building tools with GitHub: customize your workflow} (First Edition). O'Reilly.
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-NUXbp429}{}}%
-\emph{Features • GitHub Actions}. (n.d.). GitHub. Retrieved December 29, 2022, from \url{https://github.com/features/actions}
+\emph{Features • GitHub Actions}. (n.d.). GitHub. Retrieved January 2, 2023, from \url{https://github.com/features/actions}
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-1CM2EcdVk}{}}%
-\emph{Git - A Short History of Git}. (n.d.). Retrieved December 29, 2022, from \url{https://git-scm.com/book/en/v2/Getting-Started-A-Short-History-of-Git}
+\emph{Git - A Short History of Git}. (n.d.). Retrieved January 2, 2023, from \url{https://git-scm.com/book/en/v2/Getting-Started-A-Short-History-of-Git}
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-ZvrOcg9w}{}}%
-Hester, J. B., the STAT 545 TAs, Jim. (n.d.). \emph{Let's Git started \textbar{} Happy Git and GitHub for the useR}. Retrieved December 29, 2022, from \url{https://happygitwithr.com/}
+Hester, J. B., the STAT 545 TAs, Jim. (n.d.). \emph{Let's Git started \textbar{} Happy Git and GitHub for the useR}. Retrieved January 2, 2023, from \url{https://happygitwithr.com/}
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-3UAritXO}{}}%
-\emph{Issues · fmsabatini/sPlotOpen\_Manuscript}. (n.d.). GitHub. Retrieved December 29, 2022, from \url{https://github.com/fmsabatini/sPlotOpen_Manuscript}
+\emph{Issues · fmsabatini/sPlotOpen\_Manuscript}. (n.d.). GitHub. Retrieved January 2, 2023, from \url{https://github.com/fmsabatini/sPlotOpen_Manuscript}
+
+\leavevmode\vadjust pre{\hypertarget{ref-ndfO9H}{}}%
+Kalliamvakou, E., Damian, D., Blincoe, K., Singer, L., \& German, D.
+M.
+(2015, May).
+Open Source-Style Collaborative Development Practices in Commercial Projects Using GitHub.
+\emph{2015 IEEE/ACM 37th IEEE International Conference on Software Engineering}.
+2015 IEEE/ACM 37th IEEE International Conference on Software Engineering (ICSE).
+\url{https://doi.org/10.1109/icse.2015.74}
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Re6Eg2va}{}}%
-\emph{Manubot - Manuscripts, open and automated}. (n.d.). Retrieved December 29, 2022, from \url{https://manubot.org}
+\emph{Manubot - Manuscripts, open and automated}. (n.d.). Retrieved January 2, 2023, from \url{https://manubot.org}
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-1GRWGlDWy}{}}%
-Slack. (n.d.). \emph{Where work happens}. Slack Help Center. Retrieved December 29, 2022, from \url{https://slack.com/help/articles/232289568-GitHub-for-Slack}
-
 \leavevmode\vadjust pre{\hypertarget{ref-HiIPSSHV}{}}%
@@
 \leavevmode\vadjust pre{\hypertarget{ref-oGbKxHzj}{}}%
-\emph{Using Git and GitHub}. (n.d.). Retrieved December 29, 2022, from \url{https://www.overleaf.com/learn/how-to/Using_Git_and_GitHub}
+\emph{Using Git and GitHub}. (n.d.). Retrieved January 2, 2023, from \url{https://www.overleaf.com/learn/how-to/Using_Git_and_GitHub}
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-QqMezOMg}{}}%
-Xie, Y., Allaire, J. J., \& Grolemund, G. (2019). \emph{R Markdown: the definitive guide}. CRC Press, Taylor and Francis Group.
-
 \leavevmode\vadjust pre{\hypertarget{ref-1CJo8lo2v}{}}%

### 2023-01-03 editorial-communication/response-to-the-reviewers.Qmd
convert to Qmd for cross-reference ability

--- 2022-12-07 editorial-communication/response-to-the-reviewers.Rmd
@@
 date: "Last compiled on `r format(Sys.time(), '%d %B, %Y')`"
-output:
-  html_document:
+format:
+  html:
     theme: cosmo 
-    highlight: tango
-    self_contained: true
+    highlight-style: tango
+    embed-resources: true
 ---
-
-```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = TRUE)
-```
 
@@
 | We now directly discuss the possibility of keeping repositories private in the section "Storing and sharing research compendia" and in the "Open science discussion" to emphasize that there is not necessarily a trade-off between privacy, collaboration, and open science practices.
+|
 
@@
   We refer to Table 1 for further details on these integrations.
+|
 
@@
 More should be made of this in text, as opposed to burying it in Table 1, which is referenced only once in text (line 232) and only in the context of other longterm archives (line 231).
-Indeed, I suggest a somewhat expanded section of the ms.
-dedicated to a detailed exploration of the comparisons made in this Table.
-Otherwise, the ms.
-comes across as more proselytizing and less analytical/convincing.
+Indeed, I suggest a somewhat expanded section of the ms. dedicated to a detailed exploration of the comparisons made in this Table.
+Otherwise, the ms. comes across as more proselytizing and less analytical/convincing.
 
@@
 Advanced usage may be mentioned but not detailed as much as it is currently done.
-E.g.
-collaboratively writing a paper in GitHub is probably out of the question for most.
+E.g. collaboratively writing a paper in GitHub is probably out of the question for most.
 Most GitHub options for communication, discussion, issue tracking are still somewhat esoteric for most non-programmers.
@@
 
-| Corrected! Thank you for catching this!
+| Corrected! 
+  Thank you for catching this!
+|
 
@@
 
-| Corrected! Thank you once again!
+| Corrected! 
+  Thank you once again!
+|
 
-**R1.7.** Line 457 missing 'collaborator'? especially when many may be
+**R1.7.** Line 457 missing 'collaborator'?
+especially when many may be
 
@@
 | We agree that this sentence needed clarification. 
-We have simplified it and it reads now as: "*Moreover, additional tools may be required to fully integrate project files and GitHub repositories [...]*".
+  We have simplified it and it reads now as: "*Moreover, additional tools may be required to fully integrate project files and GitHub repositories \[...\]*". 
   Thank you once again!
+|
 
@@
 Software engineers have been working on this challenge for a long time in distributed teams where different parts of software are being built by different programmers.
-Checks can be done automatically within the software engineering framework (see Pasquier et al.
-2017 <https://www.nature.com/articles/sdata2017114>).
+Checks can be done automatically within the software engineering framework (see Pasquier et al. 2017 <https://www.nature.com/articles/sdata2017114>).
 Beyond detection, any major changes can be detected and presented without additional work from the user via features like badges (<https://shields.io/>) within the project page (e.g., README).
@@
 
-| Thank you for catching this. We closed the brackets.
+| Thank you for catching this. 
+  We closed the brackets.
+|
 
@@
 
-| Indeed! We have numbered all five barriers to using GitHub to clarify this section.
+| Indeed! 
+  We have numbered all five barriers to using GitHub to clarify this section.
+|
 
@@
 
-| You are right! We have corrected this issue. Thank you once again!
+| You are right! 
+  We have corrected this issue. 
+  Thank you once again!
+|

### 2023-01-03 editorial-communication/response-to-the-reviewers.Qmd
format for cross-referencing

--- 2022-12-07 editorial-communication/response-to-the-reviewers.Rmd
@@
 date: "Last compiled on `r format(Sys.time(), '%d %B, %Y')`"
-output:
-  html_document:
+format:
+  html:
     theme: cosmo 
-    highlight: tango
-    self_contained: true
+    highlight-style: tango
+    embed-resources: true
 ---
 
-```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = TRUE)
-```
+## Editor {#sec-E1}
 
-Dear authors,
+> As a long-term but sporadic GitHub user myself, I agree with most of the points and cases presented in the paper.
 
-Thank you for submitting your manuscript to Methods in Ecology and Evolution.
-I have now received the reviewers' reports, copies of which are included below.
-This manuscript has the potential to make a valuable contribution to the area, but there are a number of significant concerns that need to be addressed.
-I have considered your paper in light of the comments received and I would like to invite you to prepare a major revision.
+#### Streamline use cases (E1.1) {#sec-E1.1}
 
-In addition to addressing the comments from the reviewers, I note the following.
+> I agree with Reviewer 1 that these could be streamlined somewhat into a smaller number of more generalizable cases.
+> They also are a bit heavily weighted towards more experienced users.
+> "Simple" operations like push, pull, and commit are rarely understandable to new users, who routinely forget to commit their actions.
+> The GitHub Desktop app makes many of the operations and use of GitHub somewhat easier, and is a good entree into GitHub and Git for novices.
+> More could be made of the desktop app.
 
-As a long-term but sporadic GitHub user myself, I agree with most of the points and cases presented in the paper.
+#### Address private repos (E1.2) {#sec-E1.2}
 
-**E1.1.** I agree with Reviewer 1 that these could be streamlined somewhat into a smaller number of more generalizable cases.
-They also are a bit heavily weighted towards more experienced users.
-"Simple" operations like push, pull, and commit are rarely understandable to new users, who routinely forget to commit their actions.
-The GitHub Desktop app makes many of the operations and use of GitHub somewhat easier, and is a good entree into GitHub and Git for novices.
-More could be made of the desktop app.
-
-**E1.2.** In my own experience, the "public" nature of repos is a major barrier to the use of GitHub for exactly the reason you suggest - EEB practioners remain very uncomfortable with sharing data pre-publication (and often even post-publication).
-Some additional emphasis on the ability to make repos "private" should be included beyond the Boxes.
+> In my own experience, the "public" nature of repos is a major barrier to the use of GitHub for exactly the reason you suggest - EEB practioners remain very uncomfortable with sharing data pre-publication (and often even post-publication).
+> Some additional emphasis on the ability to make repos "private" should be included beyond the Boxes.
 
@@
 
-**E1.3.** Another reason that many EEBers don't use GitHub appears to be related to how we develop code for projects.
-Unless we are developing packages that others are likely to use, we tend to develop one-off scripts or functions that, once they work and are run, are never returned to.
-Version control is not used widely, or even needed in these cases (and my own work in software engineering provenance software has similarly had little uptake for the same reasons).
-I recognize that this makes it difficult to document the processes involved, but if the goal is simply to analyze the data at hand and push out another paper, why deal with the overhead of version control?
-At root, this is a sociological phenomenon, not a scientific one.
-Within your ms., consider saying something about how even one-off scripts may need to be documented, archived, and assigned a DOI to conform to evolving archiving requirements of journals.
+#### Discuss documentation of single-purpose scripts (E1.3) {#sec-E1.3}
 
-**E1.4.** I am surprised you didn't include integration between GitHub and Overleaf.
-Overleaf is also a good collaborative latex-based text processor, and provides syncing with GitHub (and Dropbox) in a way that will be more familiar to beginning users.
-(Actually, I eventually found it buried in Table 1)
+> Another reason that many EEBers don't use GitHub appears to be related to how we develop code for projects.
+> Unless we are developing packages that others are likely to use, we tend to develop one-off scripts or functions that, once they work and are run, are never returned to.
+> Version control is not used widely, or even needed in these cases (and my own work in software engineering provenance software has similarly had little uptake for the same reasons).
+> I recognize that this makes it difficult to document the processes involved, but if the goal is simply to analyze the data at hand and push out another paper, why deal with the overhead of version control?
+> At root, this is a sociological phenomenon, not a scientific one.
+> Within your ms., consider saying something about how even one-off scripts may need to be documented, archived, and assigned a DOI to conform to evolving archiving requirements of journals.
+
+#### Discuss Overleaf integration (E1.4) {#sec-E1.4}
+
+> I am surprised you didn't include integration between GitHub and Overleaf.
+> Overleaf is also a good collaborative latex-based text processor, and provides syncing with GitHub (and Dropbox) in a way that will be more familiar to beginning users.
+> (Actually, I eventually found it buried in Table 1)
 
@@
 
-**E1.5.** Finally, DropBox, SharePoint, and OneDrive are file-sharing systems that include version control, are widely supported, especially in colleges and universities, and are much easier to use for those who might be uncomfortable learning a system such as GitHub.
-Other than the ability to clone and fork, why should one choose GitHub over, for example, DropBox or SharePoint?
-More should be made of this in text, as opposed to burying it in Table 1, which is referenced only once in text (line 232) and only in the context of other longterm archives (line 231).
-Indeed, I suggest a somewhat expanded section of the ms.
-dedicated to a detailed exploration of the comparisons made in this Table.
-Otherwise, the ms.
-comes across as more proselytizing and less analytical/convincing.
+#### Improve discussion of GitHub advantages over other existing file-sharing tools (E1.5.) {#sec-E1.5}
 
-Reviewer(s)' Comments to Author: Reviewer: 1
+> Finally, DropBox, SharePoint, and OneDrive are file-sharing systems that include version control, are widely supported, especially in colleges and universities, and are much easier to use for those who might be uncomfortable learning a system such as GitHub.
+> Other than the ability to clone and fork, why should one choose GitHub over, for example, DropBox or SharePoint?
+> More should be made of this in text, as opposed to burying it in Table 1, which is referenced only once in text (line 232) and only in the context of other longterm archives (line 231).
+> Indeed, I suggest a somewhat expanded section of the ms. dedicated to a detailed exploration of the comparisons made in this Table.
+> Otherwise, the ms. comes across as more proselytizing and less analytical/convincing.
 
-Comments to the Corresponding Author
+## Reviewer 1 {#sec-R1}
 
-This paper clearly communicates the enthusiasm of the authors for integrating GitHub in the EEB research process.
-Advantages in areas of collaboration, transparent and reproducible science are clear and nicely discussed.
-This is a well written paper.
+> This paper clearly communicates the enthusiasm of the authors for integrating GitHub in the EEB research process.
+> Advantages in areas of collaboration, transparent and reproducible science are clear and nicely discussed.
+> This is a well written paper.
 
-**R1.1.** I would, however, recommend some restructuring and shortening.
-As it stands, this paper is too long and some of the use cases are too nerdy to spark enthusiasm in somebody who is not already using GitHub.
-Breaking it into 13 use cases leads to some repetition and those use cases may be combined more effectively for convincing a new user.
+#### Reduce repetition (R1.1) {#sec-R1.1}
 
-**R1.2.** The title and abstract gave me the impression that the goal is to convince EEB researcher to start using GitHub.
-If that's the case, it might be better to tailor the use cases to that entry level and use less GitHub specific lingo.
-Advanced usage may be mentioned but not detailed as much as it is currently done.
-E.g.
-collaboratively writing a paper in GitHub is probably out of the question for most.
-Most GitHub options for communication, discussion, issue tracking are still somewhat esoteric for most non-programmers.
+> I would, however, recommend some restructuring and shortening.
+> As it stands, this paper is too long and some of the use cases are too nerdy to spark enthusiasm in somebody who is not already using GitHub.
+> Breaking it into 13 use cases leads to some repetition and those use cases may be combined more effectively for convincing a new user.
 
-**R1.3.** Although the abstract states 'We outline features ranging from low to high technical difficulty' the paper reads a bit like a laundry list of what GitHub can do (in fact, the word 'can' is used about 140 times, which makes for tedious read).
-Figure 2 helps sort through this laundry list and defines the technical difficulty.
-It might be better to clearly lay out where anybody can start using GitHub effectively in the text.
-And the emphasis is on 'effectively'.
-Most people are not likely to learn a new piece of software if it does not promise to reduce effort and time.
-So, defining tasks where GitHub shines in terms of return on investment maybe the better approach to convincing new users and then only mention the advance use cases with some pointers to further reading, but not going into too much detail.
+In order to reduce repetition and jargon in the use cases sections, we've added a paragraph to the introduction \[L\_\_ -L\_\_\] explaining a basic git & GitHub workflow and pointing the reader to other resources for learning these tools.
+This allows us to focus less on explaining the specific mechanisms of git/Github in the use cases sections and more on the usefulness of the tools.
+In regards to the specific suggestion about deprioritizing GitHub communication tools, we believe these are extremely useful alternatives to reply-all email chains for a variety of reasons and have attempted to improve the clarity of this section of our manuscript \[end of project management section\].
 
-**R1.4.** In my experience, the project continuity is actually very high on the importance list for researchers, i.e., knowing that the code and data will be findable by the next student.
-This includes the discussion of organizing and managing teams, keeping lab information in one place etc.
-Followed by code versioning and the ability to go back to older versions.
-Interest in website development is picking up because it really is simple to do in GitHub, and the information can be maintained by several people (i.e., a lab group).
+#### Reduce jargon (R1.2) {#sec-R1.2}
 
-Detailed comments:
+> The title and abstract gave me the impression that the goal is to convince EEB researcher to start using GitHub.
+> If that's the case, it might be better to tailor the use cases to that entry level and use less GitHub specific lingo.
+> Advanced usage may be mentioned but not detailed as much as it is currently done.
+> E.g. collaboratively writing a paper in GitHub is probably out of the question for most.
+> Most GitHub options for communication, discussion, issue tracking are still somewhat esoteric for most non-programmers.
 
-**R1.5.** Line 346 delete second 'can': who can also can change through time
+#### Define use-cases in terms of return on investment (R1.3) {#sec-R1.3}
 
-**R1.6.** Line 389 it should be 'each other's work': contribute to each other work without necessarily
+> Although the abstract states 'We outline features ranging from low to high technical difficulty' the paper reads a bit like a laundry list of what GitHub can do (in fact, the word 'can' is used about 140 times, which makes for tedious read).
+> Figure 2 helps sort through this laundry list and defines the technical difficulty.
+> It might be better to clearly lay out where anybody can start using GitHub effectively in the text.
+> And the emphasis is on 'effectively'.
+> Most people are not likely to learn a new piece of software if it does not promise to reduce effort and time.
+> So, defining tasks where GitHub shines in terms of return on investment maybe the better approach to convincing new users and then only mention the advance use cases with some pointers to further reading, but not going into too much detail.
 
-**R1.7.** Line 457 missing 'collaborator'? especially when many may be
+-   return on investment is subjective
+-   E.g.
+all co-authors on this paper used GitHub to collectively write a manuscript (i.e.
+the one being reviewed), and for us it was an excellent return on investment, but not all co-authors have experience in the other use-cases we present and may find them more or less useful depending on their needs.
+-   figure 2 quantifies investment already
+-   However, we have taken the advice in other comments (CROSS_REFS) to combine and re-order sections somewhat.
+Hopefully we present the smaller number of cases in a way that better captures the needs of a majority of our readers.
 
-**R1.8.** Line 477: not sure what this sentence is saying: 'requiring the complementation of other tools to fully integration project files and GitHub repositories'
+#### Reorder sections based on importance (R1.4) {#sec-R1.4}
 
-Reviewer: 2
+> In my experience, the project continuity is actually very high on the importance list for researchers, i.e., knowing that the code and data will be findable by the next student.
+> This includes the discussion of organizing and managing teams, keeping lab information in one place etc.
+> Followed by code versioning and the ability to go back to older versions.
+> Interest in website development is picking up because it really is simple to do in GitHub, and the information can be maintained by several people (i.e., a lab group).
 
-Comments to the Corresponding Author
+#### Detailed comments:
 
-The manuscript presents how ecologists and evolutionary biologists (EEB) can use collaborative software development project management tools.
-The authors present a high-level view of Github and the Git version control system that is at its core.
-As the authors detail, the tools that Github provides has broad potential to be leveraged within the EEB community.
-The paper is well written and helps to make Github tools and related concepts legible to EEB audiences.
-On the whole, I see this as potentially being an impactful paper for improving EEB research.
-I have the following Major and Minor comments for the authors:
+**R1.5**
 
-Major Comments
+> Line 346 delete second 'can': who can also can change through time
 
-**R2.1.** Figure 1 was more confusing to me than helpful.
-It presents a view of a Github interface in order to detail generalized features; however, it is edited/abstracted so much that it doesn't map easily to the interface as it would be viewed by a reader of the paper.
-To improve this I would reduce the level of abstraction of the web interface.
+Corrected!
+Thank you for catching this!
 
-**R2.2.** Figure 2 was useful, especially as it summarized across multiple areas that a reader make in-roads into using Github.
-Please clarify how the "Technical Difficulty" was assessed.
-Was this based on the impression of the working group?
-Was it quantified using different types of required knowledge (e.g., programming, software design, working in the Terminal, etc.)?
+**R1.6**
 
-**R2.3.** I would find it helpful to give a brief (1-2 sentence) history of Git (L85-89).
-Namely, that it was developed as an aid for software development within distributed groups of software engineers and was developed within an open-source framework so that it could be improved by the community.
-This provides more context as to why Github (as it extends Git) is a useful tool for collaboration "by design".
+> Line 389 it should be 'each other's work': contribute to each other work without necessarily
+
+Corrected!
+Thank you once again!
+
+**R1.7**
+
+> Line 457 missing 'collaborator'?
+> especially when many may be
+
+We have added "prospective users" to this sentence.
+It now is "*It can be challenging to learn Git alongside scripting languages, statistical theory, and file system navigation, especially when many prospective users may be inexperienced with programming."*
+
+**R1.8**
+
+> Line 477: not sure what this sentence is saying: 'requiring the complementation of other tools to fully integration project files and GitHub repositories'
+
+We agree that this sentence needed clarification.
+We have simplified it and it reads now as: "*Moreover, additional tools may be required to fully integrate project files and GitHub repositories \[...\]*".
+Thank you once again!
+
+## Reviewer: 2 {#sec-R2}
+
+> The manuscript presents how ecologists and evolutionary biologists (EEB) can use collaborative software development project management tools.
+> The authors present a high-level view of Github and the Git version control system that is at its core.
+> As the authors detail, the tools that Github provides has broad potential to be leveraged within the EEB community.
+> The paper is well written and helps to make Github tools and related concepts legible to EEB audiences.
+> On the whole, I see this as potentially being an impactful paper for improving EEB research.
+> I have the following Major and Minor comments for the authors:
+
+#### Figure 1 was more confusing to me than helpful (R2.1) {#sec-R2.1}
+
+> Figure 1 was more confusing to me than helpful.
+> It presents a view of a Github interface in order to detail generalized features; however, it is edited/abstracted so much that it doesn't map easily to the interface as it would be viewed by a reader of the paper.
+> To improve this I would reduce the level of abstraction of the web interface.
+
+#### Improve Figure 2 (R2.2) {#sec-R2.2}
+
+> Figure 2 was useful, especially as it summarized across multiple areas that a reader make in-roads into using Github.
+> Please clarify how the "Technical Difficulty" was assessed.
+> Was this based on the impression of the working group?
+> Was it quantified using different types of required knowledge (e.g., programming, software design, working in the Terminal, etc.)?
+
+#### Add brief history of git (R2.3) {#sec-R2.3}
+
+> I would find it helpful to give a brief (1-2 sentence) history of Git (L85-89).
+> Namely, that it was developed as an aid for software development within distributed groups of software engineers and was developed within an open-source framework so that it could be improved by the community.
+> This provides more context as to why Github (as it extends Git) is a useful tool for collaboration "by design".
 
@@
 
-**R2.4.** I suggest adding a discussion on dependency testing within or following the paragraph on Automation (Lines 373-382).
-This is a project "ecosystem" phenomenon that comes from collaboration, where you build your project on the work of someone else.
-As projects change over time, they can alter other projects.
-Software engineers have been working on this challenge for a long time in distributed teams where different parts of software are being built by different programmers.
-Checks can be done automatically within the software engineering framework (see Pasquier et al.
-2017 <https://www.nature.com/articles/sdata2017114>).
-Beyond detection, any major changes can be detected and presented without additional work from the user via features like badges (<https://shields.io/>) within the project page (e.g., README).
+#### Additions to Automation use case (R2.4) {#sec-R2.4}
 
-**R2.5.** Related to Major Comments 1 and 4, given that the focus of the paper is toward integration into EEB scientific research workflows, I suggest adding another figure (or replacing Figure 1) that details a generalized scientific research workflow (e.g., Munafò et al.
+> I suggest adding a discussion on dependency testing within or following the paragraph on Automation (Lines 373-382).
+> This is a project "ecosystem" phenomenon that comes from collaboration, where you build your project on the work of someone else.
+> As projects change over time, they can alter other projects.
+> Software engineers have been working on this challenge for a long time in distributed teams where different parts of software are being built by different programmers.
+> Checks can be done automatically within the software engineering framework (see Pasquier et al. 2017 <https://www.nature.com/articles/sdata2017114>).
+> Beyond detection, any major changes can be detected and presented without additional work from the user via features like badges (<https://shields.io/>) within the project page (e.g., README).
+
+#### Figure detailing general scientific workflow (R2.5) {#sec-R2.5}
+
+> Related to Major Comments 1 and 4, given that the focus of the paper is toward integration into EEB scientific research workflows, I suggest adding another figure (or replacing Figure 1) that details a generalized scientific research workflow (e.g., Munafò et al.
 2017 <https://www.nature.com/articles/s41562-016-0021>) and how Github supports/augments that workflow.
-This could relate to or build on Table 2, which a useful summarization of important features as they relate to different research participants.
+> This could relate to or build on Table 2, which a useful summarization of important features as they relate to different research participants.
 
-Minor Comments
+#### Minor Comments
 
-**R2.6.** The sentence from Line 66-67 is missing a close parenthesis.
+**R2.6**
 
-**R2.7.** There appears to be a "fourth" barrier at Line 478.
-I suggest splitting the paragraph from Line 472 to 483 into two paragraphs and expanding on both "reluctance to share data" and "language-specific resources" as barriers to adoption.
+> The sentence from Line 66-67 is missing a close parenthesis.
 
-**R2.8.** Line 570 "could also be e" should be "could also be a".
+Thank you for catching this.
+We closed the brackets.
+
+**R2.7**
+
+> There appears to be a "fourth" barrier at Line 478.
+> I suggest splitting the paragraph from Line 472 to 483 into two paragraphs and expanding on both "reluctance to share data" and "language-specific resources" as barriers to adoption.
+
+Indeed!
+We have numbered all five barriers to using GitHub to clarify this section.
+
+**R2.8**
+
+> Line 570 "could also be e" should be "could also be a".
+
+You are right!
+We have corrected this issue.
+Thank you once again!

### 2023-01-03 editorial-communication/response-to-the-reviewers.Qmd
add responses to editor comments

@@
 
+1.  <!--# TODO: edit once sections get merged -->we reduced number of sections. See also our response to reviewer 1 (@sec-R1.1
+
+We have also reduced the amount of jargon repeated throughout the use cases by adding a paragraph in the introduction <!--# add line numbers --> that describes a basic git/GitHub workflow and directs readers to other sources for learning the more technical aspects.
+This allows us to be more concise in the use case sections.
+See also our response to reviewer 1 (@sec-R1.1 and @sec-R1.2).
+Use of the GitHub desktop app and RStudio as GUI interfaces for git is discussed in Box 1 of our manuscript and also in our introduction <!--# add line numbers -->.
+We believe that these mentions, combined with reduction of git jargon and directing readers to additional sources to learn git and GitHub, is sufficient to address this comment.
+
 #### Address private repos (E1.2) {#sec-E1.2}
@@
 We now directly discuss the possibility of keeping repositories private in the section "Storing and sharing research compendia" and in the "Open science discussion" to emphasize that there is not necessarily a trade-off between privacy, collaboration, and open science practices.
+
+<!--# TODO: check that this response still makes sense after merging use case sections -->
 
@@
 
+This is a great point.
+We have added the following sentences to the end of the "Why aren't more EEB researchers using GitHub" section <!--# add line numbers -->:
+
+> Other scientists may simply lack the time or incentives to document and version control their code if the code is unlikely to be reused beyond their analysis.
+> However we (and others, \_e.g.,\_ \[\@doi:10.1098/rspb.2022.1113\]) argue that the endeavour of open science and collaboration requires code owners to document and version control code despite uncertainty around future use.
+
+<!--# TODO: replace DOI above with rendered citation? -->
+
 #### Discuss Overleaf integration (E1.4) {#sec-E1.4}
@@
 
-We now discuss the possibility of integrating GitHub into existing workflows on Overleaf, Google Drive, and DropBox among others to collaboratively write scientific manuscripts, in the section "Writing a manuscript".
+We now discuss the possibility of integrating GitHub into existing workflows on Overleaf, Google Drive, and DropBox among others to collaboratively write scientific manuscripts, in the section "Writing a manuscript" <!--# add line numbers -->.
 We refer to Table 1 for further details on these integrations.
@@
 
+We think this is a good point since many readers may not immediately see the value in a time investment to learn a new tool when they are comfortable with tools that meet many or most of their needs.
+Rather than create a new section, we opted to identnify specific points in the manuscript where we could directly call out where GitHub as a platform enables greater or different types of collaboration and open science than platforms like dropbox or google.
+Due to these edits (below) we now more often refer to table 1, and earlier in the manuscript as well.\
+
+\
+In the first paragraph of the introduction we made the text more concise throughout and also added new sentence <!--# add line number -->:
+
+> Of all these tools, GitHub is uniquely positioned (Table 1) to benefit scientists because the platform is designed to enable collaboration on computer code\--a fundamental component of modern research.
+
+In the second paragraph we added <!--# add line number -->:
+
+> Additionally, unlike sharing documents and code via DropBox or Google Drive links, GitHub defaults to public sharing of code and documents and has features like Issues and Discussions (see [Box 1](https://github.com/SORTEE-Github-Hackathon/manuscript/issues/291#definitions)) that can immediately and directly contribute to more open science and knowledge sharing.
+
+Under the "storing a research compendium section" we added <!--# add line number -->:
+
+> While some EEB researchers may prefer to store their code in Google Drive or DropBox, the process of sharing code through these services becomes cumbersome when collaborators have to download and re-upload edited code.\
+>
+> On GitHub, code is by default public, and the process of forking and submitting pull requests (see [Box 1](https://github.com/SORTEE-Github-Hackathon/manuscript/issues/291#definitions)) ensures a code owner has full control over code and documents in a repository.
+
+In the first paragraph of discussion we added <!--# add line number -->:
+
+> While tools like the Google Suite and DropBox enable rapid sharing and collaboration of some research documents, GitHub brings together features that directly address open science such as tools for soliciting public discussions on code and findings, tracking multiple rounds of edits to files in a sensible way for easy review, and managing complex research projects with many collaborators and goals.
+
+And finally, in the discussion, under "why aren't more EEB researchers using github", we added <!--# add line number -->:
+
+> And with institutional availability of software licenses for tools like the Google Suite or Microsoft Office, researchers may be hesitant to spend valuable time learning another tool.
+
 ## Reviewer 1 {#sec-R1}
@@
 
-#### Reduce repetition (R1.1) {#sec-R1.1}
+#### Reduce repetition and number of use cases (R1.1) {#sec-R1.1}
 

### 2023-01-03 editorial-communication/response-to-the-reviewers.Qmd
Edits to reviewer 1 comments

@@
 
+As mentioned above (\@sec-R1.1, @sec-E1.1), we were able to reduce jargon by making it clear in the introduction that our aim was not to *teach* the use of git and GitHub, and by discussing a basic git workflow early on.
+
 #### Define use-cases in terms of return on investment (R1.3) {#sec-R1.3}
@@
 
--   return on investment is subjective
--   E.g.
-all co-authors on this paper used GitHub to collectively write a manuscript (i.e.
-the one being reviewed), and for us it was an excellent return on investment, but not all co-authors have experience in the other use-cases we present and may find them more or less useful depending on their needs.
--   figure 2 quantifies investment already
--   However, we have taken the advice in other comments (CROSS_REFS) to combine and re-order sections somewhat.
-Hopefully we present the smaller number of cases in a way that better captures the needs of a majority of our readers.
+We appreciate this comment and while we do agree that ordering the use cases by value to the reader would be ideal, we believe that value or return on investment is subjective and varies among fields, labs, and individuals.
+For example, the reviewer sees collaborative writing of a manuscript using GitHub as an "out of the question" advanced use.
+However, all of the co-authors on this manuscript have done exactly this and found it an excellent return on investment.
+At the same time, not all co-authors have experience in many of the other use cases we present and may find them less useful depending on their needs.
+We do make an attempt to quantify the investment effort in Figure 2 already.
+We've added a supplemental document better explaining *how* we made these quantifications (see also our response to reviewer 2 @sec-R2.2).
+However, we have taken the advice of reviewer 1 in other comments (\@sec-R1.4, @sec-R1.1) to reduce the number of use cases and re-order them.
 
@@
 
-We now briefly discuss the origin of Git and its expansion to applications beyond software development to help manage collaborations and community contributions, in the introduction.
+We now briefly discuss the origin of Git and its expansion to applications beyond software development to help manage collaborations and community contributions, in the introduction <!--# add line numbers -->.
 

### 2023-01-03 editorial-communication/response-to-the-reviewers.Qmd
add section numbers, fix cross-refs, remove some links

@@
     embed-resources: true
+    number-sections: true
 ---
@@
 
-1.  <!--# TODO: edit once sections get merged -->we reduced number of sections. See also our response to reviewer 1 (@sec-R1.1
+1.  <!--# TODO: edit once sections get merged -->
+
+    we reduced number of sections.
+    See also our response to reviewer 1 (@sec-R1.1
 
@@
 
-> Additionally, unlike sharing documents and code via DropBox or Google Drive links, GitHub defaults to public sharing of code and documents and has features like Issues and Discussions (see [Box 1](https://github.com/SORTEE-Github-Hackathon/manuscript/issues/291#definitions)) that can immediately and directly contribute to more open science and knowledge sharing.
+> Additionally, unlike sharing documents and code via DropBox or Google Drive links, GitHub defaults to public sharing of code and documents and has features like Issues and Discussions (see Box 1) that can immediately and directly contribute to more open science and knowledge sharing.
 
@@
 >
-> On GitHub, code is by default public, and the process of forking and submitting pull requests (see [Box 1](https://github.com/SORTEE-Github-Hackathon/manuscript/issues/291#definitions)) ensures a code owner has full control over code and documents in a repository.
+> On GitHub, code is by default public, and the process of forking and submitting pull requests (see Box 1) ensures a code owner has full control over code and documents in a repository.
 
@@
 
-In order to reduce repetition and jargon in the use cases sections, we've added a paragraph to the introduction \[L\_\_ -L\_\_\] explaining a basic git & GitHub workflow and pointing the reader to other resources for learning these tools.
+In order to reduce repetition and jargon in the use cases sections, we've added a paragraph to the introduction <!--# add line numbers --> explaining a basic git & GitHub workflow and pointing the reader to other resources for learning these tools.
 This allows us to focus less on explaining the specific mechanisms of git/Github in the use cases sections and more on the usefulness of the tools.
@@
 
-As mentioned above (\@sec-R1.1, @sec-E1.1), we were able to reduce jargon by making it clear in the introduction that our aim was not to *teach* the use of git and GitHub, and by discussing a basic git workflow early on.
+As mentioned above (@sec-R1.1, @sec-E1.1), we were able to reduce jargon by making it clear in the introduction that our aim was not to *teach* the use of git and GitHub, and by discussing a basic git workflow early on.
 
@@
 We've added a supplemental document better explaining *how* we made these quantifications (see also our response to reviewer 2 @sec-R2.2).
-However, we have taken the advice of reviewer 1 in other comments (\@sec-R1.4, @sec-R1.1) to reduce the number of use cases and re-order them.
+However, we have taken the advice of reviewer 1 in other comments (@sec-R1.4, @sec-R1.1) to reduce the number of use cases and re-order them.
 

### 2023-01-03 editorial-communication/cover-letter-submission.Qmd
convert cover-letter to Qmd too

--- 2022-10-27 editorial-communication/cover-letter-submission.Rmd
@@
 date: "Last compiled on `r format(Sys.time(), '%d %B, %Y')`"
-output:
-  html_document:
+format:
+  html:
     theme: cosmo 
-    highlight: tango
-    self_contained: true
+    highlight-style: tango
+    embed-resources: true
 ---

### 2023-01-03 editorial-communication/cover-letter-submission.Qmd
remove R code from yaml headers

@@
 title: Letter to the Editor
-author: "Not just for programmers: How GitHub can accelerate collaborative and reproducible research in ecology and evolution"
-date: "Last compiled on `r format(Sys.time(), '%d %B, %Y')`"
+subtitle: "Not just for programmers: How GitHub can accelerate collaborative and reproducible research in ecology and evolution"
+date: today
+date-format: long
 format:

### 2023-01-03 editorial-communication/response-to-the-reviewers.Qmd
Deploying to gh-pages from @ SORTEE-Github-Hackathon/manuscript@b63ae1040957ab068bf6be985d7bdebde1322e56 🚀

@@
 title: "Response to the reviewers"
-date: "Last compiled on `r format(Sys.time(), '%d %B, %Y')`"
+date: today
+date-format: long
 format:

### 2023-01-03 editorial-communication/response-to-the-reviewers.Qmd
add reference docx

@@
 format:
+  docx: 
+    reference-doc: response-template.docx
   html:

### 2023-01-22 editorial-communication/response-to-the-reviewers.Qmd
Clarifying and simplifying the layout for the response letter
- Removes titles (which are more informative to us than to the editor and the reviewers);
- Convert recommendations to level 5 headers, and sets the cross references to them. This solves the problem that Markdown quotes `>` were being used for both comments from peer reviewers and to quote changes we made to the text;
- Mirror indent our responses with div tags;
- Justify all text;
- Temporarily removes .docx rendering until document is ready;
- Adds an Rproj. file that is important to allow the Quarto document to be previewed.

--- 2023-01-03 editorial-communication/response-to-the-reviewers.Qmd
@@
 date-format: long
+number-sections: false
 format: 
@@
     embed-resources: true
-    number-sections: true
 ---
 
-## Editor {#sec-E1}
+<div style="text-align: justify">
 
-> As a long-term but sporadic GitHub user myself, I agree with most of the points and cases presented in the paper.
+Dear Dr. XXX,
 
-#### Streamline use cases (E1.1) {#sec-E1.1}
+We would like to thank you and the reviewers for the thoughtful comments and for the opportunity to submit a revised version of our manuscript "", for consideration for publication in Methods in Ecology and Evolution.
 
-> I agree with Reviewer 1 that these could be streamlined somewhat into a smaller number of more generalizable cases.
-> They also are a bit heavily weighted towards more experienced users.
-> "Simple" operations like push, pull, and commit are rarely understandable to new users, who routinely forget to commit their actions.
-> The GitHub Desktop app makes many of the operations and use of GitHub somewhat easier, and is a good entree into GitHub and Git for novices.
-> More could be made of the desktop app.
+We have addressed all the suggestions that you and the reviewers provided and, as before, we provide a point-by-point detailed response discussing each comment or suggestion.
+Our responses are mirror-indented and written in black, while the editor's and reviewers' comments are numbered and highlighted in color.
+To facilitate the review, we have also included indented extracts from the text, highlighting the changes we made in orange.
+The line numbers in our responses correspond to those in the revised manuscript.
 
-1.  <!--# TODO: edit once sections get merged -->
+We have rewritten several sentences to improve their clarity, decrease the complexity and length of sections, and improved the readability of figures.
 
-    we reduced number of sections.
-    See also our response to reviewer 1 (@sec-R1.1
+### Comments from the Editor (E1) {#sec-E1}
+
+##### As a long-term but sporadic GitHub user myself, I agree with most of the points and cases presented in the paper.
+
+##### **E1.1.** I agree with Reviewer 1 that these could be streamlined somewhat into a smaller number of more generalizable cases.
+They also are a bit heavily weighted towards more experienced users.
+"Simple" operations like push, pull, and commit are rarely understandable to new users, who routinely forget to commit their actions.
+The GitHub Desktop app makes many of the operations and use of GitHub somewhat easier, and is a good entree into GitHub and Git for novices.
+More could be made of the desktop app.
+{#sec-E1.1}
+
+**Response**:
+
+::: {#ResponseE11 style="width: 85%;   margin-left: auto;   margin-right: auto;"}
+<!--# TODO: edit once sections get merged -->
+
+1.  we reduced number of sections. See also our response to reviewer 1 (@sec-R1.1
 
@@
 We believe that these mentions, combined with reduction of git jargon and directing readers to additional sources to learn git and GitHub, is sufficient to address this comment.
+:::
 
-#### Address private repos (E1.2) {#sec-E1.2}
+##### **E1.2.** In my own experience, the "public" nature of repos is a major barrier to the use of GitHub for exactly the reason you suggest - EEB practioners remain very uncomfortable with sharing data pre-publication (and often even post-publication).
+Some additional emphasis on the ability to make repos "private" should be included beyond the Boxes.
+{#sec-E1.2}
 
-> In my own experience, the "public" nature of repos is a major barrier to the use of GitHub for exactly the reason you suggest - EEB practioners remain very uncomfortable with sharing data pre-publication (and often even post-publication).
-> Some additional emphasis on the ability to make repos "private" should be included beyond the Boxes.
-
+::: {#ResponseE12 style="width: 85%;   margin-left: auto;   margin-right: auto;"}
 We now directly discuss the possibility of keeping repositories private in the section "Storing and sharing research compendia" and in the "Open science discussion" to emphasize that there is not necessarily a trade-off between privacy, collaboration, and open science practices.
@@
 
-#### Discuss documentation of single-purpose scripts (E1.3) {#sec-E1.3}
+:::
 
-> Another reason that many EEBers don't use GitHub appears to be related to how we develop code for projects.
-> Unless we are developing packages that others are likely to use, we tend to develop one-off scripts or functions that, once they work and are run, are never returned to.
-> Version control is not used widely, or even needed in these cases (and my own work in software engineering provenance software has similarly had little uptake for the same reasons).
-> I recognize that this makes it difficult to document the processes involved, but if the goal is simply to analyze the data at hand and push out another paper, why deal with the overhead of version control?
-> At root, this is a sociological phenomenon, not a scientific one.
-> Within your ms., consider saying something about how even one-off scripts may need to be documented, archived, and assigned a DOI to conform to evolving archiving requirements of journals.
+##### **E1.3.** Another reason that many EEBers don't use GitHub appears to be related to how we develop code for projects.
+Unless we are developing packages that others are likely to use, we tend to develop one-off scripts or functions that, once they work and are run, are never returned to.
+Version control is not used widely, or even needed in these cases (and my own work in software engineering provenance software has similarly had little uptake for the same reasons).
+I recognize that this makes it difficult to document the processes involved, but if the goal is simply to analyze the data at hand and push out another paper, why deal with the overhead of version control?
+At root, this is a sociological phenomenon, not a scientific one.
+Within your ms., consider saying something about how even one-off scripts may need to be documented, archived, and assigned a DOI to conform to evolving archiving requirements of journals.
+{#sec-E1.3}
 
-This is a great point.
-We have added the following sentences to the end of the "Why aren't more EEB researchers using GitHub" section <!--# add line numbers -->:
+::: {#ResponseE13 style="width: 85%;   margin-left: auto;   margin-right: auto;"}
+
+This is a great point. We have added the following sentences to the end of the "Why aren't more EEB researchers using GitHub" section <!--# add line numbers -->:
 
 > Other scientists may simply lack the time or incentives to document and version control their code if the code is unlikely to be reused beyond their analysis.
-> However we (and others, \_e.g.,\_ \[\@doi:10.1098/rspb.2022.1113\]) argue that the endeavour of open science and collaboration requires code owners to document and version control code despite uncertainty around future use.
+However we (and others, \_e.g.,\_ \[\@doi:10.1098/rspb.2022.1113\]) argue that the endeavour of open science and collaboration requires code owners to document and version control code despite uncertainty around future use.
 
@@
 
-#### Discuss Overleaf integration (E1.4) {#sec-E1.4}
+:::
 
-> I am surprised you didn't include integration between GitHub and Overleaf.
-> Overleaf is also a good collaborative latex-based text processor, and provides syncing with GitHub (and Dropbox) in a way that will be more familiar to beginning users.
-> (Actually, I eventually found it buried in Table 1)
+#### **E1.4.** I am surprised you didn't include integration between GitHub and Overleaf.
+Overleaf is also a good collaborative latex-based text processor, and provides syncing with GitHub (and Dropbox) in a way that will be more familiar to beginning users.
+(Actually, I eventually found it buried in Table 1) {#sec-E1.4}
+
+::: {#ResponseE14 style="width: 85%;   margin-left: auto;   margin-right: auto;"}
 
@@
 
-#### Improve discussion of GitHub advantages over other existing file-sharing tools (E1.5.) {#sec-E1.5}
+:::
 
-> Finally, DropBox, SharePoint, and OneDrive are file-sharing systems that include version control, are widely supported, especially in colleges and universities, and are much easier to use for those who might be uncomfortable learning a system such as GitHub.
-> Other than the ability to clone and fork, why should one choose GitHub over, for example, DropBox or SharePoint?
-> More should be made of this in text, as opposed to burying it in Table 1, which is referenced only once in text (line 232) and only in the context of other longterm archives (line 231).
-> Indeed, I suggest a somewhat expanded section of the ms. dedicated to a detailed exploration of the comparisons made in this Table.
-> Otherwise, the ms. comes across as more proselytizing and less analytical/convincing.
+##### **E1.5.** Finally, DropBox, SharePoint, and OneDrive are file-sharing systems that include version control, are widely supported, especially in colleges and universities, and are much easier to use for those who might be uncomfortable learning a system such as GitHub.
+Other than the ability to clone and fork, why should one choose GitHub over, for example, DropBox or SharePoint?
+More should be made of this in text, as opposed to burying it in Table 1, which is referenced only once in text (line 232) and only in the context of other longterm archives (line 231).
+Indeed, I suggest a somewhat expanded section of the ms.
+dedicated to a detailed exploration of the comparisons made in this Table.
+Otherwise, the ms.
+comes across as more proselytizing and less analytical/convincing.
+{#sec-E1.5}
+
+::: {#ResponseE15 style="width: 85%;   margin-left: auto;   margin-right: auto;"}
 
 We think this is a good point since many readers may not immediately see the value in a time investment to learn a new tool when they are comfortable with tools that meet many or most of their needs.
-Rather than create a new section, we opted to identnify specific points in the manuscript where we could directly call out where GitHub as a platform enables greater or different types of collaboration and open science than platforms like dropbox or google.
+Rather than create a new section, we opted to identify specific points in the manuscript where we could directly call out where GitHub as a platform enables greater or different types of collaboration and open science than platforms like Dropbox or Google.
 Due to these edits (below) we now more often refer to table 1, and earlier in the manuscript as well.\
@@
 
-## Reviewer 1 {#sec-R1}
+:::
 
-> This paper clearly communicates the enthusiasm of the authors for integrating GitHub in the EEB research process.
-> Advantages in areas of collaboration, transparent and reproducible science are clear and nicely discussed.
-> This is a well written paper.
+### Recommendations from Reviewer 1 (R1) {#sec-R1}
 
-#### Reduce repetition and number of use cases (R1.1) {#sec-R1.1}
+##### This paper clearly communicates the enthusiasm of the authors for integrating GitHub in the EEB research process.
+Advantages in areas of collaboration, transparent and reproducible science are clear and nicely discussed.
+This is a well written paper.
 
-> I would, however, recommend some restructuring and shortening.
-> As it stands, this paper is too long and some of the use cases are too nerdy to spark enthusiasm in somebody who is not already using GitHub.
-> Breaking it into 13 use cases leads to some repetition and those use cases may be combined more effectively for convincing a new user.
+##### **R1.1.** I would, however, recommend some restructuring and shortening.
+As it stands, this paper is too long and some of the use cases are too nerdy to spark enthusiasm in somebody who is not already using GitHub.
+Breaking it into 13 use cases leads to some repetition and those use cases may be combined more effectively for convincing a new user.
+{#sec-R1.1}
+
+::: {#ResponseR11 style="width: 85%;   margin-left: auto;   margin-right: auto;"}
 
@@
 
-#### Reduce jargon (R1.2) {#sec-R1.2}
+:::
 
-> The title and abstract gave me the impression that the goal is to convince EEB researcher to start using GitHub.
-> If that's the case, it might be better to tailor the use cases to that entry level and use less GitHub specific lingo.
-> Advanced usage may be mentioned but not detailed as much as it is currently done.
-> E.g. collaboratively writing a paper in GitHub is probably out of the question for most.
-> Most GitHub options for communication, discussion, issue tracking are still somewhat esoteric for most non-programmers.
+##### **R1.2.** The title and abstract gave me the impression that the goal is to convince EEB researcher to start using GitHub.
+If that's the case, it might be better to tailor the use cases to that entry level and use less GitHub specific lingo.
+Advanced usage may be mentioned but not detailed as much as it is currently done.
+E.g.
+collaboratively writing a paper in GitHub is probably out of the question for most.
+Most GitHub options for communication, discussion, issue tracking are still somewhat esoteric for most non-programmers.
+{#sec-R1.2}
+
+::: {#ResponseR12 style="width: 85%;   margin-left: auto;   margin-right: auto;"}
 
@@
 
-#### Define use-cases in terms of return on investment (R1.3) {#sec-R1.3}
+:::
 
-> Although the abstract states 'We outline features ranging from low to high technical difficulty' the paper reads a bit like a laundry list of what GitHub can do (in fact, the word 'can' is used about 140 times, which makes for tedious read).
-> Figure 2 helps sort through this laundry list and defines the technical difficulty.
-> It might be better to clearly lay out where anybody can start using GitHub effectively in the text.
-> And the emphasis is on 'effectively'.
-> Most people are not likely to learn a new piece of software if it does not promise to reduce effort and time.
-> So, defining tasks where GitHub shines in terms of return on investment maybe the better approach to convincing new users and then only mention the advance use cases with some pointers to further reading, but not going into too much detail.
+##### **R1.3.** Although the abstract states 'We outline features ranging from low to high technical difficulty' the paper reads a bit like a laundry list of what GitHub can do (in fact, the word 'can' is used about 140 times, which makes for tedious read).
+Figure 2 helps sort through this laundry list and defines the technical difficulty.
+It might be better to clearly lay out where anybody can start using GitHub effectively in the text.
+And the emphasis is on 'effectively'.
+Most people are not likely to learn a new piece of software if it does not promise to reduce effort and time.
+So, defining tasks where GitHub shines in terms of return on investment maybe the better approach to convincing new users and then only mention the advance use cases with some pointers to further reading, but not going into too much detail.
+{#sec-R1.3}
+
+::: {#ResponseR13 style="width: 85%;   margin-left: auto;   margin-right: auto;"}
 
@@
 
-#### Reorder sections based on importance (R1.4) {#sec-R1.4}
+:::
 
-> In my experience, the project continuity is actually very high on the importance list for researchers, i.e., knowing that the code and data will be findable by the next student.
-> This includes the discussion of organizing and managing teams, keeping lab information in one place etc.
-> Followed by code versioning and the ability to go back to older versions.
-> Interest in website development is picking up because it really is simple to do in GitHub, and the information can be maintained by several people (i.e., a lab group).
+##### **R1.4.** In my experience, the project continuity is actually very high on the importance list for researchers, i.e., knowing that the code and data will be findable by the next student.
+This includes the discussion of organizing and managing teams, keeping lab information in one place etc.
+Followed by code versioning and the ability to go back to older versions.
+Interest in website development is picking up because it really is simple to do in GitHub, and the information can be maintained by several people (i.e., a lab group).
+{#sec-R1.4}
 
-#### Detailed comments:
+::: {#ResponseR14 style="width: 85%;   margin-left: auto;   margin-right: auto;"}
 
-**R1.5**
+Response
 
-> Line 346 delete second 'can': who can also can change through time
+:::
 
-Corrected!
-Thank you for catching this!
+##### **R1.5.** Line 346 delete second 'can': who can also can change through time
 
-**R1.6**
+::: {#ResponseR15 style="width: 85%;   margin-left: auto;   margin-right: auto;"}
 
-> Line 389 it should be 'each other's work': contribute to each other work without necessarily
+Corrected! Thank you for catching this!
 
-Corrected!
-Thank you once again!
+:::
 
-**R1.7**
+##### **R1.6.** Line 389 it should be 'each other's work': contribute to each other work without necessarily
 
-> Line 457 missing 'collaborator'?
-> especially when many may be
+::: {#ResponseR16 style="width: 85%;   margin-left: auto;   margin-right: auto;"}
+
+Corrected! Thank you once again!
+
+:::
+
+##### **R1.7.** Line 457 missing 'collaborator'? especially when many may be
+
+::: {#ResponseR17 style="width: 85%;   margin-left: auto;   margin-right: auto;"}
 
@@
 
-**R1.8**
+:::
 
-> Line 477: not sure what this sentence is saying: 'requiring the complementation of other tools to fully integration project files and GitHub repositories'
+##### **R1.8.** Line 477: not sure what this sentence is saying: 'requiring the complementation of other tools to fully integration project files and GitHub repositories'
+
+::: {#ResponseR18 style="width: 85%;   margin-left: auto;   margin-right: auto;"}
 
@@
 
+:::
+
 ## Reviewer: 2 {#sec-R2}
 
-> The manuscript presents how ecologists and evolutionary biologists (EEB) can use collaborative software development project management tools.
-> The authors present a high-level view of Github and the Git version control system that is at its core.
-> As the authors detail, the tools that Github provides has broad potential to be leveraged within the EEB community.
-> The paper is well written and helps to make Github tools and related concepts legible to EEB audiences.
-> On the whole, I see this as potentially being an impactful paper for improving EEB research.
-> I have the following Major and Minor comments for the authors:
+##### The manuscript presents how ecologists and evolutionary biologists (EEB) can use collaborative software development project management tools.
+The authors present a high-level view of Github and the Git version control system that is at its core.
+As the authors detail, the tools that Github provides has broad potential to be leveraged within the EEB community.
+The paper is well written and helps to make Github tools and related concepts legible to EEB audiences.
+On the whole, I see this as potentially being an impactful paper for improving EEB research.
+I have the following Major and Minor comments for the authors:
 
-#### Figure 1 was more confusing to me than helpful (R2.1) {#sec-R2.1}
+##### **R2.1.** Figure 1 was more confusing to me than helpful.
+It presents a view of a Github interface in order to detail generalized features; however, it is edited/abstracted so much that it doesn't map easily to the interface as it would be viewed by a reader of the paper.
+To improve this I would reduce the level of abstraction of the web interface.
+{#sec-R2.1}
 
-> Figure 1 was more confusing to me than helpful.
-> It presents a view of a Github interface in order to detail generalized features; however, it is edited/abstracted so much that it doesn't map easily to the interface as it would be viewed by a reader of the paper.
-> To improve this I would reduce the level of abstraction of the web interface.
+::: {#ResponseR21 style="width: 85%;   margin-left: auto;   margin-right: auto;"}
 
-#### Improve Figure 2 (R2.2) {#sec-R2.2}
+Response
 
-> Figure 2 was useful, especially as it summarized across multiple areas that a reader make in-roads into using Github.
-> Please clarify how the "Technical Difficulty" was assessed.
-> Was this based on the impression of the working group?
-> Was it quantified using different types of required knowledge (e.g., programming, software design, working in the Terminal, etc.)?
+:::
 
-#### Add brief history of git (R2.3) {#sec-R2.3}
+##### **R2.2.** Figure 2 was useful, especially as it summarized across multiple areas that a reader make in-roads into using Github.
+Please clarify how the "Technical Difficulty" was assessed.
+Was this based on the impression of the working group?
+Was it quantified using different types of required knowledge (e.g., programming, software design, working in the Terminal, etc.)?
+{#sec-R2.2}
 
-> I would find it helpful to give a brief (1-2 sentence) history of Git (L85-89).
-> Namely, that it was developed as an aid for software development within distributed groups of software engineers and was developed within an open-source framework so that it could be improved by the community.
-> This provides more context as to why Github (as it extends Git) is a useful tool for collaboration "by design".
+::: {#ResponseR22 style="width: 85%;   margin-left: auto;   margin-right: auto;"}
+
+Response
+
+:::
+
+##### **R2.3.** I would find it helpful to give a brief (1-2 sentence) history of Git (L85-89).
+Namely, that it was developed as an aid for software development within distributed groups of software engineers and was developed within an open-source framework so that it could be improved by the community.
+This provides more context as to why Github (as it extends Git) is a useful tool for collaboration "by design".
+{#sec-R2.3}
+
+::: {#ResponseR23 style="width: 85%;   margin-left: auto;   margin-right: auto;"}
 
@@
 
-#### Additions to Automation use case (R2.4) {#sec-R2.4}
+:::
 
-> I suggest adding a discussion on dependency testing within or following the paragraph on Automation (Lines 373-382).
-> This is a project "ecosystem" phenomenon that comes from collaboration, where you build your project on the work of someone else.
-> As projects change over time, they can alter other projects.
-> Software engineers have been working on this challenge for a long time in distributed teams where different parts of software are being built by different programmers.
-> Checks can be done automatically within the software engineering framework (see Pasquier et al. 2017 <https://www.nature.com/articles/sdata2017114>).
-> Beyond detection, any major changes can be detected and presented without additional work from the user via features like badges (<https://shields.io/>) within the project page (e.g., README).
+##### **R2.4.** I suggest adding a discussion on dependency testing within or following the paragraph on Automation (Lines 373-382).
+This is a project "ecosystem" phenomenon that comes from collaboration, where you build your project on the work of someone else.
+As projects change over time, they can alter other projects.
+Software engineers have been working on this challenge for a long time in distributed teams where different parts of software are being built by different programmers.
+Checks can be done automatically within the software engineering framework (see Pasquier et al.
+2017 <https://www.nature.com/articles/sdata2017114>).
+Beyond detection, any major changes can be detected and presented without additional work from the user via features like badges (<https://shields.io/>) within the project page (e.g., README).
+{#sec-R2.4}
 
-#### Figure detailing general scientific workflow (R2.5) {#sec-R2.5}
+::: {#ResponseR24 style="width: 85%;   margin-left: auto;   margin-right: auto;"}
 
-> Related to Major Comments 1 and 4, given that the focus of the paper is toward integration into EEB scientific research workflows, I suggest adding another figure (or replacing Figure 1) that details a generalized scientific research workflow (e.g., Munafò et al.
+Response
+
+:::
+
+##### **R2.5.** Related to Major Comments 1 and 4, given that the focus of the paper is toward integration into EEB scientific research workflows, I suggest adding another figure (or replacing Figure 1) that details a generalized scientific research workflow (e.g., Munafò et al.
 2017 <https://www.nature.com/articles/s41562-016-0021>) and how Github supports/augments that workflow.
-> This could relate to or build on Table 2, which a useful summarization of important features as they relate to different research participants.
+This could relate to or build on Table 2, which a useful summarization of important features as they relate to different research participants.
+{#sec-R2.5}
 
-#### Minor Comments
+::: {#ResponseR25 style="width: 85%;   margin-left: auto;   margin-right: auto;"}
 
-**R2.6**
+Response
 
-> The sentence from Line 66-67 is missing a close parenthesis.
+:::
 
-Thank you for catching this.
-We closed the brackets.
+##### **R2.6.** The sentence from Line 66-67 is missing a close parenthesis.
 
-**R2.7**
+::: {#ResponseR26 style="width: 85%;   margin-left: auto;   margin-right: auto;"}
 
-> There appears to be a "fourth" barrier at Line 478.
-> I suggest splitting the paragraph from Line 472 to 483 into two paragraphs and expanding on both "reluctance to share data" and "language-specific resources" as barriers to adoption.
+Thank you for catching this. We closed the brackets.
 
-Indeed!
-We have numbered all five barriers to using GitHub to clarify this section.
+:::
 
-**R2.8**
+##### **R2.7.** There appears to be a "fourth" barrier at Line 478.
+I suggest splitting the paragraph from Line 472 to 483 into two paragraphs and expanding on both "reluctance to share data" and "language-specific resources" as barriers to adoption.
 
-> Line 570 "could also be e" should be "could also be a".
+::: {#ResponseR27 style="width: 85%;   margin-left: auto;   margin-right: auto;"}
 
-You are right!
-We have corrected this issue.
-Thank you once again!
+Indeed! We have numbered all five barriers to using GitHub to clarify this section.
+
+:::
+
+##### **R2.8.** Line 570 "could also be e" should be "could also be a".
+
+::: {#ResponseR28 style="width: 85%;   margin-left: auto;   margin-right: auto;"}
+
+You are right! We have corrected this issue. Thank you once again!
+
+:::
+
+</div>

### 2023-01-22 editorial-communication/response-to-the-reviewers.Qmd
Minor changes to sentences.

@@
 We have addressed all the suggestions that you and the reviewers provided and, as before, we provide a point-by-point detailed response discussing each comment or suggestion.
-Our responses are mirror-indented and written in black, while the editor's and reviewers' comments are numbered and highlighted in color.
-To facilitate the review, we have also included indented extracts from the text, highlighting the changes we made in orange.
+Our responses are mirror-indented, while the editor's and reviewers' comments are numbered.
+To facilitate the review, we have also included indented extracts from the text, highlighting the changes we made.
 The line numbers in our responses correspond to those in the revised manuscript.
@@
 We have rewritten several sentences to improve their clarity, decrease the complexity and length of sections, and improved the readability of figures.
+
+[...]
 
@@
 
-**Response**:
-
 ::: {#ResponseE11 style="width: 85%;   margin-left: auto;   margin-right: auto;"}
 <!--# TODO: edit once sections get merged -->
+
+**Response**:
 
@@
 ::: {#ResponseE12 style="width: 85%;   margin-left: auto;   margin-right: auto;"}
-We now directly discuss the possibility of keeping repositories private in the section "Storing and sharing research compendia" and in the "Open science discussion" to emphasize that there is not necessarily a trade-off between privacy, collaboration, and open science practices.
+
+Thank you for this suggestion!
+We now added a discussion on how repositories can be kept private to  the section "Storing and sharing research compendia" (between lines XXX and XXX) and in the "Open science discussion" (between lines XXX and XXX).
+We emphasize that there should not be a trade-off between privacy, collaboration, and open science practices.
 
@@
 
-We now discuss the possibility of integrating GitHub into existing workflows on Overleaf, Google Drive, and DropBox among others to collaboratively write scientific manuscripts, in the section "Writing a manuscript" <!--# add line numbers -->.
+Thank you for this recommendation!
+We now discuss the possibility of integrating GitHub into existing workflows on Overleaf, Google Drive, and DropBox among other services to collaboratively write scientific manuscripts, in the section "Writing a manuscript" <!--# add line numbers -->.
 We refer to Table 1 for further details on these integrations.
@@
 We think this is a good point since many readers may not immediately see the value in a time investment to learn a new tool when they are comfortable with tools that meet many or most of their needs.
-Rather than create a new section, we opted to identify specific points in the manuscript where we could directly call out where GitHub as a platform enables greater or different types of collaboration and open science than platforms like Dropbox or Google.
+Rather than creating a new section, we identify specific points in the manuscript where we could directly call out where GitHub as a platform enables greater or different types of collaboration and open science than platforms like Dropbox or Google.
 Due to these edits (below) we now more often refer to table 1, and earlier in the manuscript as well.\
@@
 
-And finally, in the discussion, under "why aren't more EEB researchers using github", we added <!--# add line number -->:
+And finally, in the discussion, under "Why aren't more EEB researchers using Github", we added <!--# add line number -->:
 

### 2023-01-23 editorial-communication/response-to-the-reviewers.Qmd
Simplifying responses to E1.1. and E1.2.

@@
 ::: {#ResponseE11 style="width: 85%;   margin-left: auto;   margin-right: auto;"}
+
 <!--# TODO: edit once sections get merged -->
 
-**Response**:
+**Response**: Thank you for these comments. We agree that the use cases and the jargon could be simplified to make the text more readable and attractive. 
+Too address these recommendations, we: (1) added a brief paragraph in the introduction describing basic Git and Github workflows, directing readers to other references containing more technical and in-depth information about these platforms;
+(2) decreased the number of use cases (see [response to R1.1.](@sec-R1.1.) and [response to R1.2.](@sec-R1.2));
+(3) added information on how GitHub Desktop and RStudio can be used as GUI interfaces for Git into Box 1 and into the Introduction (between lines XXX and XXX).
 
-1.  we reduced number of sections. See also our response to reviewer 1 (@sec-R1.1
-
-We have also reduced the amount of jargon repeated throughout the use cases by adding a paragraph in the introduction <!--# add line numbers --> that describes a basic git/GitHub workflow and directs readers to other sources for learning the more technical aspects.
-This allows us to be more concise in the use case sections.
-See also our response to reviewer 1 (@sec-R1.1 and @sec-R1.2).
-Use of the GitHub desktop app and RStudio as GUI interfaces for git is discussed in Box 1 of our manuscript and also in our introduction <!--# add line numbers -->.
-We believe that these mentions, combined with reduction of git jargon and directing readers to additional sources to learn git and GitHub, is sufficient to address this comment.
 :::
@@
 
-Thank you for this suggestion!
-We now added a discussion on how repositories can be kept private to  the section "Storing and sharing research compendia" (between lines XXX and XXX) and in the "Open science discussion" (between lines XXX and XXX).
+**Response**: Thank you for this suggestion!
+We added a discussion on how repositories can be kept private to the section "Storing and sharing research compendia" (between lines XXX and XXX) and in the "Open science discussion" (between lines XXX and XXX).
 We emphasize that there should not be a trade-off between privacy, collaboration, and open science practices.

### 2023-01-24 editorial-communication/response-to-the-reviewers.Qmd
use css chunk to define class for responses

@@
     embed-resources: true
+  docx: 
+    reference-doc: "response-template.docx"
+  pdf: default
 ---
 
-<div style="text-align: justify">
+```{css}
+.response {
+  width: 85%;
+  margin-left: auto;
+  margin-right: auto;
+}
+```
 
+::: {style="text-align: justify"}
 Dear Dr. XXX,
@@
 
-[...]
+\[...\]
 
@@
 
-::: {#ResponseE11 style="width: 85%;   margin-left: auto;   margin-right: auto;"}
-
+::: {#ResponseE11 .response}
 <!--# TODO: edit once sections get merged -->
 
-**Response**: Thank you for these comments. We agree that the use cases and the jargon could be simplified to make the text more readable and attractive. 
-Too address these recommendations, we: (1) added a brief paragraph in the introduction describing basic Git and Github workflows, directing readers to other references containing more technical and in-depth information about these platforms;
-(2) decreased the number of use cases (see [response to R1.1.](@sec-R1.1.) and [response to R1.2.](@sec-R1.2));
-(3) added information on how GitHub Desktop and RStudio can be used as GUI interfaces for Git into Box 1 and into the Introduction (between lines XXX and XXX).
-
+**Response**: Thank you for these comments.
+We agree that the use cases and the jargon could be simplified to make the text more readable and attractive.
+Too address these recommendations, we: (1) added a brief paragraph in the introduction describing basic Git and Github workflows, directing readers to other references containing more technical and in-depth information about these platforms; (2) decreased the number of use cases (see [response to R1.1.](@sec-R1.1.) and [response to R1.2.](@sec-R1.2)); (3) added information on how GitHub Desktop and RStudio can be used as GUI interfaces for Git into Box 1 and into the Introduction (between lines XXX and XXX).
 :::
@@
 
-::: {#ResponseE12 style="width: 85%;   margin-left: auto;   margin-right: auto;"}
-
+::: {#ResponseE12 .response}
 **Response**: Thank you for this suggestion!
@@
 <!--# TODO: check that this response still makes sense after merging use case sections -->
-
 :::
@@
 
-::: {#ResponseE13 style="width: 85%;   margin-left: auto;   margin-right: auto;"}
-
-This is a great point. We have added the following sentences to the end of the "Why aren't more EEB researchers using GitHub" section <!--# add line numbers -->:
+::: {#ResponseE13 .response}
+This is a great point.
+We have added the following sentences to the end of the "Why aren't more EEB researchers using GitHub" section <!--# add line numbers -->:
 
 > Other scientists may simply lack the time or incentives to document and version control their code if the code is unlikely to be reused beyond their analysis.
-However we (and others, \_e.g.,\_ \[\@doi:10.1098/rspb.2022.1113\]) argue that the endeavour of open science and collaboration requires code owners to document and version control code despite uncertainty around future use.
+> However we (and others, \_e.g.,\_ \[\@doi:10.1098/rspb.2022.1113\]) argue that the endeavour of open science and collaboration requires code owners to document and version control code despite uncertainty around future use.
 
 <!--# TODO: replace DOI above with rendered citation? -->
-
 :::
@@
 
-::: {#ResponseE14 style="width: 85%;   margin-left: auto;   margin-right: auto;"}
-
+::: {#ResponseE14 .response}
 Thank you for this recommendation!
@@
 We refer to Table 1 for further details on these integrations.
-
 :::
@@
 
-::: {#ResponseE15 style="width: 85%;   margin-left: auto;   margin-right: auto;"}
-
+::: {#ResponseE15 .response}
 We think this is a good point since many readers may not immediately see the value in a time investment to learn a new tool when they are comfortable with tools that meet many or most of their needs.
@@
 > And with institutional availability of software licenses for tools like the Google Suite or Microsoft Office, researchers may be hesitant to spend valuable time learning another tool.
-
 :::
@@
 
-::: {#ResponseR11 style="width: 85%;   margin-left: auto;   margin-right: auto;"}
-
+::: {#ResponseR11 .response}
 In order to reduce repetition and jargon in the use cases sections, we've added a paragraph to the introduction <!--# add line numbers --> explaining a basic git & GitHub workflow and pointing the reader to other resources for learning these tools.
@@
 In regards to the specific suggestion about deprioritizing GitHub communication tools, we believe these are extremely useful alternatives to reply-all email chains for a variety of reasons and have attempted to improve the clarity of this section of our manuscript \[end of project management section\].
-
 :::
@@
 
-::: {#ResponseR12 style="width: 85%;   margin-left: auto;   margin-right: auto;"}
-
+::: {#ResponseR12 .response}
 As mentioned above (@sec-R1.1, @sec-E1.1), we were able to reduce jargon by making it clear in the introduction that our aim was not to *teach* the use of git and GitHub, and by discussing a basic git workflow early on.
-
 :::
@@
 
-::: {#ResponseR13 style="width: 85%;   margin-left: auto;   margin-right: auto;"}
-
+::: {#ResponseR13 .response}
 We appreciate this comment and while we do agree that ordering the use cases by value to the reader would be ideal, we believe that value or return on investment is subjective and varies among fields, labs, and individuals.
@@
 However, we have taken the advice of reviewer 1 in other comments (@sec-R1.4, @sec-R1.1) to reduce the number of use cases and re-order them.
-
 :::
@@
 
-::: {#ResponseR14 style="width: 85%;   margin-left: auto;   margin-right: auto;"}
-
+::: {#ResponseR14 .response}
 Response
-
 :::
@@
 
-::: {#ResponseR15 style="width: 85%;   margin-left: auto;   margin-right: auto;"}
-
-Corrected! Thank you for catching this!
-
+::: {#ResponseR15 .response}
+Corrected!
+Thank you for catching this!
 :::
@@
 
-::: {#ResponseR16 style="width: 85%;   margin-left: auto;   margin-right: auto;"}
-
-Corrected! Thank you once again!
-
+::: {#ResponseR16 .response}
+Corrected!
+Thank you once again!
 :::
@@
 
-::: {#ResponseR17 style="width: 85%;   margin-left: auto;   margin-right: auto;"}
-
+::: {#ResponseR17 .response}
 We have added "prospective users" to this sentence.
 It now is "*It can be challenging to learn Git alongside scripting languages, statistical theory, and file system navigation, especially when many prospective users may be inexperienced with programming."*
-
 :::
@@
 
-::: {#ResponseR18 style="width: 85%;   margin-left: auto;   margin-right: auto;"}
-
+::: {#ResponseR18 .response}
 We agree that this sentence needed clarification.
@@
 Thank you once again!
-
 :::
@@
 
-::: {#ResponseR21 style="width: 85%;   margin-left: auto;   margin-right: auto;"}
-
+::: {#ResponseR21 .response}
 Response
-
 :::
@@
 
-::: {#ResponseR22 style="width: 85%;   margin-left: auto;   margin-right: auto;"}
-
+::: {#ResponseR22 .response}
 Response
-
 :::
@@
 
-::: {#ResponseR23 style="width: 85%;   margin-left: auto;   margin-right: auto;"}
-
+::: {#ResponseR23 .response}
 We now briefly discuss the origin of Git and its expansion to applications beyond software development to help manage collaborations and community contributions, in the introduction <!--# add line numbers -->.
-
 :::
@@
 
-::: {#ResponseR24 style="width: 85%;   margin-left: auto;   margin-right: auto;"}
-
+::: {#ResponseR24 .response}
 Response
-
 :::
@@
 
-::: {#ResponseR25 style="width: 85%;   margin-left: auto;   margin-right: auto;"}
-
+::: {#ResponseR25 .response}
 Response
-
 :::
@@
 
-::: {#ResponseR26 style="width: 85%;   margin-left: auto;   margin-right: auto;"}
-
-Thank you for catching this. We closed the brackets.
-
+::: {#ResponseR26 .response}
+Thank you for catching this.
+We closed the brackets.
 :::
@@
 
-::: {#ResponseR27 style="width: 85%;   margin-left: auto;   margin-right: auto;"}
-
-Indeed! We have numbered all five barriers to using GitHub to clarify this section.
-
+::: {#ResponseR27 .response}
+Indeed!
+We have numbered all five barriers to using GitHub to clarify this section.
 :::
@@
 
-::: {#ResponseR28 style="width: 85%;   margin-left: auto;   margin-right: auto;"}
-
-You are right! We have corrected this issue. Thank you once again!
-
+::: {#ResponseR28 .response}
+You are right!
+We have corrected this issue.
+Thank you once again!
 :::
-
-</div>
+:::

### 2023-01-24 editorial-communication/response-to-the-reviewers.Qmd
put custom scss in separate file

@@
   html:
-    theme: cosmo 
+    theme: 
+      - cosmo 
+      - custom.scss
     highlight-style: tango
@@
 ---
-
-```{css}
-.response {
-  width: 85%;
-  margin-left: auto;
-  margin-right: auto;
-}
-```
 

### 2023-01-24 editorial-communication/response-to-the-reviewers.Qmd
Deploying to gh-pages from @ SORTEE-Github-Hackathon/manuscript@0ca4f9f3e708425ac5a6af693592ff9ccf10f053 🚀

@@
     embed-resources: true
-  docx: 
-    reference-doc: "response-template.docx"
-  pdf: default
 ---
@@
 We agree that the use cases and the jargon could be simplified to make the text more readable and attractive.
-Too address these recommendations, we: (1) added a brief paragraph in the introduction describing basic Git and Github workflows, directing readers to other references containing more technical and in-depth information about these platforms; (2) decreased the number of use cases (see [response to R1.1.](@sec-R1.1.) and [response to R1.2.](@sec-R1.2)); (3) added information on how GitHub Desktop and RStudio can be used as GUI interfaces for Git into Box 1 and into the Introduction (between lines XXX and XXX).
+Too address these recommendations, we: (1) added a brief paragraph in the introduction describing basic Git and Github workflows, directing readers to other references containing more technical and in-depth information about these platforms; (2) decreased the number of use cases (see [response to R1.1](#sec-R1.1) and [response to R1.2.](#sec-R1.2)); (3) added information on how GitHub Desktop and RStudio can be used as GUI interfaces for Git into Box 1 and into the Introduction (between lines XXX and XXX).
 :::
@@
 ::: {#ResponseR12 .response}
-As mentioned above (@sec-R1.1, @sec-E1.1), we were able to reduce jargon by making it clear in the introduction that our aim was not to *teach* the use of git and GitHub, and by discussing a basic git workflow early on.
+As mentioned above ([R1.1](#sec-R1.1), [E1.1](#sec-E1.1)), we were able to reduce jargon by making it clear in the introduction that our aim was not to *teach* the use of git and GitHub, and by discussing a basic git workflow early on.
 :::
@@
 We do make an attempt to quantify the investment effort in Figure 2 already.
-We've added a supplemental document better explaining *how* we made these quantifications (see also our response to reviewer 2 @sec-R2.2).
-However, we have taken the advice of reviewer 1 in other comments (@sec-R1.4, @sec-R1.1) to reduce the number of use cases and re-order them.
+We've added a supplemental document better explaining *how* we made these quantifications (see also our response to reviewer 2 [R2.2](#sec-R2.2)).
+However, we have taken the advice of reviewer 1 in other comments ([R1.4](#sec-R1.4), [R1.1](#sec-R1.1)) to reduce the number of use cases and re-order them.
 :::

### 2023-01-30 manuscript.tex
Merge pull request #303 from SORTEE-Github-Hackathon/r1-merge [ci skip]
This build is based on
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/b2e5480009b1ff9b626369295a0af0b08b0cf535.

This commit was created by the following CI build and job:
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/b2e5480009b1ff9b626369295a0af0b08b0cf535/checks
https://github.com/SORTEE-Github-Hackathon/manuscript/actions/runs/4045188171

@@
 This manuscript
-(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/077be9d884d5bc703a0a7db131e90f2d35254fbc/}{permalink})
+(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/b2e5480009b1ff9b626369295a0af0b08b0cf535/}{permalink})
 was automatically generated
-from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/077be9d884d5bc703a0a7db131e90f2d35254fbc}{SORTEE-Github-Hackathon/manuscript@077be9d}
-on January 2, 2023.
+from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/b2e5480009b1ff9b626369295a0af0b08b0cf535}{SORTEE-Github-Hackathon/manuscript@b2e5480}
+on January 30, 2023.
 
@@
 Despite these benefits, the use of GitHub in ecology and evolution is not widespread.
-To help researchers in ecology and evolution adopt useful features from GitHub in their own workflows, we review thirteen practical ways to use the platform.
+To help researchers in ecology and evolution adopt useful features from GitHub in their own workflows, we review twelve practical ways to use the platform.
 We outline features ranging from low to high technical difficulty: storing code, managing projects, coding collaboratively, conducting peer review, and writing a manuscript.
@@
 During the hackathon, we identified the need for formal discussions on how EEB researchers can benefit from GitHub and its features.
-Here, we outline thirteen practical ways that EEB researchers can use GitHub features for more collaborative, transparent, and reproducible science.
+Here, we outline twelve practical ways that EEB researchers can use GitHub features for more collaborative, transparent, and reproducible science.
 We also provide critical perspectives on features that could be improved and catered towards research development.
@@
 
-\hypertarget{thirteen-practical-ways-github-can-accelerate-research-in-ecology-and-evolution}{%
-\subsection{Thirteen practical ways GitHub can accelerate research in ecology and evolution}\label{thirteen-practical-ways-github-can-accelerate-research-in-ecology-and-evolution}}
+\hypertarget{twelve-practical-ways-github-can-accelerate-research-in-ecology-and-evolution}{%
+\subsection{Twelve practical ways GitHub can accelerate research in ecology and evolution}\label{twelve-practical-ways-github-can-accelerate-research-in-ecology-and-evolution}}
 
@@
 An EEB research compendium includes all computational materials related to research production, including data, code for analyses and protocols.
-Having copies of these files safely stored is essential to protect against accidental modifications or deletions.
-Many researchers begin using GitHub to store (or backup) their research compendium (\protect\hyperlink{ref-MwwMapRG}{Marwick et al., 2018}) to a centralized, readily-available remote server (see \protect\hyperlink{definitions}{Box 1}).
-A centralized research compendium stored in a version-controlled repository has the advantages of facilitating collaboration, integrating data and code archiving services, allowing file versions to be accessed and restored, and contributes to open science (see sections below).
-While some EEB researchers may prefer to store their code in Google Drive or DropBox, the process of sharing code through these services becomes cumbersome when collaborators have to download and re-upload edited code.
-On GitHub, code is by default public, and the process of forking and submitting pull requests (see \protect\hyperlink{definitions}{Box 1}) ensures a code owner has full control over code and documents in a repository.
+Safely storing these files is essential to protect against accidental modifications or deletions.
+Many researchers begin using GitHub to backup their research compendium (\protect\hyperlink{ref-MwwMapRG}{Marwick et al., 2018}) into a centralized, readily-available remote server (see \protect\hyperlink{definitions}{Box 1}).
+A centralized research compendium stored in a version-controlled repository has the advantages of facilitating collaboration, integrating data and code archiving, allowing file versions to be accessed and restored, and further contributing to open science practices (Borghi \& Van Gulick (\protect\hyperlink{ref-gLby7jt1}{2022})).
+Every change made to files in a version-controlled repository accompany a description of modifications and are authored (\protect\hyperlink{definitions}{Box 1}).
+Later, the entire history of commits and their commit messages are viewable and can be audited similar to a physical laboratory notebook (\protect\hyperlink{ref-4ny1onB0}{Ram, 2013}).
+On GitHub, code can be made public, and the process of forking and submitting pull requests (see \protect\hyperlink{definitions}{Box 1}) ensures code owners have full control over code and documents in a repository.
 The ability to make a GitHub repository private is particularly advantageous for storing materials without necessarily sacrificing privacy, which may be preferred or even essential for certain compendia.
@@
 
-\hypertarget{virtual-laboratory-notebooks}{%
-\subsubsection{Virtual laboratory notebooks}\label{virtual-laboratory-notebooks}}
-
-Laboratory notebooks help researchers track their research notes, methods, policies and protocols (\protect\hyperlink{ref-wwHxTOtm}{Kanza et al., 2017}).
-Virtual laboratory notebooks can be stored on GitHub and provide the benefits of simultaneous, centralized and selective access, and allows for the easy update of policies and experiment protocols (\protect\hyperlink{ref-10V7x4H4l}{Schnell, 2015}).
-Researchers have been increasingly using GitHub to maintain versions and share digital laboratory notebooks across many fields (\protect\hyperlink{ref-10ghgV3S8}{J.
+\hypertarget{project-continuity}{%
+\subsubsection{Project continuity}\label{project-continuity}}
+
+Projects in ecology and evolution often involve research professionals holding limited-term positions, such as graduate students, research assistants, and post-doctoral fellows (\protect\hyperlink{ref-D4C4k4ak}{Fehr et al., 2021}).
+Without clear plans on project continuity, the research code and data management upkeep tend to fall off as researchers move on to new projects or other institutions.
+Additionally, code and data can be difficult to access when kept only on personal devices (\protect\hyperlink{ref-19kmNxiHc}{Vines et al., 2014}).
+
+GitHub can facilitate project continuity among research code by making code handover easier (\protect\hyperlink{ref-D4C4k4ak}{Fehr et al., 2021}; \protect\hyperlink{ref-4ny1onB0}{Ram, 2013}).
+Through version control, the history of code and data from projects in ecology and evolution can be tracked accessible to future laboratory members and collaborators (\protect\hyperlink{ref-3DKwn1sY}{Lowndes et al., 2017}).
+Repositories and organizations can have designated data and code owners {[}or more appropriate, stewards; see Hampton et al.
+(\protect\hyperlink{ref-iIEKCTLU}{2015}), \emph{About Code Owners} (\protect\hyperlink{ref-s91uGRZ2}{n.d.}){]}, who can also change through time allowing for the transition of code between research cohorts (see also \protect\hyperlink{organizations}{``Organizing and managing teams''}).
+Other project collaborators can contribute to repository design and development, and their active involvement can both aid authors ability to act as guarantors of the project, and the clarity and reproducibility of the project for future users.
+In (Figure \ref{fig:github-diagram}), we highlight several elements of good repository structure, and the various ways that contributors may interact with them.
+
+GitHub also allows users to describe and store information about software and code dependencies, ensuring that code can run using the same version of software as when it was initially developed.
+This can be achieved through the access of GitHub repositories containing the necessary releases of such software, or through the use of automated Github Actions with specific software versions.
+
+GitHub can facilitate lab continuity by being used as a platform for storing, selectively sharing, and easily updating lab policies and experimental protocols.
+Researchers have been increasingly using GitHub to maintain versions and share digital laboratory handbooks across many fields (\protect\hyperlink{ref-10ghgV3S8}{J.
 Perkel, 2016}), including applied ecology (\emph{e.g.}, \url{https://scheuerell-lab.github.io/lab-book}), biogeography and global change biology (\emph{e.g.}, \url{https://github.com/HuckleyLab/how_we_work}), and microbial ecology (\emph{e.g.}, \url{https://github.com/CarBBAS/uqam-guide}).
-
-At least for aspects of a research project that involve writing code, a GitHub repository is a form of a laboratory notebook; when changes are made to files in a version-controlled repository, the author of those changes makes a commit (\protect\hyperlink{definitions}{Box 1}) accompanied by a description of changes.
-Later, the entire history of commits and their commit messages are viewable and can be audited similar to a physical laboratory notebook (\protect\hyperlink{ref-4ny1onB0}{Ram, 2013}).
-GitHub issues (see Project management section below) can be used to prioritize laboratory objectives and goals, as well as track any progress updates.
 
@@
 The GitHub interface for a pull request allows collaborators to comment on specific lines of code/text being changed and even to provide suggestions that the pull request author can implement with the click of a button, greatly facilitating peer review.
-Moreover, version control (\protect\hyperlink{ref-K7nbP1Ty}{Crystal-Ornelas et al., 2022}) allows researchers to make changes in code or documents without worrying about irreparably modifying someone else's work.
+Moreover, version control (\protect\hyperlink{ref-K7nbP1Ty}{Crystal-Ornelas et al., 2023}) allows researchers to make changes in code or documents without worrying about irreparably modifying someone else's work.
 By enabling more comprehensive remote collaboration, GitHub encourages the exchange of ideas among researchers at different institutions and in different countries, which can serve to improve the quality of the research itself by providing open access to data and code.
@@
 
-\hypertarget{project-continuity}{%
-\subsubsection{Project continuity}\label{project-continuity}}
-
-Projects in ecology and evolution often involve graduate students, research assistants, and post-doctoral fellows, who hold limited-term positions (\protect\hyperlink{ref-D4C4k4ak}{Fehr et al., 2021}).
-Without clear plans on project continuity, the research code and data management upkeep tends to fall off as researchers move on to new projects or to other institutions.
-Additionally, code and data can be difficult to access when kept only on personal devices (\protect\hyperlink{ref-19kmNxiHc}{Vines et al., 2014}).
-
-GitHub can facilitate project continuity among research code by making code handover easier (\protect\hyperlink{ref-D4C4k4ak}{Fehr et al., 2021}; \protect\hyperlink{ref-4ny1onB0}{Ram, 2013}).
-Through version control, the history of code and data from projects in ecology and evolution can be tracked accessible to future laboratory members and collaborators (\protect\hyperlink{ref-3DKwn1sY}{Lowndes et al., 2017}).
-Repositories and organizations can have designated data and code owners {[}or more appropriate, stewards; see Hampton et al.
-(\protect\hyperlink{ref-iIEKCTLU}{2015}), \emph{About Code Owners} (\protect\hyperlink{ref-s91uGRZ2}{n.d.}){]}, who can also change through time allowing for the transition of code between research cohorts.
-Other project collaborators can contribute to repository design and development, and their active involvement can both aid authors ability to act as guarantors of the project, and the clarity and reproducibility of the project for future users.
-In (Figure \ref{fig:github-diagram}), we highlight several elements of good repository structure, and the various ways that contributors may interact with them.
-
-GitHub also allows users to describe and store information about software and code dependencies, ensuring that code can run using the same version of software as when it was initially developed.
-This can be achieved through the access of GitHub repositories containing the necessary releases of such software, or through the use of automated Github Actions with specific software versions.
-
 \hypertarget{automation}{%
@@
 
-\hypertarget{organizing-and-managing-teams}{%
-\subsubsection{Organizing and managing teams}\label{organizing-and-managing-teams}}
+\hypertarget{organizations}{%
+\subsubsection{Organizing and managing teams}\label{organizations}}
 
@@
 
-The thirteen use cases we described here can leverage GitHub to enable more transparent and collaborative research in ecology and evolution (Figure \ref{fig:scatterblob}).
+The twelve use cases we described here can leverage GitHub to enable more transparent and collaborative research in ecology and evolution (Figure \ref{fig:scatterblob}).
 Most of these uses can be quickly integrated into the research practices of users (\emph{e.g.}, storing data, creating virtual notebooks, making code citable).
@@
 
-We describe thirteen practical ways that ecologists and evolutionary biologists can adopt GitHub to improve their research workflow and make it more open and reproducible.
+We describe twelve practical ways that ecologists and evolutionary biologists can adopt GitHub to improve their research workflow and make it more open and reproducible.
 We provide definitions (\protect\hyperlink{definitions}{Box 1}) and types of users (Figure \ref{fig:github-diagram}) to help researchers identify and prioritize the skills and tools to learn and apply.
@@
 GitHub Docs.
-Retrieved January 2, 2023, from \url{https://ghdocs-prod.azurewebsites.net/en/repositories/managing-your-repositorys-settings-and-features/customizing-your-repository/about-code-owners}
+Retrieved January 30, 2023, from \url{https://ghdocs-prod.azurewebsites.net/en/repositories/managing-your-repositorys-settings-and-features/customizing-your-repository/about-code-owners}
 
@@
 GitHub Docs.
-Retrieved January 2, 2023, from \url{https://ghdocs-prod.azurewebsites.net/en/repositories/working-with-files/managing-large-files/about-large-files-on-github}
+Retrieved January 30, 2023, from \url{https://ghdocs-prod.azurewebsites.net/en/repositories/working-with-files/managing-large-files/about-large-files-on-github}
 
@@
 GitHub Docs.
-Retrieved January 2, 2023, from \url{https://ghdocs-prod.azurewebsites.net/en/issues/planning-and-tracking-with-projects/learning-about-projects/about-projects}
+Retrieved January 30, 2023, from \url{https://ghdocs-prod.azurewebsites.net/en/issues/planning-and-tracking-with-projects/learning-about-projects/about-projects}
 
@@
 GitHub Docs.
-Retrieved January 2, 2023, from \url{https://ghdocs-prod.azurewebsites.net/en/communities/setting-up-your-project-for-healthy-contributions/adding-a-license-to-a-repository}
+Retrieved January 30, 2023, from \url{https://ghdocs-prod.azurewebsites.net/en/communities/setting-up-your-project-for-healthy-contributions/adding-a-license-to-a-repository}
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-gLby7jt1}{}}%
+Borghi, J., \& Van Gulick, A. (2022). Promoting Open Science Through Research Data Management. \emph{Harvard Data Science Review}. \url{https://doi.org/10.1162/99608f92.9497f68e}
+
 \leavevmode\vadjust pre{\hypertarget{ref-ydrk01SR}{}}%
@@
 \leavevmode\vadjust pre{\hypertarget{ref-6CMMeSeD}{}}%
-Bryan, J., \& TAs, T. S. 545. (n.d.). \emph{STAT 545}. Retrieved January 2, 2023, from \url{https://stat545.com/}
+Bryan, J., \& TAs, T. S. 545. (n.d.). \emph{STAT 545}. Retrieved January 30, 2023, from \url{https://stat545.com/}
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-lx49NGto}{}}%
-\emph{Connect GitHub to a Project - OSF Support}. (n.d.). Retrieved January 2, 2023, from \url{https://help.osf.io/article/211-connect-github-to-a-project}
+\emph{Connect GitHub to a Project - OSF Support}. (n.d.). Retrieved January 30, 2023, from \url{https://help.osf.io/article/211-connect-github-to-a-project}
 
 \leavevmode\vadjust pre{\hypertarget{ref-T03Api6e}{}}%
-\emph{Continuous Integration and Delivery}. (n.d.). CircleCI. Retrieved January 2, 2023, from \url{https://circleci.com/}
+\emph{Continuous Integration and Delivery}. (n.d.). CircleCI. Retrieved January 30, 2023, from \url{https://circleci.com/}
 
@@
 P.
-(2022).
+(2023).
 \emph{Not just for programmers: How GitHub can accelerate collaborative and reproducible research in ecology and evolution}.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-NUXbp429}{}}%
-\emph{Features • GitHub Actions}. (n.d.). GitHub. Retrieved January 2, 2023, from \url{https://github.com/features/actions}
+\emph{Features • GitHub Actions}. (n.d.). GitHub. Retrieved January 30, 2023, from \url{https://github.com/features/actions}
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-1CM2EcdVk}{}}%
-\emph{Git - A Short History of Git}. (n.d.). Retrieved January 2, 2023, from \url{https://git-scm.com/book/en/v2/Getting-Started-A-Short-History-of-Git}
+\emph{Git - A Short History of Git}. (n.d.). Retrieved January 30, 2023, from \url{https://git-scm.com/book/en/v2/Getting-Started-A-Short-History-of-Git}
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-ZvrOcg9w}{}}%
-Hester, J. B., the STAT 545 TAs, Jim. (n.d.). \emph{Let's Git started \textbar{} Happy Git and GitHub for the useR}. Retrieved January 2, 2023, from \url{https://happygitwithr.com/}
+Hester, J. B., the STAT 545 TAs, Jim. (n.d.). \emph{Let's Git started \textbar{} Happy Git and GitHub for the useR}. Retrieved January 30, 2023, from \url{https://happygitwithr.com/}
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-3UAritXO}{}}%
-\emph{Issues · fmsabatini/sPlotOpen\_Manuscript}. (n.d.). GitHub. Retrieved January 2, 2023, from \url{https://github.com/fmsabatini/sPlotOpen_Manuscript}
+\emph{Issues · fmsabatini/sPlotOpen\_Manuscript}. (n.d.). GitHub. Retrieved January 30, 2023, from \url{https://github.com/fmsabatini/sPlotOpen_Manuscript}
 
@@
 \url{https://doi.org/10.1109/icse.2015.74}
-
-\leavevmode\vadjust pre{\hypertarget{ref-wwHxTOtm}{}}%
-Kanza, S., Willoughby, C., Gibbins, N., Whitby, R., Frey, J.
-G., Erjavec, J., Zupančič, K., Hren, M., \& Kovač, K.
-(2017).
-Electronic lab notebooks: can they replace paper?
-\emph{Journal of Cheminformatics}, \emph{9}(1).
-\url{https://doi.org/10.1186/s13321-017-0221-3}
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Re6Eg2va}{}}%
-\emph{Manubot - Manuscripts, open and automated}. (n.d.). Retrieved January 2, 2023, from \url{https://manubot.org}
+\emph{Manubot - Manuscripts, open and automated}. (n.d.). Retrieved January 30, 2023, from \url{https://manubot.org}
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-10V7x4H4l}{}}%
-Schnell, S. (2015). Ten Simple Rules for a Computational Biologist's Laboratory Notebook. \emph{PLOS Computational Biology}, \emph{11}(9), e1004385. \url{https://doi.org/10.1371/journal.pcbi.1004385}
-
 \leavevmode\vadjust pre{\hypertarget{ref-HiIPSSHV}{}}%
@@
 C., \& Sakr, M.
-(2020, June 2).
+(2020, June 15).
 Using Peer Code Review as an Educational Tool.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-oGbKxHzj}{}}%
-\emph{Using Git and GitHub}. (n.d.). Retrieved January 2, 2023, from \url{https://www.overleaf.com/learn/how-to/Using_Git_and_GitHub}
+\emph{Using Git and GitHub}. (n.d.). Retrieved January 30, 2023, from \url{https://www.overleaf.com/learn/how-to/Using_Git_and_GitHub}
 

### 2023-01-31 editorial-communication/response-to-the-reviewers.Qmd

@@
 We agree that the use cases and the jargon could be simplified to make the text more readable and attractive.
-Too address these recommendations, we: (1) added a brief paragraph in the introduction describing basic Git and Github workflows, directing readers to other references containing more technical and in-depth information about these platforms; (2) decreased the number of use cases (see [response to R1.1](#sec-R1.1) and [response to R1.2.](#sec-R1.2)); (3) added information on how GitHub Desktop and RStudio can be used as GUI interfaces for Git into Box 1 and into the Introduction (between lines XXX and XXX).
+To address these recommendations, we: (1) added a brief paragraph in the introduction describing basic Git and Github workflows, directing readers to other references containing more technical and in-depth information about these platforms;
+(2) decreased the number of use cases (see [response to R1.1](#sec-R1.1) and [response to R1.2.](#sec-R1.2)); 
+(3) added information on how GitHub Desktop and RStudio can be used as GUI interfaces for Git into Box 1 and into the Introduction (between lines XXX and XXX).
 :::
@@
 We think this is a good point since many readers may not immediately see the value in a time investment to learn a new tool when they are comfortable with tools that meet many or most of their needs.
-Rather than creating a new section, we identify specific points in the manuscript where we could directly call out where GitHub as a platform enables greater or different types of collaboration and open science than platforms like Dropbox or Google.
-Due to these edits (below) we now more often refer to table 1, and earlier in the manuscript as well.\
+Rather than creating a new section, we identify specific points in the manuscript where we discuss how GitHub enables different and better types of collaboration and open science than alternative platforms, such as Dropbox or Google Suite.
+We added this discussion earlier in the manuscript, and now refer more often to Table 1.
+These changes are listed below:
+\
 
@@
 ::: {#ResponseR11 .response}
-In order to reduce repetition and jargon in the use cases sections, we've added a paragraph to the introduction <!--# add line numbers --> explaining a basic git & GitHub workflow and pointing the reader to other resources for learning these tools.
-This allows us to focus less on explaining the specific mechanisms of git/Github in the use cases sections and more on the usefulness of the tools.
+Thank you for this recommendation! We agree that the many sections could be restructured to become more concise and clearer.
+To address this recommendation, we did the following: (1) to reduce repetition and jargon in the use cases sections, we added a paragraph to the introduction <!--# add line numbers --> explaining basic Git and Github workflows.
+We also cited resources for learning how to use tools.
+These changes allowed us to focus on the usefulness of these tools for research in ecology and evolution.
+(2) We removed the "laboratory notebooks" section and merged part of its contents into the X section, which allowed us to further shorten the text; and, (3) [...].
+
+ <!--# This comment does not seem to fit within this section  -->
 In regards to the specific suggestion about deprioritizing GitHub communication tools, we believe these are extremely useful alternatives to reply-all email chains for a variety of reasons and have attempted to improve the clarity of this section of our manuscript \[end of project management section\].
@@
 ::: {#ResponseR12 .response}
-As mentioned above ([R1.1](#sec-R1.1), [E1.1](#sec-E1.1)), we were able to reduce jargon by making it clear in the introduction that our aim was not to *teach* the use of git and GitHub, and by discussing a basic git workflow early on.
+Following our modifications to address [R1.1](#sec-R1.1) and [E1.1](#sec-E1.1), we reduced jargon, simplified the narrative, and focused more in the advantages of the features GitHub provide to improve the research workflow in ecology and evolution.
+We also clarify to the reader that the objective of the manuscript is not to instruct how these tools.
+ <!--# Self-note: This comment needs improvement, as it is not very convincing. -->
 :::
@@
 ::: {#ResponseR13 .response}
-We appreciate this comment and while we do agree that ordering the use cases by value to the reader would be ideal, we believe that value or return on investment is subjective and varies among fields, labs, and individuals.
-For example, the reviewer sees collaborative writing of a manuscript using GitHub as an "out of the question" advanced use.
-However, all of the co-authors on this manuscript have done exactly this and found it an excellent return on investment.
-At the same time, not all co-authors have experience in many of the other use cases we present and may find them less useful depending on their needs.
-We do make an attempt to quantify the investment effort in Figure 2 already.
-We've added a supplemental document better explaining *how* we made these quantifications (see also our response to reviewer 2 [R2.2](#sec-R2.2)).
-However, we have taken the advice of reviewer 1 in other comments ([R1.4](#sec-R1.4), [R1.1](#sec-R1.1)) to reduce the number of use cases and re-order them.
+We appreciate this comment.
+While the attribution of a type of return of investment index to use cases could be interesting, we believe that such value can be highly biased, subjective and vary much among fields, laboratories, research culture, and individuals.
+For instance, while collaborative writing of a manuscript using GitHub may be seen as a strong time investment and an advanced usage, there is an increasing number of research articles adopting this features, such as XXXX, XXXX, XXXX, in addition to our manuscript.
+In these cases, most co-authors had little experience with effectively integrating Github tools to write a manuscript within the platform, and had to commit to learn and adopt proposed frameworks to achieve project completion.
+It is also difficult to measure return on investment on innovative tools that only recently took off, such as the usage of Github Actions in ecological research frameworks for data management, processing, and analysis (*e.g.*, in XXXX, XXXX, XXX).
+As we mentioned, we appreciate this suggestion, however we think that the quantification of a ratio between investment of time and resources and returns when learning research aiding skills requires an in-depth individual study.
+Taking this into account, our metric of cognitive requirement represented in Figure 2 considers the usefulness?
+or cognitive requirement?
+for learning this new tool (see also our response to [R2.2](#sec-R2.2)).
+Moreover, we have taken the advice of reviewer 1, and reduced and reordered the use cases (see our responses to [R1.4](#sec-R1.4) and [R1.1](#sec-R1.1)).
 :::

### 2023-02-05 manuscript.tex
Merge pull request #302 from SORTEE-Github-Hackathon/response-qmd [ci skip]
This build is based on
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/ac022f888171bd26895e5be7f44228e72d1a32ca.

This commit was created by the following CI build and job:
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/ac022f888171bd26895e5be7f44228e72d1a32ca/checks
https://github.com/SORTEE-Github-Hackathon/manuscript/actions/runs/4094889950

@@
 This manuscript
-(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/b2e5480009b1ff9b626369295a0af0b08b0cf535/}{permalink})
+(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/ac022f888171bd26895e5be7f44228e72d1a32ca/}{permalink})
 was automatically generated
-from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/b2e5480009b1ff9b626369295a0af0b08b0cf535}{SORTEE-Github-Hackathon/manuscript@b2e5480}
-on January 30, 2023.
+from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/ac022f888171bd26895e5be7f44228e72d1a32ca}{SORTEE-Github-Hackathon/manuscript@ac022f8}
+on February 5, 2023.
 
@@
 For instance, one can create a discussion on a project repository to decide which method to apply for biodiversity data analysis.
-Then, an issue can be created to establish steps and responsibilities including data formatting, statistical analyses, figure generation, and issue resolution (\emph{e.g.}, see issues and discussions in the sPlotOpen manuscript repository, \protect\hyperlink{ref-doi:10.1111ux2fgeb.13346}{\textbf{doi:10.1111/geb.13346?}}); \emph{Issues · Fmsabatini/sPlotOpen\_Manuscript} (\protect\hyperlink{ref-3UAritXO}{n.d.})=is\%3Aissue+is\%3Aclosed{]}.
+Then, an issue can be created to establish steps and responsibilities including data formatting, statistical analyses, figure generation, and issue resolution (\emph{e.g.}, see issues and discussions in the sPlotOpen manuscript repository, \protect\hyperlink{ref-doi:10.1111ux2fgeb.13346}{\textbf{doi:10.1111/geb.13346?}}); (\protect\hyperlink{ref-3UAritXO}{n.d.})=is\%3Aissue+is\%3Aclosed{]}.
 Using GitHub for all project-related conversation and planning, rather than email or messaging tools, makes it easier to keep track of progress throughout the lifespan of a project.
@@
 \begin{CSLReferences}{1}{0}
+\leavevmode\vadjust pre{\hypertarget{ref-3UAritXO}{}}%
+(n.d.). \url{https://github.com/fmsabatini/sPlotOpen_Manuscript/issues?q}
+
 \leavevmode\vadjust pre{\hypertarget{ref-s91uGRZ2}{}}%
@@
 GitHub Docs.
-Retrieved January 30, 2023, from \url{https://ghdocs-prod.azurewebsites.net/en/repositories/managing-your-repositorys-settings-and-features/customizing-your-repository/about-code-owners}
+Retrieved February 4, 2023, from \url{https://ghdocs-prod.azurewebsites.net/en/repositories/managing-your-repositorys-settings-and-features/customizing-your-repository/about-code-owners}
 
@@
 GitHub Docs.
-Retrieved January 30, 2023, from \url{https://ghdocs-prod.azurewebsites.net/en/repositories/working-with-files/managing-large-files/about-large-files-on-github}
+Retrieved February 4, 2023, from \url{https://ghdocs-prod.azurewebsites.net/en/repositories/working-with-files/managing-large-files/about-large-files-on-github}
 
@@
 GitHub Docs.
-Retrieved January 30, 2023, from \url{https://ghdocs-prod.azurewebsites.net/en/issues/planning-and-tracking-with-projects/learning-about-projects/about-projects}
+Retrieved February 4, 2023, from \url{https://ghdocs-prod.azurewebsites.net/en/issues/planning-and-tracking-with-projects/learning-about-projects/about-projects}
 
@@
 GitHub Docs.
-Retrieved January 30, 2023, from \url{https://ghdocs-prod.azurewebsites.net/en/communities/setting-up-your-project-for-healthy-contributions/adding-a-license-to-a-repository}
+Retrieved February 4, 2023, from \url{https://ghdocs-prod.azurewebsites.net/en/communities/setting-up-your-project-for-healthy-contributions/adding-a-license-to-a-repository}
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-6CMMeSeD}{}}%
-Bryan, J., \& TAs, T. S. 545. (n.d.). \emph{STAT 545}. Retrieved January 30, 2023, from \url{https://stat545.com/}
+Bryan, J., \& TAs, T. S. 545. (n.d.). \emph{STAT 545}. Retrieved February 4, 2023, from \url{https://stat545.com/}
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-lx49NGto}{}}%
-\emph{Connect GitHub to a Project - OSF Support}. (n.d.). Retrieved January 30, 2023, from \url{https://help.osf.io/article/211-connect-github-to-a-project}
+\emph{Connect GitHub to a Project - OSF Support}. (n.d.). Retrieved February 4, 2023, from \url{https://help.osf.io/article/211-connect-github-to-a-project}
 
 \leavevmode\vadjust pre{\hypertarget{ref-T03Api6e}{}}%
-\emph{Continuous Integration and Delivery}. (n.d.). CircleCI. Retrieved January 30, 2023, from \url{https://circleci.com/}
+\emph{Continuous Integration and Delivery}. (n.d.). CircleCI. Retrieved February 4, 2023, from \url{https://circleci.com/}
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-NUXbp429}{}}%
-\emph{Features • GitHub Actions}. (n.d.). GitHub. Retrieved January 30, 2023, from \url{https://github.com/features/actions}
+\emph{Features • GitHub Actions}. (n.d.). GitHub. Retrieved February 4, 2023, from \url{https://github.com/features/actions}
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-1CM2EcdVk}{}}%
-\emph{Git - A Short History of Git}. (n.d.). Retrieved January 30, 2023, from \url{https://git-scm.com/book/en/v2/Getting-Started-A-Short-History-of-Git}
+\emph{Git - A Short History of Git}. (n.d.). Retrieved February 4, 2023, from \url{https://git-scm.com/book/en/v2/Getting-Started-A-Short-History-of-Git}
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-ZvrOcg9w}{}}%
-Hester, J. B., the STAT 545 TAs, Jim. (n.d.). \emph{Let's Git started \textbar{} Happy Git and GitHub for the useR}. Retrieved January 30, 2023, from \url{https://happygitwithr.com/}
+Hester, J. B., the STAT 545 TAs, Jim. (n.d.). \emph{Let's Git started \textbar{} Happy Git and GitHub for the useR}. Retrieved February 4, 2023, from \url{https://happygitwithr.com/}
 
@@
 Hudgins, E. (2022). \emph{emmajhudgins/UStreedamage: publication release} (accepted) {[}Computer software{]}. Zenodo. \url{https://doi.org/10.5281/zenodo.6097109}
-
-\leavevmode\vadjust pre{\hypertarget{ref-3UAritXO}{}}%
-\emph{Issues · fmsabatini/sPlotOpen\_Manuscript}. (n.d.). GitHub. Retrieved January 30, 2023, from \url{https://github.com/fmsabatini/sPlotOpen_Manuscript}
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Re6Eg2va}{}}%
-\emph{Manubot - Manuscripts, open and automated}. (n.d.). Retrieved January 30, 2023, from \url{https://manubot.org}
+\emph{Manubot - Manuscripts, open and automated}. (n.d.). Retrieved February 4, 2023, from \url{https://manubot.org}
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-oGbKxHzj}{}}%
-\emph{Using Git and GitHub}. (n.d.). Retrieved January 30, 2023, from \url{https://www.overleaf.com/learn/how-to/Using_Git_and_GitHub}
+\emph{Using Git and GitHub}. (n.d.). Retrieved February 4, 2023, from \url{https://www.overleaf.com/learn/how-to/Using_Git_and_GitHub}
 

### 2023-02-06 manuscript.tex
Merge pull request #304 from fhillemann/fhillemann-figure-1 [ci skip]
This build is based on
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/659dbf07d94474726c8403d04555afbb3a45da57.

This commit was created by the following CI build and job:
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/659dbf07d94474726c8403d04555afbb3a45da57/checks
https://github.com/SORTEE-Github-Hackathon/manuscript/actions/runs/4108427799

--- 2023-01-30 manuscript.tex
@@
 This manuscript
-(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/b2e5480009b1ff9b626369295a0af0b08b0cf535/}{permalink})
+(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/659dbf07d94474726c8403d04555afbb3a45da57/}{permalink})
 was automatically generated
-from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/b2e5480009b1ff9b626369295a0af0b08b0cf535}{SORTEE-Github-Hackathon/manuscript@b2e5480}
-on January 30, 2023.
+from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/659dbf07d94474726c8403d04555afbb3a45da57}{SORTEE-Github-Hackathon/manuscript@659dbf0}
+on February 6, 2023.
 
@@
 \centering
-\includegraphics{images/github_diagram.png}
+\includegraphics{images/Figure1.png}
 \caption{An overview of Git's core features.
@@
 B) Issues, Pull Requests, Discussions, and Projects allow for team members to ask for feedback, suggest fixes, discuss related ideas, and keep track of all the moving parts of a project.
-C) All collaborators on a project can be a part of a single repository, with varying push privileges and responsibilities}\label{fig:github-diagram}
+C) All collaborators on a project can be a part of a single repository, with varying push privileges and responsibilities.}\label{fig:github-diagram}
 }
@@
 GitHub Docs.
-Retrieved January 30, 2023, from \url{https://ghdocs-prod.azurewebsites.net/en/repositories/managing-your-repositorys-settings-and-features/customizing-your-repository/about-code-owners}
+Retrieved February 6, 2023, from \url{https://ghdocs-prod.azurewebsites.net/en/repositories/managing-your-repositorys-settings-and-features/customizing-your-repository/about-code-owners}
 
@@
 GitHub Docs.
-Retrieved January 30, 2023, from \url{https://ghdocs-prod.azurewebsites.net/en/repositories/working-with-files/managing-large-files/about-large-files-on-github}
+Retrieved February 6, 2023, from \url{https://ghdocs-prod.azurewebsites.net/en/repositories/working-with-files/managing-large-files/about-large-files-on-github}
 
@@
 GitHub Docs.
-Retrieved January 30, 2023, from \url{https://ghdocs-prod.azurewebsites.net/en/issues/planning-and-tracking-with-projects/learning-about-projects/about-projects}
+Retrieved February 6, 2023, from \url{https://ghdocs-prod.azurewebsites.net/en/issues/planning-and-tracking-with-projects/learning-about-projects/about-projects}
 
@@
 GitHub Docs.
-Retrieved January 30, 2023, from \url{https://ghdocs-prod.azurewebsites.net/en/communities/setting-up-your-project-for-healthy-contributions/adding-a-license-to-a-repository}
+Retrieved February 6, 2023, from \url{https://ghdocs-prod.azurewebsites.net/en/communities/setting-up-your-project-for-healthy-contributions/adding-a-license-to-a-repository}
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-6CMMeSeD}{}}%
-Bryan, J., \& TAs, T. S. 545. (n.d.). \emph{STAT 545}. Retrieved January 30, 2023, from \url{https://stat545.com/}
+Bryan, J., \& TAs, T. S. 545. (n.d.). \emph{STAT 545}. Retrieved February 6, 2023, from \url{https://stat545.com/}
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-lx49NGto}{}}%
-\emph{Connect GitHub to a Project - OSF Support}. (n.d.). Retrieved January 30, 2023, from \url{https://help.osf.io/article/211-connect-github-to-a-project}
+\emph{Connect GitHub to a Project - OSF Support}. (n.d.). Retrieved February 6, 2023, from \url{https://help.osf.io/article/211-connect-github-to-a-project}
 
 \leavevmode\vadjust pre{\hypertarget{ref-T03Api6e}{}}%
-\emph{Continuous Integration and Delivery}. (n.d.). CircleCI. Retrieved January 30, 2023, from \url{https://circleci.com/}
+\emph{Continuous Integration and Delivery}. (n.d.). CircleCI. Retrieved February 6, 2023, from \url{https://circleci.com/}
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-NUXbp429}{}}%
-\emph{Features • GitHub Actions}. (n.d.). GitHub. Retrieved January 30, 2023, from \url{https://github.com/features/actions}
+\emph{Features • GitHub Actions}. (n.d.). GitHub. Retrieved February 6, 2023, from \url{https://github.com/features/actions}
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-1CM2EcdVk}{}}%
-\emph{Git - A Short History of Git}. (n.d.). Retrieved January 30, 2023, from \url{https://git-scm.com/book/en/v2/Getting-Started-A-Short-History-of-Git}
+\emph{Git - A Short History of Git}. (n.d.). Retrieved February 6, 2023, from \url{https://git-scm.com/book/en/v2/Getting-Started-A-Short-History-of-Git}
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-ZvrOcg9w}{}}%
-Hester, J. B., the STAT 545 TAs, Jim. (n.d.). \emph{Let's Git started \textbar{} Happy Git and GitHub for the useR}. Retrieved January 30, 2023, from \url{https://happygitwithr.com/}
+Hester, J. B., the STAT 545 TAs, Jim. (n.d.). \emph{Let's Git started \textbar{} Happy Git and GitHub for the useR}. Retrieved February 6, 2023, from \url{https://happygitwithr.com/}
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-3UAritXO}{}}%
-\emph{Issues · fmsabatini/sPlotOpen\_Manuscript}. (n.d.). GitHub. Retrieved January 30, 2023, from \url{https://github.com/fmsabatini/sPlotOpen_Manuscript}
+\emph{Issues · fmsabatini/sPlotOpen\_Manuscript}. (n.d.). GitHub. Retrieved February 6, 2023, from \url{https://github.com/fmsabatini/sPlotOpen_Manuscript}
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Re6Eg2va}{}}%
-\emph{Manubot - Manuscripts, open and automated}. (n.d.). Retrieved January 30, 2023, from \url{https://manubot.org}
+\emph{Manubot - Manuscripts, open and automated}. (n.d.). Retrieved February 6, 2023, from \url{https://manubot.org}
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-oGbKxHzj}{}}%
-\emph{Using Git and GitHub}. (n.d.). Retrieved January 30, 2023, from \url{https://www.overleaf.com/learn/how-to/Using_Git_and_GitHub}
+\emph{Using Git and GitHub}. (n.d.). Retrieved February 6, 2023, from \url{https://www.overleaf.com/learn/how-to/Using_Git_and_GitHub}
 

### 2023-02-06 manuscript.tex
Merge pull request #305 from fhillemann/fhillemann-fig-1 [ci skip]
This build is based on
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/62e51b8b993037bb5cc302309cb8c9b983e00378.

This commit was created by the following CI build and job:
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/62e51b8b993037bb5cc302309cb8c9b983e00378/checks
https://github.com/SORTEE-Github-Hackathon/manuscript/actions/runs/4108433864

@@
 This manuscript
-(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/659dbf07d94474726c8403d04555afbb3a45da57/}{permalink})
+(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/62e51b8b993037bb5cc302309cb8c9b983e00378/}{permalink})
 was automatically generated
-from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/659dbf07d94474726c8403d04555afbb3a45da57}{SORTEE-Github-Hackathon/manuscript@659dbf0}
+from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/62e51b8b993037bb5cc302309cb8c9b983e00378}{SORTEE-Github-Hackathon/manuscript@62e51b8}
 on February 6, 2023.

### 2023-02-15 editorial-communication/response-to-the-reviewers.Qmd

@@
 
-We would like to thank you and the reviewers for the thoughtful comments and for the opportunity to submit a revised version of our manuscript "", for consideration for publication in Methods in Ecology and Evolution.
+We would like to thank you and the reviewers for the thoughtful comments and for the opportunity to submit a revised version of our manuscript "Not just for programmers: How GitHub can accelerate collaborative and reproducible research in ecology and evolution", for consideration for publication in Methods in Ecology and Evolution.
 
-We have addressed all the suggestions that you and the reviewers provided and, as before, we provide a point-by-point detailed response discussing each comment or suggestion.
+We have addressed all the suggestions that you and the reviewers provided. 
+We provide a point-by-point detailed response discussing each comment or suggestion.
 Our responses are mirror-indented, while the editor's and reviewers' comments are numbered.
@@
 
-We have rewritten several sentences to improve their clarity, decrease the complexity and length of sections, and improved the readability of figures.
+Briefly, we have rewritten several sentences to improve their clarity, decrease the complexity and length of sections. 
+We also improved the readability of figures.
+
+We hope that our revision has further improved this manuscript.
+We thank you again for your time and for the opportunity to submit this revised version of the manuscript.
+We very much look forward to hearing from you.
 
@@
 We added a discussion on how repositories can be kept private to the section "Storing and sharing research compendia" (between lines XXX and XXX) and in the "Open science discussion" (between lines XXX and XXX).
-We emphasize that there should not be a trade-off between privacy, collaboration, and open science practices.
+We emphasized that there should not be a trade-off between privacy, using GitHub for collaboration, and open science practices.
 
@@
 > Other scientists may simply lack the time or incentives to document and version control their code if the code is unlikely to be reused beyond their analysis.
-> However we (and others, \_e.g.,\_ \[\@doi:10.1098/rspb.2022.1113\]) argue that the endeavour of open science and collaboration requires code owners to document and version control code despite uncertainty around future use.
+> However, we (and others, \_e.g.,\_ \[\@doi:10.1098/rspb.2022.1113\]) argue that the endeavour of open science and collaboration requires code owners to document and version control code despite uncertainty around future use.
 
@@
 Thank you for this recommendation!
-We now discuss the possibility of integrating GitHub into existing workflows on Overleaf, Google Drive, and DropBox among other services to collaboratively write scientific manuscripts, in the section "Writing a manuscript" <!--# add line numbers -->.
+We now discuss the possibility of integrating GitHub into existing workflows on Overleaf, Google Drive, and DropBox among other services to collaboratively write scientific manuscripts, in the section "Writing a manuscript" (between lines XXX and XXX) <!--# add line numbers -->.
 We refer to Table 1 for further details on these integrations.
 :::
-
 ##### **E1.5.** Finally, DropBox, SharePoint, and OneDrive are file-sharing systems that include version control, are widely supported, especially in colleges and universities, and are much easier to use for those who might be uncomfortable learning a system such as GitHub.
@@
 ::: {#ResponseE15 .response}
-We think this is a good point since many readers may not immediately see the value in a time investment to learn a new tool when they are comfortable with tools that meet many or most of their needs.
+We think this is a good point since many readers may not immediately see the value in a time investment to learn a new tool when they are already comfortable with tools that meet many or most of their needs.
 Rather than creating a new section, we identify specific points in the manuscript where we discuss how GitHub enables different and better types of collaboration and open science than alternative platforms, such as Dropbox or Google Suite.
@@
 
-\
 In the first paragraph of the introduction we made the text more concise throughout and also added new sentence <!--# add line number -->:
@@
 
-## Reviewer: 2 {#sec-R2}
+## Recommendations from Reviewer 2 (R2) {#sec-R2}
 
@@
 ::: {#ResponseR24 .response}
-Response
+
+Thank you for this recommendation.
+We recognize that these are developments that have been increasingly encourage to be adopted in biological research.
+We now provide brief comments on how automation can aid unit testing of research code (between lines XXX and XXX), and that automation can also help the interpretation, integration and usage of data and software across different sources.
+
 :::

### 2023-02-15 manuscript.tex
Merge pull request #307 from SORTEE-Github-Hackathon/phpb-edits-textual-improvements [ci skip]
This build is based on
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/0f535fb40daf2d5e43a8b34dbd7ecf45fdb6cded.

This commit was created by the following CI build and job:
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/0f535fb40daf2d5e43a8b34dbd7ecf45fdb6cded/checks
https://github.com/SORTEE-Github-Hackathon/manuscript/actions/runs/4187693537

@@
 This manuscript
-(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/62e51b8b993037bb5cc302309cb8c9b983e00378/}{permalink})
+(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/0f535fb40daf2d5e43a8b34dbd7ecf45fdb6cded/}{permalink})
 was automatically generated
-from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/62e51b8b993037bb5cc302309cb8c9b983e00378}{SORTEE-Github-Hackathon/manuscript@62e51b8}
-on February 6, 2023.
+from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/0f535fb40daf2d5e43a8b34dbd7ecf45fdb6cded}{SORTEE-Github-Hackathon/manuscript@0f535fb}
+on February 15, 2023.
 
@@
 
-Researchers in ecology and evolutionary biology are increasingly dependent on computational code to conduct research, and the use of efficient methods to share, reproduce, and collaborate on code as well as any research-related documentation has become fundamental.
+Researchers in ecology and evolutionary biology are increasingly dependent on computational code to conduct research.
+Hence, the use of efficient methods to share, reproduce, and collaborate on code as well as document research is fundamental.
 GitHub is an online, cloud-based service that can help researchers track, organize, discuss, share, and collaborate on software and other materials related to research production, including data, code for analyses, and protocols.
@@
 Despite these benefits, the use of GitHub in ecology and evolution is not widespread.
-To help researchers in ecology and evolution adopt useful features from GitHub in their own workflows, we review twelve practical ways to use the platform.
+To help researchers in ecology and evolution adopt useful features from GitHub to improve their research workflows, we review twelve practical ways to use the platform.
 We outline features ranging from low to high technical difficulty: storing code, managing projects, coding collaboratively, conducting peer review, and writing a manuscript.
@@
 Perkel, 2016}){]}.
-Of all the tools mentioned above, GitHub is uniquely positioned (\protect\hyperlink{tbl:compare}{Table 1}) to benefit scientists because the platform is designed to enable collaboration on computer code--a fundamental component of modern research.
-However, most researchers lack exposure to adequate code practices and thus dedicate valuable time and effort to self-teaching research-facilitating tools.
-GitHub is one of the most used web-based platforms for computational version control and collaboration, and in this paper we provide researchers in ecology and evolutionary biology (EEB) with practical workflows to use GitHub to facilitate and improve their code and its management.
+Within the spectrum of cloud-based services for collaboration, GitHub is uniquely positioned (\protect\hyperlink{tbl:compare}{Table 1}) to benefit scientists because it is designed to store, track changes, and enable collaboration on computer code -- fundamental components of modern research.
+Albeit, most researchers lack exposure to adequate programming and coding practices and thus dedicate valuable time and effort to self-teaching research-facilitating tools.
+GitHub is one of the most used web-based platforms for computational version control and collaboration, and in this paper, we provide researchers in ecology and evolutionary biology (EEB) with practical workflows to use GitHub to facilitate their collaborative research and code management practices.
 
 GitHub (\url{https://github.com}) provides a simple but powerful web interface that allows users to participate in projects by contributing, modifying and discussing existing code, reporting bugs, discovering code and data, and publishing new code.
-Through version control, users have a detailed, chronological record of the files and directories stored in their repositories (\protect\hyperlink{ref-RVetqmsg}{Bryan, 2018}) (see \protect\hyperlink{definitions}{Box 1}).
-Additionally, unlike sharing documents and code via DropBox or Google Drive links, GitHub defaults to public sharing of code and documents and has features like Issues and Discussions (see \protect\hyperlink{definitions}{Box 1}) that can immediately and directly contribute to more open science and knowledge sharing.
-This workflow provides a strong and clear advantage over sending files back-and-forth (\emph{e.g.}, via email), a process that can become challenging and time-consuming in long-term and collaborative projects (\protect\hyperlink{ref-4ny1onB0}{Ram, 2013}).
-Through its combination of version control and collaborative features, GitHub facilitates open-source code alongside collaborative development (\protect\hyperlink{ref-kEX5dgzK}{Perez-Riverol et al., 2016}).
-
-Git is the version control system that enables all the collaborative tools available on GitHub.
-Git was originally developed as a fast, lightweight and open-source system that would allow software engineers to efficiently develop and collaborate in projects (\protect\hyperlink{ref-1CM2EcdVk}{\emph{Git - A Short History of Git}, n.d.}).
-Since its launch in 2005, Git has become the leading version control system in software development and in other disciplines that similarly require collaboration and community contributions, such as scientific research (\protect\hyperlink{ref-7q3wZN6d}{Spinellis, 2012}).
-Although the understanding of basic concepts of Git (such as commit, push, pull, checkout; see \protect\hyperlink{definitions}{Box 1}) is necessary, the GitHub web-based platform and its integrated development environments (such as GitHub Desktop) allow users to perform most repository and data management operations without opening Git command-line sessions, making these functionalities available to users who are less familiar with software development.
-
-Version control involves tracking the state of the files in a folder, called a ``repository'' (see \protect\hyperlink{definitions}{Box 1}), through the evolution of a project.
-A basic workflow using git and GitHub is to 1) make changes to files in a repository on your computer, 2) record related changes in files as a ``commit'' (see \protect\hyperlink{definitions}{Box 1}) along with a message describing the changes, 3) synchronize commits with GitHub (see ``push'' in \protect\hyperlink{definitions}{Box 1}) so that the repository on the web is up to date.
-Collaborators can then view your changes online and synchronize them to their own computers (see ``pull'' in \protect\hyperlink{definitions}{Box 1}).
-Commits act like snapshots and one can view or even revert the state of the project to any previous commit.
-If the modified files are plain text (\emph{e.g.} computer code or .txt files), only the differences from the previous commit are recorded, allowing you to frequently commit changes without causing the size of the project to grow excessively.
-This provides a safe and less cluttered alternative to frequently making full copies of documents at different points in their evolution (\emph{e.g.} analysis.R, analasys\_v2.R, analysis\_FINAL.R).
-More technical details about the use of Git and GitHub are beyond the scope of this paper (but see Perez-Riverol et al.
+Github allows users to store files and directories in repositories, and keeps a chronological record of modifications (\protect\hyperlink{ref-RVetqmsg}{Bryan, 2018}) (see \protect\hyperlink{definitions}{Box 1}).
+Beyond storage and record-tracking, file management in GitHub is integrated with several communication features, allowing users to engage in discussions, to plan and collaborate in code, and publish information to a webpage (Github Issues, Github Discussions, Github Pages; see \protect\hyperlink{definitions}{Box 1}).
+These features contrast with traditional practices of directly sharing files through email, other cloud-based services or physical storage units, which become challenging and time-consuming in long-term and collaborative projects (\protect\hyperlink{ref-4ny1onB0}{Ram, 2013}).
+By allowing users to easily integrate versioning, communication, collaboration with research code and data, Github paves the way for easier implementation of open science practices within research projects (\protect\hyperlink{ref-kEX5dgzK}{Perez-Riverol et al., 2016}).
+
+Git is the version control system that enables the collaborative tools available on GitHub.
+Git was originally developed as a fast, lightweight and open-source system to allow software engineers to efficiently develop and collaborate in projects (\protect\hyperlink{ref-1CM2EcdVk}{\emph{Git - A Short History of Git}, n.d.}).
+Since its launch in 2005, Git has become the leading version control system in software development and in other disciplines that require collaboration and community contributions, such as in scientific research (\protect\hyperlink{ref-7q3wZN6d}{Spinellis, 2012}).
+Knowledge of basic concepts of Git (such as commit, push, pull, and checkout; see \protect\hyperlink{definitions}{Box 1}) is recommended to understand how GitHub keeps track of changes to files and folders.
+Nevertheless, the GitHub web-based platform and its integrated development environments (such as GitHub Desktop) allow users to perform most repository and data management operations without using the command console, making these functionalities available to users who are less familiar with software development.
+
+Version control involves tracking the state of the files and directories which are stored in a ``repository'' (see \protect\hyperlink{definitions}{Box 1}).
+A basic workflow using Git and GitHub is to: (i) create a remote repository that is synchronized with files and directories stored locally; (ii) modify these files, either locally or remotely; (iii) frequently ``commit'' (or record) changes to these files (see \protect\hyperlink{definitions}{Box 1}) along with a description of modifications; (iv) synchronize commits with GitHub (see ``push'' and ``pull'' in \protect\hyperlink{definitions}{Box 1}) so that the repository on the web and the local repositories are up-to-date.
+Repositories, which contain files, their modifications, and the description of their changes can then be accessed by chosen collaborators or, whenever applicable, the public, who can easily download and synchronize them to their own computers (see ``clone'' in \protect\hyperlink{definitions}{Box 1}).
+Commits act like snapshots, one can view or even revert the state of the project to any previous commit.
+If the modified files are plain text, only the differences from the previous commit are recorded, allowing you to frequently commit changes without causing the size of the project to grow excessively.
+This provides a safe and less cluttered alternative to frequently making full copies of documents at different points in their evolution (\emph{e.g.} \texttt{analysis.R}, \texttt{analysis\_v2.R}, \texttt{analysis\_FINAL.R}).
+While focusing on technical details about the use of Git and GitHub is beyond the scope of this study, we recommend users explore available resources to become more familiar with version control features (but see Perez-Riverol et al.
 (\protect\hyperlink{ref-kEX5dgzK}{2016}), Blischak et al.
@@
 Many researchers begin using GitHub to backup their research compendium (\protect\hyperlink{ref-MwwMapRG}{Marwick et al., 2018}) into a centralized, readily-available remote server (see \protect\hyperlink{definitions}{Box 1}).
-A centralized research compendium stored in a version-controlled repository has the advantages of facilitating collaboration, integrating data and code archiving, allowing file versions to be accessed and restored, and further contributing to open science practices (Borghi \& Van Gulick (\protect\hyperlink{ref-gLby7jt1}{2022})).
-Every change made to files in a version-controlled repository accompany a description of modifications and are authored (\protect\hyperlink{definitions}{Box 1}).
-Later, the entire history of commits and their commit messages are viewable and can be audited similar to a physical laboratory notebook (\protect\hyperlink{ref-4ny1onB0}{Ram, 2013}).
-On GitHub, code can be made public, and the process of forking and submitting pull requests (see \protect\hyperlink{definitions}{Box 1}) ensures code owners have full control over code and documents in a repository.
-The ability to make a GitHub repository private is particularly advantageous for storing materials without necessarily sacrificing privacy, which may be preferred or even essential for certain compendia.
-Researchers can then grant specific collaborators read and/or write access to private repositories to pursue pre-publication analyses or writing in privacy, or even to collaborate on research that will permanently remain private.
-
-GitHub limits committed file sizes to 100 Mb (megabytes) (\protect\hyperlink{ref-1Co6ZZjF1}{\emph{About Large Files on GitHub}, n.d.}), which can may require external file storage alternatives (such as local or cloud-hosting) for some parts of research compendia.
-However, with some additional setup, users can still track versions of these external files in their repositories using Git Large File Storage (\url{https://git-lfs.github.com}).
+This practice has the advantages of facilitating collaboration, integrating data and code archiving, allowing file versions to be accessed and restored, and further contributing to open science practices (Borghi \& Van Gulick (\protect\hyperlink{ref-gLby7jt1}{2022})).
+Every change made to files in version-controlled repositories accompany authored descriptions of modifications (\protect\hyperlink{definitions}{Box 1}).
+Later, the entire history of commits and their commit messages are viewable and can be audited similarly to physical laboratory notebooks (\protect\hyperlink{ref-4ny1onB0}{Ram, 2013}).
+GitHub allows administrative control over who can view and modify repositories, and the process of cloning, forking and suggesting changes through pull requests (see \protect\hyperlink{definitions}{Box 1}) ensures code owners have full control over code and documents.
+Repositories can be changed from public to private, allowing data storage and management without sacrificing the privacy that may be necessary for certain compendia.
+With this, researchers can grant collaborators read and/or write access to files in private repositories to pursue pre-publication analyses or writing in privacy.
+
+GitHub limits committed file sizes to 100 Mb (megabytes) (\protect\hyperlink{ref-1Co6ZZjF1}{\emph{About Large Files on GitHub}, n.d.}), which may require external file storage alternatives (such as local or cloud-hosting) for some parts of research compendia.
+However, users can still track versions of remotely- or locally-stored files in their repositories using Git Large File Storage (\url{https://git-lfs.github.com}).
 
@@
 Projects in ecology and evolution often involve research professionals holding limited-term positions, such as graduate students, research assistants, and post-doctoral fellows (\protect\hyperlink{ref-D4C4k4ak}{Fehr et al., 2021}).
-Without clear plans on project continuity, the research code and data management upkeep tend to fall off as researchers move on to new projects or other institutions.
-Additionally, code and data can be difficult to access when kept only on personal devices (\protect\hyperlink{ref-19kmNxiHc}{Vines et al., 2014}).
-
-GitHub can facilitate project continuity among research code by making code handover easier (\protect\hyperlink{ref-D4C4k4ak}{Fehr et al., 2021}; \protect\hyperlink{ref-4ny1onB0}{Ram, 2013}).
-Through version control, the history of code and data from projects in ecology and evolution can be tracked accessible to future laboratory members and collaborators (\protect\hyperlink{ref-3DKwn1sY}{Lowndes et al., 2017}).
-Repositories and organizations can have designated data and code owners {[}or more appropriate, stewards; see Hampton et al.
-(\protect\hyperlink{ref-iIEKCTLU}{2015}), \emph{About Code Owners} (\protect\hyperlink{ref-s91uGRZ2}{n.d.}){]}, who can also change through time allowing for the transition of code between research cohorts (see also \protect\hyperlink{organizations}{``Organizing and managing teams''}).
-Other project collaborators can contribute to repository design and development, and their active involvement can both aid authors ability to act as guarantors of the project, and the clarity and reproducibility of the project for future users.
-In (Figure \ref{fig:github-diagram}), we highlight several elements of good repository structure, and the various ways that contributors may interact with them.
-
-GitHub also allows users to describe and store information about software and code dependencies, ensuring that code can run using the same version of software as when it was initially developed.
-This can be achieved through the access of GitHub repositories containing the necessary releases of such software, or through the use of automated Github Actions with specific software versions.
-
-GitHub can facilitate lab continuity by being used as a platform for storing, selectively sharing, and easily updating lab policies and experimental protocols.
-Researchers have been increasingly using GitHub to maintain versions and share digital laboratory handbooks across many fields (\protect\hyperlink{ref-10ghgV3S8}{J.
+Without clear plans on project continuity, research code and data management upkeep tends to fall off as researchers move on to new projects or other institutions.
+Additionally, code and data can be difficult to access and recover when kept only on personal devices (\protect\hyperlink{ref-19kmNxiHc}{Vines et al., 2014}).
+
+GitHub can facilitate project continuity in research by making code and data handover between users easier (\protect\hyperlink{ref-D4C4k4ak}{Fehr et al., 2021}; \protect\hyperlink{ref-4ny1onB0}{Ram, 2013}).
+Through version control, the history of code and data from projects in ecology and evolution becomes accessible to future laboratory members and collaborators (\protect\hyperlink{ref-3DKwn1sY}{Lowndes et al., 2017}).
+Repositories and organizations can have designated data and code owners {[}or more appropriately, ``data stewards''; see Hampton et al.
+(\protect\hyperlink{ref-iIEKCTLU}{2015}), \emph{About Code Owners} (\protect\hyperlink{ref-s91uGRZ2}{n.d.}){]}, who can also change through time, allowing for the transition of code between research cohorts (see also \protect\hyperlink{organizations}{``Organizing and managing teams''}).
+Other project collaborators can contribute to repository design and development, and their active involvement can both aid authors ability to act as guarantors, and the clarity and reproducibility of the project for future users.
+In (Figure \ref{fig:github-diagram}), we highlight several elements of recommended repository structure, and the various ways that contributors may interact with them.
+
+Software compatibility during the analysis and reanalysis of project data can be ensured by storing information about software dependencies and their versions within the same project repository.
+With more advanced practices, one can remotely install and execute scripts using specific versions of software within GitHub's project automation tools, GitHub Actions (see below).
+
+In addition to projects, long-term management of laboratory materials (such as notebooks or experimental protocols) can also be done within GitHub, a practice that has been increasingly adopted across many fields (\protect\hyperlink{ref-10ghgV3S8}{J.
 Perkel, 2016}), including applied ecology (\emph{e.g.}, \url{https://scheuerell-lab.github.io/lab-book}), biogeography and global change biology (\emph{e.g.}, \url{https://github.com/HuckleyLab/how_we_work}), and microbial ecology (\emph{e.g.}, \url{https://github.com/CarBBAS/uqam-guide}).
@@
 
-Syllabi, presentations, and other course materials can be version-controlled and stored in GitHub.
-Although plain text formats such as markdown or HTML work best with GitHub and help to keep the total size of the repository within limits, any file type can be stored on and downloaded from GitHub including PowerPoint and Word documents.
-Content can then be delivered by sharing a link to the GitHub repository or creating a template repository with assignments that students can use.
-Using GitHub to host a course website is also an option for making course content more widely and easily accessible (see \protect\hyperlink{hosting-a-website}{Hosting a Website}).
-
-Using GitHub to collect student submissions is more advanced, but the new GitHub Classroom tool (\url{https://classroom.github.com}) allows instructors to host private assignments to be submitted collaboratively or individually as code or PDF files, and even build auto-grading tests.
-Using GitHub for course management may take an additional time investment compared to traditional tools, but integrating version control and GitHub into course content can boost students' feelings of self-efficacy and confidence (\protect\hyperlink{ref-dqrFjoSb}{Trujillo \& Tanner, 2014}).
+Syllabi, presentations, and other course materials can be version-controlled, stored and managed in GitHub.
+While any file type for presentations and documents can be stored and tracked in repositories, GitHub can directly render and display certain markup languages, such as HyperText Markup Language (HTML) and Markdown documents, making these file types especially useful for educational materials.
+Course content can then be delivered to the audience by sharing links of web-hosted GitHub Pages (see \protect\hyperlink{hosting-a-website}{Hosting a Website}), GitHub Repositories and/or GitHub Organizations.
+Finally, instructors can host and assign student work to be submitted collaboratively or individually as code and text files, and even build autograding tests using the GitHub Classroom tool (\url{https://classroom.github.com}).
+
+Although time-consuming, adopting these features in classrooms can integrate the learning of version-control and GitHub practices with the learning of course contents, and thus boost students' feelings of self-efficacy and confidence (\protect\hyperlink{ref-dqrFjoSb}{Trujillo \& Tanner, 2014}).
 
@@
 Despite researchers in ecology and evolution generally lacking experience in building or hosting webpages, many tools have been developed to help this process.
-Simple websites can consist of a single HTML or markdown document that will be rendered as a website by activating GitHub's Pages (\url{https://pages.github.com}) feature.
-More complex websites can now be easily built from templates that can be found on GitHub (\url{https://github.com/topics/website-template}) or generated using literate programming tools like Quarto (\url{https://quarto.org}) and RMarkdown (e.g.~with the \texttt{blogdown} package).
-These can be customized by editing text files and GitHub Pages will automatically generate and publish the resulting website.
-These methods of creating and hosting websites on GitHub pages lack a graphical user interface; however, free hosting, widely available template customization, and versioning are strong advantages over alternatives (\emph{e.g.}, Wix, Weebly, Google Sites).
-
-\hypertarget{archiving-citable-code-and-data}{%
-\subsubsection{Archiving citable code and data}\label{archiving-citable-code-and-data}}
+Static websites can now be easily built {[}using, for example Quarto (\url{https://quarto.org}), RMarkdown, Hugo (\url{https://gohugo.io}), GitHub Website templates (\url{https://github.com/topics/website-template})){]}, stored in a repository, and be readily hosted by activating GitHub's Pages (\url{https://pages.github.com}) feature.
+Creating and hosting websites on GitHub Pages is more complex than out-of-the-box platforms (\emph{e.g.}, Wix, Weebly, Google Sites).
+However, free hosting, widely available template customization, and versioning are strong advantages over alternatives.
+
+\hypertarget{archiving-citable-code}{%
+\subsubsection{Archiving citable code and data}\label{archiving-citable-code}}
 
@@
 Also, GitHub does not issue Digital Object Identifiers (DOI) for content uploaded to their servers.
-DOIs are persistent and citable unique alpha-numeric identifiers assigned to digitally stored research materials.
+DOIs are persistent and citable unique alpha-numeric identifiers assigned to digitally-stored research materials.
 Because of this, scientists sharing code and data through GitHub are strongly encouraged to independently submit their research materials to long-term data archives (\emph{e.g.}, Zenodo, Figshare, Dryad, OSF (\protect\hyperlink{ref-1Du6fzB8g}{Crystal‐Ornelas et al., 2021}; \protect\hyperlink{ref-kEX5dgzK}{Perez-Riverol et al., 2016}; \protect\hyperlink{ref-10ghgV3S8}{J.
@@
 
-In academic settings, GitHub can serve as a platform for everyone (advisors, advisees, collaborators) to share in-progress work, and flag specific challenges or questions for each other (\protect\hyperlink{tbl:roles}{Table 2}).
-Periodic code review (\protect\hyperlink{ref-hm9PaCLD}{Song et al., 2020}) is useful for identifying errors early in the scientific process, and informing further training and mentorship to fill gaps in skills.
-This is facilitated by a group of core features of git and GitHub that allow contributors to work simultaneously on the same project without interfering with each other's work.
-``Branching'' and ``forking'' (see \protect\hyperlink{definitions}{Box 1}) allow users to work independently on a linked copy of a repository and then later merge their changes into the main project.
-When a set of related changes contributing some new feature or milestone are ready to be evaluated and merged, one makes a ``pull request'' (see \protect\hyperlink{definitions}{Box 1}).
-Pull requests are a formalized way of integrating changes to avoid conflicts that arise when users make simultaneous edits to the same parts of files (\protect\hyperlink{ref-1BJcvyTmV}{Vale et al., 2019}).
-The GitHub interface for a pull request allows collaborators to comment on specific lines of code/text being changed and even to provide suggestions that the pull request author can implement with the click of a button, greatly facilitating peer review.
+GitHub can serve as a platform for everyone working with research (\emph{e.g.}, supervisors or advisors, graduate students, postdoctoral fellows, and collaborators) to share in-progress work, and flag specific challenges or questions for each other (\protect\hyperlink{tbl:roles}{Table 2}).
+Periodic code, data and text review is useful for identifying errors early in the research process (\protect\hyperlink{ref-hm9PaCLD}{Song et al., 2020}), and informing further training and mentorship to fill gaps in skills.
+This is facilitated by a group of core features of Git and GitHub that allow contributors to discuss and simultaneously work on a project.
+For instance, users can clone and fork repositories (see \protect\hyperlink{definitions}{Box 1}), allowing for modifications to be done on a linked copy of a repository, which can then later be merged into the main project through pull requests.
+Collaborators can comment on specific lines of code and text or suggest changes, which can then be incorporated with the click of a button, greatly facilitating peer review.
+Explicit project organization and increased communication within pull requests, in GitHub Issues, or in GitHub Discussions can help with project development and with potential merge conflicts due to users simultaneously working on the same sections.
 Moreover, version control (\protect\hyperlink{ref-K7nbP1Ty}{Crystal-Ornelas et al., 2023}) allows researchers to make changes in code or documents without worrying about irreparably modifying someone else's work.
+
 By enabling more comprehensive remote collaboration, GitHub encourages the exchange of ideas among researchers at different institutions and in different countries, which can serve to improve the quality of the research itself by providing open access to data and code.
 
-\hypertarget{writing-a-manuscript}{%
-\subsubsection{Writing a manuscript}\label{writing-a-manuscript}}
+\hypertarget{writing-manuscript}{%
+\subsubsection{Writing a manuscript}\label{writing-manuscript}}
 
@@
 Writing a manuscript and storing its associated data and code in GitHub increases scientific reproducibility because text, code, and data can be found in one place.
-Writing a manuscript on GitHub may take more time when compared to using conventional text processors (\protect\hyperlink{ref-4ny1onB0}{Ram, 2013}).
-Nevertheless, GitHub has many features that can allow for a powerful collaborative workflow when writing manuscripts.
+Although it may involve more initial time investment for setup, GitHub has many features that support a powerful collaborative workflow when writing manuscripts (\protect\hyperlink{ref-4ny1onB0}{Ram, 2013}).
 Text documents stored and versioned in GitHub can be instantly displayed when written in Markdown, a lightweight markup language increasingly popular among scientists.
@@
 Incorporating GitHub into the process of writing a manuscript does not necessarily mean pivoting to an entirely new workflow.
-For instance, authors who prefer writing in LaTeX can link their new or existing Overleaf projects to GitHub via the Git-Bridge and GitHub Synchronization features (\protect\hyperlink{tbl:compare}{Table 1}), which are available through premium subscriptions to Overleaf or through many institutions worldwide via the Overleaf Commons service (\url{https://www.overleaf.com/for/universities}) (\protect\hyperlink{ref-oGbKxHzj}{\emph{Using Git and GitHub}, n.d.}).
-Similar GitHub integrations are available for projects stored in DropBox, Google Drive, among other popular tools that are likely to be familiar to many scientists and their collaborators (\protect\hyperlink{tbl:compare}{Table 1}).
+For instance, authors who prefer writing in LaTeX or Markdown can synchronize Overleaf (\protect\hyperlink{ref-oGbKxHzj}{\emph{Using Git and GitHub}, n.d.}), HackMD (\url{https://hackmd.io}), and other platforms directly with a GitHub repository.
+Similar GitHub integrations are available for projects stored in DropBox, Google Drive, among other popular tools familiar to many scientists and their collaborators (\protect\hyperlink{tbl:compare}{Table 1}).
 
@@
 Manubot uses GitHub's automation workflow, GitHub Actions, to combine and convert individual Markdown files into a single LaTeX document, which can then be converted to a Word or PDF document, and displayed as a webpage.
-Citations and bibliographic references are automatically managed with citable persistent identifiers (\emph{e.g.}, DOIs, PubMed IDs, ISBNs, URLs).
+Citations and bibliographic references are automatically managed with citable persistent identifiers (\emph{e.g.}, DOI, PubMed ID, ISBN, URL).
 The resulting manuscript can be rendered with document templates and citation style language formatting to meet journal formatting requirements.
@@
 
-Peer review is the standard process for assessing and judging whether research done in ecology and evolution should be published in a scientific journal.
+Peer review is the standard process for assessing whether research done in ecology and evolution should be published in a scientific journal.
 GitHub provides an open and transparent platform that can be used for either directly providing feedback on research products or addressing changes recommended by reviewers.
-GitHub Issues can be used to organize and discuss reviewer suggestions and to assign them to co-authors (\emph{e.g.}, \url{https://github.com/SORTEE-Github-Hackathon/manuscript/issues?q=label\%3A\%22Reviewer+Comment\%22+}).
-When reviewer comments are posted as separate issues, authors can comment on the issues to discuss possible changes and assign themselves to indicate which comments they intend to handle.
-Co-authors can then integrate their edits and responses to reviewers using pull requests.
+GitHub Issues can be used to organize and discuss reviewer suggestions and to assign them to co-authors (\emph{e.g.}, \url{https://github.com/SORTEE-Github-Hackathon/manuscript/issues?q=label\%3A\%22Reviewer+Comment\%22}).
+When reviewer comments are posted as separate issues, authors can comment on the issues to discuss possible changes and assign co-authors who will address the issue.
+Co-authors can then integrate their edits and responses to reviewers using pull requests, which can be directly linked to the issues they address.
 
@@
 Certain journals or software development communities require submitted work or research code to be hosted on GitHub and their review processes make use of GitHub Issues (\emph{e.g.}, rOpenSci (\url{https://ropensci.org/software-review/}), Journal of Open Source Software (\url{https://joss.readthedocs.io/en/latest/submitting.html})).
-rOpenSci's efforts have resulted in many well-used R packages for ecology research including \texttt{rfishbase} (\protect\hyperlink{ref-Xsdcv6q}{Boettiger et al., 2012}) and \texttt{taxize} (\protect\hyperlink{ref-FVBWKkZu}{Chamberlain \& Szöcs, 2013}).
 
@@
 This transparency can be extended beyond co-authors to the entire scientific community and to the public.
-Supplying code for (novel) methods that are proposed or used reduces barriers to knowledge, improving the ability of others to build on existing work.
-This results in greater proliferation and accessibility for a broader audience.
+Supplying code for novel or currently used methods reduces barriers to knowledge, improving the ability of others to build on existing work.
+This practice results in greater proliferation and accessibility for a broader audience.
 Projects can make use of GitHub Discussions (\url{https://docs.github.com/en/discussions}) to communicate among repository members (collaborators) and to engage with other scientists and the general public.
@@
 
-The desire or need for privacy during the developmental stages of a manuscript or of a larger research project is common in EEB, and this is often perceived as a major barrier to doing science openly through GitHub.
+The desire or need for privacy during the developmental stages of a manuscript or of a larger research project is common in EEB, and this is often perceived as a major barrier to doing science openly.
 Because GitHub repositories can be made private or public at any time, there is no need to choose privacy over open science, or vice-versa.
-As such, repositories can simply be kept private until their contents are ready to be shared publicly, as might occur when a research article is published or when an embargo is lifted.
+Repositories can be kept private until their contents are ready to be shared publicly, as might occur when a research article is published or when an embargo is lifted.
 
@@
 
-Automation has a strong potential to expand the scale and pace of research in ecology and evolution (\protect\hyperlink{ref-cfgXxgt1}{Keitt \& Abelson, 2021}).
-Automation frameworks can streamline many stages of the scientific process, including automated data collection and data validation (\emph{e.g.}, \protect\hyperlink{ref-bhDgD6lF}{Micheletti et al., 2021}; \protect\hyperlink{ref-lXvpQxeN}{Yenni et al., 2018}), automated data analysis (\emph{e.g.}, \protect\hyperlink{ref-Qh7xTLwz}{Beaulieu-Jones \& Greene, 2017}), automated archiving and deployment of data, code and reports (\emph{e.g.}, this manuscript, \protect\hyperlink{ref-SirQKFIz}{White et al., 2018}).
+Automation has the strong potential to expand the scale and pace of research in ecology and evolution (\protect\hyperlink{ref-cfgXxgt1}{Keitt \& Abelson, 2021}).
+Automation frameworks can streamline many stages of the scientific process, including data collection and data validation (\emph{e.g.}, \protect\hyperlink{ref-bhDgD6lF}{Micheletti et al., 2021}; \protect\hyperlink{ref-lXvpQxeN}{Yenni et al., 2018}), data analysis (\emph{e.g.}, \protect\hyperlink{ref-Qh7xTLwz}{Beaulieu-Jones \& Greene, 2017}), unit testing of research code (\emph{e.g.}, \protect\hyperlink{ref-lYazDTau}{Sarma et al., 2016}), archiving and deployment of data, code and reports (\emph{e.g.}, this manuscript, \protect\hyperlink{ref-SirQKFIz}{White et al., 2018}), and the interpretation, integration and usage of data and software across different sources (see \protect\hyperlink{ref-1FJhfqfiX}{Pasquier et al., 2017}).
 In this context, small modifications to code and data can be frequently committed and automatically tested, as in continuous integration and continuous deployment practices (\protect\hyperlink{ref-1Ep9EJL6y}{Meyer, 2014}).
 This allows for early detection and correction of errors, potentially improving confidence in scientific development by minimizing software errors (see \protect\hyperlink{ref-ufw0ZdnI}{Soergel, 2015}).
-In addition to increasing scientific rigor and confidence in ecological software (\protect\hyperlink{ref-12103x16N}{Scheller et al., 2010}), automation can help advance more rapidly sharing ecological data and making sure the data are high quality (\protect\hyperlink{ref-rTbinQMj}{Dietze et al., 2018}).
+In addition to increasing scientific rigour and confidence in ecological software (\protect\hyperlink{ref-12103x16N}{Scheller et al., 2010}), automation can help advance more rapidly sharing ecological data and making sure the data are high quality (\protect\hyperlink{ref-rTbinQMj}{Dietze et al., 2018}).
 Integrating automation workflows has been highly encouraged in areas of EEB, including predictive ecology (\protect\hyperlink{ref-mmCOSRfr}{McIntire et al., 2022}), long-term ecological studies (\protect\hyperlink{ref-RxK4CmfR}{Ernest et al., 2018}; \protect\hyperlink{ref-1CJo8lo2v}{Yenni et al., 2019}), and management of species at risk information (\protect\hyperlink{ref-kZzfmBNu}{Naujokaitis-Lewis et al., 2022}).
@@
 These calls come in light of the continuous shift towards open-science and the increasing computational and data requirements in EEB.
-While tools like the Google Suite and DropBox enable rapid sharing and collaboration of some research documents, GitHub brings together features that directly address open science such as tools for soliciting public discussions on code and findings, tracking multiple rounds of edits to files in a sensible way for easy review, and managing complex research projects with many collaborators and goals.
-Until now, resources and practical guidance on using GitHub within the EEB community have been dispersed in blog posts and video tutorials (\protect\hyperlink{tips}{Box 2}).
-These resources have been useful for learning to use GitHub in our own work.
-We expect that situating the main uses of GitHub in EEB into one medium, while adding on our personal perspectives, will be useful to the EEB community.
+While tools like the Google Suite and DropBox enable rapid sharing and collaboration of some research documents, GitHub brings together features that directly integrate open science practices, such as the association of public discussions with data, code and findings, tracking multiple rounds of edits to files in a sensible way for easy review, and managing complex research projects with many collaborators and goals.
+Until now, resources and practical guidance on using GitHub within the EEB community have been dispersed across blog posts, as well as written and video tutorials (\protect\hyperlink{tips}{Box 2}).
+These resources have been useful for learning to use GitHub in our own research, as ecologists and evolutionary biologists.
+We expect that situating the main uses of GitHub in EEB alongside examples in this paper will be useful to the EEB community.
 
@@
 Most of these uses can be quickly integrated into the research practices of users (\emph{e.g.}, storing data, creating virtual notebooks, making code citable).
-Making stored data and code citable usually involves creating a repository on GitHub, pushing code and data, and then integrating a DOI minting service to the repository (\emph{e.g.}, with Zenodo; see below).
-On the other hand, some examples we described here, including course material development, web hosting, and automation, require greater effort and time commitment, but have the potential to make EEB research more open, accessible, and collaborative.
-Managing full research projects or laboratories on GitHub require careful thought as to how to delegate tasks such as reviewing pull requests or creating issues.
-For example, collaboratively authoring a paper using GitHub, as we have done here, involves a learning curve for co-authors less familiar with the intricacies of GitHub, requires overhead to set up the automation framework through GitHub Actions, and especially, the commitment from all co-authors to use GitHub when modifying and reviewing the text.
+Making stored data and code citable usually involves creating a repository on GitHub, pushing code and data, and then integrating a DOI minting service to the repository (\emph{e.g.}, with Zenodo or OSF; see below).
+On the other hand, some cases we described here, including course material development, web hosting, and automation, require greater effort and time commitment, but have the potential to make EEB research more open, accessible, and collaborative.
+Managing full research projects or laboratories on GitHub require careful thought as to how to delegate tasks, such as reviewing pull requests or creating issues.
+For example, collaboratively authoring a paper using GitHub, as we have done here, involves a learning curve for co-authors less familiar with the intricacies of GitHub, requires overhead to set up automation frameworks through GitHub Actions, and especially, the commitment from all co-authors to use GitHub when modifying and reviewing the text.
 Despite the potential applications of GitHub to EEB research, we acknowledge that researchers might still look to other platforms for research collaboration.
@@
 
-Despite its strong collaborative potential, we describe two use cases where GitHub's features fall short of highly collaborative work.
-
-First, real-time document editing is still best performed on other platforms (\emph{e.g.}, cloud-stored documents from Microsoft Word, Google Docs, hackMD (\url{https://hackmd.io/})).
-Second, operations that are dependent on other software might not be easily achievable in GitHub, such as manipulating figures or tables.
+Despite its strong collaborative potential, we describe two use cases where GitHub falls short of highly collaborative work.
+
+First, real-time document editing is still best performed on other platforms (\emph{e.g.}, cloud-stored documents from Microsoft Word, Google Docs, HackMD (\url{https://hackmd.io/})).
+Second, operations that are dependent on software requiring graphical user interfaces might not be easily achievable in GitHub, such as designing and manipulating figures or tables.
 While creating tables and figures can be done through code, users may choose other software to collaboratively brainstorm figures and tables (\emph{e.g}., Google Slides, Google Sheets; but see GitHub Discussions).
@@
 
-GitHub has been available as a platform for more than a decade, its uptake among EEB researchers, especially as a tool for collaboration, has been slow.
+Although GitHub has been available as a platform for more than a decade, its uptake among EEB researchers, especially as a tool for collaboration, has been slow.
 Here, we discuss five potential barriers to GitHub use in EEB:
@@
 \\
-2.
-\textbf{Consider taking free courses}, such as those from Software Carpentry (\protect\hyperlink{ref-pjy75gHr}{Madicken Munk et al., 2019}), and sharing these courses with your lab members or colleagues.
-\\
+2. \textbf{Consider taking free courses}, such as those from Software Carpentry (\protect\hyperlink{ref-pjy75gHr}{Madicken Munk et al., 2019}), and sharing them with your lab members or colleagues. \\
 3.
@@
 GitHub Docs.
-Retrieved February 6, 2023, from \url{https://ghdocs-prod.azurewebsites.net/en/repositories/managing-your-repositorys-settings-and-features/customizing-your-repository/about-code-owners}
+Retrieved February 15, 2023, from \url{https://ghdocs-prod.azurewebsites.net/en/repositories/managing-your-repositorys-settings-and-features/customizing-your-repository/about-code-owners}
 
@@
 GitHub Docs.
-Retrieved February 6, 2023, from \url{https://ghdocs-prod.azurewebsites.net/en/repositories/working-with-files/managing-large-files/about-large-files-on-github}
+Retrieved February 15, 2023, from \url{https://ghdocs-prod.azurewebsites.net/en/repositories/working-with-files/managing-large-files/about-large-files-on-github}
 
@@
 GitHub Docs.
-Retrieved February 6, 2023, from \url{https://ghdocs-prod.azurewebsites.net/en/issues/planning-and-tracking-with-projects/learning-about-projects/about-projects}
+Retrieved February 15, 2023, from \url{https://ghdocs-prod.azurewebsites.net/en/issues/planning-and-tracking-with-projects/learning-about-projects/about-projects}
 
@@
 GitHub Docs.
-Retrieved February 6, 2023, from \url{https://ghdocs-prod.azurewebsites.net/en/communities/setting-up-your-project-for-healthy-contributions/adding-a-license-to-a-repository}
+Retrieved February 15, 2023, from \url{https://ghdocs-prod.azurewebsites.net/en/communities/setting-up-your-project-for-healthy-contributions/adding-a-license-to-a-repository}
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Xsdcv6q}{}}%
-Boettiger, C., Lang, D.
-T., \& Wainwright, P.
-C.
-(2012).
-rfishbase: exploring, manipulating and visualizing FishBase data from R.
-\emph{Journal of Fish Biology}, \emph{81}(6), 2030--2039.
-\url{https://doi.org/10.1111/j.1095-8649.2012.03464.x}
-
 \leavevmode\vadjust pre{\hypertarget{ref-gLby7jt1}{}}%
@@
 \leavevmode\vadjust pre{\hypertarget{ref-6CMMeSeD}{}}%
-Bryan, J., \& TAs, T. S. 545. (n.d.). \emph{STAT 545}. Retrieved February 6, 2023, from \url{https://stat545.com/}
-
-\leavevmode\vadjust pre{\hypertarget{ref-FVBWKkZu}{}}%
-Chamberlain, S. A., \& Szöcs, E. (2013). taxize: taxonomic search and retrieval in R. \emph{F1000Research}, \emph{2}, 191. \url{https://doi.org/10.12688/f1000research.2-191.v2}
+Bryan, J., \& TAs, T. S. 545. (n.d.). \emph{STAT 545}. Retrieved February 15, 2023, from \url{https://stat545.com/}
 
 \leavevmode\vadjust pre{\hypertarget{ref-lx49NGto}{}}%
-\emph{Connect GitHub to a Project - OSF Support}. (n.d.). Retrieved February 6, 2023, from \url{https://help.osf.io/article/211-connect-github-to-a-project}
+\emph{Connect GitHub to a Project - OSF Support}. (n.d.). Retrieved February 15, 2023, from \url{https://help.osf.io/article/211-connect-github-to-a-project}
 
 \leavevmode\vadjust pre{\hypertarget{ref-T03Api6e}{}}%
-\emph{Continuous Integration and Delivery}. (n.d.). CircleCI. Retrieved February 6, 2023, from \url{https://circleci.com/}
+\emph{Continuous Integration and Delivery}. (n.d.). CircleCI. Retrieved February 15, 2023, from \url{https://circleci.com/}
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-NUXbp429}{}}%
-\emph{Features • GitHub Actions}. (n.d.). GitHub. Retrieved February 6, 2023, from \url{https://github.com/features/actions}
+\emph{Features • GitHub Actions}. (n.d.). GitHub. Retrieved February 15, 2023, from \url{https://github.com/features/actions}
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-1CM2EcdVk}{}}%
-\emph{Git - A Short History of Git}. (n.d.). Retrieved February 6, 2023, from \url{https://git-scm.com/book/en/v2/Getting-Started-A-Short-History-of-Git}
+\emph{Git - A Short History of Git}. (n.d.). Retrieved February 15, 2023, from \url{https://git-scm.com/book/en/v2/Getting-Started-A-Short-History-of-Git}
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-ZvrOcg9w}{}}%
-Hester, J. B., the STAT 545 TAs, Jim. (n.d.). \emph{Let's Git started \textbar{} Happy Git and GitHub for the useR}. Retrieved February 6, 2023, from \url{https://happygitwithr.com/}
+Hester, J. B., the STAT 545 TAs, Jim. (n.d.). \emph{Let's Git started \textbar{} Happy Git and GitHub for the useR}. Retrieved February 15, 2023, from \url{https://happygitwithr.com/}
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-3UAritXO}{}}%
-\emph{Issues · fmsabatini/sPlotOpen\_Manuscript}. (n.d.). GitHub. Retrieved February 6, 2023, from \url{https://github.com/fmsabatini/sPlotOpen_Manuscript}
+\emph{Issues · fmsabatini/sPlotOpen\_Manuscript}. (n.d.). GitHub. Retrieved February 15, 2023, from \url{https://github.com/fmsabatini/sPlotOpen_Manuscript}
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Re6Eg2va}{}}%
-\emph{Manubot - Manuscripts, open and automated}. (n.d.). Retrieved February 6, 2023, from \url{https://manubot.org}
+\emph{Manubot - Manuscripts, open and automated}. (n.d.). Retrieved February 15, 2023, from \url{https://manubot.org}
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-1FJhfqfiX}{}}%
+Pasquier, T., Lau, M.
+K., Trisovic, A., Boose, E.
+R., Couturier, B., Crosas, M., Ellison, A.
+M., Gibson, V., Jones, C.
+R., \& Seltzer, M.
+(2017).
+If these data could talk.
+\emph{Scientific Data}, \emph{4}(1).
+\url{https://doi.org/10.1038/sdata.2017.114}
+
 \leavevmode\vadjust pre{\hypertarget{ref-kEX5dgzK}{}}%
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-lYazDTau}{}}%
+Sarma, G.
+P., Jacobs, T.
+W., Watts, M.
+D., Ghayoomie, S.
+V., Larson, S.
+D., \& Gerkin, R.
+C.
+(2016).
+Unit testing, model validation, and biological simulation.
+\emph{F1000Research}, \emph{5}, 1946.
+\url{https://doi.org/10.12688/f1000research.9315.1}
+
 \leavevmode\vadjust pre{\hypertarget{ref-12103x16N}{}}%
@@
 \leavevmode\vadjust pre{\hypertarget{ref-oGbKxHzj}{}}%
-\emph{Using Git and GitHub}. (n.d.). Retrieved February 6, 2023, from \url{https://www.overleaf.com/learn/how-to/Using_Git_and_GitHub}
-
-\leavevmode\vadjust pre{\hypertarget{ref-1BJcvyTmV}{}}%
-Vale, G., Schmid, A., Santos, A.
-R., de Almeida, E.
-S., \& Apel, S.
-(2019).
-On the relation between Github communication activity and merge conflicts.
-\emph{Empirical Software Engineering}, \emph{25}(1), 402--433.
-\url{https://doi.org/10.1007/s10664-019-09774-x}
+\emph{Using Git and GitHub}. (n.d.). Retrieved February 15, 2023, from \url{https://www.overleaf.com/learn/how-to/Using_Git_and_GitHub}
 

### 2023-02-20 manuscript.tex
Merge pull request #308 from SORTEE-Github-Hackathon/fhillemann-fig1 [ci skip]
This build is based on
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/d42ec283f2696204f3fcc8bdcd6835260a492415.

This commit was created by the following CI build and job:
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/d42ec283f2696204f3fcc8bdcd6835260a492415/checks
https://github.com/SORTEE-Github-Hackathon/manuscript/actions/runs/4226653887

@@
 This manuscript
-(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/0f535fb40daf2d5e43a8b34dbd7ecf45fdb6cded/}{permalink})
+(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/d42ec283f2696204f3fcc8bdcd6835260a492415/}{permalink})
 was automatically generated
-from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/0f535fb40daf2d5e43a8b34dbd7ecf45fdb6cded}{SORTEE-Github-Hackathon/manuscript@0f535fb}
-on February 15, 2023.
+from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/d42ec283f2696204f3fcc8bdcd6835260a492415}{SORTEE-Github-Hackathon/manuscript@d42ec28}
+on February 20, 2023.
 
@@
 GitHub Docs.
-Retrieved February 15, 2023, from \url{https://ghdocs-prod.azurewebsites.net/en/repositories/managing-your-repositorys-settings-and-features/customizing-your-repository/about-code-owners}
+Retrieved February 20, 2023, from \url{https://ghdocs-prod.azurewebsites.net/en/repositories/managing-your-repositorys-settings-and-features/customizing-your-repository/about-code-owners}
 
@@
 GitHub Docs.
-Retrieved February 15, 2023, from \url{https://ghdocs-prod.azurewebsites.net/en/repositories/working-with-files/managing-large-files/about-large-files-on-github}
+Retrieved February 20, 2023, from \url{https://ghdocs-prod.azurewebsites.net/en/repositories/working-with-files/managing-large-files/about-large-files-on-github}
 
@@
 GitHub Docs.
-Retrieved February 15, 2023, from \url{https://ghdocs-prod.azurewebsites.net/en/issues/planning-and-tracking-with-projects/learning-about-projects/about-projects}
+Retrieved February 20, 2023, from \url{https://ghdocs-prod.azurewebsites.net/en/issues/planning-and-tracking-with-projects/learning-about-projects/about-projects}
 
@@
 GitHub Docs.
-Retrieved February 15, 2023, from \url{https://ghdocs-prod.azurewebsites.net/en/communities/setting-up-your-project-for-healthy-contributions/adding-a-license-to-a-repository}
+Retrieved February 20, 2023, from \url{https://ghdocs-prod.azurewebsites.net/en/communities/setting-up-your-project-for-healthy-contributions/adding-a-license-to-a-repository}
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-6CMMeSeD}{}}%
-Bryan, J., \& TAs, T. S. 545. (n.d.). \emph{STAT 545}. Retrieved February 15, 2023, from \url{https://stat545.com/}
+Bryan, J., \& TAs, T. S. 545. (n.d.). \emph{STAT 545}. Retrieved February 20, 2023, from \url{https://stat545.com/}
 
 \leavevmode\vadjust pre{\hypertarget{ref-lx49NGto}{}}%
-\emph{Connect GitHub to a Project - OSF Support}. (n.d.). Retrieved February 15, 2023, from \url{https://help.osf.io/article/211-connect-github-to-a-project}
+\emph{Connect GitHub to a Project - OSF Support}. (n.d.). Retrieved February 20, 2023, from \url{https://help.osf.io/article/211-connect-github-to-a-project}
 
 \leavevmode\vadjust pre{\hypertarget{ref-T03Api6e}{}}%
-\emph{Continuous Integration and Delivery}. (n.d.). CircleCI. Retrieved February 15, 2023, from \url{https://circleci.com/}
+\emph{Continuous Integration and Delivery}. (n.d.). CircleCI. Retrieved February 20, 2023, from \url{https://circleci.com/}
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-NUXbp429}{}}%
-\emph{Features • GitHub Actions}. (n.d.). GitHub. Retrieved February 15, 2023, from \url{https://github.com/features/actions}
+\emph{Features • GitHub Actions}. (n.d.). GitHub. Retrieved February 20, 2023, from \url{https://github.com/features/actions}
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-1CM2EcdVk}{}}%
-\emph{Git - A Short History of Git}. (n.d.). Retrieved February 15, 2023, from \url{https://git-scm.com/book/en/v2/Getting-Started-A-Short-History-of-Git}
+\emph{Git - A Short History of Git}. (n.d.). Retrieved February 20, 2023, from \url{https://git-scm.com/book/en/v2/Getting-Started-A-Short-History-of-Git}
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-ZvrOcg9w}{}}%
-Hester, J. B., the STAT 545 TAs, Jim. (n.d.). \emph{Let's Git started \textbar{} Happy Git and GitHub for the useR}. Retrieved February 15, 2023, from \url{https://happygitwithr.com/}
+Hester, J. B., the STAT 545 TAs, Jim. (n.d.). \emph{Let's Git started \textbar{} Happy Git and GitHub for the useR}. Retrieved February 20, 2023, from \url{https://happygitwithr.com/}
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-3UAritXO}{}}%
-\emph{Issues · fmsabatini/sPlotOpen\_Manuscript}. (n.d.). GitHub. Retrieved February 15, 2023, from \url{https://github.com/fmsabatini/sPlotOpen_Manuscript}
+\emph{Issues · fmsabatini/sPlotOpen\_Manuscript}. (n.d.). GitHub. Retrieved February 20, 2023, from \url{https://github.com/fmsabatini/sPlotOpen_Manuscript}
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Re6Eg2va}{}}%
-\emph{Manubot - Manuscripts, open and automated}. (n.d.). Retrieved February 15, 2023, from \url{https://manubot.org}
+\emph{Manubot - Manuscripts, open and automated}. (n.d.). Retrieved February 20, 2023, from \url{https://manubot.org}
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-oGbKxHzj}{}}%
-\emph{Using Git and GitHub}. (n.d.). Retrieved February 15, 2023, from \url{https://www.overleaf.com/learn/how-to/Using_Git_and_GitHub}
+\emph{Using Git and GitHub}. (n.d.). Retrieved February 20, 2023, from \url{https://www.overleaf.com/learn/how-to/Using_Git_and_GitHub}
 

### 2023-02-22 R/Supp_Info_1.tex
Writing part of Appendix S1.1, and removing some code.

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  11pt,
]{article}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
  \setmainfont[]{Times New Roman}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage[margin = 1in]{geometry}
\usepackage{color}
\usepackage{fancyvrb}
\newcommand{\VerbBar}{|}
\newcommand{\VERB}{\Verb[commandchars=\\\{\}]}
\DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
% Add ',fontsize=\small' for more characters per line
\usepackage{framed}
\definecolor{shadecolor}{RGB}{248,248,248}
\newenvironment{Shaded}{\begin{snugshade}}{\end{snugshade}}
\newcommand{\AlertTok}[1]{\textcolor[rgb]{0.94,0.16,0.16}{#1}}
\newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.77,0.63,0.00}{#1}}
\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\BuiltInTok}[1]{#1}
\newcommand{\CharTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
\newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
\newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{#1}}
\newcommand{\DecValTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\ErrorTok}[1]{\textcolor[rgb]{0.64,0.00,0.00}{\textbf{#1}}}
\newcommand{\ExtensionTok}[1]{#1}
\newcommand{\FloatTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\ImportTok}[1]{#1}
\newcommand{\InformationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
\newcommand{\NormalTok}[1]{#1}
\newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.81,0.36,0.00}{\textbf{#1}}}
\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{#1}}
\newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
\newcommand{\RegionMarkerTok}[1]{#1}
\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\StringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\VariableTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\WarningTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\usepackage{lineno}
\linenumbers
\usepackage{setspace}\doublespacing
\usepackage{parskip}
\setlength{\parindent}{4em}
\setlength{\parskip}{0em}
\usepackage{caption}
\usepackage{pdflscape}
\newcommand{\blandscape}{\begin{landscape}}
\newcommand{\elandscape}{\end{landscape}}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

\author{}
\date{\vspace{-2.5em}}

\begin{document}

\hypertarget{study}{%
\subsection{Study}\label{study}}

\hypertarget{not-just-for-programmers-how-github-can-accelerate-collaborative-and-reproducible-research-in-ecology-and-evolution}{%
\subsubsection{Not just for programmers: How GitHub can accelerate collaborative and reproducible research in ecology and evolution}\label{not-just-for-programmers-how-github-can-accelerate-collaborative-and-reproducible-research-in-ecology-and-evolution}}

\hypertarget{supplementary-information-1}{%
\subsubsection{Supplementary Information 1}\label{supplementary-information-1}}

\hypertarget{representing-technical-difficulty-and-degree-of-collaboration-in-use-cases-for-github-in-ecology-and-evolution}{%
\subsubsection{Representing technical difficulty and degree of collaboration in use cases for Github in ecology and evolution}\label{representing-technical-difficulty-and-degree-of-collaboration-in-use-cases-for-github-in-ecology-and-evolution}}

\textbf{Appendix S1.1. Computing indices of technical difficulty and degree of collaboration}

We aimed at distributing the use cases discussed in our study across gradients of technical difficulty and collaboration.
For this, we estimated the perceived degree of collaboration and the perceived level of technical difficulty for each use case.
Each author attributed a value ranging from 1 to 10 to their perceived degree of collaboration for a use case, with one representing a use case that offer very low advantages in terms of collaboration, while ten classified that use case as highly advantageous in terms of collaboration.

We then {[}...{]}.

We used Google Docs and Google Sheets to manipulate data, and plotted results using the basic visualisation functions from \texttt{R} version 4.02.

\noindent
\textbf{Appendix S1.2. Annotated code and prose allowing the representation of indices of technical difficulty and degree of collaboration}

Here, we provide the annotated \texttt{R} code and instructions that are required to load and present the indices of technical difficulty and degree of collaboration of the eleven use cases of GitHub we present in our piece.

(May be removed) \textbf{Goal}: This is a summary figure, e.g., here are all the ways and here are the entry points with low technical difficulty, some for beginners and some more advanced ways to use GitHub.

(May be removed) \textbf{Highlight}: There are ways to use github that allow different degrees of collaboration that do not require too many technical skills.

\hypertarget{data}{%
\subsubsection{Data}\label{data}}

Data was assembled collaboratively using Google Docs, then manually saved as a \texttt{CSV} file called \texttt{scatterblob\_data\_raw.csv} in the \texttt{data} folder.

The collaborative \href{https://docs.google.com/spreadsheets/d/1zCRgctjfjE2xZN9MkqfFh222K6bvVvA3gT0UdkL_CS8/edit\#gid=0}{Google Spreadsheet} features a first column listing the ways to use GitHub that were addressed in the manuscript (Archiving citeable code and data; Storing a research compendium; Project management; Project continuity; Open scientific discussions; Virtual laboratory notebook; Educational materials; Academic websites; Writing a manuscript; Organizing and managing teams; Peer-reviews; Asynchronous collaborative coding and writing; Automation).

The column \emph{Perceived Technical difficulty} corresponds to the degree of difficulty that was perceived by the authors when assembling the data, based on personal experience.
We quickly realized this varied greatly across authors, and that this variation seemed to depend on which github tools were previously known or mastered by the authors.

The columns tagged as \emph{Cognitive load -} showcase a different way to assess technical difficulty of GitHub uses, measured as cognitive load (explained in the next section).

The columns tagged as \emph{degree of collaboration} showcase the span of collaboration that can be achieved with each tool, as perceived by the authors.

\hypertarget{measuring-degree-of-technical-difficulty}{%
\subsubsection{Measuring degree of technical difficulty}\label{measuring-degree-of-technical-difficulty}}

\href{https://docs.google.com/spreadsheets/d/1YipCCdg5Z8w-IQO67rFfMBSTpLjO-_7HiW44gqzTXPM/edit\#gid=0}{Cognitive load} was measured as follows:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  We first created a list of skills that are needed to implement different GitHub uses. These occupied a column each.
\item
  For each GitHub use listed on the first column, we went through each column, and marked a 1 if a skill was needed for that particular GitHub use, and 0 if the skill was not needed.
\item
  The sum of values across columns provides a measure of cognitive load required for a user that is a ``GitHub beginner'' to implement any GitHub use. The column \emph{Cognitive load - real} reflects this number.
\item
  As many GitHub uses tied with the same cognitive load value, we resourced to perceived difficulty to break ties and avoid overlap of uses in the figure, mainly to improve visualization of the data. The column \emph{Cognitive load - real - non-overlapping} shows this adjustment.
\item
  Finally, we ordered the GitHub uses in increasing order following \emph{Cognitive load - real - non-overlapping}, and assigned a sequential value of cognitive load, from 1 to \emph{maximum number of GitHub uses}. This is column \emph{Cognitive load - sequential}
\end{enumerate}

\hypertarget{leading-the-data-csv-file}{%
\subsection{\texorpdfstring{Leading the data \texttt{CSV} file:}{Leading the data CSV file:}}\label{leading-the-data-csv-file}}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{scatterblob\_data }\OtherTok{\textless{}{-}} \FunctionTok{read\_csv}\NormalTok{(}\FunctionTok{here}\NormalTok{(}\StringTok{"data"}\NormalTok{, }\StringTok{"scatterblob\_data\_raw.csv"}\NormalTok{))}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## New names:
## Rows: 13 Columns: 11
## -- Column specification
## -------------------------------------------------------- Delimiter: "," chr
## (5): Ways to use GitHub, Alternative title, Example, ...10, ...11 dbl (6):
## Cognitive load - real, Cognitive load - sequential, Cognitive load ...
## i Use `spec()` to retrieve the full column specification for this data. i
## Specify the column types or set `show_col_types = FALSE` to quiet this message.
## * `` -> `...10`
## * `` -> `...11`
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{head}\NormalTok{(scatterblob\_data)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## # A tibble: 6 x 11
##   Ways t~1 Alter~2 Cogni~3 Cogni~4 Cogni~5 Perce~6 Min d~7 Max d~8 Example ...10
##   <chr>    <chr>     <dbl>   <dbl>   <dbl>   <dbl>   <dbl>   <dbl> <chr>   <chr>
## 1 Archivi~ Citeab~       2       1    2.2        1       1       4 link    <NA> 
## 2 Storing~ Workin~       2       2    2.8        1       1       4 life-l~ 1 = ~
## 3 Project~ Projec~       4       3    4          1       2       5 (e.g.,~ 4 = ~
## 4 Project~ Projec~       4       4    4.7        1       2       4 <NA>    4 = ~
## 5 Open sc~ Develo~       4       5    4.35       1       4       5 https:~ 3 = ~
## 6 Virtual~ Lab ma~       5       6    5.35       4       1       4 link 1~ 3 = ~
## # ... with 1 more variable: ...11 <chr>, and abbreviated variable names
## #   1: `Ways to use GitHub`, 2: `Alternative title`,
## #   3: `Cognitive load - real`, 4: `Cognitive load - sequential`,
## #   5: `Cognitive load - real - non-overlapping`,
## #   6: `Perceived Technical difficulty`, 7: `Min degree of collaboration X1`,
## #   8: `Max degree of collaboration X2`
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{\#  View(scatterblob\_data)}
\end{Highlighting}
\end{Shaded}

Cleaning the raw data and saving it as a \texttt{my\_data} object:

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{names}\NormalTok{(scatterblob\_data)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
##  [1] "Ways to use GitHub"                     
##  [2] "Alternative title"                      
##  [3] "Cognitive load - real"                  
##  [4] "Cognitive load - sequential"            
##  [5] "Cognitive load - real - non-overlapping"
##  [6] "Perceived Technical difficulty"         
##  [7] "Min degree of collaboration X1"         
##  [8] "Max degree of collaboration X2"         
##  [9] "Example"                                
## [10] "...10"                                  
## [11] "...11"
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{scatterblob\_data}\SpecialCharTok{$}\NormalTok{x1 }\OtherTok{\textless{}{-}}\NormalTok{ scatterblob\_data}\SpecialCharTok{$}\StringTok{\textasciigrave{}}\AttributeTok{Min degree of collaboration X1}\StringTok{\textasciigrave{}}
\NormalTok{scatterblob\_data}\SpecialCharTok{$}\NormalTok{x2 }\OtherTok{\textless{}{-}}\NormalTok{ scatterblob\_data}\SpecialCharTok{$}\StringTok{\textasciigrave{}}\AttributeTok{Max degree of collaboration X2}\StringTok{\textasciigrave{}}
\NormalTok{scatterblob\_data}\SpecialCharTok{$}\NormalTok{y\_real }\OtherTok{\textless{}{-}}\NormalTok{ scatterblob\_data}\SpecialCharTok{$}\StringTok{\textasciigrave{}}\AttributeTok{Cognitive load {-} real {-} non{-}overlapping}\StringTok{\textasciigrave{}}
\NormalTok{scatterblob\_data}\SpecialCharTok{$}\NormalTok{y\_seq }\OtherTok{\textless{}{-}}\NormalTok{ scatterblob\_data}\SpecialCharTok{$}\StringTok{\textasciigrave{}}\AttributeTok{Cognitive load {-} sequential}\StringTok{\textasciigrave{}}
\NormalTok{my\_data }\OtherTok{\textless{}{-}}\NormalTok{ scatterblob\_data[}\DecValTok{1}\SpecialCharTok{:}\DecValTok{13}\NormalTok{,}\FunctionTok{c}\NormalTok{(}\StringTok{"Ways to use GitHub"}\NormalTok{,}\StringTok{"y\_seq"}\NormalTok{, }\StringTok{"y\_real"}\NormalTok{, }\StringTok{"x1"}\NormalTok{, }\StringTok{"x2"}\NormalTok{)]}
\NormalTok{my\_data}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## # A tibble: 13 x 5
##    `Ways to use GitHub`                          y_seq y_real    x1    x2
##    <chr>                                         <dbl>  <dbl> <dbl> <dbl>
##  1 Archiving citeable code and data                  1   2.2      1     4
##  2 Storing a research compendium                     2   2.8      1     4
##  3 Project management                                3   4        2     5
##  4 Project continuity                                4   4.7      2     4
##  5 Open scientific discussions                       5   4.35     4     5
##  6 Virtual laboratory notebook                       6   5.35     1     4
##  7 Educational materials                             7   5.7      1     5
##  8 Academic websites                                 8   6.05     1     5
##  9 Writing a manuscript                              9   6.4      2     4
## 10 Organizing and managing teams                    10   6.75     2     5
## 11 Peer-reviews                                     11   8.4      1     3
## 12 Asynchronous collaborative coding and writing    12   9.3      4     5
## 13 Automation                                       13   9.8      1     5
\end{verbatim}

\hypertarget{plotting-the-data}{%
\subsection{Plotting the data}\label{plotting-the-data}}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{outpath }\OtherTok{\textless{}{-}} \FunctionTok{here}\NormalTok{(}\StringTok{"content"}\NormalTok{, }\StringTok{"images"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\hypertarget{using-raw-cognitive-values.}{%
\subsubsection{1) Using raw cognitive values.}\label{using-raw-cognitive-values.}}

Define colors:

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{some\_colors }\OtherTok{\textless{}{-}}\NormalTok{ viridis}\SpecialCharTok{::}\FunctionTok{turbo}\NormalTok{(}\AttributeTok{n =} \FunctionTok{nrow}\NormalTok{(my\_data), }\AttributeTok{alpha =} \FloatTok{0.9}\NormalTok{)}

\NormalTok{some\_colors1 }\OtherTok{\textless{}{-}}\NormalTok{ viridis}\SpecialCharTok{::}\FunctionTok{turbo}\NormalTok{(}\AttributeTok{n =} \DecValTok{30}\NormalTok{, }\AttributeTok{alpha =} \FloatTok{0.9}\NormalTok{)}

\NormalTok{some\_colors2 }\OtherTok{\textless{}{-}}\NormalTok{ viridis}\SpecialCharTok{::}\FunctionTok{magma}\NormalTok{(}\AttributeTok{n =} \DecValTok{30}\NormalTok{, }\AttributeTok{alpha =} \FloatTok{0.9}\NormalTok{)}

\FunctionTok{plot}\NormalTok{(}\DecValTok{1}\SpecialCharTok{:}\DecValTok{30}\NormalTok{, }\DecValTok{1}\SpecialCharTok{:}\DecValTok{30}\NormalTok{, }\AttributeTok{col =}\NormalTok{ some\_colors2, }\AttributeTok{pch =} \DecValTok{8}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\includegraphics{Supp_Info_1_files/figure-latex/unnamed-chunk-4-1.pdf}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{my\_colors }\OtherTok{\textless{}{-}}\NormalTok{ some\_colors1[}\FunctionTok{c}\NormalTok{(}\DecValTok{2}\SpecialCharTok{:}\DecValTok{3}\NormalTok{, }\DecValTok{5}\NormalTok{,}
                           \DecValTok{8}\NormalTok{, }\DecValTok{10}\NormalTok{, }\DecValTok{12}\NormalTok{,}
                           \DecValTok{20}\NormalTok{, }\DecValTok{21}\NormalTok{, }\DecValTok{22}\NormalTok{, }\DecValTok{23}\NormalTok{, }\DecValTok{24}\NormalTok{,}
                           \DecValTok{28}\NormalTok{, }\DecValTok{30}\NormalTok{)]}

\FunctionTok{plot}\NormalTok{(}\DecValTok{1}\SpecialCharTok{:}\FunctionTok{length}\NormalTok{(my\_colors), }
     \DecValTok{1}\SpecialCharTok{:}\FunctionTok{length}\NormalTok{(my\_colors), }
     \AttributeTok{col =}\NormalTok{ my\_colors, }\AttributeTok{pch =} \DecValTok{8}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\includegraphics{Supp_Info_1_files/figure-latex/unnamed-chunk-5-1.pdf}

\begin{Shaded}
\begin{Highlighting}[]
\DocumentationTok{\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#}
\CommentTok{\# start the pdf/png connection and set graphical parameters}
\DocumentationTok{\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#}
\CommentTok{\# plot\_format \textless{}{-} "pdf"}
\CommentTok{\# plot\_format \textless{}{-} "svg"}
\NormalTok{ plot\_format }\OtherTok{\textless{}{-}} \StringTok{"png"}

\ControlFlowTok{if}\NormalTok{ (plot\_format }\SpecialCharTok{==} \StringTok{"pdf"}\NormalTok{) \{}
  \FunctionTok{pdf}\NormalTok{(}\AttributeTok{file =} \FunctionTok{here}\NormalTok{(outpath, }\StringTok{"scatterblob\_0.pdf"}\NormalTok{),}
      \AttributeTok{width =} \FloatTok{8.25}\NormalTok{,}
      \AttributeTok{height =} \DecValTok{6}\NormalTok{,}
      \AttributeTok{bg =} \StringTok{"white"}\NormalTok{)  }
\NormalTok{\}}
\ControlFlowTok{if}\NormalTok{ (plot\_format }\SpecialCharTok{==} \StringTok{"svg"}\NormalTok{) \{}
  \FunctionTok{svg}\NormalTok{(}\AttributeTok{filename =} \FunctionTok{here}\NormalTok{(outpath, }\StringTok{"scatterblob\_0.svg"}\NormalTok{),}
      \AttributeTok{width =} \FloatTok{8.25}\NormalTok{,}
      \AttributeTok{height =} \DecValTok{6}\NormalTok{,}
      \AttributeTok{bg =} \StringTok{"white"}\NormalTok{)  }
\NormalTok{\}}
\ControlFlowTok{if}\NormalTok{ (plot\_format }\SpecialCharTok{==} \StringTok{"png"}\NormalTok{) \{}
  \FunctionTok{png}\NormalTok{(}\AttributeTok{file =} \FunctionTok{here}\NormalTok{(outpath, }\StringTok{"scatterblob\_0.png"}\NormalTok{),}
      \AttributeTok{width =} \FloatTok{8.25}\NormalTok{,}
      \AttributeTok{height =} \DecValTok{6}\NormalTok{,}
      \AttributeTok{units =} \StringTok{"in"}\NormalTok{,}
      \AttributeTok{res =} \DecValTok{300}\NormalTok{,}
      \AttributeTok{bg =} \StringTok{"white"}\NormalTok{)  }
\NormalTok{\}}
\FunctionTok{par}\NormalTok{(}\AttributeTok{xpd =} \ConstantTok{NA}\NormalTok{,}
    \AttributeTok{mai =} \FunctionTok{c}\NormalTok{(}\FloatTok{1.02}\NormalTok{, }\DecValTok{1}\NormalTok{, }\FloatTok{0.82}\NormalTok{, }\DecValTok{4}\NormalTok{),}
    \AttributeTok{bty=}\StringTok{"n"}\NormalTok{)}
\DocumentationTok{\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#}
\CommentTok{\# create the plot background}
\DocumentationTok{\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#}
\FunctionTok{plot}\NormalTok{(}\AttributeTok{x =} \FunctionTok{c}\NormalTok{(}\FloatTok{0.5}\NormalTok{, }\FloatTok{5.5}\NormalTok{),}
     \AttributeTok{y =} \FunctionTok{c}\NormalTok{(}\FloatTok{1.75}\NormalTok{, }\FloatTok{11.5}\NormalTok{),}
     \AttributeTok{xlab =} \StringTok{""}\NormalTok{,}
     \AttributeTok{ylab =} \StringTok{""}\NormalTok{,}
     \AttributeTok{col =} \StringTok{"white"}\NormalTok{,}
     \CommentTok{\# "hide" the tick labels so we can put some words instead of numbers:}
     \AttributeTok{col.axis =} \StringTok{"white"}\NormalTok{,}
     \AttributeTok{tck =} \FloatTok{0.02}\NormalTok{)}
\FunctionTok{title}\NormalTok{(}\AttributeTok{ylab=}\StringTok{"Technical difficulty"}\NormalTok{, }\AttributeTok{line =} \DecValTok{4}\NormalTok{, }\AttributeTok{cex.lab =} \DecValTok{1}\NormalTok{)}
\FunctionTok{title}\NormalTok{(}\AttributeTok{xlab=}\StringTok{"Degree of collaboration"}\NormalTok{, }\AttributeTok{line =} \FloatTok{3.5}\NormalTok{, }\AttributeTok{cex.lab =} \DecValTok{1}\NormalTok{)}
\DocumentationTok{\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#}
\CommentTok{\# add tick labels}
\DocumentationTok{\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#}
\FunctionTok{text}\NormalTok{(}\AttributeTok{x =} \DecValTok{1}\SpecialCharTok{:}\DecValTok{5}\NormalTok{,}
     \AttributeTok{y =} \FunctionTok{c}\NormalTok{(}\DecValTok{1}\NormalTok{, }\FunctionTok{rep}\NormalTok{(}\FloatTok{1.05}\NormalTok{, }\DecValTok{4}\NormalTok{)),}
     \AttributeTok{cex =} \FloatTok{0.7}\NormalTok{,}
     \AttributeTok{labels =} \FunctionTok{c}\NormalTok{(}\StringTok{"Personal"}\NormalTok{,}
                \StringTok{"Lab }\SpecialCharTok{\textbackslash{}n}\StringTok{Members"}\NormalTok{,}
                \StringTok{"Other }\SpecialCharTok{\textbackslash{}n}\StringTok{Labs"}\NormalTok{,}
                \StringTok{"EEB }\SpecialCharTok{\textbackslash{}n}\StringTok{Community"}\NormalTok{,}
                \StringTok{"All }\SpecialCharTok{\textbackslash{}n}\StringTok{Users"}\NormalTok{))}
\FunctionTok{text}\NormalTok{(}\AttributeTok{x =} \FunctionTok{c}\NormalTok{(}\DecValTok{1}\NormalTok{, }\DecValTok{3}\NormalTok{, }\DecValTok{5}\NormalTok{),}
     \AttributeTok{y =} \FloatTok{0.5}\NormalTok{,}
     \AttributeTok{labels =} \FunctionTok{c}\NormalTok{(}\StringTok{"Low"}\NormalTok{, }\StringTok{"Medium"}\NormalTok{, }\StringTok{"High"}\NormalTok{))}
\CommentTok{\# Technical difficulty levels from https://www.londonschool.com/level{-}scale/}
\FunctionTok{text}\NormalTok{(}\AttributeTok{x =} \FloatTok{0.2}\NormalTok{,}
     \AttributeTok{y =} \FunctionTok{c}\NormalTok{(}\DecValTok{2}\NormalTok{, }\DecValTok{4}\NormalTok{, }\DecValTok{6}\NormalTok{, }\DecValTok{8}\NormalTok{, }\DecValTok{10}\NormalTok{),}
     \AttributeTok{cex =} \FloatTok{0.7}\NormalTok{,}
     \AttributeTok{adj =} \DecValTok{1}\NormalTok{,}
     \AttributeTok{labels =} \FunctionTok{c}\NormalTok{(}\StringTok{"Elementary"}\NormalTok{,}
                \StringTok{"Low }\SpecialCharTok{\textbackslash{}n}\StringTok{Intermediate"}\NormalTok{,}
                \StringTok{"Intermediate"}\NormalTok{,}
                \StringTok{"Pre }\SpecialCharTok{\textbackslash{}n}\StringTok{Advanced"}\NormalTok{,}
                \StringTok{"Very }\SpecialCharTok{\textbackslash{}n}\StringTok{Advanced"}\NormalTok{))}
\DocumentationTok{\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#}
\CommentTok{\# plot scatter blobs}
\DocumentationTok{\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#}
\ControlFlowTok{for}\NormalTok{ (i }\ControlFlowTok{in} \FunctionTok{seq}\NormalTok{(}\FunctionTok{nrow}\NormalTok{(my\_data))) \{}
\NormalTok{  X0 }\OtherTok{\textless{}{-}}\NormalTok{ my\_data}\SpecialCharTok{$}\NormalTok{x1[i]}
\NormalTok{  X1 }\OtherTok{\textless{}{-}}\NormalTok{ my\_data}\SpecialCharTok{$}\NormalTok{x2[i]}
\NormalTok{  Y }\OtherTok{\textless{}{-}}\NormalTok{ my\_data}\SpecialCharTok{$}\NormalTok{y\_real[i]}
  \ControlFlowTok{if}\NormalTok{ (X0 }\SpecialCharTok{==}\NormalTok{ X1) \{}
\NormalTok{    X0 }\OtherTok{\textless{}{-}}\NormalTok{ X0 }\SpecialCharTok{{-}} \FloatTok{0.01}
\NormalTok{    X1 }\OtherTok{\textless{}{-}}\NormalTok{ X1 }\SpecialCharTok{+} \FloatTok{0.01}
\NormalTok{   \}}
  \FunctionTok{segments}\NormalTok{(}\AttributeTok{x0 =}\NormalTok{ X0,}
           \AttributeTok{x1 =}\NormalTok{ X1,}
           \AttributeTok{y0 =}\NormalTok{ Y,}
           \AttributeTok{col =}\NormalTok{ my\_colors[i],}
           \AttributeTok{lwd =} \DecValTok{13}\NormalTok{)}
\NormalTok{\}}
\DocumentationTok{\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#}
\CommentTok{\# add github uses text}
\DocumentationTok{\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#}
\FunctionTok{text}\NormalTok{(}\AttributeTok{x =} \FloatTok{5.5}\NormalTok{,}
    \AttributeTok{y =}\NormalTok{ my\_data}\SpecialCharTok{$}\NormalTok{y\_real,}
    \AttributeTok{labels =}\NormalTok{ my\_data}\SpecialCharTok{$}\StringTok{\textasciigrave{}}\AttributeTok{Ways to use GitHub}\StringTok{\textasciigrave{}}\NormalTok{,}
    \AttributeTok{adj =} \DecValTok{0}\NormalTok{,}
    \AttributeTok{col =}\NormalTok{ my\_colors)}
\FunctionTok{dev.off}\NormalTok{()}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## pdf 
##   2
\end{verbatim}

\begin{figure}
\centering
\includegraphics{../content/images/scatterblob_0.png}
\caption{Degree of collaboration VS technical difficulty (real, non-overlapping)}
\end{figure}

\hypertarget{distributing-cognitive-load-evenly}{%
\subsubsection{2) Distributing cognitive load evenly:}\label{distributing-cognitive-load-evenly}}

We tried different color palettes from two different R packages: \href{https://cran.r-project.org/web/packages/viridis/vignettes/intro-to-viridis.html\#the-color-scales}{viridis} and \href{https://github.com/karthik/wesanderson\#readme}{wesanderson}:

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{some\_colors3 }\OtherTok{\textless{}{-}}\NormalTok{ viridis}\SpecialCharTok{::}\FunctionTok{turbo}\NormalTok{(}\AttributeTok{n =} \DecValTok{100}\NormalTok{, }\AttributeTok{alpha =} \FloatTok{0.9}\NormalTok{)}
\NormalTok{some\_colors4 }\OtherTok{\textless{}{-}}\NormalTok{ wesanderson}\SpecialCharTok{::}\FunctionTok{wes\_palette}\NormalTok{(}\StringTok{"Zissou1"}\NormalTok{, }\DecValTok{75}\NormalTok{, }\AttributeTok{type =} \StringTok{"continuous"}\NormalTok{)}
\NormalTok{some\_colors5 }\OtherTok{\textless{}{-}}\NormalTok{ wesanderson}\SpecialCharTok{::}\FunctionTok{wes\_palette}\NormalTok{(}\StringTok{"Darjeeling1"}\NormalTok{, }\DecValTok{75}\NormalTok{, }\AttributeTok{type =} \StringTok{"continuous"}\NormalTok{)}
\NormalTok{some\_colors6 }\OtherTok{\textless{}{-}}\NormalTok{ wesanderson}\SpecialCharTok{::}\FunctionTok{wes\_palette}\NormalTok{(}\StringTok{"Darjeeling2"}\NormalTok{, }\DecValTok{75}\NormalTok{, }\AttributeTok{type =} \StringTok{"continuous"}\NormalTok{)}
\NormalTok{some\_colors7 }\OtherTok{\textless{}{-}}\NormalTok{ wesanderson}\SpecialCharTok{::}\FunctionTok{wes\_palette}\NormalTok{(}\StringTok{"Royal2"}\NormalTok{, }\DecValTok{75}\NormalTok{, }\AttributeTok{type =} \StringTok{"continuous"}\NormalTok{)}
\FunctionTok{plot}\NormalTok{(}\DecValTok{1}\SpecialCharTok{:}\DecValTok{75}\NormalTok{, }\DecValTok{1}\SpecialCharTok{:}\DecValTok{75}\NormalTok{, }\AttributeTok{col =}\NormalTok{ some\_colors7, }\AttributeTok{pch =} \DecValTok{8}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\includegraphics{Supp_Info_1_files/figure-latex/unnamed-chunk-7-1.pdf}

We agreed that viridis-turbo was the nicest palette for the purposes of our figure.

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{my\_colors }\OtherTok{\textless{}{-}}\NormalTok{ some\_colors3[}\FunctionTok{c}\NormalTok{(}\DecValTok{2}\NormalTok{, }\DecValTok{5}\NormalTok{, }\DecValTok{15}\NormalTok{,}
                           \DecValTok{26}\NormalTok{, }\DecValTok{28}\NormalTok{, }\DecValTok{30}\NormalTok{,}
                           \DecValTok{68}\NormalTok{, }\DecValTok{72}\NormalTok{, }\DecValTok{76}\NormalTok{, }\DecValTok{80}\NormalTok{, }\DecValTok{84}\NormalTok{,}
                           \DecValTok{94}\NormalTok{, }\DecValTok{100}\NormalTok{)]}
\NormalTok{plot\_name }\OtherTok{\textless{}{-}} \StringTok{"scatterblob\_1{-}viridis{-}turbo"}
\CommentTok{\# my\_colors \textless{}{-} some\_colors4[round(my\_data$y\_real*10){-}20]}
\CommentTok{\# plot\_name \textless{}{-} "scatterblob\_1{-}zissou1"}
\CommentTok{\# my\_colors \textless{}{-} some\_colors5[round(my\_data$y\_real*10){-}20]}
\CommentTok{\# plot\_name \textless{}{-} "scatterblob\_1{-}darjeeling1"}
\CommentTok{\# my\_colors \textless{}{-} some\_colors6[round(my\_data$y\_real*10){-}20]}
\CommentTok{\# plot\_name \textless{}{-} "scatterblob\_1{-}darjeeling2"}
\CommentTok{\# my\_colors \textless{}{-} some\_colors7[round(my\_data$y\_real*10){-}20]}
\CommentTok{\# plot\_name \textless{}{-} "scatterblob\_1{-}royal2"}
\DocumentationTok{\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#}
\CommentTok{\# start the pdf/png/svg connection and set graphical parameters}
\DocumentationTok{\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#}
\CommentTok{\# plot\_format \textless{}{-} "pdf"}
\NormalTok{plot\_format }\OtherTok{\textless{}{-}} \StringTok{"png"}
\CommentTok{\# plot\_format \textless{}{-} "svg"}

\ControlFlowTok{if}\NormalTok{ (plot\_format }\SpecialCharTok{==} \StringTok{"pdf"}\NormalTok{) \{}
  \FunctionTok{pdf}\NormalTok{(}\AttributeTok{file =} \FunctionTok{here}\NormalTok{(outpath, }\FunctionTok{paste0}\NormalTok{(plot\_name, }\StringTok{".pdf"}\NormalTok{)),}
      \AttributeTok{width =} \FloatTok{8.25}\NormalTok{,}
      \AttributeTok{height =} \DecValTok{6}\NormalTok{,}
      \AttributeTok{bg =} \StringTok{"white"}\NormalTok{)  }
\NormalTok{\}}
\ControlFlowTok{if}\NormalTok{ (plot\_format }\SpecialCharTok{==} \StringTok{"svg"}\NormalTok{) \{}
  \FunctionTok{svg}\NormalTok{(}\AttributeTok{filename =} \FunctionTok{here}\NormalTok{(outpath, }\FunctionTok{paste0}\NormalTok{(plot\_name, }\StringTok{".svg"}\NormalTok{)),}
      \AttributeTok{width =} \FloatTok{8.25}\NormalTok{,}
      \AttributeTok{height =} \DecValTok{6}\NormalTok{,}
      \AttributeTok{bg =} \StringTok{"white"}\NormalTok{)  }
\NormalTok{\}}
\ControlFlowTok{if}\NormalTok{ (plot\_format }\SpecialCharTok{==} \StringTok{"png"}\NormalTok{) \{}
  \FunctionTok{png}\NormalTok{(}\AttributeTok{file =} \FunctionTok{here}\NormalTok{(outpath, }\FunctionTok{paste0}\NormalTok{(plot\_name, }\StringTok{".png"}\NormalTok{)),}
      \AttributeTok{width =} \FloatTok{8.25}\NormalTok{,}
      \AttributeTok{height =} \DecValTok{6}\NormalTok{,}
      \AttributeTok{units =} \StringTok{"in"}\NormalTok{,}
      \AttributeTok{res =} \DecValTok{300}\NormalTok{,}
      \AttributeTok{bg =} \StringTok{"white"}\NormalTok{)  }
\NormalTok{\}}
\FunctionTok{par}\NormalTok{(}\AttributeTok{xpd =} \ConstantTok{NA}\NormalTok{,}
    \AttributeTok{mai =} \FunctionTok{c}\NormalTok{(}\FloatTok{1.02}\NormalTok{, }\DecValTok{1}\NormalTok{, }\FloatTok{0.82}\NormalTok{, }\DecValTok{4}\NormalTok{),}
    \AttributeTok{bty=}\StringTok{"n"}\NormalTok{)}
\DocumentationTok{\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#}
\CommentTok{\# create the plot background}
\DocumentationTok{\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#}
\FunctionTok{plot}\NormalTok{(}\AttributeTok{x =} \FunctionTok{c}\NormalTok{(}\FloatTok{0.5}\NormalTok{, }\FloatTok{5.5}\NormalTok{),}
     \AttributeTok{y =} \FunctionTok{c}\NormalTok{(}\FloatTok{0.5}\NormalTok{, }\FloatTok{13.5}\NormalTok{),}
     \AttributeTok{xlab =} \StringTok{""}\NormalTok{,}
     \AttributeTok{ylab =} \StringTok{""}\NormalTok{,}
     \AttributeTok{col =} \StringTok{"white"}\NormalTok{,}
     \CommentTok{\# "hide" the tick labels so we can put some words instead of numbers:}
     \AttributeTok{col.axis =} \StringTok{"white"}\NormalTok{,}
     \AttributeTok{tck =} \FloatTok{0.02}\NormalTok{)}

\FunctionTok{title}\NormalTok{(}\AttributeTok{ylab =} \StringTok{"Technical Difficulty"}\NormalTok{, }
      \AttributeTok{line =} \DecValTok{4}\NormalTok{, }
      \AttributeTok{cex.lab =} \DecValTok{1}\NormalTok{)}

\FunctionTok{title}\NormalTok{(}\AttributeTok{xlab =} \StringTok{"Degree of Collaboration"}\NormalTok{, }
      \AttributeTok{line =} \FloatTok{3.5}\NormalTok{, }
      \AttributeTok{cex.lab =} \DecValTok{1}\NormalTok{)}
\DocumentationTok{\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#}
\CommentTok{\# add tick labels}
\DocumentationTok{\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#}
\FunctionTok{text}\NormalTok{(}\AttributeTok{x =} \DecValTok{1}\SpecialCharTok{:}\DecValTok{5}\NormalTok{,}
     \AttributeTok{y =} \FunctionTok{c}\NormalTok{(}\SpecialCharTok{{-}}\FloatTok{0.65}\NormalTok{, }\FunctionTok{rep}\NormalTok{(}\SpecialCharTok{{-}}\FloatTok{0.7}\NormalTok{, }\DecValTok{4}\NormalTok{)), }
     \AttributeTok{cex =} \FloatTok{0.7}\NormalTok{,}
     \AttributeTok{labels =} \FunctionTok{c}\NormalTok{(}\StringTok{"Personal"}\NormalTok{, }
                \StringTok{"Lab }\SpecialCharTok{\textbackslash{}n}\StringTok{Members"}\NormalTok{, }
                \StringTok{"Other }\SpecialCharTok{\textbackslash{}n}\StringTok{Labs"}\NormalTok{, }
                \StringTok{"EEB }\SpecialCharTok{\textbackslash{}n}\StringTok{Community"}\NormalTok{, }
                \StringTok{"All }\SpecialCharTok{\textbackslash{}n}\StringTok{Users"}\NormalTok{))}
\FunctionTok{text}\NormalTok{(}\AttributeTok{x =} \FunctionTok{c}\NormalTok{(}\DecValTok{1}\NormalTok{, }\DecValTok{3}\NormalTok{, }\DecValTok{5}\NormalTok{),}
     \AttributeTok{y =} \SpecialCharTok{{-}}\FloatTok{1.7}\NormalTok{, }
     \AttributeTok{labels =} \FunctionTok{c}\NormalTok{(}\StringTok{"Low"}\NormalTok{, }\StringTok{"Medium"}\NormalTok{, }\StringTok{"High"}\NormalTok{))}
\CommentTok{\# Technical difficulty levels from https://www.londonschool.com/level{-}scale/}
\FunctionTok{text}\NormalTok{(}\AttributeTok{x =} \FloatTok{0.2}\NormalTok{,}
     \AttributeTok{y =} \FunctionTok{seq}\NormalTok{(}\DecValTok{1}\NormalTok{, }\DecValTok{13}\NormalTok{, }\AttributeTok{length.out =} \DecValTok{5}\NormalTok{),}
     \AttributeTok{cex =} \FloatTok{0.7}\NormalTok{,}
     \AttributeTok{adj =} \DecValTok{1}\NormalTok{,}
     \AttributeTok{labels =} \FunctionTok{c}\NormalTok{(}\StringTok{"Beginner"}\NormalTok{,}
                \StringTok{"Low}\SpecialCharTok{\textbackslash{}n}\StringTok{Intermediate"}\NormalTok{,}
                \StringTok{"Intermediate"}\NormalTok{, }
                \StringTok{"Pre }\SpecialCharTok{\textbackslash{}n}\StringTok{Advanced"}\NormalTok{,}
                \StringTok{"Advanced"}\NormalTok{))}
\DocumentationTok{\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#}
\CommentTok{\# plot scatter blobs on sequential cognitive load}
\DocumentationTok{\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#}
\ControlFlowTok{for}\NormalTok{ (i }\ControlFlowTok{in} \FunctionTok{seq}\NormalTok{(}\FunctionTok{nrow}\NormalTok{(my\_data))) \{}
\NormalTok{  X0 }\OtherTok{\textless{}{-}}\NormalTok{ my\_data}\SpecialCharTok{$}\NormalTok{x1[i]}
\NormalTok{  X1 }\OtherTok{\textless{}{-}}\NormalTok{ my\_data}\SpecialCharTok{$}\NormalTok{x2[i]}
\NormalTok{  Y }\OtherTok{\textless{}{-}}\NormalTok{ my\_data}\SpecialCharTok{$}\NormalTok{y\_seq[i]}
  \ControlFlowTok{if}\NormalTok{ (X0 }\SpecialCharTok{==}\NormalTok{ X1) \{}
\NormalTok{    X0 }\OtherTok{\textless{}{-}}\NormalTok{ X0 }\SpecialCharTok{{-}} \FloatTok{0.01}
\NormalTok{    X1 }\OtherTok{\textless{}{-}}\NormalTok{ X1 }\SpecialCharTok{+} \FloatTok{0.01}
\NormalTok{   \}}
  \FunctionTok{segments}\NormalTok{(}\AttributeTok{x0 =}\NormalTok{ X0,}
           \AttributeTok{x1 =}\NormalTok{ X1,}
           \AttributeTok{y0 =}\NormalTok{ Y,}
           \AttributeTok{col =}\NormalTok{ my\_colors[i],}
           \AttributeTok{lwd =} \DecValTok{23}\NormalTok{)}
\NormalTok{\}}
\DocumentationTok{\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#}
\CommentTok{\# add github uses text}
\DocumentationTok{\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#}
\FunctionTok{text}\NormalTok{(}\AttributeTok{x =} \FloatTok{5.5}\NormalTok{,}
    \AttributeTok{y =}\NormalTok{ my\_data}\SpecialCharTok{$}\NormalTok{y\_seq,}
    \AttributeTok{labels =}\NormalTok{ my\_data}\SpecialCharTok{$}\StringTok{\textasciigrave{}}\AttributeTok{Ways to use GitHub}\StringTok{\textasciigrave{}}\NormalTok{,}
    \AttributeTok{adj =} \DecValTok{0}\NormalTok{,}
    \AttributeTok{col =}\NormalTok{ my\_colors)}
\FunctionTok{dev.off}\NormalTok{()}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## pdf 
##   2
\end{verbatim}

\begin{figure}
\centering
\includegraphics{../content/images/scatterblob_1-viridis-turbo.png}
\caption{Degree of collaboration \emph{versus} technical difficulty (sequential)}
\end{figure}

\end{document}

### 2023-02-23 R/Supp_Info_1.Rmd
streamline Appendix S1 and S2 and code chunks (somewhat)
This commit edits S1 to be more concise, and moves some content from S2 into S1. This was done so the descriptions about how each index was computed is in one section. The Appendix S2 is now mainly the instructions to treat the data and plot it to generate Figure 2 from the main text. This code has also been edited down slightly, to only show the code needed to generate final Figure 2, without exercises in colour choices.

@@
    - \usepackage{parskip}
-   - \setlength{\parindent}{4em}
-   - \setlength{\parskip}{0em}
+   - \setlength{\parindent}{0em}
+   - \setlength{\parskip}{1em}
    - \usepackage{caption}
@@
 We aimed at distributing the use cases discussed in our study across gradients of technical difficulty and collaboration.
-For this, we [...].
+For this, we estimated the perceived degree of collaboration and the perceived level of technical difficulty for each use case.
 
-We then [\...].
+**Degree of collaboration**
 
-We used Google Docs and Google Sheets to manipulate data, and plotted results using `R` version 4.02.
+_Each author attributed a value ranging from 1 to 10 to their perceived degree of collaboration for a use case, with one representing a use case that offer very low advantages in terms of collaboration, while ten classified that use case as highly advantageous in terms of collaboration._
 
-\noindent
+We determined the degree of collaboration for each GitHub use case as the range of collaborative contexts that can be achieved with each tool, as perceived by the authors.
+We identified the five levels of possible collaboration in the context of Ecology and Evolutionary Biology research, as follows:
 
-**Appendix S1.2. Annotated code and prose allowing the representation of indices of technical difficulty and degree of collaboration**
+| Level |           Degree of collaboration |
+| ----: | --------------------------------: |
+|     1 |                        Individual |
+|     2 |     Lab or group of collaborators |
+|     3 | An organisation, or multiple labs |
+|     4 |            The research community |
+|     5 |                The general public |
 
-**Goal**: This is a summary figure, e.g., here are all the ways and here are the entry points with low technical difficulty, some for beginners and some more advanced ways to use GitHub.
+We determined the minimum and maximum degree of collaboration from these levels for each GitHub use case.
 
-**Highlight**: There are ways to use github that allow different degrees of collaboration that do not require too many technical skills.
+**Technical difficulty**
 
-## The data
+We then assessed the technical difficulty of GitHub use cases in terms of their cognitive load.
 
-Data was assembled collaboratively using Google docs, then manually saved as a "csv" file called `scatterblob_data_raw.csv` in the `data` folder.
+As a note, we measured the perceived technical difficulty of each GitHub use case as the degree of difficulty as perceived by the authors, based on personal experience.
+This metric represents a consensus value among the authors, though the perceived degree of difficulty will ultimately vary among GitHub users depending on each person's previous experience with these use cases.
 
-The collaborative [google spread sheet](https://docs.google.com/spreadsheets/d/1zCRgctjfjE2xZN9MkqfFh222K6bvVvA3gT0UdkL_CS8/edit#gid=0), features a first column listing the ways to use GitHub that were addressed in the manuscript (`r paste0(uses[1:13], collapse = "; " )`).
-
-The column *`r column_names[6]`* corresponds to the degree of difficulty that was perceived by the authors when assembling the data, based on personal experience.
-We quickly realized this varied greatly across authors, and that this variation seemed to depend on which github tools were previously known or mastered by the authors.
-
-The columns tagged as *Cognitive load -* showcase a different way to assess technical difficulty of GitHub uses, measured as cognitive load (explained in the next section).
-
-The columns tagged as *degree of collaboration* showcase the span of collaboration that can be achieved with each tool, as perceived by the authors.
-
-### Measuring degree of technical difficulty
-
-[Cognitive load](https://docs.google.com/spreadsheets/d/1YipCCdg5Z8w-IQO67rFfMBSTpLjO-_7HiW44gqzTXPM/edit#gid=0) was measured as follows:
+The table we used to quantify cognitive load was assembled collaboratively using Google Sheets, then manually saved as a `CSV` file called `cognitive_load_table.csv` in the `data` folder.
 
@@
 
-## Reading the data CSV file:
+The collaborative Google Sheet used to quantify cognitive load is also available at the following link: [https://docs.google.com/spreadsheets/d/1YipCCdg5Z8w-IQO67rFfMBSTpLjO-_7HiW44gqzTXPM/edit#gid=0](https://docs.google.com/spreadsheets/d/1YipCCdg5Z8w-IQO67rFfMBSTpLjO-_7HiW44gqzTXPM/edit#gid=0).
+
+\noindent
+\newpage
+
+**Appendix S1.2. Annotated code and prose allowing the representation of indices of technical difficulty and degree of collaboration**
+
+Here, we provide the annotated `R` code and instructions that are required to load and present the indices of technical difficulty and degree of collaboration of the eleven use cases of GitHub we present in our piece.
+
+We used Google Docs and Google Sheets to collect and manipulate data, and plotted results using the basic visualisation functions from `R` version 4.02.
+
+### Data collection
+
+These data were assembled collaboratively using Google Docs following the methodology described in Appendix S1.1.
+then manually saved as a `CSV` file called `scatterblob_data_raw.csv` in the `data` folder.
+The collaborative Google Spreadsheet is also accessible at the following link: [https://docs.google.com/spreadsheets/d/1zCRgctjfjE2xZN9MkqfFh222K6bvVvA3gT0UdkL_CS8/edit#gid=0](https://docs.google.com/spreadsheets/d/1zCRgctjfjE2xZN9MkqfFh222K6bvVvA3gT0UdkL_CS8/edit#gid=0).
+
+The data table features a first column listing the ways to use GitHub that were addressed in the manuscript (`r paste0(uses[1:13], collapse = "; " )`).
+
+### Creating Figure 2: A summary of ways GitHub can be used showing technical difficulty and degree of collaboration for each use case.
+
+1. Loading the data `CSV` file:
+
+```{r, message=FALSE, collapse=TRUE}
+scatterblob_data <- read_csv(here("data", "scatterblob_data_raw.csv"))
+```
+
+2. Cleaning the raw data and saving it as a `my_data` object:
 
 ```{r}
-scatterblob_data <- read_csv(here("data", "scatterblob_data_raw.csv"))
-head(scatterblob_data)
-#  View(scatterblob_data)
-```
-
-Cleaning the raw data and saving it as a `my_data` object:
-
-```{r}
-names(scatterblob_data)
+# names(scatterblob_data)
 scatterblob_data$x1 <- scatterblob_data$`Min degree of collaboration X1`
@@
 my_data <- scatterblob_data[1:13,c("Ways to use GitHub","y_seq", "y_real", "x1", "x2")]
-my_data
 ```
-
-## Plotting the data
 
@@
 
-### 1) Using raw cognitive values.
+3. Plotting cognitive load
 
-Define colors:
+We used the color palette "turbo" from the R package [viridis](https://cran.r-project.org/web/packages/viridis/vignettes/intro-to-viridis.html#the-color-scales):
 
 ```{r}
-some_colors <- viridis::turbo(n = nrow(my_data), alpha = 0.9)
+my_colors <- viridis::turbo(n = 100, alpha = 0.9)[c(2, 5, 15, 26, 28, 30,
+                           68, 72, 76, 80, 84, 94, 100)]
+plot_name <- "scatterblob_1-viridis-turbo"
 
-some_colors1 <- viridis::turbo(n = 30, alpha = 0.9)
+###############################################################
+# start the png connection and set graphical parameters
+###############################################################
 
-some_colors2 <- viridis::magma(n = 30, alpha = 0.9)
-
-plot(1:30, 1:30, col = some_colors2, pch = 8)
-```
-
-```{r}
-my_colors <- some_colors1[c(2:3, 5,
-                           8, 10, 12,
-                           20, 21, 22, 23, 24,
-                           28, 30)]
-
-plot(1:length(my_colors), 
-     1:length(my_colors), 
-     col = my_colors, pch = 8)
-
-```
-
-```{r}
-###############################################################
-# start the pdf/png connection and set graphical parameters
-###############################################################
-# plot_format <- "pdf"
-# plot_format <- "svg"
 plot_format <- "png"
-
-if (plot_format == "pdf") {
-  pdf(file = here(outpath, "scatterblob_0.pdf"),
-      width = 8.25,
-      height = 6,
-      bg = "white")  
-}
-if (plot_format == "svg") {
-  svg(filename = here(outpath, "scatterblob_0.svg"),
-      width = 8.25,
-      height = 6,
-      bg = "white")  
-}
-if (plot_format == "png") {
-  png(file = here(outpath, "scatterblob_0.png"),
-      width = 8.25,
-      height = 6,
-      units = "in",
-      res = 300,
-      bg = "white")  
-}
-par(xpd = NA,
-    mai = c(1.02, 1, 0.82, 4),
-    bty="n")
-###############################################################
-# create the plot background
-###############################################################
-plot(x = c(0.5, 5.5),
-     y = c(1.75, 11.5),
-     xlab = "",
-     ylab = "",
-     col = "white",
-     # "hide" the tick labels so we can put some words instead of numbers:
-     col.axis = "white",
-     tck = 0.02)
-title(ylab="Technical difficulty", line = 4, cex.lab = 1)
-title(xlab="Degree of collaboration", line = 3.5, cex.lab = 1)
-###############################################################
-# add tick labels
-###############################################################
-text(x = 1:5,
-     y = c(1, rep(1.05, 4)),
-     cex = 0.7,
-     labels = c("Personal",
-                "Lab \nMembers",
-                "Other \nLabs",
-                "EEB \nCommunity",
-                "All \nUsers"))
-text(x = c(1, 3, 5),
-     y = 0.5,
-     labels = c("Low", "Medium", "High"))
-# Technical difficulty levels from https://www.londonschool.com/level-scale/
-text(x = 0.2,
-     y = c(2, 4, 6, 8, 10),
-     cex = 0.7,
-     adj = 1,
-     labels = c("Elementary",
-                "Low \nIntermediate",
-                "Intermediate",
-                "Pre \nAdvanced",
-                "Very \nAdvanced"))
-###############################################################
-# plot scatter blobs
-###############################################################
-for (i in seq(nrow(my_data))) {
-  X0 <- my_data$x1[i]
-  X1 <- my_data$x2[i]
-  Y <- my_data$y_real[i]
-  if (X0 == X1) {
-    X0 <- X0 - 0.01
-    X1 <- X1 + 0.01
-   }
-  segments(x0 = X0,
-           x1 = X1,
-           y0 = Y,
-           col = my_colors[i],
-           lwd = 13)
-}
-###############################################################
-# add github uses text
-###############################################################
-text(x = 5.5,
-    y = my_data$y_real,
-    labels = my_data$`Ways to use GitHub`,
-    adj = 0,
-    col = my_colors)
-dev.off()
-```
-
-![Degree of collaboration VS technical difficulty (real, non-overlapping)](../content/images/scatterblob_0.png)
-
-### 2) Distributing cognitive load evenly:
-
-We tried different color palettes from two different R packages: [viridis](https://cran.r-project.org/web/packages/viridis/vignettes/intro-to-viridis.html#the-color-scales) and [wesanderson](https://github.com/karthik/wesanderson#readme):
-
-```{r}
-some_colors3 <- viridis::turbo(n = 100, alpha = 0.9)
-some_colors4 <- wesanderson::wes_palette("Zissou1", 75, type = "continuous")
-some_colors5 <- wesanderson::wes_palette("Darjeeling1", 75, type = "continuous")
-some_colors6 <- wesanderson::wes_palette("Darjeeling2", 75, type = "continuous")
-some_colors7 <- wesanderson::wes_palette("Royal2", 75, type = "continuous")
-plot(1:75, 1:75, col = some_colors7, pch = 8)
-```
-
-We agreed that viridis-turbo was the nicest palette for the purposes of our figure.
-
-```{r}
-my_colors <- some_colors3[c(2, 5, 15,
-                           26, 28, 30,
-                           68, 72, 76, 80, 84,
-                           94, 100)]
-plot_name <- "scatterblob_1-viridis-turbo"
-# my_colors <- some_colors4[round(my_data$y_real*10)-20]
-# plot_name <- "scatterblob_1-zissou1"
-# my_colors <- some_colors5[round(my_data$y_real*10)-20]
-# plot_name <- "scatterblob_1-darjeeling1"
-# my_colors <- some_colors6[round(my_data$y_real*10)-20]
-# plot_name <- "scatterblob_1-darjeeling2"
-# my_colors <- some_colors7[round(my_data$y_real*10)-20]
-# plot_name <- "scatterblob_1-royal2"
-###############################################################
-# start the pdf/png/svg connection and set graphical parameters
-###############################################################
-# plot_format <- "pdf"
-plot_format <- "png"
-# plot_format <- "svg"
-
-if (plot_format == "pdf") {
-  pdf(file = here(outpath, paste0(plot_name, ".pdf")),
-      width = 8.25,
-      height = 6,
-      bg = "white")  
-}
-if (plot_format == "svg") {
-  svg(filename = here(outpath, paste0(plot_name, ".svg")),
-      width = 8.25,
-      height = 6,
-      bg = "white")  
-}
 if (plot_format == "png") {
@@
     bty="n")
+
 ###############################################################
@@
      tck = 0.02)
-
 title(ylab = "Technical Difficulty", 
@@
       cex.lab = 1)
-
 title(xlab = "Degree of Collaboration", 
@@
       cex.lab = 1)
+
 ###############################################################
@@
 ###############################################################
+
 text(x = 1:5,
@@
      labels = c("Low", "Medium", "High"))
+
 # Technical difficulty levels from https://www.londonschool.com/level-scale/
@@
                 "Advanced"))
+
 ###############################################################
@@
 }
+
 ###############################################################
@@
 
-![Degree of collaboration *versus* technical difficulty (sequential)](../content/images/scatterblob_1-viridis-turbo.png)
+![A summary of ways GitHub can be used showing technical difficulty and degree of collaboration for each use case.](../content/images/scatterblob_1-viridis-turbo.png)

### 2023-02-23 editorial-communication/cover-letter-submission.Qmd
Deploying to gh-pages from @ SORTEE-Github-Hackathon/manuscript@6500cdf1e50df11f876d0a05b756c5722fc4e223 🚀

@@
 ---
-```{r include=FALSE}
-knitr::opts_chunk$set(fig.retina = 2)
-```
 

### 2023-02-23 R/Supp_Info_1.Rmd
Removing the virtual lab notebook from the figure and from the supplementary material.

@@
 knitr::opts_chunk$set(echo = TRUE)
+
 library(googlesheets4)
@@
 library(readr)
+
 scatterblob_data <- read_csv(here("data", "scatterblob_data_raw.csv"))
@@
 column_names <- colnames(scatterblob_data[1:8])
+
 ```
@@
 
-_Each author attributed a value ranging from 1 to 10 to their perceived degree of collaboration for a use case, with one representing a use case that offer very low advantages in terms of collaboration, while ten classified that use case as highly advantageous in terms of collaboration._
+Each author attributed a value ranging from 1 to 10 to their perceived degree of collaboration for a use case, with one representing a use case that offer very low advantages in terms of collaboration, while ten classified that use case as highly advantageous in terms of collaboration.
 
@@
 
-We determined the minimum and maximum degree of collaboration from these levels for each GitHub use case.
+Finally, we determined the minimum and maximum degree of collaboration from these levels for each GitHub use case.
 
@@
 
-As a note, we measured the perceived technical difficulty of each GitHub use case as the degree of difficulty as perceived by the authors, based on personal experience.
+We measured the perceived technical difficulty of each GitHub use case as the degree of difficulty as perceived by the authors, based on personal experience. 
 This metric represents a consensus value among the authors, though the perceived degree of difficulty will ultimately vary among GitHub users depending on each person's previous experience with these use cases.
@@
 The table we used to quantify cognitive load was assembled collaboratively using Google Sheets, then manually saved as a `CSV` file called `cognitive_load_table.csv` in the `data` folder. 
+Specifically, :
 
-1.  We first created a list of skills that are needed to implement different GitHub uses. These occupied a column each. 
-2.  For each GitHub use listed on the first column, we went through each column, and marked a 1 if a skill was needed for that particular GitHub use, and 0 if the skill was not needed.
+1.  We first created a list of skills that are needed to implement different GitHub uses. These occupied a column each; 
+2.  For each GitHub use listed on the first column, we went through each column, and marked a 1 if a skill was needed for that particular GitHub use, and 0 if the skill was not needed;
 3.
 The sum of values across columns provides a measure of cognitive load required for a user that is a "GitHub beginner" to implement any GitHub use.
-The column *`r column_names[3]`* reflects this number.
+The column *`r column_names[3]`* reflects this number;
 4.
 As many GitHub uses tied with the same cognitive load value, we resourced to perceived difficulty to break ties and avoid overlap of uses in the figure, mainly to improve visualization of the data.
-The column *`r column_names[5]`* shows this adjustment.
+The column *`r column_names[5]`* shows this adjustment;
 5.
@@
 then manually saved as a `CSV` file called `scatterblob_data_raw.csv` in the `data` folder.
-The collaborative Google Spreadsheet is also accessible at the following link: [https://docs.google.com/spreadsheets/d/1zCRgctjfjE2xZN9MkqfFh222K6bvVvA3gT0UdkL_CS8/edit#gid=0](https://docs.google.com/spreadsheets/d/1zCRgctjfjE2xZN9MkqfFh222K6bvVvA3gT0UdkL_CS8/edit#gid=0).
+The collaborative Google Spreadsheet is also accessible at the following link: [https://docs.google.com/spreadsheets/d/1zCRgctjfjE2xZN9MkqfFh222K6bvVvA3gT0UdkL_CS8/](https://docs.google.com/spreadsheets/d/1zCRgctjfjE2xZN9MkqfFh222K6bvVvA3gT0UdkL_CS8).
 
@@
 scatterblob_data$y_seq <- scatterblob_data$`Cognitive load - sequential`
-my_data <- scatterblob_data[1:13,c("Ways to use GitHub","y_seq", "y_real", "x1", "x2")]
+my_data <- scatterblob_data[-6, c("Ways to use GitHub","y_seq", "y_real", "x1", "x2")]
+my_data$y_seq <- 1:12
 ```
@@
 
-We used the color palette "turbo" from the R package [viridis](https://cran.r-project.org/web/packages/viridis/vignettes/intro-to-viridis.html#the-color-scales):
+We used the colour palette `turbo` from the R package [`viridis`](https://cran.r-project.org/web/packages/viridis/vignettes/intro-to-viridis.html#the-color-scales):
 
 ```{r}
-my_colors <- viridis::turbo(n = 100, alpha = 0.9)[c(2, 5, 15, 26, 28, 30,
-                           68, 72, 76, 80, 84, 94, 100)]
+my_colors <- viridis::turbo(n = 100, alpha = 0.9)[c(2, 
+                                                    5, 
+                                                    15, 
+                                                    26, 
+                                                    30,
+                                                    68, 
+                                                    72, 
+                                                    76,
+                                                    80,
+                                                    84,
+                                                    94,
+                                                    100)]
+
 plot_name <- "scatterblob_1-viridis-turbo"
@@
 plot(x = c(0.5, 5.5),
-     y = c(0.5, 13.5),
+     y = c(0.5, 12.5),
      xlab = "",
@@
 text(x = 0.2,
-     y = seq(1, 13, length.out = 5),
+     y = seq(1, 12, length.out = 5),
      cex = 0.7,
@@
     col = my_colors)
+
 dev.off()

### 2023-02-23 R/Supp_Info_1.Rmd
Returns the italics to the sentence that needs attention. Oops!

@@
 
-Each author attributed a value ranging from 1 to 10 to their perceived degree of collaboration for a use case, with one representing a use case that offer very low advantages in terms of collaboration, while ten classified that use case as highly advantageous in terms of collaboration.
+_Each author attributed a value ranging from 1 to 10 to their perceived degree of collaboration for a use case, with one representing a use case that offer very low advantages in terms of collaboration, while ten classified that use case as highly advantageous in terms of collaboration._
 

### 2023-02-26 R/Supp_Info_1.Rmd
add table to show the final data used to produce Figure 2

--- 2023-02-23 R/Supp_Info_1.Rmd
@@
 library(readr)
+library(dplyr)
 
@@
 **Degree of collaboration**
-
-Each author attributed a value ranging from 1 to 10 to their perceived degree of collaboration for a use case, with one representing a use case that offer very low advantages in terms of collaboration, while ten classified that use case as highly advantageous in terms of collaboration.
 
@@
 
-The data table features a first column listing the ways to use GitHub that were addressed in the manuscript (`r paste0(uses[1:13], collapse = "; " )`).
+\newpage
+
+```{r, echo = FALSE}
+to_print = scatterblob_data[-6,-c(2,3,5,9:11)]
+colnames(to_print) = c("GitHub Use Cases", 
+                       "Cognitive Load",
+                       "Technical Difficulty",
+                       "Degree of Collaboration (Minimum)",
+                       "Degree of Collaboration (Maximum)")
+knitr::kable(to_print, 
+             label = "data",
+             caption = "Indices of technical difficulty and degree of collaboration for each GitHub use case.
+The first column lists the GitHub use cases that were addressed in the main text.
+Indices were assessed collaboratively following the steps in Appendix S1.1.",
+              align = c('l','c','c','c','c')) %>% 
+  kableExtra::column_spec(1, width = "3.5cm") %>%
+  kableExtra::column_spec(2:5, width = "2cm")
+```
+
+\newpage
 

### 2023-02-26 R/Supp_Info_1.Rmd

--- 2023-02-23 R/Supp_Info_1.Rmd
@@
 library(readr)
+library(dplyr)
+library(kableExtra)
 
@@
 
-Each author attributed a value ranging from 1 to 10 to their perceived degree of collaboration for a use case, with one representing a use case that offer very low advantages in terms of collaboration, while ten classified that use case as highly advantageous in terms of collaboration.
+We determined the degree of collaboration for each GitHub use case as the range of collaborative contexts that can be achieved with each tool, as perceived by the authors.
+We attributed five levels of possible collaboration in the context of ecology and evolutionary biology research (see Table S1.1).
 
-We determined the degree of collaboration for each GitHub use case as the range of collaborative contexts that can be achieved with each tool, as perceived by the authors.
-We identified the five levels of possible collaboration in the context of Ecology and Evolutionary Biology research, as follows:
+**Table S1.1.** Classification of depress of collaboration attributed to the use cases for GitHub in research in the field of ecology and evolutionary biology.
 
 | Level |           Degree of collaboration         |
-| ----: | --------------------------------: |
+| ----: | ----------------------------------------: |
 |     1 |                                Individual |
-|     2 |     Lab or group of collaborators |
+|     2 |      Laboratory or group of collaborators |
 |     3 |         An organisation, or multiple labs |
@@
 1.  We first created a list of skills that are needed to implement different GitHub uses. These occupied a column each; 
-2.  For each GitHub use listed on the first column, we went through each column, and marked a 1 if a skill was needed for that particular GitHub use, and 0 if the skill was not needed;
+2.  For each GitHub use listed on the first column, we went through each column, and marked a 1 if a skill was needed for that particular GitHub use, and zero if the skill was not needed;
 3.
@@
 5.
-Finally, we ordered the GitHub uses in increasing order following *`r column_names[5]`*, and assigned a sequential value of cognitive load, from 1 to *maximum number of GitHub uses*.
-This is column *`r column_names[4]`*
+Finally, we ordered the GitHub uses in increasing order following *`r column_names[5]`*, and assigned a sequential value of cognitive load, from one to *maximum number of GitHub uses*.
+This is column *`r column_names[4]`*.
 
@@
 
-The data table features a first column listing the ways to use GitHub that were addressed in the manuscript (`r paste0(uses[1:13], collapse = "; " )`).
+\newpage
+
+\captionsetup[table]{labelformat=empty}
+
+```{r table, echo=F}
+to_print = scatterblob_data[-6,-c(2, 3, 5,9:11)]
+colnames(to_print) = c("GitHub Use Cases", 
+                       "Cognitive Load",
+                       "Technical Difficulty",
+                       "Degree of Collaboration (Minimum)",
+                       "Degree of Collaboration (Maximum)")
+knitr::kable(to_print, 
+             label = "data",
+             caption = "'\\textbf{Table S1.2.} Indices of technical difficulty and degree of collaboration for each GitHub use case.
+The first column lists the GitHub use cases that were addressed in the main text.
+Indices were assessed collaboratively following the steps in Appendix S1.1.",
+             align = c('l','c','c','c','c'),
+             booktabs = T) %>% 
+  kableExtra::column_spec(1, width = "3.5cm") %>%
+  kableExtra::column_spec(2:5, width = "2cm")
+```
+
+\newpage
 

### 2023-02-26 manuscript.tex
Merge pull request #298 from SORTEE-Github-Hackathon/phpb_luna_supp_mat [ci skip]
This build is based on
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/afbbe55b2ad8febebb104fc9358170f15b3a4596.

This commit was created by the following CI build and job:
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/afbbe55b2ad8febebb104fc9358170f15b3a4596/checks
https://github.com/SORTEE-Github-Hackathon/manuscript/actions/runs/4276518486

@@
 This manuscript
-(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/d42ec283f2696204f3fcc8bdcd6835260a492415/}{permalink})
+(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/afbbe55b2ad8febebb104fc9358170f15b3a4596/}{permalink})
 was automatically generated
-from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/d42ec283f2696204f3fcc8bdcd6835260a492415}{SORTEE-Github-Hackathon/manuscript@d42ec28}
-on February 20, 2023.
+from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/afbbe55b2ad8febebb104fc9358170f15b3a4596}{SORTEE-Github-Hackathon/manuscript@afbbe55}
+on February 26, 2023.
 
@@
 GitHub Docs.
-Retrieved February 20, 2023, from \url{https://ghdocs-prod.azurewebsites.net/en/repositories/managing-your-repositorys-settings-and-features/customizing-your-repository/about-code-owners}
+Retrieved February 26, 2023, from \url{https://ghdocs-prod.azurewebsites.net/en/repositories/managing-your-repositorys-settings-and-features/customizing-your-repository/about-code-owners}
 
@@
 GitHub Docs.
-Retrieved February 20, 2023, from \url{https://ghdocs-prod.azurewebsites.net/en/repositories/working-with-files/managing-large-files/about-large-files-on-github}
+Retrieved February 26, 2023, from \url{https://ghdocs-prod.azurewebsites.net/en/repositories/working-with-files/managing-large-files/about-large-files-on-github}
 
@@
 GitHub Docs.
-Retrieved February 20, 2023, from \url{https://ghdocs-prod.azurewebsites.net/en/issues/planning-and-tracking-with-projects/learning-about-projects/about-projects}
+Retrieved February 26, 2023, from \url{https://ghdocs-prod.azurewebsites.net/en/issues/planning-and-tracking-with-projects/learning-about-projects/about-projects}
 
@@
 GitHub Docs.
-Retrieved February 20, 2023, from \url{https://ghdocs-prod.azurewebsites.net/en/communities/setting-up-your-project-for-healthy-contributions/adding-a-license-to-a-repository}
+Retrieved February 26, 2023, from \url{https://ghdocs-prod.azurewebsites.net/en/communities/setting-up-your-project-for-healthy-contributions/adding-a-license-to-a-repository}
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-6CMMeSeD}{}}%
-Bryan, J., \& TAs, T. S. 545. (n.d.). \emph{STAT 545}. Retrieved February 20, 2023, from \url{https://stat545.com/}
+Bryan, J., \& TAs, T. S. 545. (n.d.). \emph{STAT 545}. Retrieved February 26, 2023, from \url{https://stat545.com/}
 
 \leavevmode\vadjust pre{\hypertarget{ref-lx49NGto}{}}%
-\emph{Connect GitHub to a Project - OSF Support}. (n.d.). Retrieved February 20, 2023, from \url{https://help.osf.io/article/211-connect-github-to-a-project}
+\emph{Connect GitHub to a Project - OSF Support}. (n.d.). Retrieved February 26, 2023, from \url{https://help.osf.io/article/211-connect-github-to-a-project}
 
 \leavevmode\vadjust pre{\hypertarget{ref-T03Api6e}{}}%
-\emph{Continuous Integration and Delivery}. (n.d.). CircleCI. Retrieved February 20, 2023, from \url{https://circleci.com/}
+\emph{Continuous Integration and Delivery}. (n.d.). CircleCI. Retrieved February 26, 2023, from \url{https://circleci.com/}
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-NUXbp429}{}}%
-\emph{Features • GitHub Actions}. (n.d.). GitHub. Retrieved February 20, 2023, from \url{https://github.com/features/actions}
+\emph{Features • GitHub Actions}. (n.d.). GitHub. Retrieved February 26, 2023, from \url{https://github.com/features/actions}
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-1CM2EcdVk}{}}%
-\emph{Git - A Short History of Git}. (n.d.). Retrieved February 20, 2023, from \url{https://git-scm.com/book/en/v2/Getting-Started-A-Short-History-of-Git}
+\emph{Git - A Short History of Git}. (n.d.). Retrieved February 26, 2023, from \url{https://git-scm.com/book/en/v2/Getting-Started-A-Short-History-of-Git}
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-ZvrOcg9w}{}}%
-Hester, J. B., the STAT 545 TAs, Jim. (n.d.). \emph{Let's Git started \textbar{} Happy Git and GitHub for the useR}. Retrieved February 20, 2023, from \url{https://happygitwithr.com/}
+Hester, J. B., the STAT 545 TAs, Jim. (n.d.). \emph{Let's Git started \textbar{} Happy Git and GitHub for the useR}. Retrieved February 26, 2023, from \url{https://happygitwithr.com/}
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-3UAritXO}{}}%
-\emph{Issues · fmsabatini/sPlotOpen\_Manuscript}. (n.d.). GitHub. Retrieved February 20, 2023, from \url{https://github.com/fmsabatini/sPlotOpen_Manuscript}
+\emph{Issues · fmsabatini/sPlotOpen\_Manuscript}. (n.d.). GitHub. Retrieved February 26, 2023, from \url{https://github.com/fmsabatini/sPlotOpen_Manuscript}
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Re6Eg2va}{}}%
-\emph{Manubot - Manuscripts, open and automated}. (n.d.). Retrieved February 20, 2023, from \url{https://manubot.org}
+\emph{Manubot - Manuscripts, open and automated}. (n.d.). Retrieved February 26, 2023, from \url{https://manubot.org}
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-oGbKxHzj}{}}%
-\emph{Using Git and GitHub}. (n.d.). Retrieved February 20, 2023, from \url{https://www.overleaf.com/learn/how-to/Using_Git_and_GitHub}
+\emph{Using Git and GitHub}. (n.d.). Retrieved February 26, 2023, from \url{https://www.overleaf.com/learn/how-to/Using_Git_and_GitHub}
 

### 2023-02-26 manuscript.tex
Adjusting author contributions, statements of conflict of interest, and funding [ci skip]
This build is based on
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/dd2c5af597f1c7b6482aa346aca45b009ab10d25.

This commit was created by the following CI build and job:
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/dd2c5af597f1c7b6482aa346aca45b009ab10d25/checks
https://github.com/SORTEE-Github-Hackathon/manuscript/actions/runs/4276630098

@@
 This manuscript
-(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/afbbe55b2ad8febebb104fc9358170f15b3a4596/}{permalink})
+(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/dd2c5af597f1c7b6482aa346aca45b009ab10d25/}{permalink})
 was automatically generated
-from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/afbbe55b2ad8febebb104fc9358170f15b3a4596}{SORTEE-Github-Hackathon/manuscript@afbbe55}
+from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/dd2c5af597f1c7b6482aa346aca45b009ab10d25}{SORTEE-Github-Hackathon/manuscript@dd2c5af}
 on February 26, 2023.
@@
 \item
-  Project administration: RCO
+  Project Administration: RCO, PHPB
 \item
@@
 \item
-  Writing -- original draft: RCO, BPME, KH, EJH, LLSR, ERS, MJG, VF, ADB, CBB, KMG, SSHS, AG, FH, HW, DGEG, PHPB
-\item
-  Writing -- review and editing: RCO, BPME, KH, EJH, LLSR, ERS, MJG, VF, ADB, CBB, KMG, SSHS, AG, FH, HW, DGEG, PHPB
+  Writing - Original Draft: RCO, BPME, KH, EJH, LLSR, ERS, MJG, VF, ADB, CBB, KMG, SSHS, AG, FH, HW, DGEG, PHPB
+\item
+  Writing - Review and Editing: RCO, BPME, KH, EJH, LLSR, ERS, MJG, VF, ADB, CBB, KMG, SSHS, AG, FH, HW, DGEG, PHPB
 \item
   Resources: PHPB
+\item
+  Revisions: PHPB, ERS, RCO, KH, EH, FH
 \end{itemize}
@@
 Department of Energy, Office of Science, Office of Biological and Environmental Research, Earth and Environmental Sciences Division, Data Management program under contract number DE-AC02-05CH11231.
+PHPB was supported by the Science without Borders program and the Brazilian National Council for Research and Technological Development (CNPq-SwB-GDE 142493/2013-0).
 
@@
 
-\hypertarget{ethics-declarations---competing-interests}{%
-\subsection{Ethics declarations - Competing interests}\label{ethics-declarations---competing-interests}}
-
-RCO was recently offered a position to work at GitHub (on July 15, 2022) and will start employment at GitHub on August 23, 2022.
-Initial discussion of publishing this manuscript began in July 2021 and all work on the manuscript took place while RCO was an employee at Lawrence Berkeley National Laboratory.
+\hypertarget{conflict-of-interest-statement}{%
+\subsection{Conflict of Interest Statement}\label{conflict-of-interest-statement}}
+
+On July 15, 2022, RCO was offered a position to work at GitHub and became an employee on August 23, 2022.
+Initial discussion of publishing this manuscript began in July 2021 and all work on the manuscript prior to the first revision was done while RCO was an employee at Lawrence Berkeley National Laboratory.
+The authors declare that there is no conflict of interest that could be perceived as prejudicing the impartiality of the research reported.
 

### 2023-02-26 manuscript.tex
Adjusting figure label, and adding citations for the tables and appendices in the supplementary information. [ci skip]
This build is based on
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/1762a2ed3bf279cca9b4be82485b466dcc2b1623.

This commit was created by the following CI build and job:
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/1762a2ed3bf279cca9b4be82485b466dcc2b1623/checks
https://github.com/SORTEE-Github-Hackathon/manuscript/actions/runs/4276637756

@@
 This manuscript
-(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/dd2c5af597f1c7b6482aa346aca45b009ab10d25/}{permalink})
+(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/1762a2ed3bf279cca9b4be82485b466dcc2b1623/}{permalink})
 was automatically generated
-from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/dd2c5af597f1c7b6482aa346aca45b009ab10d25}{SORTEE-Github-Hackathon/manuscript@dd2c5af}
+from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/1762a2ed3bf279cca9b4be82485b466dcc2b1623}{SORTEE-Github-Hackathon/manuscript@1762a2e}
 on February 26, 2023.
@@
 On the horizontal axis, each activity spans a region representing who is potentially involved with or benefits from each activity.
-For example, storing data and code mainly benefits individual researchers or members of a lab group while making data and code citable and reproducible benefit other labs and the larger community as well.
-Independently of a users knowledge level of GitHub features, there are ways to use GitHub that allow tapping unto one of the most salient benefits of the platform: facilitating and enhancing collaboration.}\label{fig:scatterblob}
+For example, storing data and code mainly benefits individual researchers or members of a laboratory while making data and code citable and reproducible benefit other labs and the larger community as well.
+Independently of ones knowledge of GitHub features, there are ways to use GitHub that allow tapping unto one of the strongest benefits of the platform: facilitating and enhancing collaboration.
+For information on the methods and the data used to create this figure, see Appendix S1.1, Appendix S1.2, and Tables S1.1 and S1.2.}\label{fig:scatterblob}
 }

### 2023-02-26 editorial-communication/response-to-the-reviewers.Qmd
Updating the response to reviewers and the editor

@@
 Our responses are mirror-indented, while the editor's and reviewers' comments are numbered.
-To facilitate the review, we have also included indented extracts from the text, highlighting the changes we made.
+To facilitate the review, we have also included indented extracts from the text, which are indented and displayed in a gray colour.
 The line numbers in our responses correspond to those in the revised manuscript.
@@
 
-<!--# TODO: check that this response still makes sense after merging use case sections -->
+> GitHub allows administrative control over who can view and modify repositories, and the process of cloning, forking and suggesting changes through pull requests (see Box 1) ensures code owners have full control over code and documents.
+> Repositories can be changed from public to private, allowing data storage and management without sacrificing the privacy that may be necessary for certain compendia.
+With this, researchers can grant collaborators read and/or write access to files in private repositories to pursue pre-publication analyses or writing in privacy.
+
 :::
@@
 ::: {#ResponseE13 .response}
-This is a great point.
+**Response**: This is a great point.
 We have added the following sentences to the end of the "Why aren't more EEB researchers using GitHub" section <!--# add line numbers -->:
@@
 > Other scientists may simply lack the time or incentives to document and version control their code if the code is unlikely to be reused beyond their analysis. 
-> However, we (and others, \_e.g.,\_ \[\@doi:10.1098/rspb.2022.1113\]) argue that the endeavour of open science and collaboration requires code owners to document and version control code despite uncertainty around future use.
+> However, we (and others, _e.g._ Gomes _et al._, 2022a) argue that the endeavour of open science and collaboration requires code owners to document and version control code despite uncertainty around future use.
 
-<!--# TODO: replace DOI above with rendered citation? -->
 :::
@@
 ::: {#ResponseE14 .response}
-Thank you for this recommendation!
+**Response**: Thank you for this recommendation!
 We now discuss the possibility of integrating GitHub into existing workflows on Overleaf, Google Drive, and DropBox among other services to collaboratively write scientific manuscripts, in the section "Writing a manuscript" (between lines XXX and XXX) <!--# add line numbers -->.
-We refer to Table 1 for further details on these integrations.
+We refer to Table 1 for further details on these integrations. The changes appear as below:
+
+> Incorporating GitHub into the process of writing a manuscript does not necessarily mean pivoting to an entirely new workflow.
+For instance, authors who prefer writing in LaTeX or Markdown can synchronize Overleaf (https://overleaf.com), HackMD (https://hackmd.io), and other platforms directly with a GitHub repository.
+> Similar GitHub integrations are available for projects stored in DropBox, Google Drive, among other popular tools familiar to many scientists and their collaborators (Table 1).
+
 :::
+
 ##### **E1.5.** Finally, DropBox, SharePoint, and OneDrive are file-sharing systems that include version control, are widely supported, especially in colleges and universities, and are much easier to use for those who might be uncomfortable learning a system such as GitHub.
@@
 ::: {#ResponseE15 .response}
-We think this is a good point since many readers may not immediately see the value in a time investment to learn a new tool when they are already comfortable with tools that meet many or most of their needs.
-Rather than creating a new section, we identify specific points in the manuscript where we discuss how GitHub enables different and better types of collaboration and open science than alternative platforms, such as Dropbox or Google Suite.
+We think this is a good point, as many readers may not immediately see the value in a time investment to learn a new tool when they are already comfortable with tools that meet most of their needs.
+To keep with the recommendations to decrease the complexity and the length of the manuscript, we refrained from creating a new section. 
+To address your recommendation, we identify specific points in the manuscript where we discuss how GitHub enables different and better types of collaboration and open science in relation to alternatives (such as Dropbox or Google Suite).
 We added this discussion earlier in the manuscript, and now refer more often to Table 1.
@@
 
-In the first paragraph of the introduction we made the text more concise throughout and also added new sentence <!--# add line number -->:
+In the first paragraph of the introduction, we made the text more concise and also added the following sentence (between lines XXX and XXX):
 
-> Of all these tools, GitHub is uniquely positioned (Table 1) to benefit scientists because the platform is designed to enable collaboration on computer code\--a fundamental component of modern research.
+> Within the spectrum of cloud-based services for collaboration, GitHub is uniquely positioned (Table 1) to benefit scientists because it is designed to store, track changes, and enable collaboration on computer code – fundamental components of modern research.
 
-In the second paragraph we added <!--# add line number -->:
+To the second paragraph, we added (between lines XXX and XXX):
 
-> Additionally, unlike sharing documents and code via DropBox or Google Drive links, GitHub defaults to public sharing of code and documents and has features like Issues and Discussions (see Box 1) that can immediately and directly contribute to more open science and knowledge sharing.
+> Beyond storage and record-tracking, file management in GitHub is integrated with several communication features, allowing users to engage in discussions, to plan and collaborate in code, and publish information to a webpage (Github Issues, Github Discussions, Github Pages; see Box 1).
+> These features contrast with traditional practices of directly sharing files through email, other cloud-based services or physical storage units, which become challenging and time-consuming in long-term and collaborative projects (Ram, 2013).
+> By allowing users to easily integrate versioning, communication, collaboration with research code and data, Github paves the way for easier implementation of open science practices within research projects (Perez-Riverol et al., 2016).
 
-Under the "storing a research compendium section" we added <!--# add line number -->:
+We added the following sentences to the "Storing a research compendia" section (between lines XXX and XXX):
 
-> While some EEB researchers may prefer to store their code in Google Drive or DropBox, the process of sharing code through these services becomes cumbersome when collaborators have to download and re-upload edited code.\
->
-> On GitHub, code is by default public, and the process of forking and submitting pull requests (see Box 1) ensures a code owner has full control over code and documents in a repository.
+> Many researchers begin using GitHub to backup their research compendium (Marwick et al., 2018) into a centralized, readily-available remote server (see Box 1).
+This practice has the advantages of facilitating collaboration, integrating data and code archiving, allowing file versions to be accessed and restored, and further contributing to open science practices (Borghi & Van Gulick (2022)).
+Every change made to files in version-controlled repositories accompany authored descriptions of modifications (Box 1).
 
@@
 
-> While tools like the Google Suite and DropBox enable rapid sharing and collaboration of some research documents, GitHub brings together features that directly address open science such as tools for soliciting public discussions on code and findings, tracking multiple rounds of edits to files in a sensible way for easy review, and managing complex research projects with many collaborators and goals.
+> While tools like the Google Suite and DropBox enable rapid sharing and collaboration of some research documents, GitHub brings together features that directly integrate open science practices, such as the association of public discussions with data, code and findings, tracking multiple rounds of edits to files in a sensible way for easy review, and managing complex research projects with many collaborators and goals.
 
@@
 > And with institutional availability of software licenses for tools like the Google Suite or Microsoft Office, researchers may be hesitant to spend valuable time learning another tool.
+
+We also note that GitHub falls short in certain features that exist or work better in other platforms, within the "Other platforms section":
+
+> First, real-time document editing is still best performed on other platforms (e.g., cloud-stored documents from Microsoft Word, Google Docs, HackMD (https://hackmd.io/)).
+Second, operations that are dependent on software requiring graphical user interfaces might not be easily achievable in GitHub, such as designing and manipulating figures or tables.
+> While creating tables and figures can be done through code, users may choose other software to collaboratively brainstorm figures and tables (e.g., Google Slides, Google Sheets; but see GitHub Discussions).
+
 :::
@@
 We also cited resources for learning how to use tools.
-These changes allowed us to focus on the usefulness of these tools for research in ecology and evolution.
-(2) We removed the "laboratory notebooks" section and merged part of its contents into the X section, which allowed us to further shorten the text; and, (3) [...].
+These changes allowed us to focus on the usefulness of these tools for research in ecology and evolution;
+(2) we removed the "laboratory notebooks" section and merged part of its contents into the other sections section, which allowed us to further shorten the text; and, (3) we performed an extensive review of the text to clarify and shorten sentences.
 
- <!--# This comment does not seem to fit within this section  -->
-In regards to the specific suggestion about deprioritizing GitHub communication tools, we believe these are extremely useful alternatives to reply-all email chains for a variety of reasons and have attempted to improve the clarity of this section of our manuscript \[end of project management section\].
 :::
@@
 ::: {#ResponseR12 .response}
+We thank you for this suggestion and we agree that the narrative could be simplified to convince researchers to adopt GitHub for certain of their practices. 
 Following our modifications to address [R1.1](#sec-R1.1) and [E1.1](#sec-E1.1), we reduced jargon, simplified the narrative, and focused more in the advantages of the features GitHub provide to improve the research workflow in ecology and evolution.
-We also clarify to the reader that the objective of the manuscript is not to instruct how these tools.
- <!--# Self-note: This comment needs improvement, as it is not very convincing. -->
+We also clarify to the reader that the objective of the manuscript is not to instruct how these tools work.
+We still mention certain advanced tools, but we refer the reader to additional learning resources instead of describing them in the manuscript.
+
 :::
@@
 ::: {#ResponseR13 .response}
-We appreciate this comment.
+We appreciate this suggestion.
 While the attribution of a type of return of investment index to use cases could be interesting, we believe that such value can be highly biased, subjective and vary much among fields, laboratories, research culture, and individuals.
-For instance, while collaborative writing of a manuscript using GitHub may be seen as a strong time investment and an advanced usage, there is an increasing number of research articles adopting this features, such as XXXX, XXXX, XXXX, in addition to our manuscript.
+For instance, while collaborative writing of a manuscript using GitHub may be seen as a strong time investment and an advanced usage, there is an increasing number of research articles using GitHub to write manuscripts, such as Halie et al.
+(arXiv:2102.01521, 2021),  Halie et al.
+(mSystems.00233-21, 2021), Lordan et al.
+(mSystems.00122-21, 2021),  Rando et al.
+(CEUR.2976.2, 2022), Sabatini et al.
+(Global Ecology and Biogeogrpahy, 2021), Le et al.
+(Cell Systems, 2021), and many more (see https://manubot.org/catalog/; in addition to our manuscript).
 In these cases, most co-authors had little experience with effectively integrating Github tools to write a manuscript within the platform, and had to commit to learn and adopt proposed frameworks to achieve project completion.
-It is also difficult to measure return on investment on innovative tools that only recently took off, such as the usage of Github Actions in ecological research frameworks for data management, processing, and analysis (*e.g.*, in XXXX, XXXX, XXX).
-As we mentioned, we appreciate this suggestion, however we think that the quantification of a ratio between investment of time and resources and returns when learning research aiding skills requires an in-depth individual study.
-Taking this into account, our metric of cognitive requirement represented in Figure 2 considers the usefulness?
-or cognitive requirement?
-for learning this new tool (see also our response to [R2.2](#sec-R2.2)).
+It is also difficult to measure return on investment on innovative tools that only recently took off, such as the usage of Github Actions in ecological research frameworks for data management, processing, and analysis [*e.g.*, in Sabatini et al.
+(Global Ecology and Biogeography, 2021), McIntire et al.
+(Ecology Letters, 2022), Micheletti et al.
+(Frontiers of Ecology and Evolution, 2021)].
+We reiterate our appreciation for this suggestion, however we think that the quantification of a ratio between investment of time and resources and returns when learning research aiding skills requires an in-depth individual study.
+
+In this context, we note that our metric of cognitive requirement represented in Figure 2 considers the "usefulness" or cognitive requirement for learning GitHub (see also our response to [R2.2](#sec-R2.2)).
 Moreover, we have taken the advice of reviewer 1, and reduced and reordered the use cases (see our responses to [R1.4](#sec-R1.4) and [R1.1](#sec-R1.1)).
+
 :::
@@
 ::: {#ResponseR14 .response}
-Response
+
+Thank you for this recommendation. We moved the "Project continuity" section to be presented as the second use case, immediately after introducing storing and research compedia.
+
 :::
@@
 ::: {#ResponseR21 .response}
-Response
+
+Thank you for this recommendation!
+We have decreased the complexity and clarified Figure 1.
+We changed it to bright-mode instead of dark-mode, blurred out irrelevant content, added three clear bounding boxes with their respective labels to highlight the repository resources, the file system organization and commit history, and the contributors.
+
 :::
@@
 ::: {#ResponseR22 .response}
-Response
+
+Thank you for catching this.
+We added a supplementary material containing appendices, tables and code that detail how the indices for degrees of collaboration and of difficulty were estimated for each use case.
+We also added citations to these elements in the text.
+
 :::
@@
 ::: {#ResponseR23 .response}
+
 We now briefly discuss the origin of Git and its expansion to applications beyond software development to help manage collaborations and community contributions, in the introduction <!--# add line numbers -->.
+
 :::
@@
 Thank you for this recommendation.
-We recognize that these are developments that have been increasingly encourage to be adopted in biological research.
-We now provide brief comments on how automation can aid unit testing of research code (between lines XXX and XXX), and that automation can also help the interpretation, integration and usage of data and software across different sources.
+We recognize that these are developments that have been increasingly encouraged in biological research.
+We now provide brief comments on how automation can aid unit testing of research code (between lines XXX and XXX), and that automation can also help the interpretation, integration and usage of data and software across different sources, as seen below:
+
+> In addition to increasing scientific rigour and confidence in ecological software (Scheller et al., 2010), automation can help advance more rapidly sharing ecological data and making sure the data are high quality (Dietze et al., 2018).
+Integrating automation workflows has been highly encouraged in areas of EEB, including predictive ecology (McIntire et al., 2022), long-term ecological studies (Ernest et al., 2018; Yenni et al., 2019), and management of species at risk information (Naujokaitis-Lewis et al., 2022).
 

### 2023-02-26 editorial-communication/response-to-the-reviewers.Qmd
Minor edits to the letter

@@
 ::: {style="text-align: justify"}
-Dear Dr. XXX,
+Dear Dr. XXX, Editor for Methods in Ecology and Evolution
 
@@
 
-Briefly, we have rewritten several sentences to improve their clarity, decrease the complexity and length of sections. 
+Within our extensive revision, we have rewritten several sentences to improve their clarity, decrease the complexity and length of sections. 
 We also improved the readability of figures.
@@
 
-\[...\]
+Sincerely,
+
+Pedro Henrique Pereira Braga, on behalf of my co-authors
 
@@
 ::: {#ResponseR25 .response}
-Response
+We thank you for this comment. [WORKING ON THIS]
 :::

### 2023-02-26 manuscript.tex
Updating the response to reviewers and the editor [ci skip]
This build is based on
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/371f6f710b0016df19bf0858b534ba45cc4c2505.

This commit was created by the following CI build and job:
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/371f6f710b0016df19bf0858b534ba45cc4c2505/checks
https://github.com/SORTEE-Github-Hackathon/manuscript/actions/runs/4276922798

@@
 This manuscript
-(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/1762a2ed3bf279cca9b4be82485b466dcc2b1623/}{permalink})
+(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/371f6f710b0016df19bf0858b534ba45cc4c2505/}{permalink})
 was automatically generated
-from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/1762a2ed3bf279cca9b4be82485b466dcc2b1623}{SORTEE-Github-Hackathon/manuscript@1762a2e}
+from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/371f6f710b0016df19bf0858b534ba45cc4c2505}{SORTEE-Github-Hackathon/manuscript@371f6f7}
 on February 26, 2023.

### 2023-02-26 manuscript.tex
Minor edits to the letter [ci skip]
This build is based on
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/040e70b2b68ac8822e659081c5404a1ed8afe972.

This commit was created by the following CI build and job:
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/040e70b2b68ac8822e659081c5404a1ed8afe972/checks
https://github.com/SORTEE-Github-Hackathon/manuscript/actions/runs/4276944252

@@
 This manuscript
-(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/371f6f710b0016df19bf0858b534ba45cc4c2505/}{permalink})
+(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/040e70b2b68ac8822e659081c5404a1ed8afe972/}{permalink})
 was automatically generated
-from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/371f6f710b0016df19bf0858b534ba45cc4c2505}{SORTEE-Github-Hackathon/manuscript@371f6f7}
+from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/040e70b2b68ac8822e659081c5404a1ed8afe972}{SORTEE-Github-Hackathon/manuscript@040e70b}
 on February 26, 2023.

### 2023-02-26 manuscript.tex
Update README with new dates [ci skip]
This build is based on
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/6ddc6c567be38982e38bb2090b00fb76430b0776.

This commit was created by the following CI build and job:
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/6ddc6c567be38982e38bb2090b00fb76430b0776/checks
https://github.com/SORTEE-Github-Hackathon/manuscript/actions/runs/4276965432

@@
 This manuscript
-(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/040e70b2b68ac8822e659081c5404a1ed8afe972/}{permalink})
+(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/6ddc6c567be38982e38bb2090b00fb76430b0776/}{permalink})
 was automatically generated
-from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/040e70b2b68ac8822e659081c5404a1ed8afe972}{SORTEE-Github-Hackathon/manuscript@040e70b}
+from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/6ddc6c567be38982e38bb2090b00fb76430b0776}{SORTEE-Github-Hackathon/manuscript@6ddc6c5}
 on February 26, 2023.

### 2023-02-26 manuscript.tex
Update README.md [ci skip]
This build is based on
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/ad2c9cccb40e8cfde96b21bdb5c7368f051d42e5.

This commit was created by the following CI build and job:
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/ad2c9cccb40e8cfde96b21bdb5c7368f051d42e5/checks
https://github.com/SORTEE-Github-Hackathon/manuscript/actions/runs/4276977122

@@
 This manuscript
-(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/6ddc6c567be38982e38bb2090b00fb76430b0776/}{permalink})
+(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/ad2c9cccb40e8cfde96b21bdb5c7368f051d42e5/}{permalink})
 was automatically generated
-from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/6ddc6c567be38982e38bb2090b00fb76430b0776}{SORTEE-Github-Hackathon/manuscript@6ddc6c5}
+from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/ad2c9cccb40e8cfde96b21bdb5c7368f051d42e5}{SORTEE-Github-Hackathon/manuscript@ad2c9cc}
 on February 26, 2023.

### 2023-03-01 R/Supp_Info_1.Rmd
Fixing problem with the axis in the plot

@@
 
-```{r}
+```{r plot-segments}
 my_colors <- viridis::turbo(n = 100, alpha = 0.9)[c(2, 
@@
       units = "in",
-      res = 300,
+      res = 600,
       bg = "white")  
 }
+
 par(xpd = NA,
     mai = c(1.02, 1, 0.82, 4),
-    bty="n")
+    bty = "n")
 
@@
 ###############################################################
+
 plot(x = c(0.5, 5.5),
@@
      col.axis = "white",
-     tck = 0.02)
+     tck = 0.02,
+     yaxt = "n"
+     # yaxs = 'i'
+     )
+
 title(ylab = "Technical Difficulty", 
@@
       cex.lab = 1)
+
 title(xlab = "Degree of Collaboration", 
@@
 ###############################################################
+
+axis(2,
+     seq(1, 12, length.out = 5),
+     outer = F,
+     labels = F,
+     pos = 0.5,
+     hadj = 1)
 
@@
                 "All \nUsers"))
-text(x = c(1, 3, 5),
+
+text(x = c(0.5, 3, 5),
      y = -1.7, 

### 2023-03-01 manuscript.tex
Merge branch 'main' of https://github.com/SORTEE-Github-Hackathon/manuscript [ci skip]
This build is based on
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/bab6e3fbfbc8e0e7e619032dc0976b53d321f9e8.

This commit was created by the following CI build and job:
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/bab6e3fbfbc8e0e7e619032dc0976b53d321f9e8/checks
https://github.com/SORTEE-Github-Hackathon/manuscript/actions/runs/4307143261

@@
 This manuscript
-(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/ad2c9cccb40e8cfde96b21bdb5c7368f051d42e5/}{permalink})
+(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/bab6e3fbfbc8e0e7e619032dc0976b53d321f9e8/}{permalink})
 was automatically generated
-from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/ad2c9cccb40e8cfde96b21bdb5c7368f051d42e5}{SORTEE-Github-Hackathon/manuscript@ad2c9cc}
-on February 26, 2023.
+from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/bab6e3fbfbc8e0e7e619032dc0976b53d321f9e8}{SORTEE-Github-Hackathon/manuscript@bab6e3f}
+on March 1, 2023.
 
@@
 GitHub Docs.
-Retrieved February 26, 2023, from \url{https://ghdocs-prod.azurewebsites.net/en/repositories/managing-your-repositorys-settings-and-features/customizing-your-repository/about-code-owners}
+Retrieved March 1, 2023, from \url{https://ghdocs-prod.azurewebsites.net/en/repositories/managing-your-repositorys-settings-and-features/customizing-your-repository/about-code-owners}
 
@@
 GitHub Docs.
-Retrieved February 26, 2023, from \url{https://ghdocs-prod.azurewebsites.net/en/repositories/working-with-files/managing-large-files/about-large-files-on-github}
+Retrieved March 1, 2023, from \url{https://ghdocs-prod.azurewebsites.net/en/repositories/working-with-files/managing-large-files/about-large-files-on-github}
 
@@
 GitHub Docs.
-Retrieved February 26, 2023, from \url{https://ghdocs-prod.azurewebsites.net/en/issues/planning-and-tracking-with-projects/learning-about-projects/about-projects}
+Retrieved March 1, 2023, from \url{https://ghdocs-prod.azurewebsites.net/en/issues/planning-and-tracking-with-projects/learning-about-projects/about-projects}
 
@@
 GitHub Docs.
-Retrieved February 26, 2023, from \url{https://ghdocs-prod.azurewebsites.net/en/communities/setting-up-your-project-for-healthy-contributions/adding-a-license-to-a-repository}
+Retrieved March 1, 2023, from \url{https://ghdocs-prod.azurewebsites.net/en/communities/setting-up-your-project-for-healthy-contributions/adding-a-license-to-a-repository}
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-6CMMeSeD}{}}%
-Bryan, J., \& TAs, T. S. 545. (n.d.). \emph{STAT 545}. Retrieved February 26, 2023, from \url{https://stat545.com/}
+Bryan, J., \& TAs, T. S. 545. (n.d.). \emph{STAT 545}. Retrieved March 1, 2023, from \url{https://stat545.com/}
 
 \leavevmode\vadjust pre{\hypertarget{ref-lx49NGto}{}}%
-\emph{Connect GitHub to a Project - OSF Support}. (n.d.). Retrieved February 26, 2023, from \url{https://help.osf.io/article/211-connect-github-to-a-project}
+\emph{Connect GitHub to a Project - OSF Support}. (n.d.). Retrieved March 1, 2023, from \url{https://help.osf.io/article/211-connect-github-to-a-project}
 
 \leavevmode\vadjust pre{\hypertarget{ref-T03Api6e}{}}%
-\emph{Continuous Integration and Delivery}. (n.d.). CircleCI. Retrieved February 26, 2023, from \url{https://circleci.com/}
+\emph{Continuous Integration and Delivery}. (n.d.). CircleCI. Retrieved March 1, 2023, from \url{https://circleci.com/}
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-NUXbp429}{}}%
-\emph{Features • GitHub Actions}. (n.d.). GitHub. Retrieved February 26, 2023, from \url{https://github.com/features/actions}
+\emph{Features • GitHub Actions}. (n.d.). GitHub. Retrieved March 1, 2023, from \url{https://github.com/features/actions}
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-1CM2EcdVk}{}}%
-\emph{Git - A Short History of Git}. (n.d.). Retrieved February 26, 2023, from \url{https://git-scm.com/book/en/v2/Getting-Started-A-Short-History-of-Git}
+\emph{Git - A Short History of Git}. (n.d.). Retrieved March 1, 2023, from \url{https://git-scm.com/book/en/v2/Getting-Started-A-Short-History-of-Git}
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-ZvrOcg9w}{}}%
-Hester, J. B., the STAT 545 TAs, Jim. (n.d.). \emph{Let's Git started \textbar{} Happy Git and GitHub for the useR}. Retrieved February 26, 2023, from \url{https://happygitwithr.com/}
+Hester, J. B., the STAT 545 TAs, Jim. (n.d.). \emph{Let's Git started \textbar{} Happy Git and GitHub for the useR}. Retrieved March 1, 2023, from \url{https://happygitwithr.com/}
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-3UAritXO}{}}%
-\emph{Issues · fmsabatini/sPlotOpen\_Manuscript}. (n.d.). GitHub. Retrieved February 26, 2023, from \url{https://github.com/fmsabatini/sPlotOpen_Manuscript}
+\emph{Issues · fmsabatini/sPlotOpen\_Manuscript}. (n.d.). GitHub. Retrieved March 1, 2023, from \url{https://github.com/fmsabatini/sPlotOpen_Manuscript}
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Re6Eg2va}{}}%
-\emph{Manubot - Manuscripts, open and automated}. (n.d.). Retrieved February 26, 2023, from \url{https://manubot.org}
+\emph{Manubot - Manuscripts, open and automated}. (n.d.). Retrieved March 1, 2023, from \url{https://manubot.org}
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-oGbKxHzj}{}}%
-\emph{Using Git and GitHub}. (n.d.). Retrieved February 26, 2023, from \url{https://www.overleaf.com/learn/how-to/Using_Git_and_GitHub}
+\emph{Using Git and GitHub}. (n.d.). Retrieved March 1, 2023, from \url{https://www.overleaf.com/learn/how-to/Using_Git_and_GitHub}
 

### 2023-03-01 editorial-communication/response-to-the-reviewers.Qmd
Triggering action
Deploying to gh-pages from @ SORTEE-Github-Hackathon/manuscript@6bf75de9b4247f2fc93b6331ebb4ff32dfbb2277 🚀

@@
 ::: {style="text-align: justify"}
-Dear Dr. XXX, Editor for Methods in Ecology and Evolution
+Dear Dr. XXXX, Editor for Methods in Ecology and Evolution
 
@@
 ::: {#ResponseR25 .response}
-We thank you for this comment. [WORKING ON THIS]
+We thank you for this comment.
+We discussed amd attempted to associate the use cases to hypothetical versions of the scientific method and academic roles.
+Despite enjoying the idea of a figure resembling Figure 1 from Munafò et al.
+2017 (Nature), we have not been able to produce a figure that would not feel polluted or redundant with Figure 2.
+We have attempted this with a circular flow, stacked bar chart, or a network graph.
+The issue is that most use cases are related to many stages of the scientific process.
+The exception are "Academic websites" and "Educational materials", which may contribute to research development, but more marginally in relation to the other use cases.
+We appreciate the suggestion and would be happy to come to back it if you think it is important for our study.
 :::

### 2023-03-01 manuscript.tex
Update response-to-the-reviewers.Qmd [ci skip]
This build is based on
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/f105568d200daed275bf3735ef04dd1b237642b8.

This commit was created by the following CI build and job:
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/f105568d200daed275bf3735ef04dd1b237642b8/checks
https://github.com/SORTEE-Github-Hackathon/manuscript/actions/runs/4307394423

@@
 This manuscript
-(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/bab6e3fbfbc8e0e7e619032dc0976b53d321f9e8/}{permalink})
+(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/f105568d200daed275bf3735ef04dd1b237642b8/}{permalink})
 was automatically generated
-from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/bab6e3fbfbc8e0e7e619032dc0976b53d321f9e8}{SORTEE-Github-Hackathon/manuscript@bab6e3f}
+from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/f105568d200daed275bf3735ef04dd1b237642b8}{SORTEE-Github-Hackathon/manuscript@f105568}
 on March 1, 2023.

### 2023-03-02 manuscript.tex
Merge pull request #310 from SORTEE-Github-Hackathon/kaitlyngaynor-patch-1 [ci skip]
This build is based on
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/28ba5dabdf12d85204b45ef08ed5ed4348d1dee6.

This commit was created by the following CI build and job:
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/28ba5dabdf12d85204b45ef08ed5ed4348d1dee6/checks
https://github.com/SORTEE-Github-Hackathon/manuscript/actions/runs/4317539530

@@
 This manuscript
-(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/f105568d200daed275bf3735ef04dd1b237642b8/}{permalink})
+(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/28ba5dabdf12d85204b45ef08ed5ed4348d1dee6/}{permalink})
 was automatically generated
-from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/f105568d200daed275bf3735ef04dd1b237642b8}{SORTEE-Github-Hackathon/manuscript@f105568}
-on March 1, 2023.
+from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/28ba5dabdf12d85204b45ef08ed5ed4348d1dee6}{SORTEE-Github-Hackathon/manuscript@28ba5da}
+on March 2, 2023.
 
@@
   \href{https://twitter.com/kaitlyngaynor}{kaitlyngaynor}
-  Departments of Zoology and Botany, University of British Columbia, Vancouver, BC, Canada; National Center for Ecological Analysis and Synthesis, Santa Barbara, CA 93101, USA
+  Departments of Zoology and Botany, University of British Columbia, Vancouver, BC, Canada
 \item
@@
 GitHub Docs.
-Retrieved March 1, 2023, from \url{https://ghdocs-prod.azurewebsites.net/en/repositories/managing-your-repositorys-settings-and-features/customizing-your-repository/about-code-owners}
+Retrieved March 2, 2023, from \url{https://ghdocs-prod.azurewebsites.net/en/repositories/managing-your-repositorys-settings-and-features/customizing-your-repository/about-code-owners}
 
@@
 GitHub Docs.
-Retrieved March 1, 2023, from \url{https://ghdocs-prod.azurewebsites.net/en/repositories/working-with-files/managing-large-files/about-large-files-on-github}
+Retrieved March 2, 2023, from \url{https://ghdocs-prod.azurewebsites.net/en/repositories/working-with-files/managing-large-files/about-large-files-on-github}
 
@@
 GitHub Docs.
-Retrieved March 1, 2023, from \url{https://ghdocs-prod.azurewebsites.net/en/issues/planning-and-tracking-with-projects/learning-about-projects/about-projects}
+Retrieved March 2, 2023, from \url{https://ghdocs-prod.azurewebsites.net/en/issues/planning-and-tracking-with-projects/learning-about-projects/about-projects}
 
@@
 GitHub Docs.
-Retrieved March 1, 2023, from \url{https://ghdocs-prod.azurewebsites.net/en/communities/setting-up-your-project-for-healthy-contributions/adding-a-license-to-a-repository}
+Retrieved March 2, 2023, from \url{https://ghdocs-prod.azurewebsites.net/en/communities/setting-up-your-project-for-healthy-contributions/adding-a-license-to-a-repository}
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-6CMMeSeD}{}}%
-Bryan, J., \& TAs, T. S. 545. (n.d.). \emph{STAT 545}. Retrieved March 1, 2023, from \url{https://stat545.com/}
+Bryan, J., \& TAs, T. S. 545. (n.d.). \emph{STAT 545}. Retrieved March 2, 2023, from \url{https://stat545.com/}
 
 \leavevmode\vadjust pre{\hypertarget{ref-lx49NGto}{}}%
-\emph{Connect GitHub to a Project - OSF Support}. (n.d.). Retrieved March 1, 2023, from \url{https://help.osf.io/article/211-connect-github-to-a-project}
+\emph{Connect GitHub to a Project - OSF Support}. (n.d.). Retrieved March 2, 2023, from \url{https://help.osf.io/article/211-connect-github-to-a-project}
 
 \leavevmode\vadjust pre{\hypertarget{ref-T03Api6e}{}}%
-\emph{Continuous Integration and Delivery}. (n.d.). CircleCI. Retrieved March 1, 2023, from \url{https://circleci.com/}
+\emph{Continuous Integration and Delivery}. (n.d.). CircleCI. Retrieved March 2, 2023, from \url{https://circleci.com/}
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-NUXbp429}{}}%
-\emph{Features • GitHub Actions}. (n.d.). GitHub. Retrieved March 1, 2023, from \url{https://github.com/features/actions}
+\emph{Features • GitHub Actions}. (n.d.). GitHub. Retrieved March 2, 2023, from \url{https://github.com/features/actions}
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-1CM2EcdVk}{}}%
-\emph{Git - A Short History of Git}. (n.d.). Retrieved March 1, 2023, from \url{https://git-scm.com/book/en/v2/Getting-Started-A-Short-History-of-Git}
+\emph{Git - A Short History of Git}. (n.d.). Retrieved March 2, 2023, from \url{https://git-scm.com/book/en/v2/Getting-Started-A-Short-History-of-Git}
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-ZvrOcg9w}{}}%
-Hester, J. B., the STAT 545 TAs, Jim. (n.d.). \emph{Let's Git started \textbar{} Happy Git and GitHub for the useR}. Retrieved March 1, 2023, from \url{https://happygitwithr.com/}
+Hester, J. B., the STAT 545 TAs, Jim. (n.d.). \emph{Let's Git started \textbar{} Happy Git and GitHub for the useR}. Retrieved March 2, 2023, from \url{https://happygitwithr.com/}
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-3UAritXO}{}}%
-\emph{Issues · fmsabatini/sPlotOpen\_Manuscript}. (n.d.). GitHub. Retrieved March 1, 2023, from \url{https://github.com/fmsabatini/sPlotOpen_Manuscript}
+\emph{Issues · fmsabatini/sPlotOpen\_Manuscript}. (n.d.). GitHub. Retrieved March 2, 2023, from \url{https://github.com/fmsabatini/sPlotOpen_Manuscript}
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Re6Eg2va}{}}%
-\emph{Manubot - Manuscripts, open and automated}. (n.d.). Retrieved March 1, 2023, from \url{https://manubot.org}
+\emph{Manubot - Manuscripts, open and automated}. (n.d.). Retrieved March 2, 2023, from \url{https://manubot.org}
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-oGbKxHzj}{}}%
-\emph{Using Git and GitHub}. (n.d.). Retrieved March 1, 2023, from \url{https://www.overleaf.com/learn/how-to/Using_Git_and_GitHub}
+\emph{Using Git and GitHub}. (n.d.). Retrieved March 2, 2023, from \url{https://www.overleaf.com/learn/how-to/Using_Git_and_GitHub}
 

### 2023-03-04 manuscript.tex
Merge pull request #311 from SORTEE-Github-Hackathon/Matt_typos [ci skip]
This build is based on
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/290c4cd8316ffaa08ceafd6ac4cfcdfe09774653.

This commit was created by the following CI build and job:
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/290c4cd8316ffaa08ceafd6ac4cfcdfe09774653/checks
https://github.com/SORTEE-Github-Hackathon/manuscript/actions/runs/4332721252

@@
 This manuscript
-(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/28ba5dabdf12d85204b45ef08ed5ed4348d1dee6/}{permalink})
+(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/290c4cd8316ffaa08ceafd6ac4cfcdfe09774653/}{permalink})
 was automatically generated
-from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/28ba5dabdf12d85204b45ef08ed5ed4348d1dee6}{SORTEE-Github-Hackathon/manuscript@28ba5da}
-on March 2, 2023.
+from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/290c4cd8316ffaa08ceafd6ac4cfcdfe09774653}{SORTEE-Github-Hackathon/manuscript@290c4cd}
+on March 4, 2023.
 
@@
 For instance, one can create a discussion on a project repository to decide which method to apply for biodiversity data analysis.
-Then, an issue can be created to establish steps and responsibilities including data formatting, statistical analyses, figure generation, and issue resolution (\emph{e.g.}, see issues and discussions in the sPlotOpen manuscript repository, \protect\hyperlink{ref-doi:10.1111ux2fgeb.13346}{\textbf{doi:10.1111/geb.13346?}}); \emph{Issues · Fmsabatini/sPlotOpen\_Manuscript} (\protect\hyperlink{ref-3UAritXO}{n.d.})=is\%3Aissue+is\%3Aclosed{]}.
+Then, an issue can be created to establish steps and responsibilities including data formatting, statistical analyses, figure generation, and issue resolution (\protect\hyperlink{ref-3UAritXO}{\emph{Issues · Fmsabatini/sPlotOpen\_Manuscript}, n.d.}, =is\%3Aissue+is\%3Aclosed; \emph{e.g.}, see issues and discussions in the sPlotOpen manuscript repository, \protect\hyperlink{ref-doi:10.1111ux2fgeb.13346}{\textbf{doi:10.1111/geb.13346?}}).
 Using GitHub for all project-related conversation and planning, rather than email or messaging tools, makes it easier to keep track of progress throughout the lifespan of a project.
@@
 Despite researchers in ecology and evolution generally lacking experience in building or hosting webpages, many tools have been developed to help this process.
-Static websites can now be easily built {[}using, for example Quarto (\url{https://quarto.org}), RMarkdown, Hugo (\url{https://gohugo.io}), GitHub Website templates (\url{https://github.com/topics/website-template})){]}, stored in a repository, and be readily hosted by activating GitHub's Pages (\url{https://pages.github.com}) feature.
+Static websites can now be easily built {[}using, for example Quarto (\url{https://quarto.org}), RMarkdown, Hugo (\url{https://gohugo.io}), GitHub Website templates (\url{https://github.com/topics/website-template})), stored in a repository, and be readily hosted by activating GitHub's Pages (\url{https://pages.github.com}) feature.
 Creating and hosting websites on GitHub Pages is more complex than out-of-the-box platforms (\emph{e.g.}, Wix, Weebly, Google Sites).
-However, free hosting, widely available template customization, and versioning are strong advantages over alternatives.
-
-\hypertarget{archiving-citable-code}{%
-\subsubsection{Archiving citable code and data}\label{archiving-citable-code}}
-
-Government, funding agencies, and publishers exercise rigorous open access data policies and mandates (\protect\hyperlink{ref-1Hcf13Q0k}{Nugroho et al., 2015}; \protect\hyperlink{ref-PLmDFZrm}{Tenopir et al., 2020}).
-However, code and data sharing may be met by individual reluctance, temporary embargoes, or partially prevented by privacy and confidentiality reasons (\protect\hyperlink{ref-SLq38RVv}{Figueiredo, 2017}; \protect\hyperlink{ref-1CzUZwyU2}{Tenopir et al., 2015}; \protect\hyperlink{ref-1Ch6LSHef}{Wicherts et al., 2011}).
-Still, data deposition and ensuring its availability can amplify the outreach of published studies (\protect\hyperlink{ref-666HppfO}{Pronk et al., 2015}), increase citation rates (\protect\hyperlink{ref-1CcAUn3Lu}{Piwowar et al., 2007}), and among many other reasons, enable the reproducibility and robustness of scientific advances (\protect\hyperlink{ref-1HZdsK5Kn}{Baker, 2016}; \protect\hyperlink{ref-uBJwnPbq}{Mislan et al., 2016}; \protect\hyperlink{ref-4LaijDIZ}{{``On Data Availability, Reproducibility and Reuse,''} 2017}).
-While public repositories on GitHub make it easy to store and share data files, they are not considered long-term repositories for research materials.
-This is because GitHub, a for-profit company, does not have long-term data availability guarantees, allowing users to delete or make repositories private after publication.
-Also, GitHub does not issue Digital Object Identifiers (DOI) for content uploaded to their servers.
-DOIs are persistent and citable unique alpha-numeric identifiers assigned to digitally-stored research materials.
-Because of this, scientists sharing code and data through GitHub are strongly encouraged to independently submit their research materials to long-term data archives (\emph{e.g.}, Zenodo, Figshare, Dryad, OSF (\protect\hyperlink{ref-1Du6fzB8g}{Crystal‐Ornelas et al., 2021}; \protect\hyperlink{ref-kEX5dgzK}{Perez-Riverol et al., 2016}; \protect\hyperlink{ref-10ghgV3S8}{J.
-Perkel, 2016}); \protect\hyperlink{tbl:compare}{Table 1}).
-Some of these options (Zenodo, Figshare and OSF) integrate with GitHub, allowing project, code, and data releases (\protect\hyperlink{definitions}{Box 1}) to be archived with versioned, citable DOIs.
-Linking GitHub repositories with a DOI helps research become findable, properly cited, and can ensure long-term stability (\protect\hyperlink{ref-iIEKCTLU}{Hampton et al., 2015}).
-This strategy has been increasingly adopted in numerous studies in ecology and evolution (\emph{e.g.}, the Zenodo repositores for Hudgins (\protect\hyperlink{ref-GQj3c17f}{2022}), EllenJCoombs (\protect\hyperlink{ref-bZNn2hbh}{2020}), and Lrharper1 (\protect\hyperlink{ref-ZI1OqZNr}{2018})).
-
-An important aspect of making code and data citable and reusable is to add an appropriate license to protect intellectual property.
-Code published without a license is under exclusive copyright (by default), protecting it from copy, distribution, and modifications.
-One may grant specific rights to their code for reuse by adding licensing files and specifications within GitHub repositories (\protect\hyperlink{ref-TOsASkn5}{\emph{Adding a License to a Repository}, n.d.}).
-The Choose a License (\url{https://choosealicense.com/non-software/}) website offers further guidance on the licenses available for research and creative products.
-For example, Creative Commons (CC; \url{https://creativecommons.org/licenses/}) licenses can specify that shared code is intended for a specific analysis.
-A CC BY 4.0 license specifies that any code (or other creative products) must be appropriately credited to its original author when distributed, adapted or reused.
-
-\hypertarget{code-editing}{%
-\subsubsection{Collaborative and asynchronous code editing}\label{code-editing}}
-
-GitHub can serve as a platform for everyone working with research (\emph{e.g.}, supervisors or advisors, graduate students, postdoctoral fellows, and collaborators) to share in-progress work, and flag specific challenges or questions for each other (\protect\hyperlink{tbl:roles}{Table 2}).
-Periodic code, data and text review is useful for identifying errors early in the research process (\protect\hyperlink{ref-hm9PaCLD}{Song et al., 2020}), and informing further training and mentorship to fill gaps in skills.
-This is facilitated by a group of core features of Git and GitHub that allow contributors to discuss and simultaneously work on a project.
-For instance, users can clone and fork repositories (see \protect\hyperlink{definitions}{Box 1}), allowing for modifications to be done on a linked copy of a repository, which can then later be merged into the main project through pull requests.
-Collaborators can comment on specific lines of code and text or suggest changes, which can then be incorporated with the click of a button, greatly facilitating peer review.
-Explicit project organization and increased communication within pull requests, in GitHub Issues, or in GitHub Discussions can help with project development and with potential merge conflicts due to users simultaneously working on the same sections.
-Moreover, version control (\protect\hyperlink{ref-K7nbP1Ty}{Crystal-Ornelas et al., 2023}) allows researchers to make changes in code or documents without worrying about irreparably modifying someone else's work.
-
-By enabling more comprehensive remote collaboration, GitHub encourages the exchange of ideas among researchers at different institutions and in different countries, which can serve to improve the quality of the research itself by providing open access to data and code.
-
-\hypertarget{writing-manuscript}{%
-\subsubsection{Writing a manuscript}\label{writing-manuscript}}
-
-Beyond supporting collaborative code development, GitHub can be used for writing manuscripts.
-Writing a manuscript and storing its associated data and code in GitHub increases scientific reproducibility because text, code, and data can be found in one place.
-Although it may involve more initial time investment for setup, GitHub has many features that support a powerful collaborative workflow when writing manuscripts (\protect\hyperlink{ref-4ny1onB0}{Ram, 2013}).
-Text documents stored and versioned in GitHub can be instantly displayed when written in Markdown, a lightweight markup language increasingly popular among scientists.
-When manuscripts are written in Markdown on GitHub, co-authors can contribute changes or suggest revisions to a manuscript in the same ways they would contribute changes or suggest revisions to code (see \protect\hyperlink{code-editing}{Collaborative and asynchronous code editing}).
-Relevant literature or issues can be suggested using the Discussions and Issues features.
-
-Incorporating GitHub into the process of writing a manuscript does not necessarily mean pivoting to an entirely new workflow.
-For instance, authors who prefer writing in LaTeX or Markdown can synchronize Overleaf (\protect\hyperlink{ref-oGbKxHzj}{\emph{Using Git and GitHub}, n.d.}), HackMD (\url{https://hackmd.io}), and other platforms directly with a GitHub repository.
-Similar GitHub integrations are available for projects stored in DropBox, Google Drive, among other popular tools familiar to many scientists and their collaborators (\protect\hyperlink{tbl:compare}{Table 1}).
-
-We wrote this manuscript using Manubot (\protect\hyperlink{ref-Re6Eg2va}{\emph{Manubot - Manuscripts, Open and Automated}, n.d.}), a modifiable workflow implemented in GitHub to automatically render manuscripts and automate bibliographical tasks (\protect\hyperlink{ref-YuJbg3zO}{Himmelstein et al., 2019}).
-Manubot uses GitHub's automation workflow, GitHub Actions, to combine and convert individual Markdown files into a single LaTeX document, which can then be converted to a Word or PDF document, and displayed as a webpage.
-Citations and bibliographic references are automatically managed with citable persistent identifiers (\emph{e.g.}, DOI, PubMed ID, ISBN, URL).
-The resulting manuscript can be rendered with document templates and citation style language formatting to meet journal formatting requirements.
-Every change made to the manuscript triggers its rendering, so that updates are readily displayed and made publicly available.
-Additional GitHub Actions can be integrated with Manubot, such as ones creating figures or generating tables (\emph{e.g.}, \url{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/main/.github/workflows}).
-
-\hypertarget{peer-review}{%
-\subsubsection{Peer review}\label{peer-review}}
-
-Peer review is the standard process for assessing whether research done in ecology and evolution should be published in a scientific journal.
-GitHub provides an open and transparent platform that can be used for either directly providing feedback on research products or addressing changes recommended by reviewers.
-GitHub Issues can be used to organize and discuss reviewer suggestions and to assign them to co-authors (\emph{e.g.}, \url{https://github.com/SORTEE-Github-Hackathon/manuscript/issues?q=label\%3A\%22Reviewer+Comment\%22}).
-When reviewer comments are posted as separate issues, authors can comment on the issues to discuss possible changes and assign co-authors who will address the issue.
-Co-authors can then integrate their edits and responses to reviewers using pull requests, which can be directly linked to the issues they address.
-
-GitHub can also assist reviewers during the peer review process.
-If the code associated with a manuscript is made available at the time of submission (\emph{e.g.}, as a link to a GitHub repository within the Data Availability Statement), peer reviewers may be able to offer more comprehensive suggestions on the code and written materials, potentially recognizing errors before publication.
-Certain journals or software development communities require submitted work or research code to be hosted on GitHub and their review processes make use of GitHub Issues (\emph{e.g.}, rOpenSci (\url{https://ropensci.org/software-review/}), Journal of Open Source Software (\url{https://joss.readthedocs.io/en/latest/submitting.html})).
-
-\hypertarget{open-science-discussion}{%
-\subsubsection{Open science discussion}\label{open-science-discussion}}
-
-Scientific publications often omit part of their intellectual and computational workflows, including the treatment of raw data and analytical steps (\emph{e.g.}, model assumption testing).
-Publishing data and reproducible workflows along with manuscripts can provide readers with all details about analytical steps and enable reproducing research experiments and results (\protect\hyperlink{ref-NOgBWVAr}{Culina et al., 2020}).
-In addition to storing data and code, GitHub repositories can provide a time-stamped (version controlled) preregistration of research plans and hypotheses.
-
-Conventional research practices typically separate tasks among collaborators (\emph{i.e.}, data entry, analysis, writing).
-It is common that coauthors discuss, but do not actively verify, edit, or execute research tasks that are not their main responsibility.
-GitHub can serve as a tool for open and tractable research development.
-Collaborators can directly interact with code and data, inspect for errors, and potentially identify scientific misconduct prior to manuscript submission (\emph{e.g.}, \url{https://ecologyforthemasses.com/2020/02/04/pruittdata-and-the-ethics-of-data-in-science}).
-Collaborators and readers are better positioned to discover erroneous or questionable findings if they have complete and transparent access to projects.
-
-This transparency can be extended beyond co-authors to the entire scientific community and to the public.
-Supplying code for novel or currently used methods reduces barriers to knowledge, improving the ability of others to build on existing work.
-This practice results in greater proliferation and accessibility for a broader audience.
-Projects can make use of GitHub Discussions (\url{https://docs.github.com/en/discussions}) to communicate among repository members (collaborators) and to engage with other scientists and the general public.
-Moreover, researchers can also use the GitHub Community (\url{https://github.community/}) forum to share expertise or request help from others on their analyses and ideas (\protect\hyperlink{tbl:roles}{Table 2}).
-
-The desire or need for privacy during the developmental stages of a manuscript or of a larger research project is common in EEB, and this is often perceived as a major barrier to doing science openly.
-Because GitHub repositories can be made private or public at any time, there is no need to choose privacy over open science, or vice-versa.
-Repositories can be kept private until their contents are ready to be shared publicly, as might occur when a research article is published or when an embargo is lifted.
-
-\hypertarget{automation}{%
-\subsubsection{Automation}\label{automation}}
-
-Automation has the strong potential to expand the scale and pace of research in ecology and evolution (\protect\hyperlink{ref-cfgXxgt1}{Keitt \& Abelson, 2021}).
-Automation frameworks can streamline many stages of the scientific process, including data collection and data validation (\emph{e.g.}, \protect\hyperlink{ref-bhDgD6lF}{Micheletti et al., 2021}; \protect\hyperlink{ref-lXvpQxeN}{Yenni et al., 2018}), data analysis (\emph{e.g.}, \protect\hyperlink{ref-Qh7xTLwz}{Beaulieu-Jones \& Greene, 2017}), unit testing of research code (\emph{e.g.}, \protect\hyperlink{ref-lYazDTau}{Sarma et al., 2016}), archiving and deployment of data, code and reports (\emph{e.g.}, this manuscript, \protect\hyperlink{ref-SirQKFIz}{White et al., 2018}), and the interpretation, integration and usage of data and software across different sources (see \protect\hyperlink{ref-1FJhfqfiX}{Pasquier et al., 2017}).
-In this context, small modifications to code and data can be frequently committed and automatically tested, as in continuous integration and continuous deployment practices (\protect\hyperlink{ref-1Ep9EJL6y}{Meyer, 2014}).
-This allows for early detection and correction of errors, potentially improving confidence in scientific development by minimizing software errors (see \protect\hyperlink{ref-ufw0ZdnI}{Soergel, 2015}).
-In addition to increasing scientific rigour and confidence in ecological software (\protect\hyperlink{ref-12103x16N}{Scheller et al., 2010}), automation can help advance more rapidly sharing ecological data and making sure the data are high quality (\protect\hyperlink{ref-rTbinQMj}{Dietze et al., 2018}).
-Integrating automation workflows has been highly encouraged in areas of EEB, including predictive ecology (\protect\hyperlink{ref-mmCOSRfr}{McIntire et al., 2022}), long-term ecological studies (\protect\hyperlink{ref-RxK4CmfR}{Ernest et al., 2018}; \protect\hyperlink{ref-1CJo8lo2v}{Yenni et al., 2019}), and management of species at risk information (\protect\hyperlink{ref-kZzfmBNu}{Naujokaitis-Lewis et al., 2022}).
-
-Automation can be integrated into GitHub repositories through the GitHub Actions feature (\protect\hyperlink{ref-NUXbp429}{\emph{Features • GitHub Actions}, n.d.}), or through alternative automation systems (\emph{e.g.}, Circle CI, \protect\hyperlink{ref-T03Api6e}{\emph{Continuous Integration and Delivery}, n.d.}); Travis CI, \emph{Home -- Travis-CI} (\protect\hyperlink{ref-YeFSbfFV}{2022}){]}.
+However, free hosting, widely available template customization, and versioning are strong advantages over alternatives.{]}.
 Users can set up workflows associated with their repositories that are triggered by events (\emph{e.g.}, push, pull request or at specified times) for remote servers to perform user-specified steps and actions.
@@
 This openness may add additional pressure to students and scientists learning to use the platform.
-Moreover, additional tools may be required to fully integrate project files and GitHub repositories (\emph{e.g.}, (\protect\hyperlink{ref-lx49NGto}{\emph{Connect GitHub to a Project - OSF Support}, n.d.})).
+Moreover, additional tools may be required to fully integrate project files and GitHub repositories (\emph{e.g.}, \protect\hyperlink{ref-lx49NGto}{\emph{Connect GitHub to a Project - OSF Support}, n.d.}).
 Other scientists may simply lack the time or incentives to document and version control their code if the code is unlikely to be reused beyond their analysis.
-However we (and others, \emph{e.g.,} (\protect\hyperlink{ref-VDJput1V}{Gomes et al., 2022a})) argue that the endeavour of open science and collaboration requires code owners to document and version control code despite uncertainty around future use.
+However we (and others, \emph{e.g.,} \protect\hyperlink{ref-VDJput1V}{Gomes et al., 2022a}) argue that the endeavour of open science and collaboration requires code owners to document and version control code despite uncertainty around future use.
 
@@
 GitHub Docs.
-Retrieved March 2, 2023, from \url{https://ghdocs-prod.azurewebsites.net/en/repositories/managing-your-repositorys-settings-and-features/customizing-your-repository/about-code-owners}
+Retrieved March 4, 2023, from \url{https://ghdocs-prod.azurewebsites.net/en/repositories/managing-your-repositorys-settings-and-features/customizing-your-repository/about-code-owners}
 
@@
 GitHub Docs.
-Retrieved March 2, 2023, from \url{https://ghdocs-prod.azurewebsites.net/en/repositories/working-with-files/managing-large-files/about-large-files-on-github}
+Retrieved March 4, 2023, from \url{https://ghdocs-prod.azurewebsites.net/en/repositories/working-with-files/managing-large-files/about-large-files-on-github}
 
@@
 GitHub Docs.
-Retrieved March 2, 2023, from \url{https://ghdocs-prod.azurewebsites.net/en/issues/planning-and-tracking-with-projects/learning-about-projects/about-projects}
-
-\leavevmode\vadjust pre{\hypertarget{ref-TOsASkn5}{}}%
-\emph{Adding a license to a repository}.
-(n.d.).
-GitHub Docs.
-Retrieved March 2, 2023, from \url{https://ghdocs-prod.azurewebsites.net/en/communities/setting-up-your-project-for-healthy-contributions/adding-a-license-to-a-repository}
+Retrieved March 4, 2023, from \url{https://ghdocs-prod.azurewebsites.net/en/issues/planning-and-tracking-with-projects/learning-about-projects/about-projects}
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-1HZdsK5Kn}{}}%
-Baker, M. (2016). 1,500 scientists lift the lid on reproducibility. \emph{Nature}, \emph{533}(7604), 452--454. \url{https://doi.org/10.1038/533452a}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Qh7xTLwz}{}}%
-Beaulieu-Jones, B.
-K., \& Greene, C.
-S.
-(2017).
-Reproducibility of computational workflows is automated using continuous analysis.
-\emph{Nature Biotechnology}, \emph{35}(4), 342--346.
-\url{https://doi.org/10.1038/nbt.3780}
-
 \leavevmode\vadjust pre{\hypertarget{ref-PlcxShQU}{}}%
@@
 \leavevmode\vadjust pre{\hypertarget{ref-6CMMeSeD}{}}%
-Bryan, J., \& TAs, T. S. 545. (n.d.). \emph{STAT 545}. Retrieved March 2, 2023, from \url{https://stat545.com/}
+Bryan, J., \& TAs, T. S. 545. (n.d.). \emph{STAT 545}. Retrieved March 4, 2023, from \url{https://stat545.com/}
 
 \leavevmode\vadjust pre{\hypertarget{ref-lx49NGto}{}}%
-\emph{Connect GitHub to a Project - OSF Support}. (n.d.). Retrieved March 2, 2023, from \url{https://help.osf.io/article/211-connect-github-to-a-project}
-
-\leavevmode\vadjust pre{\hypertarget{ref-T03Api6e}{}}%
-\emph{Continuous Integration and Delivery}. (n.d.). CircleCI. Retrieved March 2, 2023, from \url{https://circleci.com/}
-
-\leavevmode\vadjust pre{\hypertarget{ref-K7nbP1Ty}{}}%
-Crystal-Ornelas, R., Edwards, B.
-P.
-M., Hébert, K., Hudgins, E.
-J., Reyes, L.
-L.
-S., Scott, E.
-R., Grainger, M.
-J., Foroughirad, V., Binley, A.
-D., Brookson, C.
-B., Gaynor, K.
-M., Sabet, S.
-S., Güncan, A., Hillemann, F., Weierbach, H., Gomes, D.
-G.
-E., \& Braga, P.
-H.
-P.
-(2023).
-\emph{Not just for programmers: How GitHub can accelerate collaborative and reproducible research in ecology and evolution}.
-Manubot.
-\url{https://SORTEE-Github-Hackathon.github.io/manuscript/}
+\emph{Connect GitHub to a Project - OSF Support}. (n.d.). Retrieved March 4, 2023, from \url{https://help.osf.io/article/211-connect-github-to-a-project}
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-NOgBWVAr}{}}%
-Culina, A., van den Berg, I., Evans, S., \& Sánchez-Tójar, A.
-(2020).
-Low availability of code in ecology: A~call for urgent action.
-\emph{PLOS Biology}, \emph{18}(7), e3000763.
-\url{https://doi.org/10.1371/journal.pbio.3000763}
-
-\leavevmode\vadjust pre{\hypertarget{ref-rTbinQMj}{}}%
-Dietze, M.
-C., Fox, A., Beck-Johnson, L.
-M., Betancourt, J.
-L., Hooten, M.
-B., Jarnevich, C.
-S., Keitt, T.
-H., Kenney, M.
-A., Laney, C.
-M., Larsen, L.
-G., Loescher, H.
-W., Lunch, C.
-K., Pijanowski, B.
-C., Randerson, J.
-T., Read, E.
-K., Tredennick, A.
-T., Vargas, R., Weathers, K.
-C., \& White, E.
-P.
-(2018).
-Iterative near-term ecological forecasting: Needs, opportunities, and challenges.
-\emph{Proceedings of the National Academy of Sciences}, \emph{115}(7), 1424--1432.
-\url{https://doi.org/10.1073/pnas.1710231115}
-
-\leavevmode\vadjust pre{\hypertarget{ref-bZNn2hbh}{}}%
-EllenJCoombs. (2020). \emph{EllenJCoombs/Asymmetry-evolution-cetaceans-for-publication-v.1.0.0} (Version v.1.0.0) {[}Computer software{]}. Zenodo. \url{https://doi.org/10.5281/zenodo.3893943}
-
-\leavevmode\vadjust pre{\hypertarget{ref-RxK4CmfR}{}}%
-Ernest, S.
-K.
-M., Yenni, G.
-M., Allington, G., Bledsoe, E.
-K., Christensen, E.
-M., Diaz, R.
-M., Geluso, K., Goheen, J.
-R., Guo, Q., Heske, E., Kelt, D., Meiners, J.
-M., Munger, J., Restrepo, C., Samson, D.
-A., Schutzenhofer, M.
-R., Skupski, M., Supp, S.
-R., Thibault, K., \ldots{} Valone, T.
-J.
-(2018).
-\emph{The Portal Project: a long-term study of a Chihuahuan desert ecosystem}.
-Cold Spring Harbor Laboratory.
-\url{https://doi.org/10.1101/332783}
-
-\leavevmode\vadjust pre{\hypertarget{ref-NUXbp429}{}}%
-\emph{Features • GitHub Actions}. (n.d.). GitHub. Retrieved March 2, 2023, from \url{https://github.com/features/actions}
-
 \leavevmode\vadjust pre{\hypertarget{ref-D4C4k4ak}{}}%
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-SLq38RVv}{}}%
-Figueiredo, A. S. (2017). Data Sharing: Convert Challenges into Opportunities. \emph{Frontiers in Public Health}, \emph{5}. \url{https://doi.org/10.3389/fpubh.2017.00327}
-
 \leavevmode\vadjust pre{\hypertarget{ref-1CM2EcdVk}{}}%
-\emph{Git - A Short History of Git}. (n.d.). Retrieved March 2, 2023, from \url{https://git-scm.com/book/en/v2/Getting-Started-A-Short-History-of-Git}
+\emph{Git - A Short History of Git}. (n.d.). Retrieved March 4, 2023, from \url{https://git-scm.com/book/en/v2/Getting-Started-A-Short-History-of-Git}
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-ZvrOcg9w}{}}%
-Hester, J. B., the STAT 545 TAs, Jim. (n.d.). \emph{Let's Git started \textbar{} Happy Git and GitHub for the useR}. Retrieved March 2, 2023, from \url{https://happygitwithr.com/}
-
-\leavevmode\vadjust pre{\hypertarget{ref-YuJbg3zO}{}}%
-Himmelstein, D.
-S., Rubinetti, V., Slochower, D.
-R., Hu, D., Malladi, V.
-S., Greene, C.
-S., \& Gitter, A.
-(2019).
-Open collaborative writing with Manubot.
-\emph{PLOS Computational Biology}, \emph{15}(6), e1007128.
-\url{https://doi.org/10.1371/journal.pcbi.1007128}
-
-\leavevmode\vadjust pre{\hypertarget{ref-YeFSbfFV}{}}%
-\emph{Home -- Travis-CI}. (2022, October 6). \url{https://www.travis-ci.com/}
-
-\leavevmode\vadjust pre{\hypertarget{ref-GQj3c17f}{}}%
-Hudgins, E. (2022). \emph{emmajhudgins/UStreedamage: publication release} (accepted) {[}Computer software{]}. Zenodo. \url{https://doi.org/10.5281/zenodo.6097109}
+Hester, J. B., the STAT 545 TAs, Jim. (n.d.). \emph{Let's Git started \textbar{} Happy Git and GitHub for the useR}. Retrieved March 4, 2023, from \url{https://happygitwithr.com/}
 
 \leavevmode\vadjust pre{\hypertarget{ref-3UAritXO}{}}%
-\emph{Issues · fmsabatini/sPlotOpen\_Manuscript}. (n.d.). GitHub. Retrieved March 2, 2023, from \url{https://github.com/fmsabatini/sPlotOpen_Manuscript}
+\emph{Issues · fmsabatini/sPlotOpen\_Manuscript}. (n.d.). GitHub. Retrieved March 4, 2023, from \url{https://github.com/fmsabatini/sPlotOpen_Manuscript}
 
@@
 \url{https://doi.org/10.1109/icse.2015.74}
-
-\leavevmode\vadjust pre{\hypertarget{ref-cfgXxgt1}{}}%
-Keitt, T. H., \& Abelson, E. S. (2021). Ecology in the age of automation. \emph{Science}, \emph{373}(6557), 858--859. \url{https://doi.org/10.1126/science.abi4692}
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-ZI1OqZNr}{}}%
-Lrharper1.
-(2018).
-\emph{Hulluni-Bioinformatics/Harper\_Et\_Al\_2018: Github Repository Deposited With Harper Et Al.
-(2018) In Ecology And Evolution.} Zenodo.
-\url{https://doi.org/10.5281/zenodo.1188710}
-
 \leavevmode\vadjust pre{\hypertarget{ref-pjy75gHr}{}}%
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Re6Eg2va}{}}%
-\emph{Manubot - Manuscripts, open and automated}. (n.d.). Retrieved March 2, 2023, from \url{https://manubot.org}
-
 \leavevmode\vadjust pre{\hypertarget{ref-MwwMapRG}{}}%
@@
 \url{https://doi.org/10.1080/00031305.2017.1375986}
-
-\leavevmode\vadjust pre{\hypertarget{ref-mmCOSRfr}{}}%
-McIntire, E.
-J.
-B., Chubaty, A.
-M., Cumming, S.
-G., Andison, D., Barros, C., Boisvenue, C., Haché, S., Luo, Y., Micheletti, T., \& Stewart, F.
-E.
-C.
-(2022).
-PERFICT: A Re‐imagined foundation for predictive ecology.
-\emph{Ecology Letters}, \emph{25}(6), 1345--1351.
-\url{https://doi.org/10.1111/ele.13994}
-
-\leavevmode\vadjust pre{\hypertarget{ref-1Ep9EJL6y}{}}%
-Meyer, M. (2014). Continuous Integration and Its Tools. \emph{IEEE Software}, \emph{31}(3), 14--16. \url{https://doi.org/10.1109/ms.2014.58}
-
-\leavevmode\vadjust pre{\hypertarget{ref-bhDgD6lF}{}}%
-Micheletti, T., Stewart, F.
-E.
-C., Cumming, S.
-G., Haché, S., Stralberg, D., Tremblay, J.
-A., Barros, C., Eddy, I.
-M.
-S., Chubaty, A.
-M., Leblond, M., Pankratz, R.
-F., Mahon, C.
-L., Van Wilgenburg, S.
-L., Bayne, E.
-M., Schmiegelow, F., \& McIntire, E.
-J.
-B.
-(2021).
-Assessing Pathways of Climate Change Effects in SpaDES: An Application to Boreal Landbirds of Northwest Territories Canada.
-\emph{Frontiers in Ecology and Evolution}, \emph{9}.
-\url{https://doi.org/10.3389/fevo.2021.679673}
-
-\leavevmode\vadjust pre{\hypertarget{ref-uBJwnPbq}{}}%
-Mislan, K.
-A.
-S., Heer, J.
-M., \& White, E.
-P.
-(2016).
-Elevating The Status of Code in Ecology.
-\emph{Trends in Ecology \&Amp; Evolution}, \emph{31}(1), 4--7.
-\url{https://doi.org/10.1016/j.tree.2015.11.006}
-
-\leavevmode\vadjust pre{\hypertarget{ref-kZzfmBNu}{}}%
-Naujokaitis-Lewis, I., Endicott, S., \& Guezen, J.
-M.
-(2022).
-CAN-SAR: A database of Canadian species at risk information.
-\emph{Scientific Data}, \emph{9}(1).
-\url{https://doi.org/10.1038/s41597-022-01381-8}
-
-\leavevmode\vadjust pre{\hypertarget{ref-1Hcf13Q0k}{}}%
-Nugroho, R.
-P., Zuiderwijk, A., Janssen, M., \& de Jong, M.
-(2015).
-A comparison of national open data policies: lessons learned.
-\emph{Transforming Government: People, Process and Policy}, \emph{9}(3), 286--308.
-\url{https://doi.org/10.1108/tg-03-2014-0008}
-
-\leavevmode\vadjust pre{\hypertarget{ref-4LaijDIZ}{}}%
-On data availability, reproducibility and reuse. (2017). \emph{Nature Cell Biology}, \emph{19}(4), 259--259. \url{https://doi.org/10.1038/ncb3506}
-
-\leavevmode\vadjust pre{\hypertarget{ref-1FJhfqfiX}{}}%
-Pasquier, T., Lau, M.
-K., Trisovic, A., Boose, E.
-R., Couturier, B., Crosas, M., Ellison, A.
-M., Gibson, V., Jones, C.
-R., \& Seltzer, M.
-(2017).
-If these data could talk.
-\emph{Scientific Data}, \emph{4}(1).
-\url{https://doi.org/10.1038/sdata.2017.114}
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-1CcAUn3Lu}{}}%
-Piwowar, H.
-A., Day, R.
-S., \& Fridsma, D.
-B.
-(2007).
-Sharing Detailed Research Data Is Associated with Increased Citation Rate.
-\emph{PLoS ONE}, \emph{2}(3), e308.
-\url{https://doi.org/10.1371/journal.pone.0000308}
-
-\leavevmode\vadjust pre{\hypertarget{ref-666HppfO}{}}%
-Pronk, T. E., Wiersma, P. H., van Weerden, A., \& Schieving, F. (2015). A game theoretic analysis of research data sharing. \emph{PeerJ}, \emph{3}, e1242. \url{https://doi.org/10.7717/peerj.1242}
-
 \leavevmode\vadjust pre{\hypertarget{ref-4ny1onB0}{}}%
 Ram, K. (2013). Git can facilitate greater reproducibility and increased transparency in science. \emph{Source Code for Biology and Medicine}, \emph{8}(1). \url{https://doi.org/10.1186/1751-0473-8-7}
-
-\leavevmode\vadjust pre{\hypertarget{ref-lYazDTau}{}}%
-Sarma, G.
-P., Jacobs, T.
-W., Watts, M.
-D., Ghayoomie, S.
-V., Larson, S.
-D., \& Gerkin, R.
-C.
-(2016).
-Unit testing, model validation, and biological simulation.
-\emph{F1000Research}, \emph{5}, 1946.
-\url{https://doi.org/10.12688/f1000research.9315.1}
-
-\leavevmode\vadjust pre{\hypertarget{ref-12103x16N}{}}%
-Scheller, R.
-M., Sturtevant, B.
-R., Gustafson, E.
-J., Ward, B.
-C., \& Mladenoff, D.
-J.
-(2010).
-Increasing the reliability of ecological models using modern software engineering techniques.
-\emph{Frontiers in Ecology and the Environment}, \emph{8}(5), 253--260.
-\url{https://doi.org/10.1890/080141}
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-ufw0ZdnI}{}}%
-Soergel, D. A. W. (2015). Rampant software errors may undermine scientific results. \emph{F1000Research}, \emph{3}, 303. \url{https://doi.org/10.12688/f1000research.5930.2}
-
-\leavevmode\vadjust pre{\hypertarget{ref-hm9PaCLD}{}}%
-Song, X., Goldstein, S.
-C., \& Sakr, M.
-(2020, June 15).
-Using Peer Code Review as an Educational Tool.
-\emph{Proceedings of the 2020 ACM Conference on Innovation and Technology in Computer Science Education}.
-ITiCSE '20: Innovation and Technology in Computer Science Education.
-\url{https://doi.org/10.1145/3341525.3387370}
-
 \leavevmode\vadjust pre{\hypertarget{ref-7q3wZN6d}{}}%
 Spinellis, D. (2012). Git. \emph{IEEE Software}, \emph{29}(3), 100--101. \url{https://doi.org/10.1109/ms.2012.61}
-
-\leavevmode\vadjust pre{\hypertarget{ref-1CzUZwyU2}{}}%
-Tenopir, C., Dalton, E.
-D., Allard, S., Frame, M., Pjesivac, I., Birch, B., Pollock, D., \& Dorsett, K.
-(2015).
-Changes in Data Sharing and Data Reuse Practices and Perceptions among Scientists Worldwide.
-\emph{PLOS ONE}, \emph{10}(8), e0134826.
-\url{https://doi.org/10.1371/journal.pone.0134826}
-
-\leavevmode\vadjust pre{\hypertarget{ref-PLmDFZrm}{}}%
-Tenopir, C., Rice, N.
-M., Allard, S., Baird, L., Borycz, J., Christian, L., Grant, B., Olendorf, R., \& Sandusky, R.
-J.
-(2020).
-Data sharing, management, use, and reuse: Practices and perceptions of scientists worldwide.
-\emph{PLOS ONE}, \emph{15}(3), e0229003.
-\url{https://doi.org/10.1371/journal.pone.0229003}
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-oGbKxHzj}{}}%
-\emph{Using Git and GitHub}. (n.d.). Retrieved March 2, 2023, from \url{https://www.overleaf.com/learn/how-to/Using_Git_and_GitHub}
-
 \leavevmode\vadjust pre{\hypertarget{ref-19kmNxiHc}{}}%
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-SirQKFIz}{}}%
-White, E.
-P., Yenni, G.
-M., Taylor, S.
-D., Christensen, E.
-M., Bledsoe, E.
-K., Simonis, J.
-L., \& Ernest, S.
-K.
-M.
-(2018).
-Developing an automated iterative near‐term forecasting system for an ecological study.
-\emph{Methods in Ecology and Evolution}, \emph{10}(3), 332--344.
-\url{https://doi.org/10.1111/2041-210x.13104}
-
-\leavevmode\vadjust pre{\hypertarget{ref-1Ch6LSHef}{}}%
-Wicherts, J.
-M., Bakker, M., \& Molenaar, D.
-(2011).
-Willingness to Share Research Data Is Related to the Strength of the Evidence and the Quality of Reporting of Statistical Results.
-\emph{PLoS ONE}, \emph{6}(11), e26828.
-\url{https://doi.org/10.1371/journal.pone.0026828}
-
-\leavevmode\vadjust pre{\hypertarget{ref-1CJo8lo2v}{}}%
-Yenni, G.
-M., Christensen, E.
-M., Bledsoe, E.
-K., Supp, S.
-R., Diaz, R.
-M., White, E.
-P., \& Ernest, S.
-K.
-M.
-(2019).
-Developing a modern data workflow for regularly updated data.
-\emph{PLOS Biology}, \emph{17}(1), e3000125.
-\url{https://doi.org/10.1371/journal.pbio.3000125}
-
-\leavevmode\vadjust pre{\hypertarget{ref-lXvpQxeN}{}}%
-Yenni, G.
-M., Christensen, E.
-M., Bledsoe, E.
-K., Supp, S.
-R., Diaz, R.
-M., White, E.
-P., \& Ernest, S.
-K.
-M.
-(2018).
-\emph{Developing a modern data workflow for evolving data}.
-Cold Spring Harbor Laboratory.
-\url{https://doi.org/10.1101/344804}
-
 \end{CSLReferences}

### 2023-03-04 manuscript.tex
Merge pull request #316 from SORTEE-Github-Hackathon/eric-edits [ci skip]
This build is based on
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/4a0cc6accf8643e836371ea6dcf75962146c372d.

This commit was created by the following CI build and job:
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/4a0cc6accf8643e836371ea6dcf75962146c372d/checks
https://github.com/SORTEE-Github-Hackathon/manuscript/actions/runs/4332730335

@@
 This manuscript
-(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/290c4cd8316ffaa08ceafd6ac4cfcdfe09774653/}{permalink})
+(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/4a0cc6accf8643e836371ea6dcf75962146c372d/}{permalink})
 was automatically generated
-from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/290c4cd8316ffaa08ceafd6ac4cfcdfe09774653}{SORTEE-Github-Hackathon/manuscript@290c4cd}
+from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/4a0cc6accf8643e836371ea6dcf75962146c372d}{SORTEE-Github-Hackathon/manuscript@4a0cc6a}
 on March 4, 2023.
@@
   \href{https://github.com/Aariq}{Aariq}
-  Department of Wildlife Ecology and Conservation, University of Florida, Gainesville, FL, USA
+  Communications \& Cyber Techologies, University of Arizona, Tucson, USA
 \item
@@
 Perkel, 2016}){]}.
-Within the spectrum of cloud-based services for collaboration, GitHub is uniquely positioned (\protect\hyperlink{tbl:compare}{Table 1}) to benefit scientists because it is designed to store, track changes, and enable collaboration on computer code -- fundamental components of modern research.
+Within the spectrum of cloud-based services for collaboration, GitHub is uniquely positioned (\protect\hyperlink{tbl:compare}{Table 1}) to benefit scientists because it is designed to store, track changes, and enable collaboration on computer code---fundamental components of modern research.
 Albeit, most researchers lack exposure to adequate programming and coding practices and thus dedicate valuable time and effort to self-teaching research-facilitating tools.
@@
 This provides a safe and less cluttered alternative to frequently making full copies of documents at different points in their evolution (\emph{e.g.} \texttt{analysis.R}, \texttt{analysis\_v2.R}, \texttt{analysis\_FINAL.R}).
-While focusing on technical details about the use of Git and GitHub is beyond the scope of this study, we recommend users explore available resources to become more familiar with version control features (but see Perez-Riverol et al.
+While focusing on technical details about the use of Git and GitHub is beyond the scope of this study, we recommend users explore available resources to become more familiar with version control features (see Perez-Riverol et al.
 (\protect\hyperlink{ref-kEX5dgzK}{2016}), Blischak et al.
@@
 Widespread adoption of GitHub for collaborating on research tasks can ultimately enable EEB researchers to spend less time on creating novel processes for collaboration and more time on their research (\protect\hyperlink{ref-ydrk01SR}{Briney et al., 2020}).
-More importantly, expanding the availability of data and code management standards---of which GitHub is one increasingly important component---makes research more reproducible and collaborative (\protect\hyperlink{ref-13QX8XU3J}{Alston \& Rick, 2021}; \protect\hyperlink{ref-pq2Tv1BC}{Gomes et al., 2022b}).
+More importantly, expanding the availability of data and code management standards---of which GitHub is one increasingly important component---makes research more reproducible and collaborative (\protect\hyperlink{ref-13QX8XU3J}{Alston \& Rick, 2021}; \protect\hyperlink{ref-VDJput1V}{Gomes et al., 2022}).
 
@@
 
-\hypertarget{storing-and-sharing-research-compendia}{%
-\subsubsection{Storing and sharing research compendia}\label{storing-and-sharing-research-compendia}}
+\hypertarget{storing-sharing}{%
+\subsubsection{Storing and sharing research compendia}\label{storing-sharing}}
 
@@
 Many researchers begin using GitHub to backup their research compendium (\protect\hyperlink{ref-MwwMapRG}{Marwick et al., 2018}) into a centralized, readily-available remote server (see \protect\hyperlink{definitions}{Box 1}).
-This practice has the advantages of facilitating collaboration, integrating data and code archiving, allowing file versions to be accessed and restored, and further contributing to open science practices (Borghi \& Van Gulick (\protect\hyperlink{ref-gLby7jt1}{2022})).
-Every change made to files in version-controlled repositories accompany authored descriptions of modifications (\protect\hyperlink{definitions}{Box 1}).
+This practice has the advantages of facilitating collaboration, integrating data and code archiving, allowing file versions to be accessed and restored, and further contributing to open science practices (\protect\hyperlink{ref-gLby7jt1}{Borghi \& Van Gulick, 2022}).
+Changes made to files in version-controlled repositories are accompanied by authored descriptions of modifications (\protect\hyperlink{definitions}{Box 1}).
 Later, the entire history of commits and their commit messages are viewable and can be audited similarly to physical laboratory notebooks (\protect\hyperlink{ref-4ny1onB0}{Ram, 2013}).
@@
 
-A third barrier may come from general reluctance to share data and code publicly, or technical and logistical issues (\protect\hyperlink{ref-pq2Tv1BC}{Gomes et al., 2022b}).
+A third barrier may come from general reluctance to share data and code publicly, or technical and logistical issues (\protect\hyperlink{ref-VDJput1V}{Gomes et al., 2022}).
 GitHub is, by default, a public and open platform.
@@
 Other scientists may simply lack the time or incentives to document and version control their code if the code is unlikely to be reused beyond their analysis.
-However we (and others, \emph{e.g.,} \protect\hyperlink{ref-VDJput1V}{Gomes et al., 2022a}) argue that the endeavour of open science and collaboration requires code owners to document and version control code despite uncertainty around future use.
+However we (and others, \emph{e.g.,} \protect\hyperlink{ref-VDJput1V}{Gomes et al., 2022}) argue that the endeavour of open science and collaboration requires code owners to document and version control code despite uncertainty around future use.
 
@@
 M.
-(2022a).
+(2022).
 Why don't we share data and code?
@@
 \url{https://doi.org/10.1098/rspb.2022.1113}
-
-\leavevmode\vadjust pre{\hypertarget{ref-pq2Tv1BC}{}}%
-Gomes, D.
-G.
-E., Pottier, P., Crystal-Ornelas, R., Hudgins, E.
-J., Foroughirad, V., Sánchez-Reyes, L.
-L., Turba, R., Martinez, P.
-A., Moreau, D., Bertram, M., Smout, C., \& Gaynor, K.
-(2022b).
-\emph{Why don't we share data and code?
-Perceived barriers and benefits to public archiving practices}.
-Center for Open Science.
-\url{https://doi.org/10.31222/osf.io/gaj43}
 

### 2023-03-04 manuscript.tex
Update README.md [ci skip]
This build is based on
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/003c9db3c507b7e3b0f010f1c8f579bac7ba666d.

This commit was created by the following CI build and job:
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/003c9db3c507b7e3b0f010f1c8f579bac7ba666d/checks
https://github.com/SORTEE-Github-Hackathon/manuscript/actions/runs/4332971966

@@
 This manuscript
-(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/4a0cc6accf8643e836371ea6dcf75962146c372d/}{permalink})
+(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/003c9db3c507b7e3b0f010f1c8f579bac7ba666d/}{permalink})
 was automatically generated
-from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/4a0cc6accf8643e836371ea6dcf75962146c372d}{SORTEE-Github-Hackathon/manuscript@4a0cc6a}
+from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/003c9db3c507b7e3b0f010f1c8f579bac7ba666d}{SORTEE-Github-Hackathon/manuscript@003c9db}
 on March 4, 2023.

### 2023-03-04 manuscript.tex
Adding CSS for section numbering. [ci skip]
This build is based on
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/540c54a0e1a9c1b107387aa297db8144b6a79d5e.

This commit was created by the following CI build and job:
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/540c54a0e1a9c1b107387aa297db8144b6a79d5e/checks
https://github.com/SORTEE-Github-Hackathon/manuscript/actions/runs/4332996437

@@
 This manuscript
-(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/003c9db3c507b7e3b0f010f1c8f579bac7ba666d/}{permalink})
+(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/540c54a0e1a9c1b107387aa297db8144b6a79d5e/}{permalink})
 was automatically generated
-from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/003c9db3c507b7e3b0f010f1c8f579bac7ba666d}{SORTEE-Github-Hackathon/manuscript@003c9db}
+from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/540c54a0e1a9c1b107387aa297db8144b6a79d5e}{SORTEE-Github-Hackathon/manuscript@540c54a}
 on March 4, 2023.

### 2023-03-04 manuscript.tex
Update environment.yml [ci skip]
This build is based on
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/c300807d221901c7441dc86e15a3e2c6c4d2f7c4.

This commit was created by the following CI build and job:
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/c300807d221901c7441dc86e15a3e2c6c4d2f7c4/checks
https://github.com/SORTEE-Github-Hackathon/manuscript/actions/runs/4333031977

@@
 This manuscript
-(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/540c54a0e1a9c1b107387aa297db8144b6a79d5e/}{permalink})
+(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/c300807d221901c7441dc86e15a3e2c6c4d2f7c4/}{permalink})
 was automatically generated
-from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/540c54a0e1a9c1b107387aa297db8144b6a79d5e}{SORTEE-Github-Hackathon/manuscript@540c54a}
-on March 4, 2023.
+from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/c300807d221901c7441dc86e15a3e2c6c4d2f7c4}{SORTEE-Github-Hackathon/manuscript@c300807}
+on 2023-03-04.
 
@@
   >{\raggedright\arraybackslash}p{(\columnwidth - 0\tabcolsep) * \real{1.0000}}@{}}
-\toprule
+\toprule()
 \begin{minipage}[b]{\linewidth}\raggedright
@@
 \end{minipage} \\
-\midrule
+\midrule()
 \endhead
@@
 \textbf{community}: A forum where GitHub users can ask for advice, offer solutions to questions, and share ideas (\url{https://github.community/}). \\
-\bottomrule
+\bottomrule()
 \end{longtable}
@@
 Creating and hosting websites on GitHub Pages is more complex than out-of-the-box platforms (\emph{e.g.}, Wix, Weebly, Google Sites).
-However, free hosting, widely available template customization, and versioning are strong advantages over alternatives.{]}.
+However, free hosting, widely available template customization, and versioning are strong advantages over alternatives.
+
+\hypertarget{archiving-citable-code}{%
+\subsubsection{Archiving citable code and data}\label{archiving-citable-code}}
+
+Government, funding agencies, and publishers exercise rigorous open access data policies and mandates (\protect\hyperlink{ref-1Hcf13Q0k}{Nugroho et al., 2015}; \protect\hyperlink{ref-PLmDFZrm}{Tenopir et al., 2020}).
+However, code and data sharing may be met by individual reluctance, temporary embargoes, or partially prevented by privacy and confidentiality reasons (\protect\hyperlink{ref-SLq38RVv}{Figueiredo, 2017}; \protect\hyperlink{ref-1CzUZwyU2}{Tenopir et al., 2015}; \protect\hyperlink{ref-1Ch6LSHef}{Wicherts et al., 2011}).
+Still, data deposition and ensuring its availability can amplify the outreach of published studies (\protect\hyperlink{ref-666HppfO}{Pronk et al., 2015}), increase citation rates (\protect\hyperlink{ref-1CcAUn3Lu}{Piwowar et al., 2007}), and among many other reasons, enable the reproducibility and robustness of scientific advances (\protect\hyperlink{ref-1HZdsK5Kn}{Baker, 2016}; \protect\hyperlink{ref-uBJwnPbq}{Mislan et al., 2016}; \protect\hyperlink{ref-4LaijDIZ}{{``On Data Availability, Reproducibility and Reuse,''} 2017}).
+While public repositories on GitHub make it easy to store and share data files, they are not considered long-term repositories for research materials.
+This is because GitHub, a for-profit company, does not have long-term data availability guarantees, allowing users to delete or make repositories private after publication.
+Also, GitHub does not issue Digital Object Identifiers (DOI) for content uploaded to their servers.
+DOIs are persistent and citable unique alpha-numeric identifiers assigned to digitally-stored research materials.
+Because of this, scientists sharing code and data through GitHub are strongly encouraged to independently submit their research materials to long-term data archives (\emph{e.g.}, Zenodo, Figshare, Dryad, OSF (\protect\hyperlink{ref-1Du6fzB8g}{Crystal‐Ornelas et al., 2021}; \protect\hyperlink{ref-kEX5dgzK}{Perez-Riverol et al., 2016}; \protect\hyperlink{ref-10ghgV3S8}{J.
+Perkel, 2016}); \protect\hyperlink{tbl:compare}{Table 1}).
+Some of these options (Zenodo, Figshare and OSF) integrate with GitHub, allowing project, code, and data releases (\protect\hyperlink{definitions}{Box 1}) to be archived with versioned, citable DOIs.
+Linking GitHub repositories with a DOI helps research become findable, properly cited, and can ensure long-term stability (\protect\hyperlink{ref-iIEKCTLU}{Hampton et al., 2015}).
+This strategy has been increasingly adopted in numerous studies in ecology and evolution (\emph{e.g.}, the Zenodo repositores for Hudgins (\protect\hyperlink{ref-GQj3c17f}{2022}), EllenJCoombs (\protect\hyperlink{ref-bZNn2hbh}{2020}), and Lrharper1 (\protect\hyperlink{ref-ZI1OqZNr}{2018})).
+
+An important aspect of making code and data citable and reusable is to add an appropriate license to protect intellectual property.
+Code published without a license is under exclusive copyright (by default), protecting it from copy, distribution, and modifications.
+One may grant specific rights to their code for reuse by adding licensing files and specifications within GitHub repositories (\protect\hyperlink{ref-TOsASkn5}{\emph{Adding a License to a Repository}, n.d.}).
+The Choose a License (\url{https://choosealicense.com/non-software/}) website offers further guidance on the licenses available for research and creative products.
+For example, Creative Commons (CC; \url{https://creativecommons.org/licenses/}) licenses can specify that shared code is intended for a specific analysis.
+A CC BY 4.0 license specifies that any code (or other creative products) must be appropriately credited to its original author when distributed, adapted or reused.
+
+\hypertarget{code-editing}{%
+\subsubsection{Collaborative and asynchronous code editing}\label{code-editing}}
+
+GitHub can serve as a platform for everyone working with research (\emph{e.g.}, supervisors or advisors, graduate students, postdoctoral fellows, and collaborators) to share in-progress work, and flag specific challenges or questions for each other (\protect\hyperlink{tbl:roles}{Table 2}).
+Periodic code, data and text review is useful for identifying errors early in the research process (\protect\hyperlink{ref-hm9PaCLD}{Song et al., 2020}), and informing further training and mentorship to fill gaps in skills.
+This is facilitated by a group of core features of Git and GitHub that allow contributors to discuss and simultaneously work on a project.
+For instance, users can clone and fork repositories (see \protect\hyperlink{definitions}{Box 1}), allowing for modifications to be done on a linked copy of a repository, which can then later be merged into the main project through pull requests.
+Collaborators can comment on specific lines of code and text or suggest changes, which can then be incorporated with the click of a button, greatly facilitating peer review.
+Explicit project organization and increased communication within pull requests, in GitHub Issues, or in GitHub Discussions can help with project development and with potential merge conflicts due to users simultaneously working on the same sections.
+Moreover, version control allows researchers to make changes in code or documents without worrying about irreparably modifying someone else's work (\#storing-sharing).
+
+By enabling more comprehensive remote collaboration, GitHub encourages the exchange of ideas among researchers at different institutions and in different countries, which can serve to improve the quality of the research itself by providing open access to data and code.
+
+\hypertarget{writing-manuscript}{%
+\subsubsection{Writing a manuscript}\label{writing-manuscript}}
+
+Beyond supporting collaborative code development, GitHub can be used for writing manuscripts.
+Writing a manuscript and storing its associated data and code in GitHub increases scientific reproducibility because text, code, and data can be found in one place.
+Although it may involve more initial time investment for setup, GitHub has many features that support a powerful collaborative workflow when writing manuscripts (\protect\hyperlink{ref-4ny1onB0}{Ram, 2013}).
+Text documents stored and versioned in GitHub can be instantly displayed when written in Markdown, a lightweight markup language increasingly popular among scientists.
+When manuscripts are written in Markdown on GitHub, co-authors can contribute changes or suggest revisions to a manuscript in the same ways they would contribute changes or suggest revisions to code (see \protect\hyperlink{code-editing}{Collaborative and asynchronous code editing}).
+Relevant literature or issues can be suggested using the Discussions and Issues features.
+
+Incorporating GitHub into the process of writing a manuscript does not necessarily mean pivoting to an entirely new workflow.
+For instance, authors who prefer writing in LaTeX or Markdown can synchronize Overleaf (\protect\hyperlink{ref-oGbKxHzj}{\emph{Using Git and GitHub}, n.d.}), HackMD (\url{https://hackmd.io}), and other platforms directly with a GitHub repository.
+Similar GitHub integrations are available for projects stored in DropBox, Google Drive, among other popular tools familiar to many scientists and their collaborators (\protect\hyperlink{tbl:compare}{Table 1}).
+
+We wrote this manuscript using Manubot, a modifiable workflow implemented in GitHub to automatically render manuscripts and automate bibliographical tasks (\protect\hyperlink{ref-YuJbg3zO}{Himmelstein et al., 2019}).
+Manubot uses GitHub's automation workflow, GitHub Actions, to combine and convert individual Markdown files into a single LaTeX document, which can then be converted to a Word or PDF document, and displayed as a webpage.
+Citations and bibliographic references are automatically managed with citable persistent identifiers (\emph{e.g.}, DOI, PubMed ID, ISBN, URL).
+The resulting manuscript can be rendered with document templates and citation style language formatting to meet journal formatting requirements.
+Every change made to the manuscript triggers its rendering, so that updates are readily displayed and made publicly available.
+Additional GitHub Actions can be integrated with Manubot, such as ones creating figures or generating tables (\emph{e.g.}, \url{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/main/.github/workflows}).
+
+\hypertarget{peer-review}{%
+\subsubsection{Peer review}\label{peer-review}}
+
+Peer review is the standard process for assessing whether research done in ecology and evolution should be published in a scientific journal.
+GitHub provides an open and transparent platform that can be used for either directly providing feedback on research products or addressing changes recommended by reviewers.
+GitHub Issues can be used to organize and discuss reviewer suggestions and to assign them to co-authors (\emph{e.g.}, \url{https://github.com/SORTEE-Github-Hackathon/manuscript/issues?q=label\%3A\%22Reviewer+Comment\%22}).
+When reviewer comments are posted as separate issues, authors can comment on the issues to discuss possible changes and assign co-authors who will address the issue.
+Co-authors can then integrate their edits and responses to reviewers using pull requests, which can be directly linked to the issues they address.
+
+GitHub can also assist reviewers during the peer review process.
+If the code associated with a manuscript is made available at the time of submission (\emph{e.g.}, as a link to a GitHub repository within the Data Availability Statement), peer reviewers may be able to offer more comprehensive suggestions on the code and written materials, potentially recognizing errors before publication.
+Certain journals or software development communities require submitted work or research code to be hosted on GitHub and their review processes make use of GitHub Issues (\emph{e.g.}, rOpenSci (\url{https://ropensci.org/software-review/}), Journal of Open Source Software (\url{https://joss.readthedocs.io/en/latest/submitting.html}).
+
+\hypertarget{open-science-discussion}{%
+\subsubsection{Open science discussion}\label{open-science-discussion}}
+
+Scientific publications often omit part of their intellectual and computational workflows, including the treatment of raw data and analytical steps (\emph{e.g.}, model assumption testing).
+Publishing data and reproducible workflows along with manuscripts can provide readers with all details about analytical steps and enable reproducing research experiments and results (\protect\hyperlink{ref-NOgBWVAr}{Culina et al., 2020}).
+In addition to storing data and code, GitHub repositories can provide a time-stamped (version controlled) preregistration of research plans and hypotheses.
+
+Conventional research practices typically separate tasks among collaborators (\emph{i.e.}, data entry, analysis, writing).
+It is common that coauthors discuss, but do not actively verify, edit, or execute research tasks that are not their main responsibility.
+GitHub can serve as a tool for open and tractable research development.
+Collaborators can directly interact with code and data, inspect for errors, and potentially identify scientific misconduct prior to manuscript submission (\emph{e.g.}, \url{https://ecologyforthemasses.com/2020/02/04/pruittdata-and-the-ethics-of-data-in-science}).
+Collaborators and readers are better positioned to discover erroneous or questionable findings if they have complete and transparent access to projects.
+
+This transparency can be extended beyond co-authors to the entire scientific community and to the public.
+Supplying code for novel or currently used methods reduces barriers to knowledge, improving the ability of others to build on existing work.
+This practice results in greater proliferation and accessibility for a broader audience.
+Projects can make use of GitHub Discussions (\url{https://docs.github.com/en/discussions}) to communicate among repository members (collaborators) and to engage with other scientists and the general public.
+Moreover, researchers can also use the GitHub Community (\url{https://github.community/}) forum to share expertise or request help from others on their analyses and ideas (\protect\hyperlink{tbl:roles}{Table 2}).
+
+The desire or need for privacy during the developmental stages of a manuscript or of a larger research project is common in EEB, and this is often perceived as a major barrier to doing science openly.
+Because GitHub repositories can be made private or public at any time, there is no need to choose privacy over open science, or vice-versa.
+Repositories can be kept private until their contents are ready to be shared publicly, as might occur when a research article is published or when an embargo is lifted.
+
+\hypertarget{automation}{%
+\subsubsection{Automation}\label{automation}}
+
+Automation has the strong potential to expand the scale and pace of research in ecology and evolution (\protect\hyperlink{ref-cfgXxgt1}{Keitt \& Abelson, 2021}).
+Automation frameworks can streamline many stages of the scientific process, including data collection and data validation (\emph{e.g.}, \protect\hyperlink{ref-bhDgD6lF}{Micheletti et al., 2021}; \protect\hyperlink{ref-1CJo8lo2v}{Yenni et al., 2019}), data analysis (\emph{e.g.}, \protect\hyperlink{ref-Qh7xTLwz}{Beaulieu-Jones \& Greene, 2017}), unit testing of research code (\emph{e.g.}, \protect\hyperlink{ref-lYazDTau}{Sarma et al., 2016}), archiving and deployment of data, code and reports (\emph{e.g.}, this manuscript, \protect\hyperlink{ref-SirQKFIz}{White et al., 2018}), and the interpretation, integration and usage of data and software across different sources (see \protect\hyperlink{ref-1FJhfqfiX}{Pasquier et al., 2017}).
+In this context, small modifications to code and data can be frequently committed and automatically tested, as in continuous integration and continuous deployment practices (\protect\hyperlink{ref-1Ep9EJL6y}{Meyer, 2014}).
+This allows for early detection and correction of errors, potentially improving confidence in scientific development by minimizing software errors (see \protect\hyperlink{ref-ufw0ZdnI}{Soergel, 2015}).
+In addition to increasing scientific rigour and confidence in ecological software (\protect\hyperlink{ref-12103x16N}{Scheller et al., 2010}), automation can help advance more rapidly sharing ecological data and making sure the data are high quality (\protect\hyperlink{ref-rTbinQMj}{Dietze et al., 2018}).
+Integrating automation workflows has been highly encouraged in areas of EEB, including predictive ecology (\protect\hyperlink{ref-mmCOSRfr}{McIntire et al., 2022}), long-term ecological studies (\protect\hyperlink{ref-RxK4CmfR}{Ernest et al., 2018}; \protect\hyperlink{ref-1CJo8lo2v}{Yenni et al., 2019}), and management of species at risk information (\protect\hyperlink{ref-kZzfmBNu}{Naujokaitis-Lewis et al., 2022}).
+
+Automation can be integrated into GitHub repositories through the GitHub Actions feature (\protect\hyperlink{ref-NUXbp429}{\emph{Features • GitHub Actions}, n.d.}), or through alternative automation systems (\emph{e.g.}, Circle CI, \protect\hyperlink{ref-T03Api6e}{\emph{Continuous Integration and Delivery}, n.d.}); Travis CI, \emph{Home -- Travis-CI} (\protect\hyperlink{ref-YeFSbfFV}{2022}){]}.
 Users can set up workflows associated with their repositories that are triggered by events (\emph{e.g.}, push, pull request or at specified times) for remote servers to perform user-specified steps and actions.
@@
 10. \textbf{Get help deciphering GitHub Notifications.} Try using tools like Octobox (\url{https://octobox.io}) to disentangle and manage multiple notifications from distinct GitHub projects. \\
-\bottomrule
+\bottomrule()
 \end{longtable}
@@
 The remaining columns indicate whether the platform for collaboration includes certain features.
-\label{tbl:compare}}\tabularnewline
-\toprule
+\label{tbl:compare}}\label{tbl:compare}\tabularnewline
+\toprule()
 \begin{minipage}[b]{\linewidth}\raggedright
@@
 \end{minipage} \\
-\midrule
+\midrule()
 \endfirsthead
-\toprule
+\toprule()
 \begin{minipage}[b]{\linewidth}\raggedright
@@
 Collaborative code/text editors & HackMD & yes & yes & yes & yes & limited free version \& paid & no & 3 documents free, private invitee limits & yes \\
-\bottomrule
+\bottomrule()
 \end{longtable}
@@
 be a code contributor and code reviewer, for example. For definitions of
-the GitHub features, see Box 1. \label{tbl:roles}}\tabularnewline
-\toprule
+the GitHub features, see Box 1. \label{tbl:roles}}\label{tbl:roles}\tabularnewline
+\toprule()
 \begin{minipage}[b]{\linewidth}\raggedright
@@
 Community & & & Suggest additional features and report bugs & Ask questions about data and code & & Create a linked, editable copy of the repository & View project website \\
-\bottomrule
+\bottomrule()
 \end{longtable}
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-TOsASkn5}{}}%
+\emph{Adding a license to a repository}.
+(n.d.).
+GitHub Docs.
+Retrieved March 4, 2023, from \url{https://ghdocs-prod.azurewebsites.net/en/communities/setting-up-your-project-for-healthy-contributions/adding-a-license-to-a-repository}
+
 \leavevmode\vadjust pre{\hypertarget{ref-13QX8XU3J}{}}%
@@
 (2021).
-A Beginner's Guide to Conducting Reproducible Research.
+A Beginner\textquotesingle s Guide to Conducting Reproducible Research.
 \emph{The Bulletin of the Ecological Society of America}, \emph{102}(2).
@@
 Anbaroğlu, B. (2021). A collaborative GIS programming course using GitHub Classroom. \emph{Transactions in GIS}, \emph{25}(6), 3132--3158. \url{https://doi.org/10.1111/tgis.12810}
+
+\leavevmode\vadjust pre{\hypertarget{ref-1HZdsK5Kn}{}}%
+Baker, M. (2016). 1,500 scientists lift the lid on reproducibility. \emph{Nature}, \emph{533}(7604), 452--454. \url{https://doi.org/10.1038/533452a}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Qh7xTLwz}{}}%
+Beaulieu-Jones, B.
+K., \& Greene, C.
+S.
+(2017).
+Reproducibility of computational workflows is automated using continuous analysis.
+\emph{Nature Biotechnology}, \emph{35}(4), 342--346.
+\url{https://doi.org/10.1038/nbt.3780}
 
@@
 \emph{Connect GitHub to a Project - OSF Support}. (n.d.). Retrieved March 4, 2023, from \url{https://help.osf.io/article/211-connect-github-to-a-project}
+
+\leavevmode\vadjust pre{\hypertarget{ref-T03Api6e}{}}%
+\emph{Continuous Integration and Delivery}. (n.d.). CircleCI. Retrieved March 4, 2023, from \url{https://circleci.com/}
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-NOgBWVAr}{}}%
+Culina, A., van den Berg, I., Evans, S., \& Sánchez-Tójar, A.
+(2020).
+Low availability of code in ecology: A~call for urgent action.
+\emph{PLOS Biology}, \emph{18}(7), e3000763.
+\url{https://doi.org/10.1371/journal.pbio.3000763}
+
+\leavevmode\vadjust pre{\hypertarget{ref-rTbinQMj}{}}%
+Dietze, M.
+C., Fox, A., Beck-Johnson, L.
+M., Betancourt, J.
+L., Hooten, M.
+B., Jarnevich, C.
+S., Keitt, T.
+H., Kenney, M.
+A., Laney, C.
+M., Larsen, L.
+G., Loescher, H.
+W., Lunch, C.
+K., Pijanowski, B.
+C., Randerson, J.
+T., Read, E.
+K., Tredennick, A.
+T., Vargas, R., Weathers, K.
+C., \& White, E.
+P.
+(2018).
+Iterative near-term ecological forecasting: Needs, opportunities, and challenges.
+\emph{Proceedings of the National Academy of Sciences}, \emph{115}(7), 1424--1432.
+\url{https://doi.org/10.1073/pnas.1710231115}
+
+\leavevmode\vadjust pre{\hypertarget{ref-bZNn2hbh}{}}%
+EllenJCoombs. (2020). \emph{EllenJCoombs/Asymmetry-evolution-cetaceans-for-publication-v.1.0.0} (Version v.1.0.0) {[}Computer software{]}. Zenodo. \url{https://doi.org/10.5281/zenodo.3893943}
+
+\leavevmode\vadjust pre{\hypertarget{ref-RxK4CmfR}{}}%
+Ernest, S.
+K.
+M., Yenni, G.
+M., Allington, G., Bledsoe, E.
+K., Christensen, E.
+M., Diaz, R.
+M., Geluso, K., Goheen, J.
+R., Guo, Q., Heske, E., Kelt, D., Meiners, J.
+M., Munger, J., Restrepo, C., Samson, D.
+A., Schutzenhofer, M.
+R., Skupski, M., Supp, S.
+R., Thibault, K., \ldots{} Valone, T.
+J.
+(2018).
+\emph{The Portal Project: a long-term study of a Chihuahuan desert ecosystem}.
+Cold Spring Harbor Laboratory.
+\url{https://doi.org/10.1101/332783}
+
+\leavevmode\vadjust pre{\hypertarget{ref-NUXbp429}{}}%
+\emph{Features • GitHub Actions}. (n.d.). GitHub. Retrieved March 4, 2023, from \url{https://github.com/features/actions}
+
 \leavevmode\vadjust pre{\hypertarget{ref-D4C4k4ak}{}}%
 Fehr, J., Himpe, C., Rave, S., \& Saak, J. (2021). Sustainable Research Software Hand-Over. \emph{Journal of Open Research Software}, \emph{9}(1), 5. \url{https://doi.org/10.5334/jors.307}
+
+\leavevmode\vadjust pre{\hypertarget{ref-SLq38RVv}{}}%
+Figueiredo, A. S. (2017). Data Sharing: Convert Challenges into Opportunities. \emph{Frontiers in Public Health}, \emph{5}. \url{https://doi.org/10.3389/fpubh.2017.00327}
 
@@
 (2022).
-Why don't we share data and code?
+Why don\textquotesingle t we share data and code?
 Perceived barriers and benefits to public archiving practices.
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-YuJbg3zO}{}}%
+Himmelstein, D.
+S., Rubinetti, V., Slochower, D.
+R., Hu, D., Malladi, V.
+S., Greene, C.
+S., \& Gitter, A.
+(2019).
+Open collaborative writing with Manubot.
+\emph{PLOS Computational Biology}, \emph{15}(6), e1007128.
+\url{https://doi.org/10.1371/journal.pcbi.1007128}
+
+\leavevmode\vadjust pre{\hypertarget{ref-YeFSbfFV}{}}%
+\emph{Home -- Travis-CI}. (2022, October 6). \url{https://www.travis-ci.com/}
+
+\leavevmode\vadjust pre{\hypertarget{ref-GQj3c17f}{}}%
+Hudgins, E. (2022). \emph{emmajhudgins/UStreedamage: publication release} (accepted) {[}Computer software{]}. Zenodo. \url{https://doi.org/10.5281/zenodo.6097109}
+
 \leavevmode\vadjust pre{\hypertarget{ref-3UAritXO}{}}%
@@
 \url{https://doi.org/10.1109/icse.2015.74}
+
+\leavevmode\vadjust pre{\hypertarget{ref-cfgXxgt1}{}}%
+Keitt, T. H., \& Abelson, E. S. (2021). Ecology in the age of automation. \emph{Science}, \emph{373}(6557), 858--859. \url{https://doi.org/10.1126/science.abi4692}
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-ZI1OqZNr}{}}%
+Lrharper1.
+(2018).
+\emph{Hulluni-Bioinformatics/Harper\_Et\_Al\_2018: Github Repository Deposited With Harper Et Al.
+(2018) In Ecology And Evolution.} Zenodo.
+\url{https://doi.org/10.5281/zenodo.1188710}
+
 \leavevmode\vadjust pre{\hypertarget{ref-pjy75gHr}{}}%
@@
 \url{https://doi.org/10.1080/00031305.2017.1375986}
+
+\leavevmode\vadjust pre{\hypertarget{ref-mmCOSRfr}{}}%
+McIntire, E.
+J.
+B., Chubaty, A.
+M., Cumming, S.
+G., Andison, D., Barros, C., Boisvenue, C., Haché, S., Luo, Y., Micheletti, T., \& Stewart, F.
+E.
+C.
+(2022).
+PERFICT: A Re‐imagined foundation for predictive ecology.
+\emph{Ecology Letters}, \emph{25}(6), 1345--1351.
+\url{https://doi.org/10.1111/ele.13994}
+
+\leavevmode\vadjust pre{\hypertarget{ref-1Ep9EJL6y}{}}%
+Meyer, M. (2014). Continuous Integration and Its Tools. \emph{IEEE Software}, \emph{31}(3), 14--16. \url{https://doi.org/10.1109/ms.2014.58}
+
+\leavevmode\vadjust pre{\hypertarget{ref-bhDgD6lF}{}}%
+Micheletti, T., Stewart, F.
+E.
+C., Cumming, S.
+G., Haché, S., Stralberg, D., Tremblay, J.
+A., Barros, C., Eddy, I.
+M.
+S., Chubaty, A.
+M., Leblond, M., Pankratz, R.
+F., Mahon, C.
+L., Van Wilgenburg, S.
+L., Bayne, E.
+M., Schmiegelow, F., \& McIntire, E.
+J.
+B.
+(2021).
+Assessing Pathways of Climate Change Effects in SpaDES: An Application to Boreal Landbirds of Northwest Territories Canada.
+\emph{Frontiers in Ecology and Evolution}, \emph{9}.
+\url{https://doi.org/10.3389/fevo.2021.679673}
+
+\leavevmode\vadjust pre{\hypertarget{ref-uBJwnPbq}{}}%
+Mislan, K.
+A.
+S., Heer, J.
+M., \& White, E.
+P.
+(2016).
+Elevating The Status of Code in Ecology.
+\emph{Trends in Ecology \&Amp; Evolution}, \emph{31}(1), 4--7.
+\url{https://doi.org/10.1016/j.tree.2015.11.006}
+
+\leavevmode\vadjust pre{\hypertarget{ref-kZzfmBNu}{}}%
+Naujokaitis-Lewis, I., Endicott, S., \& Guezen, J.
+M.
+(2022).
+CAN-SAR: A database of Canadian species at risk information.
+\emph{Scientific Data}, \emph{9}(1).
+\url{https://doi.org/10.1038/s41597-022-01381-8}
+
+\leavevmode\vadjust pre{\hypertarget{ref-1Hcf13Q0k}{}}%
+Nugroho, R.
+P., Zuiderwijk, A., Janssen, M., \& de Jong, M.
+(2015).
+A comparison of national open data policies: lessons learned.
+\emph{Transforming Government: People, Process and Policy}, \emph{9}(3), 286--308.
+\url{https://doi.org/10.1108/tg-03-2014-0008}
+
+\leavevmode\vadjust pre{\hypertarget{ref-4LaijDIZ}{}}%
+On data availability, reproducibility and reuse. (2017). \emph{Nature Cell Biology}, \emph{19}(4), 259--259. \url{https://doi.org/10.1038/ncb3506}
+
+\leavevmode\vadjust pre{\hypertarget{ref-1FJhfqfiX}{}}%
+Pasquier, T., Lau, M.
+K., Trisovic, A., Boose, E.
+R., Couturier, B., Crosas, M., Ellison, A.
+M., Gibson, V., Jones, C.
+R., \& Seltzer, M.
+(2017).
+If these data could talk.
+\emph{Scientific Data}, \emph{4}(1).
+\url{https://doi.org/10.1038/sdata.2017.114}
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-1CcAUn3Lu}{}}%
+Piwowar, H.
+A., Day, R.
+S., \& Fridsma, D.
+B.
+(2007).
+Sharing Detailed Research Data Is Associated with Increased Citation Rate.
+\emph{PLoS ONE}, \emph{2}(3), e308.
+\url{https://doi.org/10.1371/journal.pone.0000308}
+
+\leavevmode\vadjust pre{\hypertarget{ref-666HppfO}{}}%
+Pronk, T. E., Wiersma, P. H., van Weerden, A., \& Schieving, F. (2015). A game theoretic analysis of research data sharing. \emph{PeerJ}, \emph{3}, e1242. \url{https://doi.org/10.7717/peerj.1242}
+
 \leavevmode\vadjust pre{\hypertarget{ref-4ny1onB0}{}}%
 Ram, K. (2013). Git can facilitate greater reproducibility and increased transparency in science. \emph{Source Code for Biology and Medicine}, \emph{8}(1). \url{https://doi.org/10.1186/1751-0473-8-7}
+
+\leavevmode\vadjust pre{\hypertarget{ref-lYazDTau}{}}%
+Sarma, G.
+P., Jacobs, T.
+W., Watts, M.
+D., Ghayoomie, S.
+V., Larson, S.
+D., \& Gerkin, R.
+C.
+(2016).
+Unit testing, model validation, and biological simulation.
+\emph{F1000Research}, \emph{5}, 1946.
+\url{https://doi.org/10.12688/f1000research.9315.1}
+
+\leavevmode\vadjust pre{\hypertarget{ref-12103x16N}{}}%
+Scheller, R.
+M., Sturtevant, B.
+R., Gustafson, E.
+J., Ward, B.
+C., \& Mladenoff, D.
+J.
+(2010).
+Increasing the reliability of ecological models using modern software engineering techniques.
+\emph{Frontiers in Ecology and the Environment}, \emph{8}(5), 253--260.
+\url{https://doi.org/10.1890/080141}
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-ufw0ZdnI}{}}%
+Soergel, D. A. W. (2015). Rampant software errors may undermine scientific results. \emph{F1000Research}, \emph{3}, 303. \url{https://doi.org/10.12688/f1000research.5930.2}
+
+\leavevmode\vadjust pre{\hypertarget{ref-hm9PaCLD}{}}%
+Song, X., Goldstein, S.
+C., \& Sakr, M.
+(2020, June 15).
+Using Peer Code Review as an Educational Tool.
+\emph{Proceedings of the 2020 ACM Conference on Innovation and Technology in Computer Science Education}.
+ITiCSE \textquotesingle20: Innovation and Technology in Computer Science Education.
+\url{https://doi.org/10.1145/3341525.3387370}
+
 \leavevmode\vadjust pre{\hypertarget{ref-7q3wZN6d}{}}%
 Spinellis, D. (2012). Git. \emph{IEEE Software}, \emph{29}(3), 100--101. \url{https://doi.org/10.1109/ms.2012.61}
+
+\leavevmode\vadjust pre{\hypertarget{ref-1CzUZwyU2}{}}%
+Tenopir, C., Dalton, E.
+D., Allard, S., Frame, M., Pjesivac, I., Birch, B., Pollock, D., \& Dorsett, K.
+(2015).
+Changes in Data Sharing and Data Reuse Practices and Perceptions among Scientists Worldwide.
+\emph{PLOS ONE}, \emph{10}(8), e0134826.
+\url{https://doi.org/10.1371/journal.pone.0134826}
+
+\leavevmode\vadjust pre{\hypertarget{ref-PLmDFZrm}{}}%
+Tenopir, C., Rice, N.
+M., Allard, S., Baird, L., Borycz, J., Christian, L., Grant, B., Olendorf, R., \& Sandusky, R.
+J.
+(2020).
+Data sharing, management, use, and reuse: Practices and perceptions of scientists worldwide.
+\emph{PLOS ONE}, \emph{15}(3), e0229003.
+\url{https://doi.org/10.1371/journal.pone.0229003}
 
@@
 (2014).
-Considering the Role of Affect in Learning: Monitoring Students' Self-Efficacy, Sense of Belonging, and Science Identity.
+Considering the Role of Affect in Learning: Monitoring Students\textquotesingle{} Self-Efficacy, Sense of Belonging, and Science Identity.
 \emph{CBE---Life Sciences Education}, \emph{13}(1), 6--15.
 \url{https://doi.org/10.1187/cbe.13-12-0241}
+
+\leavevmode\vadjust pre{\hypertarget{ref-oGbKxHzj}{}}%
+\emph{Using Git and GitHub}. (n.d.). Retrieved March 4, 2023, from \url{https://www.overleaf.com/learn/how-to/Using_Git_and_GitHub}
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-SirQKFIz}{}}%
+White, E.
+P., Yenni, G.
+M., Taylor, S.
+D., Christensen, E.
+M., Bledsoe, E.
+K., Simonis, J.
+L., \& Ernest, S.
+K.
+M.
+(2018).
+Developing an automated iterative near‐term forecasting system for an ecological study.
+\emph{Methods in Ecology and Evolution}, \emph{10}(3), 332--344.
+\url{https://doi.org/10.1111/2041-210x.13104}
+
+\leavevmode\vadjust pre{\hypertarget{ref-1Ch6LSHef}{}}%
+Wicherts, J.
+M., Bakker, M., \& Molenaar, D.
+(2011).
+Willingness to Share Research Data Is Related to the Strength of the Evidence and the Quality of Reporting of Statistical Results.
+\emph{PLoS ONE}, \emph{6}(11), e26828.
+\url{https://doi.org/10.1371/journal.pone.0026828}
+
+\leavevmode\vadjust pre{\hypertarget{ref-1CJo8lo2v}{}}%
+Yenni, G.
+M., Christensen, E.
+M., Bledsoe, E.
+K., Supp, S.
+R., Diaz, R.
+M., White, E.
+P., \& Ernest, S.
+K.
+M.
+(2019).
+Developing a modern data workflow for regularly updated data.
+\emph{PLOS Biology}, \emph{17}(1), e3000125.
+\url{https://doi.org/10.1371/journal.pbio.3000125}
+
 \end{CSLReferences}

### 2023-03-04 manuscript.tex
Update manubot.yaml [ci skip]
This build is based on
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/ec905395a96fdfb763884c88fe68815dba1be09d.

This commit was created by the following CI build and job:
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/ec905395a96fdfb763884c88fe68815dba1be09d/checks
https://github.com/SORTEE-Github-Hackathon/manuscript/actions/runs/4333050954

@@
 This manuscript
-(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/c300807d221901c7441dc86e15a3e2c6c4d2f7c4/}{permalink})
+(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/ec905395a96fdfb763884c88fe68815dba1be09d/}{permalink})
 was automatically generated
-from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/c300807d221901c7441dc86e15a3e2c6c4d2f7c4}{SORTEE-Github-Hackathon/manuscript@c300807}
+from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/ec905395a96fdfb763884c88fe68815dba1be09d}{SORTEE-Github-Hackathon/manuscript@ec90539}
 on 2023-03-04.

### 2023-03-04 manuscript.tex
Clarification of abstract and introduction [ci skip]
This build is based on
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/c47fa107ec52cb7dd5081b0143986b78169d5c2e.

This commit was created by the following CI build and job:
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/c47fa107ec52cb7dd5081b0143986b78169d5c2e/checks
https://github.com/SORTEE-Github-Hackathon/manuscript/actions/runs/4333302078

@@
 This manuscript
-(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/ec905395a96fdfb763884c88fe68815dba1be09d/}{permalink})
+(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/c47fa107ec52cb7dd5081b0143986b78169d5c2e/}{permalink})
 was automatically generated
-from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/ec905395a96fdfb763884c88fe68815dba1be09d}{SORTEE-Github-Hackathon/manuscript@ec90539}
+from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/c47fa107ec52cb7dd5081b0143986b78169d5c2e}{SORTEE-Github-Hackathon/manuscript@c47fa10}
 on 2023-03-04.
@@
 GitHub is an online, cloud-based service that can help researchers track, organize, discuss, share, and collaborate on software and other materials related to research production, including data, code for analyses, and protocols.
-
 Despite these benefits, the use of GitHub in ecology and evolution is not widespread.
@@
 
-Most scientists, including ecologists and evolutionary biologists, depend on computational tools for their research (\protect\hyperlink{ref-fJWFe93e}{Hannay et al., 2009}).
-Researchers write and use software packages or write code (hereafter, code) to perform scientific tasks ranging from data management, data analysis, and study replication, to the application and the development of tools for hypothesis testing.
-Maintaining code for scientific collaboration requires an efficient and well-documented work-flow (\protect\hyperlink{ref-1Kqna6l2}{J. M. Perkel, 2020}).
-To facilitate this process, scientists have been adopting tools from information and systems technology, such as cloud-based services for documentation and version control {[}\emph{e.g.}, the Google Suite, the Microsoft Suite, DropBox, and GitHub (\protect\hyperlink{ref-10ghgV3S8}{J.
-Perkel, 2016}){]}.
-Within the spectrum of cloud-based services for collaboration, GitHub is uniquely positioned (\protect\hyperlink{tbl:compare}{Table 1}) to benefit scientists because it is designed to store, track changes, and enable collaboration on computer code---fundamental components of modern research.
-Albeit, most researchers lack exposure to adequate programming and coding practices and thus dedicate valuable time and effort to self-teaching research-facilitating tools.
-GitHub is one of the most used web-based platforms for computational version control and collaboration, and in this paper, we provide researchers in ecology and evolutionary biology (EEB) with practical workflows to use GitHub to facilitate their collaborative research and code management practices.
+Most scientists, including ecologists and evolutionary biologists, rely on computational tools for their research (\protect\hyperlink{ref-fJWFe93e}{Hannay et al., 2009}).
+Researchers write and use software packages or write code to perform tasks ranging from data management, data analysis, and study replication, to the application and the development of tools for hypothesis testing.
+Maintaining code for scientific collaboration requires an efficient and well-documented workflow (\protect\hyperlink{ref-1Kqna6l2}{J. M. Perkel, 2020}).
+To facilitate this process, scientists have been adopting tools from information and systems technology, such as cloud-based services for documentation and version control (\protect\hyperlink{ref-10ghgV3S8}{J.
+Perkel, 2016}).
+These include the Google Suite, the Microsoft Suite, DropBox, and GitHub.
+Within the spectrum of cloud-based services for collaboration, GitHub is uniquely positioned (\protect\hyperlink{tbl:compare}{Table 1}) to benefit scientists because it is specifically designed to store, track changes, and enable collaboration on computer code---fundamental components of modern research.
+Albeit, many researchers lack exposure to adequate programming and coding practices and thus dedicate valuable time and effort to teach themselves research-facilitating tools.
+In this paper, we provide researchers in ecology and evolutionary biology (EEB) with practical workflows to use GitHub -- the most used web-based platform for computational version control and collaboration -- to facilitate their collaborative research and code management practices.
 
 GitHub (\url{https://github.com}) provides a simple but powerful web interface that allows users to participate in projects by contributing, modifying and discussing existing code, reporting bugs, discovering code and data, and publishing new code.
-Github allows users to store files and directories in repositories, and keeps a chronological record of modifications (\protect\hyperlink{ref-RVetqmsg}{Bryan, 2018}) (see \protect\hyperlink{definitions}{Box 1}).
-Beyond storage and record-tracking, file management in GitHub is integrated with several communication features, allowing users to engage in discussions, to plan and collaborate in code, and publish information to a webpage (Github Issues, Github Discussions, Github Pages; see \protect\hyperlink{definitions}{Box 1}).
-These features contrast with traditional practices of directly sharing files through email, other cloud-based services or physical storage units, which become challenging and time-consuming in long-term and collaborative projects (\protect\hyperlink{ref-4ny1onB0}{Ram, 2013}).
-By allowing users to easily integrate versioning, communication, collaboration with research code and data, Github paves the way for easier implementation of open science practices within research projects (\protect\hyperlink{ref-kEX5dgzK}{Perez-Riverol et al., 2016}).
+It stores files and directories in repositories, and keeps a chronological record of modifications (\protect\hyperlink{ref-RVetqmsg}{Bryan, 2018}) (see \protect\hyperlink{definitions}{Box 1}).
+GitHub also integrates several communication features, such as Github Issues, Github Discussions, Github Pages, which allows users to engage in discussions, to plan and collaborate on code, and publish information to a webpage (see \protect\hyperlink{definitions}{Box 1}).
+These features are an improvement over traditional practices of directly sharing files through email, other cloud-based services or physical storage units, which can become challenging and time-consuming in long-term and collaborative projects (\protect\hyperlink{ref-4ny1onB0}{Ram, 2013}).
+By making it easier to integrate versioning, communication, collaboration with research code and data, Github helps facilitate open science practices in research projects (\protect\hyperlink{ref-kEX5dgzK}{Perez-Riverol et al., 2016}).
 
 Git is the version control system that enables the collaborative tools available on GitHub.
-Git was originally developed as a fast, lightweight and open-source system to allow software engineers to efficiently develop and collaborate in projects (\protect\hyperlink{ref-1CM2EcdVk}{\emph{Git - A Short History of Git}, n.d.}).
+Git was initially developed as a fast, lightweight and open-source system to allow software engineers to efficiently develop and collaborate on projects (\protect\hyperlink{ref-1CM2EcdVk}{\emph{Git - A Short History of Git}, n.d.}).
 Since its launch in 2005, Git has become the leading version control system in software development and in other disciplines that require collaboration and community contributions, such as in scientific research (\protect\hyperlink{ref-7q3wZN6d}{Spinellis, 2012}).
-Knowledge of basic concepts of Git (such as commit, push, pull, and checkout; see \protect\hyperlink{definitions}{Box 1}) is recommended to understand how GitHub keeps track of changes to files and folders.
-Nevertheless, the GitHub web-based platform and its integrated development environments (such as GitHub Desktop) allow users to perform most repository and data management operations without using the command console, making these functionalities available to users who are less familiar with software development.
+To understand how GitHub keeps track of changes to files and folders, it is recommended to have knowledge of basic concepts of Git (such as commit, push, pull, and checkout; see \protect\hyperlink{definitions}{Box 1}).
+However, the GitHub web-based platform and its integrated development environments (such as GitHub Desktop) allow users to perform most repository and data management operations without using the command console, making these functionalities available even to users who are less familiar with software development.
 
 Version control involves tracking the state of the files and directories which are stored in a ``repository'' (see \protect\hyperlink{definitions}{Box 1}).
-A basic workflow using Git and GitHub is to: (i) create a remote repository that is synchronized with files and directories stored locally; (ii) modify these files, either locally or remotely; (iii) frequently ``commit'' (or record) changes to these files (see \protect\hyperlink{definitions}{Box 1}) along with a description of modifications; (iv) synchronize commits with GitHub (see ``push'' and ``pull'' in \protect\hyperlink{definitions}{Box 1}) so that the repository on the web and the local repositories are up-to-date.
-Repositories, which contain files, their modifications, and the description of their changes can then be accessed by chosen collaborators or, whenever applicable, the public, who can easily download and synchronize them to their own computers (see ``clone'' in \protect\hyperlink{definitions}{Box 1}).
-Commits act like snapshots, one can view or even revert the state of the project to any previous commit.
-If the modified files are plain text, only the differences from the previous commit are recorded, allowing you to frequently commit changes without causing the size of the project to grow excessively.
+A typical workflow using Git and GitHub is to: (i) create a remote repository that is synchronized with files and directories stored locally; (ii) modify these files, either locally or remotely; (iii) frequently ``commit'' (or record) changes to these files (see \protect\hyperlink{definitions}{Box 1}) along with a description of modifications; (iv) synchronize commits with GitHub (see ``push'' and ``pull'' in \protect\hyperlink{definitions}{Box 1}) so that the repository on the web and the local repositories are up-to-date.
+The repository, which contains files, their modifications, and the description of their changes can then be accessed by chosen collaborators or, whenever applicable, the public, who can easily download and synchronize them to their own computers (see ``clone'' in \protect\hyperlink{definitions}{Box 1}).
+Commits act like snapshots, allowing users to view or even revert the state of the project to any previous commit.
+If the modified files are plain text, only the differences from the previous commit are recorded, allowing frequent commits without causing the size of the project to grow excessively.
 This provides a safe and less cluttered alternative to frequently making full copies of documents at different points in their evolution (\emph{e.g.} \texttt{analysis.R}, \texttt{analysis\_v2.R}, \texttt{analysis\_FINAL.R}).
-While focusing on technical details about the use of Git and GitHub is beyond the scope of this study, we recommend users explore available resources to become more familiar with version control features (see Perez-Riverol et al.
+While we do not focus on technical details about the use of Git and GitHub in this study, we recommend users explore available resources to become more familiar with version control features (see Perez-Riverol et al.
 (\protect\hyperlink{ref-kEX5dgzK}{2016}), Blischak et al.

### 2023-03-04 manuscript.tex
Last few changes to improve clarity in the introduction [ci skip]
This build is based on
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/354ed9fa4d9227c97bb04cd7e127ee0062622901.

This commit was created by the following CI build and job:
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/354ed9fa4d9227c97bb04cd7e127ee0062622901/checks
https://github.com/SORTEE-Github-Hackathon/manuscript/actions/runs/4333323612

@@
 This manuscript
-(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/c47fa107ec52cb7dd5081b0143986b78169d5c2e/}{permalink})
+(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/354ed9fa4d9227c97bb04cd7e127ee0062622901/}{permalink})
 was automatically generated
-from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/c47fa107ec52cb7dd5081b0143986b78169d5c2e}{SORTEE-Github-Hackathon/manuscript@c47fa10}
+from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/354ed9fa4d9227c97bb04cd7e127ee0062622901}{SORTEE-Github-Hackathon/manuscript@354ed9f}
 on 2023-03-04.
@@
 
-The expansive GitHub user-community and numerous GitHub resources have boosted its popularity {[}Perez-Riverol et al.
+The use of GitHub has become increasingly popular in recent years due to the expansive GitHub user-community and numerous GitHub resources {[}Perez-Riverol et al.
 (\protect\hyperlink{ref-kEX5dgzK}{2016}); Bryan (\protect\hyperlink{ref-RVetqmsg}{2018}); \url{https://happygitwithr.com}; \url{https://ourcodingclub.github.io}{]}.
-Nevertheless, although multiple articles have encouraged researchers in EEB to adopt GitHub as part of their research process (\protect\hyperlink{ref-3DKwn1sY}{Lowndes et al., 2017}; \protect\hyperlink{ref-10ghgV3S8}{J.
+Nevertheless, although multiple articles have encouraged researchers in ecology and evolution to adopt GitHub as part of their research process (\protect\hyperlink{ref-3DKwn1sY}{Lowndes et al., 2017}; \protect\hyperlink{ref-10ghgV3S8}{J.
 Perkel, 2016}), its use is still not widespread.
-First-time users without formal training in information technology may face steep learning curves because GitHub and its features have been centered on software development (\protect\hyperlink{ref-139b0pSGc}{Leibzon, 2016}).
-Moreover, domain-specific resources providing tractable examples and practical guidance for researchers in EEB on GitHub are scarce {[}but see Kim et al.
+Among many other factors, this may be because first-time users without formal training in information technology can face a steep learning curve, as GitHub and its features have been centered on software development (\protect\hyperlink{ref-139b0pSGc}{Leibzon, 2016}).
+Furthermore, there are few domain-specific resources providing tractable examples and practical guidance for researchers in EEB on how to use GitHub {[}but see Kim et al.
 (\protect\hyperlink{ref-lJAgyhYq}{2022}); \url{https://ourcodingclub.github.io}; \url{https://www.openscapes.org}{]}.
-Widespread adoption of GitHub for collaborating on research tasks can ultimately enable EEB researchers to spend less time on creating novel processes for collaboration and more time on their research (\protect\hyperlink{ref-ydrk01SR}{Briney et al., 2020}).
-More importantly, expanding the availability of data and code management standards---of which GitHub is one increasingly important component---makes research more reproducible and collaborative (\protect\hyperlink{ref-13QX8XU3J}{Alston \& Rick, 2021}; \protect\hyperlink{ref-VDJput1V}{Gomes et al., 2022}).
+Widespread adoption of GitHub for collaborative research tasks can ultimately enable EEB researchers to save time on creating novel processes for collaboration and focus more on their research (\protect\hyperlink{ref-ydrk01SR}{Briney et al., 2020}).
+More importantly, expanding the availability of data and code management standards, of which GitHub is an increasingly important component, makes research more reproducible and collaborative (\protect\hyperlink{ref-13QX8XU3J}{Alston \& Rick, 2021}; \protect\hyperlink{ref-VDJput1V}{Gomes et al., 2022}).
 
 This paper is the result of an academic hackathon held during the 2021 conference for the Society for Open, Reliable, and Transparent Ecology and Evolutionary Biology (SORTEE, \url{https://www.sortee.org}).
-We convened around thirty researchers in EEB with varying levels of familiarity with the usage of GitHub in research projects to showcase and discuss how existing features can contribute to documentation and collaboration in EEB research.
-During the hackathon, we identified the need for formal discussions on how EEB researchers can benefit from GitHub and its features.
+We convened around thirty researchers in EEB with varying levels of familiarity with the use of GitHub in research projects.
+The aim of the hackathon was to showcase and discuss how existing features of GitHub can contribute to documentation and collaboration in EEB research.
+During the event, we identified the need for formal discussions on how EEB researchers can benefit from GitHub and its features.
 Here, we outline twelve practical ways that EEB researchers can use GitHub features for more collaborative, transparent, and reproducible science.
-We also provide critical perspectives on features that could be improved and catered towards research development.
+We also provide critical perspectives on features that could be improved and catered towards research development, drawing on examples from the literature.
 

### 2023-03-04 manuscript.tex
A few more clarifications to sentences [ci skip]
This build is based on
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/3601d15cc9a4fffce47dacf71ccee802a971eb55.

This commit was created by the following CI build and job:
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/3601d15cc9a4fffce47dacf71ccee802a971eb55/checks
https://github.com/SORTEE-Github-Hackathon/manuscript/actions/runs/4333385634

@@
 This manuscript
-(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/354ed9fa4d9227c97bb04cd7e127ee0062622901/}{permalink})
+(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/3601d15cc9a4fffce47dacf71ccee802a971eb55/}{permalink})
 was automatically generated
-from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/354ed9fa4d9227c97bb04cd7e127ee0062622901}{SORTEE-Github-Hackathon/manuscript@354ed9f}
+from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/3601d15cc9a4fffce47dacf71ccee802a971eb55}{SORTEE-Github-Hackathon/manuscript@3601d15}
 on 2023-03-04.
@@
 
-\hypertarget{the-promise-of-github-for-eeb-researchers}{%
-\subsubsection{The promise of GitHub for EEB researchers}\label{the-promise-of-github-for-eeb-researchers}}
-
-There have been many calls for researchers outside of the software development community to adopt GitHub for their collaborative research (\protect\hyperlink{ref-UsTxAq4f}{Anbaroğlu, 2021}; \protect\hyperlink{ref-1Du6fzB8g}{Crystal‐Ornelas et al., 2021}; \protect\hyperlink{ref-10ghgV3S8}{J.
+\hypertarget{the-promise-of-github-for-ecology-and-evolutionary-biology-researchers}{%
+\subsubsection{The promise of GitHub for ecology and evolutionary biology researchers}\label{the-promise-of-github-for-ecology-and-evolutionary-biology-researchers}}
+
+Many researchers outside of software development have been encouraged to use GitHub for their collaborative research (\protect\hyperlink{ref-UsTxAq4f}{Anbaroğlu, 2021}; \protect\hyperlink{ref-1Du6fzB8g}{Crystal‐Ornelas et al., 2021}; \protect\hyperlink{ref-10ghgV3S8}{J.
 Perkel, 2016}).
-These calls come in light of the continuous shift towards open-science and the increasing computational and data requirements in EEB.
-While tools like the Google Suite and DropBox enable rapid sharing and collaboration of some research documents, GitHub brings together features that directly integrate open science practices, such as the association of public discussions with data, code and findings, tracking multiple rounds of edits to files in a sensible way for easy review, and managing complex research projects with many collaborators and goals.
-Until now, resources and practical guidance on using GitHub within the EEB community have been dispersed across blog posts, as well as written and video tutorials (\protect\hyperlink{tips}{Box 2}).
+This is largely due to the rise of open science and the growing computational and data needs of ecology and evolutionary biology.
+While tools like the Google Suite and DropBox enable rapid sharing and collaboration of some research documents, GitHub brings together features that directly integrate open science practices.
+These include linking data, code and findings to public discussions, tracking edits to files for review, and managing complex research projects with many collaborators and goals.
+Until now, resources and practical guidance on using GitHub within the EEB community have been scattered across blog posts, written and video tutorials (\protect\hyperlink{tips}{Box 2}).
 These resources have been useful for learning to use GitHub in our own research, as ecologists and evolutionary biologists.
@@
 The twelve use cases we described here can leverage GitHub to enable more transparent and collaborative research in ecology and evolution (Figure \ref{fig:scatterblob}).
-Most of these uses can be quickly integrated into the research practices of users (\emph{e.g.}, storing data, creating virtual notebooks, making code citable).
+Most of these uses can be quickly integrated into researchers' practices, such as storing data, creating virtual notebooks, and making code citable.
 Making stored data and code citable usually involves creating a repository on GitHub, pushing code and data, and then integrating a DOI minting service to the repository (\emph{e.g.}, with Zenodo or OSF; see below).
-On the other hand, some cases we described here, including course material development, web hosting, and automation, require greater effort and time commitment, but have the potential to make EEB research more open, accessible, and collaborative.
-Managing full research projects or laboratories on GitHub require careful thought as to how to delegate tasks, such as reviewing pull requests or creating issues.
+On the other hand, some cases we described here, including course material development, web hosting, and automation, require more effort and time, but have the potential to make ecology and evolution research more open, accessible, and collaborative.
+If researchers wish to manage full research projects or laboratories on GitHub, they should consider how to delegate tasks, such as reviewing pull requests or creating issues.
 For example, collaboratively authoring a paper using GitHub, as we have done here, involves a learning curve for co-authors less familiar with the intricacies of GitHub, requires overhead to set up automation frameworks through GitHub Actions, and especially, the commitment from all co-authors to use GitHub when modifying and reviewing the text.
@@
 
-First, real-time document editing is still best performed on other platforms (\emph{e.g.}, cloud-stored documents from Microsoft Word, Google Docs, HackMD (\url{https://hackmd.io/})).
+First, real-time document editing is still best performed on other platforms, such as cloud-stored documents from Microsoft Word, Google Docs, and HackMD (\url{https://hackmd.io/}).
 Second, operations that are dependent on software requiring graphical user interfaces might not be easily achievable in GitHub, such as designing and manipulating figures or tables.
-While creating tables and figures can be done through code, users may choose other software to collaboratively brainstorm figures and tables (\emph{e.g}., Google Slides, Google Sheets; but see GitHub Discussions).
+While creating tables and figures can be done through code, users may choose other software to collaboratively brainstorm figures and tables, like Google Slides or Google Sheets (but see GitHub Discussions).
 
@@
 Institutional encouragement and instructional resources focused on researchers in ecology and evolution may be limited.
-And with institutional availability of software licenses for tools like the Google Suite or Microsoft Office, researchers may be hesitant to spend valuable time learning another tool.
+Additionally, with the availability of software licenses for tools like the Google Suite or Microsoft Office, researchers may be reluctant to spend valuable time learning another tool.
 When GitHub is taught within an EEB context, it usually accompanies coursework in topics such as statistical programming.
-It can be challenging to learn Git alongside scripting languages, statistical theory, and file system navigation, especially when many prospective users may be inexperienced with programming.
-Instructors likewise may confuse the expected digital literacy of students with computational fluency, even when modern technology increasingly abstracts concepts through search optimization and preponderant integrated development environments (IDE), or `point-and-click' user interfaces.
+This can be difficult for those who lack programming experience, as they must learn Git alongside scripting languages, statistical theory, and file system navigation.
+Instructors may also confuse the expected digital literacy of students with computational fluency, despite modern technology abstracting concepts through search optimization and user-friendly integrated development environments (IDEs) or `point-and-click' user interfaces.
 
@@
 Despite broad utility, GitHub remains a tool predominantly used by computer scientists and software developers.
-EEB researchers may take the view that GitHub is a platform that only needs to be used by individuals writing code and may silo those aspects of projects to a single individual.
-Those assumptions may obscure the utility of GitHub for tasks other than traditional data analysis and code development.
-However, we emphasize that there are opportunities for collaboration using GitHub by researchers of all skill levels or time constraints (\protect\hyperlink{tbl:roles}{Table 2}); for example, project stakeholders can provide a list of use-cases or highlight important conceptual components of a project using GitHub Issues or Discussions features.
-
-A third barrier may come from general reluctance to share data and code publicly, or technical and logistical issues (\protect\hyperlink{ref-VDJput1V}{Gomes et al., 2022}).
-GitHub is, by default, a public and open platform.
-This openness may add additional pressure to students and scientists learning to use the platform.
-Moreover, additional tools may be required to fully integrate project files and GitHub repositories (\emph{e.g.}, \protect\hyperlink{ref-lx49NGto}{\emph{Connect GitHub to a Project - OSF Support}, n.d.}).
+EEB researchers may take the view that GitHub is a platform that only needs to be used by individuals writing code, and may silo those aspects of projects to a single individual.
+These assumptions may obscure the utility of GitHub for tasks other than traditional data analysis and code development.
+However, we emphasize that there are opportunities for collaboration using GitHub by researchers of all skill levels or time constraints (\protect\hyperlink{tbl:roles}{Table 2}).
+For example, project stakeholders can provide a list of use-cases or highlight important conceptual components of a project using GitHub Issues or Discussions features.
+
+A third barrier to the use of GitHub may come from general reluctance to share data and code publicly, or technical and logistical issues (\protect\hyperlink{ref-VDJput1V}{Gomes et al., 2022}).
+GitHub is, by default, a public and open platform, which may add additional pressure to students and scientists learning to use it.
+Moreover, additional tools may be needed to fully integrate project files and GitHub repositories (\emph{e.g.}, \protect\hyperlink{ref-lx49NGto}{\emph{Connect GitHub to a Project - OSF Support}, n.d.}).
 Other scientists may simply lack the time or incentives to document and version control their code if the code is unlikely to be reused beyond their analysis.
-However we (and others, \emph{e.g.,} \protect\hyperlink{ref-VDJput1V}{Gomes et al., 2022}) argue that the endeavour of open science and collaboration requires code owners to document and version control code despite uncertainty around future use.
+However, we (and others, \emph{e.g.,} \protect\hyperlink{ref-VDJput1V}{Gomes et al., 2022}) argue that for open science and collaboration to be successful, code owners should document and version control their code, despite uncertainty about future use.
 
@@
 
-Fifth and lastly, when projects become highly collaborative, they may have to pay for GitHub features such as branch protections, multiple reviewers of pull requests, and time in its automation tools.
-Currently, GitHub offers Education Packs (\url{https://education.github.com/}) to students and academics, which extend some paid features to the free plan.
-However, the acquisition of GitHub by Microsoft has raised concerns over the future of free plans, causing several biodiversity data managers to shift to alternative Open Source Git services (\emph{e.g.}, Bitbucket and GitLab).
+Fifth and lastly, when projects require a high degree of collaboration, they may need to pay for certain GitHub features, such as branch protections, multiple reviewers of pull requests, and time in its automation tools.
+Fortunately, GitHub offers Education Packs (\url{https://education.github.com/}) to students and academics, which extend some paid features to the free plan.
+However, the acquisition of GitHub by Microsoft has raised concerns over the future of free plans, causing several biodiversity data managers to shift to alternative Open Source Git services, such as Bitbucket and GitLab.
 
@@
 
-We describe twelve practical ways that ecologists and evolutionary biologists can adopt GitHub to improve their research workflow and make it more open and reproducible.
+We provide twelve practical ways that ecologists and evolutionary biologists can use GitHub to improve their research workflow, make it more open, reproducible and transparent.
 We provide definitions (\protect\hyperlink{definitions}{Box 1}) and types of users (Figure \ref{fig:github-diagram}) to help researchers identify and prioritize the skills and tools to learn and apply.

### 2023-03-05 manuscript.tex
Update 03.use-cases-a.md [ci skip]
This build is based on
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/6855a7f181d90025efefe38a357366e9594bb35d.

This commit was created by the following CI build and job:
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/6855a7f181d90025efefe38a357366e9594bb35d/checks
https://github.com/SORTEE-Github-Hackathon/manuscript/actions/runs/4333432537

@@
 This manuscript
-(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/3601d15cc9a4fffce47dacf71ccee802a971eb55/}{permalink})
+(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/6855a7f181d90025efefe38a357366e9594bb35d/}{permalink})
 was automatically generated
-from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/3601d15cc9a4fffce47dacf71ccee802a971eb55}{SORTEE-Github-Hackathon/manuscript@3601d15}
-on 2023-03-04.
+from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/6855a7f181d90025efefe38a357366e9594bb35d}{SORTEE-Github-Hackathon/manuscript@6855a7f}
+on 2023-03-05.
 
@@
 For instance, one can create a discussion on a project repository to decide which method to apply for biodiversity data analysis.
-Then, an issue can be created to establish steps and responsibilities including data formatting, statistical analyses, figure generation, and issue resolution (\protect\hyperlink{ref-3UAritXO}{\emph{Issues · Fmsabatini/sPlotOpen\_Manuscript}, n.d.}, =is\%3Aissue+is\%3Aclosed; \emph{e.g.}, see issues and discussions in the sPlotOpen manuscript repository, \protect\hyperlink{ref-doi:10.1111ux2fgeb.13346}{\textbf{doi:10.1111/geb.13346?}}).
+Then, an issue can be created to establish steps and responsibilities including data formatting, statistical analyses, figure generation, and issue resolution.
+For example, sPlotOpen (\protect\hyperlink{ref-doi:10.1111ux2fgeb.13346}{\textbf{doi:10.1111/geb.13346?}}) manuscript repository contains issues and discussions tracking the development of the project (see \url{https://github.com/fmsabatini/sPlotOpen_Manuscript/issues?q=is\%3Aissue+is\%3Aclosed}).
 Using GitHub for all project-related conversation and planning, rather than email or messaging tools, makes it easier to keep track of progress throughout the lifespan of a project.
-However, one can opt to receive new issues, discussions, and responses as emails and can post replies by email as well.\\
+However, one can opt to receive new issues, discussions, and responses as emails and can post replies by email as well.
 This allows for centralized communication for a team even when some members prefer to use email for communication.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-3UAritXO}{}}%
-\emph{Issues · fmsabatini/sPlotOpen\_Manuscript}. (n.d.). GitHub. Retrieved March 4, 2023, from \url{https://github.com/fmsabatini/sPlotOpen_Manuscript}
-
 \leavevmode\vadjust pre{\hypertarget{ref-ndfO9H}{}}%

### 2023-03-05 manuscript.tex
Updating my information in the metadata [ci skip]
This build is based on
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/a177cf5c28b557f4befa7f1ad912f64e65101efb.

This commit was created by the following CI build and job:
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/a177cf5c28b557f4befa7f1ad912f64e65101efb/checks
https://github.com/SORTEE-Github-Hackathon/manuscript/actions/runs/4333442113

@@
 This manuscript
-(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/6855a7f181d90025efefe38a357366e9594bb35d/}{permalink})
+(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/a177cf5c28b557f4befa7f1ad912f64e65101efb/}{permalink})
 was automatically generated
-from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/6855a7f181d90025efefe38a357366e9594bb35d}{SORTEE-Github-Hackathon/manuscript@6855a7f}
+from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/a177cf5c28b557f4befa7f1ad912f64e65101efb}{SORTEE-Github-Hackathon/manuscript@a177cf5}
 on 2023-03-05.

### 2023-03-05 manuscript.tex
Updating front matter [ci skip]
This build is based on
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/ad17a823a0016184735b9a130ff14a3e88c36e98.

This commit was created by the following CI build and job:
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/ad17a823a0016184735b9a130ff14a3e88c36e98/checks
https://github.com/SORTEE-Github-Hackathon/manuscript/actions/runs/4333509078

@@
 This manuscript
-(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/a177cf5c28b557f4befa7f1ad912f64e65101efb/}{permalink})
+(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/ad17a823a0016184735b9a130ff14a3e88c36e98/}{permalink})
 was automatically generated
-from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/a177cf5c28b557f4befa7f1ad912f64e65101efb}{SORTEE-Github-Hackathon/manuscript@a177cf5}
-on 2023-03-05.
+from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/ad17a823a0016184735b9a130ff14a3e88c36e98}{SORTEE-Github-Hackathon/manuscript@ad17a82}
+on March 5, 2023.
 
@@
   \textbf{Pedro Henrique Pereira Braga}
+  \textsuperscript{\protect\hyperlink{correspondence}{✉}}
   \includegraphics[width=0.16667in,height=0.16667in]{images/orcid.svg}
@@
   \href{https://twitter.com/pedrohp_braga}{pedrohp\_braga}
+  · \includegraphics{images/mastodon.svg}
+  \href{https://ecoevo.social/@pedrobraga}{@pedrobraga@ecoevo.social}
   Department of Biology, Concordia University, 7141 Sherbrooke Street West, Montreal, QC H4B 1R6, Canada
 \end{itemize}
+
+\leavevmode\vadjust pre{\hypertarget{correspondence}{}}%
+✉ --- Correspondence possible via \href{https://github.com/SORTEE-Github-Hackathon/manuscript/issues}{GitHub Issues}
+or email to
+Pedro Henrique Pereira Braga \textless ph.pereirabraga@gmail.com\textgreater.
 

### 2023-03-08 manuscript.tex
Updating citations related to academic misconduct in behavioural ecology [ci skip]
This build is based on
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/172dcb1ccde7bbd26b6c3e3335201992dc5c131b.

This commit was created by the following CI build and job:
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/172dcb1ccde7bbd26b6c3e3335201992dc5c131b/checks
https://github.com/SORTEE-Github-Hackathon/manuscript/actions/runs/4366532719

@@
 This manuscript
-(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/ad17a823a0016184735b9a130ff14a3e88c36e98/}{permalink})
+(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/172dcb1ccde7bbd26b6c3e3335201992dc5c131b/}{permalink})
 was automatically generated
-from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/ad17a823a0016184735b9a130ff14a3e88c36e98}{SORTEE-Github-Hackathon/manuscript@ad17a82}
-on March 5, 2023.
+from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/172dcb1ccde7bbd26b6c3e3335201992dc5c131b}{SORTEE-Github-Hackathon/manuscript@172dcb1}
+on March 8, 2023.
 
@@
 GitHub can serve as a tool for open and tractable research development.
-Collaborators can directly interact with code and data, inspect for errors, and potentially identify scientific misconduct prior to manuscript submission (\emph{e.g.}, \url{https://ecologyforthemasses.com/2020/02/04/pruittdata-and-the-ethics-of-data-in-science}).
+Collaborators can directly interact with code and data, inspect for errors, and potentially identify scientific misconduct prior to manuscript submission {[}\emph{e.g.}, Kozlov (\protect\hyperlink{ref-ut2crxgX}{2022}); Viglione (\protect\hyperlink{ref-crC1Mhe4}{2020}); \url{https://ecologyforthemasses.com/2020/02/04/pruittdata-and-the-ethics-of-data-in-science}{]}.
 Collaborators and readers are better positioned to discover erroneous or questionable findings if they have complete and transparent access to projects.
@@
 GitHub Docs.
-Retrieved March 4, 2023, from \url{https://ghdocs-prod.azurewebsites.net/en/repositories/managing-your-repositorys-settings-and-features/customizing-your-repository/about-code-owners}
+Retrieved March 8, 2023, from \url{https://ghdocs-prod.azurewebsites.net/en/repositories/managing-your-repositorys-settings-and-features/customizing-your-repository/about-code-owners}
 
@@
 GitHub Docs.
-Retrieved March 4, 2023, from \url{https://ghdocs-prod.azurewebsites.net/en/repositories/working-with-files/managing-large-files/about-large-files-on-github}
+Retrieved March 8, 2023, from \url{https://ghdocs-prod.azurewebsites.net/en/repositories/working-with-files/managing-large-files/about-large-files-on-github}
 
@@
 GitHub Docs.
-Retrieved March 4, 2023, from \url{https://ghdocs-prod.azurewebsites.net/en/issues/planning-and-tracking-with-projects/learning-about-projects/about-projects}
+Retrieved March 8, 2023, from \url{https://ghdocs-prod.azurewebsites.net/en/issues/planning-and-tracking-with-projects/learning-about-projects/about-projects}
 
@@
 GitHub Docs.
-Retrieved March 4, 2023, from \url{https://ghdocs-prod.azurewebsites.net/en/communities/setting-up-your-project-for-healthy-contributions/adding-a-license-to-a-repository}
+Retrieved March 8, 2023, from \url{https://ghdocs-prod.azurewebsites.net/en/communities/setting-up-your-project-for-healthy-contributions/adding-a-license-to-a-repository}
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-6CMMeSeD}{}}%
-Bryan, J., \& TAs, T. S. 545. (n.d.). \emph{STAT 545}. Retrieved March 4, 2023, from \url{https://stat545.com/}
+Bryan, J., \& TAs, T. S. 545. (n.d.). \emph{STAT 545}. Retrieved March 8, 2023, from \url{https://stat545.com/}
 
 \leavevmode\vadjust pre{\hypertarget{ref-lx49NGto}{}}%
-\emph{Connect GitHub to a Project - OSF Support}. (n.d.). Retrieved March 4, 2023, from \url{https://help.osf.io/article/211-connect-github-to-a-project}
+\emph{Connect GitHub to a Project - OSF Support}. (n.d.). Retrieved March 8, 2023, from \url{https://help.osf.io/article/211-connect-github-to-a-project}
 
 \leavevmode\vadjust pre{\hypertarget{ref-T03Api6e}{}}%
-\emph{Continuous Integration and Delivery}. (n.d.). CircleCI. Retrieved March 4, 2023, from \url{https://circleci.com/}
+\emph{Continuous Integration and Delivery}. (n.d.). CircleCI. Retrieved March 8, 2023, from \url{https://circleci.com/}
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-NUXbp429}{}}%
-\emph{Features • GitHub Actions}. (n.d.). GitHub. Retrieved March 4, 2023, from \url{https://github.com/features/actions}
+\emph{Features • GitHub Actions}. (n.d.). GitHub. Retrieved March 8, 2023, from \url{https://github.com/features/actions}
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-1CM2EcdVk}{}}%
-\emph{Git - A Short History of Git}. (n.d.). Retrieved March 4, 2023, from \url{https://git-scm.com/book/en/v2/Getting-Started-A-Short-History-of-Git}
+\emph{Git - A Short History of Git}. (n.d.). Retrieved March 8, 2023, from \url{https://git-scm.com/book/en/v2/Getting-Started-A-Short-History-of-Git}
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-ZvrOcg9w}{}}%
-Hester, J. B., the STAT 545 TAs, Jim. (n.d.). \emph{Let's Git started \textbar{} Happy Git and GitHub for the useR}. Retrieved March 4, 2023, from \url{https://happygitwithr.com/}
+Hester, J. B., the STAT 545 TAs, Jim. (n.d.). \emph{Let's Git started \textbar{} Happy Git and GitHub for the useR}. Retrieved March 8, 2023, from \url{https://happygitwithr.com/}
 
@@
 \url{https://doi.org/10.1111/2041-210x.13982}
+
+\leavevmode\vadjust pre{\hypertarget{ref-ut2crxgX}{}}%
+Kozlov, M. (2022). How a scandal in spider biology upended researchers' lives. \emph{Nature}, \emph{608}(7924), 658--659. \url{https://doi.org/10.1038/d41586-022-02156-2}
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-oGbKxHzj}{}}%
-\emph{Using Git and GitHub}. (n.d.). Retrieved March 4, 2023, from \url{https://www.overleaf.com/learn/how-to/Using_Git_and_GitHub}
+\emph{Using Git and GitHub}. (n.d.). Retrieved March 8, 2023, from \url{https://www.overleaf.com/learn/how-to/Using_Git_and_GitHub}
+
+\leavevmode\vadjust pre{\hypertarget{ref-crC1Mhe4}{}}%
+Viglione, G. (2020). `Avalanche' of spider-paper retractions shakes behavioural-ecology community. \emph{Nature}, \emph{578}(7794), 199--200. \url{https://doi.org/10.1038/d41586-020-00287-y}
 

### 2023-03-08 manuscript.tex
Fixing and adding DOI for OSF and Dryad repositories [ci skip]
This build is based on
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/ddd995f3f5e7c62f7171b6281520a9be8cf82da1.

This commit was created by the following CI build and job:
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/ddd995f3f5e7c62f7171b6281520a9be8cf82da1/checks
https://github.com/SORTEE-Github-Hackathon/manuscript/actions/runs/4366592231

@@
 This manuscript
-(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/172dcb1ccde7bbd26b6c3e3335201992dc5c131b/}{permalink})
+(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/ddd995f3f5e7c62f7171b6281520a9be8cf82da1/}{permalink})
 was automatically generated
-from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/172dcb1ccde7bbd26b6c3e3335201992dc5c131b}{SORTEE-Github-Hackathon/manuscript@172dcb1}
+from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/ddd995f3f5e7c62f7171b6281520a9be8cf82da1}{SORTEE-Github-Hackathon/manuscript@ddd995f}
 on March 8, 2023.
@@
 Linking GitHub repositories with a DOI helps research become findable, properly cited, and can ensure long-term stability (\protect\hyperlink{ref-iIEKCTLU}{Hampton et al., 2015}).
-This strategy has been increasingly adopted in numerous studies in ecology and evolution (\emph{e.g.}, the Zenodo repositores for Hudgins (\protect\hyperlink{ref-GQj3c17f}{2022}), EllenJCoombs (\protect\hyperlink{ref-bZNn2hbh}{2020}), and Lrharper1 (\protect\hyperlink{ref-ZI1OqZNr}{2018})).
+This strategy has been increasingly adopted in numerous studies in ecology and evolution (\emph{e.g.}, the Zenodo repositores Hudgins (\protect\hyperlink{ref-GQj3c17f}{2022}), Lrharper1 (\protect\hyperlink{ref-ZI1OqZNr}{2018}); the Dryad and OSF repositories Braga et al.
+(\protect\hyperlink{ref-xbM3u93u}{2023}) and Braga et al.
+(\protect\hyperlink{ref-TpcnPdJo}{2021})).
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-TpcnPdJo}{}}%
+Braga, P.
+H.
+P., Kembel, S., \& Peres-Neto, P.
+(2021).
+Code for: Historical and contemporary processes drive global phylogenetic structure across geographical scales: insights from bat communities.
+\emph{Open Science Framework}.
+\url{https://doi.org/10.17605/osf.io/amvp5}
+
+\leavevmode\vadjust pre{\hypertarget{ref-xbM3u93u}{}}%
+Braga, P.
+H.
+P., Peres-Neto, P., \& Kembel, S.
+(2023).
+\emph{Data for: Historical and contemporary processes drive global phylogenetic structure across geographical scales: Insights from bat communities} (Version 7) {[}Data set{]}.
+Dryad.
+\url{https://doi.org/10.5061/dryad.rjdfn2zgj}
+
 \leavevmode\vadjust pre{\hypertarget{ref-ydrk01SR}{}}%
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-bZNn2hbh}{}}%
-EllenJCoombs. (2020). \emph{EllenJCoombs/Asymmetry-evolution-cetaceans-for-publication-v.1.0.0} (Version v.1.0.0) {[}Computer software{]}. Zenodo. \url{https://doi.org/10.5281/zenodo.3893943}
-
 \leavevmode\vadjust pre{\hypertarget{ref-RxK4CmfR}{}}%

### 2023-03-08 manuscript.tex
Trying @https to see if solves the problems we are having. [ci skip]
This build is based on
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/83d351133890f19b69d7c2fe2cf608d2bc773ceb.

This commit was created by the following CI build and job:
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/83d351133890f19b69d7c2fe2cf608d2bc773ceb/checks
https://github.com/SORTEE-Github-Hackathon/manuscript/actions/runs/4366672176

@@
 This manuscript
-(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/ddd995f3f5e7c62f7171b6281520a9be8cf82da1/}{permalink})
+(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/83d351133890f19b69d7c2fe2cf608d2bc773ceb/}{permalink})
 was automatically generated
-from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/ddd995f3f5e7c62f7171b6281520a9be8cf82da1}{SORTEE-Github-Hackathon/manuscript@ddd995f}
+from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/83d351133890f19b69d7c2fe2cf608d2bc773ceb}{SORTEE-Github-Hackathon/manuscript@83d3511}
 on March 8, 2023.

### 2023-03-08 manuscript.tex
Adding manual references and testing fixes [ci skip]
This build is based on
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/c6a8b5b1c928dbf7ce2eb84352ffbbdf4ff77e1d.

This commit was created by the following CI build and job:
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/c6a8b5b1c928dbf7ce2eb84352ffbbdf4ff77e1d/checks
https://github.com/SORTEE-Github-Hackathon/manuscript/actions/runs/4366796796

@@
 This manuscript
-(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/83d351133890f19b69d7c2fe2cf608d2bc773ceb/}{permalink})
+(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/c6a8b5b1c928dbf7ce2eb84352ffbbdf4ff77e1d/}{permalink})
 was automatically generated
-from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/83d351133890f19b69d7c2fe2cf608d2bc773ceb}{SORTEE-Github-Hackathon/manuscript@83d3511}
+from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/c6a8b5b1c928dbf7ce2eb84352ffbbdf4ff77e1d}{SORTEE-Github-Hackathon/manuscript@c6a8b5b}
 on March 8, 2023.
@@
 
-The use of GitHub has become increasingly popular in recent years due to the expansive GitHub user-community and numerous GitHub resources {[}Perez-Riverol et al.
-(\protect\hyperlink{ref-kEX5dgzK}{2016}); Bryan (\protect\hyperlink{ref-RVetqmsg}{2018}); \url{https://happygitwithr.com}; \url{https://ourcodingclub.github.io}{]}.
+The use of GitHub has become increasingly popular in recent years due to the expansive GitHub user-community and numerous GitHub resources (\protect\hyperlink{ref-RVetqmsg}{Bryan, 2018}; \protect\hyperlink{ref-13jOlVcpp}{\emph{Happy Git with R}, n.d.}; \protect\hyperlink{ref-u5aEVE4B}{\emph{Our Coding Club}, n.d.}; \protect\hyperlink{ref-kEX5dgzK}{Perez-Riverol et al., 2016}).
 Nevertheless, although multiple articles have encouraged researchers in ecology and evolution to adopt GitHub as part of their research process (\protect\hyperlink{ref-3DKwn1sY}{Lowndes et al., 2017}; \protect\hyperlink{ref-10ghgV3S8}{J.
@@
 Among many other factors, this may be because first-time users without formal training in information technology can face a steep learning curve, as GitHub and its features have been centered on software development (\protect\hyperlink{ref-139b0pSGc}{Leibzon, 2016}).
-Furthermore, there are few domain-specific resources providing tractable examples and practical guidance for researchers in EEB on how to use GitHub {[}but see Kim et al.
-(\protect\hyperlink{ref-lJAgyhYq}{2022}); \url{https://ourcodingclub.github.io}; \url{https://www.openscapes.org}{]}.
+Furthermore, there are few domain-specific resources providing tractable examples and practical guidance for researchers in EEB on how to use GitHub (but see \protect\hyperlink{ref-lJAgyhYq}{Kim et al., 2022}; \protect\hyperlink{ref-nDkLlAch}{\emph{Openscapes}, n.d.}, \textgreater; \protect\hyperlink{ref-u5aEVE4B}{\emph{Our Coding Club}, n.d.}, \textgreater).
 Widespread adoption of GitHub for collaborative research tasks can ultimately enable EEB researchers to save time on creating novel processes for collaboration and focus more on their research (\protect\hyperlink{ref-ydrk01SR}{Briney et al., 2020}).
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-13jOlVcpp}{}}%
+\emph{Happy Git with R}. (n.d.). Retrieved March 8, 2023, from \url{https://happygitwithr.com}
+
 \leavevmode\vadjust pre{\hypertarget{ref-ZvrOcg9w}{}}%
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-nDkLlAch}{}}%
+\emph{Openscapes}. (n.d.). Retrieved March 8, 2023, from \href{https:////}{//}
+
+\leavevmode\vadjust pre{\hypertarget{ref-u5aEVE4B}{}}%
+\emph{Our Coding Club}. (n.d.). Retrieved March 8, 2023, from \url{https://ourcodingclub.github.io}
+
 \leavevmode\vadjust pre{\hypertarget{ref-1FJhfqfiX}{}}%

### 2023-03-08 manuscript.tex
Fixing the size of Mastodon's icon [ci skip]
This build is based on
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/f2068e319930774a03f19646dc6c571d617a9f34.

This commit was created by the following CI build and job:
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/f2068e319930774a03f19646dc6c571d617a9f34/checks
https://github.com/SORTEE-Github-Hackathon/manuscript/actions/runs/4366818427

@@
 This manuscript
-(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/c6a8b5b1c928dbf7ce2eb84352ffbbdf4ff77e1d/}{permalink})
+(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/f2068e319930774a03f19646dc6c571d617a9f34/}{permalink})
 was automatically generated
-from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/c6a8b5b1c928dbf7ce2eb84352ffbbdf4ff77e1d}{SORTEE-Github-Hackathon/manuscript@c6a8b5b}
+from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/f2068e319930774a03f19646dc6c571d617a9f34}{SORTEE-Github-Hackathon/manuscript@f2068e3}
 on March 8, 2023.
@@
   \href{https://twitter.com/pedrohp_braga}{pedrohp\_braga}
-  · \includegraphics{images/mastodon.svg}
+  · \includegraphics[width=0.16667in,height=0.16667in]{images/mastodon.svg}
   \href{https://ecoevo.social/@pedrobraga}{@pedrobraga@ecoevo.social}

### 2023-03-08 manuscript.tex
Adding librsvg v.2.52.5 to correctly export SVG files to DOCX [ci skip]
This build is based on
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/cd23484da8a997acd9bf63c08b6317c3d9e4ac2b.

This commit was created by the following CI build and job:
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/cd23484da8a997acd9bf63c08b6317c3d9e4ac2b/checks
https://github.com/SORTEE-Github-Hackathon/manuscript/actions/runs/4366847805

@@
 This manuscript
-(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/f2068e319930774a03f19646dc6c571d617a9f34/}{permalink})
+(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/cd23484da8a997acd9bf63c08b6317c3d9e4ac2b/}{permalink})
 was automatically generated
-from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/f2068e319930774a03f19646dc6c571d617a9f34}{SORTEE-Github-Hackathon/manuscript@f2068e3}
+from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/cd23484da8a997acd9bf63c08b6317c3d9e4ac2b}{SORTEE-Github-Hackathon/manuscript@cd23484}
 on March 8, 2023.

### 2023-03-08 manuscript.tex
Changing pip git+ to f62dd4cfdebf67f99f63c9b2e64edeaa591eeb69 [ci skip]
This build is based on
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/077b97a7cbbaa6291b5ae7dd0da4f671c4978aee.

This commit was created by the following CI build and job:
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/077b97a7cbbaa6291b5ae7dd0da4f671c4978aee/checks
https://github.com/SORTEE-Github-Hackathon/manuscript/actions/runs/4366864034

@@
 This manuscript
-(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/cd23484da8a997acd9bf63c08b6317c3d9e4ac2b/}{permalink})
+(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/077b97a7cbbaa6291b5ae7dd0da4f671c4978aee/}{permalink})
 was automatically generated
-from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/cd23484da8a997acd9bf63c08b6317c3d9e4ac2b}{SORTEE-Github-Hackathon/manuscript@cd23484}
+from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/077b97a7cbbaa6291b5ae7dd0da4f671c4978aee}{SORTEE-Github-Hackathon/manuscript@077b97a}
 on March 8, 2023.

### 2023-03-08 manuscript.tex
Fixing Hudgin's et al. 2020 Zenodo ref. title [ci skip]
This build is based on
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/2ba66415ee4d5e69b7890e54bec942747e76e441.

This commit was created by the following CI build and job:
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/2ba66415ee4d5e69b7890e54bec942747e76e441/checks
https://github.com/SORTEE-Github-Hackathon/manuscript/actions/runs/4367090381

@@
 This manuscript
-(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/077b97a7cbbaa6291b5ae7dd0da4f671c4978aee/}{permalink})
+(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/2ba66415ee4d5e69b7890e54bec942747e76e441/}{permalink})
 was automatically generated
-from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/077b97a7cbbaa6291b5ae7dd0da4f671c4978aee}{SORTEE-Github-Hackathon/manuscript@077b97a}
+from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/2ba66415ee4d5e69b7890e54bec942747e76e441}{SORTEE-Github-Hackathon/manuscript@2ba6641}
 on March 8, 2023.

### 2023-03-08 manuscript.tex
Fixing 10.5281/zenodo.6097109 [ci skip]
This build is based on
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/db4ebdb09871e3ca3db2086b8fabfe614cc5ba56.

This commit was created by the following CI build and job:
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/db4ebdb09871e3ca3db2086b8fabfe614cc5ba56/checks
https://github.com/SORTEE-Github-Hackathon/manuscript/actions/runs/4367119918

@@
 This manuscript
-(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/2ba66415ee4d5e69b7890e54bec942747e76e441/}{permalink})
+(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/db4ebdb09871e3ca3db2086b8fabfe614cc5ba56/}{permalink})
 was automatically generated
-from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/2ba66415ee4d5e69b7890e54bec942747e76e441}{SORTEE-Github-Hackathon/manuscript@2ba6641}
+from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/db4ebdb09871e3ca3db2086b8fabfe614cc5ba56}{SORTEE-Github-Hackathon/manuscript@db4ebdb}
 on March 8, 2023.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-GQj3c17f}{}}%
-Hudgins, E. (2022). \emph{emmajhudgins/UStreedamage: publication release} (accepted) {[}Computer software{]}. Zenodo. \url{https://doi.org/10.5281/zenodo.6097109}
+Hudgins, E.
+(2022).
+\emph{Data and code for 'Hotspots of pest‐induced US urban tree death, 2020--2050', published in Journal of Applied Ecology} (published) {[}Computer software{]}.
+Zenodo.
+\url{https://doi.org/10.5281/zenodo.6097109}
 

### 2023-03-08 manuscript.tex
Manually adding citation for sPlotOpen, 10.1111/geb.13346 [ci skip]
This build is based on
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/8ffc29ead8fe50fa37fb68dc41d9fc3c10f316fc.

This commit was created by the following CI build and job:
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/8ffc29ead8fe50fa37fb68dc41d9fc3c10f316fc/checks
https://github.com/SORTEE-Github-Hackathon/manuscript/actions/runs/4367140985

@@
 This manuscript
-(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/db4ebdb09871e3ca3db2086b8fabfe614cc5ba56/}{permalink})
+(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/8ffc29ead8fe50fa37fb68dc41d9fc3c10f316fc/}{permalink})
 was automatically generated
-from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/db4ebdb09871e3ca3db2086b8fabfe614cc5ba56}{SORTEE-Github-Hackathon/manuscript@db4ebdb}
+from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/8ffc29ead8fe50fa37fb68dc41d9fc3c10f316fc}{SORTEE-Github-Hackathon/manuscript@8ffc29e}
 on March 8, 2023.
@@
 Then, an issue can be created to establish steps and responsibilities including data formatting, statistical analyses, figure generation, and issue resolution.
-For example, sPlotOpen (\protect\hyperlink{ref-doi:10.1111ux2fgeb.13346}{\textbf{doi:10.1111/geb.13346?}}) manuscript repository contains issues and discussions tracking the development of the project (see \url{https://github.com/fmsabatini/sPlotOpen_Manuscript/issues?q=is\%3Aissue+is\%3Aclosed}).
+For example, sPlotOpen (\protect\hyperlink{ref-HtStoSAI}{Sabatini et al., 2021}) manuscript repository contains issues and discussions tracking the development of the project (see \url{https://github.com/fmsabatini/sPlotOpen_Manuscript/issues?q=is\%3Aissue+is\%3Aclosed}).
 Using GitHub for all project-related conversation and planning, rather than email or messaging tools, makes it easier to keep track of progress throughout the lifespan of a project.
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-HtStoSAI}{}}%
+Sabatini, F.
+M., Lenoir, J., Hattab, T., Arnst, E.
+A., Chytrý, M., Dengler, J., De Ruffray, P., Hennekens, S.
+M., Jandt, U., Jansen, F., Jiménez-Alfaro, B., Kattge, J., Levesley, A., Pillar, V.
+D., Purschke, O., Sandel, B., Sultana, F., Aavik, T., Aćić, S., \ldots{} Bruelheide, H.
+(2021).
+sPlotOpen -- an environmentally balanced, open-access, global dataset of vegetation plots.
+\emph{Global Ecology and Biogeography}, \emph{30}(9), 1740--1764.
+https://doi.org/\url{https://doi-org.lib-ezproxy.concordia.ca/10.1111/geb.13346}
+
 \leavevmode\vadjust pre{\hypertarget{ref-lYazDTau}{}}%

### 2023-03-08 manuscript.tex
Updating authorship order in accordance with #309 [ci skip]
This build is based on
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/1ca2ca79ea1ca4ca324b13f577b7bd2b52a8a8eb.

This commit was created by the following CI build and job:
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/1ca2ca79ea1ca4ca324b13f577b7bd2b52a8a8eb/checks
https://github.com/SORTEE-Github-Hackathon/manuscript/actions/runs/4367208550

@@
 This manuscript
-(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/8ffc29ead8fe50fa37fb68dc41d9fc3c10f316fc/}{permalink})
+(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/1ca2ca79ea1ca4ca324b13f577b7bd2b52a8a8eb/}{permalink})
 was automatically generated
-from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/8ffc29ead8fe50fa37fb68dc41d9fc3c10f316fc}{SORTEE-Github-Hackathon/manuscript@8ffc29e}
+from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/1ca2ca79ea1ca4ca324b13f577b7bd2b52a8a8eb}{SORTEE-Github-Hackathon/manuscript@1ca2ca7}
 on March 8, 2023.
@@
 \begin{itemize}
-\item
-  \textbf{Robert Crystal-Ornelas}
-  \includegraphics[width=0.16667in,height=0.16667in]{images/orcid.svg}
-  \href{https://orcid.org/0000-0002-6339-1139}{0000-0002-6339-1139}
-  · \includegraphics[width=0.16667in,height=0.16667in]{images/github.svg}
-  \href{https://github.com/robcrystalornelas}{robcrystalornelas}
-  · \includegraphics[width=0.16667in,height=0.16667in]{images/twitter.svg}
-  \href{https://twitter.com/rob_c_ornelas}{rob\_c\_ornelas}
-  Earth and Environmental Sciences Area, Lawrence Berkeley National Laboratory, Berkeley, CA 94720, USA
-\item
-  \textbf{Brandon P.M. Edwards}
-  \includegraphics[width=0.16667in,height=0.16667in]{images/orcid.svg}
-  \href{https://orcid.org/0000-0003-0865-3076}{0000-0003-0865-3076}
-  · \includegraphics[width=0.16667in,height=0.16667in]{images/github.svg}
-  \href{https://github.com/BrandonEdwards}{BrandonEdwards}
-  Department of Biology, Carleton University, Ottawa, ON K1S 5B6, Canada
-\item
-  \textbf{Katherine Hébert}
-  \includegraphics[width=0.16667in,height=0.16667in]{images/orcid.svg}
-  \href{https://orcid.org/0000-0001-7866-6775}{0000-0001-7866-6775}
-  · \includegraphics[width=0.16667in,height=0.16667in]{images/github.svg}
-  \href{https://github.com/katherinehebert}{katherinehebert}
-  · \includegraphics[width=0.16667in,height=0.16667in]{images/twitter.svg}
-  \href{https://twitter.com/hebert_kat}{hebert\_kat}
-  Département de biologie, Université de Sherbrooke, Québec, Canada
-\item
-  \textbf{Emma J. Hudgins}
-  \includegraphics[width=0.16667in,height=0.16667in]{images/orcid.svg}
-  \href{https://orcid.org/0000-0002-8402-5111}{0000-0002-8402-5111}
-  · \includegraphics[width=0.16667in,height=0.16667in]{images/github.svg}
-  \href{https://github.com/emmajhudgins}{emmajhudgins}
-  Department of Biology, Carleton University, Ottawa, ON K1S 5B6, Canada
-\item
-  \textbf{Luna L. Sánchez Reyes}
-  \includegraphics[width=0.16667in,height=0.16667in]{images/orcid.svg}
-  \href{https://orcid.org/0000-0001-7668-2528}{0000-0001-7668-2528}
-  · \includegraphics[width=0.16667in,height=0.16667in]{images/github.svg}
-  \href{https://github.com/LunaSare}{LunaSare}
-  · \includegraphics[width=0.16667in,height=0.16667in]{images/twitter.svg}
-  \href{https://twitter.com/LunaSare}{LunaSare}
-  School of Natural Sciences, University of California, Merced, USA
-\item
-  \textbf{Eric R. Scott}
-  \includegraphics[width=0.16667in,height=0.16667in]{images/orcid.svg}
-  \href{https://orcid.org/0000-0002-7430-7879}{0000-0002-7430-7879}
-  · \includegraphics[width=0.16667in,height=0.16667in]{images/github.svg}
-  \href{https://github.com/Aariq}{Aariq}
-  Communications \& Cyber Techologies, University of Arizona, Tucson, USA
-\item
-  \textbf{Matthew J. Grainger}
-  \includegraphics[width=0.16667in,height=0.16667in]{images/orcid.svg}
-  \href{https://orcid.org/0000-0001-8426-6495}{0000-0001-8426-6495}
-  · \includegraphics[width=0.16667in,height=0.16667in]{images/github.svg}
-  \href{https://github.com/DrMattG}{DrMattG}
-  · \includegraphics[width=0.16667in,height=0.16667in]{images/twitter.svg}
-  \href{https://twitter.com/Ed_pheasant}{Ed\_pheasant}
-  Terrestrial Biodiversity, Norwegian Institute for Nature Research - NINA, Postbox 5685 Torgarden, 7485 Trondheim, Norway
-\item
-  \textbf{Vivienne Foroughirad}
-  \includegraphics[width=0.16667in,height=0.16667in]{images/orcid.svg}
-  \href{https://orcid.org/0000-0002-8656-7440}{0000-0002-8656-7440}
-  · \includegraphics[width=0.16667in,height=0.16667in]{images/github.svg}
-  \href{https://github.com/vjf2}{vjf2}
-  · \includegraphics[width=0.16667in,height=0.16667in]{images/twitter.svg}
-  \href{https://twitter.com/vforoughirad}{vforoughirad}
-  Department of Biology, Georgetown University, Washington, DC, USA
-\item
-  \textbf{Allison D. Binley}
-  \includegraphics[width=0.16667in,height=0.16667in]{images/orcid.svg}
-  \href{https://orcid.org/0000-0001-8790-9935}{0000-0001-8790-9935}
-  · \includegraphics[width=0.16667in,height=0.16667in]{images/github.svg}
-  \href{https://github.com/adbinley}{adbinley}
-  · \includegraphics[width=0.16667in,height=0.16667in]{images/twitter.svg}
-  \href{https://twitter.com/AllisonBinley}{AllisonBinley}
-  Department of Biology, Carleton University, Ottawa, ON K1S 5B6, Canada
-\item
-  \textbf{Cole B. Brookson}
-  \includegraphics[width=0.16667in,height=0.16667in]{images/orcid.svg}
-  \href{https://orcid.org/0000-0003-1237-4096}{0000-0003-1237-4096}
-  · \includegraphics[width=0.16667in,height=0.16667in]{images/github.svg}
-  \href{https://github.com/colebrookson}{colebrookson}
-  Department of Biological Sciences, University of Alberta, Edmonton, AB, Canada
-\item
-  \textbf{Kaitlyn M. Gaynor}
-  \includegraphics[width=0.16667in,height=0.16667in]{images/orcid.svg}
-  \href{https://orcid.org/0000-0002-5747-0543}{0000-0002-5747-0543}
-  · \includegraphics[width=0.16667in,height=0.16667in]{images/github.svg}
-  \href{https://github.com/kaitlyngaynor}{kaitlyngaynor}
-  · \includegraphics[width=0.16667in,height=0.16667in]{images/twitter.svg}
-  \href{https://twitter.com/kaitlyngaynor}{kaitlyngaynor}
-  Departments of Zoology and Botany, University of British Columbia, Vancouver, BC, Canada
-\item
-  \textbf{Saeed Shafiei Sabet}
-  \includegraphics[width=0.16667in,height=0.16667in]{images/orcid.svg}
-  \href{https://orcid.org/0000-0001-5919-2527}{0000-0001-5919-2527}
-  · \includegraphics[width=0.16667in,height=0.16667in]{images/github.svg}
-  \href{https://github.com/shafieisabets}{shafieisabets}
-  · \includegraphics[width=0.16667in,height=0.16667in]{images/twitter.svg}
-  \href{https://twitter.com/SaeedSHSABET}{SaeedSHSABET}
-  Fisheries Department, Faculty of Natural Resources, University of Guilan, Sowmeh Sara, Iran
-\item
-  \textbf{Ali Güncan}
-  \includegraphics[width=0.16667in,height=0.16667in]{images/orcid.svg}
-  \href{https://orcid.org/0000-0003-1765-648X}{0000-0003-1765-648X}
-  · \includegraphics[width=0.16667in,height=0.16667in]{images/github.svg}
-  \href{https://github.com/Aguncan}{Aguncan}
-  · \includegraphics[width=0.16667in,height=0.16667in]{images/twitter.svg}
-  \href{https://twitter.com/aliguncan}{aliguncan}
-  Department of Plant Protection, Faculty of Agriculture, Ordu University, 52200, Ordu, Turkey
-\item
-  \textbf{Friederike Hillemann}
-  \includegraphics[width=0.16667in,height=0.16667in]{images/orcid.svg}
-  \href{https://orcid.org/0000-0002-8992-0676}{0000-0002-8992-0676}
-  · \includegraphics[width=0.16667in,height=0.16667in]{images/github.svg}
-  \href{https://github.com/fhillemann}{fhillemann}
-  Department of Human Behavior, Ecology and Culture, Max Planck Institute for Evolutionary Anthropology, Leipzig, Germany
-\item
-  \textbf{Helen Weierbach}
-  \includegraphics[width=0.16667in,height=0.16667in]{images/orcid.svg}
-  \href{https://orcid.org/0000-0001-6348-9120}{0000-0001-6348-9120}
-  · \includegraphics[width=0.16667in,height=0.16667in]{images/github.svg}
-  \href{https://github.com/helenweierbach}{helenweierbach}
-  · \includegraphics[width=0.16667in,height=0.16667in]{images/twitter.svg}
-  \href{https://twitter.com/HWeierbach}{HWeierbach}
-  Earth and Environmental Sciences Area, Lawrence Berkeley National Laboratory, Berkeley, CA 94720, USA
-\item
-  \textbf{Dylan G. E. Gomes}
-  \includegraphics[width=0.16667in,height=0.16667in]{images/orcid.svg}
-  \href{https://orcid.org/0000-0002-2642-3728}{0000-0002-2642-3728}
-  · \includegraphics[width=0.16667in,height=0.16667in]{images/github.svg}
-  \href{https://github.com/dylangomes}{dylangomes}
-  (Current) National Academy of Sciences NRC Research Associateship Program, Northwest Fisheries Science Center, National Marine Fisheries Service, National Oceanic and Atmospheric Administration, Seattle, WA, USA 98112; (Former) Cooperative Institute for Marine Resources Studies, Hatfield Marine Science Center, Oregon State University, Newport, OR, USA 97365
 \item
@@
   Department of Biology, Concordia University, 7141 Sherbrooke Street West, Montreal, QC H4B 1R6, Canada
+\item
+  \textbf{Katherine Hébert}
+  \includegraphics[width=0.16667in,height=0.16667in]{images/orcid.svg}
+  \href{https://orcid.org/0000-0001-7866-6775}{0000-0001-7866-6775}
+  · \includegraphics[width=0.16667in,height=0.16667in]{images/github.svg}
+  \href{https://github.com/katherinehebert}{katherinehebert}
+  · \includegraphics[width=0.16667in,height=0.16667in]{images/twitter.svg}
+  \href{https://twitter.com/hebert_kat}{hebert\_kat}
+  Département de biologie, Université de Sherbrooke, Québec, Canada
+\item
+  \textbf{Emma J. Hudgins}
+  \includegraphics[width=0.16667in,height=0.16667in]{images/orcid.svg}
+  \href{https://orcid.org/0000-0002-8402-5111}{0000-0002-8402-5111}
+  · \includegraphics[width=0.16667in,height=0.16667in]{images/github.svg}
+  \href{https://github.com/emmajhudgins}{emmajhudgins}
+  Department of Biology, Carleton University, Ottawa, ON K1S 5B6, Canada
+\item
+  \textbf{Eric R. Scott}
+  \includegraphics[width=0.16667in,height=0.16667in]{images/orcid.svg}
+  \href{https://orcid.org/0000-0002-7430-7879}{0000-0002-7430-7879}
+  · \includegraphics[width=0.16667in,height=0.16667in]{images/github.svg}
+  \href{https://github.com/Aariq}{Aariq}
+  Communications \& Cyber Techologies, University of Arizona, Tucson, USA
+\item
+  \textbf{Brandon P.M. Edwards}
+  \includegraphics[width=0.16667in,height=0.16667in]{images/orcid.svg}
+  \href{https://orcid.org/0000-0003-0865-3076}{0000-0003-0865-3076}
+  · \includegraphics[width=0.16667in,height=0.16667in]{images/github.svg}
+  \href{https://github.com/BrandonEdwards}{BrandonEdwards}
+  Department of Biology, Carleton University, Ottawa, ON K1S 5B6, Canada
+\item
+  \textbf{Luna L. Sánchez Reyes}
+  \includegraphics[width=0.16667in,height=0.16667in]{images/orcid.svg}
+  \href{https://orcid.org/0000-0001-7668-2528}{0000-0001-7668-2528}
+  · \includegraphics[width=0.16667in,height=0.16667in]{images/github.svg}
+  \href{https://github.com/LunaSare}{LunaSare}
+  · \includegraphics[width=0.16667in,height=0.16667in]{images/twitter.svg}
+  \href{https://twitter.com/LunaSare}{LunaSare}
+  School of Natural Sciences, University of California, Merced, USA
+\item
+  \textbf{Matthew J. Grainger}
+  \includegraphics[width=0.16667in,height=0.16667in]{images/orcid.svg}
+  \href{https://orcid.org/0000-0001-8426-6495}{0000-0001-8426-6495}
+  · \includegraphics[width=0.16667in,height=0.16667in]{images/github.svg}
+  \href{https://github.com/DrMattG}{DrMattG}
+  · \includegraphics[width=0.16667in,height=0.16667in]{images/twitter.svg}
+  \href{https://twitter.com/Ed_pheasant}{Ed\_pheasant}
+  Terrestrial Biodiversity, Norwegian Institute for Nature Research - NINA, Postbox 5685 Torgarden, 7485 Trondheim, Norway
+\item
+  \textbf{Vivienne Foroughirad}
+  \includegraphics[width=0.16667in,height=0.16667in]{images/orcid.svg}
+  \href{https://orcid.org/0000-0002-8656-7440}{0000-0002-8656-7440}
+  · \includegraphics[width=0.16667in,height=0.16667in]{images/github.svg}
+  \href{https://github.com/vjf2}{vjf2}
+  · \includegraphics[width=0.16667in,height=0.16667in]{images/twitter.svg}
+  \href{https://twitter.com/vforoughirad}{vforoughirad}
+  Department of Biology, Georgetown University, Washington, DC, USA
+\item
+  \textbf{Friederike Hillemann}
+  \includegraphics[width=0.16667in,height=0.16667in]{images/orcid.svg}
+  \href{https://orcid.org/0000-0002-8992-0676}{0000-0002-8992-0676}
+  · \includegraphics[width=0.16667in,height=0.16667in]{images/github.svg}
+  \href{https://github.com/fhillemann}{fhillemann}
+  Department of Human Behavior, Ecology and Culture, Max Planck Institute for Evolutionary Anthropology, Leipzig, Germany
+\item
+  \textbf{Allison D. Binley}
+  \includegraphics[width=0.16667in,height=0.16667in]{images/orcid.svg}
+  \href{https://orcid.org/0000-0001-8790-9935}{0000-0001-8790-9935}
+  · \includegraphics[width=0.16667in,height=0.16667in]{images/github.svg}
+  \href{https://github.com/adbinley}{adbinley}
+  · \includegraphics[width=0.16667in,height=0.16667in]{images/twitter.svg}
+  \href{https://twitter.com/AllisonBinley}{AllisonBinley}
+  Department of Biology, Carleton University, Ottawa, ON K1S 5B6, Canada
+\item
+  \textbf{Cole B. Brookson}
+  \includegraphics[width=0.16667in,height=0.16667in]{images/orcid.svg}
+  \href{https://orcid.org/0000-0003-1237-4096}{0000-0003-1237-4096}
+  · \includegraphics[width=0.16667in,height=0.16667in]{images/github.svg}
+  \href{https://github.com/colebrookson}{colebrookson}
+  Department of Biological Sciences, University of Alberta, Edmonton, AB, Canada
+\item
+  \textbf{Kaitlyn M. Gaynor}
+  \includegraphics[width=0.16667in,height=0.16667in]{images/orcid.svg}
+  \href{https://orcid.org/0000-0002-5747-0543}{0000-0002-5747-0543}
+  · \includegraphics[width=0.16667in,height=0.16667in]{images/github.svg}
+  \href{https://github.com/kaitlyngaynor}{kaitlyngaynor}
+  · \includegraphics[width=0.16667in,height=0.16667in]{images/twitter.svg}
+  \href{https://twitter.com/kaitlyngaynor}{kaitlyngaynor}
+  Departments of Zoology and Botany, University of British Columbia, Vancouver, BC, Canada
+\item
+  \textbf{Saeed Shafiei Sabet}
+  \includegraphics[width=0.16667in,height=0.16667in]{images/orcid.svg}
+  \href{https://orcid.org/0000-0001-5919-2527}{0000-0001-5919-2527}
+  · \includegraphics[width=0.16667in,height=0.16667in]{images/github.svg}
+  \href{https://github.com/shafieisabets}{shafieisabets}
+  · \includegraphics[width=0.16667in,height=0.16667in]{images/twitter.svg}
+  \href{https://twitter.com/SaeedSHSABET}{SaeedSHSABET}
+  Fisheries Department, Faculty of Natural Resources, University of Guilan, Sowmeh Sara, Iran
+\item
+  \textbf{Ali Güncan}
+  \includegraphics[width=0.16667in,height=0.16667in]{images/orcid.svg}
+  \href{https://orcid.org/0000-0003-1765-648X}{0000-0003-1765-648X}
+  · \includegraphics[width=0.16667in,height=0.16667in]{images/github.svg}
+  \href{https://github.com/Aguncan}{Aguncan}
+  · \includegraphics[width=0.16667in,height=0.16667in]{images/twitter.svg}
+  \href{https://twitter.com/aliguncan}{aliguncan}
+  Department of Plant Protection, Faculty of Agriculture, Ordu University, 52200, Ordu, Turkey
+\item
+  \textbf{Helen Weierbach}
+  \includegraphics[width=0.16667in,height=0.16667in]{images/orcid.svg}
+  \href{https://orcid.org/0000-0001-6348-9120}{0000-0001-6348-9120}
+  · \includegraphics[width=0.16667in,height=0.16667in]{images/github.svg}
+  \href{https://github.com/helenweierbach}{helenweierbach}
+  · \includegraphics[width=0.16667in,height=0.16667in]{images/twitter.svg}
+  \href{https://twitter.com/HWeierbach}{HWeierbach}
+  Earth and Environmental Sciences Area, Lawrence Berkeley National Laboratory, Berkeley, CA 94720, USA
+\item
+  \textbf{Dylan G. E. Gomes}
+  \includegraphics[width=0.16667in,height=0.16667in]{images/orcid.svg}
+  \href{https://orcid.org/0000-0002-2642-3728}{0000-0002-2642-3728}
+  · \includegraphics[width=0.16667in,height=0.16667in]{images/github.svg}
+  \href{https://github.com/dylangomes}{dylangomes}
+  (Current) National Academy of Sciences NRC Research Associateship Program, Northwest Fisheries Science Center, National Marine Fisheries Service, National Oceanic and Atmospheric Administration, Seattle, WA, USA 98112; (Former) Cooperative Institute for Marine Resources Studies, Hatfield Marine Science Center, Oregon State University, Newport, OR, USA 97365
+\item
+  \textbf{Robert Crystal-Ornelas}
+  \includegraphics[width=0.16667in,height=0.16667in]{images/orcid.svg}
+  \href{https://orcid.org/0000-0002-6339-1139}{0000-0002-6339-1139}
+  · \includegraphics[width=0.16667in,height=0.16667in]{images/github.svg}
+  \href{https://github.com/robcrystalornelas}{robcrystalornelas}
+  · \includegraphics[width=0.16667in,height=0.16667in]{images/twitter.svg}
+  \href{https://twitter.com/rob_c_ornelas}{rob\_c\_ornelas}
+  Earth and Environmental Sciences Area, Lawrence Berkeley National Laboratory, Berkeley, CA 94720, USA
 \end{itemize}

### 2023-03-08 R/comparison_table.Rmd
Fixing captions

@@
 ```{r compare}
-kable(comp_tbl, caption = "Table: a comparison of technologies... {#tbl:compare}")
+kable(comp_tbl, caption = "A comparison of technologies commonly used for collaborating on research in Ecology and Evolutionary Biology.
+In the first column, we group platforms for collaboration into broad guilds.
+The second column lists the platform for collaboration.
+The remaining columns indicate whether the platform for collaboration includes certain features {#tbl:compare}")
 ```

### 2023-03-08 R/roles_table.Rmd
Addressing R2.8. by replacing "e" with "a"
Fixing captions

@@
 ```{r roles}
-kable(roles_wide, caption = "Table: A non-exhaustive collection of ideas for how various GitHub features could be utilized for a research project.
+kable(roles_wide, caption = "A non-exhaustive collection of ideas for how various GitHub features could be utilized for a research project.
 Here we have categorized contributors/collaborators into five roles.
@@
 Finally, community members could be other researchers or non-researchers interested in reproducing results, re-using code or data, or communicating with researchers involved in the project.
-These roles are not mutually exclusive—a co-author could also be e code contributor and code reviewer, for example.
+These roles are not mutually exclusive—a co-author could also be a code contributor and code reviewer, for example.
 For definitions of the GitHub features, see Box 1.

### 2023-03-08 manuscript.tex
Updating the comparison table [ci skip]
This build is based on
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/454ea98fc5bad08fda4ba675c377a7db51d7a419.

This commit was created by the following CI build and job:
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/454ea98fc5bad08fda4ba675c377a7db51d7a419/checks
https://github.com/SORTEE-Github-Hackathon/manuscript/actions/runs/4367442220

@@
 This manuscript
-(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/1ca2ca79ea1ca4ca324b13f577b7bd2b52a8a8eb/}{permalink})
+(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/454ea98fc5bad08fda4ba675c377a7db51d7a419/}{permalink})
 was automatically generated
-from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/1ca2ca79ea1ca4ca324b13f577b7bd2b52a8a8eb}{SORTEE-Github-Hackathon/manuscript@1ca2ca7}
+from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/454ea98fc5bad08fda4ba675c377a7db51d7a419}{SORTEE-Github-Hackathon/manuscript@454ea98}
 on March 8, 2023.
@@
 Collaborative code/text editors & HackMD & yes & yes & yes & yes & limited free version \& paid & no & 3 documents free, private invitee limits & yes \\
+\bottomrule()
+\end{longtable}
+
+\begin{longtable}[]{@{}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.0674}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.0567}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.0301}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.0390}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.0408}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.0567}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.2039}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.1844}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.2855}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.0355}}@{}}
+\caption{a comparison of technologies\ldots{} \label{tbl:compare}}\label{tbl:compare}\tabularnewline
+\toprule()
+\begin{minipage}[b]{\linewidth}\raggedright
+Guild
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+Software
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+Version control
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+Cloud-storage backup
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+Passive collaboration
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+Active real-time collaboration
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+Does it provide a reasonably unrestrictive free version?
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+Is it permanent (e.g.~through a DOI)?
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+Storage limits
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+GitHub Integration
+\end{minipage} \\
+\midrule()
+\endfirsthead
+\toprule()
+\begin{minipage}[b]{\linewidth}\raggedright
+Guild
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+Software
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+Version control
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+Cloud-storage backup
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+Passive collaboration
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+Active real-time collaboration
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+Does it provide a reasonably unrestrictive free version?
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+Is it permanent (e.g.~through a DOI)?
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+Storage limits
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+GitHub Integration
+\end{minipage} \\
+\midrule()
+\endhead
+Multi-tool & GitHub & Yes & Yes & Yes & No & Broadly used free version.
+Advanced features are provided for free to students and education professionals.
+& A DOI can only be obtained when integrating to other services that can mint a DOI (e.g., Zenodo, OSF).
+& 100 MB per file, 500 MB per private repository (2 GB for paid accounts).
+100 GB for public repositories.
+Larger files (up to 2 GB) can be attached to releases.
+& Not applicable.
+\\
+Multi-tool & Open Science Framework & Yes & Yes & Yes & Yes & Yes. & Yes & 25 GB for private projects, up to 5 GB per file, plus partner add-ons, 50 GB for public projects & Yes \\
+Long-term (public) data repositories & PANGAEA & Yes & Yes & Yes & No & Yes. & Yes & 10 GB free & No \\
+Long-term (public) data repositories & Zenodo & After published & After published & Yes & No & Yes. & Yes & 50 GB per dataset & Yes \\
+Long-term (public) data repositories & Dryad & After published & After published & Yes & No & No, however certain journals cover costs. & Yes & 300 GB per publication & No. \\
+Long-term (public) data repositories & Figshare & Yes & Yes & Yes & No & Yes. & Yes & 20 GB free, up to 5 TB & Yes \\
+Temporary (personal) drive storage & Google Drive & Yes & Yes & Yes & Yes & Free version is restrictive. & No & 15GB free, up to 100GB with Google One & Yes \\
+Temporary (personal) drive storage & Box & Limited & Yes & Yes & Yes & No. & No & UnLimited total size for subscription & Yes \\
+Temporary (personal) drive storage & DropBox & Limited & Yes & Yes & Yes & Free version is restrictive. & No & 2 GB free & Yes \\
+Temporary (personal) drive storage & OneDrive and the Office Suite & Yes & Yes & Yes & Yes & Free version is restrictive. & No & 5 GB free, up to 1TB paid & Yes \\
+Collaborative code and text editors & Overleaf (online latex editor) & Yes & Yes & Yes & Yes & Free version is restrictive.
+Only affiliated institutions (majority from the Global North) obtain premium access.
+& No & 1 MB for individual LaTeX files, 50MB for individual files, unlimited project size.
+& Yes \\
+Collaborative code and text editors & Jupyter Notebook & Yes & Yes & Yes & With Colab & Yes.
+& No & via Binder: no hard limit, but suggests no files \textgreater100MB, can also store on GitHub or Google Colab & Yes \\
+Collaborative code and text editors & HackMD & Yes & Yes & Yes & Yes & Free version is moderatively restrictive. & No & 3 documents free, private invitee limits & Yes \\
+Collaborative code and text editors & Colaboratory & Yes & Yes & Yes & Yes & Free version is moderatively unresitrcitve, unless high computational resources are required.
+& No & Colab that is free of charge notebooks can run for at most 12 hours.
+File storage is bounded to Google Drive's limitations.
+12 GB GPU RAM .
+& No.
+\\
 \bottomrule()

### 2023-03-08 manuscript.tex
Fixing captions [ci skip]
This build is based on
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/6f7126e88d2a25b0e683001ae1a3f9a04bfc43e1.

This commit was created by the following CI build and job:
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/6f7126e88d2a25b0e683001ae1a3f9a04bfc43e1/checks
https://github.com/SORTEE-Github-Hackathon/manuscript/actions/runs/4367467250

@@
 This manuscript
-(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/454ea98fc5bad08fda4ba675c377a7db51d7a419/}{permalink})
+(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/6f7126e88d2a25b0e683001ae1a3f9a04bfc43e1/}{permalink})
 was automatically generated
-from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/454ea98fc5bad08fda4ba675c377a7db51d7a419}{SORTEE-Github-Hackathon/manuscript@454ea98}
+from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/6f7126e88d2a25b0e683001ae1a3f9a04bfc43e1}{SORTEE-Github-Hackathon/manuscript@6f7126e}
 on March 8, 2023.
@@
 \emph{Global Ecology and Biogeography}, \emph{30}(9), 1740--1764.
-https://doi.org/\url{https://doi-org.lib-ezproxy.concordia.ca/10.1111/geb.13346}
+\url{https://doi.org/10.1111/geb.13346}
 

### 2023-03-08 manuscript.tex
Fixing caption once again. [ci skip]
This build is based on
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/45bcf9513abb9e8e2c4d9134d4bceb88a8696810.

This commit was created by the following CI build and job:
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/45bcf9513abb9e8e2c4d9134d4bceb88a8696810/checks
https://github.com/SORTEE-Github-Hackathon/manuscript/actions/runs/4367471680

@@
 This manuscript
-(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/6f7126e88d2a25b0e683001ae1a3f9a04bfc43e1/}{permalink})
+(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/45bcf9513abb9e8e2c4d9134d4bceb88a8696810/}{permalink})
 was automatically generated
-from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/6f7126e88d2a25b0e683001ae1a3f9a04bfc43e1}{SORTEE-Github-Hackathon/manuscript@6f7126e}
+from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/45bcf9513abb9e8e2c4d9134d4bceb88a8696810}{SORTEE-Github-Hackathon/manuscript@45bcf95}
 on March 8, 2023.
@@
 
+\begin{tablenos:no-prefix-table-caption}
+
 \begin{longtable}[]{@{}
@@
   >{\raggedright\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.0355}}@{}}
-\caption{a comparison of technologies\ldots{} \label{tbl:compare}}\label{tbl:compare}\tabularnewline
-\toprule()
-\begin{minipage}[b]{\linewidth}\raggedright
-Guild
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
-Software
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
-Version control
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
-Cloud-storage backup
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
-Passive collaboration
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
-Active real-time collaboration
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
-Does it provide a reasonably unrestrictive free version?
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
-Is it permanent (e.g.~through a DOI)?
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
-Storage limits
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
-GitHub Integration
-\end{minipage} \\
-\midrule()
-\endfirsthead
 \toprule()
@@
 \end{longtable}
+
+\end{tablenos:no-prefix-table-caption}
+
+A comparison of technologies commonly used for collaborating on research
+in Ecology and Evolutionary Biology. In the first column, we group
+platforms for collaboration into broad guilds. The second column lists
+the platform for collaboration. The remaining columns indicate whether
+the platform for collaboration includes certain features \{\#tbl:compare\}
 

### 2023-03-09 R/comparison_table.Rmd
Fixing output_file for 10.comparison_table.md

@@
  encoding=encoding,
- output_file=file.path(dirname(input_file), out_dir, '11.comparison_table.md'))})
+ output_file=file.path(dirname(input_file), out_dir, '10.comparison_table.md'))})
 output: 

### 2023-03-09 manuscript.tex
Removing duplicated table. [ci skip]
This build is based on
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/388ca7cf852b78a84a8e8b3411f1243976ed978b.

This commit was created by the following CI build and job:
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/388ca7cf852b78a84a8e8b3411f1243976ed978b/checks
https://github.com/SORTEE-Github-Hackathon/manuscript/actions/runs/4378560886

@@
 This manuscript
-(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/45bcf9513abb9e8e2c4d9134d4bceb88a8696810/}{permalink})
+(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/388ca7cf852b78a84a8e8b3411f1243976ed978b/}{permalink})
 was automatically generated
-from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/45bcf9513abb9e8e2c4d9134d4bceb88a8696810}{SORTEE-Github-Hackathon/manuscript@45bcf95}
-on March 8, 2023.
+from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/388ca7cf852b78a84a8e8b3411f1243976ed978b}{SORTEE-Github-Hackathon/manuscript@388ca7c}
+on March 9, 2023.
 
@@
 \subsection{Tables}\label{tables}}
-
-\begin{longtable}[]{@{}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.0627}}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.0528}}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.0281}}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.0281}}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.0380}}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.0528}}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.1799}}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.1683}}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.2558}}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.1337}}@{}}
-\caption{A comparison of technologies commonly used for collaborating on research in Ecology and Evolutionary Biology.
-In the first column, we group platforms for collaboration into broad guilds.
-The second column lists the platform for collaboration.
-The remaining columns indicate whether the platform for collaboration includes certain features.
-\label{tbl:compare}}\label{tbl:compare}\tabularnewline
-\toprule()
-\begin{minipage}[b]{\linewidth}\raggedright
-Guild
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
-Software
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
-Version control
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
-Backup (cloud)
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
-Passive collaboration
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
-Active real-time collaboration
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
-Free plan available
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
-Permanent (DOI)
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
-Storage limits
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
-GitHub Integration
-\end{minipage} \\
-\midrule()
-\endfirsthead
-\toprule()
-\begin{minipage}[b]{\linewidth}\raggedright
-Guild
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
-Software
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
-Version control
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
-Backup (cloud)
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
-Passive collaboration
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
-Active real-time collaboration
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
-Free plan available
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
-Permanent (DOI)
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
-Storage limits
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
-GitHub Integration
-\end{minipage} \\
-\midrule()
-\endhead
-Multi-tool & GitHub & yes & yes & yes & no & Broadly used free version.
-Advanced features are provided for free to students and education professionals.
-& A DOI can only be obtained when integrating to other services that can mint DOI (e.g., Zenodo, OSF).
-& 100MB per file, 500MB per private repository (2GB for paid accounts).
-100GB for public repositories.
-Larger files (up to 2GB) can be attached to releases & N/A \\
-Multi-tool & Open Science Framework & yes & yes & yes & yes & yes & yes & 25GB for private projects, up to 5GB per file, plus partner add-ons, 50GB for public projects & yes \\
-Long-term (public) data repositories & PANGAEA & yes & yes & yes & no & yes & yes & 10 GB free & no \\
-Long-term (public) data repositories & Zenodo & after published & after published & yes & no & yes & yes & 50 GB per dataset & yes \\
-Long-term (public) data repositories & Dryad & after published & after published & yes & no & some journals cover cost & yes & 300 GB per publication & Can link to individual files (not entire repository), thus not fully integrated \\
-Long-term (public) data repositories & Figshare & yes & yes & yes & no & yes & yes & 20 GB free, up to 5 TB & yes \\
-Temporary (personal) drive storage & Google Drive & yes & yes & yes & yes & limited free version \& paid & no & 15GB free, up to 100GB with Google One & yes \\
-Temporary (personal) drive storage & Box & limited & yes & yes & yes & no & no & Unlimited total size for subscription & yes \\
-Temporary (personal) drive storage & DropBox & limited & yes & yes & yes & limited free version \& paid & no & 2GB free & yes \\
-Temporary (personal) drive storage & OneDrive and the Office Suite & yes & yes & yes & yes & limited free version \& paid & no & 5 GB free, up to 1TB paid & yes \\
-Collaborative code/text editors & Overleaf (online latex editor) & yes & yes & yes & yes & yes & no & 1MB for individual .tex, 50MB for individual files, unlimited project size & yes \\
-Collaborative code/text editors & Jupyter Notebook & yes & ?
-& yes & with Colab & yes & no & via Binder: no hard limit, but suggests no files \textgreater100MB, can also store on GitHub or Google Colab & yes \\
-Collaborative code/text editors & HackMD & yes & yes & yes & yes & limited free version \& paid & no & 3 documents free, private invitee limits & yes \\
-\bottomrule()
-\end{longtable}
 
@@
 GitHub Docs.
-Retrieved March 8, 2023, from \url{https://ghdocs-prod.azurewebsites.net/en/repositories/managing-your-repositorys-settings-and-features/customizing-your-repository/about-code-owners}
+Retrieved March 9, 2023, from \url{https://ghdocs-prod.azurewebsites.net/en/repositories/managing-your-repositorys-settings-and-features/customizing-your-repository/about-code-owners}
 
@@
 GitHub Docs.
-Retrieved March 8, 2023, from \url{https://ghdocs-prod.azurewebsites.net/en/repositories/working-with-files/managing-large-files/about-large-files-on-github}
+Retrieved March 9, 2023, from \url{https://ghdocs-prod.azurewebsites.net/en/repositories/working-with-files/managing-large-files/about-large-files-on-github}
 
@@
 GitHub Docs.
-Retrieved March 8, 2023, from \url{https://ghdocs-prod.azurewebsites.net/en/issues/planning-and-tracking-with-projects/learning-about-projects/about-projects}
+Retrieved March 9, 2023, from \url{https://ghdocs-prod.azurewebsites.net/en/issues/planning-and-tracking-with-projects/learning-about-projects/about-projects}
 
@@
 GitHub Docs.
-Retrieved March 8, 2023, from \url{https://ghdocs-prod.azurewebsites.net/en/communities/setting-up-your-project-for-healthy-contributions/adding-a-license-to-a-repository}
+Retrieved March 9, 2023, from \url{https://ghdocs-prod.azurewebsites.net/en/communities/setting-up-your-project-for-healthy-contributions/adding-a-license-to-a-repository}
 
@@
 H.
-P., Peres-Neto, P., \& Kembel, S.
+P., Kembel, S., \& Peres-Neto, P.
 (2023).
-\emph{Data for: Historical and contemporary processes drive global phylogenetic structure across geographical scales: Insights from bat communities} (Version 7) {[}Data set{]}.
+\emph{Data for: Historical and contemporary processes drive global phylogenetic structure across geographical scales: Insights from bat communities} (Version 9) {[}Data set{]}.
 Dryad.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-6CMMeSeD}{}}%
-Bryan, J., \& TAs, T. S. 545. (n.d.). \emph{STAT 545}. Retrieved March 8, 2023, from \url{https://stat545.com/}
+Bryan, J., \& TAs, T. S. 545. (n.d.). \emph{STAT 545}. Retrieved March 9, 2023, from \url{https://stat545.com/}
 
 \leavevmode\vadjust pre{\hypertarget{ref-lx49NGto}{}}%
-\emph{Connect GitHub to a Project - OSF Support}. (n.d.). Retrieved March 8, 2023, from \url{https://help.osf.io/article/211-connect-github-to-a-project}
+\emph{Connect GitHub to a Project - OSF Support}. (n.d.). Retrieved March 9, 2023, from \url{https://help.osf.io/article/211-connect-github-to-a-project}
 
 \leavevmode\vadjust pre{\hypertarget{ref-T03Api6e}{}}%
-\emph{Continuous Integration and Delivery}. (n.d.). CircleCI. Retrieved March 8, 2023, from \url{https://circleci.com/}
+\emph{Continuous Integration and Delivery}. (n.d.). CircleCI. Retrieved March 9, 2023, from \url{https://circleci.com/}
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-NUXbp429}{}}%
-\emph{Features • GitHub Actions}. (n.d.). GitHub. Retrieved March 8, 2023, from \url{https://github.com/features/actions}
+\emph{Features • GitHub Actions}. (n.d.). GitHub. Retrieved March 9, 2023, from \url{https://github.com/features/actions}
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-ZvrOcg9w}{}}%
-Hester, J. B., the STAT 545 TAs, Jim. (n.d.). \emph{Let's Git started \textbar{} Happy Git and GitHub for the useR}. Retrieved March 8, 2023, from \url{https://happygitwithr.com/}
+Hester, J. B., the STAT 545 TAs, Jim. (n.d.). \emph{Let's Git started \textbar{} Happy Git and GitHub for the useR}. Retrieved March 9, 2023, from \url{https://happygitwithr.com/}
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-nDkLlAch}{}}%
-\emph{Openscapes}. (n.d.). Retrieved March 8, 2023, from \href{https:////}{//}
+\emph{Openscapes}. (n.d.). Retrieved March 9, 2023, from \href{https:////}{//}
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-oGbKxHzj}{}}%
-\emph{Using Git and GitHub}. (n.d.). Retrieved March 8, 2023, from \url{https://www.overleaf.com/learn/how-to/Using_Git_and_GitHub}
+\emph{Using Git and GitHub}. (n.d.). Retrieved March 9, 2023, from \url{https://www.overleaf.com/learn/how-to/Using_Git_and_GitHub}
 

### 2023-03-09 manuscript.tex
Specifying equal contributions within the metadata [ci skip]
This build is based on
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/b7b98e0dba83c2c25ae7518de3f87bfe64fa235d.

This commit was created by the following CI build and job:
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/b7b98e0dba83c2c25ae7518de3f87bfe64fa235d/checks
https://github.com/SORTEE-Github-Hackathon/manuscript/actions/runs/4378679802

@@
 This manuscript
-(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/388ca7cf852b78a84a8e8b3411f1243976ed978b/}{permalink})
+(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/b7b98e0dba83c2c25ae7518de3f87bfe64fa235d/}{permalink})
 was automatically generated
-from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/388ca7cf852b78a84a8e8b3411f1243976ed978b}{SORTEE-Github-Hackathon/manuscript@388ca7c}
+from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/b7b98e0dba83c2c25ae7518de3f87bfe64fa235d}{SORTEE-Github-Hackathon/manuscript@b7b98e0}
 on March 9, 2023.
@@
   \textbf{Pedro Henrique Pereira Braga}
-  \textsuperscript{\protect\hyperlink{correspondence}{✉}}
+  \textsuperscript{\protect\hyperlink{correspondence}{✉}}†
   \includegraphics[width=0.16667in,height=0.16667in]{images/orcid.svg}
@@
   \textbf{Katherine Hébert}
+  ††
   \includegraphics[width=0.16667in,height=0.16667in]{images/orcid.svg}
@@
   \textbf{Emma J. Hudgins}
+  ††
   \includegraphics[width=0.16667in,height=0.16667in]{images/orcid.svg}
@@
   \textbf{Eric R. Scott}
+  ††
   \includegraphics[width=0.16667in,height=0.16667in]{images/orcid.svg}
@@
   \textbf{Brandon P.M. Edwards}
+  ††
   \includegraphics[width=0.16667in,height=0.16667in]{images/orcid.svg}
@@
   \textbf{Luna L. Sánchez Reyes}
+  ††
   \includegraphics[width=0.16667in,height=0.16667in]{images/orcid.svg}
@@
   \textbf{Robert Crystal-Ornelas}
+  †
   \includegraphics[width=0.16667in,height=0.16667in]{images/orcid.svg}
@@
 \end{itemize}
+
+† and †† --- These authors contributed equally to this work.
 

### 2023-03-09 manuscript.tex
Fixing table [ci skip]
This build is based on
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/b85d18073a2e39374aa8bd2e77e5046947734a25.

This commit was created by the following CI build and job:
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/b85d18073a2e39374aa8bd2e77e5046947734a25/checks
https://github.com/SORTEE-Github-Hackathon/manuscript/actions/runs/4378805497

@@
 This manuscript
-(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/b7b98e0dba83c2c25ae7518de3f87bfe64fa235d/}{permalink})
+(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/b85d18073a2e39374aa8bd2e77e5046947734a25/}{permalink})
 was automatically generated
-from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/b7b98e0dba83c2c25ae7518de3f87bfe64fa235d}{SORTEE-Github-Hackathon/manuscript@b7b98e0}
+from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/b85d18073a2e39374aa8bd2e77e5046947734a25}{SORTEE-Github-Hackathon/manuscript@b85d180}
 on March 9, 2023.
@@
 
-\begin{tablenos:no-prefix-table-caption}
-
 \begin{longtable}[]{@{}
@@
   >{\raggedright\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.0355}}@{}}
+\caption{A comparison of technologies commonly used for collaborating on research
+in Ecology and Evolutionary Biology. In the first column, we group
+platforms for collaboration into broad guilds. The second column lists
+the platform for collaboration. The remaining columns indicate whether
+the platform for collaboration includes certain features \label{tbl:compare}}\label{tbl:compare}\tabularnewline
+\toprule()
+\begin{minipage}[b]{\linewidth}\raggedright
+Guild
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+Software
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+Version control
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+Cloud-storage backup
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+Passive collaboration
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+Active real-time collaboration
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+Does it provide a reasonably unrestrictive free version?
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+Is it permanent (e.g.~through a DOI)?
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+Storage limits
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+GitHub Integration
+\end{minipage} \\
+\midrule()
+\endfirsthead
 \toprule()
@@
 \end{longtable}
-
-\end{tablenos:no-prefix-table-caption}
-
-A comparison of technologies commonly used for collaborating on research
-in Ecology and Evolutionary Biology. In the first column, we group
-platforms for collaboration into broad guilds. The second column lists
-the platform for collaboration. The remaining columns indicate whether
-the platform for collaboration includes certain features \{\#tbl:compare\}
 

### 2023-03-13 manuscript.tex
Updating response letter submitted to MEE [ci skip]
This build is based on
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/c374dc4881f6664230ad5434139fb56036a8579b.

This commit was created by the following CI build and job:
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/c374dc4881f6664230ad5434139fb56036a8579b/checks
https://github.com/SORTEE-Github-Hackathon/manuscript/actions/runs/4407649961

@@
 This manuscript
-(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/b85d18073a2e39374aa8bd2e77e5046947734a25/}{permalink})
+(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/c374dc4881f6664230ad5434139fb56036a8579b/}{permalink})
 was automatically generated
-from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/b85d18073a2e39374aa8bd2e77e5046947734a25}{SORTEE-Github-Hackathon/manuscript@b85d180}
-on March 9, 2023.
+from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/c374dc4881f6664230ad5434139fb56036a8579b}{SORTEE-Github-Hackathon/manuscript@c374dc4}
+on March 13, 2023.
 
@@
 GitHub Docs.
-Retrieved March 9, 2023, from \url{https://ghdocs-prod.azurewebsites.net/en/repositories/managing-your-repositorys-settings-and-features/customizing-your-repository/about-code-owners}
+Retrieved March 13, 2023, from \url{https://ghdocs-prod.azurewebsites.net/en/repositories/managing-your-repositorys-settings-and-features/customizing-your-repository/about-code-owners}
 
@@
 GitHub Docs.
-Retrieved March 9, 2023, from \url{https://ghdocs-prod.azurewebsites.net/en/repositories/working-with-files/managing-large-files/about-large-files-on-github}
+Retrieved March 13, 2023, from \url{https://ghdocs-prod.azurewebsites.net/en/repositories/working-with-files/managing-large-files/about-large-files-on-github}
 
@@
 GitHub Docs.
-Retrieved March 9, 2023, from \url{https://ghdocs-prod.azurewebsites.net/en/issues/planning-and-tracking-with-projects/learning-about-projects/about-projects}
+Retrieved March 13, 2023, from \url{https://ghdocs-prod.azurewebsites.net/en/issues/planning-and-tracking-with-projects/learning-about-projects/about-projects}
 
@@
 GitHub Docs.
-Retrieved March 9, 2023, from \url{https://ghdocs-prod.azurewebsites.net/en/communities/setting-up-your-project-for-healthy-contributions/adding-a-license-to-a-repository}
+Retrieved March 13, 2023, from \url{https://ghdocs-prod.azurewebsites.net/en/communities/setting-up-your-project-for-healthy-contributions/adding-a-license-to-a-repository}
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-6CMMeSeD}{}}%
-Bryan, J., \& TAs, T. S. 545. (n.d.). \emph{STAT 545}. Retrieved March 9, 2023, from \url{https://stat545.com/}
+Bryan, J., \& TAs, T. S. 545. (n.d.). \emph{STAT 545}. Retrieved March 13, 2023, from \url{https://stat545.com/}
 
 \leavevmode\vadjust pre{\hypertarget{ref-lx49NGto}{}}%
-\emph{Connect GitHub to a Project - OSF Support}. (n.d.). Retrieved March 9, 2023, from \url{https://help.osf.io/article/211-connect-github-to-a-project}
+\emph{Connect GitHub to a Project - OSF Support}. (n.d.). Retrieved March 13, 2023, from \url{https://help.osf.io/article/211-connect-github-to-a-project}
 
 \leavevmode\vadjust pre{\hypertarget{ref-T03Api6e}{}}%
-\emph{Continuous Integration and Delivery}. (n.d.). CircleCI. Retrieved March 9, 2023, from \url{https://circleci.com/}
+\emph{Continuous Integration and Delivery}. (n.d.). CircleCI. Retrieved March 13, 2023, from \url{https://circleci.com/}
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-NUXbp429}{}}%
-\emph{Features • GitHub Actions}. (n.d.). GitHub. Retrieved March 9, 2023, from \url{https://github.com/features/actions}
+\emph{Features • GitHub Actions}. (n.d.). GitHub. Retrieved March 13, 2023, from \url{https://github.com/features/actions}
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-ZvrOcg9w}{}}%
-Hester, J. B., the STAT 545 TAs, Jim. (n.d.). \emph{Let's Git started \textbar{} Happy Git and GitHub for the useR}. Retrieved March 9, 2023, from \url{https://happygitwithr.com/}
+Hester, J. B., the STAT 545 TAs, Jim. (n.d.). \emph{Let's Git started \textbar{} Happy Git and GitHub for the useR}. Retrieved March 13, 2023, from \url{https://happygitwithr.com/}
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-nDkLlAch}{}}%
-\emph{Openscapes}. (n.d.). Retrieved March 9, 2023, from \href{https:////}{//}
+\emph{Openscapes}. (n.d.). Retrieved March 13, 2023, from \href{https:////}{//}
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-oGbKxHzj}{}}%
-\emph{Using Git and GitHub}. (n.d.). Retrieved March 9, 2023, from \url{https://www.overleaf.com/learn/how-to/Using_Git_and_GitHub}
+\emph{Using Git and GitHub}. (n.d.). Retrieved March 13, 2023, from \url{https://www.overleaf.com/learn/how-to/Using_Git_and_GitHub}
 

### 2023-03-14 editorial-communication/response-to-the-reviewers.Qmd
Deploying to gh-pages from @ SORTEE-Github-Hackathon/manuscript@f105568d200daed275bf3735ef04dd1b237642b8 🚀
Deploying to gh-pages from @ SORTEE-Github-Hackathon/manuscript@c374dc4881f6664230ad5434139fb56036a8579b 🚀

@@
 ::: {style="text-align: justify"}
-Dear Dr. XXXX, Editor for Methods in Ecology and Evolution
+Dear Dr. Aaron Elison,
 
@@
 
-We have addressed all the suggestions that you and the reviewers provided. 
+We have addressed all the comments that you and the reviewers provided.
 We provide a point-by-point detailed response discussing each comment or suggestion.
@@
 
-Within our extensive revision, we have rewritten several sentences to improve their clarity, decrease the complexity and length of sections. 
-We also improved the readability of figures.
+In the response to your recommendations, we have made several changes to the manuscript.
 
-We hope that our revision has further improved this manuscript.
+We have revised all sections to rewrite several sentences to decrease their length, improve the clarity and decrease the complexity of sentences.
+We removed one of the use cases to simplify the narrative, and improved the readability of figures and tables.
+We have also included additional references to support and to clarify certain sections.
+
 We thank you again for your time and for the opportunity to submit this revised version of the manuscript.
-We very much look forward to hearing from you.
+
+We hope that our revision has further improved this manuscript and that it now meets your expectations. We very much look forward to hearing from you.
 
@@
 ::: {#ResponseE11 .response}
-<!--# TODO: edit once sections get merged -->
-
 **Response**: Thank you for these comments.
 We agree that the use cases and the jargon could be simplified to make the text more readable and attractive.
-To address these recommendations, we: (1) added a brief paragraph in the introduction describing basic Git and Github workflows, directing readers to other references containing more technical and in-depth information about these platforms;
-(2) decreased the number of use cases (see [response to R1.1](#sec-R1.1) and [response to R1.2.](#sec-R1.2)); 
-(3) added information on how GitHub Desktop and RStudio can be used as GUI interfaces for Git into Box 1 and into the Introduction (between lines XXX and XXX).
+To address these recommendations, we: (1) added a brief paragraph in the introduction describing basic Git and Github workflows (between lines 98 and 115), directing readers to other references containing more technical and in-depth information about these platforms; (2) decreased the number of use cases (see [response to R1.1](#0){style="font-size: 12pt;"} and [response to R1.2.](#0){style="font-size: 12pt;"}); (3) added information on how GitHub Desktop and RStudio can be used as GUI interfaces for Git into Box 1 and into the Introduction.
 :::
@@
 **Response**: Thank you for this suggestion!
-We added a discussion on how repositories can be kept private to the section "Storing and sharing research compendia" (between lines XXX and XXX) and in the "Open science discussion" (between lines XXX and XXX).
-We emphasized that there should not be a trade-off between privacy, using GitHub for collaboration, and open science practices.
+We added a discussion on how repositories can be kept private, as well as emphasized that there should not be a trade-off between privacy, using GitHub for collaboration, and open science practices.
+
+These changes have been added to two sections. To the "Storing and sharing research compendia" section (between lines 153 and 159), we modified the text to the form below:
 
 > GitHub allows administrative control over who can view and modify repositories, and the process of cloning, forking and suggesting changes through pull requests (see Box 1) ensures code owners have full control over code and documents.
-> Repositories can be changed from public to private, allowing data storage and management without sacrificing the privacy that may be necessary for certain compendia.
+Repositories can be changed from public to private, allowing data storage and management without sacrificing the privacy that may be necessary for certain compendia.
 With this, researchers can grant collaborators read and/or write access to files in private repositories to pursue pre-publication analyses or writing in privacy.
 
+To the "Open science discussion" section (between lines 367 and 372), we modified the following paragraph to this form:
+
+> The desire or need for privacy during the developmental stages of a manuscript or of a larger research project is common in EEB, and this is often perceived as a major barrier to doing science openly.
+Because GitHub repositories can be made private or public at any time, there is no need to choose privacy over open science, or vice-versa.
+Repositories can be kept private until their contents are ready to be shared publicly, as might occur when a research article is published or when an embargo is lifted.
 :::
@@
 ::: {#ResponseE13 .response}
-**Response**: This is a great point.
-We have added the following sentences to the end of the "Why aren't more EEB researchers using GitHub" section <!--# add line numbers -->:
+**Response**: This is a great point. We have added the following sentences to the end of the "Why aren't more EEB researchers using GitHub" section (between lines 497 and 501) :
 
 > Other scientists may simply lack the time or incentives to document and version control their code if the code is unlikely to be reused beyond their analysis.
-> However, we (and others, _e.g._ Gomes _et al._, 2022a) argue that the endeavour of open science and collaboration requires code owners to document and version control code despite uncertainty around future use.
-
+However, we (and others, e.g., Gomes et al., 2022) argue that for open science and collaboration to be successful, code owners should document, and version control their code, despite uncertainty about future use.
 :::
@@
 **Response**: Thank you for this recommendation!
-We now discuss the possibility of integrating GitHub into existing workflows on Overleaf, Google Drive, and DropBox among other services to collaboratively write scientific manuscripts, in the section "Writing a manuscript" (between lines XXX and XXX) <!--# add line numbers -->.
-We refer to Table 1 for further details on these integrations. The changes appear as below:
+We now discuss the possibility of integrating GitHub into existing workflows on Overleaf, Google Drive, and DropBox among other services to collaboratively write scientific manuscripts, in the section "Writing a manuscript" (between lines 307 and 312).
+We refer to Table 1 for further details on these integrations.
+These changes appear as below:
 
 > Incorporating GitHub into the process of writing a manuscript does not necessarily mean pivoting to an entirely new workflow.
-For instance, authors who prefer writing in LaTeX or Markdown can synchronize Overleaf (https://overleaf.com), HackMD (https://hackmd.io), and other platforms directly with a GitHub repository.
-> Similar GitHub integrations are available for projects stored in DropBox, Google Drive, among other popular tools familiar to many scientists and their collaborators (Table 1).
-
+For instance, authors who prefer writing in LaTeX or Markdown can synchronize Overleaf (Using Git and GitHub), HackMD (https://hackmd.io), and other platforms directly with a GitHub repository.
+Similar GitHub integrations are available for projects stored in DropBox, Google Drive, among other popular tools familiar to many scientists and their collaborators (Table 1).
 :::
@@
 We added this discussion earlier in the manuscript, and now refer more often to Table 1.
-These changes are listed below:
-\
+These changes are listed below:\
 
-In the first paragraph of the introduction, we made the text more concise and also added the following sentence (between lines XXX and XXX):
+In the first paragraph of the introduction, we made the text more concise and also modified the following sentences to incorporate these suggestions (between lines 62 and 69):
 
-> Within the spectrum of cloud-based services for collaboration, GitHub is uniquely positioned (Table 1) to benefit scientists because it is designed to store, track changes, and enable collaboration on computer code – fundamental components of modern research.
+> Maintaining code for scientific collaboration requires an efficient and well-documented workflow (J.
+M.
+Perkel, 2020).
+To facilitate this process, scientists have been adopting tools from information and systems technology, such as cloud-based services for documentation and version control (J.
+Perkel, 2016).
+These include Google Suite, Microsoft Suite, DropBox, and GitHub.
+Within the spectrum of cloud-based services for collaboration, GitHub is uniquely positioned (Table 1) to benefit scientists because it is specifically designed to store, track changes, and enable collaboration on computer code---fundamental components of modern research.
 
-To the second paragraph, we added (between lines XXX and XXX):
+To the second paragraph (between lines 78 and 86), we incorporated these suggestions in the following sentences:
 
-> Beyond storage and record-tracking, file management in GitHub is integrated with several communication features, allowing users to engage in discussions, to plan and collaborate in code, and publish information to a webpage (Github Issues, Github Discussions, Github Pages; see Box 1).
-> These features contrast with traditional practices of directly sharing files through email, other cloud-based services or physical storage units, which become challenging and time-consuming in long-term and collaborative projects (Ram, 2013).
-> By allowing users to easily integrate versioning, communication, collaboration with research code and data, Github paves the way for easier implementation of open science practices within research projects (Perez-Riverol et al., 2016).
+> GitHub also integrates several communication features, such as Github Issues, Github Discussions, Github Pages, which allows users to engage in discussions, to plan and collaborate on code, and publish information to a webpage (see Box 1).
+These features are an improvement over traditional practices of directly sharing files through email, other cloud-based services or physical storage units, which can become challenging and time-consuming in long-term and collaborative projects (Ram, 2013).
+By making it easier to integrate versioning, communication, collaboration with research code and data, Github helps facilitate open science practices in research projects (Perez-Riverol et al., 2016).
 
-We added the following sentences to the "Storing a research compendia" section (between lines XXX and XXX):
+We added the following sentences to the "Storing a research compendia" section (between lines 146 and 152):
 
 > Many researchers begin using GitHub to backup their research compendium (Marwick et al., 2018) into a centralized, readily-available remote server (see Box 1).
-This practice has the advantages of facilitating collaboration, integrating data and code archiving, allowing file versions to be accessed and restored, and further contributing to open science practices (Borghi & Van Gulick (2022)).
-Every change made to files in version-controlled repositories accompany authored descriptions of modifications (Box 1).
+This practice has the advantages of facilitating collaboration, integrating data and code archiving, allowing file versions to be accessed and restored, and further contributing to open science practices (Borghi & Van Gulick, 2022).
+Changes made to files in version-controlled repositories are accompanied by authored descriptions of modifications (Box 1).
 
-In the first paragraph of discussion we added <!--# add line number -->:
+In the first paragraph of discussion we incorporated these recommendations in the sentences below (between lines 435 and 439):
 
-> While tools like the Google Suite and DropBox enable rapid sharing and collaboration of some research documents, GitHub brings together features that directly integrate open science practices, such as the association of public discussions with data, code and findings, tracking multiple rounds of edits to files in a sensible way for easy review, and managing complex research projects with many collaborators and goals.
+> While tools like Google Suite and DropBox enable rapid sharing and collaboration of some research documents, GitHub brings together features that directly integrate open science practices.
+These include linking data, code and findings to public discussions, tracking edits to files for review, and managing complex research projects with many collaborators and goals.
 
-And finally, in the discussion, under "Why aren't more EEB researchers using Github", we added <!--# add line number -->:
+And finally, in the discussion, under "Why aren't more EEB researchers using Github", we added (between lines 475 and 476):
 
-> And with institutional availability of software licenses for tools like the Google Suite or Microsoft Office, researchers may be hesitant to spend valuable time learning another tool.
+> Additionally, with the availability of software licenses for tools like Google Suite or Microsoft Office, researchers may be reluctant to spend valuable time learning another tool.
 
-We also note that GitHub falls short in certain features that exist or work better in other platforms, within the "Other platforms section":
+We also note that GitHub falls short in certain features that exist or work better in other platforms, within the "Other platforms section" (between lines 463 and 468):
 
-> First, real-time document editing is still best performed on other platforms (e.g., cloud-stored documents from Microsoft Word, Google Docs, HackMD (https://hackmd.io/)).
+> First, real-time document editing is still best performed on other platforms, such as cloud-stored documents from Microsoft Word, Google Docs, and HackMD (https://hackmd.io/).
 Second, operations that are dependent on software requiring graphical user interfaces might not be easily achievable in GitHub, such as designing and manipulating figures or tables.
-> While creating tables and figures can be done through code, users may choose other software to collaboratively brainstorm figures and tables (e.g., Google Slides, Google Sheets; but see GitHub Discussions).
-
+While creating tables and figures can be done through code, users may choose other software to collaboratively brainstorm figures and tables, like Google Slides or Google Sheets (but see GitHub Discussions).
 :::
@@
 ::: {#ResponseR11 .response}
-Thank you for this recommendation! We agree that the many sections could be restructured to become more concise and clearer.
-To address this recommendation, we did the following: (1) to reduce repetition and jargon in the use cases sections, we added a paragraph to the introduction <!--# add line numbers --> explaining basic Git and Github workflows.
+Thank you for this recommendation!
+We agree that the many sections could be restructured to become more concise and clearer.
+To address this recommendation, we did the following: (1) to reduce repetition and jargon in the use cases sections, we added a paragraph to the introduction (between lines 98 and 115) explaining basic Git and Github workflows.
 We also cited resources for learning how to use tools.
-These changes allowed us to focus on the usefulness of these tools for research in ecology and evolution;
-(2) we removed the "laboratory notebooks" section and merged part of its contents into the other sections section, which allowed us to further shorten the text; and, (3) we performed an extensive review of the text to clarify and shorten sentences.
-
+These changes allowed us to focus on the usefulness of these tools for research in ecology and evolution; (2) we removed the "laboratory notebooks" section and merged part of its contents into the other sections section, which allowed us to further shorten the text; and, (3) we performed an extensive review of the text to clarify and shorten sentences.
 :::
@@
 We still mention certain advanced tools, but we refer the reader to additional learning resources instead of describing them in the manuscript.
-
 :::
@@
 For instance, while collaborative writing of a manuscript using GitHub may be seen as a strong time investment and an advanced usage, there is an increasing number of research articles using GitHub to write manuscripts, such as Halie et al.
-(arXiv:2102.01521, 2021),  Halie et al.
-(mSystems.00233-21, 2021), Lordan et al.
-(mSystems.00122-21, 2021),  Rando et al.
+([arXiv:2102.01521](https://arxiv.org/abs/2102.01521), 2021), Halie et al.
+([mSystems.00233-21](https://journals.asm.org/doi/10.1128/mSystems.00233-21), 2021), Lordan et al.
+([mSystems.00122-21](https://journals.asm.org/doi/10.1128/mSystems.00122-21), 2021), Rando et al.
 (CEUR.2976.2, 2022), Sabatini et al.
-(Global Ecology and Biogeogrpahy, 2021), Le et al.
-(Cell Systems, 2021), and many more (see https://manubot.org/catalog/; in addition to our manuscript).
+([Global Ecology and Biogeography](doi.org/10.1111/geb.13346), 2021), Le et al.
+([Cell Systems](https://www.cell.com/cell-systems/pdf/S2405-4712(21)00285-4.pdf), 2021), and many more (see <https://manubot.org/catalog/>; in addition to our manuscript).
 In these cases, most co-authors had little experience with effectively integrating Github tools to write a manuscript within the platform, and had to commit to learn and adopt proposed frameworks to achieve project completion.
-It is also difficult to measure return on investment on innovative tools that only recently took off, such as the usage of Github Actions in ecological research frameworks for data management, processing, and analysis [*e.g.*, in Sabatini et al.
+It is also difficult to measure return on investment on innovative tools that only recently took off, such as the usage of Github Actions in ecological research frameworks for data management, processing, and analysis \[*e.g.*, in Sabatini et al.
 (Global Ecology and Biogeography, 2021), McIntire et al.
 (Ecology Letters, 2022), Micheletti et al.
-(Frontiers of Ecology and Evolution, 2021)].
+(Frontiers of Ecology and Evolution, 2021)\].
 We reiterate our appreciation for this suggestion, however we think that the quantification of a ratio between investment of time and resources and returns when learning research aiding skills requires an in-depth individual study.
@@
 Moreover, we have taken the advice of reviewer 1, and reduced and reordered the use cases (see our responses to [R1.4](#sec-R1.4) and [R1.1](#sec-R1.1)).
-
 :::
@@
 ::: {#ResponseR14 .response}
-
 Thank you for this recommendation. We moved the "Project continuity" section to be presented as the second use case, immediately after introducing storing and research compedia.
-
 :::
@@
 ::: {#ResponseR15 .response}
-Corrected!
-Thank you for catching this!
+Corrected! Thank you for catching this!
 :::
@@
 ::: {#ResponseR16 .response}
-Corrected!
-Thank you once again!
+Corrected! Thank you once again!
 :::
@@
 ::: {#ResponseR21 .response}
-
 Thank you for this recommendation!
@@
 We changed it to bright-mode instead of dark-mode, blurred out irrelevant content, added three clear bounding boxes with their respective labels to highlight the repository resources, the file system organization and commit history, and the contributors.
-
 :::
@@
 ::: {#ResponseR22 .response}
-
 Thank you for catching this.
@@
 We also added citations to these elements in the text.
-
 :::
@@
 ::: {#ResponseR23 .response}
+We now briefly discuss the origin of Git and its expansion to applications beyond software development to help manage collaborations and community contributions, in the introduction (between lines 87 and 97), as seen below:
 
-We now briefly discuss the origin of Git and its expansion to applications beyond software development to help manage collaborations and community contributions, in the introduction <!--# add line numbers -->.
-
+> Git is the version control system that enables the collaborative tools available on GitHub.
+Git was initially developed as a fast, lightweight, and open-source system to allow software engineers to efficiently develop and collaborate on projects (Git - A Short History of Git).
+Since its launch in 2005, Git has become the leading version control system in software development and in other disciplines that require collaboration and community contributions, such as in scientific research (Spinellis, 2012).
+To understand how GitHub keeps track of changes to files and folders, it is recommended to have knowledge of basic concepts of Git (such as commit, push, pull, and checkout; see Box 1).
+However, the GitHub web-based platform and its integrated development environments (such as GitHub Desktop) allow users to perform most repository and data management operations without using the command console, making these functionalities available even to users who are less familiar with software development.
 :::
@@
 ::: {#ResponseR24 .response}
-
 Thank you for this recommendation.
 We recognize that these are developments that have been increasingly encouraged in biological research.
-We now provide brief comments on how automation can aid unit testing of research code (between lines XXX and XXX), and that automation can also help the interpretation, integration and usage of data and software across different sources, as seen below:
+We now provide brief comments on how automation can aid unit testing of research code (between lines 375 and 389), and that automation can also help the interpretation, integration and usage of data and software across different sources.
+These modifications are contextualized in the extract below:
 
-> In addition to increasing scientific rigour and confidence in ecological software (Scheller et al., 2010), automation can help advance more rapidly sharing ecological data and making sure the data are high quality (Dietze et al., 2018).
+> Automation frameworks can streamline many stages of the scientific process, including data collection and data validation (e.g., Micheletti et al., 2021; Yenni et al., 2019), data analysis (e.g., Beaulieu-Jones & Greene, 2017), unit testing of research code (e.g., Sarma et al., 2016), archiving and deployment of data, code and reports (e.g., this manuscript, White et al., 2018), and the interpretation, integration and usage of data and software across different sources (see Pasquier et al., 2017).
+In this context, small modifications to code and data can be frequently committed and automatically tested, as in continuous integration and continuous deployment practices (Meyer, 2014).
+This allows for early detection and correction of errors, potentially improving confidence in scientific development by minimizing software errors (see Soergel, 2015).
+In addition to increasing scientific rigour and confidence in ecological software (Scheller et al., 2010), automation can help advance more rapidly sharing ecological data and making sure the data are high quality (Dietze et al., 2018).
 Integrating automation workflows has been highly encouraged in areas of EEB, including predictive ecology (McIntire et al., 2022), long-term ecological studies (Ernest et al., 2018; Yenni et al., 2019), and management of species at risk information (Naujokaitis-Lewis et al., 2022).
-
 :::
@@
 We thank you for this comment.
-We discussed amd attempted to associate the use cases to hypothetical versions of the scientific method and academic roles.
+We discussed and attempted to associate the use cases to hypothetical versions of the scientific method and academic roles.
 Despite enjoying the idea of a figure resembling Figure 1 from Munafò et al.
@@
 The exception are "Academic websites" and "Educational materials", which may contribute to research development, but more marginally in relation to the other use cases.
-We appreciate the suggestion and would be happy to come to back it if you think it is important for our study.
+We appreciate the suggestion and would be happy to come to back to it if we can work on an alternative to this problem.
 :::
@@
 ::: {#ResponseR26 .response}
-Thank you for catching this.
-We closed the brackets.
+Thank you for catching this. We closed the brackets.
 :::
@@
 ::: {#ResponseR27 .response}
-Indeed!
-We have numbered all five barriers to using GitHub to clarify this section.
+Indeed! We have numbered all five barriers to using GitHub to clarify this section.
 :::
@@
 ::: {#ResponseR28 .response}
-You are right!
-We have corrected this issue.
-Thank you once again!
+You are right! We have corrected this issue. Thank you once again!
 :::

### 2023-03-14 manuscript.tex
Update README.md [ci skip]
This build is based on
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/dadc33c9fc7c9c7510b88ccf81b5ab517bbbf511.

This commit was created by the following CI build and job:
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/dadc33c9fc7c9c7510b88ccf81b5ab517bbbf511/checks
https://github.com/SORTEE-Github-Hackathon/manuscript/actions/runs/4411263539

@@
 This manuscript
-(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/c374dc4881f6664230ad5434139fb56036a8579b/}{permalink})
+(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/dadc33c9fc7c9c7510b88ccf81b5ab517bbbf511/}{permalink})
 was automatically generated
-from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/c374dc4881f6664230ad5434139fb56036a8579b}{SORTEE-Github-Hackathon/manuscript@c374dc4}
-on March 13, 2023.
+from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/dadc33c9fc7c9c7510b88ccf81b5ab517bbbf511}{SORTEE-Github-Hackathon/manuscript@dadc33c}
+on March 14, 2023.
 

### 2023-04-23 manuscript.tex
Merge pull request #318 from SORTEE-Github-Hackathon/badges [ci skip]
This build is based on
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/89a66fa3126d65456724dfec0cc1b21af4fed1e0.

This commit was created by the following CI build and job:
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/89a66fa3126d65456724dfec0cc1b21af4fed1e0/checks
https://github.com/SORTEE-Github-Hackathon/manuscript/actions/runs/4779303980

--- 2023-03-09 manuscript.tex
@@
 This manuscript
-(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/b85d18073a2e39374aa8bd2e77e5046947734a25/}{permalink})
+(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/89a66fa3126d65456724dfec0cc1b21af4fed1e0/}{permalink})
 was automatically generated
-from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/b85d18073a2e39374aa8bd2e77e5046947734a25}{SORTEE-Github-Hackathon/manuscript@b85d180}
-on March 9, 2023.
+from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/89a66fa3126d65456724dfec0cc1b21af4fed1e0}{SORTEE-Github-Hackathon/manuscript@89a66fa}
+on April 23, 2023.
 
@@
 GitHub Docs.
-Retrieved March 9, 2023, from \url{https://ghdocs-prod.azurewebsites.net/en/repositories/managing-your-repositorys-settings-and-features/customizing-your-repository/about-code-owners}
+Retrieved April 23, 2023, from \url{https://ghdocs-prod.azurewebsites.net/en/repositories/managing-your-repositorys-settings-and-features/customizing-your-repository/about-code-owners}
 
@@
 GitHub Docs.
-Retrieved March 9, 2023, from \url{https://ghdocs-prod.azurewebsites.net/en/repositories/working-with-files/managing-large-files/about-large-files-on-github}
+Retrieved April 23, 2023, from \url{https://ghdocs-prod.azurewebsites.net/en/repositories/working-with-files/managing-large-files/about-large-files-on-github}
 
@@
 GitHub Docs.
-Retrieved March 9, 2023, from \url{https://ghdocs-prod.azurewebsites.net/en/issues/planning-and-tracking-with-projects/learning-about-projects/about-projects}
+Retrieved April 23, 2023, from \url{https://ghdocs-prod.azurewebsites.net/en/issues/planning-and-tracking-with-projects/learning-about-projects/about-projects}
 
@@
 GitHub Docs.
-Retrieved March 9, 2023, from \url{https://ghdocs-prod.azurewebsites.net/en/communities/setting-up-your-project-for-healthy-contributions/adding-a-license-to-a-repository}
+Retrieved April 23, 2023, from \url{https://ghdocs-prod.azurewebsites.net/en/communities/setting-up-your-project-for-healthy-contributions/adding-a-license-to-a-repository}
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-6CMMeSeD}{}}%
-Bryan, J., \& TAs, T. S. 545. (n.d.). \emph{STAT 545}. Retrieved March 9, 2023, from \url{https://stat545.com/}
+Bryan, J., \& TAs, T. S. 545. (n.d.). \emph{STAT 545}. Retrieved April 23, 2023, from \url{https://stat545.com/}
 
 \leavevmode\vadjust pre{\hypertarget{ref-lx49NGto}{}}%
-\emph{Connect GitHub to a Project - OSF Support}. (n.d.). Retrieved March 9, 2023, from \url{https://help.osf.io/article/211-connect-github-to-a-project}
+\emph{Connect GitHub to a Project - OSF Support}. (n.d.). Retrieved April 23, 2023, from \url{https://help.osf.io/article/211-connect-github-to-a-project}
 
 \leavevmode\vadjust pre{\hypertarget{ref-T03Api6e}{}}%
-\emph{Continuous Integration and Delivery}. (n.d.). CircleCI. Retrieved March 9, 2023, from \url{https://circleci.com/}
+\emph{Continuous Integration and Delivery}. (n.d.). CircleCI. Retrieved April 23, 2023, from \url{https://circleci.com/}
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-NUXbp429}{}}%
-\emph{Features • GitHub Actions}. (n.d.). GitHub. Retrieved March 9, 2023, from \url{https://github.com/features/actions}
+\emph{Features • GitHub Actions}. (n.d.). GitHub. Retrieved April 23, 2023, from \url{https://github.com/features/actions}
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-ZvrOcg9w}{}}%
-Hester, J. B., the STAT 545 TAs, Jim. (n.d.). \emph{Let's Git started \textbar{} Happy Git and GitHub for the useR}. Retrieved March 9, 2023, from \url{https://happygitwithr.com/}
+Hester, J. B., the STAT 545 TAs, Jim. (n.d.). \emph{Let's Git started \textbar{} Happy Git and GitHub for the useR}. Retrieved April 23, 2023, from \url{https://happygitwithr.com/}
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-nDkLlAch}{}}%
-\emph{Openscapes}. (n.d.). Retrieved March 9, 2023, from \href{https:////}{//}
+\emph{Openscapes}. (n.d.). Retrieved April 23, 2023, from \href{https:////}{//}
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-oGbKxHzj}{}}%
-\emph{Using Git and GitHub}. (n.d.). Retrieved March 9, 2023, from \url{https://www.overleaf.com/learn/how-to/Using_Git_and_GitHub}
+\emph{Using Git and GitHub}. (n.d.). Retrieved April 23, 2023, from \url{https://www.overleaf.com/learn/how-to/Using_Git_and_GitHub}
 

### 2023-04-23 manuscript.tex
Merge pull request #319 from SORTEE-Github-Hackathon/pedrohbraga-patch-1 [ci skip]
This build is based on
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/8d5bc4ece59c37b94e74db337e837df52f6ac713.

This commit was created by the following CI build and job:
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/8d5bc4ece59c37b94e74db337e837df52f6ac713/checks
https://github.com/SORTEE-Github-Hackathon/manuscript/actions/runs/4779316109

@@
 This manuscript
-(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/89a66fa3126d65456724dfec0cc1b21af4fed1e0/}{permalink})
+(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/8d5bc4ece59c37b94e74db337e837df52f6ac713/}{permalink})
 was automatically generated
-from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/89a66fa3126d65456724dfec0cc1b21af4fed1e0}{SORTEE-Github-Hackathon/manuscript@89a66fa}
+from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/8d5bc4ece59c37b94e74db337e837df52f6ac713}{SORTEE-Github-Hackathon/manuscript@8d5bc4e}
 on April 23, 2023.
